### 2015-05-29 old stuff/cifrEmpirics.tex
pdj initial

\documentclass[authoryear]{elsarticle}
\usepackage{latexsym}
%\usepackage{rotate}
\usepackage{graphics}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{comment}
\bibliographystyle{chicago}

\newcommand{\logit}{\mathrm{logit}}
\newcommand{\I}{\mathrm{I}}
\newcommand{\E}{\mathrm{E}}
\newcommand{\p}{\mathrm{P}}
\newcommand{\e}{\mathrm{e}}
\newcommand{\vecm}{\mathrm{vec}}
\newcommand{\kp}{\otimes}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\cov}{\mathrm{cov}}
\newcommand{\eps}{\epsilon}
\newcommand{\ep}{\varepsilon}
\newcommand{\obdots}{\ddots}    % change this later
\newcommand{\Ex}{{\cal E}}
\newcommand{\rat}{{\frac{c_{ij}}{c_{i,j-1}}}}
\newcommand{\rmu}{m}
\newcommand{\rsig}{\nu}
\newcommand{\fd}{\mu}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\cor}{\mathrm{cor}}
\newcommand{\bx}[1]{\ensuremath{\overline{#1}|}}
\newcommand{\an}[1]{\ensuremath{a_{\bx{#1}}}}

\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}

\renewcommand{\i}{\item}
\newcommand{\sr}{\ensuremath{\mathrm{SRISK}}}
\newcommand{\cs}{\ensuremath{\mathrm{CS}}}
\newcommand{\cri}{\ensuremath{\mathrm{Crisis}}}
\newcommand{\var}{\ensuremath{\mathrm{VaR}}}
\newcommand{\covar}{\ensuremath{\mathrm{CoVaR}}}
\newcommand{\med}{\ensuremath{\mathrm{m}}}
\newcommand{\de}{\mathrm{d}}
\renewcommand{\v}{\ensuremath{\mathrm{v}_q}}
\newcommand{\m}{\ensuremath{\mathrm{m}}}
\newcommand{\tvar}{\ensuremath{\mathrm{TVaR}}}
\newcommand{\mes}{\ensuremath{\mathrm{MES}}}
\newcommand{\es}{\ensuremath{\mathrm{ES}}}
\newcommand{\lmes}{\ensuremath{\mathrm{LRMES}}}
\newcommand{\coes}{\ensuremath{\mathrm{CoES}}}
\newcommand{\cat}{\ensuremath{\mathrm{CATFIN}}}
\newcommand{\sged}{\ensuremath{\mathrm{SGED}}}
\newcommand{\gpd}{\ensuremath{\mathrm{GPD}}}

\newcommand{\eref}[1]{(\ref{#1})}
\newcommand{\fref}[1]{Figure \ref{#1}}
\newcommand{\sref}[1]{\S\ref{#1}}
\newcommand{\tref}[1]{Table \ref{#1}}
\newcommand{\aref}[1]{Appendix \ref{#1}}

\newcommand{\cq}{\ , \qquad}
\renewcommand{\P}{\mathrm{P}}
\newcommand{\Q}{\mathrm{Q}}

\newcommand{\Vx}{{\cal V}}
\newcommand{\be}[1]{\begin{equation}\label{#1}}
\newcommand{\ee}{\end{equation}}

\begin{document}

\renewcommand{\cs}{\ensuremath{\mathrm{CS}}}

\section{Zeta score modelling}

The zeta score of an observation $x_i$ is $\zeta_t\equiv (\Phi^-\circ  \P)r_t$ where $\P$ denotes the empirical percentile and $\Phi$ the standard normal distribution.   By construction the $\zeta_i$ are normally distributed and hence should be particularly amenable to modelling.

  How is time dependence modelled   with a copula?  One way is to plot percentiles $(u_{it},u_{i,t-1})$ for each $i$ or $(\zeta_{it},\zeta_{i,t-1})$

\cite {Engle2014} use data  on  196 large financial institutions in Europe: banks, insurance companies, financial services firms and real estate firms; daily equity returns and market capitalization from Datastream; quarterly book values for equity and debt from Compustat; world and Europe equity indexes from MSCI
\bi
\i Period: 1990-2012 
\i Econometric methods:  
\bi
\i estimate multi-factor, time varying model of returns using Dynamical Conditional Betas,
\cite{Engle2014dcb}
\i model volatility of errors using univariate asymmetric GARCH model
\i use skewed $t$ distribution for marginals of the innovations and a \textit{t} copula for the dependence structure between the innovations
\i estimation proceeds recursively from an international model [World and European indexes]; then country models [add in respective country index and use the parameters from the international model] then firm model [include firm returns and use parameters from country model]  
\i directly estimate $\lmes$
\bi
\i simulate forward 125 days returns from model estimates
\i use $S=50,000$ draws to compute
$$\lmes_{jt}=\frac{\sum_{s=1}^{S}R_{jt+1:t+h}^{s} \times I(R_{mt+1:t+h}^{s} < -40\%)}{\sum_{s=1}^{S}I(R_{mt+1:t+h}^{s}<-40\%)}$$
where $I(x)=1$ if true and 0 otherwise.
where $I(x)=1$ if true and 0 otherwise.
\ei 
\ei

\i Results:
\bi
\i rank firms, firm types and countries by $\sr$: banks contribute 83\% insurance companies 15\% of systemic risk in Europe; highest countries - France and UK contribute 52\%
\i aggregate $\sr$ Granger-causes industrial production and business confidence index
\i $\sr$ is positively related to changes in 3-month interbank rate but not significantly related to stock market return and volatility.
\ei
\ei

\section{$\covar$}

\cite{adrian2011} propose $\covar$ which is the $\var$ of the financial system $m$ when financial institution $j$ is in distress which is operationally defined as its $\var(q)$ level. 
$$\text{Pr}(r_t^m\leq\covar_{qt}^{m|j}|r_t^j=\var_{qt}^j)=q.$$
Increased risk to system $m$ when financial institution $j$ is in distress 
$$\Delta \covar_{qt}=\covar_{qt}^{m|j}-\covar_{qt}^{m|b^j}$$ 
where $b^j$ denotes the benchmark state for $j$ and equals its median return.

\cite{Girardi2013} suggest to condition on when financial institution $j$ is at its $\var$ level at best:
$$\text{Pr}(r_t^m\leq \covar_{qt}^{m|j}|r_t^j\leq \var_{qt}^j)=q.$$ They define the benchmark state $b^j$ as a one standard deviation around the mean
$$\mu_t^j - \sigma_t^j \leq r_t^j \leq \mu_t^j + \sigma_t^j.$$
and measure the percentage systemic risk contribution of $j$ by
$$\Delta \covar_{q,t}^{m|j}=100\times (\covar_{qt}^{m|j}-\covar_{qt}^{m|b^j})/\covar_{qt}^{m|b^j}.$$  \cite{Girardi2013} argue their measure improves on \cite{adrian2011} as it
\bi
\i is more general and relevant as it takes into account severity of tail losses
\i facilitates back-testing of $\covar$ using standard back-tests for $\var$.
\ei
\cite{Mainik2012} also show the \cite{Girardi2013} measure is better 
\bi
\i it is consistent with respect to the dependence parameter unlike the \cite{adrian2011} measure which is not, e.g.in a bivariate Gaussian model, the \cite{adrian2011} measure is decreasing in the correlation! 
\i consistency property also extends to Conditional Expected Shortfall [$\coes$]. 
\ei

\subsection{\cite{adrian2011}}
\bi
\i Data: weekly equity returns of 357 US bank holding companies from CRSP; quarterly balance sheet data from Compustat; state variables: VIX, liquidity spread; change in T-bill rate; change in slope of yield curve; change in credit spread; controls - market equity return; return on real estate sector.
\i Period:  1986-2010
\i Econometric methods:  
\bi
\i use quantile regressions of asset returns to estimate $CoVaR$ 
\i add lagged state variables for conditional results
\i construct out-of-sample forward $\Delta \covar$ by projecting $\Delta \covar$ on lagged size, leverage, maturity mismatch and industry dummies
\ei
\i Results:
\bi
\i $\var$ and $\Delta \covar$ are weakly related in the cross section but strongly related over time
\i $\Delta \covar$ larger for firms with higher leverage, more maturity mismatch and larger size
\i strong negative correlation between contemporaneous $\Delta \covar$ and forward $\Delta \covar$
\ei
\ei

\subsection{\cite{Girardi2013}}
\bi
\i Data:  estimate $CoVaR$ and conduct back-tests using daily equity returns of 74 large US financial firms 
\i Period:  2000-20087 
\i Econometric methods:  
\bi
\i bivariate GARCH-DCC models assuming (i) bivariate Gaussian (ii) bivariate skewed-$t$ distributions
\i 3-step procedure: 1. estimate individual $\var$ using univariate GARCH; 2. estimate bivariate density for returns using bivariate GARCH; 3. numerically solve $\covar$s
$$\int_{-\infty}^{\covar_{qt}^{m|j}}\int_{-\infty}^{\var_{qt}^{j}}pdf_t(x,y)dydx=q^2$$
$$\int_{-\infty}^{\covar_{qt}^{m|b^j}}\int_{\mu_t^j - \sigma_t^j}^{\mu_t^j + \sigma_t^j} pdf_t(x,y)dydx=p_t^j q.$$
\ei

\i Results:
\bi
\i backtests favour skewed-$t$ distribution 
\i rank of contribution to systemic risk: depositary institutions [largest]; broker-dealers; insurance companies; non-depositary institutions [smallest]
\i $\var$ and $\Delta \covar$ are weakly related cross sectionally and over time
\i all industry groups showed substantial increase in pre crisis $\Delta \covar$ 
\i $\Delta \covar$ is positively related to size and equity beta, and to leverage during down markets.
\ei
\ei

\section{$\cat$}

\cite{Allen2012} create a macroindex of systemic risk designated $\cat$  which is the arithmetic average of three $\var$ measures using the Generalized Pareto distribution [$\gpd$], skewed generalized error distribution [$\sged$] and a nonparametric approach being the relevant quantile of the empirical distribution.

$$\var_{\gpd} =\mu + \left(\frac{\sigma}{\xi} \right) \left[  \left(\frac{\alpha N}{n} \right)^{-\xi} -1\right]  $$ where $\mu,\sigma,\xi$ are location, scale and shape parameters. $\alpha$ is loss probability level, $n$ is number of extremes and $N$ is total data points.

Obtain $\var_{\sged}$ by solving numerically
$$\int_{-\infty}^{\var_{\sged(\alpha)}}f_{\mu,\sigma,\kappa,\lambda}(z)dz=\alpha$$
where $f$ is $\sged$ probability density function; $\kappa$ controls height and tails of the density and $\lambda$ is skewness.

\cite{Allen2012} also create analogous measures for expected shortfall but report that the predictability results are similar.

\subsection{\cite{Allen2012}}
\bi
\i Data:  monthly returns and market capitalization for US financial companies; Chicago Fed National Activity Index [CFNAI] and alternative macro-economic performance indicators; collect similar stock price data for EU and Asia and GDP growth rates 
\i Period:  1973-2009  
\i Econometric methods:  
\bi
\i use maximum likelihood to estimate $\gpd$ and $\sged$ parameters from monthly returns
\i estimate predictive auto-regressions of CFNAI using $\cat$ as a predictor plus other control variables
\ei

\i Results:
\bi
\i $\cat$ is negatively related to the future CFNAI for 1- to 6-month ahead forecast horizons 
\i this predictability comes from banks
\i results are robust to alternative measures of economic performance
\i regional $\cat$ also has predictive power for GDP growth in EU and Asia
\ei
\ei

\section*{References}

\bibliography{cifrEmpirics}

\end{document}

\subsection{\cite{}}
\bi
\i Data:   
\i Period:  2000-2007 
\i Econometric methods:  
\bi
\i 
\i 
\ei

\i Results:
\bi
\i 
\i 
\ei
\ei

\subsection{$SRISK$}

\ei

\subsection{$CoVaR$}

Estimate $\covarab$.

Data: d

Period: 1986-2010

Estimation:
\bi

\ei

Results:
\bi
\i
\ei

\cite{Girardi2013}

Estimation:
\bi

\ei

Results:
\bi

\ei

\cite{Huang2009}

\cite{Allen2012}

\cite{adrian2011} 
Purpose: propose a countercyclical, forward looking systemic risk measure

Data: daily equity returns of large US financial firms; quarterly balance sheet data; state variables: VIX, liquidity spread; change in T-bill rate; change in slope of yield curve; change in credit spread; controls - market equity return; return on real estate sector

Period: 1986-2010

Definitions:
$CoVaR$

Increased risk to system $m$ when firm $i$ is at its $VaR$ level (in distress) is 
$$\Delta CoVar_t=CoVaR_{i,t}^{q,q}-CoVaR_{i,t}^{q,0.5}$$

Estimation:
\bi
\i use quantile regressions of asset returns to estimate $CoVaR$
\i add lagged state variables for conditional results
\ei

 is contribution of institution $i$ to system ES
$$MES_{it}(C)=E_{t-1}(r_{it}|r_{mt}<C)$$

Systemic Expected Shortfall is amount capital [$W$] drops below its target level of $k$ times assets [$A$], conditional on a systemic crisis which occurs when aggregate capital is less than $k$ times aggregate assets
$$\frac{SES_{it}}{W_{it}}=kL_{it}-1-E_{t-1}(r_{it}|\sum_{i=1}^N W_{it}<k \sum_{i=1}^N A_{it})$$
SES is linearly related to MES:
$$SES_{it}=(kL_{it}-1+\theta MES_{it}+\Delta_i)W_{it}$$ where $\theta,\Delta$ are constants.

SRISK extends MES by accounting for liabilities and size of financial institution
$$SRISK_{it}=\max[0,(kL_{it}-1+(1-k)LRMES_{it})W_{it}]$$

SES and SRISK almost identical; choose SRISK.

Relations:
Assume a bivariate GARCH-DCC model

$$MES_{it}(\alpha)=\beta_{it}ES_{mt}(\alpha)$$ where $\beta_{it}=\rho_{it}\sigma_{it}/\sigma_{mt}.$

$$SRISK_{it}= \max[0,(kL_{it}-1+(1-k)LRMES_{it})W_{it}]$$
\cite{acharya2012aer} propose $LRMES_{it}\simeq 1-\exp(18\times MES_{it})$ [why 18? convert daily threshold of 2\% to 6 month fall of 40\%] so 
$$SRISK_{it}\simeq \max[0,(kL_{it}-1+(1-k)\exp(18\times \beta_{it} \times ES_{mt}(\alpha))W_{it}]$$

$$\Delta CoVaR_{it}(\alpha)=\gamma_{it}[VaR_{it}(\alpha)-VaR_{it}(0.5)]$$ where $\gamma_{it}=\rho_{it}\sigma_{mt}/\sigma_{it}.$

\subsection{SRISK}

\subsection{CoVaR}
\subsection{\cite{adrian2011}}

Purpose: propose a countercyclical, forward looking systemic risk measure

Data: daily equity returns of large US financial firms; quarterly balance sheet data; state variables: VIX, liquidity spread; change in T-bill rate; change in slope of yield curve; change in credit spread; controls - market equity return; return on real estate sector

Period: 1986-2010

Definitions:
$CoVaR$ 
$$\text{Pr}(R_{m,t}<-CoVaR_{i,t}^{q,p}|R_{i,t}=-VaR_{i,t}^p)=q$$
Increased risk to system $m$ when firm $i$ is at its $VaR$ level (in distress) is 
$$\Delta CoVar_t=CoVaR_{i,t}^{q,q}-CoVaR_{i,t}^{q,0.5}$$

Estimation:
\bi
\i use quantile regressions of asset returns to estimate $CoVaR$
\i add lagged state variables for conditional results
\ei

\subsubsection{CoVaR[AB]}

AB

\subsubsection{CoVaR}

Explain why this is better

\subsection{CATFIN}

\subsection{}

\subsection{

\subsection{\citet{acharya2012aer}}

\cite{acharya2012aer}

\subsection{\citep{acharya2012wp}}

\cite{acharya2012wp}

\subsection{\cite{Engle31032014}}

Purpose: measure systemic risk for large financial institutions in Europe: banks, insurance companies, financial services firms and real estate firms.

Data: individual equity returns; index returns for world, Europe and country; financial leverage

Period: 1990-2012

Definitions:

Long run marginal expected shortfall [expected loss conditional on extreme event]:
$$LRMES_{i,t:t+T}=-E_t[R_{i,t:t+T} | R_{M,t:t+T} \leq -40\%]$$
where $R$ is equity return; $40\%$ is arbitrary definition of crisis and equal to worst 6-month market fall over last decade.

Capital shortfall
$$CS_{i,t:t+T}=\{\theta(L_{i,t}-1)-(1-\theta )E_t(1-LRMES_{i,t:t+T})\}W_{i,t}$$
where $L$ is financial leverage; $\theta$ is prudential ratio of equity to assets; $W$ is market value of equity.

Systemic risk [positive capital shortfall]
$$SRISK_{i,t:t+T}=\max(0,CS_{i,t:t+T})$$

Industry level [value weighted sum]:
$$LRMES_{F,t:t+T}=\sum_{i=1}^{N}w_{i,t}LRMES_{i,t:t+T}$$

Econometric methods: 
\bi
\i estimate multi-factor, time varying model of returns using Dynamical Conditional Betas,
\cite{Engle2014}
\i model volatility of errors using univariate asymmetric GARCH model
\i use skewed $t$ distribution for marginals of the innovations and a \textit{t} copula for the dependence structure between the innovations
\i estimation proceeds recursively from an international model [World and European indexes]; then country models [add in respective country index and use the parameters from the international model] then firm model [include firm returns and use parameters from country model]  
\i directly estimate $LRMES$
\bi
\i simulate forward 125 days returns from model estimates
\i use $S=50,000$ draws to compute
$$LRMES_{i,t:t+T}^{(W)}=-\frac{\sum_{s=1}^{S}R_{i,t:t+T}^{(s)} \times I(R_{W,t:t+T}^{(s)}\leq -40\%)}{\sum_{s=1}^{S}I(R_{W,t:t+T}^{(s)}\leq -40\%)}$$
where $I(x)=1$ if true and 0 otherwise.
\ei 
\ei

Suggestions:

\subsection{\cite{Corvasce2013}}

\subsection{\cite{Benoit2013}}

Purpose: show how several popular systemic risk measures are transformations of market risk measures and derive conditions under which these measures provide similar rankings of systemically important financial institutions

Data: daily returns for large US financial firms; quarterly book values for debt

Period: 2000-2010

Definitions:

Marginal Expected Shortfall is contribution of institution $i$ to system ES
$$MES_{it}(C)=E_{t-1}(r_{it}|r_{mt}<C)$$

Systemic Expected Shortfall is amount capital [$W$] drops below its target level of $k$ times assets [$A$], conditional on a systemic crisis which occurs when aggregate capital is less than $k$ times aggregate assets
$$\frac{SES_{it}}{W_{it}}=kL_{it}-1-E_{t-1}(r_{it}|\sum_{i=1}^N W_{it}<k \sum_{i=1}^N A_{it})$$
SES is linearly related to MES:
$$SES_{it}=(kL_{it}-1+\theta MES_{it}+\Delta_i)W_{it}$$ where $\theta,\Delta$ are constants.

SRISK extends MES by accounting for liabilities and size of financial institution
$$SRISK_{it}=\max[0,(kL_{it}-1+(1-k)LRMES_{it})W_{it}]$$

SES and SRISK almost identical; choose SRISK.

Relations:
Assume a bivariate GARCH-DCC model

$$MES_{it}(\alpha)=\beta_{it}ES_{mt}(\alpha)$$ where $\beta_{it}=\rho_{it}\sigma_{it}/\sigma_{mt}.$

$$SRISK_{it}= \max[0,(kL_{it}-1+(1-k)LRMES_{it})W_{it}]$$
\cite{acharya2012aer} propose $LRMES_{it}\simeq 1-\exp(18\times MES_{it})$ [why 18? convert daily threshold of 2\% to 6 month fall of 40\%] so 
$$SRISK_{it}\simeq \max[0,(kL_{it}-1+(1-k)\exp(18\times \beta_{it} \times ES_{mt}(\alpha))W_{it}]$$

$$\Delta CoVaR_{it}(\alpha)=\gamma_{it}[VaR_{it}(\alpha)-VaR_{it}(0.5)]$$ where $\gamma_{it}=\rho_{it}\sigma_{mt}/\sigma_{it}.$

\subsection{\cite{Girardi2013}}

\subsection{more}

indicators of distress: equity return losses; CDS rates

\section*{References}

\bibliography{cifrEmpirics}

\end{document}

\cite{Huang2009}

\cite{Allen2012}

\subsection{Relations}

\cite{Benoit2013} show how several popular systemic risk measures are transformations of market risk measures and derive conditions under which these measures provide similar rankings of systemically important financial institutions.

Assume a bivariate GARCH-DCC model:
$$\mes_{jt}=\beta_{jt}\es_{st}$$ where $\beta_{jt}=\rho_{jt}\sigma_{jt}/\sigma_{st}.$
\cite{acharya2012aer} propose $LRMES_{jt}\simeq 1-\exp(18\times \mes_{jt})$ [why 18? convert daily threshold of 2\% to 6 month fall of 40\%] so

$$\sr_{jt}\simeq \min[0,(E_{jt}\exp(18\times \beta_{jt} \times \es_{st})-k(E_{jT}+D_{jT})]$$

$$\Delta \covar_{it}(\alpha)=\gamma_{it}[\var_{it}(\alpha)-\var_{it}(0.5)]$$ where $\gamma_{it}=\rho_{it}\sigma_{mt}/\sigma_{it}.$

### 2015-05-29 old stuff/cifrpaper.tex
pdj initial

\documentclass[authoryear]{elsarticle}
\usepackage{latexsym}
%\usepackage{rotate}
\usepackage{graphics}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{comment}
\bibliographystyle{chicago}

\newcommand{\logit}{\mathrm{logit}}
\newcommand{\I}{\mathrm{I}}
\newcommand{\E}{\mathrm{E}}
\newcommand{\p}{\mathrm{P}}
\newcommand{\e}{\mathrm{e}}
\newcommand{\vecm}{\mathrm{vec}}
\newcommand{\kp}{\otimes}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\cov}{\mathrm{cov}}
\newcommand{\eps}{\epsilon}
\newcommand{\ep}{\varepsilon}
\newcommand{\obdots}{\ddots}    % change this later
\newcommand{\Ex}{{\cal E}}
\newcommand{\rat}{{\frac{c_{ij}}{c_{i,j-1}}}}
\newcommand{\rmu}{m}
\newcommand{\rsig}{\nu}
\newcommand{\fd}{\mu}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\cor}{\mathrm{cor}}
\newcommand{\bx}[1]{\ensuremath{\overline{#1}|}}
\newcommand{\an}[1]{\ensuremath{a_{\bx{#1}}}}

\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}

\renewcommand{\i}{\item}
\newcommand{\sr}{\ensuremath{\mathrm{SRISK}}}
\newcommand{\cs}{\ensuremath{\mathrm{CS}}}
\newcommand{\cri}{\ensuremath{\mathrm{Crisis}}}
\newcommand{\var}{\ensuremath{\mathrm{VaR}}}
\newcommand{\covar}{\ensuremath{\mathrm{CoVaR}}}
\newcommand{\med}{\ensuremath{\mathrm{m}}}
\newcommand{\de}{\mathrm{d}}
\renewcommand{\v}{\ensuremath{\mathrm{v}_q}}
\newcommand{\m}{\ensuremath{\mathrm{m}}}
\newcommand{\tvar}{\ensuremath{\mathrm{TVaR}}}

\newcommand{\eref}[1]{(\ref{#1})}
\newcommand{\fref}[1]{Figure \ref{#1}}
\newcommand{\sref}[1]{\S\ref{#1}}
\newcommand{\tref}[1]{Table \ref{#1}}
\newcommand{\aref}[1]{Appendix \ref{#1}}

\newcommand{\cq}{\ , \qquad}
\renewcommand{\P}{\mathrm{P}}
\newcommand{\Q}{\mathrm{Q}}

\newcommand{\Vx}{{\cal V}}
\newcommand{\be}[1]{\begin{equation}\label{#1}}
\newcommand{\ee}{\end{equation}}

\begin{document}

% Title of paper
\title{Systemic risk and contagion effects in Australian financial institutions and sectors}
% List of authors, with corresponding author marked by asterisk
\author{Piet de Jong,  Geoff Loudon and Weihao Choo \\[4pt]
% Author addresses
\textit{Department of Applied Finance and Actuarial Studies\\ Macquarie University, Sydney, NSW 2109.}
\\[2pt]
%E-mail address for correspondence
{piet.dejong@mq.edu.au}}

% Running headers of paper:
\markboth%
% First field is the short list of authors
{De Jong}
% Second field is the short title of the paper
{Systemic risk}

\maketitle

\section{Literature review}

The starting point for the proposed research is the recent literature and the CIFR targeted areas and APRA aims and functions.
This recent literature includes the following
\cite{adrian2011covar},
\cite{acharya2012capital},
\cite{acharya2012measuring}
and \cite{brownlees2010volatility}.   The proposed research aims to extend and apply these techniques particularly in relation to the entities regulated by APRA.   Thus our  broad aim is to develop, implement and bring to bear recent developments in stress testing  on the aims of APRA and the CIFR targeted research areas detailed above.

\section{Improved  measures of contagion and systematic risk}
\renewcommand{\c}{\ensuremath{\mathrm{CoVaR_q}}}
\renewcommand{\v}{\ensuremath{\mathrm{VaR}_q}}

$\covar_q$ as proposed in \cite{adrian2011covar} is a basis for proposed measures contagion, exposure and systemic risk.   It  suffers from a number of drawbacks:
\bi
\i Couched in terms of $\var_q$ containing the scale of the original measurements.   It is worthwhile to have measures and techniques robust to scale.
\i  Conditioning  on $\var_{0.5}$ is undesirable and relatively intractable.  In our proposal we reference stress with respect  to the unconditional $\var_q$.   This permits a more transparent analysis and estimation. 
\i  Our proposed approach  separates out scale effects and interdependence effects and aims to  relates these separately to external variables including shocks and drivers of systemic risk.   Thus $\var_q$ movements due to scale are disentangled from movements due to codependence with separate driver responses.
\ei

\section{Significance of the project and  policy implications}

Understanding the impact of external shocks and their propagation through   the financial system is vital for managing and remediating systemic risk. Effective regulation is dependent upon the development of a robust and reliable set of appropriate risk measures.  We propose new measures of systemic risk that relate marginal and joint distributions separately to external drivers. This allows for more cogent and coherent stress testing as it includes the estimation of contagion effects, exposure effects and systemic risk across related entities and different financial sectors. Improved stress testing, estimation of risk effects and transmission of shocks through the financial system will make for more cogent prudential policy, prudential margin setting and better identify sources of risk to the financial system.

\newcommand{\q}{\mathrm{Q}}
\section{Percentile sensitivity and contagion}\label{perc}

\subsection{Theorem}  Suppose $x$ is a random vector with marginal distributions\footnote{To economise on notation, write $F_j(x)\equiv F_j(x_j)\equiv F(x_j)$ and similar for other vector functions.} 
$$
F(x)\equiv \{F(x_1),\ldots ,F(x_p)\} \equiv (u_1,\ldots,u_p)\equiv u\ .
$$ 
Further suppose $0\le q\le 1$ is given and  $\q(x)$ is the vector of $q$--quantiles
$$
F\{\q(x)\}=q1=\q(u)\ ,
$$
where $1$ is a vector of $p$ ones. 
Define the stress vector with respect to $x_j$ as\footnote{In \cite{adrian2011covar}  $\Delta CoVar_q\equiv q_{y|x=q_x}-q_y$.  Variable $y$  is generally the ``financial system" and hence considered is the change in the \v\ of the system when institution $x$ stressed, with stress  interpreted as $x=q_x$.  On page 10 of their paper they incorrectly state ``... $CoVaR$ conditions on the event that [an] institution is at its VaR level, which occurs with probability $q$."} 
\be{stress}
\frac{\de\q(x)}{\de x_j} \equiv \q(x|u_j>q) - \q(x)\ ,
\ee
where $\q(x|u_j>q)$ is the vector of $q$--quantiles of $x$ given $u_j>q$.    Then if $\q(x)$  is linear in $q$ 
 then
\be{implicit}
\frac{\de\q(x_i)}{\de\q(x_j)} \equiv \frac{\de\q(x_i)/\de x_j}{\de\q(x_j)/\de x_j} =  
\frac{f_j}{f_i} 
 \frac{q_{ij}}{q(1-q)}\cq q_{ij}=C_{ij}(q+q_{ij},q) - q^2\ ,
\ee
where $f_i$ and $f_j$ are the densities of $x_i$ and $x_j$ evaluated at $\q(x_i)$ and $\q(x_j)$ and  $C_{ij}$ is the copula of $(u_i,u_j)$.   
Further if 
$$
s_{ij}\equiv \frac{q_{ij}}{q(1-q)}\ ,
$$ then  $-1\le s_{ij}\le 1$ with $s_{ij}=\pm 1$ if $x_i$ and $x_j$ are comonotonic and counter monotonic, respectively.  If $x_i$ and $x_j$ are independent then  $s_{ij}=0$. If $u_i$ and $u_j$ are exchangeable  then  $s_{ji}=s_{ij}$.

\subsection{Proof}

By definition
$$
\frac{\de\q(u_i)}{\de u_j} \equiv \q(u_i|u_j>q) -q \equiv q_{ij}\ ,
$$
where  $q_{ij}$ is such that
\be{Qdef}
q =  \frac{\P(u_i\le  q+q_{ij},u_j>q)}{1-q}  = \frac{ q+q_{ij}-C_{ij}(q+q_{ij},q)}{1-q}\ ,
\ee
Rearranging yields the second equation in \eref{implicit}.
Now
 \be{first}
 \frac{\de\q(x_i)}{\de x_j}\equiv \q_{q+q_{ij}}(x_i) - \q(x_i) \approx \q'(x_i)q_{ij}= \frac{q_{ij}}{f_i} \ ,
 \ee
where $'$ denotes differentiation with respect to $q$ and the subscript on $\q$ indicates the revised $q$ for the quantile calculation.  The approximation follows from a first order Taylor expansion and is exact if the quantile is linear in $q$.   Similarly
 \be{second}
 \frac{\de\q(x_j)}{\de x_j}\equiv  \q_{q+q(1-q)}(x_j) - \q(x_j)\approx \frac{q(1-q)}{f_j}\ .
 \ee
 Dividing \eref{first} by \eref{second} yields the first equation in  \eref{implicit} and completes the proof.

\subsection{Discussion}  The critical  result is that sensitivities factor into contributions from the ratios of the marginal densities and quantities calculated from the pairwise copulas.  The via  the implicit  equation for $q_{ij}$ in \eref{implicit}, solved using a  root finding algorithm.
  The quantities $q_{ij}$ are implicitly defined from the pairwise copulas. In summary the ``sensitivity" matrix 
$$
S \equiv \frac{\de Q(x)}{\de Q'(x)}\ ,
$$
where $'$ denotes transposition has ones on the diagonal quantities between $\pm 1$ off the diagonal.   The matrix $S$ is called the sensitivity matrix and displays the sensitivity of the $q$--quantile of  each component of $x$ to  stress in the same or other components.

Since $f_i$ and $f_j$ are  the densities evaluated at $\q(x_i)$ and $\q(x_j)$  it follows that the ratio $f_i/f_j$ can be replaced by the ratio of the hazards.   This is  useful in cases were it is practical to model the hazard rather than the density.

\subsection{Implementation}

\fref{fig1} displays the empirical copulas calculated from four weekly closing stock prices labelled anz, cba, mcq and  wbc for $n=761$ weeks from 2000 April 12 through to 2014 October 29.  The empirical copulas are calculated by converting each observation to an empirical percentile and plotting the same against each of the other series percentiles.

\begin{figure}
  \begin{center}
    \includegraphics{fig1.pdf}
    \caption{Pairwise copulas of bank stocks  cba, anz, mqg, wbc, and the overall bank index.  Red lines plot sensitivity $s_{ij}$ as a function of $q$.}\label{fig1}
   \end{center}
\end{figure}

To estimate  $q_{ij}$  at a particular $q$, the second equation in \eref{implicit} is iterated\footnote{The second equation in \eref{implicit} is a contraction mapping and hence has a fixed point.} starting from $q_{ij}=0$ where copulas are estimated as 
$$
\hat C_{ij}(u_i,u_j) \equiv \hat\E\{(p_{ik}\le u_i)(p_{jk}\le u_j)\}\ .
$$
Here $\hat\E$ computes the empirical mean over the cases $k=1,\ldots,n$ and $p_{ik}$ and $p_{jk}$ are the empirical percentiles  of case $k$ of $x_i$ and $x_j$, respectively.

\subsection{Generalisations}
\renewcommand{\r}{\mathrm{R}}
Similar results apply when $\Q(x)$ is replaced by  other risk measures such as $\r(x)\equiv\E\{xr(u)\}$ where $r$ is a given function which acts componentwise and $xr(u)$ denotes componentwise multiplication.  For example if $r(u)=mu^{m-1}$ then  $\r(x)=\E\{\max(x^1,\ldots,x^m)\}$ where  $x^1,\ldots,x^m$ are $m$ independent copies of $x$ and the risk measure is the expected worst outcome in $m$ independent trials.

With $\r(x)$, the analogue of \eref{stress} is 
\be{stress2}
\frac{\de\r(x)}{\de x_j} \equiv \r(x|u_j>r_j) - \r(x_j)\cq r_j\equiv\p\{x_j\le\r(x_j)\} \ .
\ee
This differs from \eref{stress}  in that a different risk measure is used and  $r_j$ replaces $q$.   If  the components of $\r(x)$ are linear in the $r_i$ then
\be{implicit2}
\frac{\de\r(x_i)}{\de\r(x_j)} =  
\frac{f_j}{f_i} 
 \frac{q_{ij}}{q(1-q)}\cq q_{ij}=C_{ij}(r_i+q_{ij},r_j) - r_ir_j\ ,
\ee
where $f_i$ and $f_j$ are the $x_i$ and $x_j$ densities at the $r_i$ and $r_i$ quantiles, respectively.

\section{Systemic risk}
\cite{brownlees2015} describe a model for systemic risk (SRISK) estimated for each financial firm $i$ and each time point $t$.    SRISK of a firm at time $t$ is the expected capital shortfall  it will experience in the period $(t,t+h)$ given a crisis downtown in the market over the same period.    Capital shortfall is defined as the ratio of equity to equity plus debt falling below a certain level $k$.  A crises market is a market return below $c$.

If expected capital shortfall  is zero then SRISK is zero.   The sum of  SRISK's  across all firms is the total SRISK in the economy and each firm contributes either zero or some proportion to the total SRISK in the economy.    Firms with a high  percentage SRISK (denoted SRISK\%) are systemically important and will be  of major concern to regulators.

\subsection{Debt and Equity}

Suppose a firm at time $t$ has debt $D_t$ and equity $W_t$.   Then at $t$, $D_t+W_t$ is the total claim on the firm. 
Regulated firms are generally required to hold a proportion $k$ of total claims $k(D_t+W_t)$ as a prudential margin.    If  $k(D_t+W_t)>W_t$ then, prudentially speaking, the firm has capital shortfall   
$$S_t\equiv k(D_t+W_t)-W_t\ .
$$  
Negative capital shortfall indicates positive working capital.

Concerned with predicting capital shortfall $S_{t+h}$ conditional on a systemic event defined as a market decline below a threshold $c$ over the time horizon $(t,t+h)$.  This is similar to \cite{acharya2012wp}.

\subsection{Returns, leverage and capital shortfall}

Consider a single firm with return $r_t$.   This is the percentage change in value over the period  $(t-1,t)$ known as period $t$.   The arithmetic return over the period $(t,t+h)$ is $\nu_t\equiv r_{t+1}+r_{t+2}+\cdots+r_{t+h}$ and is an $h$ period return.  If $h=1$ then  $\nu_t=r_{t+1}$.

The equity of a firm at time $t+h$ is 
$$
w_{t+h} = (1+\nu_{t})w_t\cq \nu_t\equiv r_{t+1}+\cdots+r_{t+h}\ ,
$$

If the debt of the firm $d_t$  stays constant over the period $(t,t+h)$:   $d_t=d_{t+1}=\cdots=d_{t+h}$  and the capital shortfall i 
\be{cs}
c_{t+h}\equiv  k(d_{t+h}+w_{t+h})-w_{t+h} = k d_{t} - (1-k)(1+\nu_{t})w_t
\ee
 Note  $c_{t+h}$ is a linear in $\nu_t$.

\subsection{Systemic events and systemic risk of a firm}
A systemic event or ``crisis"   occurs in the period $(t,t+h)$ if the market  return $r_{mt}(h)\le c$.   The systemic risk (SRISK)  of  a firm is the expectation of the capital shortfall given  a crisis:
\be{sr}
\mathrm{SRISK}_t\equiv  \E_t\{S_{t+h}|r_{mt}(h)\le c\}  =  [k\ell_t-(1-k)\E_t^c\{r_{t}(h)\}-1]W_t\ .
\ee
where
$$
\mathrm{LRMES}_t \equiv \E^c\{r_{t}(h)\}\equiv \E_t\{r_t(h)|r_{mt}(h)<c\}\ ,
$$
and in terms of this notation:
$$ 
 \mathrm{SRISK}_t = \{k\mathrm{LVG}_t - (1-k)\mathrm{LRMES}_t - 1\}W_t\ .
$$
The condition $D_{t+h}=D_t$ or less strongly $\E_t^c(D_{t+h})=D_t$ indicates the value of debt  does not change if there is a crisis.

Evaluating the systemic risk in a firm requires the evaluation or estimation of the ``crisis" expectation, also called  the long run marginal expected shortfall (LRMES):

$\mathrm{SRISK}_t$ is a point estimate of capital shortfall in a crisis.   Since $S_t$ is linear in $r_t$ the crisis distribution of $S_t$ is known if the conditional distribution of $r_t(h)|r_{mt}(h)<c$ is known.

\subsection{Vector generalisation}

Aggregate systemic risk is 
$$
\mathrm{SRISK}_t = \sum_i \mathrm{SRISK}^+_{it}
$$
where $^+$ indicates the positive part of.   
   The proportion of systemic risk in firm $i$ is then
$$
\mathrm{SRISK\%}_{it} = \frac{\mathrm{SRISK}_{it}^+}{\mathrm{SRISK}_{t}}
$$

\subsection{Example from vlab}
See \fref{vlab} taken on 15 April 2015 from the website http://vlab.stern.nyu.edu

\begin{figure}[htbp]
\caption{default}\label{vlab}
\begin{center}
%\includegraphics[width=15cm]{vlab.pdf}
\end{center}
\end{figure}

\subsection{Discussion points}

\begin{enumerate}
\item  Above is similar to ``stress tests" regularly applied to financial firms.   However above uses only publicly available information
\item  Above approach is forward looking -- ie distribution of future assets conditional on a systemic event.  Markets look at things forwardly so incorporating forward information.
\item  Should have an appropriate $h$ and $c$ -- not too small etc.
\item  Capital shortfall is natural to use since this generates reduced lending activiity etc.
\item Measuring distress a firm is going to suffer conditional on a systemic event affecting the entire system.   Note this is different from capital shortfall conditional on firm default as with credit models.
\item Not concerned with the probability of joint distress of a large proportion of firms in the financial system.   Here systemic risk is determined by the capital shortfall generated distressed institutions conditional on a systemic event.  Framework takes into account joint dependence among firms, as well as their size and degree of leverage.   Do a small number of large financial institutions pose systemic threats to the entire system?  Tail correlations might fail to do so.
\item  Simplifying assumptions are made to deliver a measure that can be easily computed in practice.    Asset structure is captured in a limited sense.   
\item   Measurement approach can be applied to non financial firms.   However these firms are not highly levereged and are not as vulnerable as financial firms.    Not clear how capital shortfall transmits to rest of economy.

\end{enumerate}

\subsection{Static econometric model for systemic risk}

An econometric models  links one period returns $r_{it}$  to the  market return $r_{mt}$ enabling  the calculation of 
LRMES and SRISK.   The approach is to assume $(r_{it},r_{mt})$ are zero mean bivariate normal with volatilities $\sigma_{it}$ and $\sigma_{mt}$ and correlation $\rho_t$.  In this case
$$
\E(r_{it}|r_{mt}<c) = \frac{\rho_t\sigma_{it}}{\sigma_{mt}}\E(r_{mt}|r_{mt}<c)  = \rho_t\sigma_{it}\psi\left(\frac{c}{\sigma_{mt}}\right)\cq \psi(x)\equiv\frac{\phi(x)}{\Psi(x)}\ .
$$
Noting $r_{it}(h)=r_{i,t+1}+\cdots+r_{i,t+h}$ and similarly for $r_{mt}(h)$ then 
$$
\E\{r_{it}(h)|r_{mt}(h)<c\}  = \sqrt{h}\rho_t\sigma_{it}\ \psi\left\{\frac{\ln(1+c)}{\sigma_{mt}\sqrt h}\right\}\ .
$$
{\it Let us emphasize that the [last] formula ... has an error which is due to the fact that we are approximating MES using compound returns rather than arithmetic returns.    In particular [the] formula ... has a negative approximation error  and provides more extreme negative LRMES values.}

\subsection{Modelling systemic risk using a dynamic model}

\cite{brownlees2015} use  data on 95 large US financial firms for the period 2000-2012:   daily equity returns and market capitalization from CRSP; quarterly book values for equity and debt from Compustat.   A   Dynamic Conditional Correlation (DCC) model is estimated for  firm and market returns.  Write
\newcommand{\veps}{\varepsilon}
$$
\cov (r_t|t) = V_tR_tV_t'\cq R_t\equiv \cov(\veps_t|t)\cq \veps_t=V_t^{-1}r_t\ ,
$$
where $R_t$ and  $V_t$  are the correlation and diagonal volatility matrix, respectively, at time $t$.   Volatilities in $V_t$  are estimated using univariate threshold GARCH models.  The estimate of $R_t$ corresponds to the correlations in covariance matrix $C_t$ assuming
$$
(C_t - C) = \alpha (C_{t-1}-C)+\beta (\veps_t\veps'_t-C) \cq C\equiv\cov(\veps_t)\ .
$$
where $C$ is the long run covariance matrix.

\cite{brownlees2015} find the above systemic risk measure  a)  successfully identifies systemically risky firms during the GFC;
b)  predicts capital injections by Fed Reserve; and c) aggregate systemic risk provides early warning of declines in industrial production and higher unemployment.

Thus the model  estimates the beta of a firm equity on a broad market index.
A bivariate volatility model is estimated for the return on the broad market and the equity return of each firm. This model allows volatilities and correlations to evolve.    The estimated process is used to simulate the probability of severely negative outcomes over an extended period. Assuming that firms can only operate if capital is a non--trivial proportion of their total liabilities, SRISK is defined as the capital that would be needed to achieve a market cap that is 8\% of the book value of assets in the event of a crisis. The input to SRISK is size, leverage and risk. Each is important and a firm that wants to reduce its SRISK, can operate on any of these characteristics. A crisis is taken to be a 40\% drop in global equity values over six months. SRISK is computed weekly for firms from about 70 countries and published on the internet at http://vlab.stern.nyu.edu.  In extending this analysis to international markets, the model is naturally generalized to a multivariate volatility model. The data are considered to be the equity return on one firm, the equity return on a global index of equity returns, and perhaps some lags. The use of daily data for assets that are priced in different time zones means that closing prices are not measured at the same time and consequently there may be some important effect from lagged factor returns.

\subsection{Systemic risk based on probabilities}

If $d_t$ and $w_t$ are the debt and equity of a firm at time $t$ then the capital shortfall at time $t$ is 
$$
(1-k) d_t  - k w_t
$$
Basel II assumes $1-k=0.08$ implying there is  positive  capital shortfall if 
$
 0.08 d_t>0.92 w_t
$
or  leverage $d_t/w_t>11.5$ or the log--leverage is greater than $\ln(11.5)=2.44$.

Given the debt and equity, the capital shortfall at time $t$ is zero if 
$$
\frac{k_t}{1-k_t} = \frac{d_t}{w_t}\cq k_t= \frac{d_t/w_t}{1+d_t/w_t} = \frac{d_t}{d_t+w_t}
$$
where $0\le k_t\le 1$  is thought of as a risk index and $k_t/(1-k_t)$ is the leverage or risk odds.

Now consider the situation at time  $t+h$ where $h>0$, 
$$
 k_{t+h}\equiv\frac{d_{t+h}}{d_{t+h}+w_{t+h}} =  \frac{d_t}{d_t+\e^{\nu_{t+h}}w_t}
$$ 
where it is assumed $d_{t+h}=d_t$ and $\nu_{t+h}$ is the $h$ period return over $(t,t+h)$.  The   logit risk/log leverage is
$$
\ell_{t+h}\equiv\ln \frac{k_{t+h}}{1-k_{t+h}} = \ln \frac{d_{t+h}}{w_{t+h}} = \ln d_t - \ln w_t - \nu_{t+h} = \ell_t -\nu_{t+h} \ .
$$
Hence a large positive return $\nu_{t+h}$ implies a lower  risk.  As the logit risk/log leverage  increases to 2.44 the firm approaches the Basel II threshold.

If there are a number of  firms $i$ then $\ell_t$ and $\nu_{t+h}$ are  vectors with components $\ell_{it}$ and $\nu_{it}$, respectively, and in vector terms, $\ell_{t+h}=\ell_t - \nu_{t+h}$.   The aggregate risk is $1'\ell_{t+h}$.

\subsection{Systemic risk}

Systemic risk is defined as the log--leverage in the system as a whole:   that is  aggregate all debt and equity and compute, as above, the log--leverage $\ell_t^+$.    Then
$$
\ell^+_{t+h} = \ln \frac{d^+_t}{w^+_t}-\nu^+_{t+h} =  \ln \sum_i\alpha_{it}\frac{ d_{it}}{ w_{it}} -\nu^+_{t+h}= \ln \Ex_w(\e^{\ell_{it}})-\nu^+_{t+h} \cq \alpha_{it}\equiv\frac{w_{it}}{ w^+_t}\ .
$$
where $\nu_{t+h}^+$ is the aggregate return
$$
\ln \frac{1'w_{t+h}}{1'w_t} = \ln\Ex_w(\nu_{it})
$$
Differentiating with respect to $\ell_{i,t+h}$ yields
$$
\frac{\de \ell^+_{t+h}}{\de \ell_{i,t+h}} = \frac{\alpha_{it}\e^{\ell_{it}}}{\sum_i\alpha_{it}\e^{\ell_{it}}} \frac{\de\nu_{i,t+h}}{\de \ell_{i,t+h}}=\frac{w_{it}\e^{\ell_{it}}}{\sum_iw_{it}\e^{\ell_{it}}}
=\frac{d_{it}}{\sum_id_{it}}=\frac{d_{it}}{d_t^+}\ ,
$$
implying the percentage change in overall forecast leverage respect to a percentage change of the forecast leverage of  firm $i$ is proportional to the proportion of debt in firm $i$.   Further 
$$
\ell^+_{t+h} = \ln \Ex_w(\e^{\ell_{it}})-\nu^+_{t+h} \approx \Ex_d(\ell_{it})-\Ex_d(\nu_{i,t+h})\
$$
Thus the contribution of firm $i$ to the systemic risk is

\subsection{Comparing default probabilities}

Suppose $\ell_{it}$ and $\ell_{t}$ are the risk for firm $i$ and the combination of firms.   Then the excess risk in firm $i$ is
$$
\ell_{it}-\ell_t = \ln \frac{d_{it}}{d_t} - \ln \frac{w_{it}}{w_t} + (\nu_t-\nu_{it})\ .
$$
Thus if firm $i$ has the the same leverage as the average leverage then the excess risk is the underperformance over the time interval $(t,t+h)$.

Note

and hence can define
$$
x
$$

\subsection{Systemic risk}

The total leverage in the system is

a value weighted average of the individual leverages.   The $k_t$ for  capital shortfall for the system as a whole can be
produced from this total leverage.   The logit $\ell_t$ of $k_t$ then yields a risk index for the system as a whole.  Note
$$
\ell_t \equiv \ln \frac{d_{t+h}}{w_{t+h}}=-\nu_t+\ln \sum_i\alpha_{it}\frac{ d_{it}}{ w_{it}}\ne \sum_i \ell_{it}
$$

Can look at
$$
\ell_{it}-\ell_t  = \ln d_{it}-\ln d_t - (\ln w_{it}-\ln w_t) - (\nu_{it}-\nu_t)
$$

Suppose there are a number of firms and define
$$
d_t=\sum_i d_{it}\cq w_t=\sum_i w_{it} \cq  \frac{\ell_{it}}{\ell_t}
$$

The log--odds can be related to other variables.  In many cases the capital injection required is negative indicating capital can be withdrawn from the company without it breaching prudential standards.

\subsection{GARCH-DDC simulation}

We can consider the distribution of the projected log--leverage (pll) conditional on other variables including the market return
$$
\E(\ell_t|\nu_{mt}\le c)  = \ln d_t -\ln w_t -\E(\nu_t|\nu_{mt}\le c)\ .
$$
Alternatively we can consider the  $\alpha$--percentiles of $\ell_t$ denoted $\ell^\alpha_t$ such that
$
\alpha=\P(\ell_t\le \ell_t^\alpha)
$.  Note
$$
\ell_t^\alpha = \ln d_t -\ln w_t -\nu_t^\alpha = \ln \frac{d_t}{w_t}-\nu_t^\alpha\  .
$$

The GARCH-DCC setup delivers forecast or simulated values of $r^s_{t}(h)$, $s=1,\ldots, S$  for each  $t$.      Assume the simulated values are ordered in terms of increasing market returns $r^s_{mt}(h)$ and arranged in an $2\times S$ matrix $C_t$ where  the bottom row is the simulated market return.

This computation is complicated by two things:
\begin{enumerate}
\item  Dividends my be paid  in the period $(t, t+h)$ serving to reduce equity.  Typically at most one dividend  is payable which can be accumulated to  $t+h$ and used to increase equity.   That is for purposes of  assessing model accuracy $w_{t+h}$ is increased by proportion $1+f_{t'}(1+r_{t'})^{t+h-t'}$ where $t\le t'<t+h$ is  ex--dividend date and $f_t$ is the dividend yield.
\item  Debt may change over the period.
\end{enumerate}

In terms of $C_t$ the SRISK measure of \cite{brownlees2015} is the average, along each row of the prefixes.  For example,  the average in row $i$ of the  first $s$ entries is the systemic risk of firm $i$ at time $t$ conditional on  $r_{mt}(h)\le F_{mt}^{-}(s/S)$ where  $F_{mt}$ is the empirical distribution of the  $r^s_{mt}(h)$, $s=1,\ldots,S$.

A default or breach of prudential margins occurs if $c_{it}^s>0$.  The probability of a default if $r_{mt}(h)\le F_{mt}^{-}(v)$ is estimated as 
$$
\hat p_{it}=\frac{\sum_{s=1}^{[vS]}I(c^s_{it}>0)}{[vS]}\ ,
$$
where $v$ is given, for example $v=0.1$.
Joint probabilities of default are estimated similarly: the joint probability of a subset $B$ of firms  breaching their margins is 
estimated as
$$
\hat p_{Bt} = \frac{\sum_{s=1}^{[vS]}\prod_{i\in B} I(c^s_{it}>0)}{[vS]}\ .
$$
These probabilities generally decline with $v$: that is as the market downturn becomes less extreme.

Instead of asking what is the probability of a default (ie breach of prudential regulation) it is meaningful to consider what would $k$ have to be in order for it to be in default at time $t+h$.    Writing this value as
$$
k_t d_t - (1-k_t)\{1+r_t(h)\}w_t = 0 \qquad \implies \qquad k_t=\frac{1}{1+d_t/[\{1+r_t(h)\}w_t]}
$$
This equation can be computed given $r_t(h)$ and hence for every simulated value to arrive at $k_t^s$.    If $d_t\equiv0$ then $k_t=1$ indicating  a healthy state of affairs.  If $d_t/w_t$ is large then $k_t\approx 0$.    Hence as $k_t$ drops there is more danger.

Furthermore
$$
\ln k_t = -\ln \left[1+\{1+r_t(h)\}^{-1}\frac{d_t}{w_t}\right]\approx -\{1+r_t(h)\}^{-1}\frac{d_t}{w_t}\approx -\e^{-r_t(h)}\frac{d_t}{w_t}
$$
$$
\kappa_t \equiv \ln(-\ln k_t) \approx  \ln (d_t) - \ln (w_t) - r_t(h)
$$
A large value for $\kappa_t$ indicates

To study the time series and cross sectional behaviour of $\hat p_{it}$, it is useful to define the  normal scores 
$$
z_{it} \equiv \Phi^-(\hat p_{it})\cq i=1,\ldots, n\cq t=1,\ldots, T\ .
$$
Defining  $z_t\equiv (z_{1t},\ldots,z_{nt})'$ then a firm is systemically important if it is highly collinear with the other scores.

An entropy based measure of systemic risk is
$$
H_t = -\E(\ln p_{Bt})\equiv -\sum_B p_{Bt}\ln p_{Bt}\ .
$$

Systemically important firms are those which, when in default, are highly likely to be associated with a joint default.
joint probability of matrix is then 
$$
  P_t\equiv \frac{1}{S} I_tI_t'\cq  I_t = I(\rho^s_{it}>0)
$$

 can define the probability of a firm going in default as
$$
\hat p_{it}\equiv \frac{\sum_{s=1}^SI(\rho_{it}^s>0)}{S}
$$ 
In terms of this notation the probability of all firms going bankrupt and non

\subsection{Time--varying copula model}

Suppose $\delta\ge 1$ and the rotated Gumbel copula modelling lower tail dependence:
$$
C_\delta(u,v) = u+v-1+\e^{-[\{-\ln(1-u)\}^{\delta}+\{-\ln(1-v)\}^{\delta}]^{1/\delta}}
$$
Further suppose a sequence
$$
\delta_{t+1} = 1+\left(\omega + \alpha \frac{\sum_{s=0}^{m-1}|u_{t-s}-v_{t-s}|}{m}+ \beta\delta_t\right)^2\ .
$$
Note $\delta_t$ is always greater than 1.  \cite{patton2006modelling} has more details.   The model is fitted by estimating marginal models first and then by maximizing the copula likelihood using the fitted uniform marginals.

\subsection{Data  used in \cite{brownlees2015} }

\begin{itemize}
\item Large US financial firms (ie capitalization greater than 5bln US)
\item Jan 3, 2000 through to Dec 31, 2012:  not all companies continuously traded
\item Daily returns and market capitalization from CRSP
\item Quaterly book value of equity and debt from COMPUSTAT.
\item SIC codes used to segment firms into 4 industry groups (Depositries (29), Broker Dealers (10), Insurance (34) and Others (22))
\end{itemize}

SRISK is computed with the parameters $k=0.08$, $c=-0.1$, $h=22$ (a month).  SRISK computed at end of each month using all available data at that data, therefore no look ahead bias.

LRMES computed with the GARCH-DCC model for each firm.   Uses all available data starting from Jan 3, 2000 to end of each month.

\subsection{Older stuff}

$$
\E^c(r_{it}) \equiv \E(r_{it}|u_{mt}\le c^*)\cq c^*=\E\{(r_{mt}\le c)\}\ ,
$$
where $u_{mt}$ is the percentile of $r_{mt}$.
Given a joint distribution for $(r_{it},r_{mt})$ the distribution is simulated and
\be{sim}
\E^c(r_{it}) \approx \frac{\hat \E\{(r_{mt}\leq c)r_{it}\}}{\hat \E\{(r_{mt}\leq c)\}}= \frac{\hat\E\{(u_{mt}\leq c^*)F^-_{it}(u_{it})\}}{c^*}\ ,
\ee
where the $r$ values in the middle expressions denote simulated values and $\hat\E$, averages over the simulated values.   The $u_{it}$ and $u_{mt}$ are the percentiles of $r_{it}$ and $r_{mt}$, respectively.

The right hand expression in \eref{sim}  suggests using a copula to model the joint distributions $(r_{it},r_{mt})$.  Simulate $(u_{it},u_{mt})$, from the copula, discarding pairs with $u_{mt}>c^*$.   For each accepted $(u_{it},u_{mt})$  determine the actual return using the respective marginal distributions.   Issues to be addressed are:
\bi
\i Are the marginal distributions time invariant?  Could have situation where the marginal distribution evolves over time and/or is state dependent
\i Is the copula time invariant?   Could have situation where the copula is state dependent.    
\ei

The first step here is to examine the marginal distributions of the returns and the empirical copula of returns.

{\bf Comment.}  With the DCC model both volatilities and correlations have a time dependent structure.  These are modelled separately.
An alternative approach is where ...

{\bf \cite{engle2014dynamic}} describes a new approach to estimating time varying regression coefficients.   The approach is called Dynamic Conditional Beta (DCB).   Consider $(y_t,x_t)$ where  $y_t$  and $x_t$ are vectors.  Interested in $\E_t(y_t|x_t)$.   This is expression  may be linear in $x_t$ and depending on the past information set.  Write
\newcommand{\F}{{\cal F}}
$$
(y_t,x_t)|\F_{t-1} \sim N(\mu_t,H_t) \implies y_t|x_t,\F_{t-1}\sim N\{\mu_{yt}+B_t(x_t-\mu_{xt}), C_{yy,t}\}
$$
where
$$
B_t= H_{yx,t}H^-_{xx,t}\cq  C_{yy,t}= H_{yy,t}-B_tH_{xx,t}B'_t\ .
$$
These expressions depend on the time varying covariance matrix $H_t$.    For implementation we need a model for $\mu_t$ and $H_t$.

\section{TARCH modelling}

The standard approach to the joint modelling of returns is where volatility adjusted returns are modelled, for each security, as
\newcommand{\vareps}{\varepsilon}
\be{mean.model}
r_{t}=\mu+\sigma_t\eps_t\cq \eps_t\sim (0,1)\cq  \eps^-_t\equiv(\eps_t<0)=(r_t<\mu)\ ,
\ee
%frac{r_{it} - \mu_i}{\sigma_{it}} = \rho_{it}\eps_{mt} + \sqrt{1-\rho_{it}^2}\vareps_{it}
Further
\be{vol}
\sigma_{t+1}^2 = \omega+ (\alpha+\gamma\eps^-_t) (r_t-\mu)^2 + \beta\sigma^2_t=\omega+ \sigma^2_t\{(\alpha+\gamma \eps^-_t)\eps_{t}^2 + \beta\}\\ .
\ee
Hence the response in the variance to $\eps_t^2$  is increased by $\gamma$   if $\eps_{t}<0$ compared to the response if $\eps_t>0$.  This is a simple threshold GARCH model:  called TARCH.

The simple TARCH model \eref{mean.model} and \eref{vol} is generalised by replacing $r_t-\mu$ by a time series model possibly including explanatory variables.   Further $\omega$ can be replaced by $x_t'\delta$ where $x_t$ is a vector of explanatory variables, while extra lags can be introduced on the right hand side of \eref{vol}.

 Taking expectations of both sides of \eref{vol} yields
 $$
\sigma_{t+1}^2 = \omega+ \left\{\alpha+\beta+\gamma \E(\eps^-_t\eps_{t}^2)\right\}\sigma_t^2\ .
 $$
For a long run stationary solution 
$$
\sigma^2 = \frac{\omega }{1-\alpha-\beta-\gamma\E(\eps^-_t\eps_t^2)}\cq \E(\eps^-_t\eps_t^2)=p\E(\eps_t^2|\eps_t<0)+(1-p)\E(\eps_t^2|\eps_t\ge 0)\\ .
$$
where $p\equiv\E(\eps_t^-)$.  For the symmetric case, $p=1/2$ and  $\E(\eps_t^2|\eps_t<0)=1$ implying $\E(\eps^-_t\eps_t^2)=1$ and
$
\omega=(1-\alpha-\beta-\gamma)\sigma^2
$.  With the zeta transform  $\sigma^2=1$ and hence the sum of the coefficients is 1.

Alternatively
$$
\E(\eps^-_t\eps_t^2) = p +\rho\sqrt{p(1-p)} = p\left(1+\rho\sqrt{\frac{1-p}{p}}\right)\ ,
$$
where $\rho$ is the correlation between $\eps_t^-$ and $\eps_t^2$.   For a symmetric distribution this reduces to $(1+\rho)/2$.

The above setup holds for each security $i$ including the market, assumed to have index $i=m$.   The correlation between securities can also be modelled.   This is achieved by modelling the correlation of each security with the market, denoted $\rho_{it}$ or assuming the correlation matrix of the stack of the $\eps_t$, denoted $\eps_t$  are generated from a positive definite matrix $Q_t$ say where \citep{engle2002dynamic}
$$
Q_{t+1} = (1-\alpha-\beta) S + \alpha \eps_t\eps_t' + \beta Q_t\ ,
$$
where $\eps_t$ is the vector of $\eps_{it}$, including that of the market.

 \section{TARCH modelling applied to zeta scores}

 In this case $\omega_i\approx 0$, $\alpha_i$ and $\beta_i$ is generally positive and significant, while $\gamma_i$ is positive and marginally significant.  This suggests in these cases
 $$
 \zeta_{it}=\sigma_{it}\eps_{it}\cq \sigma_{i,t+1}^2= \{\alpha_i + \gamma_i(\zeta_{it}<0)\}\zeta_{it}^2+\beta_i\sigma^2_{it} 
 $$
 Thus negative $\zeta_{it}$ tend to increase volatility while positive $\zeta_{it}$ have no effect on volatility.  The persistence is 
 $$
1+\alpha_i+\frac{\gamma_i}{2}+\beta_i
 $$
 assuming $\E\{(\zeta_i<0)\}=1/2$.

\section{Lee--Carter modelling of financial variables}

Suppose $r_t$ is a vector of rate of returns with mean vector $\mu$.   Further suppose the returns are standardised so that over time each has mean zero and standard deviation 1.  Then write
$$
\frac{r_{it}-m_i}{s_i}=\beta_i\kappa_t+ \psi_i\eps_{it}\cq \kappa_t= \mu+\sigma_t\eps_t\cq  \eps_t,\eps_{it}\sim N(0,1)\ ,
$$
where $\kappa_t$ is normalised so that $\kappa_1=\overline r_1$ and $\kappa_n=\overline r_n$ and
$$
\sigma^2_{t+1} = \alpha_0+\alpha_1(\kappa_{t}-\mu)^2+ \beta_0 \sigma_t^2\ .
$$
Under the model the variance at time $t$ of the standardised $r_{it}$ is 
$\beta_i^2 \sigma^2_t + \psi^2_i$ while the covariance between $r_{it}$ and $r_{jt}$ is  $\beta_i\sigma^2_t\beta_j$.
Hence the squared correlation between $r_{it}$ and $r_{jt}$ is
$$
\frac{(\beta_i\sigma^2_t\beta_j)^2}{(\beta_i^2 \sigma^2_t + \psi^2_i)(\beta_j^2 \sigma^2_t + \psi^2_j)} = \left\{\left(1+\frac{\psi^2_i}{\beta_i^2\sigma_t^2}\right)\left(1+\frac{\psi^2_j}{\beta_i^2\sigma_t^2}\right)\right\}^{-1}
$$
As $\sigma_t$ becomes large the correlation approaches 1.

\section{Understanding of model}
\bi
\i  The observed distribution of $r_{mt}$ outcomes is a reasonable reflection of the (unconditional) marginal distribution at each $t$.
\i  Hence the $u_{mt}\equiv \P(r_{mt})$ are reasonable uniforms on the basis of the unconditional marginals
\i  In the standard analysis we use a model describing the conditional distribution at each $t$
\i  To what extent is $u_{mt}$ the conditional uniform i.e. uniforms calculated from the conditional distribution?  Do we need these.  Note that $r_{mt}$ can be viewed unconditionally or conditionally.   i.e. the across time distribution of the $r_{mt}$ will be close the unconditional whereas $r_{mt}$ itself is chosen conditionally if we employ a time series model.     
\i  So it appears the computed $u_{mt}$ can be regarded as unconditional.  (just like $r_{mt}$).    However they can also regarded as generated conditionally.  Ditto for $\zeta_{mt}$ etc.
\i  So suppose we have estimate $\sigma_{mt}$ using a garch model based on either the $r_{mt}$, $\logit \P(r_{mt})$ or $\zeta_{mt}$.   For the latter this is the conditional variance of $\zeta_{mt}$ i.e.
$$
\zeta_{mt}|t-1 \sim N(0,\sigma^2_{mt})
$$
\i So at each future $t$ (forecast or smoothed), given $\sigma_{mt}$  we draw $r_{mt}$ or $\zeta_{mt}$, compute $\P(r_{mt})$ or $\Phi(\zeta_{mt})$.  The former is with respect to the whole distributions whereas the latter is with respect to the normal.
\ei

\section{ARCH specification}
   A GARCH(1,1) model stated in terms of noise $\eps_t\sim(0,1)$ and time varying volatility $\sigma_t$:
$$
r_t= \mu + \sigma_t\eps_t\cq \sigma^2_{t+1} = \alpha_0+\alpha_1(r_{t}-\mu)^2+ \beta_0 \sigma_t^2\cq \eps_t\sim N(0,1)\ .
$$
Here $\mu$ is the average return, assumed independent of time.

Instead of using  actual returns we can consider the zeta transform $\zeta_t=(\Phi^-\circ \P)(r_t-\mu)$
with 
\begin{equation}\label{garch}
\zeta_t=  \sigma_t\eps_t\cq (\sigma^2_{t+1}-1) = \alpha (\sigma^2_{t}-1) + \beta(\zeta_t^2-1)\cq \eps_t\sim N(0,1)\ .
\end{equation}
The second equation can be written as
$$
\sigma^2_{t+1} = (1-\alpha-\beta) +  \alpha \sigma^2_{t} + \beta \zeta_t^2\ .
$$

Given the fit, \eref{garch} is simulated forward from $t=n$ to yield $\zeta_{n+1},\zeta_{n+2},\ldots$ and in turn
$$
\hat r_{t}=\mu+(\P^-\circ \Phi)(\zeta_{t})\cq t=n+1,n+2,\ldots\ .
$$
The inverse $\P^-$ is  with respect to the empirical distribution, or some modified version of the same  (a stressed version?)

Now take the $u_{mt} = \Phi(\zeta_t)$ and the copulas $C(u_{it},u_{mt})$.   The copula can be the empirical copula or some smoothed version of the same.   Then 
$$
\hat r_{it} = \mu_i + \P^-(u_{it})\cq u_{it}\sim C(u_{it}|u_{mt}) \cq t=n+1,n+2,\ldots\ .
$$
Again, $\P^-$ is with respect to the past distribution of returns $r_{it}$ or some modified version of the same.  With the PG model the $\zeta_{it}$ are chosen given $\zeta_t$ and hence the relation becomes
$$
\hat r_{it} = \mu_i + (\P^-\circ\Phi)(\zeta_{it})\cq \zeta_{it}\sim \mathrm{PG}(\zeta_{it}|\zeta_{mt}) \cq t=n+1,n+2,\ldots\ .
$$
If returns are jointly normal this model reduces to the usual normal modelling.

In terms of this setup:
\bi
\i Future market returns are generated in terms of an ARCH model stated in terms of the zeta transform
\i Relationships (i.e. systemic risk) inherent in other returns are stated in terms of a PG copula
\i Stressing is achieved in terms of stressing $\P_m$.
\ei

suggesting that in an unconstrained fit the coefficients should add to 1.
$$
r_{mt}=(F_m^-\circ\Phi)(\sigma_t\eps_t)
$$
Since $\E(z_t^2)=1$ and $\alpha<1$, then in the long run $\sigma^2_t\rightarrow 1$.   If $z_t$ is in either tail and hence $z_t^2$ is far from  1 then $\sigma^2_{t+1}$ is much bigger than 1 and $z_{t+1}$ will be in the tail.   Then
\be{forward}
r_{it}=F_i^-(u_{it})\cq u_{it}\sim C\{u_{it}|\Phi(z_t)\}
\ee
Thus volatility clustering occurs since $z_t$ in one or tail, drives, via the copula, both $r_{it}$ and $r_{jt}$ into the tail.

Steps in fitting:
\begin{enumerate}
\i  An ARCH model is fit to the market return $z_t=(\Phi^-\circ F_m)(r_{mt})$ where $F_m$ is the empirical distribution of the market rates
\i  The $z_t$ is simulated forward from time $t=n$ using the ARCH model. 
\i  Retain only those forward simulations such that the cumulative drop $\prod_{t=n+1}^N\{1+(F_m^-\circ \Phi)(z_t)\}$ is less than the crisis drop.
\i  For each forward simulated value, chose $r_{it}$ using the conditional copula and simulation smoothing
\i Calculate the capital shortfall for firm $i$.
\end{enumerate}

The rationale is that  $(y_{t}-\mu)^2$ is the latest available estimate of the variance at time $t$ and this latest   estimate is combined with the  ``permanent" component $\sigma^2_{t}$.   Constraints  are required on $a_0$, $a_1$ and $b_1$ to ensure $\sigma_t$ stays positive and finite.  If  $a_1=b_1=0$ then $y_t$ is noise with mean $\mu$.

In our case $y_t=z_t$ is standard normal so we can drop $\mu$ to get
$$
z_t=  \sigma_t\eps_t\cq \sigma^2_{t+1} = a_0+a_1 \sigma^2_{t} + b_1z_t^2\ .
$$

Fitting GARCH models with R.  The  command $garch(y,c(1,1))$ fits  model $garch$ to $y$.  The $garch$ command requires $library(tseries)$.

The quantity $a_0/(1-a_1-b_1)$ is the long run average $\sigma^2_t$ since it is the constant solution to the right hand side equation \eref{garch}, if  $(y_t-\mu)^2$ is replaced by its expectation.    We want the long run average to be 1 implying
$
a_0=1-a_1-b_1
$ and hence
$$
z_t=  \sigma_t\eps_t\cq \sigma^2_{t+1} = a_0+a_1 \sigma^2_{t} + (1-a_0-a_1)z_t^2\ .
$$
$$
z_t=  \sigma_t\eps_t\cq (\sigma^2_{t+1}-1) = a_1 (\sigma^2_{t}-1) + (1-a_0-a_1)(z_t^2-1)\ .
$$

 \fref{fig7} displays output from fitting a GARCH model to the daily percentage returns of the FTSE index plotted in \fref{fig6}.   In this fit  $\mu$ is set to the sample mean return, $\hat a_1=0.045$ indicates moderate autocorrelation in the standard deviation while $\hat b_1= 0.942$ indicates high reaction to the latest volatility $(y_t-\mu)^2$.  The long run average standard deviation is $\sqrt{0.009/(1-0.045-0.942)}=0.825$, marginally above the empirical standard deviation of 0.796.   The  standard errors of the coefficients are 0.003, 0.007 and 0.010, respectively for $a_0$, $a_1$ and $b_1$.  These are available using the $vcov(r)$ where $r$ contains the results of the $garch$ command.  Hence all three coefficients are significant.

GARCH stands for generalized ARCH where the latter stands for autoregressive conditional heteroskedasticity.    GARCH(1,1) indicates one lag in both the $\sigma_t^2$ and $(y_t-\mu)^2$ terms.   The GARCH($p,q$) model extends this to $p$ and $q$ lags.   The  ARCH($q$) model contains only lags in $(y_{t}-\mu_t)^2$  and hence is GARCH($0,q$).

Estimating GARCH models is similar to ARMA models.   For any set of $a$ and $b$ parameters as well as starting conditions,  $y_0$ and $\sigma_0$,   the GARCH equation for $\sigma_t^2$  is used to recursively calculate $(y_t-\hat y_{t})/\sigma_t$.  These standardised errors, as well as related information,  are combined to evaluate the normal based likelihood.   The likelihood is maximised  with respect to the unknown parameters using a numerical search.

Forecasting future volatility with  a GARCH model consists of iterating the $\sigma_t^2$ equation \eref{garch} forward from the latest available time point $t=n$.    In this iteration, future $(y_t-\mu_t)^2$ are replaced by their latest conditional expectation.

\section{Partially Gaussian copulas}

Suppose $(u,v)=F_*(x,y)$  where $x$ and $y$ are scalar random variables.    Suppose $0<u_1<\cdots<u_n<1$  are   ordered observed values of $u$ and $q_j=\Phi^-(u_j)$, $t=1,\ldots,n$.  The correspondingly ordered values of $v$ and $z=\Phi^-(v)$ are denoted $v_j$ and $z_j$.  Note $\Ex(z_j)=\Ex(q_j)=0$ and $\Ex(z^2_j)=\Ex(q^2_j)=1$ where $\Ex$  is the empirical mean.

Smoothing methods are here proposed to smooth and simulate $y$ values  using a copula on $(u,v)$ constructed via    a cubic spline model linking $u$ to $z$.   Of particular concern are simulated $z$ when $u$ is  near $0$ or $1$ corresponding to  $x$ extremes.    Given a simulated $u$ and in turn $z$, $(x,y)=F^-_*\{u,\Phi(z)\}$, a draw from the joint.  Constraining $u$ draws to say the upper tail, yields corresponding upper tail values for $y$.   The challenge is to produce cogent $z$'s or $y$'s that properly reflect dependence in different parts of the distribution unencumbered by inappropriate constraints, and in particular tail constraints, inherent in say the Gaussian copula setup.    Practical methods admit fitting on the basis of observed data, and testing procedures for  departures or otherwise from Gaussianity.   The method outlined below achieves this.

\begin{comment}
   The simulation singles out independent and dependent variables.   Which should be which?  If $x$ and $y$ are actual time series the simulation $(x_j,\hat y_j)$ is ordered back into the original time series order.
\end{comment}

The partially Gaussian  (PG) copula for $(u,v)$ is stated in terms of  $q\equiv\Phi^-(u)$ and $z\equiv\Phi^-(v)$ on the grid   $u_j=j/(n+1)$, $j=1,\ldots,n$ with 
\be{cusp}
z_j = \alpha_j+\beta q_j+ sh_j\eps_j\cq \alpha_{j+1}=\alpha_j +\delta_j+c\eta_j\cq \delta_{t+1}=\delta_j+\eta_j\ .
\ee
Here $\eps_j$ and $\eta_j$ are serially and contemporaneously uncorrelated zero mean disturbances with common variance $\sigma^2$ and $c=3-\sqrt 3$. The  $q_j$ term is the   Gaussian component and  $\alpha_j$ a nonparametric deviation.

The parameter $s$ controls overall smoothness while  $h_j\ge 0$,  controlling the variability at different $t$ determines local smoothness.
In particular if $s=0$ then the signal $\alpha_j+\beta q_j$ is forced to reproduce every  $z_j$ while $h_j=0$ implies reproduction at the particular $t$.     If $h_j$ is large then little notice is taken of $z_j$ and the fitted signal at $t$ is relatively smooth.  Thus $s$ controls overall smoothness of the signal and  $h_j$ the smoothness at a particular $t$.  Comparability between models and fits is facilitated by normalising $h_j>0$ such that the average  is 1.

The Gaussian copula is where $\alpha_j$ and $h_j$ are  identically 0 and  1, respectively, implying  $(z_j,q_j)$ with $t$ uniform on $1,\ldots,n$  is bivariate normal  with correlation $\beta=\pm\sqrt{1-(s\sigma)^2}\equiv\rho$.

The starting condition for the recursion in \eref{cusp} are the second two equations with $t=0$ and where $\alpha_0$ and $\delta_0$ are  unknown parameters, similar to $\beta$. If $s\rightarrow\infty$ then $\sigma\rightarrow 0$,  $(\alpha_j,\delta_j)\rightarrow 0$ for $t=0,\ldots n$, and \eref{cusp} describes a Gaussian copula.

The function $\alpha_j$ is thought of as an intercept function and provides for a nonparametric extension to the Gaussian copula.  If $\sigma\rightarrow 0$, equivalent to $s\rightarrow\infty$,  the first equation in \eref{cusp} is
$
z_j = \alpha_0+\delta_0 t + \beta q_j + s\eps_j
$
and  $\beta=\rho$ if $\alpha_0=\delta_0=0$.    Model \eref{cusp} with  $\beta=0$ is the  nonparametric model since $z_j$ is varies smoothly with $t$, unrelated to $q_j$.  If $\beta=0$ and $\sigma\rightarrow 0$ there is a probit relationship between $z_j$ and $u_j$.  Finally $s=0$ implies $\alpha_j+\beta q_j=z_j$ for any $\beta$.   The full range of possibilities is set out in \tref{pg} discussed in more detail below.

The $\alpha_j=0$ and $\alpha_j=\alpha_0+\delta_0 t$ specifications are generalised by supposing $\alpha_j$ is twice differentiable and minimising
\be{spline}
 \sum_{t=1}^n\left(\frac{z_j-\alpha_j-\beta q_j}{h_j}\right)^2 + s^2\int_{-\infty}^{\infty} \left(\alpha_j''\right)^2\de t\ .
\ee
with respect to $\alpha_j$ and $\beta$.
 In \eref{spline} the $h_j$  are fitting weights: a large  $h_j$ implies  error at $t$ is largely ignored while a small $h_j$ implies  error at $t$ is  minimized at all cost.  The function $a_j$ and scalar $b$ minimising \eref{spline} deliver a function $a_j+bq_j$ where $a_j$ is piecewise twice differentiable and $a_j+bq_j$ passes closest to, in a mean square error sense, to $z_j$  with a penalty $s^2$ for  roughness measured in terms of the second derivative.   At the minimum, the first term in \eref{spline} is $(s\sigma)^2$.   \cite{Brown&DeJong:2001} demonstrate the equivalence of \eref{cusp} and \eref{spline}.

The  function $\alpha_j$ minimising \eref{spline}  is, at integer $t$,  $a_j=\E(\alpha_j|z_1,\ldots,z_n)$  computed with \eref{cusp} where $\eps_j$ and $\eta_j$ are normal, 0 mean, variance $\sigma^2$ random variables and $q_j$ fixed.  Between integer $t$,  the  minimum is quadratic in $t$.  A useful feature is that $\beta$ is simultaneously estimated alongside $a_j$ as the generalised least squares estimate under \eref{cusp}.  All calculations under \eref{cusp} provide error covariance matrices as detailed and applied below.

\section{Special cases of the PG model}

Special cases of  \eref{cusp}  are displayed in \tref{pg}.   In \eref{cusp}, if $s\rightarrow\infty$ then $\sigma\rightarrow 0$   since the variance of $z_j$ is finite.    Thus $s\rightarrow\infty$  implies the noise to signal ratio becomes large where noise refers to   $s\eps_j$ and signal to $\eta_j$, the error term driving  the smooth component $\alpha_j$.   As the noise to signal ratio $s$ increases, less of the variation in $z_j$ is explained by $\alpha_j$.  In the limit $\sigma$ is zero implying $\alpha_j=\alpha_0+\delta_0 t$, as straight line.   The further restriction $\alpha_0=\delta_0=0$ forces $\alpha_j$ identically zero.

The first row in \tref{pg} is the  Gaussian copula.  In this setup $\alpha_j$ is identically zero: there is no  signal component.  The additional restriction $\beta=0$ eliminates the Gaussian component $q_j$.  Co (or counter) monotonicity results in the Gaussian framework if $\rho=\pm 1$ as displayed in the third row.
If $s= 0$ then there is no measurement noise and the combined signal $\alpha_j+\beta q_j$ must pass through the points $z_j$ resulting in a perfect fit.   In terms of \eref{spline}, $s=0$ implies there is no roughness penalty and hence the minimisation is solely focussed on minimising the first, squared error, term, achieved  by setting $\alpha_j+\beta q_j=z_j$.

 \begin{table}[htdp]
\caption{Special cases of the PG copula; in all cases $\rho\equiv\pm\sqrt{1-(s\sigma)^2}$}\label{pg}
\begin{center}
\begin{tabular}{l|c|ccccc|l}
\hline
case& $\alpha_j$ & $\beta$ &$s$ & $\sigma$ & $\alpha_0$&$\delta_0$  & other\\
\hline
Gaussian & 0 &  & $\infty$ & $0$&  0&0 &$\rho=\beta$\\
independence &  0 & 0 & $\infty$&0 & 0 &0 &$\rho=0$\\
$\pm$comonotonic  & 0 &$\pm 1$ &0 & 0 &0 & 0 &$z_j=\pm q_j$  \\
empirical  & $z_j$ &  & $0$  &  &   &  &$\rho=1$ \\ 
linear probit &$\alpha_0(1-2u_j)$&  0 &  $\infty$ &0& & $\frac{-2\alpha_0}{n+1}$ &indep. if $\alpha_0=0$\\
nonparametric & $\E(z_j|u_j)$  & 0 & & & &  & non Gaussian \\
PG & $\E(z_j-\beta q_j|u_j)$ & & & & & &  \\
\hline
\end{tabular}
\end{center}
\end{table}%

The linear probit row in \tref{pg}  eliminates the Gaussian component $q_j$ by setting $\beta=0$, and giving maximum penalty for rougness.   The resulting prediction  is a straight line $\hat z_j=\alpha_0+\delta_0 t$.  However the mean of the $z_j$ and hence $\hat z_j$ is zero implying $0=\alpha_0 + \delta_0(n+1)/2$.   Solving for $\delta_0$ gives the $\delta_0$ constraint displayed in \tref{pg} and the resulting straight line signal $\alpha_j$.

The bottom row of \tref{pg} displays the general partial Gaussian specification absent  any constraints on the parameters.  Eliminating the Gaussian component from the signal by setting $\beta=0$ leads to the nonparametric, non Gaussian specification in the second last row of \tref{pg}.

\section{Assessing goodness of fit}

A plot of $a_j+b q_j$ versus $r q_j$ is useful for assessing Gaussianity -- that is whether the copula  is Gaussian.   If $a_j+bq_j\approx rq_j$ then the quantiles predicted under the G and PG models are approximately the same and  a 45 degree line plot suggests a Gaussian copula is adequate.     This analog of the qq--plot is converted to the pp--plot analog  by transforming each coordinate using $\Phi$.   Using the inverse marginal distribution of each of the variables displays the copula fit information in the original scale.

For the Gaussian copula the single parameter is $0\le\rho\le 1$, estimated by  $r$.   The analogous estimate for the PG copula is $R=\pm\sqrt{1-(s\hat\sigma)^2}$ signed according to $b$.   A measure of the  contribution of the nonparametric component $\alpha_j$  to the PG fit is  
$
R^2-r^2 = 1-r^2 - (s\hat\sigma)^2
$.
A more formal analysis is based on the log--likelihood where in $\eref{cusp}$ the disturbance terms $\eps_j$ and $\eta_j$ are assumed normally distributed.    Then  minus twice the log--likelihood\footnote{This is the log--likelihood $z_j\sim N(\rho q_j,1-\rho^2)$ and differs from the bivariate Gaussian log--likelihood.  It appears  as  $s\rightarrow\infty$, $s\hat\sigma\rightarrow\sqrt{ 1-b^2}$ and so the G copula appears enforced.}  of the Gaussian and  PG model  are computed and their difference compared to a chi--squared distribution with 2 degrees of freedom for significance.

Local  measures of departure from Gaussianity are 
\be{lr}
\frac{z_j-r q_j}{h_j\sqrt{1-r^2}}\cq \frac{z_j-a_j-bq_j}{ s\hat\sigma h_j}\ .
\ee
The  standardised residuals
provide insight into areas of lack of fit, with mean and standard deviation, across $t$,  of 0 and 1, respectively.

\section{Tuning PG to particular parts of the joint distribution}
The function $h_j$ is used to assign  importance to parts of the joint of distribution.  If all parts are equally important then $h_j=1$ for all $t$.   If $h_j\approx 0$ when $t\approx n$ then fidelity  is enforced in the upper tail.  Alternatively if $h_j\approx 0$ for $t\approx n/2$ then there is an attempt to accurately reproduce $z_j$ in the middle of the distribution with smoothness  in both tails.
\section{Overall and local correlation}

\cite{bjerve1993correlation} state ``The local regression slope, which focuses on change in expected $y$ as $x$ changes, may be of greater interest than expected  $y$ for a given $x$." They go on to argue for  a  ``scale--free standardised version of the local regression slope."\footnote{The scale free feature conflicts with the calculations below where  slope differs according to whether it is with respect to $t$ compared to $q_j$.  Hence the noise terms must also be affected by the transformation in a way not apparent in the expressions below.} In terms of the current notation, their suggested measure is 
\be{rhot}
 \rho_t\equiv\pm\left\{1+\left(\frac{\psi_t}{s\sigma h_t}\right)^{-2}\right\}^{-\frac{1}{2}}\ ,
\ee
where $s$, $\sigma$ and $h_t$ are as in \eref{cusp} or \eref{spline} and $\psi_t$ is the regression slope at $t$ as set out below.  The ratio $\psi_t/(s\sigma h_t)$ is a signal to noise ratio and a high value implies $\rho_t\approx \pm 1$.    In general the signal  $\psi_t$ is the local slope of the relationship while $s\sigma h_t$ is a measure of local noise.   The sign of $\rho_t$ is discussed in the context of particular choices of signal $\psi_t$.

With the Gaussian copula 
$$
z_t=\beta q_t + (\sqrt{1-\rho^2})\varepsilon_t\cq \eps_t\sim N(0,1)\ .
$$
In this  case the nonparametric component $\alpha_t$ is absent.  The slope with respect to $q_t$ is constant $\psi_t=\beta=\rho$ as is the noise variance: $s\sigma h_t=\sqrt{1-\rho^2}$.  Further  \eref{rhot} reduces to $\rho_t=\rho$ for all $t$.  The Gaussian copula case is displayed in the first row of the of \tref{corr}.

\begin{table}[htdp]
\caption{Overall and local correlations.  In all cases $R=\sqrt{1-\Ex\{(z_t-\hat z_t)^2\}}$}\label{corr}
\begin{center}
\begin{tabular}{l|ccc|l}
\hline
case & $\psi_t$ & $q_t$ & $\alpha_t$ & estimates\\
\hline\hline
Gaussian & & & \\
-- overall,  local &$\rho=\beta$ &$\checkmark$& $\times$ & $r=\Ex(z_tq_t)$ \\
\hline
nonparametric & & & \\
-- overall &$\rho$ &$\times$ & $\checkmark$& $r$ from $\widehat{\mathrm{PG}}(\beta=0)$\\
-- local  &$n\phi(q_t)\delta_t$ &$\times$ & $\checkmark$& $\hat\delta_t$ from $\widehat{\mathrm{PG}}(\beta=0)$\\
\hline
PG & & & \\
-- overall & $\rho$ & $\checkmark$& $\checkmark$& $r$ from $\widehat{\mathrm{PG}}$ \\
-- local & $n\phi(q_t)\delta_t+\beta$&$\checkmark$& $\checkmark$&$\hat\beta$, $\hat\delta_t$ from $\widehat{\mathrm{PG}}$  \\
\hline\hline
\end{tabular}
\end{center}
\end{table}%

The second set of row in \tref{corr} is the nonparametric Gaussian copula where, in \eref{cusp},  $\beta=0$.  Hence $q_t$ is removed and  the relationship between $z_t$ and $t$ or $u_t$ is  modelled in terms of the  nonparametric component $\alpha_t$.  The   slope $\alpha_{t+1}-\alpha_t$  at  $t$ is, apart from error,
$\delta_t$.   However $\delta_t$ is the slope with respect to $t$ and required is the slope with respect to $q_t$:
\be{normslope}
\psi_t=\frac{\de \alpha_t}{\de q_t} = \left( \frac{\de u}{\de t}\frac{\de q_t}{\de u}\right)^{-1}\frac{\de \alpha_t}{\de t}  \approx
\left\{\frac{1}{n\phi(q_t)}\right\}^{-1}\delta_t  = n\delta_t\phi(q_t)\ ,
\ee
where $\phi$ is the standard normal density.

The final set of rows in \tref{corr} deals with the general PG case.   As in the other situations, the overall correlation $\rho$ is derived from the overall fit.   The overall correlation exceeds that derived from both the specialised Gaussian and nonparametric cases.   The higher overall correlation is partialed out locally according to both nonparametric and parametric components.   In any PG fit $\hat\beta$ will differ from the Gaussian copula estimate $\Ex(z_tq_t)$.

If $s=0$ then $s\eps_t=0$  and  the signal to noise ratio is infinite implying $\rho_t=1$ for all $t$.  Thus the empirical and comonotonic cases imply, as expected,  $\rho_t=\pm 1$.   With the linear probit model $\sigma=0$ and $\alpha_t=\alpha_0(1-2u_t)$ with slope with respect to $u_t$ of $-2\alpha_0$ and
\be{normslope2}
\psi_t =  \left( \frac{\de q_t}{\de u_t}\right)^{-1}\frac{\de \alpha_t}{\de u_t}  =
 -2\alpha_0\phi(q_t)\cq  \rho_t\equiv\pm\left[1+\left\{\frac{2\alpha_0\phi(q_t)}{s\sigma h_t}\right\}^{-2}\right]^{-\frac{1}{2}}\ ,
\ee
If $h_t$ is constant then  local correlation is  highest if  $q_t=0$ and monotonically declines towards zero as $q_t$ moves away from zero.

The above $\psi_t$ and implied correlations are for the $(q,z)$ scale.  However the local correlations also apply on the $(u,v)$ scale since the transformation from $u$ to $q$ and $v$ to $z$ are the same inverse normal probability transform and slopes are identical\footnote{This also follows since local correlation is independent of scale.}
$$
\frac{\de v}{\de u} =\left(\frac{\de z}{\de v}\right)^{-1} \frac{\de z}{\de q} \frac{\de q}{\de u} = \frac{\de z}{\de q}\ .
$$ 
\section{Simulating from the PG copula}

To explain PG simulation, consider initially  the Gaussian model.   Given data $(q_t,z_t)$, $t=1,\ldots,n$ where
$q_t=\Phi(u_t)$ and $u_t=t/(n+1)$ suppose 
\be{rhohat}
\tilde z_i\sim N(r \tilde q_i,1-r^2)\cq r=\Ex(z_tq_t) = \E(\rho|  z)\cq \tilde q_i\sim N(0,1)\ ,
\ee
where $z\equiv(z_1,\ldots,z_n)$ contains the observed values of $z_t$.
Simulating $\tilde q_i$ multiple times produces multiple $\tilde z_i$ while $r$  remains fixed.   To ensure  coverage, $\tilde q_i=q_i$,  $i=1,\ldots, n$.   The  $n$ pairs $(u_i, \tilde v_i)$ where $\tilde v_i=\Phi(\tilde z_i)$, $i=1,\ldots,n$  provide $n$ independent draws with   uniform  empirical distribution for the $u_i$ and approximately uniform empirical distribution for the $\tilde v_i$.   Repeatedly cycling over $i=1,\ldots,n$  produces an unlimited supply of  draws.

The PG generalisation of \eref{rhohat} is to repeatedly cycle over  $i=1,\ldots,n$ with 
\be{rhohat2}
\tilde z_i\sim N(a_i+bq_i, s^2\hat\sigma^2)\ , \ \ \ \  a_i=\E(\alpha_i|  z)\ , \ \ \ \ b=\E(\beta|  z)\ .
\ee
The $a_i\equiv\E(\alpha_i|z)$ and $b\equiv\E(\beta|z)$ and estimate of $\sigma$ are calculated with the Kalman Filter Smoother (KFS)  \citep{DeJong:91a} while $s$ is set to achieve desired smoothness.  Alternatively $s$ is estimated as discussed in \sref{xx}.  In  \eref{rho2} the $a_i$, $q_i$  and $b$ remain fixed across cycles, analogous to fixing $r$  in the  Gaussian copula simulation.  If $a_i=0$ for all $i$ then \eref{rhohat2} reduces to \eref{rhohat} since in this case $b=r$ and $s^2\hat\sigma^2=1-r^2$.

Iterations \eref{rhohat} and \eref{rhohat2}  ignore  estimation variability in $r$ or $a_i$ and $b$.  This shortcoming is addressed by varying  $a_i$ and $b$  across  each cycle 
$$
\tilde a_i \sim N\{a_i,\cov(\alpha_i|  z)\}\cq i=1,\ldots,n\cq  \tilde b\sim N\{b,\cov(\beta|  z)\}\ ,
$$
and using these  in the first relation of \eref{rhohat2}  instead of $a_i$ and $b$.
The conditional covariance matrices are recursively calculated  with the KFS alongside $a$ and $b$, while consistent  draws  across $i$  are made with the 
simulation smoother extension  \citep{DeJong&Shephard:95}.

\section{Ordering}

Suppose $z_{xt}$ is the percentile based z--score of series $x$ at index $t$.   In this section two common indexes are discussed:   time $t$ and ordering with respect to some other variable.    A first order approximation is $z_{xt} = \beta_xq_t + \eps_{xt}$ or in vector form $z_t=\beta q_t + \eps_t$ where $z_t$, $b$ and $\eps_t$ are vectors and $q_t$ scalar.   For the Gaussian copula $\beta=\rho$.

\section{Factor PG copula model}

The PG  model is stated in terms of  $q_t=\Phi^-(u_t)$ where $u_t=t/(n+1)$, $t=1,\ldots,n$.   The  role of $x$  is to order $z$:  the variable $x$ is permuted  and $z$ is permuted using the same permutation.   This suggests using a composite variable for ordering.

For example suppose $x_t$ is a vector of variables initially ordered in terms of time $t$.   The associated percentile based z--scores  are   $z_t= (\Phi^{-1}\circ \P) x_t$ where $\P$ is the generic percentile operator.\footnote{A final adjustment is made to ensure the z--scores have mean zero and variance 1.}   Write $z_t=Uc_t$ where $(c_1,\ldots,c_n)=DV'$ derived from the singular decomposition $UDV'=(z_1,\ldots,z_n)$ arranged so that the singular values in the diagonal matrix $D$ are in decreasing order.   Use the first component in $c_t$, corresponding to the largest singular value,  to permute $x_1,\ldots,x_n$ and fit PG copulas
$$
x_t = \alpha_t + \beta q_t + sh_t\eps_t\ ,
$$
where $\alpha_t$ and $\beta$ are vectors and $h_t$ is a diagonal matrix.  The components of $\alpha_t$ are individual departures from the Gaussian component and $\beta\beta'$ models the joint Gaussian structure.

Suppose $y_t$ is a $p$--vector with components $y_{it}$, $i=1,\ldots,p$ with $y_t$ is observed for $t=1,\ldots n$.   Suppose each component series in $y_t$ is ordered according to $x_t$, a scalar series observed or inferred along with the $y_{it}$.   Without loss of generality assume $y_t$, $t=1,\ldots,n$ denotes the component series after ordering with respect to $x_t$ and define $v_t$ and $z_t$ from the componentwise ordered $y_t$ as, for $t=1,\ldots,n$, 
$$
z_t = \Phi^-_*(v_t)\cq v_t = F_*(y_t)\cq q_t=\Phi^-(u_t)\cq u_t=\frac{t}{n+1}\ .
$$
Using this notation the factor PG model is as in \eref{cusp} except that $z_t$, $\alpha_t$, $\beta$ and $\eps_t$ are vector and $h_t$ is a diagonal matrix. The diagonal matrix $h_t$ distributes the quantum of error $\sigma$  across component series $i$ and percentiles $t$.   The matrix $h_t$ is standardised such that $1'h_t1=p$.    Further $\alpha_t$ is formed as in the second and third equations in \eref{cusp} expect that both $\alpha_t$ and $\delta_t$ are vector.    More specific structure is: 
\begin{itemize}
\item   If all components of $\alpha_t$ are identical then  $\alpha_t$ is written as $1\alpha_t$ where in the last expression $\alpha_t$ is scalar.  In this formulation deviations from Gaussianity are the same for each series.  This is testable in the current framework.
\item If all components of $\beta$ are the same then  $\beta$ is written as $1\beta$ where $\beta$ is scalar.   In this case all components in $z_t$ respond in the same way to the Gaussian component $q_t$ but deviations may occur.  
\item A generalisation is where $z_t=B_t\alpha_t + Q_t\beta + sh_t\eps_t$.

\end{itemize}

Replacing $1\alpha_t$ in \eref{cusp} by a vector  $\alpha_t$ and making $s\sigma$ component specific  yields the PG model.  Variants include forcing  a common response to $q_t$ by requiring  $\beta$ to be scalar.

The one--factor PG model is estimated in the same way as the PG model, using vector $z_t$.   In practice $x_t$, the scalar variable serving to order the components of $y_t$, is either an external driver or a composition from $y_t$.   At present $q_t$ is structured in terms of the normal score derived from the percentile of $x_t$.   More extreme tail behavior is modelled by  for example replacing the normal score $q_t$ by say $\chi_t$ the chi--squared score derived from the percentile.   This is explained in detail in the next section.

\section{Extreme tail copulas}

\section{Below here is review/junk}

\subsection{A  model for monitoring slope}
Suppose
\be{slope}
y_t = \beta m_t + \mu_t + s\eps_t\cq \mu_{t+1} = \mu_{t-h+1} + hr_t + c\eta_t \cq r_{t+1}=r_t + \eta_t\ ,
\ee
where $y_t$ is a stock price,  $m_t$ is a market index, $\mu_t$ is the price level and $r_t$ is the return per period and $h$ is a positive  integer.   Note $r_t$ measures  the expected  per period change in the level $\mu_t$.   Thus

\subsection{Kelly criterion}

Suppose $r$ is a vector of stock returns with mean $\mu$ and covariance matrix $C$.    Suppose proportion $\pi_i$ of total wealth $w$  is invested in stock $i$.  Then the rate of return on the portfolio is 
$ \pi'r$.   The expected  log wealth after one period   is 
$$
\E[\ln \{w(1+\pi' r)\}] \approx \ln(w) + \pi'\E(r) -\frac{\pi'\E(rr')\pi}{2} =  \ln(w) + \pi'\mu -\frac{\pi'(C+\mu\mu')\pi}{2}\ .
$$ 
To maximise log wealth (and hence wealth), maximise this expression with respect to $\pi$.   Setting up the Lagrangian, differentiating and equating to zero yields 
$$
\pi = (C+\mu\mu' - \lambda I)^{-1}\mu\cq 1'\pi=1\ .
$$
Given the optimal $\pi$ the growth rate is 
$$
\E\ln(1+\pi'r) \approx \mu'(C+\mu\mu' - \lambda I)^{-1}\mu - \frac{\mu'(C+\mu\mu' - \lambda I)^{-1}}{2}
$$

The factor $1+\pi'r$ is the growth factor.   Over $n$ periods the growth factor is
$$
\e^{\ln(1+\pi'r_1)+\ln(1+\pi'r_2)+\cdots \ln(1+\pi'r_n)} \rightarrow \e^{n\E\ln(1+ \pi'r_t)} = \e^{nm}
$$
where $r_t\sim(\mu,C)$ are the vectors of growth rates for each period and $\pi$ is the fixed allocation.   Hence the rate of growth is
$$
m=\E\ln(1+\pi'r_t) 
$$

\subsection{Continuous formulation}
For a single stock we have $\de s/s = \mu\de t + \sigma\de b$ where $b$ is brownian motion.  Alternatively 
$\de s=\mu s\de t + \sigma s\de b$.    For a portfolio $\pi$ of stocks this becomes
$$
\frac{\pi'\de s}{\pi s} =\pi'\mu\de t + \pi'\de b
$$
$$
\pi=-C^{-1}(1r_f-\mu)
$$
Note $C^{-1}(r-\mu)$ is the standardised prediction error when predicting each component of $r$ using all the other components and supposing $r$ is realised.   Since $\mu>1r_f$,  outcomes $r=1r_f$ are downside surprises.
Thus  $\pi$ is the negative of the standardised prediction error when predicting each component of $r$ using all other components and assuming the downside surprise $r=1r_f$.   A high value $\pi_i$ occurs if  there is huge downside surprise if $r_i=r_f$   when all other components  downward surprise at  $r_f$.    Hence the Kelly criterion loads the portfolio with stocks $i$ which have  large downward surprise at $r_i=r_f$ if all other stocks downward surprise with outcomes $r_f$.

\subsection{Markowitz}

Suppose we wish to maximise the expected return $\pi'\mu$ subject to a constraint on the volatility, $\pi'C\pi\le c$.  Then the Lagrangian is 
$\pi'\mu +\lambda (c-\pi'C\pi)$.   Differentiating and equating to zero yields the first order conditions
$$
\mu = 2\lambda C\pi\qquad \Rightarrow\qquad \pi = \frac{1}{2\lambda} C^{-1}\mu 
$$
where $\lambda$ is chosen so that $\pi'C\pi=c$.

 If $C=c11'$ then

To maximise the expected growth rate requires $\pi$ to be chosen as above.  Can we write a SSM for this?
$$
1=1'\pi\cq s_t=1\mu + r_t + \eps_t 
$$

Multiplying the first equation by $1'$ yields
$$
\pi=n\le \cq\lambda=n1'\mu - n1'(C+\mu\mu')\pi\cq  
$$
$$
\mu = (C+\mu\mu')\pi\qquad\Rightarrow\qquad \pi=(C+\mu\mu')^{-1}\mu
$$
Maximising the expected log--accumulation yields the first order conditions
$
\E(r_t) = \E(r_tr_t')\pi
$ or $\pi=\{\E(r_tr_t')\}^{-1}\E(r_t)$.  If one the components of $r_t$ is constant (the risk free rate of return $\delta$ say), then (using partitioned inverses)
$$
\pi = \{\cov(r_t)\}^{-1}\{\E(r_t)-\delta 1)\ .
$$

\subsection{\cite{bjerve1993correlation} review}
\begin{enumerate}
\item  Points out $\cov(z|t=t^*)\ne 0$  while $\cov\{\E(z)|t=t^*\}=0$.  So cannot form a correlation from the variation at $t$ compared to the variation in the mean -- there is no variation in the latter.
\item  Conditioning $t$ on a neighbourhood of $t^*$ and calculating the correlation in neighbourhood will lead to low correlation even if relationship is strong.  Not sure I understand this.
\item  Distinguishes between $\cov\{\E(z|t)\}/\cov(z)$ as a measure of correlation and ordinary correlation.  The former he calls Pearson correlation while Gallton--Pearson is the usual correlation.
\item  States that to the first order  both correlations are such that
$$
\cor\{z,t|t\in N_h(t^*)\}=\frac{h\beta_{t^*}}{\sqrt 3\sigma_{t^*}}
$$
where $\beta_t$ is the local regression and $\sigma_t$ the local residual? variation.
\item Then considered is
$$
\xi_{t^*} = \lim_{h \rightarrow 0}\frac{\cor\{z,t|t\in N(t^*)\}}{h/\sqrt 3} = \frac{\beta_{t^*}}{\sigma_{t^*}}
$$
that is the local slope devided by the local standard deviation.  Note I  assume the overall correlation is 1 and so $\sigma_1$ does not appear in the numerator.
\item  Maps $\xi_{t^*}$ into the unit interval
$$
\rho_{t^*}= \pm\left(1+\xi^{-2}_{t^*}\right)^{-\frac{1}{2}}= \pm\left(1+\frac{\sigma^2_{t^*}}{\beta^2_{t^*}}\right)^{-\frac{1}{2}}\ ,
$$

\end{enumerate}

\section{Fitting PG copulas}
 The PG is readily  fit to percentile data, and provides a practical platform for copula simulation.  This is discussed, implemented, and used in subsequent sections.  The  parameters defining a PG copula are $s$, $\beta$,  $\sigma$ and starting conditions $\alpha_0$ and $\delta_0$.  Given $s$, the other parameters have  closed form expressions calculated with the Kalman filter.  A best estimate of $s$ is derived by iterating over $s$ so as to minimise  an appropriate objective function such as least squares.

To compute local correlation, write $\Delta z_t\equiv z_{t+1}-z_t$ and similarly for other quantities.    Assume $t$ is given and note that 
$$
\Delta z_t =\delta_t +c\eta_t + s(\eps_{t+1}-\eps_t)+\beta\Delta q_t  \cq \Delta q_t\approx \frac{q'_t}{n+1} = \frac{1}{(n+1)\phi(q_t)}
$$
Hence
$$
\E(\Delta z_t) \approx \E(\delta_t) + \frac{\E(u_t)}{\phi(q_t)} 
$$
  Then $q_t$ is a random variable and 
$$
\cov(\Delta z_t,\Delta q_t|t) = \beta^2\cov(\Delta q_t|t)\approx (\beta q'_t)^2\cov(u_t)= \frac{(\beta\sigma)^2\pi\e^{q_t^2}}{6} 
$$$$
\cov(\Delta z_t|t) = (1+c^2 + 2s^2)\sigma^2 + \beta^2\cov(\Delta q_t|t) 
$$
This final expression assumes $\cov(\delta_t)=(n+1)\sigma^2/2$:  a random $t$ is chosen to observe the random walk. 
Hence the local correlation is 
$$
\frac{\cov(\Delta z_t,\Delta q_t)}{\sqrt{\cov(\Delta z_t)\cov(\Delta q_t)}} = \left\{1+\frac{A}{\beta^2\cov(\Delta q_t)}\right\}^{-1/2}
$$

The local correlation between $z_t$ and $q_t$ is 
$$
\rho_t\equiv\cor(\Delta z_t,\Delta q_t|t) =  \frac{\beta\cov(\Delta q_t)}{\sqrt{\cov(\Delta z_t|t)\cov(\Delta q_t)}}=\pm\left\{\frac{\cov(\Delta z_t|t)}{\beta^2\cov(\Delta q_t)}\right\}^{-1/2} 
$$
where ``$|t$" indicates conditioning on information up to and including time $t$.   A calculation shows writing $c=4-\sqrt 3$,
$$
\cov(\Delta z_t|t)  = (2s^2+c)\sigma^2+\beta^2\cov(\Delta q_t)\cq \cov(\Delta q_t) \approx (q'_t)^2\cov(u_t)= \frac{\sigma^2\pi\e^{q_t^2}}{6}
\ .
$$
Hence
$$
\O(\rho_t) = \frac{\beta}{s_t\sigma }
\cq 
s_t = \sqrt{\frac{6(2s^2+c)}{\pi}}\e^{-q_t^2/2}\ .
$$
Divisor $s_t$ is small if $|q_t|$ is large indicating the model posits higher tail correlation than normal if $\beta\ne 0$.  The ratio
$$
\frac{\O(\rho_t)}{\O(\rho)} =\frac{s}{s_t}= \sqrt{\frac{\pi}{6(2+c/s^2)}}\ \e^{q_t^2/2}\rightarrow \frac{\sqrt{2\pi}\ \e^{q_t^2/2}}{\sqrt{24}}\ ,
$$
compares local  to overall correlation.  If $s\rightarrow\infty$ local correlation in the tails  will far exceed overall  correlation.  This is obvious given $s\rightarrow\infty$ implies the model will exactly reproduce the data.  If $s\rightarrow0$

\subsection{Alternative view of local correlation}
In \eref{cusp},  a large $|\beta|$ suggests more extreme tail behaviour than in the Gaussian copula.  To see this note  
 \be{change}
\Delta \E( \alpha_t + \beta q_t)  \approx \frac{-2\delta_0}{n+1} + \frac{\beta}{(n+1)\phi(q_t)}= \frac{\beta/\phi(q_t)-2\delta_0}{n+1}\ ,
 \ee
 where $\Delta$ denotes change with respect to $t$.
Change \eref{change} is relatively large if $q_t^2$ is large, that is $t$ is near 1 or $n$. Higher than normal tail dependence implies $|\beta|$ large.  For a Gaussian copula, $\beta=\pm\sqrt{1-(s\sigma)^2}$ and comparing the ratio of estimates of the two sides to 1 is a test for Gaussianity.

\subsection{Correlation between $z_t$ and $\alpha_t$}

 The term $\alpha_t+\beta q_t$ is the signal and $\eps_t$, noise.    The signal is relatively smooth and contains both a nonparametric and Gaussian component $q_t$.   Departures of $z_t$ from the Gaussian component  are the sum of a persistent component $\alpha_t$ and  transient component, $s\eps_t$.  Since  $\eps_t$ and  the driver of persistence $\eta_t$  share $\sigma$, the smoothing parameter $s$ measures relative importance of transience as opposed to persistence.   The scale parameter $\sigma$ relates to the degree of roughness since it is the variance of the changes in the  slope of $\alpha_t$.

  Since $\Ex(q_t)=\Ex(z_t)=\Ex(\eps_t)=\Ex(\eta_t)=0$ it follows  
 $$
0= \Ex(\alpha_t)=\alpha_0+\delta_0 \Ex(t) = \alpha_0+\delta_0 \Ex(t) = \alpha_0+\delta_0 \frac{n+1}{2}\qquad\Rightarrow\qquad \delta_0 = \frac{-2\alpha_0}{n+1}\ .
 $$ 
Further $\Vx(q_t)=\Vx(z_t)=1$ implies an analysis of variance type decomposition
\be{anova}
 1= \Vx(\alpha_t) + \beta^2 + (s\sigma)^2\ .
\ee
Decomposition \eref{anova} splits the total variance  of 1 into that due to the nonparametric component $\alpha_t$,  Gaussian component $\beta^2$ and residual noise, $(s\sigma)^2$.  Alternatively \eref{anova} states the variance of the nonparametric component is $1-\beta^2-(s\sigma)^2$.

An example PG copula with $s\sigma=xx$, $\sigma=0$, $\beta=xx$ and $\alpha_0=xx$  is displayed in \fref{xx}.  
 \begin{comment}
 relation is such that
$$
\delta_0=\frac{-2\alpha_0}{n+1}\cq z_t=  \alpha_0(1-2u_t)+\beta q_t + s\eps_t \ .
$$
Additionally $\Vx(q_t)=\Vx(z_t)=1$ implying
\be{constraint}
 1= \frac{\alpha_0^2}{3}-2\alpha_0\beta c+\beta^2+(s\sigma)^2\cq c\equiv\cov(u_t,q_t)\approx 2.82\ ,
\ee
and hence at most two of $\alpha_0$, $\beta$ and $s\sigma$ can be chosen freely. 
\end{comment}

\section{Correlations with the PG copula}
With \eref{cusp}  and $t$ uniform on $1,\ldots,n$ 
$$
\Vx\left(\begin{array}{c} z_t\\ \alpha_t\\ q_t\\ \end{array}\right)
=\left(\begin{array}{ccc} 
1 & 1-(s\sigma)^2 & \beta\\
1-(s\sigma)^2 & 1-\beta^2-(s\sigma)^2 & 0\\
\beta & 0 & 1\\
\end{array}\right)\ .
$$
This covariance matrix serves to define a variety of ordinary and partial correlations.

The correlation between $z_t$ and $q_t$ is  $\beta$.  The partial correlation between $z_t$ and  the Gaussian component $q_t$, after removing the effect of the nonparametric component $\alpha_t$,  is called the Gaussian correlation:
\be{rho}
\rho_q\equiv\frac{\cov(q_t,z_t-\alpha_t)}{\sqrt{\cov(q_t)\cov(z_t-\alpha_t)}} = \frac{\beta}{\sqrt{\beta^2+(s\sigma)^2}}=\pm\left\{1+\left(\frac{s\sigma}{\beta}\right)^2\right\}^{-1/2}\ ,
\ee
where the sign is that of $\beta$.  Hence $\rho_q=1$ or 0 if  $s\sigma=0$ or $\beta=0$, respectively.
Using \eref{anova},  $\rho_q^2$ equals the proportion of  residual variance $\Vx(z_t)-\Vx(\alpha_t)=\beta^2+(s\sigma)^2$ explained by  the Gaussian component $q_t$.

\begin{comment}
$$
= \cor(\alpha_t+s\eps_t,\alpha_t) =\frac{1-\beta^2-(s\sigma)^2}{\sqrt{(1-\beta^2-(s\sigma)^2)(1-\beta^2)}}= \left\{\frac{1-\beta^2-(s\sigma)^2}{1-\beta^2}\right\}^{1/2} 
$$
\end{comment}
and  $\rho_a$ is 1 or 0 according to whether  $s\sigma$ equals 0 or  $\sqrt{1-\beta^2}$, respectively. 
\begin{comment}
$$
\cov(z_t-\alpha_t) = \cov(\beta q_t+s\eps_t) = \beta^2 +s^2\sigma^2\ .
$$
\end{comment}
Finally the overall correlation is the correlation between $z_t$ and the signal, consisting of both nonparametric and Gaussian component:
$$
\rho\equiv\cor (z_t,\alpha_t+\beta q_t)=\cor(z_t,z_t-s\eps_t)=\frac{1-(s\sigma)^2}{\sqrt{\cov(z_t-s\eps_t)}}=\sqrt{1-(s\sigma)^2}\ .
$$
with $\rho=\rho_a$ if $\beta=0$.   If $s=0$, there is no measurement error in \eref{cusp} or, equivalently, there is no roughness penalty in \eref{spline} and $\rho_q=\rho_a=\rho=1$.

\begin{comment}
reducing to \eref{rho} except that $s$ is replaced by
$$
v\equiv \Ex\left(\sum_{j=1}^{t-1}w_j^2\right) = xxx \cq \alpha_t=\sum_{j=1}^{t-1} w_j\eta_{t-j}
$$
The derivation of $v=xxx$ is shown  appendix.  Equivalently $\rho_v^{2}$ is the proportion of $\Vx(z_t)$ explained by the nonparametric and Gaussian component.

From \eref{rho} 
\be{OR}
\left(\frac{v}{s}\right)^2=\frac{\rho_s^2/(1-\rho^2_s)}{\rho_v^2/(1-\rho_v^2)} \equiv \mathrm{OR} \ ,
\ee
the odds ratio of local to global correlation.  In general $v>s$ implying $\mathrm{OR}>xx$.

\end{comment}

\begin{comment} 
$$
\rho = \cor(z_t,q_t) =\frac{\beta}{\sqrt{\beta^2+\cov(\alpha_t)}}=\pm\left\{1+\left(\frac{v\sigma}{\beta}\right)^2\right\}^{-1/2}\ .
$$
The expressions follow from a detailed calculation
$$
\cov(z_t,q_t) = \E\{(\alpha_t+\beta q_t)q_t\} = \beta
\cq
\cov(z_t) =\cov(\alpha_t)+\beta^2\cq \cov(q_t)=1
$$
where .   A detailed calculation shows
\end{comment}

\section{Special cases of the PG copula}

\tref{pp} sets out possible choices for $s$ and $\beta$.   These combinations are discussed in the further subsections.  Note that $s=0$ does not imply $s\sigma=0$ as $s\rightarrow 0$ may imply $s\sigma$ converges to a positive number.

\subsection{Empirical copula}

The empirical copula results in \eref{cusp} when $s=0$.  In this case   $z_t=\alpha_t+\beta q_t$.    The deviation of $z_t-(\alpha_t+\beta q_t)$ can be made zero by selecting appropriate $\eta_t$.  Hence $s=0$ implies the fitted copula is the empirical copula.  Note $\Vx(\alpha_t)=1-\beta^2$ and since $\beta$ is arbitrary, the correlation between $z_t$ and the nonparametric component is 1.

\subsection{Large local variation}

The other  extreme  $s\rightarrow\infty$ is displayed  in the bottom rows of \tref{pp}.  Large $s$ forces negligible $\sigma$  and straight line behaviour for $\alpha_t$ yielding
$$
z_t= \alpha_0(1-2u_t) + \beta q_t + s\eps_t\ ,
$$
where $s\eps_t$ has finite variance $(s\sigma)^2$.

\subsection{Gaussian copula}
If $s\rightarrow\infty$ and  $\alpha_0=0$ then $(q_t,z_t)$ is bivariate   Gaussian with correlation $\beta$ and \eref{cusp} reduces to a Gaussian copula with correlation $\beta$ and $\rho=\rho_q$.  In this case $s\sigma=\sqrt{1-\beta^2}$.

\subsection{Probit copula}

 If $s\rightarrow\infty$ and  $\beta=0$ then \eref{cusp} defines a probit copula.   From \eref{constraint}, $\alpha_0=\pm\sqrt{ 3\{1-(s\sigma)^2\}}$.

 \subsubsection{Independence}
 If $s\rightarrow\infty$ and  $\alpha_0=\beta=0$ then the variables are independent.   The situation is achieved either letting $\beta\rightarrow 0$ with a Gaussian copula or letting $\alpha_0\rightarrow 0$ with a Probit copula.  Under independence $s\sigma=1$.

 \subsection{Conditionally Gaussian copula}

This is the intermediate situation where  $0<s<\infty$.  Testing $\alpha_0=1/s=0$ is a test for a Gaussian copula.   Goodness of fit is measured with 
\be{R2}
\hat\rho^2= 1-(s\hat\sigma)^2=1-\Ex\{(z_t-\hat z_t)^2\}\ ,
\ee
where  $\hat z_t$ is the estimate of $z_t$ based on \eref{cusp} using estimates of $\alpha_0$, $\beta$ and $s\sigma$.  
Values of $\hat\rho^2$ lie between 0 and 1 and have the usual interpretation:    near 1 indicates the percentiles of $u$ well explain $z$ values of $v$.   
Note $R\rightarrow\beta$  if $\alpha_0=0$ and $s\rightarrow \infty$.

\section{Estimation of the PG model}

A convenient feature of the GC model is the straightforward estimation.   The unknown parameters are $\alpha_0$, $\beta$, $\sigma$, and $s$.  Given $s$, estimates of the other parameters are in closed form -- generalised least squares (GLS) estimators of $\alpha_0$ and $\beta$, while $\sigma$ is estimated from the fitted  residuals.   GLS estimates are derived using the Kalman filter (KF).   The KF  and the associated Smoothing filter (SF) also deliver diagnostics for assessing goodness of fit and estimates of  sampling error.  In these calculations $s$ is either given or alternatively is iterated over to produce a quasi maximum likelihood estimate.

From \eref{R2}
$$
\Ex\left\{ \left(\frac{z_{t}-\hat z_{t}}{s\hat\sigma}\right)^2\right\}=1
$$
suggesting  the comparison of standardised residuals  to $\pm 2$ and perhaps plotting the percentile rank of the standardised residuals against $u_t$ to identify  lack of fit.

\begin{comment}
Note $R^2$ differs from the correlation coefficient $\beta$ since.
$$
\frac{R}{\beta}=\pm \sqrt{1-(s\hat\sigma)^2}\left\{1+\left(\frac{s\sigma}{\beta}\right)^2\right\}
$$
This emphasises the difference between $R^2$ and $\beta$.   The former measures the goodness of fit of a semiparametric function of $u$ to explain $z$ while $\beta$ measures the ability of a straight line in $q$ to explain $z$.  If $\beta\ne 0$ then $q$ forms part of the semiparametric specification and hence if $\beta\ne 0$,  $R^2>\beta^2$. 
\end{comment}

   The implied correlation between $z_t$ and $q_t$ is  
$$
\beta=\frac{\beta}{\sqrt{\beta^2+(s\sigma)^2}} = \pm\left\{1+\left(\frac{s\sigma}{\beta}\right)^2\right\}^{-1/2}\ .
$$
The term $\beta/(s\sigma)$ is the signal to noise ratio.  If $z_t, q_t\sim (0,1)$ then $\beta^2+(s\sigma)^2=1$ and  
$$
\beta=\pm\sqrt{1-(s\sigma)^2}=R=\beta \cq \frac{\beta}{s\sigma} = \frac{\pm\sqrt{1-(s\sigma)^2}}{s\sigma} = \frac{\beta}{\sqrt{1-\beta^2}} 
$$.

 Thus the empirical correlation between $z_t$ and $q_t$ is
$$
\sum_{t=1}^n z_tq_t = \beta+\delta_0\sum_{t=1}^n tq_t 
$$

By construction both $z_t$ and $q_t$ have mean zero and variance 1 implying
the correlation between $z_t$ and $q_t$ is

If  $\beta=0$ then 
$$
z_t=\alpha_0 + n\delta_0 u_t+\beta \Phi^-(u_t) +s\eps_t\ ,
$$
    Testing $\delta_0=0$ amounts to testing for independence.  If $\beta=\pm 1$ then 
$z_t-(\pm q_t)=\alpha_0+t\delta_0$ implying $\alpha_0=n\delta_0=0$ and  $z_t=\pm q_t$, that is the variables are co or counter monotonic.   Finally if $\beta\ne 0,\pm 1$ then $z_t=\alpha_0+t\delta_0+\beta q_t+s\eps_t$  since  $\alpha_0=\delta_0=0$, implied by the fact that    Since both $z_t$ and $q_t$ are, by construction, standard normal, this  amounts to prescribing  a Gaussian copula with correlation indicated in \tref{pp}.
The ratio $\beta/(s\sigma)$ is the  signal to noise ratio.

The middle column of the body of \tref{pp} displays alternatives for finite $s\ne 0$.   If $\beta=0$  the implied copula is nonparametric with $\alpha_t$ evolving smoothly as a function of $t$ with the actual degree of smoothness increasing with $s$.  A constraint is $\alpha_0=\alpha_n=\sum_t\delta_t=0$ and hence $\alpha_t$ forms a bridge.  If $\beta=\pm 1$ then the signed difference $z_t-(\pm q_t)$ is modelled as a smooth. In a fit, the  bridge structure is expected to be enforced by the data.

The scale  $\sigma$ quantifies roughness in the signal $\alpha_t$ but its size is determined by $s$ with $s\sigma\le 1$ implied by the standard normality of $z_t$.   
In fitting, $s$ is either chosen a--priori, or estimated together with the other parameters. Given $s$, estimates of  $\beta$, $\alpha_0$, $\delta_0$ and $\sigma$ are closed form generalised least squares calculations.    Thus $s$ can be estimated  using a one dimensional search.   Given the values of the parameters,  standard diagnostics are used to assess the fit and reveal areas of inadequate fit.  These techniques are used and explained in the applications.

Use of $q_t$ permits  a partially Gaussian explanation of the copula with  Gaussianity increasing with $s$.   In the limit the enforced Gaussian copula has correlation $R$ signed according to $\hat\beta$.  Co or  countermonotoniticity implies $R=\pm 1$ with the sign indicating the direction of the relationship.  Setting $\beta=0$  excludes the Gaussian copula  component.

\begin{table}[htdp]
\caption{Predicted $z_t$ with conormal copula model}\label{ppp}
\begin{center}
\begin{tabular}{c||c|c|c}
\hline
&$s=0$& $0<s<\infty$ &$s\rightarrow\infty$\\
\hline\hline
$\beta=0$&& $\alpha_t$&$\alpha_0(1-2u_t)$ \\
& & non parametric& linear probit\\
& & probit & independence: $\alpha_0=0$ \\
\cline{1-1}\cline{3-4}
$\beta\ne 0,\pm 1$  & $z_t$ & $\alpha_t+\beta q_t$ &$\alpha_0(1-2u_t)+\beta q_t$\\
&empirical & conormal & Gaussian if $\alpha_0=0$\\
\cline{1-1}\cline{3-4}
$\beta=\pm 1$& & $\alpha_t\pm q_t$& $\alpha_0(1-2u_t)\pm q_t$ \\
& & cointegrated & co/counter monotonic \\
& & departure & if $\alpha_0=0$ \\
\hline
\end{tabular}
\end{center}
\end{table}%

The fitted values $\hat z_t$ stacked in  vector $\hat z$  provide a basis for simulating all percentiles including extreme percentiles.   In particular suppose $z\sim N(\hat z, \Sigma)$ where $\Sigma$ is the covariance matrix implied by the model.   Then $v\sim\Phi_*(z)$ is a simulation of the the $v_t$.   Bringing $v$ into the original order yields $(u_t,v_t)$, a simulation from the copula.  Simulated percentiles are  mapped back into the original scale as   $F_*^-(u_t,v_t)$ to provide simulated $(x_t,y_t)$ outcomes.

\section{Copula forcing}

Even if data suggests a strict Gaussian copula it  may be desirable to force stronger dependence, especially in the tails. This forcing is achieved with

\section{Application to copula fitting}

The following example illustrates the copula fitting technique.

\section{Financial sensitivity and contagion}

Suppose the singular value decomposition of the  matrix $S$ of sensitivities at a particular $q$ is 
$S= UDV'$.  Here  $D$ a diagonal matrix of singular values, arranged in decreasing order along the diagonal and $U$ and $V$ are orthonormal:  $U'U=V'V=I$.  If the series are independent then $U=D=V=I$.   If the series are comonotonic then $U=V=(1,0)$ while $D=\diag(1,0,\ldots,0)$.  Hence in the comonotonic case $S=11'$.

So the best thing is to compare 
$$
Q= s_{i1}c_{j1} + \cdots + s_{ip}c_{jp} 
$$

If $Q=I$ then $S=C=I$.   If $Q=11'$, a matrix of ones, then $S=\sqrt{p}(1,0)$ and $C=(c,0)$ both have rank 1:  here $s$ and $c$ are the leading columns of $S$ and $C$, respectively and 0 a matrix of zeros.

The approximation $Q\approx sc'$ is exact if $Q$ has rank 1 implying $Q=11'$.   The approximation $Q\approx sc'$ is inadequate if $Q=I$.  Inadequacy can be judged from the largest singular value in $D$, as a proportion of $p$, the number of variables or rows in $Q$.

$$
Q_* \equiv \frac{1}{p-1}(Q-I)=UDV'\cq s\equiv Q_*1\cq c\equiv Q_*'1\ .
$$$$
Q=I + s1'+ UDV'\cq s\equiv \frac{1}{p-1}(Q-I)1
$$
Then $s$ is the vector of average \v\ sensitivity of each variable to all others.  Further $c$ is the average \v\ impact of each variable on all others.   The matrices $U$, $D$ and $V$ define the singular value (svd) decomposition of $Q_*$, arranged so that diagonal matrix $D$ has the singular values on  the diagonal in descending order.   If $b=d_1u_1$ and $c=v_1$ where $u_1$, $d_1$ and $v_1$ are the first column, top diagonal entry, and first column of $U$, $D$ and $V$ respectively, then  for two variables $y\ne x$ in $Q$,
$$
\Delta_x q_y = s_y+ b_yc_x +\eps_{yx}
$$
This states that percentage sensitivities are, apart from the ``error" $\eps_{yx}$, an average sensitivity plus a scaled response to the contagious effect of the $x$ variable.   The contagious effects contained in $c$ are estimated by maximising the explanation of $Q$.

The vector $1'Q$ sums  the changes in \v\ when each of the column variables is stressed, and writes this as a proportion of the change in the variable being stressed.   These proportional sums, subtracting 1 and divided by  $p-1$ where $p$ is the number of variables, measures the average contagion of each variable on all others:  $c'=(p-1)^{-1}1'(Q-I)$ or $c=(p-1)^{-1}(Q-I)'1$

Alternatively the vector $Q1$ sums the changes in \v\ of each row variable when all the column variables are stressed.   Again it is appropriate to remove the effect of a variable on itself and consider the average over the remaining variables:  $s\equiv(p-1)^{-1}(Q-I)1$.  If $Q_*\equiv (p-1)^{-1}(Q-I)$ then $s=Q_*1$ and $c=\dot q_*1$ are the vectors of sensitivities and contagions, respectively.  If $Q=I$ then $s=c=0$.   If $Q=11'$ then $s=c=1$.

 \section{Systemic risk and causal chains}
A rank one approximation to the matrix  $Q$ is 
 $
 Q  \approx  sc' 
 $.
 Vector $c$ is an index of the contagious  impact of each of variables on the others while $s$ measures the sensitivity of each variable to each of the others.  The vectors $s$ and $c$ are derived from the singular value decomposition $Q=UDV'$ where $U'U=V'V=1$  and  where $s$ and $c$ are the first column of $UD$ and $V$  respectively, assuming the svd is organised so that the singular values in the diagonal matrix $D$ are organised from largest to smallest.   The appropriateness of the summarisation $sc'$ is measured with $\tr(Q-sc')$.

If the variables are independent then $Q=I$ and both $s$ and $c$ equal a column of the identity matrix with $sc'$ a matrix of 0's except in a single diagonal position where it is 1.   Then all but one variable has a contagion effect and only that variable is sensitive to the contagion provided by the  variable.

If the variables are comonotonic then $Q=11'$ and $s=1$ and $c=1$ where 1 denotes a vector of ones.   Thus the rank 1 approximation is exact and each variable is equally contagious and equally sensitive.

 Note that 
 $$
 Q^{n} \approx (s'c)^{n-1}sc'=\ ,
 $$

 If the random variables are independent the $Q-I=0$ and $a=b=k=0$ and there is no error in the first order svd approximation.    If the random variables are comonotonic then $Q=11'$ and $Q-I$ has ones everywhere except on the diagonal where it is zero.   The vector of row means is then $p^{-1}(p-1)1$

Systemic risk in the system is measured with $b'k=d_1(u_1'v_1)$.   In the case of comonotonic  random variables $Q=11'$, $a=1$ and $x$, where $p$ is the number of variables,  $d_1=1$.

Furthermore we may define quantities such as
$
u^- \equiv \var_q(v|u\le q)
$
measuring the impact of a non distressed state in $v$.  For brevity we do not dwell on these constructs in this writeup although the ramifications and potential uses of these constructs will be  investigated in the research.

\section{Generalising Sklar's Theorem}

Skalr's Theorem states that if $F(x)$ is a a joint then there exists a $C$ such that
$
F=C\circ F_*
$ where $C_F=F$
\section{Literature}

We propose a measure for systemic risk: CoVaR, the value at risk (VaR) of financial institutions conditional on other institutions being in distress. We define an institution?s (marginal) contribution to systemic risk as the difference between CoVaR and the financial system?s VaR. From our estimates of CoVaR for characteristic-sorted portfolios of publicly traded financial institutions, we quantify the extent to which characteristics such as leverage, size, and maturity mismatch predict systemic risk contribution. We argue for macro-prudential regulation based on the degree to which such characteristics forecast systemic risk contribution.

\section{Econometric implementation}

The above development sets out our proposed  broad  framework for linking bivariate copulas and marginals to external variables and shocks study the impact of the same on stresses within the system and the contagious effects of crises.   Proposed econometric analysis will implement and extend  \cite{brownlees2010volatility}.

\section{Data}

We will employ publicly available data as published by APRA and other regulators.

\section*{References}
\bibliography{/users/pietdejong/documents/research/cifr/piet2}

\end{document}

### 2015-05-29 old stuff/obs-(1)-copy.tex
pdj initial

--- 2015-05-29 old stuff/cifrpaper.tex
@@
 
-% Title of paper
-\title{Systemic risk and contagion effects in Australian financial institutions and sectors}
-% List of authors, with corresponding author marked by asterisk
-\author{Piet de Jong,  Geoff Loudon and Weihao Choo \\[4pt]
-% Author addresses
-\textit{Department of Applied Finance and Actuarial Studies\\ Macquarie University, Sydney, NSW 2109.}
-\\[2pt]
-%E-mail address for correspondence
-{piet.dejong@mq.edu.au}}
+\section{Weihao's approach}
 
-% Running headers of paper:
-\markboth%
-% First field is the short list of authors
-{De Jong}
-% Second field is the short title of the paper
-{Systemic risk}
+Univariate stressing leads to the stressed put expectation
+$$
+\E\{\phi(r_m)p_{it}\} = \int  f(r_m)\phi(r_m)\E(p_{it}|r_m) \de r_m = \int f_\phi(r_m) \E(p_{it}|r_m) \de r_m
+$$
+where $f$ is the original density of a market factor $r_m$ and $f_\phi=f\times \phi$ is the assumed density.
+Note $\phi$ may act on $r_m$ or its percentile rank $u_m$.
+The intent of $\phi$ is the enlarge the likelihood of ``bad" outcomes of $r_m$.
 
-\maketitle
-
-\section{Literature review}
-
-The starting point for the proposed research is the recent literature and the CIFR targeted areas and APRA aims and functions.
-This recent literature includes the following
-\cite{adrian2011covar},
-\cite{acharya2012capital},
-\cite{acharya2012measuring}
-and \cite{brownlees2010volatility}.
-The proposed research aims to extend and apply these techniques particularly in relation to the entities regulated by APRA.
-Thus our  broad aim is to develop, implement and bring to bear recent developments in stress testing  on the aims of APRA and the CIFR targeted research areas detailed above.
-
-\section{Improved  measures of contagion and systematic risk}
-\renewcommand{\c}{\ensuremath{\mathrm{CoVaR_q}}}
-\renewcommand{\v}{\ensuremath{\mathrm{VaR}_q}}
-
-$\covar_q$ as proposed in \cite{adrian2011covar} is a basis for proposed measures contagion, exposure and systemic risk.   It  suffers from a number of drawbacks:
-\bi
-\i Couched in terms of $\var_q$ containing the scale of the original measurements.   It is worthwhile to have measures and techniques robust to scale.
-\i  Conditioning  on $\var_{0.5}$ is undesirable and relatively intractable.
-In our proposal we reference stress with respect  to the unconditional $\var_q$.
-This permits a more transparent analysis and estimation.
-\i  Our proposed approach  separates out scale effects and interdependence effects and aims to  relates these separately to external variables including shocks and drivers of systemic risk.
-Thus $\var_q$ movements due to scale are disentangled from movements due to codependence with separate driver responses.
-\ei
-
-\section{Significance of the project and  policy implications}
-
-Understanding the impact of external shocks and their propagation through   the financial system is vital for managing and remediating systemic risk.
-Effective regulation is dependent upon the development of a robust and reliable set of appropriate risk measures.
-We propose new measures of systemic risk that relate marginal and joint distributions separately to external drivers.
-This allows for more cogent and coherent stress testing as it includes the estimation of contagion effects, exposure effects and systemic risk across related entities and different financial sectors.
-Improved stress testing, estimation of risk effects and transmission of shocks through the financial system will make for more cogent prudential policy, prudential margin setting and better identify sources of risk to the financial system.
-
-\newcommand{\q}{\mathrm{Q}}
-\section{Percentile sensitivity and contagion}\label{perc}
-
-\subsection{Theorem}  Suppose $x$ is a random vector with marginal distributions\footnote{To economise on notation, write $F_j(x)\equiv F_j(x_j)\equiv F(x_j)$ and similar for other vector functions.} 
+Bivariate stressing yields
 $$
-F(x)\equiv \{F(x_1),\ldots ,F(x_p)\} \equiv (u_1,\ldots,u_p)\equiv u\ .
-$$ 
-Further suppose $0\le q\le 1$ is given and  $\q(x)$ is the vector of $q$--quantiles
-$$
-F\{\q(x)\}=q1=\q(u)\ ,
-$$
-where $1$ is a vector of $p$ ones. 
-Define the stress vector with respect to $x_j$ as\footnote{In \cite{adrian2011covar}  $\Delta CoVar_q\equiv q_{y|x=q_x}-q_y$.
-Variable $y$  is generally the ``financial system" and hence considered is the change in the \v\ of the system when institution $x$ stressed, with stress  interpreted as $x=q_x$.
-On page 10 of their paper they incorrectly state ``...
-$CoVaR$ conditions on the event that [an] institution is at its VaR level, which occurs with probability $q$."}
-\be{stress}
-\frac{\de\q(x)}{\de x_j} \equiv \q(x|u_j>q) - \q(x)\ ,
-\ee
-where $\q(x|u_j>q)$ is the vector of $q$--quantiles of $x$ given $u_j>q$.    Then if $\q(x)$  is linear in $q$ 
- then
-\be{implicit}
-\frac{\de\q(x_i)}{\de\q(x_j)} \equiv \frac{\de\q(x_i)/\de x_j}{\de\q(x_j)/\de x_j} =  
-\frac{f_j}{f_i} 
- \frac{q_{ij}}{q(1-q)}\cq q_{ij}=C_{ij}(q+q_{ij},q) - q^2\ ,
-\ee
-where $f_i$ and $f_j$ are the densities of $x_i$ and $x_j$ evaluated at $\q(x_i)$ and $\q(x_j)$ and  $C_{ij}$ is the copula of $(u_i,u_j)$.   
-Further if 
-$$
-s_{ij}\equiv \frac{q_{ij}}{q(1-q)}\ ,
-$$ then  $-1\le s_{ij}\le 1$ with $s_{ij}=\pm 1$ if $x_i$ and $x_j$ are comonotonic and counter monotonic, respectively.
-If $x_i$ and $x_j$ are independent then  $s_{ij}=0$.
-If $u_i$ and $u_j$ are exchangeable  then  $s_{ji}=s_{ij}$.
-
-\subsection{Proof}
-
-By definition
-$$
-\frac{\de\q(u_i)}{\de u_j} \equiv \q(u_i|u_j>q) -q \equiv q_{ij}\ ,
-$$
-where  $q_{ij}$ is such that
-\be{Qdef}
-q =  \frac{\P(u_i\le  q+q_{ij},u_j>q)}{1-q}  = \frac{ q+q_{ij}-C_{ij}(q+q_{ij},q)}{1-q}\ ,
-\ee
-Rearranging yields the second equation in \eref{implicit}.
-Now
- \be{first}
- \frac{\de\q(x_i)}{\de x_j}\equiv \q_{q+q_{ij}}(x_i) - \q(x_i) \approx \q'(x_i)q_{ij}= \frac{q_{ij}}{f_i} \ ,
- \ee
-where $'$ denotes differentiation with respect to $q$ and the subscript on $\q$ indicates the revised $q$ for the quantile calculation.
-The approximation follows from a first order Taylor expansion and is exact if the quantile is linear in $q$.
-Similarly
- \be{second}
- \frac{\de\q(x_j)}{\de x_j}\equiv  \q_{q+q(1-q)}(x_j) - \q(x_j)\approx \frac{q(1-q)}{f_j}\ .
- \ee
- Dividing \eref{first} by \eref{second} yields the first equation in  \eref{implicit} and completes the proof.
-
-\subsection{Discussion}  The critical  result is that sensitivities factor into contributions from the ratios of the marginal densities and quantities calculated from the pairwise copulas.
-The via  the implicit  equation for $q_{ij}$ in \eref{implicit}, solved using a  root finding algorithm.
-  The quantities $q_{ij}$ are implicitly defined from the pairwise copulas. In summary the ``sensitivity" matrix 
-$$
-S \equiv \frac{\de Q(x)}{\de Q'(x)}\ ,
-$$
-where $'$ denotes transposition has ones on the diagonal quantities between $\pm 1$ off the diagonal.
-The matrix $S$ is called the sensitivity matrix and displays the sensitivity of the $q$--quantile of  each component of $x$ to  stress in the same or other components.
-
-Since $f_i$ and $f_j$ are  the densities evaluated at $\q(x_i)$ and $\q(x_j)$  it follows that the ratio $f_i/f_j$ can be replaced by the ratio of the hazards.
-This is  useful in cases were it is practical to model the hazard rather than the density.
-
-\subsection{Implementation}
-
-\fref{fig1} displays the empirical copulas calculated from four weekly closing stock prices labelled anz, cba, mcq and  wbc for $n=761$ weeks from 2000 April 12 through to 2014 October 29.
-The empirical copulas are calculated by converting each observation to an empirical percentile and plotting the same against each of the other series percentiles.
-
-\begin{figure}
-  \begin{center}
-    \includegraphics{fig1.pdf}
-    \caption{Pairwise copulas of bank stocks  cba, anz, mqg, wbc, and the overall bank index.  Red lines plot sensitivity $s_{ij}$ as a function of $q$.}\label{fig1}
-   \end{center}
-\end{figure}
-
-To estimate  $q_{ij}$  at a particular $q$, the second equation in \eref{implicit} is iterated\footnote{The second equation in \eref{implicit} is a contraction mapping and hence has a fixed point.} starting from $q_{ij}=0$ where copulas are estimated as
-$$
-\hat C_{ij}(u_i,u_j) \equiv \hat\E\{(p_{ik}\le u_i)(p_{jk}\le u_j)\}\ .
-$$
-Here $\hat\E$ computes the empirical mean over the cases $k=1,\ldots,n$ and $p_{ik}$ and $p_{jk}$ are the empirical percentiles  of case $k$ of $x_i$ and $x_j$, respectively.
-
-\subsection{Generalisations}
-\renewcommand{\r}{\mathrm{R}}
-Similar results apply when $\Q(x)$ is replaced by  other risk measures such as $\r(x)\equiv\E\{xr(u)\}$ where $r$ is a given function which acts componentwise and $xr(u)$ denotes componentwise multiplication.
-For example if $r(u)=mu^{m-1}$ then  $\r(x)=\E\{\max(x^1,\ldots,x^m)\}$ where  $x^1,\ldots,x^m$ are $m$ independent copies of $x$ and the risk measure is the expected worst outcome in $m$ independent trials.
-
-With $\r(x)$, the analogue of \eref{stress} is 
-\be{stress2}
-\frac{\de\r(x)}{\de x_j} \equiv \r(x|u_j>r_j) - \r(x_j)\cq r_j\equiv\p\{x_j\le\r(x_j)\} \ .
-\ee
-This differs from \eref{stress}  in that a different risk measure is used and  $r_j$ replaces $q$.   If  the components of $\r(x)$ are linear in the $r_i$ then
-\be{implicit2}
-\frac{\de\r(x_i)}{\de\r(x_j)} =  
-\frac{f_j}{f_i} 
- \frac{q_{ij}}{q(1-q)}\cq q_{ij}=C_{ij}(r_i+q_{ij},r_j) - r_ir_j\ ,
-\ee
-where $f_i$ and $f_j$ are the $x_i$ and $x_j$ densities at the $r_i$ and $r_i$ quantiles, respectively.
-
-\section{Systemic risk}
-\cite{brownlees2015} describe a model for systemic risk (SRISK) estimated for each financial firm $i$ and each time point $t$.
-SRISK of a firm at time $t$ is the expected capital shortfall  it will experience in the period $(t,t+h)$ given a crisis downtown in the market over the same period.
-Capital shortfall is defined as the ratio of equity to equity plus debt falling below a certain level $k$.
-A crises market is a market return below $c$.
-
-If expected capital shortfall  is zero then SRISK is zero.
-The sum of  SRISK's  across all firms is the total SRISK in the economy and each firm contributes either zero or some proportion to the total SRISK in the economy.
-Firms with a high  percentage SRISK (denoted SRISK\%) are systemically important and will be  of major concern to regulators.
-
-\subsection{Debt and Equity}
-
-Suppose a firm at time $t$ has debt $D_t$ and equity $W_t$.   Then at $t$, $D_t+W_t$ is the total claim on the firm. 
-Regulated firms are generally required to hold a proportion $k$ of total claims $k(D_t+W_t)$ as a prudential margin.
-If  $k(D_t+W_t)>W_t$ then, prudentially speaking, the firm has capital shortfall
-$$S_t\equiv k(D_t+W_t)-W_t\ .
-$$  
-Negative capital shortfall indicates positive working capital.
-
-Concerned with predicting capital shortfall $S_{t+h}$ conditional on a systemic event defined as a market decline below a threshold $c$ over the time horizon $(t,t+h)$.
-This is similar to \cite{acharya2012wp}.
-
-\subsection{Returns, leverage and capital shortfall}
-
-Consider a single firm with return $r_t$.
-This is the percentage change in value over the period  $(t-1,t)$ known as period $t$.
-The arithmetic return over the period $(t,t+h)$ is $\nu_t\equiv r_{t+1}+r_{t+2}+\cdots+r_{t+h}$ and is an $h$ period return.
-If $h=1$ then  $\nu_t=r_{t+1}$.
-
-The equity of a firm at time $t+h$ is 
-$$
-w_{t+h} = (1+\nu_{t})w_t\cq \nu_t\equiv r_{t+1}+\cdots+r_{t+h}\ ,
-$$
-
-If the debt of the firm $d_t$  stays constant over the period $(t,t+h)$:   $d_t=d_{t+1}=\cdots=d_{t+h}$  and the capital shortfall i 
-\be{cs}
-c_{t+h}\equiv  k(d_{t+h}+w_{t+h})-w_{t+h} = k d_{t} - (1-k)(1+\nu_{t})w_t
-\ee
- Note  $c_{t+h}$ is a linear in $\nu_t$.
-
-\subsection{Systemic events and systemic risk of a firm}
-A systemic event or ``crisis"   occurs in the period $(t,t+h)$ if the market  return $r_{mt}(h)\le c$.
-The systemic risk (SRISK)  of  a firm is the expectation of the capital shortfall given  a crisis:
-\be{sr}
-\mathrm{SRISK}_t\equiv  \E_t\{S_{t+h}|r_{mt}(h)\le c\}  =  [k\ell_t-(1-k)\E_t^c\{r_{t}(h)\}-1]W_t\ .
-\ee
-where
-$$
-\mathrm{LRMES}_t \equiv \E^c\{r_{t}(h)\}\equiv \E_t\{r_t(h)|r_{mt}(h)<c\}\ ,
-$$
-and in terms of this notation:
-$$ 
- \mathrm{SRISK}_t = \{k\mathrm{LVG}_t - (1-k)\mathrm{LRMES}_t - 1\}W_t\ .
-$$
-The condition $D_{t+h}=D_t$ or less strongly $\E_t^c(D_{t+h})=D_t$ indicates the value of debt  does not change if there is a crisis.
-
-Evaluating the systemic risk in a firm requires the evaluation or estimation of the ``crisis" expectation, also called  the long run marginal expected shortfall (LRMES):
-
-$\mathrm{SRISK}_t$ is a point estimate of capital shortfall in a crisis.
-Since $S_t$ is linear in $r_t$ the crisis distribution of $S_t$ is known if the conditional distribution of $r_t(h)|r_{mt}(h)<c$ is known.
-
-\subsection{Vector generalisation}
-
-Aggregate systemic risk is 
-$$
-\mathrm{SRISK}_t = \sum_i \mathrm{SRISK}^+_{it}
-$$
-where $^+$ indicates the positive part of.   
-   The proportion of systemic risk in firm $i$ is then
-$$
-\mathrm{SRISK\%}_{it} = \frac{\mathrm{SRISK}_{it}^+}{\mathrm{SRISK}_{t}}
-$$
-
-\subsection{Example from vlab}
-See \fref{vlab} taken on 15 April 2015 from the website http://vlab.stern.nyu.edu
-
-\begin{figure}[htbp]
-\caption{default}\label{vlab}
-\begin{center}
-%\includegraphics[width=15cm]{vlab.pdf}
-\end{center}
-\end{figure}
-
-\subsection{Discussion points}
-
-\begin{enumerate}
-\item  Above is similar to ``stress tests" regularly applied to financial firms.   However above uses only publicly available information
-\item  Above approach is forward looking -- ie distribution of future assets conditional on a systemic event.  Markets look at things forwardly so incorporating forward information.
-\item  Should have an appropriate $h$ and $c$ -- not too small etc.
-\item  Capital shortfall is natural to use since this generates reduced lending activiity etc.
-\item Measuring distress a firm is going to suffer conditional on a systemic event affecting the entire system.
-Note this is different from capital shortfall conditional on firm default as with credit models.
-\item Not concerned with the probability of joint distress of a large proportion of firms in the financial system.
-Here systemic risk is determined by the capital shortfall generated distressed institutions conditional on a systemic event.
-Framework takes into account joint dependence among firms, as well as their size and degree of leverage.
-Do a small number of large financial institutions pose systemic threats to the entire system?
-Tail correlations might fail to do so.
-\item  Simplifying assumptions are made to deliver a measure that can be easily computed in practice.    Asset structure is captured in a limited sense.   
-\item   Measurement approach can be applied to non financial firms.
-However these firms are not highly levereged and are not as vulnerable as financial firms.
-Not clear how capital shortfall transmits to rest of economy.
-
-\end{enumerate}
-
-\subsection{Static econometric model for systemic risk}
-
-An econometric models  links one period returns $r_{it}$  to the  market return $r_{mt}$ enabling  the calculation of 
-LRMES and SRISK.   The approach is to assume $(r_{it},r_{mt})$ are zero mean bivariate normal with volatilities $\sigma_{it}$ and $\sigma_{mt}$ and correlation $\rho_t$.  In this case
-$$
-\E(r_{it}|r_{mt}<c) = \frac{\rho_t\sigma_{it}}{\sigma_{mt}}\E(r_{mt}|r_{mt}<c)  = \rho_t\sigma_{it}\psi\left(\frac{c}{\sigma_{mt}}\right)\cq \psi(x)\equiv\frac{\phi(x)}{\Psi(x)}\ .
-$$
-Noting $r_{it}(h)=r_{i,t+1}+\cdots+r_{i,t+h}$ and similarly for $r_{mt}(h)$ then 
-$$
-\E\{r_{it}(h)|r_{mt}(h)<c\}  = \sqrt{h}\rho_t\sigma_{it}\ \psi\left\{\frac{\ln(1+c)}{\sigma_{mt}\sqrt h}\right\}\ .
-$$
-{\it Let us emphasize that the [last] formula ...
-has an error which is due to the fact that we are approximating MES using compound returns rather than arithmetic returns.
-In particular [the] formula ...
-has a negative approximation error  and provides more extreme negative LRMES values.}
-
-\subsection{Modelling systemic risk using a dynamic model}
-
-\cite{brownlees2015} use  data on 95 large US financial firms for the period 2000-2012:   daily equity returns and market capitalization from CRSP; quarterly book values for equity and debt from Compustat.
-A   Dynamic Conditional Correlation (DCC) model is estimated for  firm and market returns.
-Write
-\newcommand{\veps}{\varepsilon}
-$$
-\cov (r_t|t) = V_tR_tV_t'\cq R_t\equiv \cov(\veps_t|t)\cq \veps_t=V_t^{-1}r_t\ ,
-$$
-where $R_t$ and  $V_t$  are the correlation and diagonal volatility matrix, respectively, at time $t$.
-Volatilities in $V_t$  are estimated using univariate threshold GARCH models.
-The estimate of $R_t$ corresponds to the correlations in covariance matrix $C_t$ assuming
-$$
-(C_t - C) = \alpha (C_{t-1}-C)+\beta (\veps_t\veps'_t-C) \cq C\equiv\cov(\veps_t)\ .
-$$
-where $C$ is the long run covariance matrix.
-
-\cite{brownlees2015} find the above systemic risk measure  a)  successfully identifies systemically risky firms during the GFC;
-b)  predicts capital injections by Fed Reserve; and c) aggregate systemic risk provides early warning of declines in industrial production and higher unemployment.
-
-Thus the model  estimates the beta of a firm equity on a broad market index.
-A bivariate volatility model is estimated for the return on the broad market and the equity return of each firm.
-This model allows volatilities and correlations to evolve.
-The estimated process is used to simulate the probability of severely negative outcomes over an extended period.
-Assuming that firms can only operate if capital is a non--trivial proportion of their total liabilities, SRISK is defined as the capital that would be needed to achieve a market cap that is 8\% of the book value of assets in the event of a crisis.
-The input to SRISK is size, leverage and risk.
-Each is important and a firm that wants to reduce its SRISK, can operate on any of these characteristics.
-A crisis is taken to be a 40\% drop in global equity values over six months.
-SRISK is computed weekly for firms from about 70 countries and published on the internet at http://vlab.stern.nyu.edu.
-In extending this analysis to international markets, the model is naturally generalized to a multivariate volatility model.
-The data are considered to be the equity return on one firm, the equity return on a global index of equity returns, and perhaps some lags.
-The use of daily data for assets that are priced in different time zones means that closing prices are not measured at the same time and consequently there may be some important effect from lagged factor returns.
-
-\subsection{Systemic risk based on probabilities}
-
-If $d_t$ and $w_t$ are the debt and equity of a firm at time $t$ then the capital shortfall at time $t$ is 
-$$
-(1-k) d_t  - k w_t
-$$
-Basel II assumes $1-k=0.08$ implying there is  positive  capital shortfall if 
-$
- 0.08 d_t>0.92 w_t
-$
-or  leverage $d_t/w_t>11.5$ or the log--leverage is greater than $\ln(11.5)=2.44$.
-
-Given the debt and equity, the capital shortfall at time $t$ is zero if 
-$$
-\frac{k_t}{1-k_t} = \frac{d_t}{w_t}\cq k_t= \frac{d_t/w_t}{1+d_t/w_t} = \frac{d_t}{d_t+w_t}
-$$
-where $0\le k_t\le 1$  is thought of as a risk index and $k_t/(1-k_t)$ is the leverage or risk odds.
-
-Now consider the situation at time  $t+h$ where $h>0$, 
-$$
- k_{t+h}\equiv\frac{d_{t+h}}{d_{t+h}+w_{t+h}} =  \frac{d_t}{d_t+\e^{\nu_{t+h}}w_t}
-$$ 
-where it is assumed $d_{t+h}=d_t$ and $\nu_{t+h}$ is the $h$ period return over $(t,t+h)$.  The   logit risk/log leverage is
-$$
-\ell_{t+h}\equiv\ln \frac{k_{t+h}}{1-k_{t+h}} = \ln \frac{d_{t+h}}{w_{t+h}} = \ln d_t - \ln w_t - \nu_{t+h} = \ell_t -\nu_{t+h} \ .
-$$
-Hence a large positive return $\nu_{t+h}$ implies a lower  risk.  As the logit risk/log leverage  increases to 2.44 the firm approaches the Basel II threshold.
-
-If there are a number of  firms $i$ then $\ell_t$ and $\nu_{t+h}$ are  vectors with components $\ell_{it}$ and $\nu_{it}$, respectively, and in vector terms, $\ell_{t+h}=\ell_t - \nu_{t+h}$.
-The aggregate risk is $1'\ell_{t+h}$.
-
-\subsection{Systemic risk}
-
-Systemic risk is defined as the log--leverage in the system as a whole:   that is  aggregate all debt and equity and compute, as above, the log--leverage $\ell_t^+$.    Then
-$$
-\ell^+_{t+h} = \ln \frac{d^+_t}{w^+_t}-\nu^+_{t+h} =  \ln \sum_i\alpha_{it}\frac{ d_{it}}{ w_{it}} -\nu^+_{t+h}= \ln \Ex_w(\e^{\ell_{it}})-\nu^+_{t+h} \cq \alpha_{it}\equiv\frac{w_{it}}{ w^+_t}\ .
-$$
-where $\nu_{t+h}^+$ is the aggregate return
-$$
-\ln \frac{1'w_{t+h}}{1'w_t} = \ln\Ex_w(\nu_{it})
-$$
-Differentiating with respect to $\ell_{i,t+h}$ yields
-$$
-\frac{\de \ell^+_{t+h}}{\de \ell_{i,t+h}} = \frac{\alpha_{it}\e^{\ell_{it}}}{\sum_i\alpha_{it}\e^{\ell_{it}}} \frac{\de\nu_{i,t+h}}{\de \ell_{i,t+h}}=\frac{w_{it}\e^{\ell_{it}}}{\sum_iw_{it}\e^{\ell_{it}}}
-=\frac{d_{it}}{\sum_id_{it}}=\frac{d_{it}}{d_t^+}\ ,
-$$
-implying the percentage change in overall forecast leverage respect to a percentage change of the forecast leverage of  firm $i$ is proportional to the proportion of debt in firm $i$.   Further 
-$$
-\ell^+_{t+h} = \ln \Ex_w(\e^{\ell_{it}})-\nu^+_{t+h} \approx \Ex_d(\ell_{it})-\Ex_d(\nu_{i,t+h})\
-$$
-Thus the contribution of firm $i$ to the systemic risk is
-
-\subsection{Comparing default probabilities}
-
-Suppose $\ell_{it}$ and $\ell_{t}$ are the risk for firm $i$ and the combination of firms.   Then the excess risk in firm $i$ is
-$$
-\ell_{it}-\ell_t = \ln \frac{d_{it}}{d_t} - \ln \frac{w_{it}}{w_t} + (\nu_t-\nu_{it})\ .
-$$
-Thus if firm $i$ has the the same leverage as the average leverage then the excess risk is the underperformance over the time interval $(t,t+h)$.
-
-Note
-
-and hence can define
-$$
-x
-$$
-
-\subsection{Systemic risk}
-
-The total leverage in the system is
-
-a value weighted average of the individual leverages.   The $k_t$ for  capital shortfall for the system as a whole can be
-produced from this total leverage.   The logit $\ell_t$ of $k_t$ then yields a risk index for the system as a whole.  Note
-$$
-\ell_t \equiv \ln \frac{d_{t+h}}{w_{t+h}}=-\nu_t+\ln \sum_i\alpha_{it}\frac{ d_{it}}{ w_{it}}\ne \sum_i \ell_{it}
-$$
-
-Can look at
-$$
-\ell_{it}-\ell_t  = \ln d_{it}-\ln d_t - (\ln w_{it}-\ln w_t) - (\nu_{it}-\nu_t)
-$$
-
-Suppose there are a number of firms and define
-$$
-d_t=\sum_i d_{it}\cq w_t=\sum_i w_{it} \cq  \frac{\ell_{it}}{\ell_t}
-$$
-
-The log--odds can be related to other variables.
-In many cases the capital injection required is negative indicating capital can be withdrawn from the company without it breaching prudential standards.
-
-\subsection{GARCH-DDC simulation}
-
-We can consider the distribution of the projected log--leverage (pll) conditional on other variables including the market return
-$$
-\E(\ell_t|\nu_{mt}\le c)  = \ln d_t -\ln w_t -\E(\nu_t|\nu_{mt}\le c)\ .
-$$
-Alternatively we can consider the  $\alpha$--percentiles of $\ell_t$ denoted $\ell^\alpha_t$ such that
-$
-\alpha=\P(\ell_t\le \ell_t^\alpha)
-$.  Note
-$$
-\ell_t^\alpha = \ln d_t -\ln w_t -\nu_t^\alpha = \ln \frac{d_t}{w_t}-\nu_t^\alpha\  .
-$$
-
-The GARCH-DCC setup delivers forecast or simulated values of $r^s_{t}(h)$, $s=1,\ldots, S$  for each  $t$.
-Assume the simulated values are ordered in terms of increasing market returns $r^s_{mt}(h)$ and arranged in an $2\times S$ matrix $C_t$ where  the bottom row is the simulated market return.
-
-This computation is complicated by two things:
-\begin{enumerate}
-\item  Dividends my be paid  in the period $(t, t+h)$ serving to reduce equity.
-Typically at most one dividend  is payable which can be accumulated to  $t+h$ and used to increase equity.
-That is for purposes of  assessing model accuracy $w_{t+h}$ is increased by proportion $1+f_{t'}(1+r_{t'})^{t+h-t'}$ where $t\le t'<t+h$ is  ex--dividend date and $f_t$ is the dividend yield.
-\item  Debt may change over the period.
-\end{enumerate}
-
-In terms of $C_t$ the SRISK measure of \cite{brownlees2015} is the average, along each row of the prefixes.
-For example,  the average in row $i$ of the  first $s$ entries is the systemic risk of firm $i$ at time $t$ conditional on  $r_{mt}(h)\le F_{mt}^{-}(s/S)$ where  $F_{mt}$ is the empirical distribution of the  $r^s_{mt}(h)$, $s=1,\ldots,S$.
-
-A default or breach of prudential margins occurs if $c_{it}^s>0$.  The probability of a default if $r_{mt}(h)\le F_{mt}^{-}(v)$ is estimated as 
-$$
-\hat p_{it}=\frac{\sum_{s=1}^{[vS]}I(c^s_{it}>0)}{[vS]}\ ,
-$$
-where $v$ is given, for example $v=0.1$.
-Joint probabilities of default are estimated similarly: the joint probability of a subset $B$ of firms  breaching their margins is 
-estimated as
-$$
-\hat p_{Bt} = \frac{\sum_{s=1}^{[vS]}\prod_{i\in B} I(c^s_{it}>0)}{[vS]}\ .
-$$
-These probabilities generally decline with $v$: that is as the market downturn becomes less extreme.
-
-Instead of asking what is the probability of a default (ie breach of prudential regulation) it is meaningful to consider what would $k$ have to be in order for it to be in default at time $t+h$.
-Writing this value as
-$$
-k_t d_t - (1-k_t)\{1+r_t(h)\}w_t = 0 \qquad \implies \qquad k_t=\frac{1}{1+d_t/[\{1+r_t(h)\}w_t]}
-$$
-This equation can be computed given $r_t(h)$ and hence for every simulated value to arrive at $k_t^s$.
-If $d_t\equiv0$ then $k_t=1$ indicating  a healthy state of affairs.
-If $d_t/w_t$ is large then $k_t\approx 0$.
-Hence as $k_t$ drops there is more danger.
-
-Furthermore
-$$
-\ln k_t = -\ln \left[1+\{1+r_t(h)\}^{-1}\frac{d_t}{w_t}\right]\approx -\{1+r_t(h)\}^{-1}\frac{d_t}{w_t}\approx -\e^{-r_t(h)}\frac{d_t}{w_t}
+\E\{\phi(r_m,r_n)p_{it}\} = \int \int f(r_m,r_n)\phi(r_m,r_n) \E(p_{it}|r_m, r_n) \de r_m \de r_n
 $$
 $$
-\kappa_t \equiv \ln(-\ln k_t) \approx  \ln (d_t) - \ln (w_t) - r_t(h)
+= \int \int f_\phi(r_m,r_n) \E(p_{it}|r_m, r_n) \de r_m \de r_n
 $$
-A large value for $\kappa_t$ indicates
-
-To study the time series and cross sectional behaviour of $\hat p_{it}$, it is useful to define the  normal scores 
+where $r_n$ is another market factor and $f$ is now the joint density of $(r_m,r_n)$.
+The assumed joint density is $f_\phi=f\times \phi$, which again enlarges the joint likelihood of ``bad" outcomes of $(r_m,r_n)$.
+For example $f_\phi$ may have stronger tail dependence than $f$, which can be achieved by either selecting a copula which has stronger tail dependence, or setting up $\phi$ as $\phi(u_mu_n)$ where $\phi$ is decreasing.
+Marginal distributions of $r_m$ and $r_n$ may be altered or unchanged.
+If unchanged then
 $$
-z_{it} \equiv \Phi^-(\hat p_{it})\cq i=1,\ldots, n\cq t=1,\ldots, T\ .
+f(r_n) = \int f(r_m,r_n) \de r_m = \int f_\phi(r_m,r_n) \de r_m
 $$
-Defining  $z_t\equiv (z_{1t},\ldots,z_{nt})'$ then a firm is systemically important if it is highly collinear with the other scores.
-
-An entropy based measure of systemic risk is
+or
 $$
-H_t = -\E(\ln p_{Bt})\equiv -\sum_B p_{Bt}\ln p_{Bt}\ .
+1 = \int f(r_m)c(u_m,u_n) \de r_m = \int f(r_m)\phi(r_m,r_n) c(u_m,u_n) \de r_m
 $$
-
-Systemically important firms are those which, when in default, are highly likely to be associated with a joint default.
-joint probability of matrix is then 
-$$
-  P_t\equiv \frac{1}{S} I_tI_t'\cq  I_t = I(\rho^s_{it}>0)
-$$
-
- can define the probability of a firm going in default as
-$$
-\hat p_{it}\equiv \frac{\sum_{s=1}^SI(\rho_{it}^s>0)}{S}
-$$ 
-In terms of this notation the probability of all firms going bankrupt and non
-
-\subsection{Time--varying copula model}
-
-Suppose $\delta\ge 1$ and the rotated Gumbel copula modelling lower tail dependence:
-$$
-C_\delta(u,v) = u+v-1+\e^{-[\{-\ln(1-u)\}^{\delta}+\{-\ln(1-v)\}^{\delta}]^{1/\delta}}
-$$
-Further suppose a sequence
-$$
-\delta_{t+1} = 1+\left(\omega + \alpha \frac{\sum_{s=0}^{m-1}|u_{t-s}-v_{t-s}|}{m}+ \beta\delta_t\right)^2\ .
-$$
-Note $\delta_t$ is always greater than 1.
-\cite{patton2006modelling} has more details.
-The model is fitted by estimating marginal models first and then by maximizing the copula likelihood using the fitted uniform marginals.
-
-\subsection{Data  used in \cite{brownlees2015} }
-
-\begin{itemize}
-\item Large US financial firms (ie capitalization greater than 5bln US)
-\item Jan 3, 2000 through to Dec 31, 2012:  not all companies continuously traded
-\item Daily returns and market capitalization from CRSP
-\item Quaterly book value of equity and debt from COMPUSTAT.
-\item SIC codes used to segment firms into 4 industry groups (Depositries (29), Broker Dealers (10), Insurance (34) and Others (22))
-\end{itemize}
-
-SRISK is computed with the parameters $k=0.08$, $c=-0.1$, $h=22$ (a month).  SRISK computed at end of each month using all available data at that data, therefore no look ahead bias.
-
-LRMES computed with the GARCH-DCC model for each firm.   Uses all available data starting from Jan 3, 2000 to end of each month.
-
-\subsection{Older stuff}
-
-$$
-\E^c(r_{it}) \equiv \E(r_{it}|u_{mt}\le c^*)\cq c^*=\E\{(r_{mt}\le c)\}\ ,
-$$
-where $u_{mt}$ is the percentile of $r_{mt}$.
-Given a joint distribution for $(r_{it},r_{mt})$ the distribution is simulated and
-\be{sim}
-\E^c(r_{it}) \approx \frac{\hat \E\{(r_{mt}\leq c)r_{it}\}}{\hat \E\{(r_{mt}\leq c)\}}= \frac{\hat\E\{(u_{mt}\leq c^*)F^-_{it}(u_{it})\}}{c^*}\ ,
-\ee
-where the $r$ values in the middle expressions denote simulated values and $\hat\E$, averages over the simulated values.
-The $u_{it}$ and $u_{mt}$ are the percentiles of $r_{it}$ and $r_{mt}$, respectively.
-
-The right hand expression in \eref{sim}  suggests using a copula to model the joint distributions $(r_{it},r_{mt})$.
-Simulate $(u_{it},u_{mt})$, from the copula, discarding pairs with $u_{mt}>c^*$.
-For each accepted $(u_{it},u_{mt})$  determine the actual return using the respective marginal distributions.
-Issues to be addressed are:
-\bi
-\i Are the marginal distributions time invariant?  Could have situation where the marginal distribution evolves over time and/or is state dependent
-\i Is the copula time invariant?   Could have situation where the copula is state dependent.    
-\ei
-
-The first step here is to examine the marginal distributions of the returns and the empirical copula of returns.
-
-{\bf Comment.}  With the DCC model both volatilities and correlations have a time dependent structure.  These are modelled separately.
-An alternative approach is where ...
-
-{\bf \cite{engle2014dynamic}} describes a new approach to estimating time varying regression coefficients.
-The approach is called Dynamic Conditional Beta (DCB).
-Consider $(y_t,x_t)$ where  $y_t$  and $x_t$ are vectors.
-Interested in $\E_t(y_t|x_t)$.
-This is expression  may be linear in $x_t$ and depending on the past information set.
-Write
-\newcommand{\F}{{\cal F}}
-$$
-(y_t,x_t)|\F_{t-1} \sim N(\mu_t,H_t) \implies y_t|x_t,\F_{t-1}\sim N\{\mu_{yt}+B_t(x_t-\mu_{xt}), C_{yy,t}\}
-$$
-where
-$$
-B_t= H_{yx,t}H^-_{xx,t}\cq  C_{yy,t}= H_{yy,t}-B_tH_{xx,t}B'_t\ .
-$$
-These expressions depend on the time varying covariance matrix $H_t$.    For implementation we need a model for $\mu_t$ and $H_t$.
-
-\section{TARCH modelling}
-
-The standard approach to the joint modelling of returns is where volatility adjusted returns are modelled, for each security, as
-\newcommand{\vareps}{\varepsilon}
-\be{mean.model}
-r_{t}=\mu+\sigma_t\eps_t\cq \eps_t\sim (0,1)\cq  \eps^-_t\equiv(\eps_t<0)=(r_t<\mu)\ ,
-\ee
-%frac{r_{it} - \mu_i}{\sigma_{it}} = \rho_{it}\eps_{mt} + \sqrt{1-\rho_{it}^2}\vareps_{it}
-Further
-\be{vol}
-\sigma_{t+1}^2 = \omega+ (\alpha+\gamma\eps^-_t) (r_t-\mu)^2 + \beta\sigma^2_t=\omega+ \sigma^2_t\{(\alpha+\gamma \eps^-_t)\eps_{t}^2 + \beta\}\\ .
-\ee
-Hence the response in the variance to $\eps_t^2$  is increased by $\gamma$   if $\eps_{t}<0$ compared to the response if $\eps_t>0$.  This is a simple threshold GARCH model:  called TARCH.
-
-The simple TARCH model \eref{mean.model} and \eref{vol} is generalised by replacing $r_t-\mu$ by a time series model possibly including explanatory variables.
-Further $\omega$ can be replaced by $x_t'\delta$ where $x_t$ is a vector of explanatory variables, while extra lags can be introduced on the right hand side of \eref{vol}.
-
- Taking expectations of both sides of \eref{vol} yields
- $$
-\sigma_{t+1}^2 = \omega+ \left\{\alpha+\beta+\gamma \E(\eps^-_t\eps_{t}^2)\right\}\sigma_t^2\ .
- $$
-For a long run stationary solution 
-$$
-\sigma^2 = \frac{\omega }{1-\alpha-\beta-\gamma\E(\eps^-_t\eps_t^2)}\cq \E(\eps^-_t\eps_t^2)=p\E(\eps_t^2|\eps_t<0)+(1-p)\E(\eps_t^2|\eps_t\ge 0)\\ .
-$$
-where $p\equiv\E(\eps_t^-)$.  For the symmetric case, $p=1/2$ and  $\E(\eps_t^2|\eps_t<0)=1$ implying $\E(\eps^-_t\eps_t^2)=1$ and
-$
-\omega=(1-\alpha-\beta-\gamma)\sigma^2
-$.  With the zeta transform  $\sigma^2=1$ and hence the sum of the coefficients is 1.
-
-Alternatively
-$$
-\E(\eps^-_t\eps_t^2) = p +\rho\sqrt{p(1-p)} = p\left(1+\rho\sqrt{\frac{1-p}{p}}\right)\ ,
-$$
-where $\rho$ is the correlation between $\eps_t^-$ and $\eps_t^2$.   For a symmetric distribution this reduces to $(1+\rho)/2$.
-
-The above setup holds for each security $i$ including the market, assumed to have index $i=m$.
-The correlation between securities can also be modelled.
-This is achieved by modelling the correlation of each security with the market, denoted $\rho_{it}$ or assuming the correlation matrix of the stack of the $\eps_t$, denoted $\eps_t$  are generated from a positive definite matrix $Q_t$ say where \citep{engle2002dynamic}
-$$
-Q_{t+1} = (1-\alpha-\beta) S + \alpha \eps_t\eps_t' + \beta Q_t\ ,
-$$
-where $\eps_t$ is the vector of $\eps_{it}$, including that of the market.
-
- \section{TARCH modelling applied to zeta scores}
-
- In this case $\omega_i\approx 0$, $\alpha_i$ and $\beta_i$ is generally positive and significant, while $\gamma_i$ is positive and marginally significant.  This suggests in these cases
- $$
- \zeta_{it}=\sigma_{it}\eps_{it}\cq \sigma_{i,t+1}^2= \{\alpha_i + \gamma_i(\zeta_{it}<0)\}\zeta_{it}^2+\beta_i\sigma^2_{it} 
- $$
- Thus negative $\zeta_{it}$ tend to increase volatility while positive $\zeta_{it}$ have no effect on volatility.  The persistence is 
- $$
-1+\alpha_i+\frac{\gamma_i}{2}+\beta_i
- $$
- assuming $\E\{(\zeta_i<0)\}=1/2$.
-
-\section{Lee--Carter modelling of financial variables}
-
-Suppose $r_t$ is a vector of rate of returns with mean vector $\mu$.   Further suppose the returns are standardised so that over time each has mean zero and standard deviation 1.  Then write
-$$
-\frac{r_{it}-m_i}{s_i}=\beta_i\kappa_t+ \psi_i\eps_{it}\cq \kappa_t= \mu+\sigma_t\eps_t\cq  \eps_t,\eps_{it}\sim N(0,1)\ ,
-$$
-where $\kappa_t$ is normalised so that $\kappa_1=\overline r_1$ and $\kappa_n=\overline r_n$ and
-$$
-\sigma^2_{t+1} = \alpha_0+\alpha_1(\kappa_{t}-\mu)^2+ \beta_0 \sigma_t^2\ .
-$$
-Under the model the variance at time $t$ of the standardised $r_{it}$ is 
-$\beta_i^2 \sigma^2_t + \psi^2_i$ while the covariance between $r_{it}$ and $r_{jt}$ is  $\beta_i\sigma^2_t\beta_j$.
-Hence the squared correlation between $r_{it}$ and $r_{jt}$ is
-$$
-\frac{(\beta_i\sigma^2_t\beta_j)^2}{(\beta_i^2 \sigma^2_t + \psi^2_i)(\beta_j^2 \sigma^2_t + \psi^2_j)} = \left\{\left(1+\frac{\psi^2_i}{\beta_i^2\sigma_t^2}\right)\left(1+\frac{\psi^2_j}{\beta_i^2\sigma_t^2}\right)\right\}^{-1}
-$$
-As $\sigma_t$ becomes large the correlation approaches 1.
-
-\section{Understanding of model}
-\bi
-\i  The observed distribution of $r_{mt}$ outcomes is a reasonable reflection of the (unconditional) marginal distribution at each $t$.
-\i  Hence the $u_{mt}\equiv \P(r_{mt})$ are reasonable uniforms on the basis of the unconditional marginals
-\i  In the standard analysis we use a model describing the conditional distribution at each $t$
-\i  To what extent is $u_{mt}$ the conditional uniform i.e.
-uniforms calculated from the conditional distribution?
-Do we need these.
-Note that $r_{mt}$ can be viewed unconditionally or conditionally.
-i.e.
-the across time distribution of the $r_{mt}$ will be close the unconditional whereas $r_{mt}$ itself is chosen conditionally if we employ a time series model.
-\i  So it appears the computed $u_{mt}$ can be regarded as unconditional.  (just like $r_{mt}$).    However they can also regarded as generated conditionally.  Ditto for $\zeta_{mt}$ etc.
-\i  So suppose we have estimate $\sigma_{mt}$ using a garch model based on either the $r_{mt}$, $\logit \P(r_{mt})$ or $\zeta_{mt}$.
-For the latter this is the conditional variance of $\zeta_{mt}$ i.e.
-$$
-\zeta_{mt}|t-1 \sim N(0,\sigma^2_{mt})
-$$
-\i So at each future $t$ (forecast or smoothed), given $\sigma_{mt}$  we draw $r_{mt}$ or $\zeta_{mt}$, compute $\P(r_{mt})$ or $\Phi(\zeta_{mt})$.
-The former is with respect to the whole distributions whereas the latter is with respect to the normal.
-\ei
-
-\section{ARCH specification}
-   A GARCH(1,1) model stated in terms of noise $\eps_t\sim(0,1)$ and time varying volatility $\sigma_t$:
-$$
-r_t= \mu + \sigma_t\eps_t\cq \sigma^2_{t+1} = \alpha_0+\alpha_1(r_{t}-\mu)^2+ \beta_0 \sigma_t^2\cq \eps_t\sim N(0,1)\ .
-$$
-Here $\mu$ is the average return, assumed independent of time.
-
-Instead of using  actual returns we can consider the zeta transform $\zeta_t=(\Phi^-\circ \P)(r_t-\mu)$
-with 
-\begin{equation}\label{garch}
-\zeta_t=  \sigma_t\eps_t\cq (\sigma^2_{t+1}-1) = \alpha (\sigma^2_{t}-1) + \beta(\zeta_t^2-1)\cq \eps_t\sim N(0,1)\ .
-\end{equation}
-The second equation can be written as
-$$
-\sigma^2_{t+1} = (1-\alpha-\beta) +  \alpha \sigma^2_{t} + \beta \zeta_t^2\ .
-$$
-
-Given the fit, \eref{garch} is simulated forward from $t=n$ to yield $\zeta_{n+1},\zeta_{n+2},\ldots$ and in turn
-$$
-\hat r_{t}=\mu+(\P^-\circ \Phi)(\zeta_{t})\cq t=n+1,n+2,\ldots\ .
-$$
-The inverse $\P^-$ is  with respect to the empirical distribution, or some modified version of the same  (a stressed version?)
-
-Now take the $u_{mt} = \Phi(\zeta_t)$ and the copulas $C(u_{it},u_{mt})$.   The copula can be the empirical copula or some smoothed version of the same.   Then 
-$$
-\hat r_{it} = \mu_i + \P^-(u_{it})\cq u_{it}\sim C(u_{it}|u_{mt}) \cq t=n+1,n+2,\ldots\ .
-$$
-Again, $\P^-$ is with respect to the past distribution of returns $r_{it}$ or some modified version of the same.
-With the PG model the $\zeta_{it}$ are chosen given $\zeta_t$ and hence the relation becomes
-$$
-\hat r_{it} = \mu_i + (\P^-\circ\Phi)(\zeta_{it})\cq \zeta_{it}\sim \mathrm{PG}(\zeta_{it}|\zeta_{mt}) \cq t=n+1,n+2,\ldots\ .
-$$
-If returns are jointly normal this model reduces to the usual normal modelling.
-
-In terms of this setup:
-\bi
-\i Future market returns are generated in terms of an ARCH model stated in terms of the zeta transform
-\i Relationships (i.e. systemic risk) inherent in other returns are stated in terms of a PG copula
-\i Stressing is achieved in terms of stressing $\P_m$.
-\ei
-
-suggesting that in an unconstrained fit the coefficients should add to 1.
-$$
-r_{mt}=(F_m^-\circ\Phi)(\sigma_t\eps_t)
-$$
-Since $\E(z_t^2)=1$ and $\alpha<1$, then in the long run $\sigma^2_t\rightarrow 1$.
-If $z_t$ is in either tail and hence $z_t^2$ is far from  1 then $\sigma^2_{t+1}$ is much bigger than 1 and $z_{t+1}$ will be in the tail.
-Then
-\be{forward}
-r_{it}=F_i^-(u_{it})\cq u_{it}\sim C\{u_{it}|\Phi(z_t)\}
-\ee
-Thus volatility clustering occurs since $z_t$ in one or tail, drives, via the copula, both $r_{it}$ and $r_{jt}$ into the tail.
-
-Steps in fitting:
-\begin{enumerate}
-\i  An ARCH model is fit to the market return $z_t=(\Phi^-\circ F_m)(r_{mt})$ where $F_m$ is the empirical distribution of the market rates
-\i  The $z_t$ is simulated forward from time $t=n$ using the ARCH model. 
-\i  Retain only those forward simulations such that the cumulative drop $\prod_{t=n+1}^N\{1+(F_m^-\circ \Phi)(z_t)\}$ is less than the crisis drop.
-\i  For each forward simulated value, chose $r_{it}$ using the conditional copula and simulation smoothing
-\i Calculate the capital shortfall for firm $i$.
-\end{enumerate}
-
-The rationale is that  $(y_{t}-\mu)^2$ is the latest available estimate of the variance at time $t$ and this latest   estimate is combined with the  ``permanent" component $\sigma^2_{t}$.
-Constraints  are required on $a_0$, $a_1$ and $b_1$ to ensure $\sigma_t$ stays positive and finite.
-If  $a_1=b_1=0$ then $y_t$ is noise with mean $\mu$.
-
-In our case $y_t=z_t$ is standard normal so we can drop $\mu$ to get
-$$
-z_t=  \sigma_t\eps_t\cq \sigma^2_{t+1} = a_0+a_1 \sigma^2_{t} + b_1z_t^2\ .
-$$
-
-Fitting GARCH models with R.  The  command $garch(y,c(1,1))$ fits  model $garch$ to $y$.  The $garch$ command requires $library(tseries)$.
-
-The quantity $a_0/(1-a_1-b_1)$ is the long run average $\sigma^2_t$ since it is the constant solution to the right hand side equation \eref{garch}, if  $(y_t-\mu)^2$ is replaced by its expectation.
-We want the long run average to be 1 implying
-$
-a_0=1-a_1-b_1
-$ and hence
-$$
-z_t=  \sigma_t\eps_t\cq \sigma^2_{t+1} = a_0+a_1 \sigma^2_{t} + (1-a_0-a_1)z_t^2\ .
-$$
-$$
-z_t=  \sigma_t\eps_t\cq (\sigma^2_{t+1}-1) = a_1 (\sigma^2_{t}-1) + (1-a_0-a_1)(z_t^2-1)\ .
-$$
-
- \fref{fig7} displays output from fitting a GARCH model to the daily percentage returns of the FTSE index plotted in \fref{fig6}.
-In this fit  $\mu$ is set to the sample mean return, $\hat a_1=0.045$ indicates moderate autocorrelation in the standard deviation while $\hat b_1= 0.942$ indicates high reaction to the latest volatility $(y_t-\mu)^2$.
-The long run average standard deviation is $\sqrt{0.009/(1-0.045-0.942)}=0.825$, marginally above the empirical standard deviation of 0.796.
-The  standard errors of the coefficients are 0.003, 0.007 and 0.010, respectively for $a_0$, $a_1$ and $b_1$.
-These are available using the $vcov(r)$ where $r$ contains the results of the $garch$ command.
-Hence all three coefficients are significant.
-
-GARCH stands for generalized ARCH where the latter stands for autoregressive conditional heteroskedasticity.
-GARCH(1,1) indicates one lag in both the $\sigma_t^2$ and $(y_t-\mu)^2$ terms.
-The GARCH($p,q$) model extends this to $p$ and $q$ lags.
-The  ARCH($q$) model contains only lags in $(y_{t}-\mu_t)^2$  and hence is GARCH($0,q$).
-
-Estimating GARCH models is similar to ARMA models.
-For any set of $a$ and $b$ parameters as well as starting conditions,  $y_0$ and $\sigma_0$,   the GARCH equation for $\sigma_t^2$  is used to recursively calculate $(y_t-\hat y_{t})/\sigma_t$.
-These standardised errors, as well as related information,  are combined to evaluate the normal based likelihood.
-The likelihood is maximised  with respect to the unknown parameters using a numerical search.
-
-Forecasting future volatility with  a GARCH model consists of iterating the $\sigma_t^2$ equation \eref{garch} forward from the latest available time point $t=n$.
-In this iteration, future $(y_t-\mu_t)^2$ are replaced by their latest conditional expectation.
-
-\section{Partially Gaussian copulas}
-
-Suppose $(u,v)=F_*(x,y)$  where $x$ and $y$ are scalar random variables.
-Suppose $0<u_1<\cdots<u_n<1$  are   ordered observed values of $u$ and $q_j=\Phi^-(u_j)$, $t=1,\ldots,n$.
-The correspondingly ordered values of $v$ and $z=\Phi^-(v)$ are denoted $v_j$ and $z_j$.
-Note $\Ex(z_j)=\Ex(q_j)=0$ and $\Ex(z^2_j)=\Ex(q^2_j)=1$ where $\Ex$  is the empirical mean.
-
-Smoothing methods are here proposed to smooth and simulate $y$ values  using a copula on $(u,v)$ constructed via    a cubic spline model linking $u$ to $z$.
-Of particular concern are simulated $z$ when $u$ is  near $0$ or $1$ corresponding to  $x$ extremes.
-Given a simulated $u$ and in turn $z$, $(x,y)=F^-_*\{u,\Phi(z)\}$, a draw from the joint.
-Constraining $u$ draws to say the upper tail, yields corresponding upper tail values for $y$.
-The challenge is to produce cogent $z$'s or $y$'s that properly reflect dependence in different parts of the distribution unencumbered by inappropriate constraints, and in particular tail constraints, inherent in say the Gaussian copula setup.
-Practical methods admit fitting on the basis of observed data, and testing procedures for  departures or otherwise from Gaussianity.
-The method outlined below achieves this.
-
-\begin{comment}
-   The simulation singles out independent and dependent variables.
-Which should be which?
-If $x$ and $y$ are actual time series the simulation $(x_j,\hat y_j)$ is ordered back into the original time series order.
-\end{comment}
-
-The partially Gaussian  (PG) copula for $(u,v)$ is stated in terms of  $q\equiv\Phi^-(u)$ and $z\equiv\Phi^-(v)$ on the grid   $u_j=j/(n+1)$, $j=1,\ldots,n$ with 
-\be{cusp}
-z_j = \alpha_j+\beta q_j+ sh_j\eps_j\cq \alpha_{j+1}=\alpha_j +\delta_j+c\eta_j\cq \delta_{t+1}=\delta_j+\eta_j\ .
-\ee
-Here $\eps_j$ and $\eta_j$ are serially and contemporaneously uncorrelated zero mean disturbances with common variance $\sigma^2$ and $c=3-\sqrt 3$.
-The  $q_j$ term is the   Gaussian component and  $\alpha_j$ a nonparametric deviation.
-
-The parameter $s$ controls overall smoothness while  $h_j\ge 0$,  controlling the variability at different $t$ determines local smoothness.
-In particular if $s=0$ then the signal $\alpha_j+\beta q_j$ is forced to reproduce every  $z_j$ while $h_j=0$ implies reproduction at the particular $t$.
-If $h_j$ is large then little notice is taken of $z_j$ and the fitted signal at $t$ is relatively smooth.
-Thus $s$ controls overall smoothness of the signal and  $h_j$ the smoothness at a particular $t$.
-Comparability between models and fits is facilitated by normalising $h_j>0$ such that the average  is 1.
-
-The Gaussian copula is where $\alpha_j$ and $h_j$ are  identically 0 and  1, respectively, implying  $(z_j,q_j)$ with $t$ uniform on $1,\ldots,n$  is bivariate normal  with correlation $\beta=\pm\sqrt{1-(s\sigma)^2}\equiv\rho$.
-
-The starting condition for the recursion in \eref{cusp} are the second two equations with $t=0$ and where $\alpha_0$ and $\delta_0$ are  unknown parameters, similar to $\beta$.
-If $s\rightarrow\infty$ then $\sigma\rightarrow 0$,  $(\alpha_j,\delta_j)\rightarrow 0$ for $t=0,\ldots n$, and \eref{cusp} describes a Gaussian copula.
-
-The function $\alpha_j$ is thought of as an intercept function and provides for a nonparametric extension to the Gaussian copula.
-If $\sigma\rightarrow 0$, equivalent to $s\rightarrow\infty$,  the first equation in \eref{cusp} is
-$
-z_j = \alpha_0+\delta_0 t + \beta q_j + s\eps_j
-$
-and  $\beta=\rho$ if $\alpha_0=\delta_0=0$.
-Model \eref{cusp} with  $\beta=0$ is the  nonparametric model since $z_j$ is varies smoothly with $t$, unrelated to $q_j$.
-If $\beta=0$ and $\sigma\rightarrow 0$ there is a probit relationship between $z_j$ and $u_j$.
-Finally $s=0$ implies $\alpha_j+\beta q_j=z_j$ for any $\beta$.
-The full range of possibilities is set out in \tref{pg} discussed in more detail below.
-
-The $\alpha_j=0$ and $\alpha_j=\alpha_0+\delta_0 t$ specifications are generalised by supposing $\alpha_j$ is twice differentiable and minimising
-\be{spline}
- \sum_{t=1}^n\left(\frac{z_j-\alpha_j-\beta q_j}{h_j}\right)^2 + s^2\int_{-\infty}^{\infty} \left(\alpha_j''\right)^2\de t\ .
-\ee
-with respect to $\alpha_j$ and $\beta$.
- In \eref{spline} the $h_j$  are fitting weights: a large  $h_j$ implies  error at $t$ is largely ignored while a small $h_j$ implies  error at $t$ is  minimized at all cost.
-The function $a_j$ and scalar $b$ minimising \eref{spline} deliver a function $a_j+bq_j$ where $a_j$ is piecewise twice differentiable and $a_j+bq_j$ passes closest to, in a mean square error sense, to $z_j$  with a penalty $s^2$ for  roughness measured in terms of the second derivative.
-At the minimum, the first term in \eref{spline} is $(s\sigma)^2$.
-\cite{Brown&DeJong:2001} demonstrate the equivalence of \eref{cusp} and \eref{spline}.
-
-The  function $\alpha_j$ minimising \eref{spline}  is, at integer $t$,  $a_j=\E(\alpha_j|z_1,\ldots,z_n)$  computed with \eref{cusp} where $\eps_j$ and $\eta_j$ are normal, 0 mean, variance $\sigma^2$ random variables and $q_j$ fixed.
-Between integer $t$,  the  minimum is quadratic in $t$.
-A useful feature is that $\beta$ is simultaneously estimated alongside $a_j$ as the generalised least squares estimate under \eref{cusp}.
-All calculations under \eref{cusp} provide error covariance matrices as detailed and applied below.
-
-\section{Special cases of the PG model}
-
-Special cases of  \eref{cusp}  are displayed in \tref{pg}.
-In \eref{cusp}, if $s\rightarrow\infty$ then $\sigma\rightarrow 0$   since the variance of $z_j$ is finite.
-Thus $s\rightarrow\infty$  implies the noise to signal ratio becomes large where noise refers to   $s\eps_j$ and signal to $\eta_j$, the error term driving  the smooth component $\alpha_j$.
-As the noise to signal ratio $s$ increases, less of the variation in $z_j$ is explained by $\alpha_j$.
-In the limit $\sigma$ is zero implying $\alpha_j=\alpha_0+\delta_0 t$, as straight line.
-The further restriction $\alpha_0=\delta_0=0$ forces $\alpha_j$ identically zero.
-
-The first row in \tref{pg} is the  Gaussian copula.
-In this setup $\alpha_j$ is identically zero: there is no  signal component.
-The additional restriction $\beta=0$ eliminates the Gaussian component $q_j$.
-Co (or counter) monotonicity results in the Gaussian framework if $\rho=\pm 1$ as displayed in the third row.
-If $s= 0$ then there is no measurement noise and the combined signal $\alpha_j+\beta q_j$ must pass through the points $z_j$ resulting in a perfect fit.
-In terms of \eref{spline}, $s=0$ implies there is no roughness penalty and hence the minimisation is solely focussed on minimising the first, squared error, term, achieved  by setting $\alpha_j+\beta q_j=z_j$.
-
- \begin{table}[htdp]
-\caption{Special cases of the PG copula; in all cases $\rho\equiv\pm\sqrt{1-(s\sigma)^2}$}\label{pg}
-\begin{center}
-\begin{tabular}{l|c|ccccc|l}
-\hline
-case& $\alpha_j$ & $\beta$ &$s$ & $\sigma$ & $\alpha_0$&$\delta_0$  & other\\
-\hline
-Gaussian & 0 &  & $\infty$ & $0$&  0&0 &$\rho=\beta$\\
-independence &  0 & 0 & $\infty$&0 & 0 &0 &$\rho=0$\\
-$\pm$comonotonic  & 0 &$\pm 1$ &0 & 0 &0 & 0 &$z_j=\pm q_j$  \\
-empirical  & $z_j$ &  & $0$  &  &   &  &$\rho=1$ \\ 
-linear probit &$\alpha_0(1-2u_j)$&  0 &  $\infty$ &0& & $\frac{-2\alpha_0}{n+1}$ &indep. if $\alpha_0=0$\\
-nonparametric & $\E(z_j|u_j)$  & 0 & & & &  & non Gaussian \\
-PG & $\E(z_j-\beta q_j|u_j)$ & & & & & &  \\
-\hline
-\end{tabular}
-\end{center}
-\end{table}%
-
-The linear probit row in \tref{pg}  eliminates the Gaussian component $q_j$ by setting $\beta=0$, and giving maximum penalty for rougness.
-The resulting prediction  is a straight line $\hat z_j=\alpha_0+\delta_0 t$.
-However the mean of the $z_j$ and hence $\hat z_j$ is zero implying $0=\alpha_0 + \delta_0(n+1)/2$.
-Solving for $\delta_0$ gives the $\delta_0$ constraint displayed in \tref{pg} and the resulting straight line signal $\alpha_j$.
-
-The bottom row of \tref{pg} displays the general partial Gaussian specification absent  any constraints on the parameters.
-Eliminating the Gaussian component from the signal by setting $\beta=0$ leads to the nonparametric, non Gaussian specification in the second last row of \tref{pg}.
-
-\section{Assessing goodness of fit}
-
-A plot of $a_j+b q_j$ versus $r q_j$ is useful for assessing Gaussianity -- that is whether the copula  is Gaussian.
-If $a_j+bq_j\approx rq_j$ then the quantiles predicted under the G and PG models are approximately the same and  a 45 degree line plot suggests a Gaussian copula is adequate.
-This analog of the qq--plot is converted to the pp--plot analog  by transforming each coordinate using $\Phi$.
-Using the inverse marginal distribution of each of the variables displays the copula fit information in the original scale.
-
-For the Gaussian copula the single parameter is $0\le\rho\le 1$, estimated by  $r$.
-The analogous estimate for the PG copula is $R=\pm\sqrt{1-(s\hat\sigma)^2}$ signed according to $b$.
-A measure of the  contribution of the nonparametric component $\alpha_j$  to the PG fit is
-$
-R^2-r^2 = 1-r^2 - (s\hat\sigma)^2
-$.
-A more formal analysis is based on the log--likelihood where in $\eref{cusp}$ the disturbance terms $\eps_j$ and $\eta_j$ are assumed normally distributed.
-Then  minus twice the log--likelihood\footnote{This is the log--likelihood $z_j\sim N(\rho q_j,1-\rho^2)$ and differs from the bivariate Gaussian log--likelihood.
-It appears  as  $s\rightarrow\infty$, $s\hat\sigma\rightarrow\sqrt{ 1-b^2}$ and so the G copula appears enforced.}  of the Gaussian and  PG model  are computed and their difference compared to a chi--squared distribution with 2 degrees of freedom for significance.
-
-Local  measures of departure from Gaussianity are 
-\be{lr}
-\frac{z_j-r q_j}{h_j\sqrt{1-r^2}}\cq \frac{z_j-a_j-bq_j}{ s\hat\sigma h_j}\ .
-\ee
-The  standardised residuals
-provide insight into areas of lack of fit, with mean and standard deviation, across $t$,  of 0 and 1, respectively.
-
-\section{Tuning PG to particular parts of the joint distribution}
-The function $h_j$ is used to assign  importance to parts of the joint of distribution.
-If all parts are equally important then $h_j=1$ for all $t$.
-If $h_j\approx 0$ when $t\approx n$ then fidelity  is enforced in the upper tail.
-Alternatively if $h_j\approx 0$ for $t\approx n/2$ then there is an attempt to accurately reproduce $z_j$ in the middle of the distribution with smoothness  in both tails.
-\section{Overall and local correlation}
-
-\cite{bjerve1993correlation} state ``The local regression slope, which focuses on change in expected $y$ as $x$ changes, may be of greater interest than expected  $y$ for a given $x$." They go on to argue for  a  ``scale--free standardised version of the local regression slope."\footnote{The scale free feature conflicts with the calculations below where  slope differs according to whether it is with respect to $t$ compared to $q_j$.
-Hence the noise terms must also be affected by the transformation in a way not apparent in the expressions below.} In terms of the current notation, their suggested measure is
-\be{rhot}
- \rho_t\equiv\pm\left\{1+\left(\frac{\psi_t}{s\sigma h_t}\right)^{-2}\right\}^{-\frac{1}{2}}\ ,
-\ee
-where $s$, $\sigma$ and $h_t$ are as in \eref{cusp} or \eref{spline} and $\psi_t$ is the regression slope at $t$ as set out below.
-The ratio $\psi_t/(s\sigma h_t)$ is a signal to noise ratio and a high value implies $\rho_t\approx \pm 1$.
-In general the signal  $\psi_t$ is the local slope of the relationship while $s\sigma h_t$ is a measure of local noise.
-The sign of $\rho_t$ is discussed in the context of particular choices of signal $\psi_t$.
-
-With the Gaussian copula 
-$$
-z_t=\beta q_t + (\sqrt{1-\rho^2})\varepsilon_t\cq \eps_t\sim N(0,1)\ .
-$$
-In this  case the nonparametric component $\alpha_t$ is absent.
-The slope with respect to $q_t$ is constant $\psi_t=\beta=\rho$ as is the noise variance: $s\sigma h_t=\sqrt{1-\rho^2}$.
-Further  \eref{rhot} reduces to $\rho_t=\rho$ for all $t$.
-The Gaussian copula case is displayed in the first row of the of \tref{corr}.
-
-\begin{table}[htdp]
-\caption{Overall and local correlations.  In all cases $R=\sqrt{1-\Ex\{(z_t-\hat z_t)^2\}}$}\label{corr}
-\begin{center}
-\begin{tabular}{l|ccc|l}
-\hline
-case & $\psi_t$ & $q_t$ & $\alpha_t$ & estimates\\
-\hline\hline
-Gaussian & & & \\
--- overall,  local &$\rho=\beta$ &$\checkmark$& $\times$ & $r=\Ex(z_tq_t)$ \\
-\hline
-nonparametric & & & \\
--- overall &$\rho$ &$\times$ & $\checkmark$& $r$ from $\widehat{\mathrm{PG}}(\beta=0)$\\
--- local  &$n\phi(q_t)\delta_t$ &$\times$ & $\checkmark$& $\hat\delta_t$ from $\widehat{\mathrm{PG}}(\beta=0)$\\
-\hline
-PG & & & \\
--- overall & $\rho$ & $\checkmark$& $\checkmark$& $r$ from $\widehat{\mathrm{PG}}$ \\
--- local & $n\phi(q_t)\delta_t+\beta$&$\checkmark$& $\checkmark$&$\hat\beta$, $\hat\delta_t$ from $\widehat{\mathrm{PG}}$  \\
-\hline\hline
-\end{tabular}
-\end{center}
-\end{table}%
-
-The second set of row in \tref{corr} is the nonparametric Gaussian copula where, in \eref{cusp},  $\beta=0$.
-Hence $q_t$ is removed and  the relationship between $z_t$ and $t$ or $u_t$ is  modelled in terms of the  nonparametric component $\alpha_t$.
-The   slope $\alpha_{t+1}-\alpha_t$  at  $t$ is, apart from error,
-$\delta_t$.   However $\delta_t$ is the slope with respect to $t$ and required is the slope with respect to $q_t$:
-\be{normslope}
-\psi_t=\frac{\de \alpha_t}{\de q_t} = \left( \frac{\de u}{\de t}\frac{\de q_t}{\de u}\right)^{-1}\frac{\de \alpha_t}{\de t}  \approx
-\left\{\frac{1}{n\phi(q_t)}\right\}^{-1}\delta_t  = n\delta_t\phi(q_t)\ ,
-\ee
-where $\phi$ is the standard normal density.
-
-The final set of rows in \tref{corr} deals with the general PG case.
-As in the other situations, the overall correlation $\rho$ is derived from the overall fit.
-The overall correlation exceeds that derived from both the specialised Gaussian and nonparametric cases.
-The higher overall correlation is partialed out locally according to both nonparametric and parametric components.
-In any PG fit $\hat\beta$ will differ from the Gaussian copula estimate $\Ex(z_tq_t)$.
-
-If $s=0$ then $s\eps_t=0$  and  the signal to noise ratio is infinite implying $\rho_t=1$ for all $t$.
-Thus the empirical and comonotonic cases imply, as expected,  $\rho_t=\pm 1$.
-With the linear probit model $\sigma=0$ and $\alpha_t=\alpha_0(1-2u_t)$ with slope with respect to $u_t$ of $-2\alpha_0$ and
-\be{normslope2}
-\psi_t =  \left( \frac{\de q_t}{\de u_t}\right)^{-1}\frac{\de \alpha_t}{\de u_t}  =
- -2\alpha_0\phi(q_t)\cq  \rho_t\equiv\pm\left[1+\left\{\frac{2\alpha_0\phi(q_t)}{s\sigma h_t}\right\}^{-2}\right]^{-\frac{1}{2}}\ ,
-\ee
-If $h_t$ is constant then  local correlation is  highest if  $q_t=0$ and monotonically declines towards zero as $q_t$ moves away from zero.
-
-The above $\psi_t$ and implied correlations are for the $(q,z)$ scale.
-However the local correlations also apply on the $(u,v)$ scale since the transformation from $u$ to $q$ and $v$ to $z$ are the same inverse normal probability transform and slopes are identical\footnote{This also follows since local correlation is independent of scale.}
-$$
-\frac{\de v}{\de u} =\left(\frac{\de z}{\de v}\right)^{-1} \frac{\de z}{\de q} \frac{\de q}{\de u} = \frac{\de z}{\de q}\ .
-$$ 
-\section{Simulating from the PG copula}
-
-To explain PG simulation, consider initially  the Gaussian model.   Given data $(q_t,z_t)$, $t=1,\ldots,n$ where
-$q_t=\Phi(u_t)$ and $u_t=t/(n+1)$ suppose 
-\be{rhohat}
-\tilde z_i\sim N(r \tilde q_i,1-r^2)\cq r=\Ex(z_tq_t) = \E(\rho|  z)\cq \tilde q_i\sim N(0,1)\ ,
-\ee
-where $z\equiv(z_1,\ldots,z_n)$ contains the observed values of $z_t$.
-Simulating $\tilde q_i$ multiple times produces multiple $\tilde z_i$ while $r$  remains fixed.
-To ensure  coverage, $\tilde q_i=q_i$,  $i=1,\ldots, n$.
-The  $n$ pairs $(u_i, \tilde v_i)$ where $\tilde v_i=\Phi(\tilde z_i)$, $i=1,\ldots,n$  provide $n$ independent draws with   uniform  empirical distribution for the $u_i$ and approximately uniform empirical distribution for the $\tilde v_i$.
-Repeatedly cycling over $i=1,\ldots,n$  produces an unlimited supply of  draws.
-
-The PG generalisation of \eref{rhohat} is to repeatedly cycle over  $i=1,\ldots,n$ with 
-\be{rhohat2}
-\tilde z_i\sim N(a_i+bq_i, s^2\hat\sigma^2)\ , \ \ \ \  a_i=\E(\alpha_i|  z)\ , \ \ \ \ b=\E(\beta|  z)\ .
-\ee
-The $a_i\equiv\E(\alpha_i|z)$ and $b\equiv\E(\beta|z)$ and estimate of $\sigma$ are calculated with the Kalman Filter Smoother (KFS)  \citep{DeJong:91a} while $s$ is set to achieve desired smoothness.
-Alternatively $s$ is estimated as discussed in \sref{xx}.
-In  \eref{rho2} the $a_i$, $q_i$  and $b$ remain fixed across cycles, analogous to fixing $r$  in the  Gaussian copula simulation.
-If $a_i=0$ for all $i$ then \eref{rhohat2} reduces to \eref{rhohat} since in this case $b=r$ and $s^2\hat\sigma^2=1-r^2$.
-
-Iterations \eref{rhohat} and \eref{rhohat2}  ignore  estimation variability in $r$ or $a_i$ and $b$.  This shortcoming is addressed by varying  $a_i$ and $b$  across  each cycle 
-$$
-\tilde a_i \sim N\{a_i,\cov(\alpha_i|  z)\}\cq i=1,\ldots,n\cq  \tilde b\sim N\{b,\cov(\beta|  z)\}\ ,
-$$
-and using these  in the first relation of \eref{rhohat2}  instead of $a_i$ and $b$.
-The conditional covariance matrices are recursively calculated  with the KFS alongside $a$ and $b$, while consistent  draws  across $i$  are made with the 
-simulation smoother extension  \citep{DeJong&Shephard:95}.
-
-\section{Ordering}
-
-Suppose $z_{xt}$ is the percentile based z--score of series $x$ at index $t$.
-In this section two common indexes are discussed:   time $t$ and ordering with respect to some other variable.
-A first order approximation is $z_{xt} = \beta_xq_t + \eps_{xt}$ or in vector form $z_t=\beta q_t + \eps_t$ where $z_t$, $b$ and $\eps_t$ are vectors and $q_t$ scalar.
-For the Gaussian copula $\beta=\rho$.
-
-\section{Factor PG copula model}
-
-The PG  model is stated in terms of  $q_t=\Phi^-(u_t)$ where $u_t=t/(n+1)$, $t=1,\ldots,n$.
-The  role of $x$  is to order $z$:  the variable $x$ is permuted  and $z$ is permuted using the same permutation.
-This suggests using a composite variable for ordering.
-
-For example suppose $x_t$ is a vector of variables initially ordered in terms of time $t$.
-The associated percentile based z--scores  are   $z_t= (\Phi^{-1}\circ \P) x_t$ where $\P$ is the generic percentile operator.\footnote{A final adjustment is made to ensure the z--scores have mean zero and variance 1.}   Write $z_t=Uc_t$ where $(c_1,\ldots,c_n)=DV'$ derived from the singular decomposition $UDV'=(z_1,\ldots,z_n)$ arranged so that the singular values in the diagonal matrix $D$ are in decreasing order.
-Use the first component in $c_t$, corresponding to the largest singular value,  to permute $x_1,\ldots,x_n$ and fit PG copulas
-$$
-x_t = \alpha_t + \beta q_t + sh_t\eps_t\ ,
-$$
-where $\alpha_t$ and $\beta$ are vectors and $h_t$ is a diagonal matrix.
-The components of $\alpha_t$ are individual departures from the Gaussian component and $\beta\beta'$ models the joint Gaussian structure.
-
-Suppose $y_t$ is a $p$--vector with components $y_{it}$, $i=1,\ldots,p$ with $y_t$ is observed for $t=1,\ldots n$.
-Suppose each component series in $y_t$ is ordered according to $x_t$, a scalar series observed or inferred along with the $y_{it}$.
-Without loss of generality assume $y_t$, $t=1,\ldots,n$ denotes the component series after ordering with respect to $x_t$ and define $v_t$ and $z_t$ from the componentwise ordered $y_t$ as, for $t=1,\ldots,n$,
-$$
-z_t = \Phi^-_*(v_t)\cq v_t = F_*(y_t)\cq q_t=\Phi^-(u_t)\cq u_t=\frac{t}{n+1}\ .
-$$
-Using this notation the factor PG model is as in \eref{cusp} except that $z_t$, $\alpha_t$, $\beta$ and $\eps_t$ are vector and $h_t$ is a diagonal matrix.
-The diagonal matrix $h_t$ distributes the quantum of error $\sigma$  across component series $i$ and percentiles $t$.
-The matrix $h_t$ is standardised such that $1'h_t1=p$.
-Further $\alpha_t$ is formed as in the second and third equations in \eref{cusp} expect that both $\alpha_t$ and $\delta_t$ are vector.
-More specific structure is:
-\begin{itemize}
-\item   If all components of $\alpha_t$ are identical then  $\alpha_t$ is written as $1\alpha_t$ where in the last expression $\alpha_t$ is scalar.
-In this formulation deviations from Gaussianity are the same for each series.
-This is testable in the current framework.
-\item If all components of $\beta$ are the same then  $\beta$ is written as $1\beta$ where $\beta$ is scalar.
-In this case all components in $z_t$ respond in the same way to the Gaussian component $q_t$ but deviations may occur.
-\item A generalisation is where $z_t=B_t\alpha_t + Q_t\beta + sh_t\eps_t$.
-
-\end{itemize}
-
-Replacing $1\alpha_t$ in \eref{cusp} by a vector  $\alpha_t$ and making $s\sigma$ component specific  yields the PG model.
-Variants include forcing  a common response to $q_t$ by requiring  $\beta$ to be scalar.
-
-The one--factor PG model is estimated in the same way as the PG model, using vector $z_t$.
-In practice $x_t$, the scalar variable serving to order the components of $y_t$, is either an external driver or a composition from $y_t$.
-At present $q_t$ is structured in terms of the normal score derived from the percentile of $x_t$.
-More extreme tail behavior is modelled by  for example replacing the normal score $q_t$ by say $\chi_t$ the chi--squared score derived from the percentile.
-This is explained in detail in the next section.
-
-\section{Extreme tail copulas}
-
-\section{Below here is review/junk}
-
-\subsection{A  model for monitoring slope}
-Suppose
-\be{slope}
-y_t = \beta m_t + \mu_t + s\eps_t\cq \mu_{t+1} = \mu_{t-h+1} + hr_t + c\eta_t \cq r_{t+1}=r_t + \eta_t\ ,
-\ee
-where $y_t$ is a stock price,  $m_t$ is a market index, $\mu_t$ is the price level and $r_t$ is the return per period and $h$ is a positive  integer.
-Note $r_t$ measures  the expected  per period change in the level $\mu_t$.
-Thus
-
-\subsection{Kelly criterion}
-
-Suppose $r$ is a vector of stock returns with mean $\mu$ and covariance matrix $C$.
-Suppose proportion $\pi_i$ of total wealth $w$  is invested in stock $i$.
-Then the rate of return on the portfolio is
-$ \pi'r$.   The expected  log wealth after one period   is 
-$$
-\E[\ln \{w(1+\pi' r)\}] \approx \ln(w) + \pi'\E(r) -\frac{\pi'\E(rr')\pi}{2} =  \ln(w) + \pi'\mu -\frac{\pi'(C+\mu\mu')\pi}{2}\ .
-$$ 
-To maximise log wealth (and hence wealth), maximise this expression with respect to $\pi$.   Setting up the Lagrangian, differentiating and equating to zero yields 
-$$
-\pi = (C+\mu\mu' - \lambda I)^{-1}\mu\cq 1'\pi=1\ .
-$$
-Given the optimal $\pi$ the growth rate is 
-$$
-\E\ln(1+\pi'r) \approx \mu'(C+\mu\mu' - \lambda I)^{-1}\mu - \frac{\mu'(C+\mu\mu' - \lambda I)^{-1}}{2}
-$$
-
-The factor $1+\pi'r$ is the growth factor.   Over $n$ periods the growth factor is
-$$
-\e^{\ln(1+\pi'r_1)+\ln(1+\pi'r_2)+\cdots \ln(1+\pi'r_n)} \rightarrow \e^{n\E\ln(1+ \pi'r_t)} = \e^{nm}
-$$
-where $r_t\sim(\mu,C)$ are the vectors of growth rates for each period and $\pi$ is the fixed allocation.   Hence the rate of growth is
-$$
-m=\E\ln(1+\pi'r_t) 
-$$
-
-\subsection{Continuous formulation}
-For a single stock we have $\de s/s = \mu\de t + \sigma\de b$ where $b$ is brownian motion.  Alternatively 
-$\de s=\mu s\de t + \sigma s\de b$.    For a portfolio $\pi$ of stocks this becomes
-$$
-\frac{\pi'\de s}{\pi s} =\pi'\mu\de t + \pi'\de b
-$$
-$$
-\pi=-C^{-1}(1r_f-\mu)
-$$
-Note $C^{-1}(r-\mu)$ is the standardised prediction error when predicting each component of $r$ using all the other components and supposing $r$ is realised.
-Since $\mu>1r_f$,  outcomes $r=1r_f$ are downside surprises.
-Thus  $\pi$ is the negative of the standardised prediction error when predicting each component of $r$ using all other components and assuming the downside surprise $r=1r_f$.
-A high value $\pi_i$ occurs if  there is huge downside surprise if $r_i=r_f$   when all other components  downward surprise at  $r_f$.
-Hence the Kelly criterion loads the portfolio with stocks $i$ which have  large downward surprise at $r_i=r_f$ if all other stocks downward surprise with outcomes $r_f$.
-
-\subsection{Markowitz}
-
-Suppose we wish to maximise the expected return $\pi'\mu$ subject to a constraint on the volatility, $\pi'C\pi\le c$.  Then the Lagrangian is 
-$\pi'\mu +\lambda (c-\pi'C\pi)$.   Differentiating and equating to zero yields the first order conditions
-$$
-\mu = 2\lambda C\pi\qquad \Rightarrow\qquad \pi = \frac{1}{2\lambda} C^{-1}\mu 
-$$
-where $\lambda$ is chosen so that $\pi'C\pi=c$.
-
- If $C=c11'$ then
-
-To maximise the expected growth rate requires $\pi$ to be chosen as above.  Can we write a SSM for this?
-$$
-1=1'\pi\cq s_t=1\mu + r_t + \eps_t 
-$$
-
-Multiplying the first equation by $1'$ yields
-$$
-\pi=n\le \cq\lambda=n1'\mu - n1'(C+\mu\mu')\pi\cq  
-$$
-$$
-\mu = (C+\mu\mu')\pi\qquad\Rightarrow\qquad \pi=(C+\mu\mu')^{-1}\mu
-$$
-Maximising the expected log--accumulation yields the first order conditions
-$
-\E(r_t) = \E(r_tr_t')\pi
-$ or $\pi=\{\E(r_tr_t')\}^{-1}\E(r_t)$.  If one the components of $r_t$ is constant (the risk free rate of return $\delta$ say), then (using partitioned inverses)
-$$
-\pi = \{\cov(r_t)\}^{-1}\{\E(r_t)-\delta 1)\ .
-$$
-
-\subsection{\cite{bjerve1993correlation} review}
-\begin{enumerate}
-\item  Points out $\cov(z|t=t^*)\ne 0$  while $\cov\{\E(z)|t=t^*\}=0$.
-So cannot form a correlation from the variation at $t$ compared to the variation in the mean -- there is no variation in the latter.
-\item  Conditioning $t$ on a neighbourhood of $t^*$ and calculating the correlation in neighbourhood will lead to low correlation even if relationship is strong.  Not sure I understand this.
-\item  Distinguishes between $\cov\{\E(z|t)\}/\cov(z)$ as a measure of correlation and ordinary correlation.  The former he calls Pearson correlation while Gallton--Pearson is the usual correlation.
-\item  States that to the first order  both correlations are such that
-$$
-\cor\{z,t|t\in N_h(t^*)\}=\frac{h\beta_{t^*}}{\sqrt 3\sigma_{t^*}}
-$$
-where $\beta_t$ is the local regression and $\sigma_t$ the local residual? variation.
-\item Then considered is
-$$
-\xi_{t^*} = \lim_{h \rightarrow 0}\frac{\cor\{z,t|t\in N(t^*)\}}{h/\sqrt 3} = \frac{\beta_{t^*}}{\sigma_{t^*}}
-$$
-that is the local slope devided by the local standard deviation.  Note I  assume the overall correlation is 1 and so $\sigma_1$ does not appear in the numerator.
-\item  Maps $\xi_{t^*}$ into the unit interval
-$$
-\rho_{t^*}= \pm\left(1+\xi^{-2}_{t^*}\right)^{-\frac{1}{2}}= \pm\left(1+\frac{\sigma^2_{t^*}}{\beta^2_{t^*}}\right)^{-\frac{1}{2}}\ ,
-$$
-
-\end{enumerate}
-
-\section{Fitting PG copulas}
- The PG is readily  fit to percentile data, and provides a practical platform for copula simulation.
-This is discussed, implemented, and used in subsequent sections.
-The  parameters defining a PG copula are $s$, $\beta$,  $\sigma$ and starting conditions $\alpha_0$ and $\delta_0$.
-Given $s$, the other parameters have  closed form expressions calculated with the Kalman filter.
-A best estimate of $s$ is derived by iterating over $s$ so as to minimise  an appropriate objective function such as least squares.
-
-To compute local correlation, write $\Delta z_t\equiv z_{t+1}-z_t$ and similarly for other quantities.    Assume $t$ is given and note that 
-$$
-\Delta z_t =\delta_t +c\eta_t + s(\eps_{t+1}-\eps_t)+\beta\Delta q_t  \cq \Delta q_t\approx \frac{q'_t}{n+1} = \frac{1}{(n+1)\phi(q_t)}
-$$
-Hence
-$$
-\E(\Delta z_t) \approx \E(\delta_t) + \frac{\E(u_t)}{\phi(q_t)} 
-$$
-  Then $q_t$ is a random variable and 
-$$
-\cov(\Delta z_t,\Delta q_t|t) = \beta^2\cov(\Delta q_t|t)\approx (\beta q'_t)^2\cov(u_t)= \frac{(\beta\sigma)^2\pi\e^{q_t^2}}{6} 
-$$$$
-\cov(\Delta z_t|t) = (1+c^2 + 2s^2)\sigma^2 + \beta^2\cov(\Delta q_t|t) 
-$$
-This final expression assumes $\cov(\delta_t)=(n+1)\sigma^2/2$:  a random $t$ is chosen to observe the random walk. 
-Hence the local correlation is 
-$$
-\frac{\cov(\Delta z_t,\Delta q_t)}{\sqrt{\cov(\Delta z_t)\cov(\Delta q_t)}} = \left\{1+\frac{A}{\beta^2\cov(\Delta q_t)}\right\}^{-1/2}
-$$
-
-The local correlation between $z_t$ and $q_t$ is 
-$$
-\rho_t\equiv\cor(\Delta z_t,\Delta q_t|t) =  \frac{\beta\cov(\Delta q_t)}{\sqrt{\cov(\Delta z_t|t)\cov(\Delta q_t)}}=\pm\left\{\frac{\cov(\Delta z_t|t)}{\beta^2\cov(\Delta q_t)}\right\}^{-1/2} 
-$$
-where ``$|t$" indicates conditioning on information up to and including time $t$.   A calculation shows writing $c=4-\sqrt 3$,
-$$
-\cov(\Delta z_t|t)  = (2s^2+c)\sigma^2+\beta^2\cov(\Delta q_t)\cq \cov(\Delta q_t) \approx (q'_t)^2\cov(u_t)= \frac{\sigma^2\pi\e^{q_t^2}}{6}
-\ .
-$$
-Hence
-$$
-\O(\rho_t) = \frac{\beta}{s_t\sigma }
-\cq 
-s_t = \sqrt{\frac{6(2s^2+c)}{\pi}}\e^{-q_t^2/2}\ .
-$$
-Divisor $s_t$ is small if $|q_t|$ is large indicating the model posits higher tail correlation than normal if $\beta\ne 0$.  The ratio
-$$
-\frac{\O(\rho_t)}{\O(\rho)} =\frac{s}{s_t}= \sqrt{\frac{\pi}{6(2+c/s^2)}}\ \e^{q_t^2/2}\rightarrow \frac{\sqrt{2\pi}\ \e^{q_t^2/2}}{\sqrt{24}}\ ,
-$$
-compares local  to overall correlation.
-If $s\rightarrow\infty$ local correlation in the tails  will far exceed overall  correlation.
-This is obvious given $s\rightarrow\infty$ implies the model will exactly reproduce the data.
-If $s\rightarrow0$
-
-\subsection{Alternative view of local correlation}
-In \eref{cusp},  a large $|\beta|$ suggests more extreme tail behaviour than in the Gaussian copula.  To see this note  
- \be{change}
-\Delta \E( \alpha_t + \beta q_t)  \approx \frac{-2\delta_0}{n+1} + \frac{\beta}{(n+1)\phi(q_t)}= \frac{\beta/\phi(q_t)-2\delta_0}{n+1}\ ,
- \ee
- where $\Delta$ denotes change with respect to $t$.
-Change \eref{change} is relatively large if $q_t^2$ is large, that is $t$ is near 1 or $n$.
-Higher than normal tail dependence implies $|\beta|$ large.
-For a Gaussian copula, $\beta=\pm\sqrt{1-(s\sigma)^2}$ and comparing the ratio of estimates of the two sides to 1 is a test for Gaussianity.
-
-\subsection{Correlation between $z_t$ and $\alpha_t$}
-
- The term $\alpha_t+\beta q_t$ is the signal and $\eps_t$, noise.
-The signal is relatively smooth and contains both a nonparametric and Gaussian component $q_t$.
-Departures of $z_t$ from the Gaussian component  are the sum of a persistent component $\alpha_t$ and  transient component, $s\eps_t$.
-Since  $\eps_t$ and  the driver of persistence $\eta_t$  share $\sigma$, the smoothing parameter $s$ measures relative importance of transience as opposed to persistence.
-The scale parameter $\sigma$ relates to the degree of roughness since it is the variance of the changes in the  slope of $\alpha_t$.
-
-  Since $\Ex(q_t)=\Ex(z_t)=\Ex(\eps_t)=\Ex(\eta_t)=0$ it follows  
- $$
-0= \Ex(\alpha_t)=\alpha_0+\delta_0 \Ex(t) = \alpha_0+\delta_0 \Ex(t) = \alpha_0+\delta_0 \frac{n+1}{2}\qquad\Rightarrow\qquad \delta_0 = \frac{-2\alpha_0}{n+1}\ .
- $$ 
-Further $\Vx(q_t)=\Vx(z_t)=1$ implies an analysis of variance type decomposition
-\be{anova}
- 1= \Vx(\alpha_t) + \beta^2 + (s\sigma)^2\ .
-\ee
-Decomposition \eref{anova} splits the total variance  of 1 into that due to the nonparametric component $\alpha_t$,  Gaussian component $\beta^2$ and residual noise, $(s\sigma)^2$.
-Alternatively \eref{anova} states the variance of the nonparametric component is $1-\beta^2-(s\sigma)^2$.
-
-An example PG copula with $s\sigma=xx$, $\sigma=0$, $\beta=xx$ and $\alpha_0=xx$  is displayed in \fref{xx}.  
- \begin{comment}
- relation is such that
-$$
-\delta_0=\frac{-2\alpha_0}{n+1}\cq z_t=  \alpha_0(1-2u_t)+\beta q_t + s\eps_t \ .
-$$
-Additionally $\Vx(q_t)=\Vx(z_t)=1$ implying
-\be{constraint}
- 1= \frac{\alpha_0^2}{3}-2\alpha_0\beta c+\beta^2+(s\sigma)^2\cq c\equiv\cov(u_t,q_t)\approx 2.82\ ,
-\ee
-and hence at most two of $\alpha_0$, $\beta$ and $s\sigma$ can be chosen freely. 
-\end{comment}
-
-\section{Correlations with the PG copula}
-With \eref{cusp}  and $t$ uniform on $1,\ldots,n$ 
-$$
-\Vx\left(\begin{array}{c} z_t\\ \alpha_t\\ q_t\\ \end{array}\right)
-=\left(\begin{array}{ccc} 
-1 & 1-(s\sigma)^2 & \beta\\
-1-(s\sigma)^2 & 1-\beta^2-(s\sigma)^2 & 0\\
-\beta & 0 & 1\\
-\end{array}\right)\ .
-$$
-This covariance matrix serves to define a variety of ordinary and partial correlations.
-
-The correlation between $z_t$ and $q_t$ is  $\beta$.
-The partial correlation between $z_t$ and  the Gaussian component $q_t$, after removing the effect of the nonparametric component $\alpha_t$,  is called the Gaussian correlation:
-\be{rho}
-\rho_q\equiv\frac{\cov(q_t,z_t-\alpha_t)}{\sqrt{\cov(q_t)\cov(z_t-\alpha_t)}} = \frac{\beta}{\sqrt{\beta^2+(s\sigma)^2}}=\pm\left\{1+\left(\frac{s\sigma}{\beta}\right)^2\right\}^{-1/2}\ ,
-\ee
-where the sign is that of $\beta$.  Hence $\rho_q=1$ or 0 if  $s\sigma=0$ or $\beta=0$, respectively.
-Using \eref{anova},  $\rho_q^2$ equals the proportion of  residual variance $\Vx(z_t)-\Vx(\alpha_t)=\beta^2+(s\sigma)^2$ explained by  the Gaussian component $q_t$.
-
-\begin{comment}
-$$
-= \cor(\alpha_t+s\eps_t,\alpha_t) =\frac{1-\beta^2-(s\sigma)^2}{\sqrt{(1-\beta^2-(s\sigma)^2)(1-\beta^2)}}= \left\{\frac{1-\beta^2-(s\sigma)^2}{1-\beta^2}\right\}^{1/2} 
-$$
-\end{comment}
-and  $\rho_a$ is 1 or 0 according to whether  $s\sigma$ equals 0 or  $\sqrt{1-\beta^2}$, respectively. 
-\begin{comment}
-$$
-\cov(z_t-\alpha_t) = \cov(\beta q_t+s\eps_t) = \beta^2 +s^2\sigma^2\ .
-$$
-\end{comment}
-Finally the overall correlation is the correlation between $z_t$ and the signal, consisting of both nonparametric and Gaussian component:
-$$
-\rho\equiv\cor (z_t,\alpha_t+\beta q_t)=\cor(z_t,z_t-s\eps_t)=\frac{1-(s\sigma)^2}{\sqrt{\cov(z_t-s\eps_t)}}=\sqrt{1-(s\sigma)^2}\ .
-$$
-with $\rho=\rho_a$ if $\beta=0$.   If $s=0$, there is no measurement error in \eref{cusp} or, equivalently, there is no roughness penalty in \eref{spline} and $\rho_q=\rho_a=\rho=1$.
-
-\begin{comment}
-reducing to \eref{rho} except that $s$ is replaced by
-$$
-v\equiv \Ex\left(\sum_{j=1}^{t-1}w_j^2\right) = xxx \cq \alpha_t=\sum_{j=1}^{t-1} w_j\eta_{t-j}
-$$
-The derivation of $v=xxx$ is shown  appendix.  Equivalently $\rho_v^{2}$ is the proportion of $\Vx(z_t)$ explained by the nonparametric and Gaussian component.
-
-From \eref{rho} 
-\be{OR}
-\left(\frac{v}{s}\right)^2=\frac{\rho_s^2/(1-\rho^2_s)}{\rho_v^2/(1-\rho_v^2)} \equiv \mathrm{OR} \ ,
-\ee
-the odds ratio of local to global correlation.  In general $v>s$ implying $\mathrm{OR}>xx$.
-
-\end{comment}
-
-\begin{comment} 
-$$
-\rho = \cor(z_t,q_t) =\frac{\beta}{\sqrt{\beta^2+\cov(\alpha_t)}}=\pm\left\{1+\left(\frac{v\sigma}{\beta}\right)^2\right\}^{-1/2}\ .
-$$
-The expressions follow from a detailed calculation
-$$
-\cov(z_t,q_t) = \E\{(\alpha_t+\beta q_t)q_t\} = \beta
-\cq
-\cov(z_t) =\cov(\alpha_t)+\beta^2\cq \cov(q_t)=1
-$$
-where .   A detailed calculation shows
-\end{comment}
-
-\section{Special cases of the PG copula}
-
-\tref{pp} sets out possible choices for $s$ and $\beta$.
-These combinations are discussed in the further subsections.
-Note that $s=0$ does not imply $s\sigma=0$ as $s\rightarrow 0$ may imply $s\sigma$ converges to a positive number.
-
-\subsection{Empirical copula}
-
-The empirical copula results in \eref{cusp} when $s=0$.
-In this case   $z_t=\alpha_t+\beta q_t$.
-The deviation of $z_t-(\alpha_t+\beta q_t)$ can be made zero by selecting appropriate $\eta_t$.
-Hence $s=0$ implies the fitted copula is the empirical copula.
-Note $\Vx(\alpha_t)=1-\beta^2$ and since $\beta$ is arbitrary, the correlation between $z_t$ and the nonparametric component is 1.
-
-\subsection{Large local variation}
-
-The other  extreme  $s\rightarrow\infty$ is displayed  in the bottom rows of \tref{pp}.  Large $s$ forces negligible $\sigma$  and straight line behaviour for $\alpha_t$ yielding
-$$
-z_t= \alpha_0(1-2u_t) + \beta q_t + s\eps_t\ ,
-$$
-where $s\eps_t$ has finite variance $(s\sigma)^2$.
-
-\subsection{Gaussian copula}
-If $s\rightarrow\infty$ and  $\alpha_0=0$ then $(q_t,z_t)$ is bivariate   Gaussian with correlation $\beta$ and \eref{cusp} reduces to a Gaussian copula with correlation $\beta$ and $\rho=\rho_q$.
-In this case $s\sigma=\sqrt{1-\beta^2}$.
-
-\subsection{Probit copula}
-
- If $s\rightarrow\infty$ and  $\beta=0$ then \eref{cusp} defines a probit copula.   From \eref{constraint}, $\alpha_0=\pm\sqrt{ 3\{1-(s\sigma)^2\}}$.
-
- \subsubsection{Independence}
- If $s\rightarrow\infty$ and  $\alpha_0=\beta=0$ then the variables are independent.
-The situation is achieved either letting $\beta\rightarrow 0$ with a Gaussian copula or letting $\alpha_0\rightarrow 0$ with a Probit copula.
-Under independence $s\sigma=1$.
-
- \subsection{Conditionally Gaussian copula}
-
-This is the intermediate situation where  $0<s<\infty$.  Testing $\alpha_0=1/s=0$ is a test for a Gaussian copula.   Goodness of fit is measured with 
-\be{R2}
-\hat\rho^2= 1-(s\hat\sigma)^2=1-\Ex\{(z_t-\hat z_t)^2\}\ ,
-\ee
-where  $\hat z_t$ is the estimate of $z_t$ based on \eref{cusp} using estimates of $\alpha_0$, $\beta$ and $s\sigma$.  
-Values of $\hat\rho^2$ lie between 0 and 1 and have the usual interpretation:    near 1 indicates the percentiles of $u$ well explain $z$ values of $v$.   
-Note $R\rightarrow\beta$  if $\alpha_0=0$ and $s\rightarrow \infty$.
-
-\section{Estimation of the PG model}
-
-A convenient feature of the GC model is the straightforward estimation.
-The unknown parameters are $\alpha_0$, $\beta$, $\sigma$, and $s$.
-Given $s$, estimates of the other parameters are in closed form -- generalised least squares (GLS) estimators of $\alpha_0$ and $\beta$, while $\sigma$ is estimated from the fitted  residuals.
-GLS estimates are derived using the Kalman filter (KF).
-The KF  and the associated Smoothing filter (SF) also deliver diagnostics for assessing goodness of fit and estimates of  sampling error.
-In these calculations $s$ is either given or alternatively is iterated over to produce a quasi maximum likelihood estimate.
-
-From \eref{R2}
-$$
-\Ex\left\{ \left(\frac{z_{t}-\hat z_{t}}{s\hat\sigma}\right)^2\right\}=1
-$$
-suggesting  the comparison of standardised residuals  to $\pm 2$ and perhaps plotting the percentile rank of the standardised residuals against $u_t$ to identify  lack of fit.
-
-\begin{comment}
-Note $R^2$ differs from the correlation coefficient $\beta$ since.
-$$
-\frac{R}{\beta}=\pm \sqrt{1-(s\hat\sigma)^2}\left\{1+\left(\frac{s\sigma}{\beta}\right)^2\right\}
-$$
-This emphasises the difference between $R^2$ and $\beta$.
-The former measures the goodness of fit of a semiparametric function of $u$ to explain $z$ while $\beta$ measures the ability of a straight line in $q$ to explain $z$.
-If $\beta\ne 0$ then $q$ forms part of the semiparametric specification and hence if $\beta\ne 0$,  $R^2>\beta^2$.
-\end{comment}
-
-   The implied correlation between $z_t$ and $q_t$ is  
-$$
-\beta=\frac{\beta}{\sqrt{\beta^2+(s\sigma)^2}} = \pm\left\{1+\left(\frac{s\sigma}{\beta}\right)^2\right\}^{-1/2}\ .
-$$
-The term $\beta/(s\sigma)$ is the signal to noise ratio.  If $z_t, q_t\sim (0,1)$ then $\beta^2+(s\sigma)^2=1$ and  
-$$
-\beta=\pm\sqrt{1-(s\sigma)^2}=R=\beta \cq \frac{\beta}{s\sigma} = \frac{\pm\sqrt{1-(s\sigma)^2}}{s\sigma} = \frac{\beta}{\sqrt{1-\beta^2}} 
-$$.
-
- Thus the empirical correlation between $z_t$ and $q_t$ is
-$$
-\sum_{t=1}^n z_tq_t = \beta+\delta_0\sum_{t=1}^n tq_t 
-$$
-
-By construction both $z_t$ and $q_t$ have mean zero and variance 1 implying
-the correlation between $z_t$ and $q_t$ is
-
-If  $\beta=0$ then 
-$$
-z_t=\alpha_0 + n\delta_0 u_t+\beta \Phi^-(u_t) +s\eps_t\ ,
-$$
-    Testing $\delta_0=0$ amounts to testing for independence.  If $\beta=\pm 1$ then 
-$z_t-(\pm q_t)=\alpha_0+t\delta_0$ implying $\alpha_0=n\delta_0=0$ and  $z_t=\pm q_t$, that is the variables are co or counter monotonic.
-Finally if $\beta\ne 0,\pm 1$ then $z_t=\alpha_0+t\delta_0+\beta q_t+s\eps_t$  since  $\alpha_0=\delta_0=0$, implied by the fact that    Since both $z_t$ and $q_t$ are, by construction, standard normal, this  amounts to prescribing  a Gaussian copula with correlation indicated in \tref{pp}.
-The ratio $\beta/(s\sigma)$ is the  signal to noise ratio.
-
-The middle column of the body of \tref{pp} displays alternatives for finite $s\ne 0$.
-If $\beta=0$  the implied copula is nonparametric with $\alpha_t$ evolving smoothly as a function of $t$ with the actual degree of smoothness increasing with $s$.
-A constraint is $\alpha_0=\alpha_n=\sum_t\delta_t=0$ and hence $\alpha_t$ forms a bridge.
-If $\beta=\pm 1$ then the signed difference $z_t-(\pm q_t)$ is modelled as a smooth.
-In a fit, the  bridge structure is expected to be enforced by the data.
-
-The scale  $\sigma$ quantifies roughness in the signal $\alpha_t$ but its size is determined by $s$ with $s\sigma\le 1$ implied by the standard normality of $z_t$.   
-In fitting, $s$ is either chosen a--priori, or estimated together with the other parameters.
-Given $s$, estimates of  $\beta$, $\alpha_0$, $\delta_0$ and $\sigma$ are closed form generalised least squares calculations.
-Thus $s$ can be estimated  using a one dimensional search.
-Given the values of the parameters,  standard diagnostics are used to assess the fit and reveal areas of inadequate fit.
-These techniques are used and explained in the applications.
-
-Use of $q_t$ permits  a partially Gaussian explanation of the copula with  Gaussianity increasing with $s$.
-In the limit the enforced Gaussian copula has correlation $R$ signed according to $\hat\beta$.
-Co or  countermonotoniticity implies $R=\pm 1$ with the sign indicating the direction of the relationship.
-Setting $\beta=0$  excludes the Gaussian copula  component.
-
-\begin{table}[htdp]
-\caption{Predicted $z_t$ with conormal copula model}\label{ppp}
-\begin{center}
-\begin{tabular}{c||c|c|c}
-\hline
-&$s=0$& $0<s<\infty$ &$s\rightarrow\infty$\\
-\hline\hline
-$\beta=0$&& $\alpha_t$&$\alpha_0(1-2u_t)$ \\
-& & non parametric& linear probit\\
-& & probit & independence: $\alpha_0=0$ \\
-\cline{1-1}\cline{3-4}
-$\beta\ne 0,\pm 1$  & $z_t$ & $\alpha_t+\beta q_t$ &$\alpha_0(1-2u_t)+\beta q_t$\\
-&empirical & conormal & Gaussian if $\alpha_0=0$\\
-\cline{1-1}\cline{3-4}
-$\beta=\pm 1$& & $\alpha_t\pm q_t$& $\alpha_0(1-2u_t)\pm q_t$ \\
-& & cointegrated & co/counter monotonic \\
-& & departure & if $\alpha_0=0$ \\
-\hline
-\end{tabular}
-\end{center}
-\end{table}%
-
-The fitted values $\hat z_t$ stacked in  vector $\hat z$  provide a basis for simulating all percentiles including extreme percentiles.
-In particular suppose $z\sim N(\hat z, \Sigma)$ where $\Sigma$ is the covariance matrix implied by the model.
-Then $v\sim\Phi_*(z)$ is a simulation of the the $v_t$.
-Bringing $v$ into the original order yields $(u_t,v_t)$, a simulation from the copula.
-Simulated percentiles are  mapped back into the original scale as   $F_*^-(u_t,v_t)$ to provide simulated $(x_t,y_t)$ outcomes.
-
-\section{Copula forcing}
-
-Even if data suggests a strict Gaussian copula it  may be desirable to force stronger dependence, especially in the tails. This forcing is achieved with
-
-\section{Application to copula fitting}
-
-The following example illustrates the copula fitting technique.
-
-\section{Financial sensitivity and contagion}
-
-Suppose the singular value decomposition of the  matrix $S$ of sensitivities at a particular $q$ is 
-$S= UDV'$.
-Here  $D$ a diagonal matrix of singular values, arranged in decreasing order along the diagonal and $U$ and $V$ are orthonormal:  $U'U=V'V=I$.
-If the series are independent then $U=D=V=I$.
-If the series are comonotonic then $U=V=(1,0)$ while $D=\diag(1,0,\ldots,0)$.
-Hence in the comonotonic case $S=11'$.
-
-So the best thing is to compare 
-$$
-Q= s_{i1}c_{j1} + \cdots + s_{ip}c_{jp} 
-$$
-
-If $Q=I$ then $S=C=I$.
-If $Q=11'$, a matrix of ones, then $S=\sqrt{p}(1,0)$ and $C=(c,0)$ both have rank 1:  here $s$ and $c$ are the leading columns of $S$ and $C$, respectively and 0 a matrix of zeros.
-
-The approximation $Q\approx sc'$ is exact if $Q$ has rank 1 implying $Q=11'$.
-The approximation $Q\approx sc'$ is inadequate if $Q=I$.
-Inadequacy can be judged from the largest singular value in $D$, as a proportion of $p$, the number of variables or rows in $Q$.
-
-$$
-Q_* \equiv \frac{1}{p-1}(Q-I)=UDV'\cq s\equiv Q_*1\cq c\equiv Q_*'1\ .
-$$$$
-Q=I + s1'+ UDV'\cq s\equiv \frac{1}{p-1}(Q-I)1
-$$
-Then $s$ is the vector of average \v\ sensitivity of each variable to all others.
-Further $c$ is the average \v\ impact of each variable on all others.
-The matrices $U$, $D$ and $V$ define the singular value (svd) decomposition of $Q_*$, arranged so that diagonal matrix $D$ has the singular values on  the diagonal in descending order.
-If $b=d_1u_1$ and $c=v_1$ where $u_1$, $d_1$ and $v_1$ are the first column, top diagonal entry, and first column of $U$, $D$ and $V$ respectively, then  for two variables $y\ne x$ in $Q$,
-$$
-\Delta_x q_y = s_y+ b_yc_x +\eps_{yx}
-$$
-This states that percentage sensitivities are, apart from the ``error" $\eps_{yx}$, an average sensitivity plus a scaled response to the contagious effect of the $x$ variable.
-The contagious effects contained in $c$ are estimated by maximising the explanation of $Q$.
-
-The vector $1'Q$ sums  the changes in \v\ when each of the column variables is stressed, and writes this as a proportion of the change in the variable being stressed.
-These proportional sums, subtracting 1 and divided by  $p-1$ where $p$ is the number of variables, measures the average contagion of each variable on all others:  $c'=(p-1)^{-1}1'(Q-I)$ or $c=(p-1)^{-1}(Q-I)'1$
-
-Alternatively the vector $Q1$ sums the changes in \v\ of each row variable when all the column variables are stressed.
-Again it is appropriate to remove the effect of a variable on itself and consider the average over the remaining variables:  $s\equiv(p-1)^{-1}(Q-I)1$.
-If $Q_*\equiv (p-1)^{-1}(Q-I)$ then $s=Q_*1$ and $c=\dot q_*1$ are the vectors of sensitivities and contagions, respectively.
-If $Q=I$ then $s=c=0$.
-If $Q=11'$ then $s=c=1$.
-
- \section{Systemic risk and causal chains}
-A rank one approximation to the matrix  $Q$ is 
- $
- Q  \approx  sc' 
- $.
- Vector $c$ is an index of the contagious  impact of each of variables on the others while $s$ measures the sensitivity of each variable to each of the others.
-The vectors $s$ and $c$ are derived from the singular value decomposition $Q=UDV'$ where $U'U=V'V=1$  and  where $s$ and $c$ are the first column of $UD$ and $V$  respectively, assuming the svd is organised so that the singular values in the diagonal matrix $D$ are organised from largest to smallest.
-The appropriateness of the summarisation $sc'$ is measured with $\tr(Q-sc')$.
-
-If the variables are independent then $Q=I$ and both $s$ and $c$ equal a column of the identity matrix with $sc'$ a matrix of 0's except in a single diagonal position where it is 1.
-Then all but one variable has a contagion effect and only that variable is sensitive to the contagion provided by the  variable.
-
-If the variables are comonotonic then $Q=11'$ and $s=1$ and $c=1$ where 1 denotes a vector of ones.
-Thus the rank 1 approximation is exact and each variable is equally contagious and equally sensitive.
-
- Note that 
- $$
- Q^{n} \approx (s'c)^{n-1}sc'=\ ,
- $$
-
- If the random variables are independent the $Q-I=0$ and $a=b=k=0$ and there is no error in the first order svd approximation.
-If the random variables are comonotonic then $Q=11'$ and $Q-I$ has ones everywhere except on the diagonal where it is zero.
-The vector of row means is then $p^{-1}(p-1)1$
-
-Systemic risk in the system is measured with $b'k=d_1(u_1'v_1)$.   In the case of comonotonic  random variables $Q=11'$, $a=1$ and $x$, where $p$ is the number of variables,  $d_1=1$.
-
-Furthermore we may define quantities such as
-$
-u^- \equiv \var_q(v|u\le q)
-$
-measuring the impact of a non distressed state in $v$.
-For brevity we do not dwell on these constructs in this writeup although the ramifications and potential uses of these constructs will be  investigated in the research.
-
-\section{Generalising Sklar's Theorem}
-
-Skalr's Theorem states that if $F(x)$ is a a joint then there exists a $C$ such that
-$
-F=C\circ F_*
-$ where $C_F=F$
-\section{Literature}
-
-We propose a measure for systemic risk: CoVaR, the value at risk (VaR) of financial institutions conditional on other institutions being in distress.
-We define an institution?s (marginal) contribution to systemic risk as the difference between CoVaR and the financial system?s VaR.
-From our estimates of CoVaR for characteristic-sorted portfolios of publicly traded financial institutions, we quantify the extent to which characteristics such as leverage, size, and maturity mismatch predict systemic risk contribution.
-We argue for macro-prudential regulation based on the degree to which such characteristics forecast systemic risk contribution.
-
-\section{Econometric implementation}
-
-The above development sets out our proposed  broad  framework for linking bivariate copulas and marginals to external variables and shocks study the impact of the same on stresses within the system and the contagious effects of crises.
-Proposed econometric analysis will implement and extend  \cite{brownlees2010volatility}.
-
-\section{Data}
-
-We will employ publicly available data as published by APRA and other regulators.
-
-\section*{References}
-\bibliography{/users/pietdejong/documents/research/cifr/piet2}
+since $f(r_m,r_n)=f(r_m)f(r_n)c(u_m,u_n)$.
 

### 2015-05-29 old stuff/obs.tex
pdj initial

--- 2015-05-29 old stuff/obs-(1)-copy.tex
@@
 
-\section{Weihao's approach}
+\section{Bivariate case}
 
@@
 
+\subsection{Copula stressors}
+
+\newcommand{\Es}{\E_\phi}
+
+Stressing can be based on a vector of variables $x$ with distribution $F(x)=u$.   Given a copula $\Phi(u)$ with density $\phi(u)$ consider
+the stressed expectation 
+\be{copula}
+\Es(p_{it}) \equiv \int \E(p_{it}|x)  \de\Phi\{F(x)\}  =  \E\{\phi(u)\E(p_{it}|x)\}  \ ,
+\ee
+The  copula $\Phi(u)$ is designed to magnify  stressful situations such as  where all components of $x$ are abnormally low.
+If $\Phi(u)=u$ then $\phi(u)=1$ and $\Es(p_{it})=\E(p_{it})$.
+
+For example $\Phi\{F(x)\}$ may have stronger tail dependence than $F$.
+In the extreme  $\Phi(u)=\min_i(u_i)$ making all  variables in $x$  comonotonic.
+The copula $\Phi(u)$  leaves marginals intact and acts as a stressor on the copula  $c(u)$  corresponding to $F$ since
+$$
+\de\Phi\{F(x)\} = \phi(u)c(u)\prod_if_i(x_i)\ ,
+$$
+where the $f_i$ are the  marginal densities of $F$.   Further marginal stress is induced by allowing $\Phi(u)$ to have non--uniform marginals in which case
+$$
+\de \Phi(u) = \phi(u)\prod_i\phi_i(u_i)\de u\ ,
+$$
+where $\phi(u)$ has, as before, uniform marginals and the $\phi_i(u_i)\ge 0$ induce non--uniformity in each of the marginals subject to $\E\{\phi_i(u_i)\} = 1$.
+
 \end{document}

### 2015-05-29 old stuff/observations.tex
pdj initial

\documentclass[authoryear]{elsarticle}
\usepackage{latexsym}
%\usepackage{rotate}
\usepackage{graphics}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{comment}
\bibliographystyle{chicago}

\newcommand{\logit}{\mathrm{logit}}
\newcommand{\I}{\mathrm{I}}
\newcommand{\E}{\mathrm{E}}
\newcommand{\p}{\mathrm{P}}
\newcommand{\e}{\mathrm{e}}
\newcommand{\vecm}{\mathrm{vec}}
\newcommand{\kp}{\otimes}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\cov}{\mathrm{cov}}
\newcommand{\eps}{\epsilon}
\newcommand{\ep}{\varepsilon}
\newcommand{\obdots}{\ddots}    % change this later
\newcommand{\Ex}{{\cal E}}
\newcommand{\rat}{{\frac{c_{ij}}{c_{i,j-1}}}}
\newcommand{\rmu}{m}
\newcommand{\rsig}{\nu}
\newcommand{\fd}{\mu}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\cor}{\mathrm{cor}}
\newcommand{\bx}[1]{\ensuremath{\overline{#1}|}}
\newcommand{\an}[1]{\ensuremath{a_{\bx{#1}}}}

\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}

\renewcommand{\i}{\item}
\newcommand{\sr}{\ensuremath{\mathrm{SRISK}}}
\newcommand{\cs}{\ensuremath{\mathrm{CS}}}
\newcommand{\cri}{\ensuremath{\mathrm{Crisis}}}
\newcommand{\var}{\ensuremath{\mathrm{VaR}}}
\newcommand{\covar}{\ensuremath{\mathrm{CoVaR}}}
\newcommand{\med}{\ensuremath{\mathrm{m}}}
\newcommand{\de}{\mathrm{d}}
\renewcommand{\v}{\ensuremath{\mathrm{v}_q}}
\newcommand{\m}{\ensuremath{\mathrm{m}}}
\newcommand{\tvar}{\ensuremath{\mathrm{TVaR}}}

\newcommand{\eref}[1]{(\ref{#1})}
\newcommand{\fref}[1]{Figure \ref{#1}}
\newcommand{\sref}[1]{\S\ref{#1}}
\newcommand{\tref}[1]{Table \ref{#1}}
\newcommand{\aref}[1]{Appendix \ref{#1}}

\newcommand{\cq}{\ , \qquad}
\renewcommand{\P}{\mathrm{P}}
\newcommand{\Q}{\mathrm{Q}}

\newcommand{\Vx}{{\cal V}}
\newcommand{\be}[1]{\begin{equation}\label{#1}}
\newcommand{\ee}{\end{equation}}

\begin{document}

\section{Weihao's observations}

\bi

\i How to standardise $\cov(p_{it},\phi)$ -- still thinking but inclined to standardise by $\sigma_\phi$ instead of $\sigma_\phi^2$.

pdj -- I agree.  Then one is inclined  to write
$$
p_{it} \approx \mu_{it} + \beta_{it}\frac{\phi-1}{\sigma_\phi}\ ,
$$
and hence $\beta_{it}$ is the response to a one--unit increase in the standardised stress factor $(\phi-1)/\sigma_\phi$.  Hence to my mind it argues the stress factor $(\phi-1)/\sigma_\phi$ is core and needs concrete characterisation.

\i Capital shortfall at time $i+h$ is the difference between debt and admissible assets
$$
d_{it}-(1-k)(w_{i,t+h}+d_{it})  \cq w_{i,t+h}=w_{it} \e^{\nu_{it}}
$$
where $k$ is the non-admissible factor and $\nu_{it}$ is the return on equity. Capital shortfall at time $i+h$ can be rewritten as
$$
d_{it} - (1-k_{i,t+h})(w_{it}+d_{it})  \cq k_{i,t+h} \equiv 1-(1-k)\frac{w_{it}\e^{\nu_{it}}+d_{it}}{w_{it}+d_{it}}
$$
where assets are constant, similar to debt. However the non-admissible or impairment factor $k_{i,t+h}$ varies inversely with $\nu_{it}$. One can either forecast capital shortfall by modeling $\nu_{it}$ or $k_{i,t+h}$, and this paper adopts the former due to available data on equity returns.

pdj -- Another way to look at this is to write
$$
\frac{1-k_{i,t+h}}{1-k} = \left(1-\frac{d_{it}}{a_{it}}\right)\e^{\nu_{it}}+\frac{d_{it}}{a_{it}}
$$
Can this be exploited? -- note debts to assets is the odds of debt to equity

\i Artzner asserts that any coherent risk measure is the supremum of the expected capital shortfall in a collection of generalised scenarios or probability measures $\mathcal{P}$ on states of the world, i.e.
$$
\sup \left\{ \E_\mathbb{P}(p_{it}) | \mathbb{P} \in \mathcal{P} \right\}
$$
pdj-- this seems a useful background result allowing us to argue the generality of our approach.  Not sure how to best write up/connect to our presentation.

\i $\tilde{\E}(p_{it}) = \E(p_{it}) + \cov\{\E(p_{it}|\phi),\phi\}$

pdj-- The implication here is that one can take each given scenario (ie possible outcome of $\phi$) and just consider how expected put prices for each scenario covary with scenario:
$$
\beta_{it} = \cov\{p_{it}(\phi^*),\phi^*\}\cq \phi^* \equiv \frac{\phi-1}{\sigma_\phi}\cq p_{it}(\phi^*)\equiv\E(p_{it}|\phi^*)\approx \mu_{it}+\beta_{it}\phi^*
$$
This seems useful to me.

\i Write the put payout as
$$
p_{it}=k\left|1-\e^{\nu_{it}^*}\right|^+ = k \int_0^\infty (1-\e^{\nu_{it}^*} > s) \de s
=  k \int_0^\infty (\nu_{it}^* < \ln(1-s)) \de s
$$
$$
= k \int_{-\infty}^0 (\nu_{it}^* < s) \e^s \de s
$$
and hence the put covariance is
$$
\cov(p_{it},\phi) = \cov\left\{ k \int_{-\infty}^0 (\nu_{it}^* < s) \e^s \de s , \phi \right\}
= k \int_{-\infty}^0  \cov\left\{  (\nu_{it}^* < s) , \phi \right\} \e^s \de s \;.
$$
The covariance in the final integral is between a capital shortfall scenario $(\nu_{it}^* < s)$ and the stress factor.

pdj -- can you use the expected stress factor trick here?  Still thinking about the implications of above. 
\ei
\end{document}

### 2015-05-29 related/copulas2.tex
pdj initial

\documentclass[a4paper,12pt]{article}
\usepackage{latexsym}
\usepackage{rotate}
%\usepackage{../texstuff/chicago}

\usepackage{graphics}

%\bibliographystyle{../texstuff/chicago}
%\renewcommand{\labelenumi}{(\roman{enumi})}
\newcommand{\eps}{\epsilon}
\newcommand{\var}{{\rm var}}
\newcommand{\cov}{{\rm cov}}
\newcommand{\nid}{{\rm NID}}
\newcommand{\diag}{{\rm diag}}
\newcommand{\E}{{\mathrm E}}
\newcommand{\R}{{\mathrm R}}
\newcommand{\U}{{\mathrm U}}
\newcommand{\Ex}{{\cal E}}
\newcommand{\cor}{\mathrm{cor}}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\e}{\mathrm{e}}
\newcommand{\de}{\mathrm{d}}
\newcommand{\p}{\mathrm{P}}
\newcommand{\Ln}{\mathrm{Ln}}
\newcommand{\ra}{\varrho}

\newcommand{\eref}[1]{(\ref{#1})}
\newcommand{\fref}[1]{Figure \ref{#1}}

\begin{document}

\title{Structured copula modelling of insurance liabilities}
\author{Piet de Jong
\\\\ \small Department of Actuarial Studies, \\ \small Macquarie
University, NSW 2109, Australia. \\ \small Email:
piet.dejong@mq.edu.au}

\date{}
\maketitle

\begin{abstract}
This article employs copulas to model total claims losses arising from different lines of insurance.   There are two contributions.   First a flexible method is developed to generate copulas.   Second total losses are considered given the marginal distributions are Weibull.
\end{abstract}

\paragraph{Keywords:}Copulas

\section{Introduction}

This article develops and discusses a practical, structural way of generating copulas.   By structural we mean the copula is generated from a generating mechanism typical of statistical modeling.   This contrasts with the usual way of specifying copulas directly via functional forms as discussed for example in \citeN{joe1997mma} or \citeN{nelsen2006ic}.

\fref{fig1} displays  simulations from a copula constructed using  the proposed copula generating method. Each  panel in \fref{fig1} is generated by firstly simulating for $t=1,\ldots, N$ from the bivariate distribution
\begin{equation}\label{chi1}
s_{1t}=\alpha_t\ , \qquad s_{2t}=\alpha_t+\ln(\rho)\eps_t\ , \qquad \alpha_t\sim\chi_1^2\ ,\qquad \eps_t\sim N(0,1)\ .
\end{equation}
where $\chi^2_1$ denotes the chi--squared with 1 degree of freedom, and $0\le\rho\le 1$. Given simulated values $s_{1t}$ and $s_{2t}$, the corresponding percentiles $G(s_t)\equiv \{G_1(s_{1t},G_2(s_{2t})\}'$ are calculated where the $G_i$ denote marginal distributions.   Since $G$ is not specified directly, the percentiles are estimated by the percentile ranks $\check s_{1t}$ and $\check s_{2t}$, that is their ranks in the simulated sample divided by the sampling effort $N$.

\begin{figure}[htb]
\centering
\includegraphics{fig1.eps}
\caption{Simulated percentile ranks $(\check s_{it},\check s_{2t})$ from model (\ref{chi1}).} \label{fig1}
\end{figure}

In \fref{fig1}, if $\rho\approx 0$ then $\ln(\rho)$ is very negative and $s_{1t}$ and $s_{2t}$ are virtually unrelated since $s_{2t}$ is dominated by $\ln(\rho)\eps_t$.  If $\rho\approx 1$ then $\ln(\rho)\approx 0$ and $s_{1t}$ and $s_{2t}$ are highly dependent.  The panels in \fref{fig1} suggest increasing upper tail dependence in that the conditional probability $P(\check s_{2t}> u|\check s_{1t}>u)$ increases as $u\rightarrow 1$.

The chi--squared specification for $\alpha_t$ can be changed to other extreme value or heavy tailed distributions. For example the log--normal is an alternative.  \fref{fig2} illustrates the copula when $\alpha_t\sim t_1$, in (\ref{chi1}), a ``t"  random variable with 1 degree of freedom.  In this case tail dependence appears to increases in both tails. Thus when $\alpha_t$ is near zero, the effect of $\eps_t$ is to mask the dependence while if $|\alpha_t|$ is large the dependence increases: the perturbing effect of $\eps_t$ in these cases is negligible.

\begin{figure}[htb]
\centering
\includegraphics{fig2.eps}
\caption{Simulated percentile ranks from model (\ref{chi1}) if $\alpha_t\sim t_1$\ .}\label{fig2}
\end{figure}

The copula generating method \eref{chi1} generalizes the Gaussian copula \cite{mcneil2005qrm}.   If $\alpha_t\sim N(0,1)$ then $s_{1t}$ and $s_{2t}$ are jointly normal with correlation
$
    1/\sqrt{1+(\ln\rho)^2}
$.
Thus  in this case the relationship between the percentiles is induced with a Gaussian copula.  The Gaussian copula  combined with Gaussian marginal distributions for the actual observed variables yields the usual factor model often employed in the study of correlated data \cite{dnlawley1971fas}.

\section{The general form of the model}

Setup \eref{chi1} can be written in the vector form
    \begin{equation}\label{mat2}
        \left(
    \begin{array}{c}
      s_{1t} \\
      s_{2t} \\
    \end{array}
  \right)=
\left(
  \begin{array}{c}
    1 \\
    1 \\
  \end{array}
\right)
\alpha_t + \left(
              \begin{array}{cc}
                0 & 0 \\
                0 & \ln\rho \\
              \end{array}
            \right)\eps_t\ ,
    \end{equation}
This suggests the generalization
 \begin{equation}\label{mcop}
     \left(
    \begin{array}{c}
      s_{1t} \\
      s_{2t} \\
      \vdots\\
      s_{pt}
    \end{array}
  \right)=
\left(
  \begin{array}{c}
    1 \\
    1 \\
    \vdots \\
    1
  \end{array}
\right)
\alpha_t + \left(
              \begin{array}{cccc}
                \ln \rho_1 & 0 & \cdots & 0 \\
                0 & \ln\rho_2 & \cdots & 0 \\
                \vdots & \vdots & \ddots & \vdots \\
                0 & 0 & \cdots & \ln \rho_p \\
              \end{array}
            \right)\eps_t\ ,\qquad \eps_t\sim N(0,I)\ ,
  \end{equation}
  where the vector random variable $\alpha_t$ has an appropriate long tail distribution, and $\rho_1=1$.

  The general form of the proposed model is
\begin{equation}\label{gfac}
   y_t=F^-(\check s_t)\ , \qquad  s_t = Z\alpha_t + \psi\cdot\eps_t\ , \qquad \eps_t\sim N(0,I)\ .
\end{equation}
Here $\check s_t$ is the vector of percentiles of each component of $s_t$.  Further $\alpha_t$ is a vector of independent random variables with a heavy tailed distribution.  Further $\psi$ is a vector with entries $\ln(\rho_j)$ where $\rho_1=1$, the $\cdot$ notation indicates componentwise product, and $Z$ is a matrix of factor loadings.  The vector function $G$ is the vector of marginal distributions determined the joint distribution of $s_t$.  In particular component $i$ of $G(s_t)$ is $G_i(s_{it})$ where $G_i$ is the marginal distribution of $s_{it}$, component $i$ of $s_t$.  The vector of functions $F$ is similarly defined in terms of the marginal distributions of $y_t$, and $F^-$ denotes the vector of inverse mapping.

Analogous to state space models in time series, $\alpha_t$ is the ``state" vector, driving the tail dependence or tail correlation in the system.  Thinking of a one--dimensional state, when $\alpha_t$ is large

The marginal distributions in $G$ are easy to describe and simulate from but functional forms for the specific cases of interest are usually not available.   For example if $\alpha_t$ contains chi--squared random variables and $\eps_t$ is normal then the marginal distributions $G$ correspond to that of linear combinations of chi--squareds and normals.

When functional forms for the components of $G$ are not available it is convenient to employ the nonparametric estimate
$$
\check G(s_t) \equiv \check s_t \equiv \frac{1}{N}\ \ra(s_t)\ ,
$$
where the $s_r$, $r=1,\ldots,N$ are simulations from the second equation in \eref{gfac} and $\ra(s_t)$ denotes the vector of ranks of each component of $s_t$.

The vector of marginal distributions $F$ may be functionally specified, up to unknown parameters,  in which case the available data $y_t$, $t=1,\ldots,n$ is used to estimate the unknown parameters  leading to the estimate $\hat F$.  Alternatively
$$
\check F(y_t) \equiv \check y_t \equiv \frac{1}{n}\ \ra(y_t)\ .
$$
If $n$ is small this estimate yields worthless tail probability estimates of either 0 or 1 arguing for a functional estimate $\hat F$ of $F$.  Suggestions are in the next section.

\section{Modeling the marginal distributions}
This section discusses the modeling of the marginals in $F$.  It is possible to model each marginal by a different form.  However in many applications differences will be confined to differences in the parameters, keeping the functional form fixed.

\subsection{Normal or log--normal marginals}

Suppose $\Phi^-(\check s_t)$ is the standard inverse normal evaluated at each of the components of $\check s_t$ and let $\mu$ and $\sigma$ be vectors of means and standard deviations, respectively.  Then the completed model is
$$
y_t=\mu+\sigma\cdot\Phi^-(\check s_t)\ ,\qquad s_t=Z\alpha_t+\psi\cdot\eps_t\ , \qquad \eps_t\sim N(0,I)\ .
$$

Note that if $\alpha_t$ is normal then 
$
\check s_t=\Phi_*(s_t)
$ where $\Phi_*$ denotes a vector of marginal normals with means and variances as induced by the state equation.   Hence the net effect of both measurement and state equation is to induce a jointly normal $y_t$ with correlation matrix derived from the state equation.  Hence this setup with $\alpha_t$ normal, returns to the classical factor analysis setup \cite{dnlawley1971fas}

With the log--normal model $y_t$ in the measurement equation is replaced by $\ln y_t$ in which case $\mu$ and $\sigma$ refer to the mean and variance of $\ln y_t$.

\fref{fig3} displays simulations from \eref{chi1} if $\alpha_t\sim \chi^2_1$ with $F$ standard normal.  Notice for all values of $\rho$, there are many more ``+2" standard deviation events compared to ``-2" standard deviation events -- that is events that lie in the upper right hand square of each panel as opposed to the lower left panel.  The bottom right panel shows moderate correlation for all occurrences below the means 0, with almost perfect correlation for  above mean events.

\begin{figure}[htb]
\centering
\includegraphics{fig3.eps}
\caption{Simulated values from \eref{chi1} if $\alpha_t\sim \chi^2_1$ with $F$ normal\ .}\label{fig3}
\end{figure}

\subsection{Pareto marginals}

The the inverse of the Pareto distribution is  
$$
F^-(u)= b\left\{(1-u)^{-1/a}-1\right\}\ ,\qquad 0<u<1\ ,
$$
where $a>1$ and $b>0$ are the parameters of the Pareto.  The mean of the distribution is $a/(b-1)$.  Thus with Pareto marginals the model becomes
$$
y_t=b\left\{(1-\check s_t)^{-1/a}-1\right\}\ ,\quad s_t=Z\alpha_t+\psi\cdot\eps_t\ , \qquad \eps_t\sim N(0,I)\ ,
$$
where $a$ and $b$ are vectors of parameters and the first equation is interpreted in an obvious componentwise sense.

\subsection{Other candidate marginal distributions}
Since $F_i^-$ maps numbers between 0 and 1 to real numbers it is convenient to think of them as
$$
1'a+\sum_i b_i\ln \frac{u}{1-u} = 1'a+\ln\prod_i\left(\frac{\check s_{it}}{1-\check s_{it}}\right)^{b_i}
$$
These have means $a_i$ and variances $b_i^2\pi^2/3$.

\section{Estimating loss distributions}

This leads to claim distribution.
\begin{equation}\label{loss}
c_t =\sum_{i=1}^p\frac{b_i}{(1-\check s_{it})^{1/a_i}}-1'b\ .
\end{equation}
Simulating this loss is a three step process:
\begin{enumerate}
  \item Simulating $N$ realizations of $s_t$.
  \item Computing the percentile ranks $\check s_t$.
  \item Combining the $\check s_t$ as in \eref{loss}.
\end{enumerate}
This formula is of independent interest. If $s_{it}$ is near 1, that is we are in the upper tail, then losses are likely to be huge.

Note that if $u$ is uniform then
$$
\frac{b}{(1-u)^{1/a}}
$$ is Pareto
In practice, for given parameter values, the losses $\ell_t$ and the loss distribution can be simulated.   This yields relevant percentiles.

\section{Time series structure}

Up to now it is assumed the $\alpha_t$ are independent random variables.  An alternative is where $\alpha_t$ has a time dependent structure.  A simple example is a geometric random walk
$$
\alpha_{t}=\e^{h_t/2}\ , \qquad h_{t+1}=h_t+\eta_t\ .
$$
$$
\alpha_{t+1}=(\eta_{t+1})^2
$$

\section{Connection to previous literature}
This setup \eref{gfac} is reminiscent of the usual factor model \cite{dnlawley1971fas} often employed to study the joint behavior of variables.  Similar to the ordinary factor analysis $Z$ spells out the way in which the heavy tailed factors manifest themselves into the components of $s_t$ and hence their percentiles $\check s_t$.

The formulation \eref{gfac} displays the obvious connection to state--space models \cite{Harvey:89}.  In terms of this latter model,  $\alpha_t$ is called the state of the system which manifest in the signal $s_t$.  The signal serves to determine the percentiles $\check y_t$ of $y_t$.   The model is completed by specifying the marginal distributions of $y_t$.

\section{Goodness of fit}

Suppose $n$  observations on a vector random variable $y$ denoted $y_1, y_2, \ldots, y_n$. The aim is to estimate the parameters in $Z$ and $\Psi$.   Suppose these two matrices depend on unknown parameters $\theta$ and $\rho$, respectively.

The first step in the estimation is to convert the $y_t$ to percentiles.  This is done either relative to a fitted marginal distributions $\hat F$ in which case $\hat F(y_t)$ is the vector of estimated percentiles, or by computing the percentile ranks 
$
\check y_t \equiv n^{-1}\ra(y_t)
$.
In the former case the estimated percentiles need not be exactly uniformly distributed although this does hold in the latter case.

Suppose we use the $\check y_t$.  Then according to the model $\check y_t=G(s_t)$ and

You can plot the time series of percentile ranks.  Actually what you do is simulate a large number of 
Given a vector of actual or estimated marginal distributions $F$ the percentile ranks are
$$
\check y_{t} = F(y_t) \approx \frac{1}{n}\sum_{r=1}^n (y_r<y_t)\ ,\qquad t=1,\ldots,n\ .
$$
The right hand side are the estimated percentile ranks in the situation if there is no estimate of $F$, and $(y_r<y_t)$ is the vector of 1's and 0's indicating whether the corresponding component of $y_r$ is  than $y_t$ or otherwise.

The model states $\check y_t$ has the same distribution as $\check s_t$ where $s_t$ is  generated as in \eref{gfac}.  For given $\theta$ and $\rho$, the percentiles $\check s_t$ are estimated by simulating a large number $N$ of $s_t$ from \eref{gfac} and computing
$$
\check s_{t} \approx \frac{1}{N}\sum_{r=1}^N(s_{r}<s_{t})\ , \qquad t=1,\ldots,N\ .
$$
The distribution of the $\check s_t$ is compared to the distribution of the $\check y_t$.   Good estimates of $\theta$ and $\rho$ will lead to good correspondence between the outcomes $\check y_t$ and $\check s_t$.

One way to check whether the distribution of the $\check s_t$ is similar to that of the $\check y_t$ is to divide the unit hypercube into smaller volumes or cells indexed by $c$ and count the number of $\check y_t$ in each cell.   These are then compared to the expected number $e_c$ calculated for given $\theta$ and $\rho$ by simulating a large number of $s_t$ and calculating the corresponding $\check s_t$.  An appropriate choice for $\theta$ and $\rho$ is indicated by a low value of chi--squared goodness of fit statistic
\begin{equation}\label{chisq}
X^2\equiv \sum_c \frac{(o_c-e_c)^2}{e_c}\ ,
\end{equation}
where the $c$ sum extends over all cells.  In practice $X^2$ in  \eref{chisq} is numerically minimized  over a grid of values of $\theta$ and $\rho$.

\section{Estimating total loss quantiles}

Under the model \eref{gfac} it is easy to simulate the distribution of total loss given the parameters $\lambda$ and $\rho$.   For each of the $N$ simulated values of the state vector $s_t=Z\alpha_t+\Psi\eps_t$ the corresponding estimated loss is
$$
\ell_t = 1'(\hat F^-\circ \hat G)(s_t)=1'\hat F(\check s_t)\ ,
$$
where $1$ is a vector of ones and $\hat F$ and $\hat G$ are the vectors of estimated marginal distributions.   In particular $\hat G(s_t)=\check s_t$ where the latter is determined with reference to the $N$ simulated $s_t$.

Ranking the $\hat\ell_t$, $t=1,\ldots,N$ yields the $1/N$ quantiles of the loss distribution.   These quantiles are conditional on the estimated copula parameters in $\lambda$ and $\rho$ and the assumed or estimated marginals in $F$.  However under a suitably large sampling effort $N$, the quantiles will be independent of the approximation involved in $G$.

$$
\ell_t=1'F^-(\check s_t)\ , \qquad s_t=Z\alpha_t+\Psi\eps_t\ ,
$$
where $F$ is the vector of marginal distributions and $F^-$ the vector of componentwise inverses.  The marginal distributions $F$ is either specified analytically, or determined empirically.
 \begin{itemize}
   \item This case requires proper spanning of the actual losses. Suppose $y_t$ are the vectors of observed losses and $\check y_t$ the corresponding vector of percentile ranks.  Then the total loss distribution is that of the $\ell_r$, $r=1,\ldots,n$ where
$$
\ell_r = 1'y_r\ ,\qquad y_r \check = s_t\ , \qquad s_t=Z\alpha_t+\Psi\eps_t\ ,
$$
where the middle expression indicates the components of $y_r$ are chosen from the components of the available $y_t$ so that $\check y_r$ is as close as possible to $\check s_t$.  Thus in this case a large number of $s_t$ are simulated and converted to percentile ranks.   Each observed $y_r$ is then associated with a simulated $s_t$ with the same, or approximately the same, percentile rank.

   \item  In the case where $F_*$ is available (either the true marginal distribution or an estimate) then the distribution of losses is built up from
       $$
       \ell_t =1'F_*^-(\check s_t)\ , \qquad s_t=Z\alpha_t+\Psi\eps_t\ ,
       $$
       Thus in this situation a large number of $s_t$ are simulated from the model from which the percentile ranks $\check s_t$ are computed.   These $\check s_t$ are then used to compute $\ell_t$ corresponding to each simulation $t$.
 \end{itemize}

Suppose $y_t$ represents a vector of losses at time $t$ on each of $p$ classes of business.   Then $x_t\equiv 1'y_t$ is the total loss and of interest is the quantile of $x_t$ corresponding to the percentile $0<\pi<1$.  In applications typical values for $\pi$ are 0.95 and 0.99.

To estimate the quantile of $x_t$.

Consider first the two dimensional case.  Percentile $\pi$ in two dimensions is carved out of the unit cube as follows.  Suppose firstly $y_{2t}=0$.  Then $y_{1t}$ is the quantile corresponding to $\check y_{1t}=\pi$.

Suppose $F_*$ is vector or marginal distribution functions and consider for vector $0<u<1$
$$
x\equiv 1'F_*^-(u)\ .
$$
This is the loss when each line of business is at the percentiles given by $u$.  Taking the total differential yields
$$
\de x = 1'\de F_*^-(u) = \frac{-\de u_1}{f_1(y_1)}+\cdots +\frac{-\de u_p}{f_2(y_p)}\ ,
$$
where $y=F_*^-(u)$.  If $\de x=0$ and $p=2$ then
$$
\frac{\de u_1}{f_1(y_1)}=\frac{-\de u_2}{f_2(y_2)}\qquad\Rightarrow\qquad
-\frac{\de u_2}{\de u_1} = \frac{f_2(y_2)}{f_1(y_1)}\ .
$$
This is the slope of an iso--loss curve and is the rate at which the percentile rank $u_2$ must be changed when the percentile ranks $u_1$ is changed in order to maintain the same level of total loss.

Suppose the Pareto survival curve
$$
S(x) = \left(\frac{\theta}{x+\theta}\right)^{\alpha}
$$
This implies
$$
f(x)=\frac{\alpha S(x)}{x+\theta}\ , \qquad S^-(u)= \theta (u^{-1/\alpha}-1)\qquad\Rightarrow\qquad f\{S^-(u)\}=\frac{\alpha u^{1+1/\alpha}}{\theta}\ .
$$
Hence in this case
$$
\ln \left|\frac{\de u_2}{\de u_1}\right|= \ln \frac{\alpha_2\theta_1}{\alpha_1\theta_2} +\left(1+\frac{1}{\alpha_2}\right)\ln u_2-\left(1+\frac{1}{\alpha_1}\right)\ln u_1\ .
$$
Note if $\alpha_1=\alpha_2=\alpha$ then
$$
\ln \left|\frac{\de u_2}{\de u_1}\right|= \ln\frac{\theta_1}{\theta_2} + \left(1+\frac{1}{\alpha}\right)\ln \frac{u_2}{u_1}
$$

 The negative of the slope, $-\de u_2/\de u_1$ is the (marginal) rate of quantile substitution (MRS).  MRS depends only on the marginal distributions $F_*(u)$.
\newcommand{\s}{\sigma}

The elasticity of substitution is defined as
$$
\s (u_1,u_2)\equiv \frac{\de\ln(u_2/u_1)}{\de \ln (\mathrm{-\de u_2/\de u_1})}
$$
which is the percentage change in the relative size of the quantiles given a percentage change in the marginal rate of  substitution.

   It would be nice to be able have a functional form for the components of $F_*(u)$ so that RQS take a simple form.  That is we estimate some nice functional form

Suppose we have
\begin{equation}\label{ces}
    s(u) =\left( \sum_{i=1}^p a_i^{\frac{1}{\s}}u_i^{\frac{\s-1}{\s}}\right)^{\frac{\s}{\s-1}}\ .
\end{equation}
Then the $p$ marginal distributions are parametrized by the $p$ numbers $a_j$ and the constant elasticity of substitution $\s$.

To see the meaning of the $a_i$ note $s(0)=0$ while   $s(1)=\sum a_i^{1/(\s-1)}$ which is the maximum loss.  Further if $u$ is  all zeros except in component $i$ where it is $u_i$ then (\ref{ces}) reduces to
$$
y_i=F_i^-(u_i)=a_i^{1/(\s-1)}u_i\qquad\Rightarrow\qquad u_i=F_i(y_i)=a_i^{1/(1-\s)}y_i
$$
Thus $F_i(y_i)$ is linear in the tail up to some maximum point $y_i=a_i^{1/(\s-1)}$.  Note that the maximum of $\ln y_i$ is $(\ln a_i)/(\s -1)$.

Iso--loss lines can be easily constructed from

Given $u$ we can easily determine the total loss to which this corresponds $s=1'F^-(u)$.  By simulating from the copula of $u$ we can determine the frequency distribution of $s$.  In particular if $\Psi$ is the distribution of $s$ then $G(s)=G\{1'F_*^-(u)\}$ is uniform.  In other words
$G\circ 1'\circ F_*^-$ is a mapping from copula distributed $u$ to uniform random variables.

The rate of quantile substitution depends only on the relative magnitudes of the densities.  The rates are used to construct a iso--loss contours.   Integrating the density of copula above the iso--loss curve corresponding to $s$ yields the probability of exceeding the loss $s$.

A sampling scheme is as follows.
$$
s=1'\hat F_*^-(u)\ , \qquad u\sim C
$$
Alternatively to find out what quantile a given $s$ corresponds to, first construct the iso loss line corresponding to $s$.   Repeatedly draw $u$ and see the proportion of those $u$ for which $1'\hat F_*^-(u)$ exceed $s$.

An improvement is where we first select $u_1$ uniformly from $(0,1)$.   If $y_1\equiv F_1^-(u_1)>s$ then stop or alternatively if $F_1(s)>u_1$ then stop.  If not compute draw $u_2\sim u_2|u_1$ and $F_2(s-y_1)>u_2$ then stop.

the positive number $s-F_1^-(u_1)$.  This is the number $y_2=F_2^-(u_2)$ has to exceed in order for the sum to exceed ...   That is we want
$$
F_2\{s-F_1^-(u_1)\}
$$

Accept--Reject sampling can also be used.   We draw

Consider $p_1u_1+p_2u_2$ where $p_1$ and $p_2$ are prices.  The prices may represent the cost of reducing each of the quantiles.   To minimize $s$ subject to

In the two dimensional case.

The aim is, to find $\lambda$ and $\rho$  consistent with the observed percentile ranks $y_j^\#$.   This can be done as follows.

\section{Junk}
Thus we have $C_{\lambda,\rho}$ and our model is
$$
y\sim C_{\lambda,\rho}\circ F_*\ , \qquad y\sim F_*^-\circ C_{\lambda,\rho}
$$
Note the left hand side states how probabilities associated with $y$ are calculated, namely
$$
P(y\le\tilde y) = (C_{\lambda,\rho}\circ F_*)(\tilde y) \equiv C_{\lambda,\rho}\{F_*(\tilde y)\}\ ,
$$
while the right hand side indicates how one generates $y$: first you generate the uniforms according the copula, then you use these uniforms to interpolate out of the marginals: namely
$$
y = F_*^-(u)\qquad \mathrm{where}\qquad u\sim C_{\lambda,\rho}\ .
$$
Alternatively we can thus write the setup as
$$
y=F_*^-(s^\#)\ , \qquad s=\Lambda f + D\eps\ .
$$

\section{Connection to time series models}
A time series version of this is
$$
\check y_t=\check s_t\ , \qquad s_t=Z \alpha_t + \Psi u_t\ , \qquad u_t\sim N(0,I)\ , \qquad \alpha_t\sim \chi^2_1\ .
$$

These generated $s$ values are used to find synthesized $s(y_j)$ values corresponding to the $y_j$  such that $s^\#(y_j)=y_j^\#$.  We then measure
$$
\min_\psi \sum_{j=1}^n\|s_j-s(y_j)\|^2
$$

 and construct the empirical distribution of the percentile ranks $s_j^\#$, $j=1,\ldots,N$.  Corresponding to each $y_j^\#$, pick out
$s(y_j^\#)$, which is the generated $s$ with percentile ranks $s^\#$ closest to that of $y_j^\#$.
Then the log--likelihood of $(\lambda,\rho)$ based on  $y_j^\#$, $j=1,\ldots,n$ is
$$
\ell(\lambda,\rho) \approx \sum_{j=1}^n \ln f\{s(y_j^\#)|\lambda,\rho\}\ ,
$$
where here $f$

\section{Copula properties}

Consider a multivariate probability distribution $F$.  Define $F_*$ as the vector of marginal distributions derived from $F$.  In particular if $y\equiv(y_1,y_2,\ldots, y_p)$ then
$$
F_*(y) \equiv \left(
           \begin{array}{c}
             F(y_1,\infty,\ldots,\infty) \\
             F(\infty,y_2,\ldots,\infty) \\
             \vdots \\
             F(\infty,\ldots,\infty,y_p) \\
           \end{array}
         \right)\equiv \left(
           \begin{array}{c}
             F_1(y_1) \\
             F_2(y_2) \\
             \vdots \\
             F_p(y_p) \\
           \end{array}
         \right)\ .
$$
In other circumstances the vector of marginals $F_*$ is specified directly.

A copula is a probability distribution $C$ on the unit hypercube with uniform marginals.  Thus $C_*(y)=y$ for  $0\le y\le 1$ implying $C_*=1$.

The usefulness of copulas, arises as follows.  Consider a multivariate distribution $F$ and define the distribution generated with copula $C$ and given marginals $F_*$:
 \begin{equation}\label{Fx}
    F_C\equiv C\circ F_*\ ,
\end{equation}
Then $F_C$ is a joint distribution with $(F_C)_*=F_*$ since $F_C$ has marginals
$$
(C\circ F_*)(\infty,\ldots,y_i,\ldots,\infty)= C\{1,\ldots,F_i(y_i),\ldots,1\} = C_i\{F_i(y_i)\}=F_i(y_i)\ .
$$

Conversely given a joint distribution $F$ with marginals $F_*$ and $F_*^-$ as the componentwise inverse to $F_*$ define the copula generated from $F$ as
\begin{equation}\label{Cu}
    C_F\equiv F\circ F_*^-\ .
\end{equation}
Then $C_F$ is a copula since it has uniform marginals:
$$
(C_F)_i(u_i)=(F\circ F_*^-)(1,\ldots,u_i,\ldots,1)= F\{\infty,\ldots,F^-_i(u_i),\ldots,\infty\} = u_i\ .
$$
Every $F$ has a copula representation which is clear from
$$
F_{C_F}= C_F\circ F_*= F\circ F_*^-\circ F_*=F\ .
$$
Finally note
$$
C_C=C\ , \qquad C_{F_C}=F_C\circ (F_C)_*^-=C\circ F_*\circ  F_*^-=C\ .
$$

\section{Copula properties}
\begin{itemize}
    \item $C_*(y)=y$.  If $y\sim F_C$ then $F_*(y)\sim C$.  If $u\sim C_F$ then $F_*^-(u)\sim F$.
    \item  If $H_*$ is the componentwise  vector of univariate monotonic functions then
$$
C_{F\circ H_*^-}\equiv F\circ H_*^- \circ(F\circ H_*^-)_*^-=F \circ F_*^-\equiv C_F\ .
$$
Hence copulas are invariant to monotonic transformations.
    \item The density associated with $C_F=F\circ F_*^-$ is
    $$
    \frac{f\circ F_*^-}{\Pi (f_*\circ F_*^-)}\ ,
    $$
    where $f$ is the density associated with $F$ and $f_*$ is the vector of marginal densitities.  If $f=\Pi f_*$ (ie independence) then $f\circ F_*^-=\Pi (f_*\circ F_*^-)$ and the density is identically 1.
    \item The Gaussian copula with correlation matrix $R$ is the copula $C_{\Phi^R}$  where $\Phi^R$ is the Gaussian distribution with mean 0 and covariance matrix $R$. Since $R$ is a correlation matrix $(\Phi^R)_*=\Phi_*$, a vector of standard normal distributions, and $C_{\Phi^R}=\Phi^R\circ \Phi_*^-$.   The meta--Gaussian model is
\begin{equation}\label{metaG}
F_*(y)\sim C_{\Phi^R}\qquad\Leftrightarrow\qquad F_*(y) =\Phi_*(\eps)\ , \qquad \eps\sim N(0,R)\ .
\end{equation}
Matrix $R$ is estimated using the average cross product matrix of  the normits  $(\Phi_*^-\circ F_*)(y)$.
\item The meta--gamma model  is
$$
F_*(y)=\Gamma_\psi(1 \eta + \Psi\eps)\ , \qquad (\eta,\eps')'\sim \Gamma(\mu,\nu)\ ,
$$
where $\psi$ is a vector of parameters, $\Psi=\diag(\psi)$ and $\Gamma_\psi$ the vector of marginal distributions associated with $1\eta+\Psi\eps$.
\item  The Levy copula is $L$ such that $L_*(u)=u$.  Thus it is a copula on the unit hypercube suitable extended to $u>1$.
\item The independence and perfectly dependent copulas is defined as $\Pi\equiv\Pi\ 1_*$ and $\vee\equiv\min$ respectively, where $1_*$ indicates the vector of identity functions.  These arise as follows:
$$
C_{\Pi F_*}\equiv(\Pi F_*)\circ F_*^-= \Pi\ 1_*\ ,\qquad C_{\vee}=\ .
$$
The perfectly dependent copula implies a single source of noise:
$y=F_*^-1u$ with $u\sim U$
where $1$ is a vector of  identity functions of one variable.

\item  Any copula is ``symmetric" in the sense that if $C$ is the copula of 2D vector $u$ then it is also the copula of the $u$ with the components interchanged.  This follows since suppose the density associated with $C$ is $c$.   Then since $c(u_1)\equiv 1\equiv c(u_2)$,
$$
c(u_1|u_2) = \frac{c(u_1,u_2)}{c(u_2)} =c(u_1,u_2) =\frac{c(u_1,u_2)}{c(u_2)}= c(u_2|u_1)
$$

\item If $C$ is a copula then $C\circ (1-)$ is the ``survival" copula.  Here $(1-)$ is defined such that $(1-)u=1-u$.  To prove this result note that
\end{itemize}

\section{Factor copula models}
The simplest factor copula model is as follows. Given a vector of nonnegative weights $\psi\ge 0$, suppose $G$ is the distribution of
$$
1\eta+\Psi\eps\qquad\mathrm{where}\qquad \eta\sim\chi^2_1\ , \qquad \eps\sim N(0,I)
$$ with $\eta$ and $\eps$ independent and $\Psi=\diag(\psi)$.  Further suppose $G_*$ is the vector of marginal distributions associated with $G$.   Then $u\equiv G_*(1\eta+\Psi\eps)$ is a vector of uniform, albeit dependent, random variables. Hence the distribution of  $u$ is a copula.

In terms of this development we suppose $y$ is generated by the marginals $F_*$ and copula derived from $G$ if
$$
F_*(y) =  G(\Lambda f +\Psi\eps)\qquad\Leftrightarrow\qquad y\sim F_*^-\circ C_G \ .
$$
These steps make it clear how things are structured.  First, the factor scores are generated.  Then transformed to uniforms and finally transformed from the uniforms to the things in the tails.

\section{Generated practical copula structures}
To simulate the model for given $F_*$ and given $\psi$, we first generate the many values of the scores $1f+\Psi\eps$. These scores are then transformed to percentile ranks and these percentile ranks are used to pull out the corresponding values from the marginal distribution.

Initially suppose $f=\chi^2_1$.

 $G_*(1f+\Psi\eps)$ one first simulates $1\eta+\Psi\eps$ and then applies the  $G_*^\psi$.  However a simpler, more practical procedure is simply to simulate a large number of $1\eta+\Psi\eps$ and then compute empirical quantiles corresponding to each component.  Figure \ref{uv} displays realizations in the bivariate case for four different values of $\psi$.   In each case the first component of $\psi$ is zero while the second component is the given positive value.

   Each of these figures was generated as follows.
\begin{enumerate}
  \item For $t=1,\ldots,n=10000$ generate $\eta_t\sim\chi^2_1$ and $\eps_t\sim N(0,I)$ of order 2 and construct $\gamma_t\equiv 1\eta_t+\diag(\psi)\eps_t$, $t=1,\ldots,n$.
  \item Compute the quantiles associated with $\gamma_{it}$ for each $i=1,2$.
\end{enumerate}

\section{Wang article}

Suppose $x$ is a vector of losses (random).  Assume from $x$ you derive (componentwise) a vector of risk capitals $r(x)$ where $r$ works componentwise.   There are two rules for calculating capital:
\begin{itemize}
  \item Basel Accords: $\iota'r(x) = \sum_ir_i(x) =\sum_ir_i(x_i)$.
  \item US Insurance NAIC RBC: $\sqrt{\sum_ir_i^2(x_i)}$.
  \item Company models:  Individual probability distributions for a company's risks are quantified.  Then assuming a correlation matrix the aggregate loss distribution is calculated yielding percentiles etc.   The total economic capital is then distributed back to the business units according to
      $$
      \pi_i = \frac{\iota'R u_i}{\iota'R\iota}\ , \qquad \iota = \sum_i u_i
      $$
      where $u_i$ is a vector of zeros except in position  $i$ where it is 1.
\end{itemize}

Next states that yield spreads exaggerate default rates.  Goes on to posit the model for the price of risk $h_t$ where
$$
h_t = \hat\mu_t + \lambda_t\sigma_t\ ,\qquad \hat \mu_t = \mu_t + \eps_t\ , \qquad \cov(\eps_t) = (\partial\sigma_t) C(\partial\sigma_t)
$$
where $\lambda_t$ is a scalar stochastic process, $C$ is a correlation matrix and $\partial \sigma_t$ is the diagonal matrix formed from the standard deviation vector $\sigma_t$. Also $\mu_t$ is the true mean value of the loss: ie $\mu_t=\E(x_t)$.  Assume $\cov(\eps_t,\lambda_t)=0$ implying
$$
\cov(h_t) = (\partial\sigma_t) C(\partial\sigma_t) + \cov(\lambda_t)\sigma_t\sigma_t'
$$
\subsection{Corner tail correlations}
The proposed measure of tail correlation proceeds as follows.   take the percentile ranks and map to the z--scores ie $z_j=(\Phi^{-1}\circ F_*)(x_j)$.  Assuming $x_j$ is bivariate, write $\pi(\alpha)$ as the proportion of the $x_j$ falling in the lower corner.  The lower tail correlation is the solution for the off diagonal entry in the correlation matrix $R$ of
$$
(\Phi^R\circ\Phi^{-1})(1\alpha) =\E[\Pi \{\hat F_*(x_j)<1\alpha\}]\ .
$$
where $\E$ denotes the empirical expectation (ie fraction).  Why not try and find the optimal $R$.

\section{Copula factor model}

Suppose $\p$ computes the ``uniforms" of a random variable. Then for any monotonic transform $f$, $\p\circ f=\p$ and hence $\p\circ \p=\p$.  Further for a monotonic decreasing function $\p\circ f = 1-\p$ implying $\p\circ (1-\p) = 1-\p$.  Also $\p\circ -=1-\p$.

 And suppose $\psi$ a vector of weights.  Then $y$ is said to be generated by the copula factor model if
$$
\p(y_t)= \p(\Lambda f_t+\Psi\eps_t)\ , \qquad f_t\sim\chi^2_\nu\ \mathrm{or}\  t_\nu\ , \qquad \eps_t\sim N(0,\sigma^2I)\ ,
$$
where $\Psi$ is a diagonal matrix with diagonal $\psi$.
Without loss of generality assume the first component of $\psi$ is zero.

\subsection{Different specifications}

Here show the effect of different $\Lambda$ and $\Psi$ and perhaps replacing $\Lambda f_t+\Psi\eps_t$ by eg $\Lambda(f_t)+\Psi\eps_t$.

\subsection{Rank correlation}

Suppose $\R(y_t)$ is the rank correlation matrix of $y_t$: that is $\R(y_t)\equiv \cor\{\p(y_t)\}$

\subsection{Estimating the copula factor model}
Consider $\hat\p(y_t)$.  If we know the cdf $\p_x$ of $x_t\equiv\Lambda f_t+\psi\eps_t$ then $\hat x_t=(P_x^-\circ \hat P)(y_t)$.  However we don't know $\p_x$.   However simulate $x_s$, $s=1,\ldots,N$ and reorder the simulated components of $x_s$, $s=1,\ldots n$ to yield $\tilde x_t$ so that $\hat\p(\tilde x_t)=\hat\p(y_t)$.  In other words we order the simulated components of $x_s$ according to the order specified in $y_t$.

What is the relationship of this to finding $\psi$ such that the rank correlation is preserved.  In this we simulate $x_t$ from the model and adjust $\psi$ till we get a rank correlation for the $x_t$ equal to the observed rank correlation.  Obviously this procedure cannot tell us anything about order of things.

So we use the procedure of the last paragraph to find $\psi$.   Then for the given $\psi$ we simulate $x_s$, $s=1,\ldots,n$ and in turn $\tilde x_t$.   We use the $\tilde x_s$ to infer about the $f_t$.

Given the estimate $\tilde x_t$ of $x_t=\Lambda f_t+\Psi\eps_t$ we can do a PC analysis on $\tilde x_t$.

   Then $\hat\p(\tilde x_t)=\hat\p(y_t)$ and $\tilde x_t$ is our estimate.

 and in particular $+/\hat\p(y_t)$.   If we know
$\Lambda f_t$ then take

Consider the the principal components of $\hat\p(y_t)$.   These
pick up the major directions of variation.
The vector $\psi$ is estimated by the following steps:
\begin{enumerate}
  \item Calculate the principal components of $\hat \p(y_t)$ to yield say $UDU'$.
  \item If $u$ is the first column of $U$ compute $u'\hat \p(y_t)\}\approx \p(f_t)$.  This the vector of weights.
  \item Minimize
\end{enumerate}

Given $\psi$ and hence $\Psi$ we simulate $1f_t^s+\Psi\eps_t^s$ and reorder each scalar series in  each simulation to yield $x_t^s$ such that $\hat \p(x_t^s)=\hat \p(y_t)$. Note that $x_t^s$ is $y_t$ interpolated back into the EDF of $1f_t^s+\Psi\eps_t^s$.

\subsection{The two variable case}

To illustrate estimation consider first the case where $y_t$ is two dimensional $\Lambda=1$.   Suppose $r$ is the correlation between the ranks the two components in $\hat\p(y_t)$ -- that is the rank correlation between the components in $y_t$.  Then we want to estimate $\psi$ subject to
$$
\cor\{\hat\p(1f_t+\Psi\eps_t)\}=\cor\{\hat \p(y_t)\}\ .
$$
Notice the correlation decreases with $\psi$.   So we simulate $1f_t+\Psi\eps_t$ and compute $\cor\{\p(1f_t+\Psi\eps_t)\}$.  Then

 Put $y$ as the $2\times n$ vector of $y_t$, $t=1,\ldots,n$.  Write $x_t=\Lambda f_t+\Psi\eps_t$ and without loss of generality $\Psi=\diag(0,1)$. For given $s=\sigma$ generate a simulated path of $x_t$ denote $x^s$.  Note $x^s$ is $2\times n$.  Rank each row of $x^s$ according to the ranks of $y$ denoted $\tilde x^s$ and redefine $s$ as  the standard deviation of   $\Delta \tilde x^s$ where the latter subtracts the first row from the second.  Cycle through this procedure as in Gibbs sampling to get a distribution of $s$.  This is the posterior distribution of $\sigma$.

Then calculate the units of each component in  $y_t$ and calculate its value in the empirical cdf of the corresponding component of $x_t$.   To achieve this rank, for each $i$ the  $x_{it}$, $t=1,\ldots,n$ according to the ranks of  $y_{it}$, $t=1,\ldots,n$.  Suppose this yields $\tilde x_t$.  This is equal to $ \eps_{2t}$.  So take the standard deviation of so as to get an estimate of $\sigma$.

 Thus the joint distribution is generated with the meta--gamma copula $C^\psi\equiv G^\psi\circ (G_*^\psi)^-$.

Maybe the model should be changed to something like this
$$
F_*(y) = H_*[1\Phi^-\{G(\eta)\}+(\partial\psi)\eps]\ , \qquad \eta\sim\chi^2_1\ , \qquad \eps\sim N(0,I)\ .
$$

\subsection{Estimation of copula parameters}
  Estimation and testing consists of the following steps:
\begin{enumerate}
  \item Compute the empirical cdfs $\hat F_*(y)$ and the percentile ranks $u_t=\hat F_*(y_t)$.
  \item Draw $\eta_i\sim \chi^2_\nu$ and $z_i\sim N(0,1)$ and form $w_i=1\eta_i+(\partial \theta)z_i$ for $i=1,\ldots,N$. Use the results to form an empirical estimate of $G_*^\theta$
  \item Use these to form an empirical estimate of $v_t(\theta)=G_*^{\theta-}(u_t)$.
  \item Compute
  $$
  \eps_{t}(\theta)\equiv \frac{v_{2t}(\theta) - v_{1t}(\theta)}{\theta}\ , \qquad t=1,\ldots,n\ .
  $$
  \item Compute the log--likelihood
  $$
  \ell(\theta) = \sum_{t=1}^n\eps_t^2(\theta)
  $$
  \item Choose $\theta$ such that $\ell(\theta)$ is minimum
\end{enumerate}

Here are some assertions I think are true about the meta--gamma.
\begin{itemize}
  \item The means on the $\eta_i$ or $\eps_i$ should not make a difference since we are transforming to percentiles.  Or maybe it is just the relative means or something.
  \item By tuning the gamma's we can pretty much describe any chi-squared/normal behaviour
  \item The sum of independent gamma's is gamma so we can easily figure out $G_\psi$ etc.
  \item If $\psi\rightarrow 0$ then the components of $y$ approach perfect dependence.
  \item If $\psi\rightarrow \pm\infty$ then the components of $y$ approach independence.
\end{itemize}

\section{Weibull losses}

Suppose the Weibull distribution function
$$
u=F(y)=1-\exp\left\{-\left(\frac{y}{\alpha}\right)^\beta\right\}\qquad\Rightarrow\qquad
F^-(u) = \alpha\left\{-\ln(1-u)\right\}^{1/\beta}\ .
$$
indicating that if $u$ is uniform then the right hand transformation is Weibull.
With this specification
$$
s(u) = \sum\alpha\left\{-\ln(1-u)\right\}^{\frac{1}{\beta}}\ ,
$$
Further note the density of corresponding to $F(y)$ is
$$
f(y) = \frac{\beta}{\alpha} \exp\left\{-\left(\frac{y}{\alpha}\right)^\beta\right\}\left(\frac{y}{\alpha}\right)^{\beta-1}\ = \frac{\beta}{\alpha}\left(\frac{y}{\alpha}\right)^{\beta-1}\{1-F(y)\}.
$$
implying the product out the front is the hazard.

Further.
$$
\de s = \sum\frac{\de u}{f\{F^-(u)\}}= \sum \frac{\alpha\left\{-\ln(1-u)\right\}^{\frac{1}{\beta}-1}}{\beta(1-u)}\ \de u\ .
$$
which defines the iso--loss curves.

In practice the parameters $\alpha$ and $\beta$ are estimated for each marginal distribution $F_i(y_i)$.  The mean and variance associated with the marginal distribution $i$ are then
$$
\alpha\Gamma\left(1+\frac{1}{\beta}\right)\ , \
\qquad \alpha^2\left\{\Gamma\left(1+\frac{2}{\beta}\right)-\Gamma^2\left(1+\frac{1}{\beta}\right)\right\}
$$

\section{Open question}

We note that $s(u)=\sum F_i^-(u_i)$ for some appropriate functions $\phi_i$.  The question is whether we can structure things such that this sum is nice.   One procedure is where we first choose $u_1$ uniformly and compute $F_1^-(u_1)$.  Next choose $u_2\sim u_2|u_1$ and compute $F_2^-(u_2)$.  Or we can just do the Gibbs sampling trick where we take $u_1|u_2$ then the other way round.

\section{Logistic losses}

Suppose
$$
s(u) = \sum \frac{\alpha u^\beta}{1-u^\beta} = \sum\frac{\alpha}{u^{-\beta}-1}
$$

\section{Iso--loss curves}

\section{Estimation in old notation}
To estimate $\lambda$ take the observations $y$ and initially transform to the quantiles
$$
u\equiv F_*(y) = G_\lambda(\chi_1^2+\lambda\cdot\eps)\ .
$$
Next, for given $\theta$ transform $u$ as
$$
G_\theta^-(u) = (G_\theta^- \circ G_\lambda)(\chi_1^2+\lambda\cdot\eps)\approx (G_\theta^-\circ G_\lambda)(\chi_1^2) + (G_\theta^-\circ G_\lambda)'(\chi_1^2)\lambda\cdot\eps\ .
$$
If $\theta=\lambda$ then this reduces to $\chi_1^2+\lambda\cdot\eps$ which has the known distribution. Hopefully things are invariant to the base category.

In this formulation $\lambda$ is unknown.  To estimate it proceed as follows:

If (\ref{ge}) holds $\hat\eps_t(\lambda)\sim N(0,I)$.  So the aim is to find $\theta$ such that

\section*{Generalizations}
More generally suppose
\begin{equation}\label{ge2}
y=(F_*^-\circ G_\lambda)(X\chi_1^2+H\eps)\ , \qquad \eps \sim N(0,I)
\end{equation}
To estimate we

\section*{Bivariate copulas}
In the following $X$ and $Y$ are scalar random variables.   The aim is to synthesize a bivariate copula with required properties.
\begin{enumerate}
  \item Consider
  $$(G_{X+Y}\circ G_X^-)(u) \equiv G_{X+Y}\{G_X^{-}(u)\}\ .
  $$
  This is the quantile in the $X+Y$ distribution if $X$ is at quantile $u$  in the $X$ distribution and $Y=0$.
      Thus if $G_Y(0)=0$ (ie $Y\ge 0$) it is the minimum quantile of $X+Y$ if $X$ is at quantile $u$ of the $X$ distribution.
  \item  Suppose $X$ and $Y$ are independent chi--squareds each with 1 degree of freedom.   Then $X+Y$ is chi--squared with 2 degrees of freedom.   Hence $(G_{X+Y}\circ G_X^-)(u)$ is the chi-squared 2 degrees of freedom distribution evaluated at quantile $u$  of the chi-squared 1 degree of freedom distribution.
  \item  Suppose $X\sim\chi_1^2$  and $Y\sim N(0,\sigma^2)$.   Then $(G_{X+Y}\circ G_X^-)(u)$ is the $\chi^2_1+ N(0,\sigma^2)$ distribution evaluated at quantile $u$ of the $\chi^2_1$ distribution.
  \item Consider
  $
  G_{X+Y}\{G_X^-(u)+G_Y^-(v)\}
  $.
  This the quantile of $X+Y$ when $X$ is at quantile $u$ and $Y$ is at quantile $v$.

  \item  Consider $G_{X+Y}\{G^-_X(u)+Y\}$.  This is a random variable -- the quantile in the $X+Y$ distribution when $X$ is at quantile $u$ of the $X$ distribution.  Further
      $
      \E\left[ G_{X+Y}\{G^-_X(u)+Y\}\right]$ and $Var\left[ G_{X+Y}\{G^-_X(u)+Y\}\right]$ are the
      expected value and variance of the quantile in the $X+Y$ distribution if $X$ is at quantile $u$ in the $X$ distribution, respectively.

  \item  Suppose $X\sim \chi^2_1$ and $Y\sim N(0,\sigma^2)$.  Then
      $$
      \E[G_{X+Y}\{G_{X}^-(u)+Y\}]=u\ , \qquad Var[G_{X+Y}\{G_X^-(u)+Y\}]=
      $$
      To prove the first relation, note that
      $$
      P\{G_X^-(u)+Y<y\}=P(Y<y-G_X^-(u)\} = G_Y\{y-G_X^-(u)\}\ .
      $$
      that is a shifted version of $G_Y$.
\end{enumerate}
\subsection*{Runoff triangles and copulas}

Let $L_k$ be the liability distribution associated with runoff triangle $k$.   Suppose the joint distribution is modelled with a copula $C(u,v)$.  Thus the joint distribution of $(X,Y)$ is
$$
y\sim C\circ F_*
$$
Want $\iota'y$.  Let's think of things in two dimensions:
\begin{enumerate}
    \item Draw $u\sim C$ and
    \item Put $y=F_*^-u$
    \item Determine $y\sim F_*^-u$
    \item AHP for determining a copula
    \begin{enumerate}
        \item For each $u$ give probability distribution of $v$
        \item Draw $u_1\sim U$, $u_2\sim C_{2|1}$
        \item $y_1=F_1^-u_1$, $y_2=F_2^-u_2$.
    \end{enumerate}
\end{enumerate}

\subsection*{AHP with copulas}

Suppose $0\le u \le 1$ is given and let $U_1$, $U_2$ and $U_3$ be risk quantiles.  Suppose we know $U_1>u$.   We now ask how much more likely this makes $U_2>u$ and $U_3>u$.  Similarly if $U_2>u$ how much more likely does this make $U_1>u$ and $U_3>u$? In tabular format:

If $U_1>u$ what is the probability of:

\begin{tabular}{|c|c|c|c|c|c|}
  \hline
  % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
  $P(U_1>u)$ & 0.5 & .25 & 0.10 & 0.05 & 0.025 \\
  \hline
  $P(U_2>u|U_1>u)$ & 1 & 1 & 1 & 1 & 1\\
  $P(U_3>u|U_1>u)$ & 0.5 & 0.25 & 0.10 & 0.05 & 0.025\\
  \hline
\end{tabular}
\\\\
This table indicates $U_2$ is perfectly dependent while $U_3$ is independent.
Since
$$
P(U_2> u|U_1> u) =\frac{P(U_2>u, U_1>u)}{P(U_1>u)} = \frac{P(U_1>u|U_2>u)P(U_2>u)}{P(U_1>u)}=P(U_1>u|U_2>u)\ ,
$$
it makes no further sense to ask the question the other way round.

\subsection*{Conditional Probability}

We have a risk vector $y$.   Define $u=F_*(y)$.   Then the marginal distributions of $u$ are uniform.   Next choose $u_1$.   We then have an effect on the conditional distributions of the remainder.   Hence construct $F_*(u|u_1)$ which again have uniform marginals, albeit of one dimension less.   The advantage is that if the effect of $u_1$ is simple on all the uniform marginals then we can keep track of everything and hopefully

\subsection*{Example copulas}

\subsubsection{Clayton} This depends on a single parameter $\delta$  and is defined as
$$
C(u)\equiv\left(\Sigma u^{-\delta}-d+1\right)^{-1/\delta}
$$
It is the distribution of
$$
u=\left\{1-\frac{\ln(v)}{\gamma}\right\}^{-1/\delta}
$$
where $\gamma \sim \Gamma(\delta^{-1},1)$ and $v\sim U^d(0,1)$.
In the last step things are done componentwise.

\subsubsection{Gumbel}
This also depends on a single parameter $\delta$ and is defined as
$$
C(u)\equiv  \exp\left[\left\{-\Sigma (-\ln u)^{\delta}\right\}^{1/\delta}\right]\ , \qquad \delta\ge 1\ .
$$
It is the distribution of
$$
u= \exp\left\{- \left(-\frac{\ln v}{s}\right)^{1/\delta}\right\}\ ,
$$
where $s\sim Stable$ and $v\sim U^d(0,1)$.

\subsection*{Problem}

Note that for a bivariate copula $f(v|u)=f(u,v)/f(u)=f(u,v)=f(u|v)$.  Choosing $u\sim f(u)$ and then $v\sim f(v|u)$ produces a draw $(u,v)\sim f(u,v)$.  But how do we constrain

So why does

One distribution is the beta distribution
$$
    f(v|u)=cv^{\alpha-1}(1-v)^{\beta-1}\ , \qquad \E(v|u)=\frac{\alpha}{\alpha+\beta}\ , \qquad \cov(v|u)=\frac{\alpha\beta}{(\alpha+\beta)^2(\alpha+\beta+1)}\ ,
$$
where $\alpha>0$ and $\beta>0$.  Now we want to make $\alpha$ and $\beta$ a function of $u$.  A way of doing this is to put $\alpha-1=-a\ln(u)$ and $\beta-1=-b\ln(1-u)$ to yield
$$
\ln\{f(v|u)\}=c-a\ln(u)\ln(v)-b\ln(1-u)\ln(1-v)=\ln\{f(u|v)\}\ .
$$
where $a>0$ and $b>0$.  Since $0<u<1$  then $\alpha>1$ and $\beta>1$.

Now $0<x<1$ and hence consider $\alpha=x/(1-x)$ implying $\alpha>0$.   Then $\alpha-1=(2x-1)/(1-x)$.  Note when $x=1/2$ then $\alpha-1=0$.

So suppose $\beta=1$
$$
f(y|x)= cy^{(2x-1)/(1-x)}\ .
$$
When $x=0.5$, $f(y|x)=1$.  As

Point is to relate $\alpha$ and/or $\beta$ to $x$, the conditioning variable.  When $x$ increases we want the mean to increase and vice versa.  So maybe make $\alpha=x/(1-x)$, $\beta=1$ in which case $\alpha-1=1/(x-1)$ and
$$
f(y|x)=cy^{1/(x-1)}
$$

  However further useful information is provided by $P(U_3>u|U_2>u)$. Natural questions that arise are:
\begin{itemize}
    \item Is the fact that we are conditioning both on $u$ important?
    \item What are the critical $u$ points to be considered?
    \item How do we measure consistency of choice across the different combinations?
    \item If we do have tables as above how do we combine them?
\end{itemize}

Combining tables.

Sampling scheme:
\begin{itemize}
    \item Select random $U_1$ from the uniform
    \item Find max table $u$ such that $U_1>u$ in the table
    \item With the table probability select $U_2$
\end{itemize}

Thus if it makes it $x_u$ times more likely then since $P(U_2>u)=1-u$ then
$$
P(U_2> u|U_1> u) = x_u(1-u)\ , \qquad P(U_2\le u|U_1> u) = 1-x_u(1-u)\ .
$$
Thus
$$
\frac{P(U_2> u|U_1> u)}{P(U_2\le u|U_1> u)}=\frac{x_u(1-u)}{1-x_u(1-u)}\ .
$$

\subsection*{Mortality smoothing with copulas}

Suppose $Y$ is a matrix of mortality measurements with rows indicating age $i$ and columns time $t$.   Define column vectors $y_t$ and $y_i$ as column $t$ and row $i$ of  $Y$, respectively.  There are two ways of smoothing the matrix $Y$:
\subsubsection{Age copula}  The copula $C$ models correlation across age and $y_t=F_*^-u_t$ where $u_t\sim C$. Age specific behavior across time defines the components of $F_*$ and are estimated from the ergodic average $\hat F_*(s) =\Ex[y_t<s]$.
Special cases are:
    \begin{enumerate}
        \item Time profiles the same for each age: $F_*=1\odot h$ where $h$ is a scalar function and estimated as $\hat h(s)\equiv\Ex\{\hat F_*(s)\}=\Ex\{\Ex[y_t<s]\}$ where the outer expectation is the ensemble, across age, average.
        \item \label{pd} Perfect dependence across age.  This implies all the component time series in $y_t$ are driven by a single source of noise: $u_t=1v_t$ with $v_t\sim U$.
        \item \label{ind} Independence across age implies $u_t\sim \Pi$.  This model invokes the unlikely assumption that each age moves independently over time.
        \item   The meta--Gaussian model correlation matrix $R$ models the contemporaneous correlation between ages with $\hat R=\Ex(z_tz_t')$ where the $z_t$ are the normits $z_t\equiv(\Phi_*^-\circ F_*)y_t\sim\Phi^R$.  Generally the correlation between close ages is  higher.   An extreme case is where the correlation between ages $i$ and $j$ is $\rho^{|i-j|}$ for $0\le\rho\le 1$.  The case $\rho=1$ is equivalent to \ref{pd} while $\rho=0$ to \ref{ind} above.
    \end{enumerate}

    \subsubsection{Serial copula} The copula $C$ models serial correlation and $y_i=F_*^-u_i$ where draws $u_i\sim C$ correspond to different ages. Time specific mortality curves are the components in $F_*$ and are estimated from the ensemble (age profile) average $\hat F_*(j)\equiv\Ex[y_i<j]$.
Special cases are:
\begin{enumerate}
    \item Age profiles are the same across time.  This  implies each marginal in  $F_*$ is the same: $F_*=1\odot h$ where $h$ is univariate and $(1\odot h) y_i$ applies $h$ componentwise.  Thus $y_i=(1\odot h)^-u_i=(1\odot h^-)u_i$.  Function $h$ is estimated from the ergodic average of the empirical ensemble (age profile) distributions
$
\hat h(j)\equiv \Ex\{\hat F_*(j)\}=\Ex\{\Ex[y_i<j]\}
$ where the outer $\Ex$ works across the components of the vector.
    \item Perfect serial dependence implies $u_i=1v_i$ where $v_i\sim U$. Combined with a single age profile yields $y_i=(1\odot h^-)1v_i=1h^-v_i$.
    \item Matrix $R$ in the meta--Gaussian model is a serial covariance matrix, estimated from the normits $z_i\equiv(\Phi_*^-\circ F_*)y_i\sim \Phi^R$ as
$
\hat R = \Ex(z_iz_i')
$.
With a fixed mortality curve $z_i=\{\Phi_*^-\circ(1\odot h)\}y_i$ implying each component of $y_i$ is transformed with a fixed $h$.

\item    With the meta--Gaussian model the stationary AR(1) case  is where entry $(t,s)$ of $R$ is $\rho^{|t-s|}$ with $0\le\rho\le 1$.
Estimate $\hat\rho$ is derived from $\hat R$ by averaging the first off diagonal.
\end{enumerate}
Which copula modelling is likely to be more appropriate?  Copulas are preferred for variables which have distinct marginal behavious.

\subsubsection{Modelling age at death}

Let $F_t(i)$ be the age--at--death distributions at time $t$ and from this define $F_*$.  Thus $F_*$ is a vector of marginals corresponding to different points of time.  Corresponding to $y_i=F_*^-u_i$ with $u_i\sim C$ write, for each age $i$,  $u_i$ as the vector with components $F_t(i)$.  A copula $C$ serves to model dependence across age.

The above approach serves to define $u_i$ from the physically constructed age at death distribution, not actual deaths.   Of course the physical age--at--death distribution

\subsubsection{Connection to usual studies}

The distribution of age--at-death in a given year is
$$
F(y)=P(Y<y)= \sum_x P(Y<y|X=x)P(X=x) = \int_x F(y|x)f(x)
$$
Differentiating with respect to $y$ implies the density is
$$
f(y) = \int_x f(y|x)f(x)
$$
$$
 F(y|x)F_X(x)] - \int_xf(y|x)F_X(x)
$$
\subsubsection{Mortality smoothing across time}

Time dependence is introduced by assuming
$$
N_* y_t=Z\alpha_t+G\eps_t\ , \qquad \alpha_{t+1}=  T\alpha_t + H\eps_t\ .
$$
where $N_*\equiv \Phi_*^-\circ F_*$.  Hence the steps in this process are that we first construct the  normits $N_* y_t$ from each of the ages over time. We then fit a standard state space model to these normits.   But there must be a cycle here since the normits are estimated over time. Given a forecast $\hat z_t$ of the normits the forecast of $y_t$ is $\hat y_t=N_*^-\hat z_t$ where $N_*^-\equiv (\Phi_*^-\circ F_*)^-=F_*^-\circ\Phi_*$

An alternative is to define $N_+=\Phi_*^-\circ F_+$ where $F_+$ computes the quantiles of all the available data considered as one group.  Thus the measurement equation becomes $N_+y_t=Z\alpha_t+G\eps_t$.

A very simple model is
$$
N_* y_t=1\alpha_t+G\eps_t\ , \qquad \alpha_{t+1}=  \rho\alpha_t +\eta_t\ .
$$

\subsection*{BvN}

Theorem 1: The Birkhoff - von Neumann Theorem [Marcus (1960), pg. 215]
A doubly stochastic matrix A can be expressed as  , where   are nonnegative real numbers summing to 1 and   are permutation matrices.

Therefore any copula can be discretized and represented in matrix form based on the partition into   regions of equal size. Then, this matrix can be decomposed into linear combination of permutation matrices which can enhance the understanding of dependence structure and help to form a basis for multivariate data analysis. In the following sections we will set up BvN decomposition and copula connection, study the dependence bones and skeletons, discuss implications of the decomposition and generating copulas, and propose an approach to decompose copulas.

\subsection*{Power copulas}

Suppose $C$ is a copula.  For positive integer $p$ consider $C^p$.  This is a distribution on the unit hypercube.   The marginals are not uniform.   However we can construct the copula
$$
C^{(p)}\equiv C^p\circ C^{p-}_*
$$
What is the dependence structure here?  The procedure is thus:
\begin{itemize}
    \item Choose a given copula $C$.  For example $C=\Phi^R\circ\Phi_*^-$
    \item Power it.  For example $C^2=(\Phi^R\circ\Phi_*^-)^2$.  Note powering it means take the appropriate pointwise power not taking the function twice.
    \item Turn the powered version into a copula.
    \item Use the copula to model dependence.
\end{itemize}

\subsection*{Tail correlation}

We want an effective method to construct the correlation in the tail of  a distribution.   For example when dealing with the Gaussian distribution there is a single correlation that describes the strength of the relationship no matter where you are in the distribution.  How can we model the situation where there is more correlation in the tails?  Here is a try.  Think of the bivariate situation.  Divide the unit square into smaller squares.  In each square we correlate the normits of the quantiles.  Thus in each little square we have a bivariate normal and we compute the correlation.   To get the overall correlation we correlate the correlations.

Is this effective?  One way to think about things is to think about
$$
\tau(x,y)\equiv P(X>x|Y>y) = \frac{P(X>x,Y>y)}{P(S>y)}= \frac{S(x,y)}{S(y)}
$$
What is a smooth way of perturbing the normal to get more emphasis in the tail.  One way of doing this is to think of the distribution on each margin and then multiply by another distribution
$$
G\circ F
$$
Call $G$ the ``tail emphasizer."  In the extreme for example we can have $G$ as a step function with knot $\kappa$. Then result is a distribution which places a discrete mass at the knot and then as usual.  What if we take a ramp function...

Note that a copula is a function of many variables and returns a probability.  So you can't apply a copula repeatedly.  What happens if you take a copula $G$ and and generate a second copula from it.   That is you construct $C_C\equiv C\circ C_*$.  But the marginals $C_*$ of $C$ are uniform.   Hence $C_C=C\circ I=C$

What about taking a Gaussian copula and applying it repeatedly?   For example $G\equiv \Phi^R\circ\Phi_*^-$ is the Gaussian copula with correlation matrix $R$.  Using    What about $G^p$.  Note that $G$ is a copula.  Hence it takes probabilities to probabilities.   Thus $G^p$ is a copula for any integer $p$.   Note $G^0=I$, the uniform copula.

\subsection*{Survival copulas}

Copulas are typically thought of as the joint distribution on the square.  Alternatively let $S$ denote a survival function:
$$
S(y)=P(Y>y)
$$
We can then think of a survival copula on the square.  Thus a survival copula is a survival function on the unit cube with uniform marginals. Note for positive random variables $S(0)=1$ and $S(y)\rightarrow 1$ as $y\rightarrow\infty$.

Suppose $y\sim S$, indicating $y$ is a random vector with survival function $S$. Consider the ``survival" transform
$$
P\{S(Y)>y\} = P\{Y<S^-(y)\}=1-S\{S^-(y)\}=1-y
$$
Thus let $D$ be a survival copula on the unit hypercube with uniform marginals and $S_*$ a vector of survival marginals and define
$$
S_D\equiv D\circ S_*\ , \qquad D_S\equiv S\circ S_*^-
$$

\subsection*{Total liability distribution}

Consider
$$
\phi(s)\equiv P(\iota'F_*^-u\le s)\ , \qquad s_\alpha=\phi^-(\alpha)\ ,
$$
where $u\sim C$ and where $0\le\alpha\le 1$ is given.
What is a good way of estimating $F(s)$?   Further what is a good way of determining $s_\alpha$ given $\alpha$?  For example we may wish to estimate $s_{\alpha}$, corresponding to $\alpha=0.75$, the 75th percentile.

One approach is to repeatedly sample $u\sim C$ and hence $\iota'F_*^-u$.  These realizations are transformed to quantiles and in turn the quantiles are used to define  $s_\alpha$.

If we are interested in say the $\alpha$ quantile then hopefully we need only consider $u$ in the triangular pyramid of points lying above

Also important is the copula to be used.  What is a good copula?

Can we simplify.   For this purpose look at the 2D case and consider the point $(u,v)$ and suppose the quantile associated with this point insofar as the sum is concerned is $\alpha$.  Suppose we move $x$ to $x-\delta$ where $\delta>0$.   At the same time we move $y$ to $y+\delta$ and hence the sum stays the same.   The change in quantile in the $x$ distribution is  from $u=F_X(x)$ to $F_X(x-\delta)\approx F_X(x)-\delta f_X(x)=u-\delta f_X(x)$.  That is the change in the quantile is approximately $-\delta f_X(x)$.   Similarly the change in the $y$ quantile is approximately $\delta f_Y(y)$.  Thus the relative change in the $y$ quantile to that in the $x$ quantile is
$$
-\frac{f_Y(y)}{f_X(x)}\ .
$$

Fix $s>0$ and consider $\Omega_s=\{(x,y): x+y\le s\}$.  Clearly $(s,0)\in \Omega_s$.  Want $F_* (\Omega_s)$, the quantile set corresponding to $\Omega_s$.  Note
$$
F_*(\Omega_s)=\{u: \iota'F_*^- u\le s\}\ .
$$
What does this set look like?  Here we look at the 2D situation.   First consider (in 2D) $(u_s,v_s)=F_*^-(s,s)$.  These are the intercepts points, ie the quantiles in the marginal distributions that yield $s$.  Hence  $(u_s,0)$ and $(0,v_s)$ are in $F_*(\Omega_s)$.  Moving from $(0,s)$ to $(\delta,s-\delta)$ keeps us in $\Omega_s$.   The corresponding movements in $(u,v)$ space is from $(0,v_s)$ to $(\delta f_X(0), v_s-\delta f_Y(s))$.  Thus the slope is $-f_Y(s)/f_X(0)$.

The above argument can be generalized to any point when moving from $(u,v)$, presumed to be such that the corresponding $x+y=s$.  The change in $v$ relative to a change in $u$ is $-f_Y(x-s)/f_X(x)$.  Hence the boundary is defined by the differential equation
$$
\partial v=\frac{-f_Y\{F_X^-(u)-s\}}{f_X\{F_X^-(u)\}}\partial u\ ,
$$
with starting condition $(0,F_Y^-(s))$.

Once we have the boundary then we sample repeatedly from the copula and check if the sampled point lies on the right side of the boundary.   If so we count 1 and otherwise 0 and averaging we determine the quantile of $s$.  Alternatively we determine say the $\alpha$ quantile in $F_Y$ called $y_\alpha$ say.  We then use the above differential equation to define the boundary using $y_\alpha$ in place of $s$.  We repeatedly sample from the copula and check if we are on the right side of the boundary and count 1 or 0.   Averaging the 1's leads to the quantile of $y_\alpha$.  Generally expect that the quantile of $y_\alpha$ will be much bigger than $\alpha$.  Interesting to see how much bigger it is.

Here is an interesting graph.   Compute $y_\alpha\equiv F_*^-1\alpha$.  Then compute the sum quantile from each component of $y_\alpha$ that is $F$  Presumably the sum quantiles in each case are much less than $\alpha$.

Alternatively, we simply sample from the copula and just construct
$$
s=\iota'F_*^-u\ ,\qquad  u\sim C\ .
$$
and compute the quantiles associated with the generated sample.

Suppose $F_X(s)=\alpha$.  Thus the point $(s,0)$ in the set of $x+y\ge s$.  Decreasing $x$ by a small amount and increasing $y$ by the corresponding amount so as to keep the sum fixed implies the ratio of the percentiles changes by
$$
-\frac{f_Y(0)}{f_X(s)}\ .
$$
It is not unreasonable to suppose $f_Y(0)=0$.  Hence the change in the percentile...
Hence provided $f_Y(0)<f_X(s)$ the change in the percentile
Suppose $F_X(x_\alpha)=\alpha$.  Thus $x_\alpha$ is the $\alpha$ quantile in the $X$ distribution.   Thus $(x_\alpha,0)$ is in the set of $x+y\ge s_\alpha$.

we wish to determine $s_\alpha$ say such that
In two dimensions this defines a line, in three dimensions a surface, and so on.  The hypersurface defines a region with a probability
$$
P\{\iota'F_*^-u\le s\}=
$$

Consider the two dimensional copula $C(u,v)$.   Consider the ``line" $v_s(u)$ such that $\iota'F_*^-\{u,v_s(u)\}=s$.  Thus for each $0\le u\le 1$, $v_s(u)$ is that point...   Note that $v_s(0)$ is the quantile  of $s$ in the $Y$ distribution, while $v_s(1)$ is the quantile of $s-\max(X)$ in the $X$ distribution.

Alternatively consider any point $u$.   Then this maps to point say $y=F_*^-u$ and sum $\iota'y=\iota' F_*^-u$.  Further
the copula $C(u)=P(U<u)$.  Thus $P(\iota'F_*^-U<s)=$

\subsection*{Tail copulas}

In liability forecasting only the  upper tails of distributions are of interest.   This motivates the use of tail copulas.   A tail copula is a copula that joins marginal distributions in the tails.   In particular define $F_\alpha$ such that
$$
F_\alpha(y)=\left\{\begin{array}{lr}(1-\alpha)^{-1}(F_*-\alpha)(y)\ , & F_*(y)\ge \alpha\ ,\\ 0\ , &F_*(y)<\alpha\ .\end{array}\right.
$$
Thus $F_\alpha$ is the vector of tail marginal distributions. We now copulate the tail marginals as $C\circ F_\alpha$ which is a distribution of

Consider a bivariate copula $C(u,v)$.  This yields tail probabilities
$$
C^\alpha(u,v) = C(u,v|u>\alpha,v>\alpha) = \frac{C(u,v)}{1-C(0.5,0.5) + ...}
$$ say.  This is a joint distribution on the upper right hand square.  We can turn this joint distribution into a copula viz.
$$
C^\alpha\circ C^\alpha_*\qquad F_{C^\alpha} \equiv C^\alpha\circ F_*
$$

\subsection*{Sampling from distributions generated with a copula}

To simulate from $C\circ F_*$, proceed as follows:
\begin{enumerate}
    \item Decompose $C$ into $C=C_1C_{2|1}C_{3|1,2}\cdots $
    \item Draw $u_1\sim C_1\equiv U$, $u_2\sim C_{2|1}$, $u_3\sim C_{3|1,2}$ and so on leading to $u\equiv(u_1,u_2,u_3,\ldots,)'$.
    \item Put $y=F_*^-u$.
\end{enumerate}
Then $y\sim C\circ F_*$.  The potential difficulty is finding/specifying the conditional distributions.  What are reasonable specifications.  How do we determine what a reasonable specification is.   Maybe, similar to time series, we should forget about specifying a global copula but concentrate on just specifying a sequence of conditional copulas starting from $C_1=U$.  Note that
$$
C(u_2|u_1)\equiv \frac{C(u_1,u_2)}{U(u_1)}=\frac{C(u_1|u_2)u_2}{u_1}\qquad\Rightarrow\qquad\frac{C(u_2|u_1)}{C(u_1|u_2)}=\frac{u_2}{u_1}\ .
$$
Hence $C(u_2|u_1)\ge C(u_1,u_2)$.

Suppose $u_t\sim C$ and $u_t=(v_t',w_t')'$

\subsection*{Tail dependence}

For two random variables $X$ and $Y$ consider
\\

\begin{tabular}{|c|l|c|c|}
  \hline
  % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
  measure & definition & $X$ and $Y$ & $X$ and $Y$ perfectly \\
          &            & independent & dependent\\
  \hline
  $
\phi(u)$&$ \E\{[F(Y)>u]|F(X)>u\}$ & $1-u$ & 1 \\
  $ \psi(u)$&$ \E\{F(Y)|F(X)>u\}
$& 1/2& $(1+u)/2$ \\
  $ \rho(u)$&$ \mathrm{cor}\{F(X),F(Y)|F(X)>u\}$ & 0& 1 \\
  \hline
\end{tabular}
\\\\\\\\

Where $[F(Y)>u]$ is 1 if $F(Y)>u$ and 0 otherwise.
Thus measures indicating the departure from independence are
$
\phi(u)/(1-u)$ and $2\psi(u)$ while measures indicating the departure from perfect dependence are
$
\phi(u)$ and $2\psi(u)/(1+u)$.

Since
$$
\phi(u)=\frac{P\{F(Y)>u,F(X)>u\}}{P\{F(X)>u\}} = \frac{P\{F(Y)>u,F(X)>u\}}{1-u}\ .
$$
Hence $\phi(u)$ is symmetric in $X$ and $Y$.  This is not a property enjoyed by the other two measures of tail dependence.

Note $2\psi(u)-\phi(u)=u$ for both perfectly dependent and independent situations.  Alternatively $2\psi(u)+\phi(u)=2-u$ if independent and $2+u$ if perfectly dependent.

A further variant is the moment generating type function
$$
\E\{\e^{sF(Y)}|F(X)>u\}\ , \qquad \
$$

For each $u$, the conditional probability is estimated as the empirical proportion of the quantiles of $Y$ that exceed $u$ given the empirical quantile of $X$ exceeds $u$.  As $u$ approaches 1, $\phi(u)$ may approach some number bigger than 0.

Let's define the normits as
$$
x
$$

By Bayes' theorem
$$
\phi(u)= \frac{P\{F(X)>u|F(Y)>u\}}{P\{F(X)>u\}}P\{F(Y)>u\}\ .
$$
Hence
$$
\phi_{Y|X}(u)=\phi_{X|Y}(u)
$$

Note that $\phi(u)\equiv 1$ if $Y$ and $X$ are perfectly dependent while $\phi(u)=1-u$ under independence.   Hence $\phi(u)$ measures the percentage reduction in dependence while  $\phi(u)/(1-u)$ measures how far things are away from independence.

Note that
$$
P\{F(X)>u,F(Y)>u\}=P\{F(X)>u\}P\{F(Y)>u|F(X)>u\}=(1-u)\phi(u) \ .
$$
This implies

Similarly we can define
$$
\qquad \rho(u)\equiv \mathrm{cor}\{F(X),F(Y)|F(X)>u\}\ .
$$
If $X$ and $Y$ are independent $\psi(u)=0.5$ and $\rho(u)=0$.  Positive tail dependence is $\psi'(u)>0$.

Note that
$$
0.5=\psi(u)(1-u)+\E\{F(Y)|F(X)<u\}u\qquad\Rightarrow\qquad E\{F(Y)|F(X)<u\}=\frac{0.5-\psi(u)(1-u)}{u}
$$

When there is perfect dependence between $Y$ and $X$ then $\psi(u)=(1+u)/2$.  Hence a reasonable measure of tail
dependence is
$$
\frac{2\psi(u)}{1+u}
$$
If there is perfect tail dependence then this should be close to 1.   If there is no tail dependence then $\psi(u)=1/2$ and this measure is $1/(1+u)$ which approaches 1/2 as

When there is dependence between
$Y$ and $X$ then $\E\{F(Y)|F(X)>u\}$ will increase with $u$.

 Theoretically the expression is
$$= \frac{P\{F(X)>u,F(Y)>u\}}{P\{F(Y)>u\}}$$$$=\lim_{u\uparrow 1} \frac{1-P\{F(X)<u\}-P\{F(Y)<u\}+P\{F(X)<u,F(Y)<u\}}{1-P\{F(Y)<u\}}=\lim_{u\uparrow 1} \frac{1-2u+C(u,u)}{1-u}\ .
$$
An empirical estimate is to take the proportion of cases where all quantiles exceed $u$ of the proportion of cases
For an empirical estimate we do the following:
\begin{enumerate}
    \item For each quantile $u$ determine the proportion of cases where both variables have a bigger quantile
    \item Divide by the proportion proportion of $x$ variables have bigger quantile
\end{enumerate}

\subsection*{Simulating using a Gaussian copula}

Suppose the correlation matrix $R$ is given and $z\sim \Phi^R$ then $\Phi_*(z)\sim\Phi^R\circ\Phi_*^- $.  To prove this consider
$$
P\{\Phi_*(z)<u\}=P\{z<\Phi_*^-(u)\}=\Phi^R\{\Phi_*^-(u)\}=(\Phi^R\circ\Phi_*^-)(u)\ ,
$$
as required.

More generally suppose $\Psi$

Suppose we take $z\sim\Phi^R$ and consider $z^2$.  Each component has a chi--squared distribution and hence $u=\chi_*^-(z^2)$ has uniform marginals.

\subsection*{Copulas for runoff triangles}

Suppose $x$

\subsubsection{Measurement noise}
In many cases it is appropriate to add ``measurement" noise.  For example
$$
y_t = F_*^-u_t+F_*^-\eps_t\ , \qquad u_t\sim C\ ,\qquad \eps_t\sim \Pi\ .
$$
In the case of the Gaussian copula a signal plus noise model is
$$
y_t = (F_*^-\circ \Phi_*)(\sqrt {R-\sigma^2I}\zeta_t +\sigma\xi_t)\ ,\qquad (\zeta_t',\xi_t')'\sim \Phi^I\ .
$$
Thus the covariance matrix of the overall disturbance is $R$.  In this formulation $\sigma^2$ cannot exceed the smallest eigenvalue of $R$. A further refinement is where the copula from which $u_t$ is drawn is a conditional copula.

%\bibliography{../texstuff/piet}

\end{document}

### 2015-05-29 related/memo.tex
pdj initial

%\include{preamble}
%define title
\documentclass[12pt,a4paper]{article}
\newcommand{\e}{\mathrm{e}}
\title{Stress testing, monte carlo simulation and scenario analysis}
\begin{document}

\maketitle

Stress testing is used in the context of the measurement of bank capital adequacy and reserving for market risk, in conjunction with Value at Risk. Value at Risk is essentially an estimate of the quantile of the distribution of the change in value of a portfolio of financial instruments. In order to do a VaR calculation, you need to specify a joint distribution for the instrements in the portfolio.

Stress testing involves estimating how a portfolio would perform under some ``extreme market movements". It is a form of scenario analysis. It is a way of taking into account extreme events that do occur from time to time but which are virtually impossible according to the probability distributions assumed for the variables that impact on the portfolio value. For example a 5 standard deviation daily move in a market index (e.g. the s\&p 500 stock market index) is one such extreme event. Under the assumption of a normal distribution this would happen about once every 7000 years, but in practice such movements are observed once or twice every 10 years.

An example of stress testing for banks is stress testing of interest rates for the value of their portfolio of bonds and debt securities. The bank may use scenarios that specify a change in the yield curve which is a combination of the effects of a parallel shift, and a change in the slope of the yield curve (e.g. so that long term yields rise by more than short term ones), and a "curvature in the yield curve" to allow for various different yield curve shapes. Another example is in stress testing a portfolio of foreign exchange instruments (such as forwards, futures, swaps, options and spot positions). It is possible to devise scenarios for changes in both the exchange rates and the volatility of exchange rates.

Stress testing can involve simple 1 factor scenarios (sensitivity analysis), complex multifactor scenarios, or a full blown monte carlo simulation.

We adapt the ideas in stress testing for banking and use them in the context of insurance reserving and the aggregation of distributions of the outstanding claims reserves of different classes of insurance

The task is to combine the distributions of the outstanding claims liability  for several classes of insurance into a single overall distribution of the outstanding claims liability.

In practice there is limited data or information on which to base a probability distribution for the outstanding claims liability for even a single class of insurance.

Natural candidates are the normal distribution, the lognormal distribution, the t distribution and the ``log t-distribution".

When it comes to combining the distributions into an overall aggregate distribution there is limited data available and it is difficult to know what joint distribution applies.
Using the ideas from stress testing / scenario analysis and monte carlo simulation, we can model statistically the joint distribution by making up a scenario.

We can propose a scenario for the distributions of the outstanding claims liabilities, and propose a scenario for different copulas to combine these distributions into an overall joint distribution. Using mc simulation we can turn these scenarios into a distribution of the overall liability (to get the distribution of the sum of the different random variables).

The outstanding claims liability is a function of
1.	the claims experience, i.e. the claim frequency and claim size distribution
2.	the claims development experience: the time lags involved in the typical pattern of claim payments
3.	the rate of interest used in discounting the projected claim payments to a present value
4.	the rate of inflation used in projecting the future claim payments
5.	rates of superimposed inflation

The economic variables used in the estimation of the outstanding claims liability would be common to all the different classes of business. In particular the interest rates and the inflation rate would be common. The rate of superimposed inflation would probably vary from one class of business to another. Other aspects of the problem may be more specific to the class of insurance: the claim frequency, claim size and claim payment patterns involved.

What we want for reserving purposes is an estimate of the quantiles / percentiles of the aggregate outstanding claims liability

Hello there

\end{document}

### 2015-05-29 related/oldcopulas.tex
pdj initial

\input{preamble}

\section*{Copulas}
A copula is a probability distribution $C$ on the unit hypercube with uniform marginals.  Given a vector $F_*$ of marginal distributions\footnote{Formally $F_*(y)$ has components $F_i(y_i)\equiv F(y_i^\infty)$ where $y_i^\infty\equiv(\infty,\ldots,y_i,\ldots\infty)$} and copula $C$ define $F_C$ as follows\footnote{The composition $G\circ H$ of two functions $G$ and $H$ is defined as $(G\circ H)(x)\equiv G\{H(x)\}$ for all $x$.} \begin{equation}\label{Fx}
    F_C\equiv C\circ F_*\ .
\end{equation}
This is  a joint distribution\footnote{Since $(C\circ F_*)_*(y)$ has components $(C\circ F_*)(y_i^\infty)=C\{F_*(y_i^\infty)\}=C_i\{F_i(y_i)\}=F_i(y_i)$} with the given marginals $F_*$  Conversely given a joint distribution $F$ with marginals $F_*$ and $F_*^-$ as the componentwise inverse to $F_*$ define
\begin{equation}\label{Cu}
    C_F\equiv F\circ F_*^-\ .
\end{equation}
This is a copula, the copula of $F$.   Further
$$
F_{C_F}= C_F\circ F_*= F\circ F_*^-\circ F_*=F\ , \qquad C_{F_C}=F_C\circ (F_C)_*^-=C\circ F_*\circ  F_*^-=C\ .
$$
Hence (Sklar's theorem) $F_C=F$ iff $C_F=C$.

\subsubsection{Copula properties} 
\begin{itemize}
    \item  Each component of $F_*$ is arrived at by setting all arguments, other than the current, to $\infty$.  Further
     $F_*^-$ depend only on the corresponding component of the argument.
     \item If $y\sim C\circ F_*$ then $y=F_*^-u$ where $u\sim C$.
    \item  If $H_*$ is the componentwise  vector of univariate monotonic functions then
$$
C_{F\circ H_*^-}\equiv F\circ H_*^- \circ(F\circ H_*^-)_*^-=F \circ F_*^-\equiv C_F\ .
$$
Hence copulas are invariant to monotonic deformations along each axis. 
    \item The density associated with $C_F=F\circ F_*^-$ is
    $$
    \frac{f\circ F_*^-}{\Pi (f_*\circ F_*^-)}\ ,
    $$
    where $f$ is the density associated with $F$ and $f_*$ is the vector of marginal distributions.  If $f=\Pi f_*$ (ie independence) then $f\circ F_*^-=\Pi (f_*\circ F_*^-)$ and the density is identically 1.
    \item The Gaussian copula with correlation matrix $R$ is the copula $C_{\Phi^R}$  where $\Phi^R$ is the Gaussian distribution with mean 0 and covariance matrix $R$.   Since $R$ is a correlation matrix, $\Phi^R_*=\Phi_*$, a vector of standard normal distributions, and $C_{\Phi^R}=\Phi^R\circ \Phi_*^-$.   The meta--Gaussian model is
\begin{equation}\label{metaG}
y = F_*^-u\ , \qquad u\sim\Phi^R\circ\Phi_*^-\qquad\Leftrightarrow\qquad y =(F_*^-\circ\Phi_*^-)\sqrt{R}\eps\ , \qquad \eps\sim \Phi^I\ .
\end{equation}
Typically $R$ is estimated using the average cross product matrix of  the normits  $(\Phi_*^-\circ F_*) y$.

\item The independence and perfectly dependent copulas is defined as $\Pi\equiv\Pi\ 1_*$ and $\vee\equiv\min$ respectively, where $1_*$ indicates the vector of identity functions.  These arise as follows:
$$
C_{\Pi F_*}\equiv(\Pi F_*)\circ F_*^-= \Pi\ 1_*\ ,\qquad C_{\vee}=\ .
$$
The perfectly dependent copula implies a single source of noise: 
$y=F_*^-1u$ with $u\sim U$
where $1$ is a vector of  identity functions of one variable.
\end{itemize}

\section{Mortality smoothing}

There are two ways of applying copulas to mortality smoothing:
\begin{enumerate}
    \item The copula $C$ models correlation across age and $u\sim C$ is a ``time" draw. Age specific  behavior across time defines the components of $F_*$.  The age profiles are generated according to $y=F_*^-u$ with $u\sim C$ and different draws correspond to different times. Marginals in $F_*$ corresponding to each age  are estimated from the ergodic average
$
\hat F_*(s) =\Ex[y<s]
$, where $\Ex$ denotes the ergodic average.
Special cases are:
    \begin{enumerate}
        \item Time profiles do not vary with age implying each marginal in $F_*$ is the same.  Hence $F_*=1\odot h$ and $h$ would be estimated as $\hat h(s)\equiv\Ex\{\hat F_*(s)\}=\Ex\{\Ex[y<s]\}$ where the outer expectation is the ensemble average.
        \item \label{pd} Perfect dependence across age implies all the time series are driven by a single source of noise: $y= F_*^-1u$ where $u\sim U$.
        \item \label{ind} Independence across age implies $ y= F_*^-u$  where $u\sim \Pi$.  This model invokes the unlikely assumption that each age moves independently over time.
        \item   Intermediate cases are  $ y=F_*^-u$ with $u\sim C$.   With the meta--Gaussian model, the correlation matrix $R$ models the correlation between ages and generally the correlation between close ages is  higher.   An extreme case is where the correlation between ages $i$ and $j$ is $\rho^{|i-j|}$ for $0\le\rho\le 1$.  The case $\rho=1$ is equivalent to \ref{pd} while $\rho=0$ to \ref{ind} above.
    \end{enumerate}        
    \item The copula $C$ models serial correlation and $u\sim C$ is an ``age" draw.  Time specific mortality curves are the components in $F_*$.   The time series profiles $y$ of mortality are generated  according to $y=F_*^-u$ where $u\sim C$ and different draws correspond to different ages.  Marginals in $F_*$ corresponding to each $t$ are estimated from the ensemble (age profile) data at time $t$, $\hat F_*(k)\equiv\Ex[y<k]$ where the expectation is empirical average is across the (age) different draws.
Special cases are:
\begin{enumerate}
    \item Age profiles do not vary with time implying each marginal in  $F_*$ is the same.  Hence $F_*=1\odot h$ where $h$ is univariate and $(1\odot h) y$ applies $h$ componentwise.  Thus $y=(1\odot h)^-u=(1\odot h^-)u$.  Map $h$ is estimated from the ergodic average of the empirical ensemble (age profile) distributions
$
\hat h(k)\equiv \Ex\{\hat F_*(k)\}=\Ex\{\Ex[y<k]\}
$ where the outer $\Ex$ works across the components of the vector.
    \item Perfect serial dependence implies $y= F_*^-1u$ where $u\sim U$. Combined with a single age profile yields $y=(1\odot h^-)1u=1h^-u$ with $u\sim U$.  To estimate $h$ is $\hat h(k)=\Ex\{\Ex[y<k]\}$.   
    \item Matrix $R$ in the meta--Gaussian model is a time series covariance matrix.  The correlation matrix is estimated from the $z\equiv(\Phi_*^-\circ F_*)y$ as
$
\hat R = \Ex(zz')
$.
Note $z\sim \Phi^R$ and $(\Phi^R)_*=\Phi_*$.  In the fixed mortality curve situation $z=\{\Phi_*^-\circ(1\odot h)\}y$.  Thus each component of $y$ is transformed by $h$.  And $h$ would be estimated as $\hat h(k)\equiv\Ex\{\Ex[y<k]\}$.

\item    With the meta--Gaussian model the stationary AR(1) case  is where entry $(t,s)$ of $R$ is $\rho^{|t-s|}$ where $0\le\rho\le 1$.  This meta--Gaussian model combined with a fixed mortality curve implies 
$$
y=\{(1\odot h^-)\circ \Phi_*^-\}\sqrt{R}\eps\ , \qquad \eps\sim \Phi^I\ .
$$
Given observed time profiles $y$ for each age, the matrix $R$ is estimated by first transforming to normits 
$
z=\{\Phi_*\circ(1\odot h)\}y
$ and $\hat R = \Ex(zz')$.  The estimate of $\rho$ is $\Ex(r_{t,t-1})$ where the average is over $t$. 
\end{enumerate}     
\end{enumerate}

\section{Usefulness of copulas in applied work}

 The above indicates there are two ways of thinking about copulas:
\begin{enumerate}
    \item As a way of generating a joint from given marginals.
    \item As a way of writing the joint in terms of its marginals.
\end{enumerate}    
In applied work the first seems to be the most important.   In other words given marginals can be ``moulded" into many different joint distributions through choice of an appropriate copula.

 is first adjusted by the use of explanatory variables to indicate it is coming from different populations.

\subsubsection{Normit modelling}

Suppose the joint distribution of $\psi(x)$ and $\psi(y)$ is bivariate normal with correlation $\rho$.   Then since $\psi(x)$ and $\psi(y)$ are standard normal  
$\rho=\E\{\psi(y)\psi(x)\}$.

For example using claim size and settlement delay as an example then the correlation between the normits is 0.68.   Hence
$$
\psi(\hat y)=0.68\psi(x)\qquad\Rightarrow\qquad  F(\hat y) =\Phi\{0.68\psi(x)\}\ .
$$
That is, given $x$  the prediction $\hat y$ has predicted quantile $\Phi\{0.68\psi(x)\}$.  The actual prediction $\hat y$ is determined by going into the distribution of $y$ and picking out the value corresponding to the predicted quantile.

\subsubsection{Simulating from Gaussian copula}

To simulate we just generate standard normals with a given correlation matrix.   That is suppose the correlation is $\rho$ then given two standard normals $z_1$ and $z_2$ we form
$$\left(%
\begin{array}{c}
  \psi(x) \\
  \psi(y) \\
\end{array}%
\right)=
\left(%
\begin{array}{cc}
  1 & \rho \\
  \rho & 1 \\
\end{array}%
\right)^{1/2} \left(%
\begin{array}{c}
  z_1 \\
  z_2 \\
\end{array}%
\right)
$$ 
We now form $\Phi\{\psi(x)\}$ and $\Phi\{\psi(y)\}$

\subsubsection{Runoff triangles}

Think of each row as a distribution $F_i(j)$ where $i$ is the accident year and $j$ the development year.  We can convert this to normits by taking $\psi_i(j)\equiv\Phi^{-1}\{F_i(j)\}$.  We now study the correlations across the rows.  Trouble is we don't know the quantiles.

Note $\psi_1(n)=$

Now take the slope
$$
\psi_i(j) = a_i+b_ij
$$

\subsubsection{Joint distribution under Gaussian copulas}

We want to find the joint distribution of $(x,y)$.  The general result about this sort of thing is as follows.   If $(x^*,y^*)$ has density $f(x^*,y^*)$ and $(x^*,y^*)=\phi(x,y)$ is one--to--one, then the joint density of $(x,y)$ is
$$
f\{\phi(x,y)\}\left|\frac{\partial \phi(x,y)}{\partial (x,y)}\right|=f\{\psi(x),\psi(y)\}\dot\psi(x)\dot\psi(y)\ ,
$$
Now
$$
\dot\psi(x) = \frac{\partial x^*}{\partial x^\dag}\frac{\partial x^\dag}{\partial x}= \left(\frac{\partial x^\dag}{\partial x^*}\right)^{-1}\frac{\partial x^\dag}{\partial x}=\left\{\frac{\partial \Phi(x^*)}{\partial x^*}\right\}^{-1}\frac{\partial x^\dag}{\partial x}=\sqrt{2\pi}\exp\left\{\frac{\psi^2(x)}{2}\right\}f(x)
$$
Hence if $f\{\psi(x),\psi(y)\}$ is bivariate standard normal with correlation $\rho$ then
the joint density  of $(x,y)$ is
$$
f(x,y)=\frac{1}{1-\rho^2}\exp\left\{\frac{\psi^2(x)+\psi^2(y)}{2}-\frac{\psi^2(x)-2\rho\psi(x)\psi(y)+\psi^2(y)}{2(1-\rho^2)}\right\} f(x) f(y)
$$$$
=\Phi\{\psi(x),\psi(y)\}f(x)f(y)
$$
where $f(x)$ and $f(y)$ are the marginal densities of $x$ and $y$ and
$$
\Psi_\rho(u,v)= \frac{1}{1-\rho^2}\exp\left\{-\frac{\rho^2(u^2+v^2)-2\rho uv}{2(1-\rho^2)}\right\}\ .
$$

Note the marginals are $f(x)$ and $f(y)$ for any choice of $\rho$ and if $\rho=0$ then the joint density is $f(x)f(y)$, as expected. Further since $f(x,y)=f(x)f(y|x)$ it follows
$$
f(y|x)=\Psi_\rho\left\{\psi(x),\psi(y)\right\}f(y)\qquad\Rightarrow\qquad \frac{f(y|x)}{f(x|y)}=\frac{f(y)}{f(x)}\ .
$$

\subsubsection{Sampling from the density}

Differentiating  $\Psi_\rho(u,v)$ with respect to $v$ yields 
$$
\Psi_\rho(u,v)\frac{\rho(\rho v- u)}{(1-\rho^2)}\ .
$$ 
Thus the maximum occurs at $v=u/\rho$ in which case 
$$
\Psi_\rho(u,v)=\frac{1}{1-\rho^2}\exp\left\{\frac{-u^2(1+\rho^2)+2u^2}{2(1-\rho^2)}\right\}=\frac{1}{1-\rho^2}\exp\left(\frac{u^2}{2}\right)\ .
$$
Thus 
$$
f(y|x)\le \frac{1}{1-\rho^2}\exp\left\{\frac{\psi^2(x)}{2}\right\}f(y) \ .
$$
Hence the ratio of the left to right hand side is
$$
\frac{\Psi_\rho\left\{\psi(x),\psi(y)\right\}}{\frac{1}{1-\rho^2}\exp\left\{\frac{\psi^2(x)}{2}\right\}}=\exp\left\{-\frac{\psi^2(x)}{2}-\frac{\rho^2\psi^2(x)+\rho^2\psi^2(y)-2\rho \psi(x)\psi(y)}{2(1-\rho^2)}\right\}  
= \exp\left[-\frac{\{\psi(x)-\rho\psi(y)\}^2}{2(1-\rho^2)}\right]
$$
Thus a rejection algorithm for generating samples from the joint is
\begin{enumerate}
    \item  $x\sim f(x)$
    \item Repeat $y\sim f(y)$ and $u \sim U(0,1)$ until $$
    \ln(u) < \frac{-\{\psi(x)-\rho\psi(y)\}^2}{2(1-\rho^2)}\ .
    $$
\end{enumerate}
The resulting draw $(x,y)$ is a draw from $f(x,y)$ generated using the Gaussian copula.   Note that if $\rho\approx 1$ then $u$ must be very small to get an accepted $y$.  If $\rho=0$ then $y$ is accepted if $\ln(u)<-\psi^2(x)/2$.  Since this latter condition makes no reference to $y$, all draws $y$ can be accepted.

Since $\psi(x)$ and $\psi(y)$ are standard normal we can just generate lots of these and only accept those meeting the condition in 2.

\section{What copula is appropriate?}

Suppose we have data vectors $x_1,\ldots,x_n$.  Corresponding to the measurements calculate the quantiles $u_1,\ldots, u_n$ or, in the case of the Gaussian copula, the normits, $z_1,\ldots,z_n$. We study the behavior of the

$F_*(x)$ denotes the vector of fitted marginals.  Then convert the data to quantiles

\section{Archimedean copulas}

These are of the form
$$
C(u,v)=A^-\{A(u)+A(v)\}
$$

\section{Reserving}
Suppose the correlation between $\psi(y)$ and $\psi(x)$ is $\rho$ and suppose the two transformed variables are jointly normal.   We want to find $c_\alpha$ such that
$$
P(x+y<c_\alpha)=\alpha\ .
$$
One approach is
$$
\int_x\int_y \Psi_\rho\left\{\psi(x),\psi(y)\right\}f(x)f(y)\ .
$$

Lets see if we can find the joint distribution of $(x,y)$ given the joint distribution of $\{\psi(x),\psi(y)\}$.

\section{Calculations} 
In this case $\phi(x,y)=\{\psi(x),\psi(y)\}$ and  the determinental term is $\psi(x)\psi(y)$.
is the density of 
in this case $z=(x^*,y^*)'=\{\psi(x),\psi(y)\}'$ and $h(z)=(x,y)'=\{\psi^{-1}(x^*),\psi^{-1}(y^*)\}$.   Thus $h^{-1}(z)=$
$$
\left|\frac{\partial h^{-1}(z)}{\partial z}\right| = \left|\right|
$$
In general terms define $\Omega_c=\{(x,y):x+y<c\}$

 and
$$
\E\{\psi(y)|x\}=\rho\psi(x)\ , \qquad Var\{\}
$$
$$
\E(y|x)=\tilde F_y^{-1}[\Phi\{\rho\psi(x)\}]\ , \qquad Var\{\}
$$
But the left hand side is approx
$$
\E\{\phi(\mu_{y|x})+\dot\phi(\mu_{y|x})(y-\mu_{y|x})|x\} = \phi(\mu)+\dot\phi(\mu)\{\E(y|x)-\mu\}\ .
$$
This implies
$$
\E(y|x)\approx\mu+\frac{\rho\phi(x)-\phi(\mu)}{\dot\phi(\mu)}\ .
$$
Thus to calculate the conditional expectation of

To calculate this redefine $y$ to be two dimensional and with $y^*=\phi(y)$

for any $0<\alpha<1$ we can find $c_\alpha$ such that
$$
P\{\phi(y)+\phi(x)<c_\alpha\}=\alpha\ .
$$
The issue is to compute the region $\{(y,x): \phi(y)+\phi(x)<c_\alpha\}$.

One way of computing the region is:
\begin{itemize}
    \item Pick random $(y^*,x^*)$ and check if $y^*+x^*<c_\alpha$
    \item If in the region then compute $y=\phi^{-1}(y^*)$ and $x=\phi^{-1}(x^*)$ 
    \item 
\end{itemize}

We now try and model the relationship between $y^*$ and explanatory variables $x^*$. Consider the normal model 
$$
y^* \sim N({x^*}'\beta,\sigma^2)\ .
$$
We fit the model and obtain predictions $\hat y^*$ and in turn $\hat y^\dag=\Phi(\hat y^*)$.  This is a prediction of the percentile of $y$ from the percentiles of $x$.  Note that the fitted vector $\hat\beta$ will be a vector of partial correlations.

Suppose now $y$ is a vector of variables (not observations).  We want the distribution of $\iota'y$ representing the total liability.  We can measure/infer the distribution of normalized scores $y^*$.   In particular $y^*\sim N(0,\Sigma)$ where $\Sigma$ is a correlation matrix since it has all 1's on the diagonal.  Thus the distribution of $\iota'y^*$ is $N(0,\iota'\Sigma\iota)$.   The $\alpha$ percentile is given by $z_\alpha\sqrt{\iota'\Sigma\iota}$ where $z_\alpha$ cuts out the required probability in a standard normal:
$$
P(\iota'y^*<z_\alpha\sqrt{\iota'\Sigma\iota})=\alpha\ .
$$

How do we convert this to a probability statement on the actual total $\iota'y$?  That is we want the set  
$$
\Omega_\alpha = \left\{y : \iota'y^*<z_\alpha\sqrt{\iota'\Sigma\iota}\right\}\ .
$$
Note that the set of $y^*$ satisfying the region is not a quadrant and the normal is centred on zero with unit variances.
One way of doing this is to see where each $y^*$ comes from.

For example in the two dimensional case this is

 In moving from the original data $y_i$ to $y_i^\dag$ and $y_i^*$ we lose all information about location and scale.  Lets have a separate model for that.

Since  $y^\dag=\Phi(y^*)=\pi(y)$.  Hence the density of $\pi(y)$ is uniform with mean 0.5.
$$
\frac{\partial \Phi^{-1}(y^*)}{\partial y^*} \exp\left\{-\frac{(y^*-{x^*}'\beta)^2}{2\sigma^2}\right\}= 
$$

For given data we can then consider a normal model 
$$
y^* \sim N({x^*}'\beta,\sigma^2)\ .
$$
But $\Phi(y^*)=\pi(y)$.  Hence the density of $\pi(y)$ is uniform with mean 0.5.
$$
\frac{\partial \Phi^{-1}(y^*)}{\partial y^*} \exp\left\{-\frac{(y^*-{x^*}'\beta)^2}{2\sigma^2}\right\}= 
$$

Thus the log--density of $y^*$ is proportional to 
$$
\frac{y*}{}
$$

The copula approach is to design a distribution on the unit hypercube $C(u)$ with uniform marginals.  Consider first 
the bivariate case.  Then $C(u,v)$

An alternative is to use the $\phi(y_i)$.  That is we just give them a covariance matrix.

Since the former are probabilities it is convenient to turn them into logits.

  Similarly let $z(y)$ be the ``zscore" of $y$, meaning we calculate the uniform then find $z$ such that
$$
z(y)=\Phi^{-1}\{u(y)\}\ ,\qquad z(y_i)=\Phi^{-1}\left\{\frac{1}{n} \sum_{j=1}^n[y_j<y_i]\right\}\ .
$$
This is different from the usual z--score calculated as
$$
\frac{y-\bar y}{s_y}
$$

For example suppose the relationship between the percentiles of two variables can be adequately described by 
$$
u(y) \approx \beta_0 + \beta_1 u(x)\ ,
$$
or from a glim perspective
$$
\E\{U(y)\}=\beta_0+\beta_1 U(x) \ , \qquad Var\{U(y)\}=\gamma_0+\gamma_1 U(x)+\gamma_2 U^2(x)\ .
$$
\section{Example copulas}

\subsubsection{Independence copula.}   Here $C(u)=\prod_ju_j$.   This would imply there is no correlation between the percentiles.

\section{Estimating copulas}

Copulas can be estimated by first using the percentile transform each variable.   Then plot these percentiles against each 
other.   What is the joint distribution of the percentiles.   One approach is  
The way to estimate copulas is to 
In many cases we observe the variables and have some information on the joint distribution.

Different copulas induce different dependence structure.

\end{document}

### 2015-05-29 srisk3.tex
pdj initial

\documentclass[authoryear]{elsarticle}
\usepackage{latexsym}
%\usepackage{rotate}
\usepackage{graphics}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{comment}
\bibliographystyle{chicago}

\newcommand{\logit}{\mathrm{lgt}}
\newcommand{\I}{\mathrm{I}}
\newcommand{\E}{\mathrm{E}}
\newcommand{\p}{\mathrm{P}}
\newcommand{\e}{\mathrm{e}}
\renewcommand{\o}{\omega}
\newcommand{\vecm}{\mathrm{vec}}
\newcommand{\kp}{\otimes}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\cov}{\mathrm{cov}}
\newcommand{\eps}{\epsilon}
\newcommand{\ep}{\varepsilon}
\newcommand{\obdots}{\ddots}    % change this later
\newcommand{\Ex}{{\cal E}}
\newcommand{\Exd}{\Ex_d}
\newcommand{\Es}{\E_\phi}
\newcommand{\rat}{{\frac{c_{ij}}{c_{i,j-1}}}}
\newcommand{\rmu}{m}
\newcommand{\rsig}{\nu}
\newcommand{\fd}{\mu}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\cor}{\mathrm{cor}}
\newcommand{\bx}[1]{\ensuremath{\overline{#1}|}}
\newcommand{\an}[1]{\ensuremath{a_{\bx{#1}}}}

\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}

\renewcommand{\i}{\item}
\newcommand{\sr}{\ensuremath{\mathrm{SRISK}}}
\newcommand{\cs}{\ensuremath{\mathrm{CS}}}
\newcommand{\cri}{\ensuremath{\mathrm{Crisis}}}
\newcommand{\var}{\ensuremath{\mathrm{VaR}}}
\newcommand{\covar}{\ensuremath{\mathrm{CoVaR}}}
\newcommand{\med}{\ensuremath{\mathrm{m}}}
\newcommand{\de}{\mathrm{d}}
\renewcommand{\v}{\ensuremath{\mathrm{v}_q}}
\newcommand{\m}{\ensuremath{\mathrm{m}}}
\newcommand{\tvar}{\ensuremath{\mathrm{TVaR}}}
\renewcommand{\c}{\ensuremath{\mathrm{CoVaR_q}}}
\renewcommand{\v}{\ensuremath{\mathrm{VaR}_q}}

\newcommand{\eref}[1]{(\ref{#1})}
\newcommand{\fref}[1]{Figure \ref{#1}}
\newcommand{\sref}[1]{\S\ref{#1}}
\newcommand{\tref}[1]{Table \ref{#1}}
\newcommand{\aref}[1]{Appendix \ref{#1}}

\newcommand{\cq}{\ , \qquad}
\renewcommand{\P}{\mathrm{P}}
\newcommand{\Q}{\mathrm{Q}}

\newcommand{\Vx}{{\cal V}}
\newcommand{\be}[1]{\begin{equation}\label{#1}}
\newcommand{\ee}{\end{equation}}

\begin{document}

% Title of paper
\title{Measuring background risk and systemic risk in finance}
% List of authors, with corresponding author marked by asterisk
\author{Piet de Jong,  Geoff Loudon and Weihao Choo \\[4pt]
% Author addresses
\textit{Department of Applied Finance and Actuarial Studies\\ Macquarie University, Sydney, NSW 2109.}
\\[2pt]
%E-mail address for correspondence
{piet.dejong@mq.edu.au}}

% Running headers of paper:
\markboth%
% First field is the short list of authors
{De Jong}
% Second field is the short title of the paper
{Systemic risk}

\begin{abstract}
This article refines, builds on, and extends  SRISK methodology recently proposed in the literature.  The refinement is to define SRISK in terms of a put on the Basel shortfall.   This  is built on by defining the background and systemic stress  of a firm as unconditional and departure from unconditional  expectation of the put, the latter when a hypothetical systemic stress is applied.  Systemic stress is defined in terms of a random variable and can take on variety of forms including alternative scenarios in usual stress testing as well stress driven by the interaction of variables.  Stressor random variables  are chosen by the practitioner.  Stressed expectations are linear, a sector systemic stress is naturally defined as linear in the firm specific systemic stress.      Application is made to Australian financial data. 
\end{abstract}

\maketitle

JEL classification
C15; E53; G21  (Needs to be filled out)

\section{Background}

Recent literature in the area of quantitative systemic stress measurement includes 
\cite{adrian2011covar},
\cite{acharya2012capital},
\cite{acharya2012measuring},
 \cite{brownlees2010volatility} and \cite{brownlees2015}.   The proposed research aims to extend and apply these techniques particularly in relation to the entities regulated by APRA.   Thus our  broad aim is to develop, implement and bring to bear recent developments in stress testing  on the aims of APRA and the CIFR targeted research areas.   (This needs much more commentary).

This study refines and develops recently proposed methods and applies the same to publicly available daily financial data for  the eight  Australian banks detailed in \tref{eightbanks} spanning the period from   3 April 2000 through to 1 December 2014.  The data is described in detail in \aref{data}.  Prices, adjusted for dividends are plotted in \fref{prices}.   Prices are combined with number of shares to derive total equity.    Total debt for each firm at each day is also collected.  (Should these be plotted?).

\begin{table}[htdp]
\label{banks}\caption{Major and minor Australian banks}\label{eightbanks}
\begin{center}
\begin{tabular}{l|l||l|l}
\hline
 \multicolumn{2}{c||}{major}& \multicolumn{2}{c}{minor}\\
 \hline
cba & Commonwealth Bank  & mqg & Macquarie \\
anz & Australia \& New Zealand  & boq & Bank of Queensland\\
nab & National Australia  & ben & Bendigo and Adelaide \\
wbc & Westpac & aba & Auswide \\
\hline
\end{tabular}
\end{center}
\end{table}%

\begin{figure}[htbp]
\begin{center}
\includegraphics{figures/prices.pdf}
\caption{Stock  prices of four major (left panel) and four minor (right panel) Australian banks from early 2000 through to the end of 2014.  All prices normalised to start at 1.}
\label{prices}
\end{center}
\end{figure}

\section{Capital shortfall and leverage}

If $d_{it}$ and $w_{it}$ are the debt and equity of a firm $i$ at time $t$ and $\kappa$ is the capital requirement,  then the capital shortfall at time $t$ is 
\be{shortfall}
\kappa(d_{it}+w_{it}) - w_{it} = \kappa d_{it}  - (1-\kappa) w_{it} = \kappa d_{it}\left(1-\e^{-\ell_{it}}\right)\ ,
\ee
where 
$$
\ell_{it} \equiv  \ln\frac{\kappa d_{it}}{(1-\kappa)w_{it}}= \ln\frac{d_{it}}{w_{it}}+\logit(\kappa) \cq \logit(\kappa)\equiv \ln \frac{\kappa}{1-\kappa} \ .
$$
The quantity $\ell_{it}$ is called   adjusted log--leverage and $\ell_{it}>0$ implies capital shortfall \eref{shortfall} is positive.
Basel II assumes\footnote{See for example \cite{brownlees2015}.   The value of $\kappa$ can and is varied to test for sensitivity etc.} 
 $\kappa=0.08$ implying $\logit(\kappa)=-2.44$ and  $\ell_{it}$ is the actual log--leverage minus 2.44.   
As the actual  log leverage of a firm  increases to 2.44, the firm approaches a Basel breach.

\fref{Bloglev} displays Basel log--leverages for the four major and four minor Australian banks listed in \tref{banks} on the first trading day of each month from January 2003  through to December 2014.  Note most banks are Basel compliant up to about 2008.

\begin{figure}[htbp]
\begin{center}
\label{Bloglev}
\includegraphics{figures/bloglev.pdf}
\caption{Adjusted log--leverages for four major (left panel) and four minor (right panel) Australian banks from the beginning of 2003 through to end of 2014.  All banks contravene the threshold (corresponding to the zero horizontal) around the start of 2009.}
\end{center}
\end{figure}

\section{Future capital shortfall}

Financial institutions and regulators are concerned with future Basel compliance and in assessing  the likelihood of a  future Basel breach.   Future compliance depends on the future return on equity.   Consider  firm $i$ at time  $t+h$ where $h>0$.  Then\footnote{In the further development $\e^\nu$ is the continuously compounded return and $\nu$  the  rate of return or log return.}
$$
\ell_{i,t+h} = \ln \frac{d_{i,t+h}}{w_{i,t+h}} +\logit(\kappa)= \ell_{it} -\nu_{it}\cq \nu_{it}\equiv \ln\frac{w_{i,t+h}}{w_{it}}  \ ,
$$
where it is assumed $d_{i,t+h}=d_{it}$.  Hence $\nu_{it}$ is the log return on equity over $(t,t+h)$.  The future return is unknown at time $t$ but its distribution may be  well understood.

The capital  shortfall  at time $t+h$ is,
\be{bs}
\kappa d_{it} |1-\e^{\nu_{it}-\ell_{it}}|^+\cq  |x|^+\equiv \max(0,x)\ . 
\ee
Thus shortfall \eref{bs} is a put on the return $\e^{\nu_{it}-\ell_{it}}$  with strike 1.  
The Basel  limit is reached at $t+h$ if $\nu_{it}=\ell_{it}$ and  breached  if
$\nu_{it}< \ell_{it}$.
A breach is  unlikely if $\ell_{it}$ is low i.e. either the log--leverage is low, or the  constant $\kappa$ in the calculation of $\ell_{it}$ is low.

If there is a breach, $\nu_{it}<\ell_{it}$, then the amount in \eref{bs} makes up for the shortfall.   This amount may be cold comfort to regulators as it leaves the firm in a precarious position, teetering on the edge of non--compliance.

Default put options similar to \eref{bs} have been discussed in the insurance literature as critical to an evaluation of a firm:  see for
example \citet{merton1977analytic}, \citet{doherty1986price}, \citet{cummins1988risk}, \citet{myers2001capital} and \citet{sherris2006solvency}.

To illustrate the setup, \fref{simulation}   displays two snapshot outputs from projections generated as described  in \aref{garchdcc}:  6000  simulated one month ahead projected returns for  CBA and the market, on  two dates: the first trading day in January 2009 and the first trading day in December 2014.    Both panels use the same horizontal and vertical scales.   Thus based on the available data at those two points in  time, policy makers and regulators faced entirely different projections based on the same time series model.   The scatter of dots are the forward simulations.  Note there is no lookahead bias as the model at each time point is based on the available data to that point in time.    The red horizontal line in each panel indicates the projected Basel limit:  any firm return less than the limit would constitute a Basel breach.   In the left panel there is little confidence that the Basel limit will be reached since it requires a return on equity approaching 20\% -- with confidence less than xxx the Basel standard will be breached.  In the right panel there is no chance of a Basel breach under any of the projected return on equity view -- the bank is ``safe."

 The black dots in each panel indicate the actual outcome after one month.    In the left panel the outcome is a decline in both  the market and stock price.    In the right panel the returns are xxx and xxx.    Thus at the beginning of January  2009 the CBA bank was projected to be far from compliance in one month's time  while in December 2015 the one month projection is of complete compliance.

 The two panels  display very different volatility and slopes.  These snapshots are used to compute systemic stress.

\begin{figure}[htbp]
\begin{center}
\includegraphics{figures/simulation.pdf}
\caption{Forecast bivariate distribution of one month forward rates of return   for CBA (vertical axis) and the market rate of return (horizontal axis) at start of January 2009 (left panel)  and December 2014 (right panel). Note scales in both panels are the same, the relatively large volatility in the left panel, and the left skew in the  marginal distributions.  Yellow and black dot in each panel indicate origin (0,0) and  realized forward  rate of return, respectively.   Red lines indicate Basel limit -- any firm return below the limit indicates a Basel breach given the bank leverage on the applicable date.}
\label{simulation}
\end{center}
\end{figure}

\section{Systemic risk -- SRISK}\label{srisk}

 \cite{brownlees2015} define  systemic risk (SRISK) for a group of firms  at time $t$ as
\be{esrisk}
\mathrm{SRISK}_t\equiv\kappa\sum_i d_{it}|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+ \ ,
\ee
where  $\Es$ denotes  conditional expectation given a major general market downturn.  The proportionate contribution of firm $i$  to \eref{esrisk} is defined as the systemic risk in firm $i$  
 \be{sriskperc}
 \mathrm{SRISK}_{it}\equiv \frac{\pi_{it}|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+}{\Ex_d\{|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+\}}\cq \pi_{it}\equiv \frac{d_{it}}{d_t}\cq d_t\equiv \sum_i d_{it}\ , 
 \ee
where $\Ex_d$ denotes  debt weighted averaging at time $t$,  weighted averaging across firms $i$  using weights $\pi_{it}$.     Large $\mathrm{SRISK}_{it}$ indicates firm $i$ is systemically important: either because it holds a high proportion of the total debt, or it is unusually likely to breach the Basel capital requirement.  Expression \eref{sriskperc} depends on $\kappa$ through each of the $\ell_{it}$.

Given a general market downturn, the values of the puts $|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+$  in \eref{sriskperc} are known at time $t$:  there is no uncertainty except for possible  uncertainty in estimating the conditional  expected value.

Since
$$
|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+ \le\Es(|1-\e^{\nu_{it}-\ell_{it}}|^+)\ ,
$$
with equality  if  $\nu_{it}-\ell_{it}$ is concentrated on the negative axis.  If  $\nu_{it}>\ell_{it}$  has positive probability then the  inequality is strict.   Further $\mathrm{SRISK}_{it}$ in \eref{sriskperc}   is zero whenever
$$
\Es(\e^{\nu_{it}})\le\e^{\ell_{it}}\ .
$$
This inequality typically holds even if the expectation conditions on an extreme market downturn.

\section{Improved systemic risk measurement}

Following from \eref{bs}   define\footnote{Alternative terminology is the per unit capital shortfall put and the per unit expected capital shortfall.  For shortness we prefer the adjective Basel.  Note ``risk" here is not a probability but rather a measure of expected capital shortfall.} the  Basel put and  Basel risk of firm $i$ at time $t$ as
\be{put}
p_{it}\equiv |1-\e^{\nu_{it}-\ell_{it}}|^+\cq q_{it}\equiv \p(\nu_{it}\le \ell_{it})=\frac{\E(p_{it})}{\E(p_{it}|\nu_{it}\le \ell_{it})}\ ,
\ee
respectively, where $\E$ denotes unconditional expectation.  Note $0\le p_{it}\le 1$ with $p_{it}\rightarrow 0$ or 1 as $\nu_{it}\rightarrow\pm\infty$.
Further the Basel risk  $q_{it}$ increases as the distribution of $\nu_{it}$ moves to the left.  Both $\E(p_{it})$ and $q_{it}$ are thought of as probabilities of default with the former reflecting the whole distribution of $\nu_{it}$ given there is a default $\nu_{it}\le\ell_{it}$.

The total Basel put value  for firm  $i$ is   
$$
\kappa d_{it}\E(p_{it}) = \kappa d_{it}q_{it}\E(p_{it}|\nu_{it}\le \ell_{it})\ ,
$$
the cost of insuring firm $i$ does not breach the Basel standard.  In practice it may be appropriate to discount $p_{it}$ in \eref{put} by the interest rate over the period $(t,t+h)$ and value the put with risk neutral rather than normal expectation.

The put $p_{it}$ is tradable since, given $\kappa$, it relies only on the present leverage and the future return $\nu_{it}$ on equity $w_{it}$.  Market participants can value the put in  the same way as any other put and use the contract to diversify risk.  Firms can buy puts in the market to hedge Basel default risk.

However regulators will value the puts $p_{it}$ using a stressed, rather than risk neutral, expectation.   Stressed expectations correspond closely to conditional expectation given a system wide financial shock.    Regulators are concerned with the possibility of Basel breaches if such shocks occur and  have an  interest in monitoring stressed expectations.   In the extreme regulators can charge firms all or a  proportion of their stressed put values if there are implicit government bailout guarantees.

\section{Stressed expectation}

In the above development $\E$  is  unstressed expectation:  that is expectation that does not assume a stressful scenario.   A stressed expectation, denoted $\Es$, is a
linear combination of  expectations, each assuming some level of stress
\be{formula}
 \Es(p_{it}) \equiv \E\{\phi\E(p_{it}|\phi)\} = \E(\phi p_{it}) = \E(p_{it}) + \cov\{\E(p_{it}|\phi),\phi\}\ .
\ee 
Here $\phi\ge 0$ with $\E(\phi)=1$ is a stress factor or ``stressor,"  defining events impacting $p_{it}$  and serving as a basis for stress testing.  Thus stress $\phi$ changes the expected value $\E(p_{it})$ by the covariance between the conditional expectation $\E(p_{it}|\phi)$  and the stressor $\phi$.

The conditioning variable $\phi$  downplays or highlight different scenarios.  The conditioning events are scenarios of interest and  probabilistic weighting is according to the level of interest.  The first equality in \eref{formula}  from the definition of conditional probability \citep{whittle2000probability}.  The second equality follows from
$$
\cov(p_{it},\phi)=\cov\{\E(p_{it}|\phi),\phi\}\ .
$$
The covariance is zero whenever  $p_{it}$ is independent of $\phi$ which occurs if $\phi=1$.

The stressed expectation \eref{formula}  is the mean of $p_{it}$  using the  density
\be{post}
\int \phi f(p_{it},\phi)\de \phi= \E(\phi|p_{it})f(p_{it})\cq \int \phi f(p_{it},\phi)\de \phi\de p_{it} = \E(\phi) = 1\ 
\  ,
\ee
where $f$ denotes density.  
Any outcome $p_{it}$ such that $\E(\phi|p_{it})$ is large  is amplified and vice versa.   To a Bayesian the density in the left  expression of $\eref{post}$ is a posterior density given a prior $f(p_{it})$ and ``likelihood" $\E(\phi|p_{it})$: more importance is given to outcomes   $p_{it}$  where $\phi$ is expected to be large.

\section{Background stress versus systemic stress}

The right hand side of \eref{formula} splits the stressed expectation $\Es(p_{it})$ into two components: 
\be{vsstress}
\Es(p_{it}) =\mu_{it}+s_{it}\cq 
 \mu_{it} \equiv \E(p_{it})=q_{it}\E(p_{it}|\nu_{it}\le \ell_{it}) \ ,
\ee
$$
s_{it} \equiv \cov\{\E(p_{it}|\phi),\phi\}\ , 
$$
called  the background stress  and systemic stress, respectively, in firm $i$ at time $t$.  Since both $\Es(p_{it})$ and $\E(p_{it})$ lie between 0 and 1 it follows both $\mu_{it}$ and $s_{it}$ lie between 0 and 1 and  are loosely interpreted as probabilities.

The  term $\mu_{it}$  is called the background stress in firm $i$ and  reflects the log--leverage and the return volatility of firm $i$ at time $t$.  Background stress is unrelated to the stress factor $\phi$ and based on the unstressed distribution of the forward return $\nu_{it}$ and depends on the current view of the likely future progression of returns including their mean and volatility.     (Have to fill out discussion with how $mu_{it}$ measures the general uncertainty building up in the system with all  uncertainty  due to monitoring the system up to time $t$.)  Background stress is unrelated to the stress factor $\phi$.  Further
\be{mstress}
\mu_{it}=q_{it}\E(p_{it}|\nu_{it}\le \ell_{it})\ ,
\ee
where  $q_{it}$ is the Basel risk for  firm $i$  in the upcoming month,  while the second factor is the expected default size  (on a log scale)  if default occurs.
The probability $q_{it}$ depends on the  mean and volatility of daily returns at time $t$.

(*** unformed idea)   We can similarly decompose   (is this useful? -- Weihao can you look at this?)
$$
s_{it} = q_{\phi it}\E_\phi(p_{it}|\nu_{it}\le \ell_{it})-q_{it}\E(p_{it}|\nu_{it} \le \ell_{it})
$$

Firm $i$ is at Basel default if $\ell_{it}=0$  and then  $q_{it}\approx 1/2$.   As  $\ell_{it}$ increases from zero,  one month ahead Basel default status  becomes more certain since $\nu_{it}\le \ell_{it}$ becomes more certain and $q_{it}$ increases to 1.

\section{Systemic beta's}

The second, systemic stress component $s_{it}$ in  \eref{vsstress},  captures the financial impact of a  hypothetical system wide financial shock.   The stress $\phi$ is systemic as it is expected to affect all firms $i$.  Further $s_{it}$ is the estimated   increase in put values on account of  $\phi$.   Examples of stress factors are given in \sref{marketstress} and \sref{genstress}.

Writing  $\sigma_{\phi}$ as the standard deviation of $\phi$,  define the systemic beta of firm $i$ with respect to stress $\phi$ as
\be{zscore}
\beta_{it}\equiv \frac{s_{it}}{\sigma_\phi}
\ee
where  $\sigma_\phi$ is the standard deviation of $\phi$.   Thus $\beta_{it}$ is the systemic stress component in \eref{formula} standardised by $\sigma_\phi$ and
\be{zscore2}
\E_s(\phi)  = \mu_{it} + \beta_{it}\sigma_\phi\cq \E(p_{it}|\phi) \approx \mu_{it} + \beta_{it}\frac{\phi-1}{\sigma_\phi}\ .
\ee
The second, approximate, relationship is suggested from   $\cov(p_{it},\phi)/\sigma^2_\phi$ analogous to the regression coefficient of $p_{it}$ on $\phi$.

The expressions in \eref{zscore2} suggests two ways of  thinking about the  systemic beta's  $\beta_{it}$.   First, the left hand side equation shows systemic stress $\beta_{it}$ serves to shift the mean $\E(p_{it})$ of put prices  by, on average, $\sigma_\phi$.    The stress from $\phi$ is captured with $\sigma_\phi\beta_{it}$, the second term on the right of the first expression.   This term is called systemic stress and represents the addition to expected put prices if stress $\phi$ materialises.

Systemic beta's are stated in terms of additions to the normal put price $\E(p_{it})$. Thus in an increasingly dire financial situation $\E(p_{it})$ will increase.   However  $\beta_{it}$ and the systemic stress measures the  change in current put values  under  further $\phi$--stress.  This varies from  \cite{brownlees2015} where $\mathrm{SRISK}_i$ does not distinguish between the current, possibly high, put prices $\E(p_{it})$ and the potential  increment due to potential stress.   Thus in an increasingly dire financial situation put prices are liable to increase on account of decreasing expected returns and increasing volatility.   However our definition of systemic stress using systemic beta's measures the further effect on account of potential extra stress imposed onto the system over and above the already existing stress.   Systemic beta's capture   ``marginal" effects.

The second interpretation is based on  the right hand side approximation in \eref{zscore2} showing   the change in the  expected Basel put price if  $\sigma_\phi$ units of stress $\phi$ are applied.  The quantity $(\phi-1)/\sigma_\phi$ is thought of as a ``stress factor."   The stress factor has mean 0 and standard deviation 1 and is scaled by $\beta_{it}$ to yield the actual stress effect on  $p_{it}$.  Thus  $\beta_{it}$ is thought of a usual finance type ``beta" with respect to $\phi$.   Stress is measured in standardised units.  Units of stress take on different meaning depending on  $\phi$ as discussed below. The distribution of $\phi$ determines the distribution of the stress factor. If the stress factor is normally distributed then a stress effect more than doubling of the put value  occurs less than about $2.5\%$ of the time.

The  monetary stress of a firm is 
$
d_{it}\beta_{it}
$
and represents the change in the monetary value of the Basel put  if stress, as captured with $\phi$, is applied.

\section{Estimating background and systemic stress via simulation}

Stress $\mu_{it}$ and can be determined using simulation.   Suppose $(\phi^\o,p_{it}^\o)$ are pairs of stress and put values generated from a model: for example $\phi^\o$ may be zero unless there is a market drop below the $\alpha$--percentile in which case it is $1/\alpha$. 
Then 
\be{simulate}
\frac{1}{N}\sum_{\o=1}^N p_{it}^\o\rightarrow \mu_{it}\cq \frac{1}{N}\sum_{\o=1}^N (\phi^\o-1)p_{it}^\o\rightarrow s_{it} \cq N\rightarrow\infty\ ,
\ee
where $N$ is the simulation effort.  The approximation is increasingly accurate as $N$ becomes large.   More details are given in ...

\section{Stress based on  market return}\label{marketstress}
The setup is illustrated with  examples generalising and fine--tuning the approach of Engle.

\subsection{Market return below a percentile threshold}

Suppose the stress event is a market return in the bottom $\alpha$--tail of the  market return distribution.   Then  $\phi(u)=1/\alpha$ for $u< \alpha$ and 0  otherwise and
$$
\Es(p_{it}) = \frac{1}{\alpha}\int_0^\alpha\E(p_{it}|u)\de u = \E(p_{it}|\nu_{mt}<\tau_{t}) \ .
$$
where $\tau_t$ cuts out $\alpha$ probability in the lower tail of the $\nu_{mt}$ distribution.   Further
$$
\mu_{it}\approx \frac{1}{N} \sum_\o p_{it}^\o \cq s_{it}   \approx  \frac{1}{N/\alpha} \sum_{u^\o_{mt}<1/\alpha}  p_{it}^\o\ .
$$
In the right hand sides $\o=1,\ldots,N$ denote $N$ simulations.  The approximations decrease with the simulation effort $N$.   The effective simulation effort is $N/\alpha$ and hence $\alpha$ small requires a  large effort.

A fixed $\alpha$ cutoff  implies the actual threshold depends on the distribution and hence  on volatility and  time.  The actual threshold drop in the market $\tau_t=F_{mt}^-(\alpha)$, where $F_{mt}^-$ is the inverse distribution function of $\nu_{mt}$.  The volatility associated with the latter distribution is approximately $\sqrt{h}\sigma_{mt}$ where $\sigma_{mt}$ is current market volatility.   Regulators and practitioners  are well versed in working with VaR type calculations and hence a varying VaR type cutoff combining market volatility and stress is closely aligned to current practice.

\subsection{Expected worst market return in $n$ identical scenarios} 
If $\phi(u)=n(1-u)^{n-1}$ then $\phi(u)\de u = \de\{1-(1-u)^n\}$ and 
$$
\Es(p_{it}) \equiv \E\{\phi\E(p_{it}|\phi)\} = \int_0^1\E(p_{it}|u)\de\{1-(1-u)^n\}\ .
$$
If $u$ is the market return percentile then  $1-(1-u)^n$ is the distribution of the worst percentile outcome in $n$ identical trials and hence the stressed expectation is that of the expected put price given the worst percentile market return in $n$ identical trials.  Further 
$$
s_{it}  \approx  \frac{1}{N} \sum_\o \{ n(1-u^\o_{mt})^{n-1}-1\}p_{it}^\o \ . 
$$
The effective simulation effort is $N/n$.
Simulated returns $\nu^\o_{mt}$ in the upper tail of the distribution  have percentiles $u^\o_{mt}\approx 1$ and hence for these market returns $(1-u^\o_{mt})^{n-1}$ is negligable and the associated simulated put $p_{it}^\omega$ is heavily downweighed.

Note the contrast with the previous example where the bottom $\alpha$ proportion of simulated market returns are selected as the stressed sample. With the current specification for $\phi$,   every simulated put contributes to the stress computation, albeit with  different weights.

\subsection{Expected worst market return given a tail event}

The above two situations can be combined.   Suppose  $\phi(u)=c(0.05-u)^{19}$ for $u\le 0.05$ and 0 otherwise and where $c$ is such that $\phi(u)$ integrates to 1.  Then (this needs to be checked)
$$
\E(p_{it}) \approx \frac{1}{N/c}\sum_{u^\o_{mt}<1/20}  \left(u^\o_{mt}-\frac{1}{20}\right)^{20}p_{it}^\o\ .
$$
 Similar to the first example, the stressed sample picks up the bottom 5\% of market returns. The bottom 5\% of market returns is further stressed by  progressively downweighing returns as the percentile approaches 1/20.   Large simulation effort $N$ is required for a reasonable approximation since $N/c$ is the effective simulation size and $c$ is small.

\section{Simulating future capital shortfall and market return}

(maybe this should be merged with material elswhere).

The estimation of systemic beta's requires  projections of future capital shortfalls and future stressors.   As in \cite{brownlees2015} in this article projections are constructed  using time series models modelling the forward rates of return $\nu_{it}$ for firms $i$ and $\nu_{mt}$ for the market.   The market return is used as the stressor with different choices of the stress function $\phi$ modelling different stress scenarios.

The time series models used for projecting are stochastic volatility models based on the GARCH--DCC model of \cite{engle2002dynamic} summarised in \aref{garchdcc}.    The GARCH--DCC framework is only one possible implementation.   For example future return scenarios may be constructed in a more ad--hoc manner e.g. judiciously chosen scenarios decided on by regulators or policy makers.   The  systemic beta framework can be based on  any  generated  future  scenarios.

While the above discussion suggests, as obvious after the fact, that in December 2009 the CBA bank was under much stress.   However the above calculations do not actually reflect real stress.   In terms of the development of the previous sections the actual stress is beta given a stressor function $\phi$ and stressor variable.   In this case the stressor variable is the market return, on the horizontal axis in each panel.   Stress occurs if the market return is low.   In the left panel low market outcomes are likely to lead to sharply lower CBA bank returns, as compared to the right panel.   This is suggested by the slope of the scatter plots:  the left slope appears steeper than the right and hence any stress in the market -- in the sense of a market downturn is expected to lead to a larger drop in the CBA bank return in the left scenario as compared to the right scenario.   The magnitudes of the two responses depends on the stressor function.   In essence the stressor function formalises the notion as to what constitutes a ``big" drop.   If a big drop is the expected worst in 20 similar market scenarios then the stress in the left and right are xxx and xxx, respectively.

\section{One month ahead forecast stress in individual financial institutions}

\fref{default} displays, in the top panels, the estimated $q_{it}$ one month ahead default probabilities for each major and minor Australian banks based on the projected one month ahead return distribution.   The  top left panel shows the first inclinations of default arose with NAB in early 2008 followed one month later by ANZ, and  a further few months later by WBC and CBA.

Systemic stress is an expected  market return equal to the worst outcome in 12 identical months.  (Have to expand on this).
(Need much more commentary here)

 \begin{figure}[htbp]
\begin{center}
\label{default}
\includegraphics{figures/default.pdf}
\caption{Forecast one month ahead  Basel default probability (top panels), background stress (middle panels) and systemic stress (bottom panels) for  four major (left panel) and four minor (right panel)  banks from the beginning of 2003 through to end of 2014.  Note different scale on bottom two rows of panels.}
\end{center}
\end{figure}

\section{Average stress}

There are two ways of aggregating stress in the financial sector as a whole.  The first is to average, using debt weighted averaging, the put
\be{nsrisk}
\overline p_t \equiv \Exd(p_{it}) \cq \Es(\overline p_t)=\Exd\{\Es(p_{it})\} = \Exd(\mu_{it}+s_{it}) \equiv \overline\mu_{t}+\overline s_t
\ee
The put $\overline p_t$ in \eref{nsrisk} pays out zero if all firms meet the Basel requirement with payments increasing with the number of Basel breaches, the sizes of the breaches, and the relative debt sizes of the breaching firms.   Further $\overline p_t>0$  if and only if one or more firms breach the Basel standard.    The relation in \eref{nsrisk} follow since  $\Es$ and $\Exd$ are linear.   (Is $\overline q_t$ a useful concept?   Weihao can you look at this?)

The monetary value  average  stress at time $t$ is the debt averaged  monetary firm stresses
$$
\kappa d_t\overline\mu_t = \kappa d_t\Exd(\mu_{it}) = \kappa\sum_i d_{it}\mu_{it}\cq \kappa d_t\overline s_t  = \kappa\sum_i d_{it}s_{it}\ . 
$$
Firm  $i$ contribution to for example systemic stress is   
$
\pi_{it}s_{it}/\overline s_t
$
which, when adding across firms, adds to 1.  Other contributions are calculated similarly.

Percentage contributions of firms to background and systemic stress are calculated as
$$
\frac{\pi_{it}\mu_{it}}{\overline \mu_t} \equiv \frac{\pi_{it}\mu_{it}}{\Ex_x(\mu_{it})}\cq \frac{\pi_{it}s_{it}}{\overline s_t} \equiv \frac{\pi_{it}s_{it}}{\Ex_x(s_{it})}\ .
$$
where $\pi_{it}\equiv d_{it}/d_t$ is the proportion of total debt held by firm $i$.   A ratio such as $s_{it}/\overline s_t$ compares the stress in firm $i$ to average stress but does not signal the importance of that firm to the system as a whole.

\section{Total sector stress}

The debt weighed average system  put $\overline p_t\equiv\Ex_d(p_{it})$ is an average put and does not permit  diversification -- the  sharing of debt and equity across firms.   Sharing may not be possible in practice but the concept is useful for assessing the stability of the system as a whole.   This leads to the second way of aggregating stress in the financial sector as whole.

Write  $d_t$ and $w_t$ are total debt and equity in the financial sector, respectively:
$$
d_t \equiv \sum_i d_{it}\cq w_{it} \equiv \sum_i w_{it}\ .
$$
Then the   adjusted log leverage for the sector is  
$$
\ell_t \equiv  \ln \frac{d_t}{w_t} +\logit(\kappa) =  \ln \sum_i\frac{w_{it}}{w_t}\left(\frac{ d_{it}}{ w_{it}}\times \frac{\kappa}{1-\kappa}\right) = \ln \Ex_w(\e^{\ell_{it}}) \ ,
$$
where $\Ex_w$ denotes equity weighted averaging.  A system wide breach occurs at $t+h$ if
$
\nu_t < \ell_t
$
where $\nu_t$ is the forward rate of return on total equity $w_t$:
\be{ew}
 \nu_t =  \ln \frac{w_{t+h}}{w_t} = \ln\Ex_w\left(\frac{w_{i,t+h}}{w_{it}}\right) = \ln \Ex_w(\e^{\nu_{it}})\ . 
\ee
In terms of this notation the system Basel put  and Basel risk are defined similar to \eref{put}
$$
p_t\equiv |1-\e^{\nu_t-\ell_t}|^+\le \overline p_t\cq q_t\equiv \frac{\E(p_t)}{\E(p_{t}|\nu_t<\ell_t)}=\p(\nu_t\le \ell_t) \ .
$$
The inequality is proved in  \aref{proof}.  The  put $p_t$ pays 0 at time $t+h$ unless the sector as whole is in Basel default, occurring if $\nu_t  <  \ell_t$. Moving from $\overline p_t$ to $p_t$  allows for diversification:   low liquidity  in one firm is offset by high liquidity  in other  firms.

\begin{figure}[htbp]
\begin{center}
\label{muqs}
\includegraphics{figures/muqs.pdf}
\caption{Average  stresses and  total stresses.   Stress measurements are, left to right, $\mu$, $q$ and $s$, respectively.   The top row of panels measure for example (top left panel)  $\overline \mu_t$ and $\mu_t$ over time.    In the bottom row of panels  specific stresses are measured are against each other:  for example $\mu_t$ (vertical axis) versus $\overline\mu_t$ (horizontal axis).  In all cases there is no total stress until there is an appreciable level of average stress.  Systemic stress $\overline s_t$ appears to be the least diversifiable.}
\end{center}
\end{figure}

Similar  to \eref{zscore2}, total  stress is decomposed as 
\be{overall}
\Es(p_t) = \mu_t  + s_t\cq q_{t}=\P(\nu_t<\ell_t) \cq  s_t \equiv \cov\{\E(p_t|\phi),\phi\}\ .
\ee
termed the sector background  and systemic stress, respectively.   Further $q_t$ is the probability of  a sector Basel default with the second factor the expected size (on a log scale) of the default if there is a Basel default.

System resilience aims to answer the question whether the system as a whole can absorb shocks.   The capacity to absorb relies on implicit merging.  When two firms merge the leverage of the resulting firm is less than that of the more highly leveraged firm.   The merged firm is more able to withstand return on equity shocks  unless negative shocks are more prone for the merged firm.   Similarly when many firms merge Basel puts for the conglomerate become less valuable.

Firms do not necessarily merge, even in dire financial circumstances.   Hence the mergers spoken of here are hypothetical.   From a regulators perspective, what would happen under a merger of all firms (or perhaps a group of firms) is nevertheless of interest.   A system as as a whole near Basel non--compliance is more threatening that one where a few firms are near Basel non--compliant but the system itself is well away from non--compliance.

System compliance  is partially monitored with the system put $p_t=\Exd(p_{it})$ and its stressed expectation $\Es(p_t)$.   The system put however simply monitors a debt weighted average of puts.   It gives no guidance as to how much risk can be diversified away.   Basing a put on system wide aggregated debt and equity and comparing the same to $p_t$  gives at least some guidance.

Possible additional issues to be discussed here
\bi
\i  Usually  $q_t<\overline q_t$ reflecting diversification benefits.   However this inequality is not guaranteed since ???
$$
\Ex_d\{\P (\nu_{it}\le \ell_{it})\} \ne  \P\{\Ex_d(\nu_{it})\le \Ex_d(\ell_{it})\}
$$
\i   Comparing say $\overline s_t/s_t$ or $(\overline\mu_t+\overline s_t/(\mu_t+s_t)$ etc.   What do each of these different measures illustrate? (System robustness)
\i   Percentage measures such as  $\pi_{it}s_{it}/s_t$,  or $\pi_{it}s_{it}/(s_t+\mu_t)$.
\i  System robustness such as 
\ei

 \section{Further generalised stress functions}\label{genstress}

Practical results for the  construction of general stress functions $\phi$ are contained in the next three subsections.

 \subsection{Stress functions as  weighted linear combinations of tail events}

\cite{brownlees2015} define a systemic event as a market based downturn greater than a certain threshold and a systemic event  depends on the chosen threshold.   This arbitrariness is partially sidestepped by choosing a decreasing function $\phi=\phi(u_{mt})$ on the unit interval and noting 
\be{wave}
\E\{\phi\E(p_{it}|\phi)\} = -\E\{u\phi'(u)\E(p_{it}|u_{mt}\le u)\}\ .
\ee
The equivalence of the left and right hand sides of \eref{wave}  follows from 
$$
\int_0^1 \phi'(u)  \int_0^u \E(\nu_{it}|u_{mt})\de u_{mt}   \de u =\int_0^1\E(\nu_{it}|u_{mt})\int_{u_{mt}}^1  \phi'(u) \de u \de u_{mt}\ ,   
$$
provided $\phi(1)=0$.

Thus stressed expectations, stressed with a decreasing function of the market return, is equivalent to taking a weighted average of conditional lower tail expectations.  This result is used to circumvent an explicit choice for the market threshold, replacing it with  $\phi(u)$, an implicit  mixture of thresholds.

\subsection{Scenario based stress testing}
 Stress events captured with $\phi$ and used  in \eref{zscore}  can be defined with respect any events, including a discrete number of scenarios labelled $k=1,2, \ldots$.   In this case 
$$
\Es(p_{it})= \sum_k \pi_k\phi_k\E(p_{it}|k)\cq \sum_k\pi_k\phi_k = \E(\phi) = 1 ,
$$
where $\phi_k$ is the weight assigned to scenario $\kappa$.   The $\pi_k\phi_k\ge 0$ are  modified  probabilities which weigh different scenarios according to level of interest.   For example in standard stress testing the $\phi_k$ are chosen such that significant weight is given to scenarios $\kappa$ causing high  firm distress.   The ``real world" probabilities $\pi_k$ are  usually ignored by  simply choosing  $\pi_k\phi_k$ to be of  required magnitude.

In the discrete case $s_{it}$ compares the expected value under an average of distress scenarios to the average without distress.  The quantity $\sigma_\phi$ is now of limited relevance, signalling the volatility in the distress probabilities.

\subsection{Copula stress functions}

Stress can be based on a vector of variables $x$ with distribution $F(x)=u$ and marginal densities $f(x_j)$.    Suppose $c(u)$ is the copula density of $x$ implying the density of $x$ is $c(u)\prod_jf(x_j)$.    If   $\phi(u)$ is a copula density then $\E\{\phi(u)\}=1$ and
consider
\be{copula}
\Es(p_{it}) \equiv \int \E(p_{it}|x)\phi(u)c(u)\prod_j\{f(x_j)\}  \de x   \ .
\ee
If $\phi(u)=1$  then $\Es(p_{it})=\E(p_{it})$, the ordinary expectation.   The density $\phi(u)$ magnifies potentially stressful situation such as where all component of $x$ are highly  tail dependent.

The copula density stressor $\phi(u)$  can be combined with marginal stressors written as functions of $x_j$ or  percentiles $u_j$.  If the latter then $\phi(u)\prod\phi(u_j)$ is the total stressor, corresponding to a density on the unit hypercube with non--uniform marginals  $\phi(u_j)\ne 1$.

Copula stress effects are simulated as follows.   Suppose $x$ is a vector $\nu_{mt}$ of  market factors  over the period $(t,t+h)$.   Simulations of a joint model are  used to  derive  vectors $(p_{it}^\o,\nu_{mt}^\o)$, $ \o=1,\ldots, N$.  The $\nu_{mt}^\o$ are  converted to percentiles $u^\o$ and scalars 
$$
\phi^\o\equiv\phi(u^\o)\prod_j\phi(u_j^\o)\cq \o=1,\ldots, N\ .
$$
The stress beta is then estimated as in \eref{simulate}.

\section{Risk weighted asset methodology}

The risk weighted asset (RWA) methodology (references ???) for determining capital adequacy is to value  assets  and subtract debt to arrive at capital shortfall.   The capital shortfall is then, similar to \eref{shortfall},
\be{csrwa}
\kappa d_{it} - (1-\kappa)\sum_j \e^{-r_{ijt}}a_{ijt}  = \kappa d_{it} - (1-\kappa)a_{it}\Ex_a(\e^{-r_{ijt}})\cq a_{it}=\sum_j a_{ijt}\ .
\ee
Here $a_{ijt}$ is the value of firm $i$'s asset  $j$ at time $t$.   Further the $r_{ijt}\ge 0$ are risk weights and $\Ex_a$ denotes an asset weighted average using  firm $i$'s asset values at time at time $t$.   If  $r_{ijt}=0$ in  \eref{csrwa} then  asset $j$ is valued at its present value. Higher weights reflect more risky assets and  potential  for asset devaluation.   The RWA methodology is a standard  approach to capital shortfall calculations.

The RWA calculations can be fit into the present framework.   If $\nu_{ijt}$ is the forward return on firm $i$ class $j$ asset at time $t$ then     a put on the  projected capital shortage at time $t+h$ is, per unit $\kappa d_{it}$, 
\be{modput}
p_{it}\equiv \left|1 - \e^{-\logit\kappa-L_{it}}\Ex_a(\e^{\nu_{ijt}})\right|^+ \cq L_{it}\equiv \ln\frac{d_{it}}{a_{it}} \ .
\ee
Thus $\e^{L_{it}}$ is the often used alternative leverage definition: dividing debt by total assets.   Similar to before $0\le p_{it}\le 1$ is a measure of  stress on firm $i$ at time $t$ with expected stress decomposed as before
$$
\Es(p_{it}) = \E(p_{it}) + \cov\{\E(p_{it}|\phi),\phi\} = \mu_{it} + s_{it}\ ,
$$
where $\mu_{it}$ is the background stress and $s_{it}$ is the systemic stress, i.e. the result of systemic event modelled with $\phi$.

To calculate asset weights $w_{ijt}$, a sample of $N$ forward returns $\nu_{ijt}^\o$ and stress factors $\phi^\o$ are  simulated using an appropriate model such as the GARCH--DCC model.   The returns $\nu_{ijt}^\o$ are used to derive $\Ex_a(\e^{\nu_{ijt}^\o})$ and in turn, using \eref{modput},   $p_{it}^\o$ which are multiplied by $\phi^\o$ to arrive at stressed put prices  $\phi^\o p_{it}^\o$.   As $N\rightarrow\infty$,
\be{rwa}
\frac{1}{N}\sum_\o \phi^\o p_{it}^\o\rightarrow \Es(p_{it})\cq \Ex_a\left( \frac{1}{N}\sum_\o\phi^\o\e^{\nu_{ijt}^\o}\right)\rightarrow \Es\{\Ex_a(\e^{\nu_{ijt}})\}\ .
\ee

Note that 
$$
\Es(p_{it}) \ne \left|1-\e^{-\logit\kappa-L_{it}}\Es\{\Ex_a(\e^{\nu_{ijt}})\}\right|^+\ ,
$$
and the stressed average return
$$
\Es\{\Ex_a(\e^{\nu_{ijt}})\} = \Ex_a\{\Es(\e^{\nu_{ijt}})\} \approx \Ex_a\left( \frac{1}{N}\sum_\o\phi^\o\e^{\nu_{ijt}^\o}\right)\ ,
$$
is cannot be used directly in the calculation of the stress in the firm.

Easily disstressed assets $j$  have a return distribution sensitive to stress $\phi$ and under stress, $\e^{\nu_{ijt}}$ is likely to be much less than 1.  Assets whose return $\e^{\nu_{ijt}}$  tends to be much less than 1 when stress $\phi$ is high,  have high risk and low weight.  An asset with no volatility, $\nu_{ijt}\equiv 0$, has risk weight 1 since, on average, $\phi^\o$ is 1.

\section{Application to Australian financial institutions}

 (have to merge this with other stuff elsewhere)

At each of the first trading day in the months from January 2003 through to December 2014,  all prior returns are used estimate a TARCH-DCC model described below.   For each first trading day of the month, the fitted model is then used to simulate the forward return distribution over the next 22 trading days, corresponding to approximately one month.  The details of the fitted models are described in the next subsection.

\subsection{Forward return simulation}

The forward simulations are implemented similar to \cite{brownlees2015}.   Given the latest available volatility and correlation estimates the filter recursions are moved forward in time using innovations randomly chosen from past standardised innovations.  Thus the innovations are chosen to have the same marginal distributions as applicable in the past.  The random choices are such  that the same market return innovations are used in each bivariate analysis.

\section{Background and systemic stress  compared to SRISK}

The methodology developed and employed in this article departs in two respects from the SRISK methodology set out in \cite{brownlees2015}.  This section examines the force of these differences.

\subsection{Put value versus put on expected value}

The SRISK methodology described in \sref{srisk}, in particular formula \eref{sriskperc}, is based on the put
\be{prisk}
 |1-\E_\phi(\e^{\nu_{it}-\ell_{it}})|^+\le \Es(|1-\e^{\nu_{it}-\ell_{it}}|^+) \equiv \mu_{it}+s_{it}\ , 
\ee
where stressed expectation $\Es$ in the \cite{brownlees2015} article is conditional expectation given a major market downturn.  The   put in the first expression is evaluated after the expectation $\Es$ and checks, in essence whether in a significant market downturn, the expected $h$ period ahead return $\nu_{it}$ exceeds the adjusted   log--leverage.  If this holds true there may still be substantial risk of a Basel breach, depending on the volatility of the return.   Volatility in $\nu_{it}$ is ignored in  $\mathrm{SRISK}_{it}$  other than through the usual adjustment on account of continuous compounding.  In particular increased volatility due to stress is ignored.

With $\mu_{it}+s_{it}$, volatility is taken into consideration.  Other things equal, high volatility leads to higher put values since breach size  is taken into consideration.

Note further we split up $\mu_{it}=q_{it}\E(p_{it}|\nu_{it}>\ell_{it})$.    (Can do analogous split up on $s_{it}$ ????)

(Should we compare $\mu_{it}+s_{it}$ to the left  hand side of $\eref{prisk}$ using graphs???)

\subsection{Systemic stress versus background stress}

\cite{brownlees2015} use $\Es$ as in \eref{prisk}.  A stressed expectation may be high simply on account of put prices being high, again reflecting higher than normal volatility.
Stress measured with $\Es$  picks up both background stress, due to high volatility, and the extra stress imparted by the stressing variable.

To gain insight into the relative sizes of these two components, consider the proportion of the stressed put price due to a possible future stress scenario
$$
\frac{\Es(p_{it})-\E(p_{it})}{\Es(p_{it})} = \frac{\sigma_\phi\beta_{it}}{\mu_{it}+\sigma_\phi\beta_{it}}  \ . 
$$
The denominator is total stress in firm $i$, made up of two components:   the volatility stress $\mu_{it}=\E(p_{it})$ and the systemic stress $\sigma_\phi\beta_{it}=\Es(p_it)-\E(p_{it})$.   Volatility stress  arises on account  of high volatility in the markets causing high put prices.   Systemic stress is the additional stress caused by  a potential  bad systemic event.

\begin{figure}[htbp]
\begin{center}
\includegraphics{figures/sysstress.pdf}
\caption{Systemic, $s_{it}$, versus background $\mu_{it}$   for four major banks (left panel) and four minor banks (right panel)  for 144 months.}
\label{sysstress}
\end{center}
\end{figure}

\fref{sysstress} plots systemic stress versus volatility stress for the eight Australian banks of \tref{banks}.   Generally volatility stress is higher than systemic stress.

\subsection{Flexible  stress  functions}

The further modification made to the SRISK methodology of \cite{brownlees2015} is to generalise the ``cutoff" functional form for stressing.   With the latter, stressed expectations are conditional expectations given a specified cutoff point.    In \cite{brownlees2015} the cutoff is in absolute terms:  a 10\% fall in the market although this can varied.   The cutoff methodology does not make explicit allowance for market volatility:   an absolute 10\% reduction is  increasingly plausible  as volatility increases.   However  SRISK does not  make judgement as to the likelihood of the conditioning stress event.   Thus SRISK mixes in various  sources of risk in an imprecise manner and it will be difficult to determine the implications of SRISK readings.

 This argues for specifying conditional behaviour in percentile terms relative to the then applicable market conditions.  After all, current market volatility is known and there is a good reason to disentangle current market conditions from the evaluation of what is likely to happen if further stress arrives in the system.

Say something about the generalized functional forms $\phi$ as well as the fact that we have firmly embedded and/or aligned the methodology with more ad--hoc approaches to stress testing.

\section{Comparing SRISK for different firms (not sure)}

Suppose of interest is whether $\beta_{it}$ varies similarly  across firms as $\tau$ varies where $\tau$ is the threshold, $\kappa$, or some other parameter used to compute $\beta_{it}$. High correlation implies high systemic risk since firms are simultaneously affected.

Define $\eps_{it}\equiv(\phi-1)p_{it}$ and $\eps_{it}$ as the vector with components $\eps_{it}$.  Then $\E(\eps_{it}|\tau)=\sigma_\phi(\tau)\beta_{it}(\tau)$, the stress in firm $i$ at the given parameter setting $\tau$  and
$$
\cov\{\E(\eps_{it}|\tau)\}=\cov(\eps_{t})-\E\{\cov(\eps_{it}|\tau)\}\ ,
$$
is the covariance between stresses as $\tau$, the stress parameter varies.   Thus the covariances and correlations between firms as stress parameters vary can be computed from the covariability between the $\eps_{it}$ and the ...

\begin{comment}
\subsection{Weihao - Allocating the market put}

The overall market shortfall after allowing for diversification between firms is
$$
p_{mt}\equiv k_+ |1-\e^{-\ell^*_{mt}+\nu_{mt}}|^+
= k_+|\Ex (1-\e^{-\ell^*_{it}+\nu_{it}})|^+
=I(\nu_{mt}<\ell_{mt}^*)k_+\Ex(1-\e^{-\ell^*_{it}+\nu_{it}}) 
$$
and hence the portion attributable to firm $i$ is $k_i(1-\e^{-\ell^*_{it}+\nu_{it}}) I(\nu_{mt}<\ell_{mt}^*)$, its capital shortfall or surplus when the overall market is in a shortfall. The allocation of the stressed expectation $\E(p_{mt})$ is then
$$
k_i\E\{(1-\e^{-\ell^*_{it}+\nu_{it}}) I(\nu_{mt}<\ell_{mt}^*)\}
$$
and applying $\Ex$ to the above expression yields $\E(p_{mt})$.
\end{comment}

\appendix
\renewcommand*{\thesection}{\Alph{section}}

\section{GARCH--DCC model}\label{garchdcc}

Denote the daily (log) return for firm $i$ at time $t$ as
\newcommand{\vareps}{\varepsilon}
\be{mean.model}
\delta_{it}=\mu_i+\sigma_{it}\eps_{it}\cq \eps_{it}\sim (0,1)\ ,
\ee
The volatility $\sigma_{it}$ is modelled as
\be{vol}
\sigma_{i,t+1}^2 = \omega+ \sigma^2_{it}\{\beta+(\alpha+\gamma \eps^-_{it})\eps_{it}^2\}  \cq  \eps^-_{it}\equiv I(\eps_{it}<0)=I(\delta_{it}<\mu)\ .
\ee
where $I$ denotes the indicator function.  Hence the response of $\sigma_{i,t+1}^2$ to $\eps_{it}^2$  is increased by $\gamma$   if
the rate of return is below the average $\mu_i$, compared to the response if $\delta_{it}>\mu_i$.  Equations \eref{mean.model} and \eref{vol} defined a simple threshold GARCH model:  called the TARCH(1,1).   In \eref{mean.model} the mean $\mu_i$ does not vary with time $t$ and in \eref{vol} it is assumed the terms  $\sigma_{it}^2$ and $\eps_{it}$ in the right hand side of \eref{vol} are sufficient to structure the dynamics of volatility.

The model defined by \eref{mean.model} and \eref{vol} is estimated  for each security $i$ jointly with  a similar model for  the market,  $i=m$.   The correlations between securities and the market are modelled using  positive definite recursions   \citep{engle2002dynamic}
$$
(Q_{i,t+1}-S) = \alpha (\eta_{it}\eta_{it}'-S) + \beta (Q_{it}-S)\cq \eta_{it}\equiv(\eps_{it},\eps_{mt})' .
$$
Correlations $\rho_{it}$ recovered from the $Q_{it}$ are used as the correlation between $\eps_{it}$ and $\eps_{mt}$.

\section{Computations}

All model fits in this paper have been performed with the R language \citep{R-Development-Core-Team:2008aa} and in particular the rmgarch package described by \cite{ghalanos2012rmgarch}.  All other calculations were performed using the J language \citep{iverson2003j}.

In the forward simulated forward projections the  innovations are chosen randomly from past innovations.   These past innovations are chosen consistently:  at a particular $t$ either all or none of $\eps_{it}$ are chosen.

\section{Proof of system put is less   than debt weighted average put}\label{proof}

$$
1-\e^{-\ell_{it}} = \frac{ \kappa d_{it} - (1-\kappa)w_{it}}{\kappa d_{it}}\cq \Ex_d (1-\e^{-\ell_{it}}) = \frac{\kappa d_t - (1-\kappa) w_t}{\kappa d_t} = 1-\e^{-\ell_t} \ ,
$$
and similarly if $-\ell_{it}$ is replaced by $\nu_{it}-\ell_{it}$.   Hence 
$$
p_t\equiv |1-\e^{-\ell_t}|^+ \le \Ex_d (|1-\e^{-\ell_{it}}|^+)\equiv \overline p_t\ . 
$$

\section{Use of more general puts}

Consider the put $p_{it}(1+cp_{it})=p_{it}+cp_{it}^2 $ for some constant $c\ge 0$.   This put is zero if $p_{it}=0$ and has slope $1+2cp_{it}$ for $p_{it}>0$ and $p_{it}(1+cp_{it})>p_{it}$ if the put is positive.  Larger slopes $c$ imply greater payoff.

The put $p_{it}+cp_{it}^2$ imposes a higher cost structure on defaults.    For every extra dollar of default the cost increases by $1+2cp_{it}$.   Further the stressed put value is
$$
\E(p_{it})\left\{1+c\E(p_{it})\right\} +c\left\{\cov(p_{it})\right\}+ \cov(p_{it},\phi) + c\left\{\cov(p^2_{it},\phi)\right\}
$$
$$
=\E(p_{it})\left\{1+c\E(p_{it})\right\} +c\left\{\cov(p_{it})\right\}+ \cov(p_{it}+cp^2_{it},\phi)\ .
$$
The first three terms in the final expression are unrelated to stress $\phi$: stress only impacts the last term.

Can easily determine all terms via simulation.

\section{Data sources}\label{data}

(Geoff -- can you fill out?)

\section*{References}
\bibliography{/users/pietdejong/documents/research/srisk/piet2}

\end{document}

### 2015-05-29 time series/stock return model.tex
pdj initial

\documentclass[authoryear]{elsarticle}
\usepackage{latexsym}
%\usepackage{rotate}
\usepackage{graphics}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{comment}
\bibliographystyle{chicago}

\newcommand{\logit}{\mathrm{logit}}
\newcommand{\I}{\mathrm{I}}
\newcommand{\E}{\mathrm{E}}
\newcommand{\p}{\mathrm{P}}
\newcommand{\e}{\mathrm{e}}
\newcommand{\vecm}{\mathrm{vec}}
\newcommand{\kp}{\otimes}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\cov}{\mathrm{cov}}
\newcommand{\eps}{\epsilon}
\newcommand{\ep}{\varepsilon}
\newcommand{\obdots}{\ddots}    % change this later
\newcommand{\Ex}{{\cal E}}
\newcommand{\rat}{{\frac{c_{ij}}{c_{i,j-1}}}}
\newcommand{\rmu}{m}
\newcommand{\rsig}{\nu}
\newcommand{\fd}{\mu}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\cor}{\mathrm{cor}}
\newcommand{\bx}[1]{\ensuremath{\overline{#1}|}}
\newcommand{\an}[1]{\ensuremath{a_{\bx{#1}}}}

\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}

\renewcommand{\i}{\item}
\newcommand{\sr}{\ensuremath{\mathrm{SRISK}}}
\newcommand{\cs}{\ensuremath{\mathrm{CS}}}
\newcommand{\cri}{\ensuremath{\mathrm{Crisis}}}
\newcommand{\var}{\ensuremath{\mathrm{VaR}}}
\newcommand{\covar}{\ensuremath{\mathrm{CoVaR}}}
\newcommand{\med}{\ensuremath{\mathrm{m}}}
\newcommand{\de}{\mathrm{d}}
\renewcommand{\v}{\ensuremath{\mathrm{v}_q}}
\newcommand{\m}{\ensuremath{\mathrm{m}}}
\newcommand{\tvar}{\ensuremath{\mathrm{TVaR}}}

\newcommand{\eref}[1]{(\ref{#1})}
\newcommand{\fref}[1]{Figure \ref{#1}}
\newcommand{\sref}[1]{\S\ref{#1}}
\newcommand{\tref}[1]{Table \ref{#1}}
\newcommand{\aref}[1]{Appendix \ref{#1}}

\newcommand{\cq}{\ , \qquad}
\renewcommand{\P}{\mathrm{P}}
\newcommand{\Q}{\mathrm{Q}}

\newcommand{\Vx}{{\cal V}}
\newcommand{\be}[1]{\begin{equation}\label{#1}}
\newcommand{\ee}{\end{equation}}

\begin{document}

% Title of paper
\title{Systemic risk and contagion effects in Australian financial institutions and sectors}
% List of authors, with corresponding author marked by asterisk
\author{Piet de Jong,  Geoff Loudon and Weihao Choo \\[4pt]
% Author addresses
\textit{Department of Applied Finance and Actuarial Studies\\ Macquarie University, Sydney, NSW 2109.}
\\[2pt]
%E-mail address for correspondence
{piet.dejong@mq.edu.au}}

% Running headers of paper:
\markboth%
% First field is the short list of authors
{De Jong}
% Second field is the short title of the paper
{Systemic risk}

\maketitle

\section{Joint model}

Suppose the market return is $r_m$ with stationary distribution function $F_m$ and percentile rank $u_m\equiv F_m(r_m)$. Hence $u_m$ is uniform over the unit interval in stationarity. In addition the return of stock $i$ is $r_i$ with percentile rank $u_i\equiv F_i(r_i)$ where $F_i$ is the stationary distribution function. There are $n$ stocks forming the market: $i=1,\ldots, n$. In addition the joint distribution of $(u_m,u_i)$ is $C_i$, a copula. Returns of individual stocks are partly driven by the market, known as systematic risk in the capital asset pricing model.
\newline

It is well known that stock returns in the short term exhibit behaviour such as volatility clustering and varying dependence. This behaviour is captured by assuming $u_m$ is a time series, or $u_{m,t}$, deviating away from uniformity in the short term but attaining uniformity in stationarity. Given $u_{m,t}$,  market return is $r_{m,t}=F_m^-(u_{m,t})$. In addition $u_{i,t}$ is drawn from the conditional distribution $C_i(u_i|u_m)$ and the return on stock $i$ is $r_{i,t}=F_i^-(u_{i,t})$. Similar to $u_{m,t}$, $(r_{m,t},r_{i,t})$ deviates from its stationary joint distribution in the short term.
\newline

Assume:
\bi
\i $F_m$ and $F_i$ have fat tails

\i $C_i$ captures positive dependence overall, and strong tail dependence

\i $u_{m,t}$ exhibits volatility clustering, that is sustained periods of stability or volatility, but uniform as $t\rightarrow \infty$.
\ei
The above setup captures stylised features of short term stock returns in the following way:
\bi
\i Fat tail distributions and strong tail dependence give rise to simultaneous extreme stock returns representing market crashes or surges.

\i Volatility clustering of both market and individual stock returns due to positive dependence.

\i Strong inter-stock dependence during market volatility due to tail dependence, and weaker dependence in times of stability.
\ei

\section{Illustration}

Suppose the pseudo market return follows a ARCH(3) process
$$
r_{m,t}=F_m^-\{\p(\tilde{r}_{m,t})\} \cq \tilde{r}_{m,t}=\epsilon_t \sqrt{a+b\tilde{r}_{m,t-1}^2+c\tilde{r}_{m,t-2}^2+d\tilde{r}_{m,t-3}^2} \;,
$$
where $\p$ is the percentile rank transform and $\epsilon_t$ is white noise. Then whilst market return $r_{m,t}$ follows $F_m$ in the long run, there are volatility clusters whereby $r_{m,t}$ is volatile for a sustained period (when $r_{m,t}$ is large) and stable otherwise (when $r_{m,t}$ is small). Assume $a=1$, $b=0.5$, $c=0.3$ and $d=0.2$.
\newline

Consider two stocks. Model the dependence between their returns with the market return using a factor copula
$$
u_{m,t} = \p(f-g+e_m) \cq u_{1,t} = \p(a_1 f-b_1 g+e_1) \cq u_{2,t} = \p(a_2 f-b_2g+e_2) \;,
$$
where $e_m$, $e_1$ and $e_2$ are noise terms, $f$ and $g$ are skewed non-negative random variables, and the other variables are constants. As before $\p$ is the percentile rank transform. The factors $f$ and $g$ induce upper and lower tail dependence between individual and market returns respectively. Assume $f$ and $g$ are exponential with mean one. In addition $a_1=b_1=2$ and $a_2=b_2=2$. Hence $r_2$ has stronger tail dependence between $r_m$. 
\newline

Lastly assume $r_m$, $r_1$ and $r_2$ follow $t_2$ distributions in stationarity. The $t_2$ distribution captures skewed returns captured to the Gaussian.
\newline

The model does not seek to specify the relationship between $r_m$, $r_1$ and $r_2$. In practice the market is formed by a large number of stocks. This model focuses on two stocks in the basket, whilst ignoring others.
\newline

The below figures illustrate the assumed model. Note that the model captures stylised features of stock return.

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \resizebox{60mm}{!}{\includegraphics{copula1.eps}}
      \resizebox{60mm}{!}{\includegraphics{copula2.eps}} \\
    \end{tabular}
    \caption{Left and right panels  plot 10,000 simulated points of $(u_m,u_1)$ and $(u_m,u_2)$ respectively based on the assumed factor copula. Note the tail dependence.}
    \label{finterpretation}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \begin{tabular}{c}
      {\includegraphics[scale=0.35]{marketreturn.eps}} \\
       {\includegraphics[scale=0.35]{return1.eps}} \\
        {\includegraphics[scale=0.35]{return2.eps}} \\
     \end{tabular}
    \caption{Daily returns $r_{m,t}$ (top panel), $r_{1,t}$ (middle panel) and $r_{2,t}$ (bottom panel). Note the simultaneous volatility clustering in each return.}
    \label{finterpretation}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \begin{tabular}{c}
      {\includegraphics[scale=0.35]{rollingvolatility.eps}} \\
       {\includegraphics[scale=0.35]{rollingcorrelation.eps}} \\
            \end{tabular}
    \caption{Top panel shows 30-day rolling volatility of $r_{m,t}$, $r_{1,t}$ and $r_{2,t}$. Bottom panel shows 30-day rolling rank correlation for $(r_{m,t},r_{1,t})$ and $(r_{m,t},r_{2,t})$. Note the strong correlations occurring simultaneously with volatility clusters. In addition stock 2 has stronger resemblance with the market.}
    \label{finterpretation}
  \end{center}
\end{figure}

\end{document}

### 2015-05-29 srisk3.tex
pdj changes

@@
 Since both $\Es(p_{it})$ and $\E(p_{it})$ lie between 0 and 1 it follows both $\mu_{it}$ and $s_{it}$ lie between 0 and 1 and  are loosely interpreted as probabilities.
+Further note
+$$
+\E(p_{it}|\nu_{it}\le \ell_{it}) \approx \ell_{it}-\E(\nu_{it}|\nu_{it}\le \ell_{it})\ .
+$$
+(Weihao, do you think it is worthwhile to decompose the $s_{it}$ analogously in terms of a probability time a tail event?)
 
@@
 \be{zscore2}
-\E_s(\phi)  = \mu_{it} + \beta_{it}\sigma_\phi\cq \E(p_{it}|\phi) \approx \mu_{it} + \beta_{it}\frac{\phi-1}{\sigma_\phi}\ .
+\Es(p_{it})  = \mu_{it} + \beta_{it}\sigma_\phi\cq \E(p_{it}|\phi) \approx \mu_{it} + \beta_{it}\frac{\phi-1}{\sigma_\phi}\ .
 \ee

### 2015-05-29 srisk3.tex
pdj changes

@@
 \E(p_{it}|\nu_{it}\le \ell_{it}) \approx \ell_{it}-\E(\nu_{it}|\nu_{it}\le \ell_{it})\ .
+$$
+and hence background risk decomposes into
+$$
+\mu_{it} \approx q_{it}\ell_{it} - q_{it}\E(\nu_{it}|\nu_{it}\le \ell_{it})
 $$

### 2015-05-31 srisk3.tex
wc/pdj changes

--- 2015-05-29 srisk3.tex
@@
 $$
-s_{it} \equiv \cov\{\E(p_{it}|\phi),\phi\}\ , 
+s_{it} \equiv \cov\{\E(p_{it}|\phi),\phi\}\cq q_{it} = \P(\nu_{it}\le \ell_it)\ , 
 $$
@@
 $$
-\E(p_{it}|\nu_{it}\le \ell_{it}) \approx \ell_{it}-\E(\nu_{it}|\nu_{it}\le \ell_{it})\ .
+q_{it}\E(p_{it}|\nu_{it}\le \ell_{it}) \approx q_{it}\E(\ell_{it}-\nu_{it}|\nu_{it}\le \ell_{it}) = \ .
+$$
+and hence background risk decomposes into
+$$
+\mu_{it} \approx q_{it}\ell_{it} - \E(|\nu_{it}-\ell_{it}|^+)
 $$

### 2015-05-31 srisk4.tex
wc/pdj changes

--- 2015-05-29 srisk3.tex
@@
 \bibliographystyle{chicago}
+
+\makeatletter
+\def\ps@pprintTitle{%
+\let\@oddhead\@empty
+\let\@evenhead\@empty
+\def\@oddfoot{}%
+\let\@evenfoot\@oddfoot}
+\makeatother
 
@@
 % Title of paper
-\title{Measuring background risk and systemic risk in finance}
+\title{Measuring background and systemic risks in finance}
 % List of authors, with corresponding author marked by asterisk
@@
 
-Recent literature in the area of quantitative systemic stress measurement includes 
+Recent literature in the area of quantitative systemic risk or stress measurement includes
 \cite{adrian2011covar},
@@
  \cite{brownlees2010volatility} and \cite{brownlees2015}.
-The proposed research aims to extend and apply these techniques particularly in relation to the entities regulated by APRA.
-Thus our  broad aim is to develop, implement and bring to bear recent developments in stress testing  on the aims of APRA and the CIFR targeted research areas.
+This study aims to extend and apply these techniques particularly in relation to the entities regulated by the Australian Prudential Regulation Authority (APRA).
+Thus our  broad aim is to develop, implement and bring to bear recent developments in systemic risk measurement and stress testing  on the aims of APRA and the CIFR targeted research areas.
 (This needs much more commentary).
@@
 (Should these be plotted?).
+
+Remaining sections are structured as follows.
+\sref{capshort} and \sref{futshort} define current and future  capital shortfall similarly as \cite{brownlees2015} under a simplistic Basel II regulatory framework.
+The definition of systemic risk used by \cite{brownlees2015} is discussed in \sref{srisk}, and is refined, extended and illustrated \sref{improve} to \sref{estimate}.
+\sref{marketstress} discusses specific stress examples which extend beyond \cite{brownlees2015}.
+Applications to Australian bank data are discussed in \sref{simulate} and \sref{simulate1}.
+\sref{aggregate} and \sref{aggregate1} discuss how stresses are combined across firms with and without allowance for merging or diversification.
+Generalised stressed are outlined in \sref{genstress}.
+\sref{riskmethod} offers an alternative modeling approach, based on assets.
+\sref{comparison} summarises differences between proposed stress measurement in this paper with that of
+\cite{brownlees2015}. \sref{conclude} concludes.
 
@@
 
-\section{Capital shortfall and leverage}
+\section{Capital shortfall and leverage}\label{capshort}
 
-If $d_{it}$ and $w_{it}$ are the debt and equity of a firm $i$ at time $t$ and $\kappa$ is the capital requirement,  then the capital shortfall at time $t$ is 
+If $d_{it}$ and $w_{it}$ are the debt and equity of firm $i$ at time $t$ respectively and $\kappa$ is the prudential requirement,  then  capital shortfall at time $t$ is
 \be{shortfall}
@@
 $$
-The quantity $\ell_{it}$ is called   adjusted log--leverage and $\ell_{it}>0$ implies capital shortfall \eref{shortfall} is positive.
-Basel II assumes\footnote{See for example \cite{brownlees2015}.   The value of $\kappa$ can and is varied to test for sensitivity etc.} 
- $\kappa=0.08$ implying $\logit(\kappa)=-2.44$ and  $\ell_{it}$ is the actual log--leverage minus 2.44.   
-As the actual  log leverage of a firm  increases to 2.44, the firm approaches a Basel breach.
+The quantity $\ell_{it}$ is the adjusted log--leverage of firm $i$ at time $t$ and $\ell_{it}>0$ implies capital shortfall in \eref{shortfall} is positive.
+The parameter $\kappa$ is the proportion of assets $d_{it}+w_{it}$ excluded from capital calculations, and higher $\kappa$ leads to higher capital shortfall.
+Assume\footnote{See for example \cite{brownlees2015}.
+The value of $\kappa$ can and is varied to test for sensitivity etc.} $\kappa=0.08$ under Basel II implying $\logit(\kappa)=-2.44$ and  $\ell_{it}$ is the actual log--leverage minus 2.44.
+The firm is in a Basel breach if actual  log leverage is above 2.44, otherwise it is Basel compliant.
 
-\fref{Bloglev} displays Basel log--leverages for the four major and four minor Australian banks listed in \tref{banks} on the first trading day of each month from January 2003  through to December 2014.
-Note most banks are Basel compliant up to about 2008.
+\fref{Bloglev} displays Basel log--leverages ($\ell_{it}$ for $\kappa=0.08$) for the four major and four minor Australian banks listed in \tref{banks} on the first trading day of each month from January 2003  through to December 2014.
+Note most banks are Basel compliant up to about 2008, entering into Basel breaches from 2009 as a result of the global financial crisis.
+Prolonged Basel breaches are experienced for particular banks, notably NAB.
 
@@
 \includegraphics{figures/bloglev.pdf}
-\caption{Adjusted log--leverages for four major (left panel) and four minor (right panel) Australian banks from the beginning of 2003 through to end of 2014.
+\caption{Adjusted or Basel log--leverages for four major (left panel) and four minor (right panel) Australian banks from the beginning of 2003 through to end of 2014.
 All banks contravene the threshold (corresponding to the zero horizontal) around the start of 2009.}
@@
 
-\section{Future capital shortfall}
+\section{Future capital shortfall}\label{futshort}
 
-Financial institutions and regulators are concerned with future Basel compliance and in assessing  the likelihood of a  future Basel breach.
+Financial institutions and regulators are concerned with future Basel compliance and the likelihood of a  future Basel breach.
 Future compliance depends on the future return on equity.
 Consider  firm $i$ at time  $t+h$ where $h>0$.
-Then\footnote{In the further development $\e^\nu$ is the continuously compounded return and $\nu$  the  rate of return or log return.}
+Then\footnote{In the further development $\e^\nu$ is the continuously compounded return (including principal) and $\nu$  the  rate of return or log return.}
 $$
@@
 $$
-where it is assumed $d_{i,t+h}=d_{it}$.  Hence $\nu_{it}$ is the log return on equity over $(t,t+h)$.  The future return is unknown at time $t$ but its distribution may be  well understood.
+where it is assumed $d_{i,t+h}=d_{it}$.
+Here $\nu_{it}$ is the log return on equity over $(t,t+h)$ and decreases adjusted log--leverage by the same amount.
+The future return is unknown at time $t$ but its probability distribution is assumed to be well understood.
 
-The capital  shortfall  at time $t+h$ is,
+The capital  shortfall  at time $t+h$, ignoring the surplus portion, is,
 \be{bs}
-\kappa d_{it} |1-\e^{\nu_{it}-\ell_{it}}|^+\cq  |x|^+\equiv \max(0,x)\ . 
+\kappa d_{it} \left|1-\e^{-\ell_{i,t+h}}\right|^+=\kappa d_{it} \left|1-\e^{\nu_{it}-\ell_{it}}\right|^+
+\cq  |x|^+\equiv \max(0,x)\ .
 \ee
-Thus shortfall \eref{bs} is a put on the return $\e^{\nu_{it}-\ell_{it}}$  with strike 1.  
+Thus shortfall \eref{bs} is a $\kappa d_{it}$ multiplied by a put on the return $\e^{\nu_{it}-\ell_{it}}$  with strike 1.
 The Basel  limit is reached at $t+h$ if $\nu_{it}=\ell_{it}$ and  breached  if
 $\nu_{it}< \ell_{it}$.
-A breach is  unlikely if $\ell_{it}$ is low i.e. either the log--leverage is low, or the  constant $\kappa$ in the calculation of $\ell_{it}$ is low.
+A breach is  unlikely if $\ell_{it}$ is low i.e.
+either the log--leverage or prudential requirement $\kappa$ is low.
+This paper models future capital shortfall using log return on equity $\nu_{it}$ as it is typically available publicly.
+An alternative approach models future asset values $d_{i,t+h}+w_{i,t+h}$ in turn implying equity returns, and is briefly discussed in \sref{riskmethod}.
+Results in this paper generally hold for any modeling approach.
 
@@
 This amount may be cold comfort to regulators as it leaves the firm in a precarious position, teetering on the edge of non--compliance.
+Firms generally maintain a positive capital surplus to avoid breaches when unexpected shocks occur.
 
@@
 
-To illustrate the setup, \fref{simulation}   displays two snapshot outputs from projections generated as described  in \aref{garchdcc}:  6000  simulated one month ahead projected returns for  CBA and the market, on  two dates: the first trading day in January 2009 and the first trading day in December 2014.
+To illustrate the setup in \eref{bs}, \fref{simulation}   displays two snapshot outputs from projections generated as described  in \aref{garchdcc}:  6000  simulated one month ahead projected returns for  CBA and the market, on  two dates: the first trading day in January 2009 and the first trading day in December 2014.
 Both panels use the same horizontal and vertical scales.
@@
 The scatter of dots are the forward simulations.
-Note there is no lookahead bias as the model at each time point is based on the available data to that point in time.
-The red horizontal line in each panel indicates the projected Basel limit:  any firm return less than the limit would constitute a Basel breach.
+Note there is no hindsight bias as the model at each time point is based on the available data to that point in time.
+The red horizontal line in each panel indicates the Basel limit:  any firm return less than the limit would constitute a Basel breach.
 In the left panel there is little confidence that the Basel limit will be reached since it requires a return on equity approaching 20\% -- with confidence less than xxx the Basel standard will be breached.
@@
  The black dots in each panel indicate the actual outcome after one month.
-In the left panel the outcome is a decline in both  the market and stock price.
+In the left panel the outcome is a decline in both  the market and CBA stock price.
 In the right panel the returns are xxx and xxx.
-Thus at the beginning of January  2009 the CBA bank was projected to be far from compliance in one month's time  while in December 2015 the one month projection is of complete compliance.
+Thus at the beginning of January  2009 CBA was projected to be far from compliance in a month while in December 2014 the one month projection is of complete compliance.
 
- The two panels  display very different volatility and slopes.  These snapshots are used to compute systemic stress.
+ The two panels  display very different volatility and slopes.
+In January 2009 both CBA and market return distributions are highly volatile and correlated.
+The correlation remains strong in December 2014 but with less return volatility.
+These snapshots are used to compute background and systemic stresses shown in subsequent sections.
 
@@
 Note scales in both panels are the same, the relatively large volatility in the left panel, and the left skew in the  marginal distributions.
-Yellow and black dot in each panel indicate origin (0,0) and  realized forward  rate of return, respectively.
+Yellow and black dots in each panel indicate origin (0,0) and  actual forward  rate of return, respectively.
 Red lines indicate Basel limit -- any firm return below the limit indicates a Basel breach given the bank leverage on the applicable date.}
@@
 
- \cite{brownlees2015} define  systemic risk (SRISK) for a group of firms  at time $t$ as
+ \cite{brownlees2015} defines  systemic risk (SRISK) for a group of firms  at time $t$ as
 \be{esrisk}
-\mathrm{SRISK}_t\equiv\kappa\sum_i d_{it}|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+ \ ,
+\mathrm{SRISK}_t\equiv\kappa\sum_i d_{it}\left|1-\Es(\e^{\nu_{it}-\ell_{it}})\right|^+ \ ,
 \ee
-where  $\Es$ denotes  conditional expectation given a major general market downturn.  The proportionate contribution of firm $i$  to \eref{esrisk} is defined as the systemic risk in firm $i$  
+where  $\Es$ denotes expectation given a major general market downturn.
+Hence the expected capital shortfall (allowing surplus offset) is computed from \eref{shortfall} assuming a market downturn and added across all firms.
+Firms having a expected capital surplus are ignored.
+The systemic risk of firm $i$ at time $t$ is its proportionate contribution to \eref{esrisk}:
  \be{sriskperc}
- \mathrm{SRISK}_{it}\equiv \frac{\pi_{it}|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+}{\Ex_d\{|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+\}}\cq \pi_{it}\equiv \frac{d_{it}}{d_t}\cq d_t\equiv \sum_i d_{it}\ , 
+ \mathrm{SRISK}_{it}\equiv \pi_{it}\frac{|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+}{\Ex_d\{|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+\}}\cq \pi_{it}\equiv \frac{d_{it}}{d_t}\cq d_t\equiv \sum_i d_{it}\ ,
  \ee
-where $\Ex_d$ denotes  debt weighted averaging at time $t$,  weighted averaging across firms $i$  using weights $\pi_{it}$.
-Large $\mathrm{SRISK}_{it}$ indicates firm $i$ is systemically important: either because it holds a high proportion of the total debt, or it is unusually likely to breach the Basel capital requirement.
+where $\Ex_d$ denotes weighted averaging across firms $i$ using weights $\pi_{it}$.
+Large $\mathrm{SRISK}_{it}$ indicates firm $i$ is systemically important: it holds a high proportion of the total debt, and it is likely to heavily breach the Basel capital requirement compared to remaining other firms.
 Expression \eref{sriskperc} depends on $\kappa$ through each of the $\ell_{it}$.
 
-Given a general market downturn, the values of the puts $|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+$  in \eref{sriskperc} are known at time $t$:  there is no uncertainty except for possible  uncertainty in estimating the conditional  expected value.
+Given a general market downturn, put values $|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+$  in \eref{sriskperc} are known at time $t$:  there is no uncertainty except for possible  uncertainty in estimating the conditional  expected value.
 
-Since
+Using the Jensen's inequality,
 $$
-|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+ \le\Es(|1-\e^{\nu_{it}-\ell_{it}}|^+)\ ,
+\left|1-\Es(\e^{\nu_{it}-\ell_{it}})\right|^+ \le\Es\left(\left|1-\e^{\nu_{it}-\ell_{it}}\right|^+\right)\ ,
 $$
@@
 $$
-\Es(\e^{\nu_{it}})\le\e^{\ell_{it}}\ .
+\Es(\e^{\nu_{it}})\ge\e^{\ell_{it}}\ .
 $$
 This inequality typically holds even if the expectation conditions on an extreme market downturn.
+The above two inequalities suggest SRISK is not risk sensitive and leads to refinements discussed in the next section.
 
-\section{Improved systemic risk measurement}
+\section{Improved systemic risk measurement}\label{improve}
 
@@
 For shortness we prefer the adjective Basel.
-Note ``risk" here is not a probability but rather a measure of expected capital shortfall.} the  Basel put and  Basel risk of firm $i$ at time $t$ as
+Note ``risk" here is not a probability but rather a measure of expected capital shortfall.} the  Basel put payoff and default probability of firm $i$ at time $t$ respectively as
 \be{put}
-p_{it}\equiv |1-\e^{\nu_{it}-\ell_{it}}|^+\cq q_{it}\equiv \p(\nu_{it}\le \ell_{it})=\frac{\E(p_{it})}{\E(p_{it}|\nu_{it}\le \ell_{it})}\ ,
+p_{it}\equiv \left|1-\e^{\nu_{it}-\ell_{it}}\right|^+\cq q_{it}\equiv \p(\nu_{it}\le \ell_{it})=\frac{\E(p_{it})}{\E(p_{it}|\nu_{it}\le \ell_{it})}\ ,
 \ee
-respectively, where $\E$ denotes unconditional expectation.  Note $0\le p_{it}\le 1$ with $p_{it}\rightarrow 0$ or 1 as $\nu_{it}\rightarrow\pm\infty$.
-Further the Basel risk  $q_{it}$ increases as the distribution of $\nu_{it}$ moves to the left.
-Both $\E(p_{it})$ and $q_{it}$ are thought of as probabilities of default with the former reflecting the whole distribution of $\nu_{it}$ given there is a default $\nu_{it}\le\ell_{it}$.
+where $\E$ denotes expectation without any imposed stress.  Note $0\le p_{it}\le 1$ with $p_{it}\rightarrow 0$ or 1 as $\nu_{it}\rightarrow\pm\infty$.
+Further $q_{it}$ increases as the distribution of $\nu_{it}$ moves to the left.
+Both $\E(p_{it})$ and $q_{it}$ measure default risk between 0 and 1, with the former reflecting the conditional distribution of $\nu_{it}$ below $\ell_{it}$ and the latter only concerned with the probability mass in the same area.
 
-The total Basel put value  for firm  $i$ is   
+The monetary Basel put value  for firm  $i$ is the total expected payout
 $$
@@
 $$
-the cost of insuring firm $i$ does not breach the Basel standard.
+the expected cost of insuring firm $i$ against a Basel breach.
+The expression on the right is the product of four terms: the capital requirement $\kappa$, firm debt $d_{it}$, probability of Basel default $q_{it}$, and the expected payout if a default occurs (against a standardised exercise price of 1).
 In practice it may be appropriate to discount $p_{it}$ in \eref{put} by the interest rate over the period $(t,t+h)$ and value the put with risk neutral rather than normal expectation.
@@
 Market participants can value the put in  the same way as any other put and use the contract to diversify risk.
-Firms can buy puts in the market to hedge Basel default risk.
+Firms can buy puts in the market to hedge their Basel default risk, or contribute an amount equal to the put value into a bailout pool.
 
-However regulators will value the puts $p_{it}$ using a stressed, rather than risk neutral, expectation.
-Stressed expectations correspond closely to conditional expectation given a system wide financial shock.
-Regulators are concerned with the possibility of Basel breaches if such shocks occur and  have an  interest in monitoring stressed expectations.
+Regulators are inclined to value the puts $p_{it}$ using a stressed, rather than risk neutral, expectation.
+Stressed expectations correspond closely to conditional expectation given a system wide shock.
+Regulators are concerned with the possibility and extent of Basel breaches if such shocks occur and  have an  interest in monitoring stressed expectations across firms and time.
 In the extreme regulators can charge firms all or a  proportion of their stressed put values if there are implicit government bailout guarantees.
@@
 
-In the above development $\E$  is  unstressed expectation:  that is expectation that does not assume a stressful scenario.   A stressed expectation, denoted $\Es$, is a
-linear combination of  expectations, each assuming some level of stress
+In the above development $\E$  is  unstressed expectation and does not assume a stressful scenario.   A stressed expectation, denoted $\Es$, is a
+linear combination of a range of conditional expectations each assuming some level of stress:
 \be{formula}
@@
 \ee
-Here $\phi\ge 0$ with $\E(\phi)=1$ is a stress factor or ``stressor,"  defining events impacting $p_{it}$  and serving as a basis for stress testing.
-Thus stress $\phi$ changes the expected value $\E(p_{it})$ by the covariance between the conditional expectation $\E(p_{it}|\phi)$  and the stressor $\phi$.
+Here $\phi\ge 0$ with $\E(\phi)=1$ is a random stress factor or ``stressor,"  with different values re-weighting, and corresponding to, scenarios impacting $p_{it}$.
+Thus stress $\phi$ increases the expected value $\E(p_{it})$ by the covariance between the conditional expectation $\E(p_{it}|\phi)$  and the stressor $\phi$.
+A larger covariance results if higher values of $\phi$, corresponding to increasingly stressed scenarios, lead to larger put values.
+The covariance is zero if $p_{it}$ does not vary with the different scenarios indicated by $\phi$, or under the trivial case $\phi=1$ where scenarios are not re-weighted.
+The impact of $\phi$ is formalised in \eref{post} below.
+Examples of $\phi$ implying various stress calculations are shown in subsequent sections.
+Weighted expectations in the form of \eref{formula} are discussed in \cite{choo2010determining} and \cite{furman2008weighted1}.
 
-The conditioning variable $\phi$  downplays or highlight different scenarios.
-The conditioning events are scenarios of interest and  probabilistic weighting is according to the level of interest.
-The first equality in \eref{formula}  from the definition of conditional probability \citep{whittle2000probability}.
-The second equality follows from
+The first equality in \eref{formula} follows from the definition of conditional probability \citep{whittle2000probability}.  The second equality follows from
 $$
@@
 $$
-The covariance is zero whenever  $p_{it}$ is independent of $\phi$ which occurs if $\phi=1$.
 
-The stressed expectation \eref{formula}  is the mean of $p_{it}$  using the  density
+The stressed expectation \eref{formula}  is the mean of $p_{it}$  using a stressed density
 \be{post}
-\int \phi f(p_{it},\phi)\de \phi= \E(\phi|p_{it})f(p_{it})\cq \int \phi f(p_{it},\phi)\de \phi\de p_{it} = \E(\phi) = 1\ 
+\int \phi f(p_{it},\phi)\de \phi= \E(\phi|p_{it})f(p_{it})\cq \int\int \phi f(p_{it},\phi)\de \phi\de p_{it} = \E(\phi) = 1\
 \  ,
 \ee
-where $f$ denotes density.  
-Any outcome $p_{it}$ such that $\E(\phi|p_{it})$ is large  is amplified and vice versa.
+where $f$ denotes the density of the quantity in parentheses.
+Hence the likelihood of any outcome $p_{it}$ such that $\E(\phi|p_{it})$ is large is amplified and vice versa.
 To a Bayesian the density in the left  expression of $\eref{post}$ is a posterior density given a prior $f(p_{it})$ and ``likelihood" $\E(\phi|p_{it})$: more importance is given to outcomes   $p_{it}$  where $\phi$ is expected to be large.
@@
 called  the background stress  and systemic stress, respectively, in firm $i$ at time $t$.
-Since both $\Es(p_{it})$ and $\E(p_{it})$ lie between 0 and 1 it follows both $\mu_{it}$ and $s_{it}$ lie between 0 and 1 and  are loosely interpreted as probabilities.
-Further note
+Both $\mu_{it}$ and $s_{it}$ are computed from the current adjusted log--leverage and the forward return distribution at time $t$.
+In addition $0\le \mu_{it},\mu_{it}+s_{it}\le 1$ and $s_{it}\ge 0$ typically holds unless firm $i$ benefits from a stress in the system.
+Applying a Taylor series expansion of the exponential function on $p_{it}$ yields
 $$
-\E(p_{it}|\nu_{it}\le \ell_{it}) \approx \ell_{it}-\E(\nu_{it}|\nu_{it}\le \ell_{it})\ .
+\E(p_{it}|\nu_{it}\le \ell_{it}) \approx \ell_{it}-\E(\nu_{it}|\nu_{it}\le \ell_{it})\ ,
 $$
-(Weihao, do you think it is worthwhile to decompose the $s_{it}$ analogously in terms of a probability time a tail event?)
+and hence background stress decomposes into
+$$
+\mu_{it} \approx q_{it} \left\{\ell_{it} - \E(\nu_{it}|\nu_{it}\le \ell_{it})\right\} \ ,
+$$
+which is increasing in the Basel default probability $q_{it}$, adjusted log--leverage $\ell_{it}$ and the left skewness of $\nu_{it}$ as measured by the lower tail conditional expectation.
+If $\ell_{it}=0$  and then firm $i$ is at Basel default at time $t+h$ if  $\nu_{it}<0$ with probability $q_{it}\approx 1/2$.
+As  $\ell_{it}$ increases,  one month ahead Basel default becomes more certain since $\nu_{it}\le \ell_{it}$ becomes more certain and $q_{it}$ increases to 1.
+Background stress is unrelated to the stress factor $\phi$ and based on the unstressed distribution of the forward return $\nu_{it}$: the current view of the future progression of returns including their mean and volatility.
 
-The  term $\mu_{it}$  is called the background stress in firm $i$ and  reflects the log--leverage and the return volatility of firm $i$ at time $t$.
-Background stress is unrelated to the stress factor $\phi$ and based on the unstressed distribution of the forward return $\nu_{it}$ and depends on the current view of the likely future progression of returns including their mean and volatility.
-(Have to fill out discussion with how $mu_{it}$ measures the general uncertainty building up in the system with all  uncertainty  due to monitoring the system up to time $t$.)  Background stress is unrelated to the stress factor $\phi$.
+Similarly decompose systemic stress
+$$
+s_{it} = q_{\phi it}\E_\phi(p_{it}|\nu_{it}\le \ell_{it})-q_{it}\E(p_{it}|\nu_{it} \le \ell_{it})
+$$
+where $q_{\phi it}$ is the default probability implied from the stressed density in \eref{post}.
+The stress typically increases both the default probability  $q_{\phi it}$ and the conditional expected default $\E_\phi(p_{it}|\nu_{it}\le \ell_{it})$ relative to the unstressed quantities $q_{it}$ and $\E(p_{it}|\nu_{it} \le \ell_{it})$.
+Greater sensitivity of firm $i$ to market wide stresses leads to higher systemic stress $s_{it}$.
+
+Monitoring $\mu_{it}$ across the market provides a leading indication of the level of background stress and anticipates buildups such as shortly before the 2008 global financial crisis.
+The aggregation of put values and stresses across the market is discussed and illustrated below.
+An increase in $\mu_{it}$ indicates either higher probabilities of defaults or larger capital shortfalls if defaults occur.
+Introducing systemic stress $s_{it}$ increases stress-sensitivity in two ways.
+Firstly adverse scenarios are emphasized which would otherwise be less obvious in $\mu_{it}$.
+Secondly, as $\phi$ is a market based stressor, system wide defaults and shortfalls resulting from market dependencies are emphasized and revealed.
+
+\begin{comment}
 Further
@@
 The probability $q_{it}$ depends on the  mean and volatility of daily returns at time $t$.
-
-(*** unformed idea)   We can similarly decompose   (is this useful? -- Weihao can you look at this?)
-$$
-s_{it} = q_{\phi it}\E_\phi(p_{it}|\nu_{it}\le \ell_{it})-q_{it}\E(p_{it}|\nu_{it} \le \ell_{it})
-$$
-
-Firm $i$ is at Basel default if $\ell_{it}=0$  and then  $q_{it}\approx 1/2$.
-As  $\ell_{it}$ increases from zero,  one month ahead Basel default status  becomes more certain since $\nu_{it}\le \ell_{it}$ becomes more certain and $q_{it}$ increases to 1.
+\end{comment}
 
@@
 
-The second, systemic stress component $s_{it}$ in  \eref{vsstress},  captures the financial impact of a  hypothetical system wide financial shock.
+The second, systemic stress component $s_{it}$ in  \eref{vsstress}  captures the financial impact of a  hypothetical system wide financial shock.
 The stress $\phi$ is systemic as it is expected to affect all firms $i$.
@@
 \be{zscore}
-\beta_{it}\equiv \frac{s_{it}}{\sigma_\phi}
+\beta_{it}\equiv \frac{s_{it}}{\sigma_\phi} = \sigma_{it}\cor(p_{it},\phi)
 \ee
-where  $\sigma_\phi$ is the standard deviation of $\phi$.   Thus $\beta_{it}$ is the systemic stress component in \eref{formula} standardised by $\sigma_\phi$ and
+where $\sigma_{it}$ is the standard deviation of $p_{it}$.
+Thus $\beta_{it}$ is the systemic stress component in \eref{formula} standardised by $\sigma_\phi$ and is composed of the variability in the put payoff and its correlation with the stressor.
+In addition
 \be{zscore2}
@@
 The second interpretation is based on  the right hand side approximation in \eref{zscore2} showing   the change in the  expected Basel put price if  $\sigma_\phi$ units of stress $\phi$ are applied.
-The quantity $(\phi-1)/\sigma_\phi$ is thought of as a ``stress factor."   The stress factor has mean 0 and standard deviation 1 and is scaled by $\beta_{it}$ to yield the actual stress effect on  $p_{it}$.
+The quantity $(\phi-1)/\sigma_\phi$ is thought of as a ``stress factor" and is akin to the $z$--score of a normal random variable.
+The stress factor has mean 0 and standard deviation 1 and is scaled by $\beta_{it}$ to yield the actual stress impact on  $p_{it}$.
 Thus  $\beta_{it}$ is thought of a usual finance type ``beta" with respect to $\phi$.
@@
 
-\section{Estimating background and systemic stress via simulation}
+\section{Estimating background and systemic stress via simulation}\label{estimate}
 
-Stress $\mu_{it}$ and can be determined using simulation.
+The following computes background Stress $\mu_{it}$ and systemic stress $s_{it}$ using simulation.
 Suppose $(\phi^\o,p_{it}^\o)$ are pairs of stress and put values generated from a model: for example $\phi^\o$ may be zero unless there is a market drop below the $\alpha$--percentile in which case it is $1/\alpha$.
@@
 \ee
-where $N$ is the simulation effort.  The approximation is increasingly accurate as $N$ becomes large.   More details are given in ...
+where $N$ is the simulation effort.  The approximation is increasingly accurate as $N$ becomes large.
 
 \section{Stress based on  market return}\label{marketstress}
-The setup is illustrated with  examples generalising and fine--tuning the approach of Engle.
+
+The following formulates stresses as functions of the market return $\nu_{mt}$ from time $t$ to $t+h$. The examples generalise and fine--tune the approach of \cite{brownlees2015}.
 
@@
 
-Suppose the stress event is a market return in the bottom $\alpha$--tail of the  market return distribution.   Then  $\phi(u)=1/\alpha$ for $u< \alpha$ and 0  otherwise and
+Suppose the stress event is defined as a market return $\nu_{mt}$ in the bottom $\alpha$--tail of the distribution.
+Then  $\phi(u)=1/\alpha$ for $u< \alpha$ and 0 otherwise (outcomes where $\nu_{mt}$ is better than the bottom $\alpha$--tail is ignored), and
 $$
-\Es(p_{it}) = \frac{1}{\alpha}\int_0^\alpha\E(p_{it}|u)\de u = \E(p_{it}|\nu_{mt}<\tau_{t}) \ .
+\Es(p_{it}) = \frac{1}{\alpha}\int_0^\alpha\E(p_{it}|u_{mt}=u)\de u = \E(p_{it}|u_{mt}<\alpha) = \E(p_{it}|\nu_{mt}<\tau_{t}) \ ,
 $$
-where $\tau_t$ cuts out $\alpha$ probability in the lower tail of the $\nu_{mt}$ distribution.   Further
+where $u_{mt}$ is the percentile rank of $\nu_{mt}$ and $\tau_t$ cuts out $\alpha$ probability in the lower tail of the $\nu_{mt}$ distribution: $\p(\nu_{mt}<\tau_t)=\alpha$.
+In addition background and systemic stresses are calculated from
 $$
-\mu_{it}\approx \frac{1}{N} \sum_\o p_{it}^\o \cq s_{it}   \approx  \frac{1}{N/\alpha} \sum_{u^\o_{mt}<1/\alpha}  p_{it}^\o\ .
+\mu_{it}\approx \frac{1}{N} \sum_\o p_{it}^\o \cq  \mu_{it}+s_{it}   \approx  \frac{1}{N/\alpha} \sum_{u^\o_{mt}<\alpha}  p_{it}^\o\ .
 $$
-In the right hand sides $\o=1,\ldots,N$ denote $N$ simulations.
-The approximations decrease with the simulation effort $N$.
-The effective simulation effort is $N/\alpha$ and hence $\alpha$ small requires a  large effort.
+The approximations decrease with the simulation effort $N$.   The effective simulation effort for $\mu_{it}+s_{it}$ or $s_{it}$ is $N/\alpha$ and hence small $\alpha$ small requires a large effort.
 
-A fixed $\alpha$ cutoff  implies the actual threshold depends on the distribution and hence  on volatility and  time.
-The actual threshold drop in the market $\tau_t=F_{mt}^-(\alpha)$, where $F_{mt}^-$ is the inverse distribution function of $\nu_{mt}$.
-The volatility associated with the latter distribution is approximately $\sqrt{h}\sigma_{mt}$ where $\sigma_{mt}$ is current market volatility.
+The threshold $\tau_t$ in the stress calculations is $F_{mt}^-(\alpha)$ where $F_{mt}^-$ is the inverse distribution function of $\nu_{mt}$.
+The threshold varies across time depending on market volatility, approximately $\sqrt{h}\sigma_{mt}$ where $\sigma_{mt}$ is current market volatility.
 Regulators and practitioners  are well versed in working with VaR type calculations and hence a varying VaR type cutoff combining market volatility and stress is closely aligned to current practice.
+In comparison \cite{brownlees2015} uses fixed threshold which may be over or under extreme depending on prevailing market volatility.
 
 \subsection{Expected worst market return in $n$ identical scenarios}
+
 If $\phi(u)=n(1-u)^{n-1}$ then $\phi(u)\de u = \de\{1-(1-u)^n\}$ and
 $$
-\Es(p_{it}) \equiv \E\{\phi\E(p_{it}|\phi)\} = \int_0^1\E(p_{it}|u)\de\{1-(1-u)^n\}\ .
+\Es(p_{it}) \equiv \E\{\phi\E(p_{it}|\phi)\} = \int_0^1\E(p_{it}|u_{mt}=u)\de\{1-(1-u)^n\}\ .
 $$
@@
 
-The above two situations can be combined.   Suppose  $\phi(u)=c(0.05-u)^{19}$ for $u\le 0.05$ and 0 otherwise and where $c$ is such that $\phi(u)$ integrates to 1.  Then (this needs to be checked)
+The above two situations can be combined.   Suppose  $\phi(u)=c(\alpha-u)^{n-1}$ for $u\le \alpha$ and 0 otherwise and where $c$ is such that $\phi(u)$ integrates to 1. Then
 $$
-\E(p_{it}) \approx \frac{1}{N/c}\sum_{u^\o_{mt}<1/20}  \left(u^\o_{mt}-\frac{1}{20}\right)^{20}p_{it}^\o\ .
+\mu_{it}+s_{it} \approx \frac{1}{N/c}\sum_{u^\o_{mt}<\alpha}  \left(\alpha-u^\o_{mt}\right)^{n-1}p_{it}^\o\ .
 $$
- Similar to the first example, the stressed sample picks up the bottom 5\% of market returns.
-The bottom 5\% of market returns is further stressed by  progressively downweighing returns as the percentile approaches 1/20.
+Similar to the first example, the stressed sample picks up the bottom $\alpha$ of market returns.
+The bottom $\alpha$ of market returns is further stressed by  progressively overweighing returns as the percentile approaches 0.
 Large simulation effort $N$ is required for a reasonable approximation since $N/c$ is the effective simulation size and $c$ is small.
 
-\section{Simulating future capital shortfall and market return}
+\section{Simulating future capital shortfall and market return}\label{simulation}
 
-(maybe this should be merged with material elswhere).
-
-The estimation of systemic beta's requires  projections of future capital shortfalls and future stressors.
-As in \cite{brownlees2015} in this article projections are constructed  using time series models modelling the forward rates of return $\nu_{it}$ for firms $i$ and $\nu_{mt}$ for the market.
+The estimation of background stresses and systemic stresses and beta's requires projections of future capital shortfalls.
+As in \cite{brownlees2015}, projections in this paper are constructed  using time series models of forward rates of return $\nu_{it}$ for firm $i$ and $\nu_{mt}$ for the market.
 The market return is used as the stressor with different choices of the stress function $\phi$ modelling different stress scenarios.
 
-The time series models used for projecting are stochastic volatility models based on the GARCH--DCC model of \cite{engle2002dynamic} summarised in \aref{garchdcc}.
+The time series models used are stochastic volatility models based on the GARCH--DCC model of \cite{engle2002dynamic} summarised in \aref{garchdcc}.
+The GARCH-DCC model captures prolonged periods of high volatility and correlation in firm and market returns, typical in financial markets.
 The GARCH--DCC framework is only one possible implementation.
 For example future return scenarios may be constructed in a more ad--hoc manner e.g.
-judiciously chosen scenarios decided on by regulators or policy makers.
+judiciously constructed scenarios by regulators or policymakers.
 The  systemic beta framework can be based on  any  generated  future  scenarios.
 
+An earlier illustration shown in \fref{simulation} is generated from the GARCH--DCC model.
+In the left panel representing one month forward returns from December 2008, low market returns are likely to lead to sharply lower CBA bank returns, as compared to the right panel showing the same as at January 2014.
+This is suggested by the slope of the scatter plots:  the left slope appears steeper than the right.
+This implies higher systemic stress in December 2008.
+In addition CBA and market return volatilities are much higher in the left panel compared to the right, indicating higher background stress in December 2008.
+Also note that with a stressor function $\phi$ defined in terms of market return percentiles, the magnitude of a market downturn at a fixed percentile threshold is more significant in the left panel.
+
+\begin{comment}
 While the above discussion suggests, as obvious after the fact, that in December 2009 the CBA bank was under much stress.
@@
 Stress occurs if the market return is low.
-In the left panel low market outcomes are likely to lead to sharply lower CBA bank returns, as compared to the right panel.
-This is suggested by the slope of the scatter plots:  the left slope appears steeper than the right and hence any stress in the market -- in the sense of a market downturn is expected to lead to a larger drop in the CBA bank return in the left scenario as compared to the right scenario.
-The magnitudes of the two responses depends on the stressor function.
-In essence the stressor function formalises the notion as to what constitutes a ``big" drop.
-If a big drop is the expected worst in 20 similar market scenarios then the stress in the left and right are xxx and xxx, respectively.
+\end{comment}
 
-\section{One month ahead forecast stress in individual financial institutions}
+\section{One month ahead forecast stresses in individual banks}\label{simulate1}
 
-\fref{default} displays, in the top panels, the estimated $q_{it}$ one month ahead default probabilities for each major and minor Australian banks based on the projected one month ahead return distribution.
-The  top left panel shows the first inclinations of default arose with NAB in early 2008 followed one month later by ANZ, and  a further few months later by WBC and CBA.
+\fref{default} displays, in the top panels, the estimated $q_{it}$ one month ahead default probabilities for each major (left) and minor (right) Australian banks based on the projected one month ahead return distribution fitted using the GARCH--DCC model.
+The first inclinations of Basel default arose with NAB in early 2008 followed one month later by ANZ, and  a further few months later by WBC and CBA.
+The probabilities subsided shortly after 2009, however NAB was close to default again in 2011 and this sustained till 2013.
+The volatility in default probabilities is more pronounced for smaller banks.
+Again note the return distributions are constructed from data only available at that time and hence are not affected by hindsight bias.
 
-Systemic stress is an expected  market return equal to the worst outcome in 12 identical months.  (Have to expand on this).
-(Need much more commentary here)
+The middle two panels in \fref{default} show estimated background stress $\mu_{it}$ using the same projected return distributions.
+A similar pattern as default probabilities is observed, and NAB appears to have the highest put value or background stress per dollar of debt.
+Smaller banks are subject to higher stress in general after normalising for debt levels.
+Background stress levels are high across all banks around 2008 during the global financial crisis and less so between 2011 and 2013 (mainly only from NAB).
+
+Bottom panels in \fref{default} show systemic stress $s_{it}$ computed by assuming $\phi(u)=12u^{11}$: the worst market return in 12 identical months.
+Systemic stress for each bank generally exhibits similar patterns as background stress $\mu_{it}$.
+However, importantly, some banks have differing patterns which is an important observation for the regulator since systemic stress indicates sensitivity to market-wide downturns.
+For example ANZ had similar systemic stress as NAB around 2012 but lower background stress.
+Hence although ANZ was not obviously in stress during 2012, it would be if a market downturn occurred.
+Bendigo and BOQ had high background stress levels after 2008, but are overtaken by Macquarie in terms of systemic risk: Macquarie is more likely to suffer in a market downturn whereas Bendigo and BOQ are less likely to be impacted.
 
@@
 
-\section{Average stress}
+\section{Overall market stress}\label{aggregate}
 
-There are two ways of aggregating stress in the financial sector as a whole.  The first is to average, using debt weighted averaging, the put
+There are two ways of aggregating stress in the financial market as a whole.  The first is to apply debt weighted averaging to individual firm stresses, yielding
 \be{nsrisk}
-\overline p_t \equiv \Exd(p_{it}) \cq \Es(\overline p_t)=\Exd\{\Es(p_{it})\} = \Exd(\mu_{it}+s_{it}) \equiv \overline\mu_{t}+\overline s_t
+\overline p_t \equiv \Exd(p_{it}) \cq \Es(\overline p_t)=\Exd\{\Es(p_{it})\} = \Exd(\mu_{it}+s_{it}) \equiv \overline\mu_{t}+\overline s_t \ ,
 \ee
-The put $\overline p_t$ in \eref{nsrisk} pays out zero if all firms meet the Basel requirement with payments increasing with the number of Basel breaches, the sizes of the breaches, and the relative debt sizes of the breaching firms.
-Further $\overline p_t>0$  if and only if one or more firms breach the Basel standard.
+where $\overline\mu_{t}=\Exd(\mu_{it})$ and $\overline s_{t}=\Exd(s_{it})$ are overall background and systemic stresses, respectively.
+The put $\overline p_t$ in \eref{nsrisk} pays out zero if all firms are Basel compliant with payouts increasing with the number and size of Basel breaches.
 The relation in \eref{nsrisk} follow since  $\Es$ and $\Exd$ are linear.
-(Is $\overline q_t$ a useful concept?
-Weihao can you look at this?)
 
-The monetary value  average  stress at time $t$ is the debt averaged  monetary firm stresses
+The monetary value of overall background and systemic stresses at time $t$ are, respectively,
 $$
@@
 $$
-Firm  $i$ contribution to for example systemic stress is   
-$
-\pi_{it}s_{it}/\overline s_t
-$
-which, when adding across firms, adds to 1.  Other contributions are calculated similarly.
+Percentage contributions of firm $i$ to background and systemic stresses are
+$$
+\frac{\pi_{it}\mu_{it}}{\overline \mu_t} \equiv \pi_{it}\frac{\mu_{it}}{\Exd(\mu_{it})}\cq \frac{\pi_{it}s_{it}}{\overline s_t} \equiv \pi_{it} \frac{s_{it}}{\Exd(s_{it})}\ .
+$$
+where $\pi_{it}\equiv d_{it}/d_t$ as before is the proportion of total debt held by firm $i$.
+Firm $i$ contributes to a larger portion of overall stress if it holds a large amount of debt and its returns are subject to high downside risk, particularly in a market downturn (for $s_{it}$).
+Contributions add to 1 across firms.
+A ratio such as $s_{it}/\overline s_t$, without reflecting firm size, compares the stress in firm $i$ to average stress but does not signal the importance of that firm to the system as a whole.
 
-Percentage contributions of firms to background and systemic stress are calculated as
-$$
-\frac{\pi_{it}\mu_{it}}{\overline \mu_t} \equiv \frac{\pi_{it}\mu_{it}}{\Ex_x(\mu_{it})}\cq \frac{\pi_{it}s_{it}}{\overline s_t} \equiv \frac{\pi_{it}s_{it}}{\Ex_x(s_{it})}\ .
-$$
-where $\pi_{it}\equiv d_{it}/d_t$ is the proportion of total debt held by firm $i$.
-A ratio such as $s_{it}/\overline s_t$ compares the stress in firm $i$ to average stress but does not signal the importance of that firm to the system as a whole.
-
-\section{Total sector stress}
+\section{Overall stress after diversification}\label{aggregate1}
 
 The debt weighed average system  put $\overline p_t\equiv\Ex_d(p_{it})$ is an average put and does not permit  diversification -- the  sharing of debt and equity across firms.
-Sharing may not be possible in practice but the concept is useful for assessing the stability of the system as a whole.
-This leads to the second way of aggregating stress in the financial sector as whole.
+Sharing may not be possible in practice but the concept is useful for assessing the resilience of the system as a whole.
+This leads to the second way of aggregating stresses across firms.
 
-Write  $d_t$ and $w_t$ are total debt and equity in the financial sector, respectively:
+Write  $d_t$ and $w_t$ as total debt and equity in the market, respectively:
 $$
@@
 $$
-Then the   adjusted log leverage for the sector is  
+Then the   adjusted log--leverage for the market overall is
 $$
@@
 \ee
-In terms of this notation the system Basel put  and Basel risk are defined similar to \eref{put}
+In terms of this notation the market Basel put  and Basel risk are defined similar to \eref{put}
 $$
-p_t\equiv |1-\e^{\nu_t-\ell_t}|^+\le \overline p_t\cq q_t\equiv \frac{\E(p_t)}{\E(p_{t}|\nu_t<\ell_t)}=\p(\nu_t\le \ell_t) \ .
+p_t\equiv \left|1-\e^{\nu_t-\ell_t}\right|^+\le \overline p_t\cq q_t\equiv \frac{\E(p_t)}{\E(p_{t}|\nu_t<\ell_t)}=\p(\nu_t\le \ell_t) \ .
 $$
@@
 \ee
-termed the sector background  and systemic stress, respectively.
-Further $q_t$ is the probability of  a sector Basel default with the second factor the expected size (on a log scale) of the default if there is a Basel default.
+termed the diversified overall background  and systemic stress, respectively.
+Further $q_t$ is the probability of  a market Basel default with the second factor the expected size of the default if one occurs.
 
-System resilience aims to answer the question whether the system as a whole can absorb shocks.
+System resilience aims to answer the question of whether the system as a whole can absorb shocks.
 The capacity to absorb relies on implicit merging.
@@
 From a regulators perspective, what would happen under a merger of all firms (or perhaps a group of firms) is nevertheless of interest.
-A system as as a whole near Basel non--compliance is more threatening that one where a few firms are near Basel non--compliant but the system itself is well away from non--compliance.
+A system as as a whole near Basel breach is more threatening that one where a few firms are near Basel breach but the system as a whole is strongly Basel compliant.
 
-System compliance  is partially monitored with the system put $p_t=\Exd(p_{it})$ and its stressed expectation $\Es(p_t)$.
-The system put however simply monitors a debt weighted average of puts.
-It gives no guidance as to how much risk can be diversified away.
+System compliance is partially monitored with the system put $\overline p_t=\Exd(p_{it})$ and its stressed expectation $\Es(\overline p_t)$.
+However both quantities are before diversification and gives no indication of system resilience and as to how much risk can be diversified away.
 Basing a put on system wide aggregated debt and equity and comparing the same to $p_t$  gives at least some guidance.
 
+\fref{muqs} compares background and systemic stresses before and after diversification.
+As expected, stresses reduce after diversification.
+The diversification is most apparent for small levels of stresses where they are close to zero.
+The diversification disappears when stresses reach a certain level, with points in bottom panels of \fref{muqs} following the 45$^\circ$ line.
+The extent of resilience or diversification over time can also be measured using the ratios $\mu_t/\overline \mu_t$ and $(\mu_t+s_t/(\overline \mu_t+\overline s_t)\le 1$.
+As diversification or resilience weakens such as during 2008, the ratio increases to 1.
+
+\begin{comment}
 Possible additional issues to be discussed here
@@
 
+\end{comment}
+
  \section{Further generalised stress functions}\label{genstress}
@@
 
-\cite{brownlees2015} define a systemic event as a market based downturn greater than a certain threshold and a systemic event  depends on the chosen threshold.
+\cite{brownlees2015} defines a systemic event as a market based downturn greater than a certain threshold and a systemic event  depends on the chosen threshold.
 This arbitrariness is partially sidestepped by choosing a decreasing function $\phi=\phi(u_{mt})$ on the unit interval and noting
 \be{wave}
-\E\{\phi\E(p_{it}|\phi)\} = -\E\{u\phi'(u)\E(p_{it}|u_{mt}\le u)\}\ .
+\E\{\phi\E(p_{it}|\phi)\} = -\int_0^1 v\phi'(v)\E(p_{it}|u_{mt}\le v) \de v \ .
 \ee
@@
 $$
-\int_0^1 \phi'(u)  \int_0^u \E(\nu_{it}|u_{mt})\de u_{mt}   \de u =\int_0^1\E(\nu_{it}|u_{mt})\int_{u_{mt}}^1  \phi'(u) \de u \de u_{mt}\ ,   
+\int_0^1 \phi'(v)  \int_0^v \E(p_{it}|u_{mt})\de u_{mt}   \de v =\int_0^1\E(p_{it}|u_{mt})\int_{u_{mt}}^1  \phi'(v) \de v \de u_{mt}\ ,
 $$
@@
 $$
-where $\phi_k$ is the weight assigned to scenario $\kappa$.
+where $\phi_k$ is the weight assigned to scenario $k$ and $\pi_k$ here is the original probability of scenario $k$.
 The $\pi_k\phi_k\ge 0$ are  modified  probabilities which weigh different scenarios according to level of interest.
-For example in standard stress testing the $\phi_k$ are chosen such that significant weight is given to scenarios $\kappa$ causing high  firm distress.
+For example in standard stress testing the $\phi_k$ are chosen such that significant weight is given to scenarios causing high  firm distress.
 The ``real world" probabilities $\pi_k$ are  usually ignored by  simply choosing  $\pi_k\phi_k$ to be of  required magnitude.
@@
 
-Stress can be based on a vector of variables $x$ with distribution $F(x)=u$ and marginal densities $f(x_j)$.
-Suppose $c(u)$ is the copula density of $x$ implying the density of $x$ is $c(u)\prod_jf(x_j)$.
-If   $\phi(u)$ is a copula density then $\E\{\phi(u)\}=1$ and
-consider
+Stress can be based on a vector of variables $x$ with marginal distributions $F$ and marginal densities $f$.
+The vector of percentile ranks corresponding to $x$ is $u=F(x)$.
+Suppose $c$ is the copula density of $x$ implying the joint density of $x$ is $c(u)\prod_jf(x_j)$.
+If   $\phi(u)$ is a copula stress density where $\E\{\phi(u)\}=1$ then the stressed expectation of the put is
 \be{copula}
@@
 If $\phi(u)=1$  then $\Es(p_{it})=\E(p_{it})$, the ordinary expectation.
-The density $\phi(u)$ magnifies potentially stressful situation such as where all component of $x$ are highly  tail dependent.
+The density $\phi(u)$ magnifies potentially stressful situation such as where all components of $x$ are distressed (either high or low depending on each component of $x$).
 
 The copula density stressor $\phi(u)$  can be combined with marginal stressors written as functions of $x_j$ or  percentiles $u_j$.
-If the latter then $\phi(u)\prod\phi(u_j)$ is the total stressor, corresponding to a density on the unit hypercube with non--uniform marginals  $\phi(u_j)\ne 1$.
+If the latter then $\phi(u)\prod_j\psi_j(u_j)$ is the total stressor which is applied to $\E(p_{it}|x)$ as above.
 
@@
 Suppose $x$ is a vector $\nu_{mt}$ of  market factors  over the period $(t,t+h)$.
-Simulations of a joint model are  used to  derive  vectors $(p_{it}^\o,\nu_{mt}^\o)$, $ \o=1,\ldots, N$.
+Simulations of a joint model are  used to  compute vectors $(p_{it}^\o,\nu_{mt}^\o)$, $ \o=1,\ldots, N$.
 The $\nu_{mt}^\o$ are  converted to percentiles $u^\o$ and scalars
 $$
-\phi^\o\equiv\phi(u^\o)\prod_j\phi(u_j^\o)\cq \o=1,\ldots, N\ .
+\phi^\o\equiv\phi(u^\o)\prod_j\psi_j(u_j^\o)\cq \o=1,\ldots, N\ ,
 $$
-The stress beta is then estimated as in \eref{simulate}.
+are calculated. The systemic stress and beta are then estimated as in \eref{simulate}.
 
-\section{Risk weighted asset methodology}
+\section{Modelling assets to determine capital shortfall}\label{riskmethod}
 
-The risk weighted asset (RWA) methodology (references ???) for determining capital adequacy is to value  assets  and subtract debt to arrive at capital shortfall.
-The capital shortfall is then, similar to \eref{shortfall},
+An alternative method to determine capital adequacy is to value  assets separately, apply the prudential requirement and subtract debt to arrive at capital shortfall.
+The capital shortfall at time $t+h$ is then, similar to \eref{shortfall},
 \be{csrwa}
-\kappa d_{it} - (1-\kappa)\sum_j \e^{-r_{ijt}}a_{ijt}  = \kappa d_{it} - (1-\kappa)a_{it}\Ex_a(\e^{-r_{ijt}})\cq a_{it}=\sum_j a_{ijt}\ .
+d_{it} - (1-\kappa)\sum_j \e^{\nu_{ijt}}a_{ijt}  = d_{it} - (1-\kappa)a_{it}\Ex_a(\e^{\nu_{ijt}})\cq a_{it}=\sum_j a_{ijt}\ .
 \ee
-Here $a_{ijt}$ is the value of firm $i$'s asset  $j$ at time $t$.
-Further the $r_{ijt}\ge 0$ are risk weights and $\Ex_a$ denotes an asset weighted average using  firm $i$'s asset values at time at time $t$.
-If  $r_{ijt}=0$ in  \eref{csrwa} then  asset $j$ is valued at its present value.
-Higher weights reflect more risky assets and  potential  for asset devaluation.
-The RWA methodology is a standard  approach to capital shortfall calculations.
-
-The RWA calculations can be fit into the present framework.
-If $\nu_{ijt}$ is the forward return on firm $i$ class $j$ asset at time $t$ then     a put on the  projected capital shortage at time $t+h$ is, per unit $\kappa d_{it}$,
+Here $a_{ijt}$ is the value of firm $i$'s asset  $j$ at time $t$ and has forward log--return $\nu_{ijt}$.
+Further  $\Ex_a$ denotes an asset weighted average using  firm $i$'s asset values at time $t$.
+The default put is, per unit $\kappa d_{it}$,
 \be{modput}
-p_{it}\equiv \left|1 - \e^{-\logit\kappa-L_{it}}\Ex_a(\e^{\nu_{ijt}})\right|^+ \cq L_{it}\equiv \ln\frac{d_{it}}{a_{it}} \ .
+p_{it}\equiv \left|k^{-1} - \e^{-\logit\kappa-L_{it}}\Ex_a(\e^{\nu_{ijt}})\right|^+ \cq L_{it}\equiv \ln\frac{d_{it}}{a_{it}} \ .
 \ee
 Thus $\e^{L_{it}}$ is the often used alternative leverage definition: dividing debt by total assets.
-Similar to before $0\le p_{it}\le 1$ is a measure of  stress on firm $i$ at time $t$ with expected stress decomposed as before
+Similar to before $0\le p_{it}\le 1$ is a measure of  stress on firm $i$ at time $t$ with total stressed expectation decomposed as before:
 $$
@@
 
-To calculate asset weights $w_{ijt}$, a sample of $N$ forward returns $\nu_{ijt}^\o$ and stress factors $\phi^\o$ are  simulated using an appropriate model such as the GARCH--DCC model.
+To calculate put values or stresses as before, a sample of $N$ forward returns $\nu_{ijt}^\o$ and stress factors $\phi^\o$ are  simulated using an appropriate model such as the GARCH--DCC model.
 The returns $\nu_{ijt}^\o$ are used to derive $\Ex_a(\e^{\nu_{ijt}^\o})$ and in turn, using \eref{modput},   $p_{it}^\o$ which are multiplied by $\phi^\o$ to arrive at stressed put prices  $\phi^\o p_{it}^\o$.
-As $N\rightarrow\infty$,
+The calculations converge as $N\rightarrow\infty$:
 \be{rwa}
@@
 $$
-\Es(p_{it}) \ne \left|1-\e^{-\logit\kappa-L_{it}}\Es\{\Ex_a(\e^{\nu_{ijt}})\}\right|^+\ ,
+\Es(p_{it}) \ne \left|k^{-1}-\e^{-\logit\kappa-L_{it}}\Es\{\Ex_a(\e^{\nu_{ijt}})\}\right|^+\ .
 $$
-and the stressed average return
+The stressed average return
 $$
@@
 $$
-is cannot be used directly in the calculation of the stress in the firm.
+cannot be used directly in the calculation of firm stress.
 
-Easily disstressed assets $j$  have a return distribution sensitive to stress $\phi$ and under stress, $\e^{\nu_{ijt}}$ is likely to be much less than 1.
-Assets whose return $\e^{\nu_{ijt}}$  tends to be much less than 1 when stress $\phi$ is high,  have high risk and low weight.
-An asset with no volatility, $\nu_{ijt}\equiv 0$, has risk weight 1 since, on average, $\phi^\o$ is 1.
+An easily stressed asset $j$  has a return distribution sensitive to stresses or changes in values of $\phi$.
+Under stress, $\e^{\nu_{ijt}}$ is likely to be much less than 1 thus increasing the capital shortfall.
+This asset increases the stressed expectation of $p_{it}$ particularly when $a_{ijt}$ contributes to large portion of $a_{it}$.
+
+\section{Background and systemic stress  compared to SRISK}\label{comparison}
+
+The methodology developed and employed in this article departs in three respects from the SRISK methodology set out in \cite{brownlees2015}.  This section examines the force of these differences.
+
+\subsection{Put value versus put on expected value}
+
+The SRISK methodology described in \sref{srisk}, in particular \eref{sriskperc}, is based on a put on the expected shortfall:
+\be{prisk}
+ |1-\E_\phi(\e^{\nu_{it}-\ell_{it}})|^+\le \Es(|1-\e^{\nu_{it}-\ell_{it}}|^+) \equiv \mu_{it}+s_{it}\ ,
+\ee
+where stressed expectation $\Es$ in \cite{brownlees2015} is conditional expectation given a major market downturn.
+The   put is evaluated after the expectation $\Es$ and checks, in essence whether in a significant market downturn, the expected $h$ period ahead return $\nu_{it}$ exceeds the adjusted   log--leverage.
+If this holds true there may still be substantial risk of a Basel breach, depending on the volatility of the return.
+Volatility in $\nu_{it}$ is ignored in  $\mathrm{SRISK}_{it}$  other than through the usual adjustment on account of continuous compounding.
+In particular increased volatility due to stress is ignored.
+
+With the proposed $\mu_{it}+s_{it}$ where the stressed expectation is performed on the put payoff as opposed to the other way round, return volatility is taken into consideration as for any other puts in general.
+Other things equal, higher volatility leads to higher put values since breach size is taken into consideration.
+An explicit decomposition is discussed in \sref{improve}.
+In addition the calculation by \cite{brownlees2015} has a probability mass at the zero value whereas the proposed calculation yields a continuous range of values unless a breach is highly unlikely.
+
+\begin{comment}
+Note further we split up $\mu_{it}=q_{it}\E(p_{it}|\nu_{it}>\ell_{it})$.    (Can do analogous split up on $s_{it}$ ????)
+
+(Should we compare $\mu_{it}+s_{it}$ to the left  hand side of $\eref{prisk}$ using graphs???)
+\end{comment}
+
+\subsection{Systemic stress versus background stress}
+
+\cite{brownlees2015} defines systemic risk as the entire left of \eref{prisk}.
+However a stressed expectation may be high simply on account of put prices already being high before stressing, reflecting higher than normal volatility or leverage.
+Hence \cite{brownlees2015} combines both background stress, due to high volatility or leverage, and the imposed system stress.
+However it is important to understand the mix of the two different stresses.
+\fref{sysstress} plots systemic stress versus background stress for the eight Australian banks of \tref{banks}.
+Generally background stress is higher than systemic stress, although the mix differs between banks and the extent of stress.
+For example compared to the smaller Australian banks, bigger banks have a larger proportion of systemic stress relative to background stress.
+In addition Macquarie is more systemically risky amongst the smaller banks.
+
+\begin{comment}
+To gain insight into the relative sizes of these two components, consider the proportion of the stressed put price due to a possible future stress scenario
+$$
+\frac{\Es(p_{it})-\E(p_{it})}{\Es(p_{it})} = \frac{\sigma_\phi\beta_{it}}{\mu_{it}+\sigma_\phi\beta_{it}}  \ .
+$$
+The denominator is total stress in firm $i$, made up of two components:   the volatility stress $\mu_{it}=\E(p_{it})$ and the systemic stress $\sigma_\phi\beta_{it}=\Es(p_it)-\E(p_{it})$.
+Volatility stress  arises on account  of high volatility in the markets causing high put prices.
+Systemic stress is the additional stress caused by  a potential  bad systemic event.
+\end{comment}
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics{figures/sysstress.pdf}
+\caption{Systemic, $s_{it}$, versus background $\mu_{it}$   for four major banks (left panel) and four minor banks (right panel)  for 144 months.}
+\label{sysstress}
+\end{center}
+\end{figure}
+
+\subsection{Flexible  stress  functions}
+
+The further modification made to the SRISK methodology of \cite{brownlees2015} is to generalise the ``cutoff" functional form for stressing.
+With the latter, stressed expectations are conditional expectations given a specified cutoff point.
+For SRISK in \cite{brownlees2015} the cutoff is in absolute terms:  a 10\% fall in the market although this can varied.
+This cutoff does not allow for market volatility:   a 10\% reduction is  increasingly plausible as volatility increases.
+In addition  SRISK does not  make judgement as to the likelihood of the conditioning stress event.
+Thus SRISK mixes in various  sources of risk in an imprecise manner and it is difficult to determine the implications of SRISK readings.
+
+This argues for specifying conditional behaviour in percentile terms relative to the then applicable market conditions, as in done in this paper.
+After all, current market volatility is known and there is a good reason to disentangle current market conditions from the evaluation of what is likely to happen if further stress arrives in the system.
+
+Stresses are further generalised in this paper with generalized univariate and multivariate forms of $\phi$, as well as discrete forms of $\phi$ which are aligned with the widespread approach of stress testing to measure individual firm and systemic risk by APRA and other prudential regulators.
+
+\section{Conclusion}\label{conclude}
+
+This paper develops an approach to measure systemic risk using the concept of stressed expectations are which akin to stress testing widely used in practice.
+Systemic stress adds to background stress which is the value of default puts on firms.
+Fitting time series to Australian bank data identifies banks previously in distress and those with high contribution to systemic risk.
+
+\begin{comment}
 
@@
 
-\section{Background and systemic stress  compared to SRISK}
-
-The methodology developed and employed in this article departs in two respects from the SRISK methodology set out in \cite{brownlees2015}.  This section examines the force of these differences.
-
-\subsection{Put value versus put on expected value}
-
-The SRISK methodology described in \sref{srisk}, in particular formula \eref{sriskperc}, is based on the put
-\be{prisk}
- |1-\E_\phi(\e^{\nu_{it}-\ell_{it}})|^+\le \Es(|1-\e^{\nu_{it}-\ell_{it}}|^+) \equiv \mu_{it}+s_{it}\ , 
-\ee
-where stressed expectation $\Es$ in the \cite{brownlees2015} article is conditional expectation given a major market downturn.
-The   put in the first expression is evaluated after the expectation $\Es$ and checks, in essence whether in a significant market downturn, the expected $h$ period ahead return $\nu_{it}$ exceeds the adjusted   log--leverage.
-If this holds true there may still be substantial risk of a Basel breach, depending on the volatility of the return.
-Volatility in $\nu_{it}$ is ignored in  $\mathrm{SRISK}_{it}$  other than through the usual adjustment on account of continuous compounding.
-In particular increased volatility due to stress is ignored.
-
-With $\mu_{it}+s_{it}$, volatility is taken into consideration.  Other things equal, high volatility leads to higher put values since breach size  is taken into consideration.
-
-Note further we split up $\mu_{it}=q_{it}\E(p_{it}|\nu_{it}>\ell_{it})$.    (Can do analogous split up on $s_{it}$ ????)
-
-(Should we compare $\mu_{it}+s_{it}$ to the left  hand side of $\eref{prisk}$ using graphs???)
-
-\subsection{Systemic stress versus background stress}
-
-\cite{brownlees2015} use $\Es$ as in \eref{prisk}.  A stressed expectation may be high simply on account of put prices being high, again reflecting higher than normal volatility.
-Stress measured with $\Es$  picks up both background stress, due to high volatility, and the extra stress imparted by the stressing variable.
-
-To gain insight into the relative sizes of these two components, consider the proportion of the stressed put price due to a possible future stress scenario
-$$
-\frac{\Es(p_{it})-\E(p_{it})}{\Es(p_{it})} = \frac{\sigma_\phi\beta_{it}}{\mu_{it}+\sigma_\phi\beta_{it}}  \ . 
-$$
-The denominator is total stress in firm $i$, made up of two components:   the volatility stress $\mu_{it}=\E(p_{it})$ and the systemic stress $\sigma_\phi\beta_{it}=\Es(p_it)-\E(p_{it})$.
-Volatility stress  arises on account  of high volatility in the markets causing high put prices.
-Systemic stress is the additional stress caused by  a potential  bad systemic event.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics{figures/sysstress.pdf}
-\caption{Systemic, $s_{it}$, versus background $\mu_{it}$   for four major banks (left panel) and four minor banks (right panel)  for 144 months.}
-\label{sysstress}
-\end{center}
-\end{figure}
-
-\fref{sysstress} plots systemic stress versus volatility stress for the eight Australian banks of \tref{banks}.   Generally volatility stress is higher than systemic stress.
-
-\subsection{Flexible  stress  functions}
-
-The further modification made to the SRISK methodology of \cite{brownlees2015} is to generalise the ``cutoff" functional form for stressing.
-With the latter, stressed expectations are conditional expectations given a specified cutoff point.
-In \cite{brownlees2015} the cutoff is in absolute terms:  a 10\% fall in the market although this can varied.
-The cutoff methodology does not make explicit allowance for market volatility:   an absolute 10\% reduction is  increasingly plausible  as volatility increases.
-However  SRISK does not  make judgement as to the likelihood of the conditioning stress event.
-Thus SRISK mixes in various  sources of risk in an imprecise manner and it will be difficult to determine the implications of SRISK readings.
-
- This argues for specifying conditional behaviour in percentile terms relative to the then applicable market conditions.
-After all, current market volatility is known and there is a good reason to disentangle current market conditions from the evaluation of what is likely to happen if further stress arrives in the system.
-
-Say something about the generalized functional forms $\phi$ as well as the fact that we have firmly embedded and/or aligned the methodology with more ad--hoc approaches to stress testing.
-
 \section{Comparing SRISK for different firms (not sure)}
@@
 
-\begin{comment}
 \subsection{Weihao - Allocating the market put}
@@
 \end{comment}
+
+\newpage
 
@@
 \section*{References}
-\bibliography{/users/pietdejong/documents/research/srisk/piet2}
+\bibliography{piet2}
 

### 2015-06-03 table.tex
pdj changes

\documentclass[authoryear]{elsarticle}
\usepackage{latexsym}
%\usepackage{rotate}
\usepackage{graphics}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{comment}
\bibliographystyle{chicago}

\newcommand{\logit}{\mathrm{lgt}}
\newcommand{\I}{\mathrm{I}}
\newcommand{\E}{\mathrm{E}}
\newcommand{\p}{\mathrm{P}}
\newcommand{\e}{\mathrm{e}}
\renewcommand{\o}{\omega}
\newcommand{\vecm}{\mathrm{vec}}
\newcommand{\kp}{\otimes}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\cov}{\mathrm{cov}}
\newcommand{\eps}{\epsilon}
\newcommand{\ep}{\varepsilon}
\newcommand{\obdots}{\ddots}    % change this later
\newcommand{\Ex}{{\cal E}}
\newcommand{\Exd}{\Ex_d}
\newcommand{\Es}{\E_\phi}
\newcommand{\rat}{{\frac{c_{ij}}{c_{i,j-1}}}}
\newcommand{\rmu}{m}
\newcommand{\rsig}{\nu}
\newcommand{\fd}{\mu}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\cor}{\mathrm{cor}}
\newcommand{\bx}[1]{\ensuremath{\overline{#1}|}}
\newcommand{\an}[1]{\ensuremath{a_{\bx{#1}}}}

\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}

\renewcommand{\i}{\item}
\newcommand{\sr}{\ensuremath{\mathrm{SRISK}}}
\newcommand{\cs}{\ensuremath{\mathrm{CS}}}
\newcommand{\cri}{\ensuremath{\mathrm{Crisis}}}
\newcommand{\var}{\ensuremath{\mathrm{VaR}}}
\newcommand{\covar}{\ensuremath{\mathrm{CoVaR}}}
\newcommand{\med}{\ensuremath{\mathrm{m}}}
\newcommand{\de}{\mathrm{d}}
\renewcommand{\v}{\ensuremath{\mathrm{v}_q}}
\newcommand{\m}{\ensuremath{\mathrm{m}}}
\newcommand{\tvar}{\ensuremath{\mathrm{TVaR}}}
\renewcommand{\c}{\ensuremath{\mathrm{CoVaR_q}}}
\renewcommand{\v}{\ensuremath{\mathrm{VaR}_q}}

\newcommand{\eref}[1]{(\ref{#1})}
\newcommand{\fref}[1]{Figure \ref{#1}}
\newcommand{\sref}[1]{\S\ref{#1}}
\newcommand{\tref}[1]{Table \ref{#1}}
\newcommand{\aref}[1]{Appendix \ref{#1}}

\newcommand{\cq}{\ , \qquad}
\renewcommand{\P}{\mathrm{P}}
\newcommand{\Q}{\mathrm{Q}}

\newcommand{\Vx}{{\cal V}}
\newcommand{\be}[1]{\begin{equation}\label{#1}}
\newcommand{\ee}{\end{equation}}

\begin{document}

\section*{Real time stress calculations on two dates}
 \tref{twodates} contains real time stress calculations for the first trading day for  January 2009 and November 2014.  As before there is no look ahead bias -- all calculations on each of the two dates only reflect information available at the start of the applicable month.  The initial eight rows in the table lists the eight banks used in this study.   The first  and second columns in the two segments of the table body contain the background and systemic stress
$$
\mu^*_{it} \equiv \frac{\pi_{it}\mu_{it}}{\Ex_d(\mu_{it})}\cq s^*_{it} \equiv \frac{\pi_{it}s_{it}}{\Ex_d(\mu_{it})}\ , 
$$
for the eight banks as well as the probability of a Basel default in one month $q_{it}$ and the proportion of total debt, $\pi_{it}$ in each bank.

January 2009 marked a time of great stress for all eight banks.    Six of the eight banks were in Basel default with positive capital shortfalls as indicated in by the $\ell_{it}$ column:   the two banks not in Basel default were wbc and aba.   The background stress column indicates most of the background stress arises from nab -- almost 40\% of the total.   The next most background stressed bank is cba with wbc also a substantial contributor.   The mqg bank contributes almost double to background stress compared to the proportion of total debt  it carries.  The other three small banks contribute relatively little to background stress with boq  almost 3 times expected on the basis of its debt.   Systemic stress is highest for the cba, higher than expected on the basis of its debt load and hence cba was most susceptible to stress from additional general market equity devaluation.    All other banks appear have systemic stress comparable to their size in terms of debt load with only nab being less systemically important.    This should be compared to its high background stress.

Continuing with January 2009, the final two rows indicate the total amount of stress in the system and it's diversifiability.   In particular 
the row labelled ``ave" immediately below the eight banks displays
$$
\overline{\mu}_t\equiv \Ex_d(\mu_{it})\cq \overline{s}_t\equiv\Ex_d(s_{it})\cq\Ex_d(q_{it})\cq \frac{d_t}{10^9}\cq \Ex_d(\ell_{it})\ .
$$
while the final row labelled ``div" displays the aggregate stress quantities $\mu_t$, $s_t$, and so on, treating all eight banks as one entity.
On an aggregate basis background stress is about twice systemic stress.   Thus there is more danger of increasing capital shortfall due to market volatility  as opposed to further stress from further substantial general market devaluation.  The final row indicates stresses are not diversifiable:    The marginally  smaller  ``diversified"  background stress is offset by an increase in systemic stress.    Also the diversified probability of Basel default is higher than the debt weighted average.

 Moving to November 2014, the stress picture has completely changed with virtually no stress in any bank and certainly none on the basis of diversification.    Most of this minimal background stress is carried by nab with lesser contributions by ben and aba.    All the stress in the minor bank aba is background stress as only nab and nab have substantial systemic stress contributions.   Again, however, it must be stressed that there is minimal systemic stress in the system.    Only aba has substantial Basel default probability, but this bank is a very minor player in the Australian banking scene.   Notice total debt in the banking sector has jumped around 35\% between January 2009 and November 2014.

\begin{table}[ht]
\caption{One month ahead stress calculations$^\dag$ }\label{twodates}
\centering
\vspace{4mm}
\begin{tabular}{|l|rrrrr|rrrrr|}
\hline
&\multicolumn{5}{c|}{January 2009}&\multicolumn{5}{c|}{November 2014}\\
  \hline
bank & \multicolumn{2}{c}{stress} & def & debt & B-log& \multicolumn{2}{c}{stress} & def & debt & B-log \\
  \cline{2-3}\cline{7-8}
           & back & syst & prob & prop & lev& back & syst & prob & prop & lev \\
  \cline{2-11} 
            & $\mu^*_{it}$  & $s^*_{it}$ & $q_{it}$ & $\pi_{it}$ & $\ell_{it}$
        & $\mu^*_{it}$  & $s^*_{it}$ & $q_{it}$ & $\pi_{it}$ & $\ell_{it}$ 
        \\
  \hline
cba & 22.99 & 29.60 & 91.43 & 24.30 & 18.57 & 0.00 & 0.00 & 0.00 & 22.70 & -70.34 \\ 
anz & 14.87 & 18.89 & 92.82 & 18.37 & 15.93 & 0.00 & 0.00 & 0.00 & 22.10 & -38.64 \\ 
nab & 39.98 & 19.41 & 99.97 & 25.50 & 31.97 & 50.52 & 67.13 & 1.23 & 25.61 & -12.45 \\ 
wbc & 5.86 & 23.94 & 40.42 & 22.84 & -1.55 & 0.00 & 0.00 & 0.00 & 22.03 & -53.84 \\ 
mqg & 11.02 & 5.46 & 99.92 & 5.75 & 41.22 & 0.17 & 0.12 & 0.03 & 4.33 & -46.10 \\ 
boq & 3.55 & 0.99 & 99.95 & 1.32 & 63.30 & 0.80 & 1.34 & 0.33 & 1.33 & -17.05 \\ 
ben & 1.72 & 1.71 & 90.53 & 1.81 & 18.91 & 25.43 & 30.71 & 8.47 & 1.84 & -7.63 \\ 
aba & 0.00 & 0.00 & 9.97 & 0.10 & -8.12 & 23.07 & 0.71 & 89.63 & 0.07 & 9.22 \\ 
  \hline
ave & 17.17 & 8.63 & 82.72 &  & 18.78 & 0.03 & 0.12 & 0.54 &  & -41.91 \\ 
div & 15.28 & 10.18 & 96.72 & $^*$2.42 & 17.81 & 0.00 & 0.00 & 0.00 & $^*$3.27 & -44.22 \\ 
   \hline
\end{tabular}
\end{table}
\small{   $^\dag$All numbers multiplied by 100 except total debt (in \$bln).}

\end{document}

### 2015-06-03 table.tex
pdj changes

@@
 \section*{Real time stress calculations on two dates}
- \tref{twodates} contains real time stress calculations for the first trading day for  January 2009 and November 2014.
+ \tref{twodates} contains real time stress calculations on the first trading day of  January 2009 and November 2014.
 As before there is no look ahead bias -- all calculations on each of the two dates only reflect information available at the start of the applicable month.
@@
 $$
-for the eight banks as well as the probability of a Basel default in one month $q_{it}$ and the proportion of total debt, $\pi_{it}$ in each bank.
+for the eight banks as well as the probability of a Basel default in one month $q_{it}$ and the proportion $\pi_{it}$ of total debt.
 
@@
 All other banks appear have systemic stress comparable to their size in terms of debt load with only nab being less systemically important.
-This should be compared to its high background stress.
+This should be compared to nab's high background stress.
 
 Continuing with January 2009, the final two rows indicate the total amount of stress in the system and it's diversifiability.   In particular 
-the row labelled ``ave" immediately below the eight banks displays
+the second last  row labelled $\Ex_e$  displays
 $$
-\overline{\mu}_t\equiv \Ex_d(\mu_{it})\cq \overline{s}_t\equiv\Ex_d(s_{it})\cq\Ex_d(q_{it})\cq \frac{d_t}{10^9}\cq \Ex_d(\ell_{it})\ .
+\overline{\mu}_t\equiv \Ex_d(\mu_{it})\cq \overline{s}_t\equiv\Ex_d(s_{it})\cq\Ex_d(q_{it})\cq \frac{d_t}{10^9}\cq \Ex_d(\ell_{it})\ ,
 $$
-while the final row labelled ``div" displays the aggregate stress quantities $\mu_t$, $s_t$, and so on, treating all eight banks as one entity.
+while the final row labelled $\Sigma$ displays the aggregate stress quantities $\mu_t$, $s_t$, and so on, treating all eight banks as one entity.
 On an aggregate basis background stress is about twice systemic stress.
@@
 
- Moving to November 2014, the stress picture has completely changed with virtually no stress in any bank and certainly none on the basis of diversification.
-Most of this minimal background stress is carried by nab with lesser contributions by ben and aba.
+ The stress picture  changes dramatically when moving to November 2014 -- there is virtually no stress in any bank and any stress is diversifiable.
+Most of the  background stress is carried by nab with lesser contributions by ben and aba.
 All the stress in the minor bank aba is background stress as only nab and nab have substantial systemic stress contributions.
-Again, however, it must be stressed that there is minimal systemic stress in the system.
+Again, however, it must be emphasised that there is minimal systemic stress in the system.
 Only aba has substantial Basel default probability, but this bank is a very minor player in the Australian banking scene.
@@
 \begin{table}[ht]
-\caption{One month ahead stress calculations$^\dag$ }\label{twodates}
+\caption{One month ahead stress calculations for Australian banks$^\dag$}\label{twodates}
 \centering
 \vspace{4mm}
-\begin{tabular}{|l|rrrrr|rrrrr|}
+\begin{tabular}{l|rrrrr|rrrrr}
 \hline
-&\multicolumn{5}{c|}{January 2009}&\multicolumn{5}{c|}{November 2014}\\
+&\multicolumn{5}{c|}{January 2009}&\multicolumn{5}{c}{November 2014}\\
   \hline
@@
   \hline
-ave & 17.17 & 8.63 & 82.72 &  & 18.78 & 0.03 & 0.12 & 0.54 &  & -41.91 \\ 
-div & 15.28 & 10.18 & 96.72 & $^*$2.42 & 17.81 & 0.00 & 0.00 & 0.00 & $^*$3.27 & -44.22 \\ 
+$\Ex_d$ & 17.17 & 8.63 & 82.72 &  & 18.78 & 0.03 & 0.12 & 0.54 &  & -41.91 \\ 
+$\Sigma$ & 15.28 & 10.18 & 96.72 & $^\dag$2.42 & 17.81 & 0.00 & 0.00 & 0.00 & $^\dag$3.27 & -44.22 \\ 
 \hline
@@
 \end{table}
-\small{   $^\dag$All numbers multiplied by 100 except total debt (in \$bln).}
+\small{$^\dag$All numbers multiplied by 100 except total debt (in \$bln).}
 

### 2015-06-03 table.tex
pdj changes

@@
 
-\section*{Real time stress calculations on two dates}
+\section*{Real time stress calculations}
  \tref{twodates} contains real time stress calculations on the first trading day of  January 2009 and November 2014.
@@
 
-Continuing with January 2009, the final two rows indicate the total amount of stress in the system and it's diversifiability.   In particular 
-the second last  row labelled $\Ex_e$  displays
+Continuing with January 2009, the final two rows indicate the total amount of stress in the system and it's diversifiability.    
+The second last  row labelled $\Ex_d$  displays
 $$
@@
 Only aba has substantial Basel default probability, but this bank is a very minor player in the Australian banking scene.
-Notice total debt in the banking sector has jumped around 35\% between January 2009 and November 2014.
+Notice total debt in the banking sector  jumps about 35\% between January 2009 and November 2014.
 
@@
 \centering
+\small
 \vspace{4mm}
@@
   \hline
-bank & \multicolumn{2}{c}{stress} & def & debt & B-log& \multicolumn{2}{c}{stress} & def & debt & B-log \\
+bank & \multicolumn{2}{c}{stress} & B-def & debt & B-log& \multicolumn{2}{c}{stress} & B-def & debt & B-log \\
   \cline{2-3}\cline{7-8}
@@
 \end{tabular}
+\normalsize
 \end{table}

### 2015-06-03 table.tex
pdj changes

@@
 
-\section*{Real time stress calculations}
+\section*{Month to month monitoring  of financial stress}
  \tref{twodates} contains real time stress calculations on the first trading day of  January 2009 and November 2014.
-As before there is no look ahead bias -- all calculations on each of the two dates only reflect information available at the start of the applicable month.
-The initial eight rows in the table lists the eight banks used in this study.
-The first  and second columns in the two segments of the table body contain the background and systemic stress
-$$
-\mu^*_{it} \equiv \frac{\pi_{it}\mu_{it}}{\Ex_d(\mu_{it})}\cq s^*_{it} \equiv \frac{\pi_{it}s_{it}}{\Ex_d(\mu_{it})}\ , 
-$$
-for the eight banks as well as the probability of a Basel default in one month $q_{it}$ and the proportion $\pi_{it}$ of total debt.
-
-January 2009 marked a time of great stress for all eight banks.
-Six of the eight banks were in Basel default with positive capital shortfalls as indicated in by the $\ell_{it}$ column:   the two banks not in Basel default were wbc and aba.
-The background stress column indicates most of the background stress arises from nab -- almost 40\% of the total.
-The next most background stressed bank is cba with wbc also a substantial contributor.
-The mqg bank contributes almost double to background stress compared to the proportion of total debt  it carries.
-The other three small banks contribute relatively little to background stress with boq  almost 3 times expected on the basis of its debt.
-Systemic stress is highest for the cba, higher than expected on the basis of its debt load and hence cba was most susceptible to stress from additional general market equity devaluation.
-All other banks appear have systemic stress comparable to their size in terms of debt load with only nab being less systemically important.
-This should be compared to nab's high background stress.
-
-Continuing with January 2009, the final two rows indicate the total amount of stress in the system and it's diversifiability.    
-The second last  row labelled $\Ex_d$  displays
-$$
-\overline{\mu}_t\equiv \Ex_d(\mu_{it})\cq \overline{s}_t\equiv\Ex_d(s_{it})\cq\Ex_d(q_{it})\cq \frac{d_t}{10^9}\cq \Ex_d(\ell_{it})\ ,
-$$
-while the final row labelled $\Sigma$ displays the aggregate stress quantities $\mu_t$, $s_t$, and so on, treating all eight banks as one entity.
-On an aggregate basis background stress is about twice systemic stress.
-Thus there is more danger of increasing capital shortfall due to market volatility  as opposed to further stress from further substantial general market devaluation.
-The final row indicates stresses are not diversifiable:    The marginally  smaller  ``diversified"  background stress is offset by an increase in systemic stress.
-Also the diversified probability of Basel default is higher than the debt weighted average.
-
- The stress picture  changes dramatically when moving to November 2014 -- there is virtually no stress in any bank and any stress is diversifiable.
-Most of the  background stress is carried by nab with lesser contributions by ben and aba.
-All the stress in the minor bank aba is background stress as only nab and nab have substantial systemic stress contributions.
-Again, however, it must be emphasised that there is minimal systemic stress in the system.
-Only aba has substantial Basel default probability, but this bank is a very minor player in the Australian banking scene.
-Notice total debt in the banking sector  jumps about 35\% between January 2009 and November 2014.
+As before there is no look ahead bias -- all calculations on each of the two dates only use data available on the first day of the applicable month.
+The initial eight rows in \tref{twodates} lists the eight banks used in this study.
 
@@
   \hline
-bank & \multicolumn{2}{c}{stress} & B-def & debt & B-log& \multicolumn{2}{c}{stress} & B-def & debt & B-log \\
-  \cline{2-3}\cline{7-8}
-           & back & syst & prob & prop & lev& back & syst & prob & prop & lev \\
+bank & B-log& debt &\multicolumn{2}{c}{stress}&  B-def   & B-log& debt   & \multicolumn{2}{c}{stress}& B-def \\
+  \cline{4-5}\cline{9-10}
+       &  lev& prop    & back & syst & prob & lev& prop  & back & syst & prob \\
   \cline{2-11} 
-            & $\mu^*_{it}$  & $s^*_{it}$ & $q_{it}$ & $\pi_{it}$ & $\ell_{it}$
-        & $\mu^*_{it}$  & $s^*_{it}$ & $q_{it}$ & $\pi_{it}$ & $\ell_{it}$ 
+         & $\ell_{it} $ & $\pi_{it}$ & $\mu^*_{it}$  & $s^*_{it}$ & $q_{it}$  
+         & $\ell_{it} $ & $\pi_{it}$ & $\mu^*_{it}$  & $s^*_{it}$ & $q_{it}$  
         \\
   \hline
-cba & 22.99 & 29.60 & 91.43 & 24.30 & 18.57 & 0.00 & 0.00 & 0.00 & 22.70 & -70.34 \\ 
-anz & 14.87 & 18.89 & 92.82 & 18.37 & 15.93 & 0.00 & 0.00 & 0.00 & 22.10 & -38.64 \\ 
-nab & 39.98 & 19.41 & 99.97 & 25.50 & 31.97 & 50.52 & 67.13 & 1.23 & 25.61 & -12.45 \\ 
-wbc & 5.86 & 23.94 & 40.42 & 22.84 & -1.55 & 0.00 & 0.00 & 0.00 & 22.03 & -53.84 \\ 
-mqg & 11.02 & 5.46 & 99.92 & 5.75 & 41.22 & 0.17 & 0.12 & 0.03 & 4.33 & -46.10 \\ 
-boq & 3.55 & 0.99 & 99.95 & 1.32 & 63.30 & 0.80 & 1.34 & 0.33 & 1.33 & -17.05 \\ 
-ben & 1.72 & 1.71 & 90.53 & 1.81 & 18.91 & 25.43 & 30.71 & 8.47 & 1.84 & -7.63 \\ 
-aba & 0.00 & 0.00 & 9.97 & 0.10 & -8.12 & 23.07 & 0.71 & 89.63 & 0.07 & 9.22 \\ 
+cba & 18.57 & 24.30 & 22.99 & 29.60 & 91.43 & -70.34 & 22.70 & 0.00 & 0.00 & 0.00 \\ 
+  anz & 15.93 & 18.37 & 14.87 & 18.89 & 92.82 & -38.64 & 22.10 & 0.00 & 0.00 & 0.00 \\ 
+  nab & 31.97 & 25.50 & 39.98 & 19.41 & 99.97 & -12.45 & 25.61 & 50.52 & 67.13 & 1.23 \\ 
+  wbc & -1.55 & 22.84 & 5.86 & 23.94 & 40.42 & -53.84 & 22.03 & 0.00 & 0.00 & 0.00 \\ 
+  mqg & 41.22 & 5.75 & 11.02 & 5.46 & 99.92 & -46.10 & 4.33 & 0.17 & 0.12 & 0.03 \\ 
+  boq & 63.30 & 1.32 & 3.55 & 0.99 & 99.95 & -17.05 & 1.33 & 0.80 & 1.34 & 0.33 \\ 
+  ben & 18.91 & 1.81 & 1.72 & 1.71 & 90.53 & -7.63 & 1.84 & 25.43 & 30.71 & 8.47 \\ 
+  aba & -8.12 & 0.10 & 0.00 & 0.00 & 9.97 & 9.22 & 0.07 & 23.07 & 0.71 & 89.63 \\ 
   \hline
-$\Ex_d$ & 17.17 & 8.63 & 82.72 &  & 18.78 & 0.03 & 0.12 & 0.54 &  & -41.91 \\ 
-$\Sigma$ & 15.28 & 10.18 & 96.72 & $^\dag$2.42 & 17.81 & 0.00 & 0.00 & 0.00 & $^\dag$3.27 & -44.22 \\ 
+  $\Ex_d$ & 18.78 &  & 17.17 & 8.63 & 82.72 & -41.91 &  & 0.03 & 0.12 & 0.54 \\ 
+  $\Sigma$ & 17.81 & $^\dag$2.42 & 15.28 & 10.18 & 96.72 & -44.22 & $^\dag$3.27 & 0.00 & 0.00 & 0.00 \\ 
 \hline
 \end{tabular}
+$^\dag$All numbers multiplied by 100 except total debt (in \$bln).
+\end{table}
 \normalsize
-\end{table}
-\small{$^\dag$All numbers multiplied by 100 except total debt (in \$bln).}
+
+January 2009 was a time of great stress for all eight banks.     The first  and second columns in the two halves of the table body contain the 
+ Basel log--leverage $\ell_{it}$ and debt $\pi_{it}\equiv d_{it}/d_t$ (as a proportion of total debt) for each of the banks.
+Six of the eight banks were in Basel default with positive capital shortfalls as indicated in by the $\ell_{it}$ column:   the two banks not in Basel default were wbc and aba.
+Background and systemic stress
+$$
+\mu^*_{it} \equiv \frac{\pi_{it}\mu_{it}}{\Ex_d(\mu_{it})}\cq s^*_{it} \equiv \frac{\pi_{it}s_{it}}{\Ex_d(\mu_{it})}\ , 
+$$
+for the eight banks as well as the probability of a Basel default in one month $q_{it}$ and the proportion $\pi_{it}$ of total debt are displayed in the next 3 columns.
+The background stress column indicates most of the background stress arises from nab -- almost 40\% of the total.
+The next most background stressed bank is cba with wbc also a substantial contributor.
+The mqg bank contributes almost double to background stress compared to the proportion of total debt  it carries.
+The other three small banks contribute relatively little to background stress with boq  almost 3 times expected on the basis of its debt.
+Systemic stress is highest for the cba, higher than expected on the basis of its debt load and hence cba was most susceptible to stress from additional general market equity devaluation.
+All other banks appear have systemic stress comparable to their size in terms of debt load with only nab being less systemically important.
+This should be compared to nab's high background stress.
+
+Continuing with January 2009, the final two rows indicate the total amount of stress in the system and it's diversifiability.    
+The second last  row labelled $\Ex_d$  displays, in order, $\Ex_d(\ell_{it})$, blank, $\overline{\mu}_t\equiv \Ex_d(\mu_{it})$, $\overline{s}_t\equiv\Ex_d(s_{it})$ and  $\Ex_d(q_{it})$.
+The final row labelled $\Sigma$ displays the aggregate stress quantities,treating all eight banks as one entity, $\ell_t$, total debt $d_t$ in billions of dollars,  $\mu_t$, $s_t$, and  $q_t$.
+On an aggregate basis background stress is about twice systemic stress.
+Thus there is more danger of increasing capital shortfall due to market volatility  as opposed to further stress from further substantial general market devaluation.
+The final row indicates stresses are not diversifiable:    The marginally  smaller  ``diversified"  background stress is offset by an increase in systemic stress.
+Also the diversified probability of Basel default is higher than the debt weighted average.
+
+Stress readings  alter dramatically when moving to November 2014 -- there is virtually no stress in any bank and the small amount of  stress in the system is diversifiable.
+Most of the  background stress is carried by nab with lesser contributions by ben and aba.
+All the stress in the minor bank aba is background stress as only nab and nab have substantial systemic stress contributions.
+Again, however, it must be emphasised that there is minimal systemic stress in the system.
+Only aba has substantial Basel default probability, but this bank is a very minor player in the Australian banking scene.
+Notice total debt in the banking sector  jumps about 35\% between January 2009 and November 2014.
 

### 2015-06-03 sriskjbes.tex
pdj jbes upload

--- 2015-06-03 table.tex
@@
-\documentclass[authoryear]{elsarticle}
-\usepackage{latexsym}
-%\usepackage{rotate}
-\usepackage{graphics}
+\documentclass[12pt]{article}
 \usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{comment}
-\bibliographystyle{chicago}
+\usepackage{graphicx,psfrag,epsf}
+\usepackage{enumerate}
+\usepackage{natbib}
+\usepackage{url} % not crucial - just used below for the URL
+
+%\pdfminorversion=4
+% NOTE: To produce blinded version, replace "0" with "1" below.
+\newcommand{\blind}{0}
+
+% DON'T change margins - should be 1 inch all around.
+\addtolength{\oddsidemargin}{-.5in}%
+\addtolength{\evensidemargin}{-.5in}%
+\addtolength{\textwidth}{1in}%
+\addtolength{\textheight}{1.3in}%
+\addtolength{\topmargin}{-.8in}%
 
@@
 \newcommand{\cq}{\ , \qquad}
-\renewcommand{\P}{\mathrm{P}}
-\newcommand{\Q}{\mathrm{Q}}
-
-\newcommand{\Vx}{{\cal V}}
-\newcommand{\be}[1]{\begin{equation}\label{#1}}
-\newcommand{\ee}{\end{equation}}
 
@@
 
-\section*{Month to month monitoring  of financial stress}
+%\bibliographystyle{natbib}
+
+\def\spacingset#1{\renewcommand{\baselinestretch}%
+{#1}\small\normalsize} \spacingset{1}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\if0\blind
+{
+  \title{\bf Measuring background and systemic risk in finance}
+  \author{Piet de Jong\thanks{
+    The authors gratefully acknowledge CIFR, the Centre of International Financial Regulation for financial support and other assistance.}\hspace{.2cm}\\
+    Department of Applied Finance and Actuarial Studies, Macquarie University\\
+    and \\
+    Department of Applied Finance and Actuarial Studies, Macquarie University}
+  \maketitle
+} \fi
+
+\if1\blind
+{
+  \bigskip
+  \bigskip
+  \bigskip
+  \begin{center}
+    {\LARGE\bf Title}
+\end{center}
+  \medskip
+} \fi
+
+\bigskip
+\begin{abstract}
+(200 or fewer words.)
+This article refines, builds on, and extends  SRISK methodology recently proposed in the literature.
+The refinement is to define SRISK in terms of a put on the Basel shortfall.
+This  is built on by defining the background and systemic stress  of a firm as unconditional and departure from unconditional  expectation of the put, the latter when a hypothetical systemic stress is applied.
+Systemic stress is defined in terms of a random variable and can take on variety of forms including alternative scenarios in usual stress testing as well stress driven by the interaction of variables.
+Stressor random variables  are chosen by the practitioner.
+Stressed expectations are linear, a sector systemic stress is naturally defined as linear in the firm specific systemic stress.
+Application is made to Australian financial data.
+\end{abstract}
+
+\noindent%
+{\it Keywords:}  3 to 6 keywords, that do not appear in the title
+\vfill
+
+\newpage
+\spacingset{1.45} % DON'T change the spacing!
+
+\section{Month to month monitoring  of financial stress}\label{monitoring}
  \tref{twodates} contains real time stress calculations on the first trading day of  January 2009 and November 2014.
@@
 \end{tabular}
+
 $^\dag$All numbers multiplied by 100 except total debt (in \$bln).
@@
 
+\section{Further guidelines}
+
+\begin{figure}
+\begin{center}
+%\includegraphics[width=3in]{fig1.pdf}
+\end{center}
+\caption{Consistency comparison in fitting surrogate model in the tidal
+power example. \label{fig:first}}
+\end{figure}
+
+\begin{table}
+\caption{D-optimality values for design $X$ under five different scenarios.  \label{tab:tabone}}
+\begin{center}
+\begin{tabular}{rrrrr}
+one & two & three & four & five\\\hline
+1.23 & 3.45 & 5.00 & 1.21 & 3.41 \\
+1.23 & 3.45 & 5.00 & 1.21 & 3.42 \\
+1.23 & 3.45 & 5.00 & 1.21 & 3.43 \\
+\end{tabular}
+\end{center}
+\end{table}
+
+\begin{itemize}
+\item Note that figures and tables (such as Figure~\ref{fig:first} and
+Table~\ref{tab:tabone}) should appear in the paper, not at the end or
+in separate files.
+\item In the latex source, near the top of the file the command
+\verb+\newcommand{\blind}{1}+ can be used to hide the authors and
+acknowledgements, producing the required blinded version.
+\item Remember that in the blind version, you should not identify authors
+indirectly in the text.  That is, don't say ``In Smith et. al.  (2009) we
+showed that ...''.  Instead, say ``Smith et. al. (2009) showed that ...''.
+\item These points are only intended to remind you of some requirements.
+Please refer to the instructions for authors
+at \url{http://amstat.tandfonline.com/action/authorSubmission?journalCode=ubes20&page=instructions#}
+\item For more about ASA\ style, please see \url{http://journals.taylorandfrancis.com/amstat/asa-style-guide/}
+\item If you have supplementary material (e.g., software, data, technical
+proofs), identify them in the section below.  In early stages of the
+submission process, you may be unsure what to include as supplementary
+material.  Don't worry---this is something that can be worked out at later stages.
+\end{itemize}
+
+\section{Methods}
+\label{sec:meth}
+Don't take any of these section titles seriously.  They're just for
+illustration.
+
+\section{Verifications}
+\label{sec:verify}
+This section will be just long enough to illustrate what a full page of
+text looks like, for margins and spacing.
+
+\cite{Campbell02}, \cite{Schubert13}, \cite{Chi81}
+
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+{\bf With this spacing we have 30 lines per page.}
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+The quick brown fox jumped over the lazy dog.
+
+\section{Conclusion}
+\label{sec:conc}
+
+\bigskip
+\begin{center}
+{\large\bf SUPPLEMENTARY MATERIAL}
+\end{center}
+
+\begin{description}
+
+\item[Title:] Brief description. (file type)
+
+\item[R-package for  MYNEW routine:] R-package ÒMYNEWÓ containing code to perform the diagnostic methods described in the article.
+The package also contains all datasets used as examples in the article.
+(GNU zipped tar file)
+
+\item[HIV data set:] Data set used in the illustration of MYNEW method in Section~ 3.2. (.txt file)
+
+\end{description}
+
+\section{BibTeX}
+
+We hope you've chosen to use BibTeX!\ If you have, please feel free to use the package natbib with any bibliography style you're comfortable with.
+The .bst file Chicago was used here, and agsm.bst has been included here for your convenience.
+
+\bibliographystyle{Chicago}
+
+\bibliography{Bibliography-MM-MC}
 \end{document}

### 2015-06-04 srisk5.tex
pdj changes

--- 2015-05-31 srisk4.tex
@@
 % List of authors, with corresponding author marked by asterisk
-\author{Piet de Jong,  Geoff Loudon and Weihao Choo \\[4pt]
+\author{Piet de Jong,  Geoffrey loudon and Weihao Choo \\[4pt]
 % Author addresses
@@
 \begin{abstract}
-This article refines, builds on, and extends  SRISK methodology recently proposed in the literature.
-The refinement is to define SRISK in terms of a put on the Basel shortfall.
-This  is built on by defining the background and systemic stress  of a firm as unconditional and departure from unconditional  expectation of the put, the latter when a hypothetical systemic stress is applied.
-Systemic stress is defined in terms of a random variable and can take on variety of forms including alternative scenarios in usual stress testing as well stress driven by the interaction of variables.
+This article refines, builds on, and extends the systemic risk methodology [SRISK] recently proposed by \cite{brownlees2015}.
+We refine SRISK by defining it in terms of a put on the Basel shortfall.
+We build on this by distinguishing background and systemic stress of a firm.
+Background stress is the unconditional expectation of the put.
+Systemic stress is the departure from the unconditional expectation when a hypothetical systemic stress is applied.
+Systemic stress is defined in terms of a random variable and can take on variety of forms including alternative scenarios as in usual stress testing and also
+stress driven by the interaction of variables.
 Stressor random variables are chosen by the practitioner.
-Stressed expectations are linear, a sector systemic stress is naturally defined as linear in the firm specific systemic stress.
+Stressed expectations are linear and sector systemic stress is naturally defined as linear in the firm specific systemic stress.
 Application is made to Australian financial data.
@@
 JEL classification
-C15; E53; G21  (Needs to be filled out)
+C15; E53; G21  %(Needs to be filled out)
 
-\section{Background}
+\section{Introduction}
 
-Recent literature in the area of quantitative systemic risk or stress measurement includes
-\cite{adrian2011covar},
-\cite{acharya2012capital},
-\cite{acharya2012measuring},
- \cite{brownlees2010volatility} and \cite{brownlees2015}.
-This study aims to extend and apply these techniques particularly in relation to the entities regulated by the Australian Prudential Regulation Authority (APRA).
+Monitoring systemic risk is a key function of macro-prudential regulation.
+Central banks and other financial regulatory bodies such as the US Financial Stability Oversight Council, the European Systemic Risk Board and the Australian Prudential Regulation Authority [APRA] are concerned with developing and applying quantitative risk measures to alert them of potential episodes of heightened systemic risk.
+Systemic risk has many dimensions.
+For example, in their influential review paper, \cite{Bisias2012} present a taxonomy of six categories of systemic risk comprising 31 quantitative risk measures.
+While attempts to gain consensus on a theoretical definition have proved elusive, several empirical measures of systemic risk have been developed and applied with some success.
+An important example is the SRISK measure due to \cite{brownlees2015} which proposes an index that measures the expected capital shortfall on a financial institution conditional on a large and lengthy decline in equity markets.
+\cite{brownlees2015} show the practical usefulness of their measure in three ways: (i) SRISK rankings identify systemically risky US banks during the global financial crisis [GFC]; (ii) pre-crisis SRISK helps predict capital injections by the Fed Reserve; (iii) aggregate SRISK provides early warning of declines in industrial production and higher unemployment.
+
+Our paper builds upon and extends the model of \cite{brownlees2015} in several interesting and important ways.
+First, we reinterpret their SRISK measure as a put on the expected shortfall using stressed expectation.
+While they condition on the event of a severe market downturn, we take the stressed expectation of the put value.
+This enables us to capture the impact of increased return volatility due to stress.
+Second, we decompose their SRISK measure into background stress and imposed system stress.
+Background stress is a function of existing volatility and leverage.
+As these factors increase, background stress rises and this makes the firm more susceptible to systemic risk, regardless of the stress event itself.
+Third,
+\cite{brownlees2015} condition on an absolute cutoff of arbitrary size and length.
+We suggest that it is also helpful to specify conditional behaviour in percentile terms relative to current market conditions.
+This provides a sharper focus on the incremental impact of further stress and allows us to draw stronger implications of SRISK numbers.
+These extensions provide additional insights into the sources and economic nature of systemic risk.
+They provide potentially new and improved ways of anticipating episodes of heightened systemic risk.
+Their practical use can be expected to help regulators monitor systemic risk in a timely fashion to facilitate remedial action where necessary.
+
+% This study aims to extend and apply these techniques particularly in relation to the entities regulated by the Australian Prudential Regulation Authority (APRA).
 Thus our  broad aim is to develop, implement and bring to bear recent developments in systemic risk measurement and stress testing  on the aims of APRA and the CIFR targeted research areas.
@@
 
-This study refines and develops recently proposed methods and applies the same to publicly available daily financial data for  the eight  Australian banks detailed in \tref{eightbanks} spanning the period from   3 April 2000 through to 1 December 2014.
+While our measures are designed for use in all financial systems, it is of particular interest to test them using the Australian setting for at least two reasons.
+First, the Australian financial system is dominated by only four banks.
+In Australia there are four major banks that hold 78\% of the total assets of all Authorised Deposit-taking Institutions in  Australia.\footnote{Based on balances at 31 December 2014 disclosed in APRA's Quarterly Authorised Deposit-taking Institution [ADI] Performance Report for March 2015.} It is therefore obvious that the four majors are systemically important and the remaining ADIs are not so unless stress in one of these minors somehow creates financial contagion to the majors, in an unforeseeable way.
+Second, the Australian banking system proved to be resilient through the recent GFC, implying that systemic risk did not reach the extreme levels experienced by other countries where bank failures occurred.
+Both these features of the Australian system suggest that it may be difficult to find useful additional information about systemic risk by refining quantitative measures like SRISK.
+Since we are able to show that our measures are informative about systemic risk in Australia, we conjecture that they will provide additional insights elsewhere.
+
+To illustrate the nature and usefulness of our measures, we use publicly available daily financial data for the eight Australian banks detailed in \tref{eightbanks} spanning the period from  3 April 2000 through to 1 December 2014.
 The data is described in detail in \aref{data}.
@@
 Prices are combined with number of shares to derive total equity.
-Total debt for each firm at each day is also collected.
-(Should these be plotted?).
+Total debt for each firm is also collected from annual accounting reports.
+% (Should these be plotted?
+No, not informative;  leverage ratio plots are sufficient).
 
 Remaining sections are structured as follows.
+\sref{litrev} briefly discusses some related literature.
 \sref{capshort} and \sref{futshort} define current and future  capital shortfall similarly as \cite{brownlees2015} under a simplistic Basel II regulatory framework.
@@
 \end{figure}
+
+\section{Literature review}\label{litrev}
+Many papers in the finance and economics literature are devoted to the development and application of a variety of quantitative measures of systemic risk or financial stress.
+\cite{Bisias2012} provide an instructive and qualitative survey of numerous measures in use.
+\cite{Giglio2015} supply empirical evidence on the ability of many of these measures, both individually and collectively, to provide early warning signals of deterioration in macro-economic conditions.
+In this section, we provide a selective overview of the measures most closely related to SRISK and its relevance for assessing systemic risk in the financial sector.
+
+The genesis of SRISK lies in a series of papers including \cite{acharya2012capital}, \cite{acharya2012measuring} and \cite{brownlees2010volatility}.
+In these papers, SRISK is defined as the expected capital shortfall of a financial firm, conditional on a crisis.
+A crisis is deemed to occur whenever the relevant market index suffers a significant decline over a chosen horizon.
+\cite{Benoit2013} show how several popular systemic risk measures including MES and SRISK are transformations of market risk measures and derive conditions under which these measures provide similar rankings of systemically important financial institutions.
+
+\cite{brownlees2015} develop SRISK. [***** to add a fuller description of this paper given it is the key paper for our work]
+
+\cite{Engle2015} extend the model in \cite{brownlees2015} to incorporate global, country and industry effects.
+This extended model makes effective use of \cite{Engle2014dcb} dynamic conditional model.
+Their empirical methods are able to provide information of the relative systemic importance of industry type and country identity.
+
+\cite{adrian2011covar} propose an alternative measure of systemic risk that emphasises the co-dependence of financial firms and the importance of risk spillovers within the financial sector.
+They introduce CoVaR$_i$ which computes the Value-at-Risk [VaR] of the entire financial system, conditional on institution $i$ being in distress.
+Distress is defined as the state where the institution is exactly at its VaR level.
+\cite{Girardi2013} improve CoVaR by conditioning on the institution being at most at its VaR.
+This generalisation is useful as it takes into account severity of tail losses and facilitates back-testing of CoVaR.
+
+Empirical estimates of SRISK measure require a model for the joint distribution of returns of individual firms and the market.
+Many of these papers use \cite{engle2002dynamic}'s GARCH-DCC model which nicely captures the time-varying dynamics of the return (co)variances in a feasible manner.
+While we also use this model in our empirical analysis, we emphasize that our approach can utilise any appropriate model for simulating forward the joint distribution of firm and market returns.
 
@@
 Hence the expected capital shortfall (allowing surplus offset) is computed from \eref{shortfall} assuming a market downturn and added across all firms.
-Firms having a expected capital surplus are ignored.
+Firms having an expected capital surplus are ignored.
 The systemic risk of firm $i$ at time $t$ is its proportionate contribution to \eref{esrisk}:
@@
 
-\section{Systemic beta's}
+\section{Systemic betas}
 
@@
 
-The expressions in \eref{zscore2} suggests two ways of  thinking about the  systemic beta's  $\beta_{it}$.
+The expressions in \eref{zscore2} suggests two ways of  thinking about the  systemic betas  $\beta_{it}$.
 First, the left hand side equation shows systemic stress $\beta_{it}$ serves to shift the mean $\E(p_{it})$ of put prices  by, on average, $\sigma_\phi$.
@@
 
-Systemic beta's are stated in terms of additions to the normal put price $\E(p_{it})$.
+Systemic betas are stated in terms of additions to the normal put price $\E(p_{it})$.
 Thus in an increasingly dire financial situation $\E(p_{it})$ will increase.
@@
 Thus in an increasingly dire financial situation put prices are liable to increase on account of decreasing expected returns and increasing volatility.
-However our definition of systemic stress using systemic beta's measures the further effect on account of potential extra stress imposed onto the system over and above the already existing stress.
-Systemic beta's capture   ``marginal" effects.
+However our definition of systemic stress using systemic betas measures the further effect on account of potential extra stress imposed onto the system over and above the already existing stress.
+Systemic betas capture   ``marginal" effects.
 
@@
 
-The estimation of background stresses and systemic stresses and beta's requires projections of future capital shortfalls.
+The estimation of background stresses and systemic stresses and betas requires projections of future capital shortfalls.
 As in \cite{brownlees2015}, projections in this paper are constructed  using time series models of forward rates of return $\nu_{it}$ for firm $i$ and $\nu_{mt}$ for the market.
@@
 
-(Geoff -- can you fill out?)
+Data are sourced from DataStream. DataStream company codes are 
+\begin{center}
+	\begin{tabular}{ll}
+A:ANZX & Australia and New Zealand Banking Group Limited\\
+A:ABAX & Auswide Bank Limited\\
+A:BOQX & Bank of Queensland Limited\\
+A:BENX & Bendigo and Adelaide Bank Limited\\
+A:CBAX & Commonwealth Bank of Australia\\
+A:MQGX & Macquarie Bank Limited\\
+A:NABX & National Australia Bank Limited\\
+A:WBCX & Westpac Banking Corporation.\\	
+\end{tabular}
+\end{center}
+
+DataStream datatype codes are
+\begin{center}
+	\begin{tabular}{ll}
+	NOSH & Number of Shares\\
+	P & Price\\
+	WC02999 & Total Assets\\
+	WC03501 & Shareholders Equity\\
+	RZ & Total return index\\
+\end{tabular}
+\end{center}
+
+Firm equity $w_{it}$ is Number of Shares multiplied by Price.
+Firm debt $d_{it}$ is Total Assets minus Shareholders Equity.
+Stock returns are computed from the Total Return Index which includes dividends as paid.
 

### 2015-06-04 srisk6.tex
pdj changes

--- 2015-06-04 srisk5.tex
@@
-\documentclass[authoryear]{elsarticle}
-\usepackage{latexsym}
-%\usepackage{rotate}
-\usepackage{graphics}
+\documentclass[12pt]{article}
 \usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{comment}
+\usepackage{graphicx,psfrag,epsf,comment}
+\usepackage{enumerate}
+\usepackage{natbib}
+\usepackage{url} % not crucial - just used below for the URL 
 \bibliographystyle{chicago}
 
-\makeatletter
-\def\ps@pprintTitle{%
-\let\@oddhead\@empty
-\let\@evenhead\@empty
-\def\@oddfoot{}%
-\let\@evenfoot\@oddfoot}
-\makeatother
+%\pdfminorversion=4
+% NOTE: To produce blinded version, replace "0" with "1" below.
+\newcommand{\blind}{0}
+
+% DON'T change margins - should be 1 inch all around.
+\addtolength{\oddsidemargin}{-.5in}%
+\addtolength{\evensidemargin}{-.5in}%
+\addtolength{\textwidth}{1in}%
+\addtolength{\textheight}{1.3in}%
+\addtolength{\topmargin}{-.8in}%
 
@@
 
-% Title of paper
-\title{Measuring background and systemic risks in finance}
-% List of authors, with corresponding author marked by asterisk
-\author{Piet de Jong,  Geoffrey loudon and Weihao Choo \\[4pt]
-% Author addresses
-\textit{Department of Applied Finance and Actuarial Studies\\ Macquarie University, Sydney, NSW 2109.}
-\\[2pt]
-%E-mail address for correspondence
-{piet.dejong@mq.edu.au}}
-
-% Running headers of paper:
-\markboth%
-% First field is the short list of authors
-{De Jong}
-% Second field is the short title of the paper
-{Systemic risk}
-
+%\bibliographystyle{natbib}
+
+\def\spacingset#1{\renewcommand{\baselinestretch}%
+{#1}\small\normalsize} \spacingset{1}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\if0\blind
+{
+  \title{\bf Measuring background and systemic risk using financial time series}
+  \author{Piet de Jong\thanks{
+    The authors gratefully acknowledge CIFR, the Centre of International Financial Regulation for financial support and other assistance.}\hspace{.2cm}\\
+    Department of Applied Finance and Actuarial Studies, Macquarie University\\
+    and \\
+    Geoff Loudon\\
+    Department of Applied Finance and Actuarial Studies, Macquarie University\\
+    and\\
+    Weihao Choo\\
+    Department of Applied Finance and Actuarial Studies, Macquarie University}
+  \maketitle
+} \fi
+
+\if1\blind
+{
+  \bigskip
+  \bigskip
+  \bigskip
+  \begin{center}
+    {\LARGE\bf Title}
+\end{center}
+  \medskip
+} \fi
+
+\bigskip
 \begin{abstract}
-This article refines, builds on, and extends the systemic risk methodology [SRISK] recently proposed by \cite{brownlees2015}.
-We refine SRISK by defining it in terms of a put on the Basel shortfall.
-We build on this by distinguishing background and systemic stress of a firm.
-Background stress is the unconditional expectation of the put.
-Systemic stress is the departure from the unconditional expectation when a hypothetical systemic stress is applied.
-Systemic stress is defined in terms of a random variable and can take on variety of forms including alternative scenarios as in usual stress testing and also
-stress driven by the interaction of variables.
+This article refines and extends  SRISK methodology recently proposed in the literature.
+The refinement is to define systemic risk in terms of a put on the Basel shortfall.
+Background and systemic stress  of a firm are defined as unconditional, and departure from unconditional  expectation, of the put, the latter when a hypothetical systemic stress is applied.
+Systemic stress is defined in terms of a random variable and can take on variety of forms including alternative scenarios in usual stress testing as well stress driven by the interaction of variables.
 Stressor random variables  are chosen by the practitioner.
-Stressed expectations are linear and sector systemic stress is naturally defined as linear in the firm specific systemic stress.
-Application is made to Australian financial data.
+Stressed expectations are linear, a sector systemic stress is naturally defined as linear in the firm specific systemic stress.
+Application is made to Australian financial daily time series data.
 \end{abstract}
 
-\maketitle
-
-JEL classification
-C15; E53; G21  %(Needs to be filled out)
-
-\section{Introduction}
-
-Monitoring systemic risk is a key function of macro-prudential regulation.
-Central banks and other financial regulatory bodies such as the US Financial Stability Oversight Council, the European Systemic Risk Board and the Australian Prudential Regulation Authority [APRA] are concerned with developing and applying quantitative risk measures to alert them of potential episodes of heightened systemic risk.
+\noindent%
+{\it Keywords:}  3 to 6 keywords, that do not appear in the title
+\vfill
+
+\newpage
+\spacingset{1.45} % DON'T change the spacing!
+
+Monitoring stresses and systemic risk in the financial system is a key function of macro--prudential regulation.
+Central banks and other financial regulatory bodies such as the US Financial Stability Oversight Council, the European Systemic Risk Board and the Australian Prudential Regulation Authority [APRA] are concerned with developing and applying early warning quantitative  measures  to warn of potential episodes of heightened systemic risk.
 Systemic risk has many dimensions.
 For example, in their influential review paper, \cite{Bisias2012} present a taxonomy of six categories of systemic risk comprising 31 quantitative risk measures.
-While attempts to gain consensus on a theoretical definition have proved elusive, several empirical measures of systemic risk have been developed and applied with some success.
-An important example is the SRISK measure due to \cite{brownlees2015} which proposes an index that measures the expected capital shortfall on a financial institution conditional on a large and lengthy decline in equity markets.
+While attempts to gain consensus on a theoretical definition have proved elusive, several empirical measures of systemic risk have been developed and applied with  success.
+An important example is the SRISK measure due to \cite{brownlees2015} -- an index that measures the expected capital shortfall of a financial institution conditional on a large and lengthy decline in equity markets.
 \cite{brownlees2015} show the practical usefulness of their measure in three ways: (i) SRISK rankings identify systemically risky US banks during the global financial crisis [GFC]; (ii) pre-crisis SRISK helps predict capital injections by the Fed Reserve; (iii) aggregate SRISK provides early warning of declines in industrial production and higher unemployment.
 
-Our paper builds upon and extends the model of \cite{brownlees2015} in several interesting and important ways.
+Our paper refines and extends the model of \cite{brownlees2015} in several interesting and important ways.
 First, we reinterpret their SRISK measure as a put on the expected shortfall using stressed expectation.
 While they condition on the event of a severe market downturn, we take the stressed expectation of the put value.
-This enables us to capture the impact of increased return volatility due to stress.
+This eNABles us to capture the impact of increased return volatility due to stress.
 Second, we decompose their SRISK measure into background stress and imposed system stress.
@@
 Remaining sections are structured as follows.
-\sref{litrev} briefly discusses some related literature.
-\sref{capshort} and \sref{futshort} define current and future  capital shortfall similarly as \cite{brownlees2015} under a simplistic Basel II regulatory framework.
+Section \ref{litrev} briefly discusses some related literature.
+Section \ref{capshort} and \ref{futshort} define current and future  capital shortfall similarly as \cite{brownlees2015} under a simplistic Basel II regulatory framework.
 The definition of systemic risk used by \cite{brownlees2015} is discussed in \sref{srisk}, and is refined, extended and illustrated \sref{improve} to \sref{estimate}.
-\sref{marketstress} discusses specific stress examples which extend beyond \cite{brownlees2015}.
+Section \ref{marketstress} discusses specific stress examples which extend beyond \cite{brownlees2015}.
 Applications to Australian bank data are discussed in \sref{simulate} and \sref{simulate1}.
-\sref{aggregate} and \sref{aggregate1} discuss how stresses are combined across firms with and without allowance for merging or diversification.
-Generalised stressed are outlined in \sref{genstress}.
-\sref{riskmethod} offers an alternative modeling approach, based on assets.
-\sref{comparison} summarises differences between proposed stress measurement in this paper with that of
-\cite{brownlees2015}. \sref{conclude} concludes.
+Section \ref{aggregate} and \ref{aggregate1} discuss how stresses are combined across firms with and without allowance for merging or diversification.
+Section \ref{monitoring} displays system stress calculations as they would proceed in real time.
+Generalised stresses are outlined in \sref{genstress}.
+Section \ref{riskmethod} offers an alternative modelling approach, based on assets.
+Section \ref{comparison} summarises differences between proposed stress measurement in this paper with that of
+\cite{brownlees2015}. Section \ref{conclude} concludes.
 
@@
  \hline
-cba & Commonwealth Bank  & mqg & Macquarie \\
-anz & Australia \& New Zealand  & boq & Bank of Queensland\\
-nab & National Australia  & ben & Bendigo and Adelaide \\
-wbc & Westpac & aba & Auswide \\
+CBA & Commonwealth Bank  & MQG & Macquarie \\
+ANZ & Australia \& New Zealand  & BOQ & Bank of Queensland\\
+NAB & National Australia  & BEN & Bendigo and Adelaide \\
+WBC & Westpac & ABA& Auswide \\
 \hline
@@
 \includegraphics{figures/prices.pdf}
-\caption{Stock  prices of four major (left panel) and four minor (right panel) Australian banks from early 2000 through to the end of 2014.  All prices normalised to start at 1.}
+\caption{Stock  prices of four major (left panel) and four minor (right panel) Australian banks from early 2000 through to the end of 2014.  Price series normalised to start at 1.}
 \label{prices}
@@
 In these papers, SRISK is defined as the expected capital shortfall of a financial firm, conditional on a crisis.
-A crisis is deemed to occur whenever the relevant market index suffers a significant decline over a chosen horizon.
+A crisis is deemed to occur whenever a relevant market index suffers a significant decline over a chosen horizon.
 \cite{Benoit2013} show how several popular systemic risk measures including MES and SRISK are transformations of market risk measures and derive conditions under which these measures provide similar rankings of systemically important financial institutions.
@@
 Empirical estimates of SRISK measure require a model for the joint distribution of returns of individual firms and the market.
-Many of these papers use \cite{engle2002dynamic}'s GARCH-DCC model which nicely captures the time-varying dynamics of the return (co)variances in a feasible manner.
-While we also use this model in our empirical analysis, we emphasize that our approach can utilise any appropriate model for simulating forward the joint distribution of firm and market returns.
+Many of these papers use \cite{engle2002dynamic}'s GARCH-DCC model aiming to capture the time-varying dynamics of the return (co)variances in a feasible manner.
+While we also use this model in our empirical analysis, we emphasize that our approach can utilise any appropriate model for simulating the joint distribution of forward firm and market returns.
 
@@
 An alternative approach models future asset values $d_{i,t+h}+w_{i,t+h}$ in turn implying equity returns, and is briefly discussed in \sref{riskmethod}.
-Results in this paper generally hold for any modeling approach.
+The risk measurement approach of this paper can be combined with any forecasting approach.
 
@@
 In the left panel the outcome is a decline in both  the market and CBA stock price.
-In the right panel the returns are xxx and xxx.
+In the right panel there is slight decline in the stock price, and a more substantial market downturn.
 Thus at the beginning of January  2009 CBA was projected to be far from compliance in a month while in December 2014 the one month projection is of complete compliance.
@@
  \be{sriskperc}
- \mathrm{SRISK}_{it}\equiv \pi_{it}\frac{|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+}{\Ex_d\{|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+\}}\cq \pi_{it}\equiv \frac{d_{it}}{d_t}\cq d_t\equiv \sum_i d_{it}\ ,
+ \mathrm{SRISK}_{it}\equiv \frac{\pi_{it}|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+}{\Ex_d\{|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+\}}\cq \pi_{it}\equiv \frac{d_{it}}{d_t}\cq d_t\equiv \sum_i d_{it}\ ,
  \ee
@@
 
-Using the Jensen's inequality,
+From Jensen's inequality,
 $$
@@
 The bottom $\alpha$ of market returns is further stressed by  progressively overweighing returns as the percentile approaches 0.
-Large simulation effort $N$ is required for a reasonable approximation since $N/c$ is the effective simulation size and $c$ is small.
-
-\section{Simulating future capital shortfall and market return}\label{simulation}
+Large simulation effort $N$ is required for a reasoNABle approximation since $N/c$ is the effective simulation size and $c$ is small.
+
+\section{Simulating future capital shortfall and market return}\label{simulate}
 
@@
 
-\section{One month ahead forecast stresses in individual banks}\label{simulate1}
+\section{One month ahead forecast stress in individual banks}\label{simulate1}
 
@@
 
+\section{Month to month monitoring  of financial stress}\label{monitoring}
+ \tref{twodates} contains real time stress calculations on the first trading day of  January 2009 and November 2014.
+As before there is no look ahead bias -- all calculations on each of the two dates only use data available on the first day of the applicable month.
+The initial eight rows in \tref{twodates} lists the eight banks used in this study.
+
+ \begin{table}[ht]
+\caption{One month ahead bank stress calculations$^\dag$}\label{twodates}
+\centering
+\small
+\vspace{4mm}
+\begin{tabular}{l|rrrrr|rrrrr}
+\hline
+&\multicolumn{5}{c|}{January 2009}&\multicolumn{5}{c}{November 2014}\\
+  \hline
+bank & B-log& debt &\multicolumn{2}{c}{stress}&  B-def   & B-log& debt   & \multicolumn{2}{c}{stress}& B-def \\
+  \cline{4-5}\cline{9-10}
+       &  lev& prop    & back & syst & prob & lev& prop  & back & syst & prob \\
+  \cline{2-11} 
+         & $\ell_{it} $ & $\pi_{it}$ & $\mu^*_{it}$  & $s^*_{it}$ & $q_{it}$  
+         & $\ell_{it} $ & $\pi_{it}$ & $\mu^*_{it}$  & $s^*_{it}$ & $q_{it}$  
+        \\
+  \hline
+CBA & 18.57 & 24.30 & 22.99 & 29.60 & 91.43 & -70.34 & 22.70 & 0.00 & 0.00 & 0.00 \\ 
+  ANZ & 15.93 & 18.37 & 14.87 & 18.89 & 92.82 & -38.64 & 22.10 & 0.00 & 0.00 & 0.00 \\ 
+  NAB & 31.97 & 25.50 & 39.98 & 19.41 & 99.97 & -12.45 & 25.61 & 50.52 & 67.13 & 1.23 \\ 
+  WBC & -1.55 & 22.84 & 5.86 & 23.94 & 40.42 & -53.84 & 22.03 & 0.00 & 0.00 & 0.00 \\ 
+  MQG & 41.22 & 5.75 & 11.02 & 5.46 & 99.92 & -46.10 & 4.33 & 0.17 & 0.12 & 0.03 \\ 
+  BOQ & 63.30 & 1.32 & 3.55 & 0.99 & 99.95 & -17.05 & 1.33 & 0.80 & 1.34 & 0.33 \\ 
+  BEN & 18.91 & 1.81 & 1.72 & 1.71 & 90.53 & -7.63 & 1.84 & 25.43 & 30.71 & 8.47 \\ 
+  ABA& -8.12 & 0.10 & 0.00 & 0.00 & 9.97 & 9.22 & 0.07 & 23.07 & 0.71 & 89.63 \\ 
+  \hline
+  $\Ex_d$ & 18.78 &  & 17.17 & 8.63 & 82.72 & -41.91 &  & 0.03 & 0.12 & 0.54 \\ 
+  $\Sigma$ & 17.81 & $^\dag$2.42 & 15.28 & 10.18 & 96.72 & -44.22 & $^\dag$3.27 & 0.00 & 0.00 & 0.00 \\ 
+\hline
+\end{tabular}
+
+$^\dag$All numbers multiplied by 100 except total debt (in \$bln).
+\end{table}
+\normalsize
+
+January 2009 was a time of great stress for all eight banks.     The first  and second columns in the two halves of the table body contain the 
+ Basel log--leverage $\ell_{it}$ and debt $\pi_{it}\equiv d_{it}/d_t$ (as a proportion of total debt) for each of the banks.
+Six of the eight banks were in Basel default with positive capital shortfalls as indicated in by the $\ell_{it}$ column:   the two banks not in Basel default were WBC and aba.
+Background and systemic stress
+$$
+\mu^*_{it} \equiv \frac{\pi_{it}\mu_{it}}{\Ex_d(\mu_{it})}\cq s^*_{it} \equiv \frac{\pi_{it}s_{it}}{\Ex_d(\mu_{it})}\ , 
+$$
+for the banks as well as the probability of a Basel default in one month $q_{it}$ and the proportion $\pi_{it}$ of total debt are displayed in the next 3 columns.
+The background stress column indicates most of the background stress arises from NAB -- almost 40\% of the total.
+The next most background stressed bank is CBA with WBC also a substantial contributor.
+The MQG bank contributes almost double to background stress compared to the proportion of total debt  it carries.
+The other three small banks contribute relatively little to background stress with BOQ  almost 3 times expected on the basis of its debt.
+Systemic stress is highest for the CBA, higher than expected on the basis of its debt load and hence CBA was most susceptible to stress from additional general market equity devaluation.
+All other banks appear have systemic stress comparable to their size in terms of debt load with only NAB being less systemically important.
+This should be compared to NAB's high background stress.
+
+Continuing with January 2009, the final two rows indicate the total amount of stress in the system and it's diversifiability.    
+The second last  row labelled $\Ex_d$  displays, in order, $\Ex_d(\ell_{it})$, blank, $\overline{\mu}_t\equiv \Ex_d(\mu_{it})$, $\overline{s}_t\equiv\Ex_d(s_{it})$ and  $\Ex_d(q_{it})$.
+The final row labelled $\Sigma$ displays the aggregate stress quantities,treating all eight banks as one entity, $\ell_t$, total debt $d_t$ in billions of dollars,  $\mu_t$, $s_t$, and  $q_t$.
+On an aggregate basis background stress is about twice systemic stress.
+Thus there is more danger of increasing capital shortfall due to market volatility  as opposed to further stress from further substantial general market devaluation.
+The final row indicates stresses are not diversifiable:    The marginally  smaller  ``diversified"  background stress is offset by an increase in systemic stress.
+Also the diversified probability of Basel default is higher than the debt weighted average.
+
+Stress readings  alter dramatically when moving to November 2014 -- there is virtually no stress in any bank and the small amount of  stress in the system is diversifiable.
+Most of the  background stress is carried by NAB with lesser contributions by BEN and aba.
+All the stress in the minor bank ABAis background stress as only NAB and NAB have substantial systemic stress contributions.
+Again, however, it must be emphasised that there is minimal systemic stress in the system.
+Only ABAhas substantial Basel default probability, but this bank is a small player in the Australian banking scene.
+Notice total debt in the banking sector  jumps about 35\% between the two dates.
+
 \begin{comment}
@@
 
- \section{Further generalised stress functions}\label{genstress}
+ \section{Generalised stress functions}\label{genstress}
 
@@
 
-\newpage
+\bigskip
+\begin{center}
+{\large\bf SUPPLEMENTARY MATERIAL}
+\end{center}
 
@@
 The first three terms in the final expression are unrelated to stress $\phi$: stress only impacts the last term.
-
-Can easily determine all terms via simulation.
 
@@
 
-\section*{References}
+\section{Submission guidelines}
+
+\begin{itemize}
+\item In the latex source, near the top of the file the command
+\verb+\newcommand{\blind}{1}+ can be used to hide the authors and
+acknowledgements, producing the required blinded version.
+\item If you have supplementary material (e.g., software, data, technical
+proofs), identify them in the section below.  In early stages of the
+submission process, you may be unsure what to include as supplementary
+material.  Don't worry---this is something that can be worked out at later stages.
+\end{itemize}
+
+\begin{description}
+
+\item[Title:] Brief description. (file type)
+
+\item[R-package for  MYNEW routine:] R-package ÒMYNEWÓ containing code to perform the diagnostic methods described in the article.
+The package also contains all datasets used as examples in the article.
+(GNU zipped tar file)
+
+\item[HIV data set:] Data set used in the illustration of MYNEW method in Section~ 3.2. (.txt file)
+
+\end{description}
+
 \bibliography{piet2}
-
 \end{document}

### 2015-06-04 srisk6.tex
pdj changes

@@
   \begin{center}
-    {\LARGE\bf Title}
+    {\LARGE\bf Measuring background and systemic risk using financial time series}
 \end{center}
@@
 \noindent%
-{\it Keywords:}  3 to 6 keywords, that do not appear in the title
+{\it Keywords:}  Capital shortfall, background risk, Basel put, stressed expectation.
 \vfill
@@
 $$
-\Es(\e^{\nu_{it}})\ge\e^{\ell_{it}}\ .
+\ell_{it}\le \ln\Es(\e^{\nu_{it}})\ .
 $$
@@
 Examples of $\phi$ implying various stress calculations are shown in subsequent sections.
-Weighted expectations in the form of \eref{formula} are discussed in \cite{choo2010determining} and \cite{furman2008weighted1}.
+Weighted expectations of the form of \eref{formula} are discussed in \cite{furman2008weighted1} and \cite{choo2010determining}.
 
@@
 An increase in $\mu_{it}$ indicates either higher probabilities of defaults or larger capital shortfalls if defaults occur.
-Introducing systemic stress $s_{it}$ increases stress-sensitivity in two ways.
+Introducing systemic stress $s_{it}$ increases stress--sensitivity in two ways.
 Firstly adverse scenarios are emphasized which would otherwise be less obvious in $\mu_{it}$.
@@
  Basel log--leverage $\ell_{it}$ and debt $\pi_{it}\equiv d_{it}/d_t$ (as a proportion of total debt) for each of the banks.
-Six of the eight banks were in Basel default with positive capital shortfalls as indicated in by the $\ell_{it}$ column:   the two banks not in Basel default were WBC and aba.
+Six of the eight banks were in Basel default with positive capital shortfalls as indicated by the $\ell_{it}$ column:   the two banks not in Basel default were WBC and ABA.
 Background and systemic stress
@@
 $$
-for the banks as well as the probability of a Basel default in one month $q_{it}$ and the proportion $\pi_{it}$ of total debt are displayed in the next 3 columns.
+for the banks as well as the probability $q_{it}$ of a Basel default in one month are displayed in the next 3 columns.
 The background stress column indicates most of the background stress arises from NAB -- almost 40\% of the total.
@@
 Stress readings  alter dramatically when moving to November 2014 -- there is virtually no stress in any bank and the small amount of  stress in the system is diversifiable.
-Most of the  background stress is carried by NAB with lesser contributions by BEN and aba.
-All the stress in the minor bank ABAis background stress as only NAB and NAB have substantial systemic stress contributions.
+Most of the  background stress is carried by NAB with lesser contributions by BEN and ABA.
+All the stress in the minor bank ABA is background stress as only NAB and NAB have substantial systemic stress contributions.
 Again, however, it must be emphasised that there is minimal systemic stress in the system.
-Only ABAhas substantial Basel default probability, but this bank is a small player in the Australian banking scene.
+Only ABA has substantial Basel default probability, but this bank is a small player in the Australian banking scene.
 Notice total debt in the banking sector  jumps about 35\% between the two dates.
@@
 
-This paper develops an approach to measure systemic risk using the concept of stressed expectations are which akin to stress testing widely used in practice.
+This paper develops an approach to measure systemic risk using the concept of stressed expectations which formalise stress testing widely used in practice.
 Systemic stress adds to background stress which is the value of default puts on firms.
@@
 
-\section{Submission guidelines}
-
-\begin{itemize}
-\item In the latex source, near the top of the file the command
-\verb+\newcommand{\blind}{1}+ can be used to hide the authors and
-acknowledgements, producing the required blinded version.
-\item If you have supplementary material (e.g., software, data, technical
-proofs), identify them in the section below.  In early stages of the
-submission process, you may be unsure what to include as supplementary
-material.  Don't worry---this is something that can be worked out at later stages.
-\end{itemize}
-
-\begin{description}
-
-\item[Title:] Brief description. (file type)
-
-\item[R-package for  MYNEW routine:] R-package ÒMYNEWÓ containing code to perform the diagnostic methods described in the article.
-The package also contains all datasets used as examples in the article.
-(GNU zipped tar file)
-
-\item[HIV data set:] Data set used in the illustration of MYNEW method in Section~ 3.2. (.txt file)
-
-\end{description}
-
 \bibliography{piet2}

### 2015-06-04 srisk6.tex
pdj changes

@@
 \ee
-where $\overline\mu_{t}=\Exd(\mu_{it})$ and $\overline s_{t}=\Exd(s_{it})$ are overall background and systemic stresses, respectively.
+where $\overline\mu_{t}\equiv\Exd(\mu_{it})$ and $\overline s_{t}\equiv\Exd(s_{it})$ are overall background and systemic stresses, respectively.
 The put $\overline p_t$ in \eref{nsrisk} pays out zero if all firms are Basel compliant with payouts increasing with the number and size of Basel breaches.
@@
 $$
-Percentage contributions of firm $i$ to background and systemic stresses are
-$$
-\frac{\pi_{it}\mu_{it}}{\overline \mu_t} \equiv \pi_{it}\frac{\mu_{it}}{\Exd(\mu_{it})}\cq \frac{\pi_{it}s_{it}}{\overline s_t} \equiv \pi_{it} \frac{s_{it}}{\Exd(s_{it})}\ .
-$$
+Proportionate contributions of firm $i$ to background and systemic stresses are
+\be{standardised}
+\mu_{it}^*\equiv \frac{\pi_{it}\mu_{it}}{\overline \mu_t} \cq s_{it}^*\equiv\frac{\pi_{it}s_{it}}{\overline s_t}\ .
+\ee
 where $\pi_{it}\equiv d_{it}/d_t$ as before is the proportion of total debt held by firm $i$.
@@
 Six of the eight banks were in Basel default with positive capital shortfalls as indicated by the $\ell_{it}$ column:   the two banks not in Basel default were WBC and ABA.
-Background and systemic stress
-$$
-\mu^*_{it} \equiv \frac{\pi_{it}\mu_{it}}{\Ex_d(\mu_{it})}\cq s^*_{it} \equiv \frac{\pi_{it}s_{it}}{\Ex_d(\mu_{it})}\ , 
-$$
+Percentage background and systemic stress as defined in \eref{standardised}
 for the banks as well as the probability $q_{it}$ of a Basel default in one month are displayed in the next 3 columns.

### 2015-06-04 srisk6.tex
pdj changes

@@
 
-\section{Systemic risk -- SRISK}\label{srisk}
+\section{SRISK and systemic risk}\label{srisk}
 
@@
 
-\section{Estimating background and systemic stress via simulation}\label{estimate}
+\section{Background and systemic stress via simulation}\label{estimate}
 
@@
 
-\section{Simulating future capital shortfall and market return}\label{simulate}
+\section{Forward capital shortfall and  return simulations}\label{simulate}
 
@@
 \begin{center}
-\label{default}
 \includegraphics{figures/default.pdf}
 \caption{Forecast one month ahead  Basel default probability (top panels), background stress (middle panels) and systemic stress (bottom panels) for  four major (left panel) and four minor (right panel)  banks from the beginning of 2003 through to end of 2014.
-Note different scale on bottom two rows of panels.}
+Note different scale on bottom two rows of panels.}\label{default}
+
 \end{center}
@@
 \begin{center}
-\label{muqs}
 \includegraphics{figures/muqs.pdf}
@@
 In all cases there is no total stress until there is an appreciable level of average stress.
-Systemic stress $\overline s_t$ appears to be the least diversifiable.}
+Systemic stress $\overline s_t$ appears to be the least diversifiable.}\label{muqs}
 \end{center}
@@
 System compliance is partially monitored with the system put $\overline p_t=\Exd(p_{it})$ and its stressed expectation $\Es(\overline p_t)$.
-However both quantities are before diversification and gives no indication of system resilience and as to how much risk can be diversified away.
+However both quantities are before diversification and give no indication of system resilience and as to how much risk can be diversified away.
 Basing a put on system wide aggregated debt and equity and comparing the same to $p_t$  gives at least some guidance.
@@
 
-\section{Computations}
-
-All model fits in this paper have been performed with the R language \citep{R-Development-Core-Team:2008aa} and in particular the rmgarch package described by \cite{ghalanos2012rmgarch}.
-All other calculations were performed using the J language \citep{iverson2003j}.
-
-In the forward simulated forward projections the  innovations are chosen randomly from past innovations.
-These past innovations are chosen consistently:  at a particular $t$ either all or none of $\eps_{it}$ are chosen.
-
 \section{Proof of system put is less   than debt weighted average put}\label{proof}
-
+Since
 $$
@@
 
+\section{Computations}
+
+All model fits in this paper are performed with the R language \citep{R-Development-Core-Team:2008aa} and in particular the rmgarch package described by \cite{ghalanos2012rmgarch}.
+All other calculations are done in the J language \citep{iverson2003j}.
+
+In the forward simulated forward projections the  innovations are chosen randomly from past innovations.
+These past innovations are chosen consistently:  at a particular $t$ either all or none of $\eps_{it}$ are chosen.
+
 \bibliography{piet2}

### 2015-06-05 srisk7.tex
GL changes
GL changes in srisk7

--- 2015-06-04 srisk6.tex
@@
     and \\
-    Geoff Loudon\\
+    Geoffrey Loudon\\
     Department of Applied Finance and Actuarial Studies, Macquarie University\\
@@
 An important example is the SRISK measure due to \cite{brownlees2015} -- an index that measures the expected capital shortfall of a financial institution conditional on a large and lengthy decline in equity markets.
-\cite{brownlees2015} show the practical usefulness of their measure in three ways: (i) SRISK rankings identify systemically risky US banks during the global financial crisis [GFC]; (ii) pre-crisis SRISK helps predict capital injections by the Fed Reserve; (iii) aggregate SRISK provides early warning of declines in industrial production and higher unemployment.
+\cite{brownlees2015} show that their SRISK based measures are able to identify systemically important financial firms and are informative about the impact of financial crises on future macro-economic conditions.
 
@@
 While they condition on the event of a severe market downturn, we take the stressed expectation of the put value.
-This eNABles us to capture the impact of increased return volatility due to stress.
+This enables us to capture the impact of increased return volatility due to stress.
 Second, we decompose their SRISK measure into background stress and imposed system stress.
@@
 We suggest that it is also helpful to specify conditional behaviour in percentile terms relative to current market conditions.
-This provides a sharper focus on the incremental impact of further stress and allows us to draw stronger implications of SRISK numbers.
+This provides a sharper focus on the incremental impact of further stress and allows us to draw stronger implications from SRISK numbers.
 These extensions provide additional insights into the sources and economic nature of systemic risk.
@@
 In Australia there are four major banks that hold 78\% of the total assets of all Authorised Deposit-taking Institutions in  Australia.\footnote{Based on balances at 31 December 2014 disclosed in APRA's Quarterly Authorised Deposit-taking Institution [ADI] Performance Report for March 2015.} It is therefore obvious that the four majors are systemically important and the remaining ADIs are not so unless stress in one of these minors somehow creates financial contagion to the majors, in an unforeseeable way.
-Second, the Australian banking system proved to be resilient through the recent GFC, implying that systemic risk did not reach the extreme levels experienced by other countries where bank failures occurred.
+Second, the Australian banking system proved to be resilient through the recent global financial crisis [GFC], implying that systemic risk did not reach the extreme levels experienced by other countries where bank failures occurred.
 Both these features of the Australian system suggest that it may be difficult to find useful additional information about systemic risk by refining quantitative measures like SRISK.
@@
 
-To illustrate the nature and usefulness of our measures, we use publicly available daily financial data for the eight Australian banks detailed in \tref{eightbanks} spanning the period from  3 April 2000 through to 1 December 2014.
+To demonstrate the nature and usefulness of our measures, we use publicly available daily financial data for the eight Australian banks detailed in \tref{eightbanks} spanning the period from  3 April 2000 through to 1 December 2014.
 The data is described in detail in \aref{data}.
@@
 \cite{Giglio2015} supply empirical evidence on the ability of many of these measures, both individually and collectively, to provide early warning signals of deterioration in macro-economic conditions.
-In this section, we provide a selective overview of the measures most closely related to SRISK and its relevance for assessing systemic risk in the financial sector.
-
-The genesis of SRISK lies in a series of papers including \cite{acharya2012capital}, \cite{acharya2012measuring} and \cite{brownlees2010volatility}.
+In this section, we provide a selective overview of those measures most closely related to SRISK and its relevance for assessing systemic risk in the financial sector.
+
+The genesis of SRISK lies in a series of papers including \cite{acharya2012aer}, \cite{acharya2012wp} and \cite{brownlees2010volatility}.
 In these papers, SRISK is defined as the expected capital shortfall of a financial firm, conditional on a crisis.
 A crisis is deemed to occur whenever a relevant market index suffers a significant decline over a chosen horizon.
-\cite{Benoit2013} show how several popular systemic risk measures including MES and SRISK are transformations of market risk measures and derive conditions under which these measures provide similar rankings of systemically important financial institutions.
-
-\cite{brownlees2015} develop SRISK. [***** to add a fuller description of this paper given it is the key paper for our work]
+SRISK measures require an estimate of the long run marginal expected shortfall [LRMES] which is typically obtained by simulation methods.
+
+\cite{brownlees2015} further develop the empirical methodology to construct SRISK measures.
+SRISK depends on the firm's size, leverage and its LRMES.
+The LRMES is obtained by assuming a dynamic process for the joint distribution of firm and market returns.
+\cite{brownlees2015} use  the standard GARCH-DCC model of \cite{engle2002dynamic} with threshold ARCH volatilities on the basis that this represents a good trade-off between model complexity and prediction accuracy.
+The LRMES is computed as the Monte Carlo average of simulated multi-period returns,  conditional on the return being worse than the cut-off level chosen to identify a financial crisis.
+Using a sample of large US financial firms,  \cite{brownlees2015} show the practical usefulness of their measure in three ways: (i) SRISK rankings identify systemically risky US banks during the GFC; (ii) pre-crisis SRISK helps predict capital injections by the Fed Reserve; (iii) aggregate SRISK provides early warning of declines in industrial production and higher unemployment.
 
 \cite{Engle2015} extend the model in \cite{brownlees2015} to incorporate global, country and industry effects.
-This extended model makes effective use of \cite{Engle2014dcb} dynamic conditional model.
-Their empirical methods are able to provide information of the relative systemic importance of industry type and country identity.
+This extended model makes effective use of \cite{Engle2014dcb}'s dynamic conditional beta model.
+Their empirical methods are able to provide information about the relative systemic importance of industry type and country identity.
+For instance, they find  that systemic risk in Europe during the GFC was predominantly due to banks while France and the UK recorded the largest country-level SRISK numbers.
 
@@
 \cite{Girardi2013} improve CoVaR by conditioning on the institution being at most at its VaR.
-This generalisation is useful as it takes into account severity of tail losses and facilitates back-testing of CoVaR.
+This generalisation is useful as it takes into account the severity of tail losses and facilitates back-testing of CoVaR.
+
+\cite{acharya2012aer} relate SRISK and CoVaR and demonstrate that assuming the joint distribution of returns is conditionally normal, SRISK is a more complete measure.
+\cite{Benoit2013} show how several popular systemic risk measures including MES, CoVaR and SRISK are different transformations of market risk measures and derive those conditions under which they provide similar rankings of systemically important financial institutions.
 
@@
 Many of these papers use \cite{engle2002dynamic}'s GARCH-DCC model aiming to capture the time-varying dynamics of the return (co)variances in a feasible manner.
-While we also use this model in our empirical analysis, we emphasize that our approach can utilise any appropriate model for simulating the joint distribution of forward firm and market returns.
+While we also use this model in our empirical analysis, we emphasize that our approach can utilise any appropriate model for simulating the joint distribution of firm and market returns going forward.
 
@@
 The bottom $\alpha$ of market returns is further stressed by  progressively overweighing returns as the percentile approaches 0.
-Large simulation effort $N$ is required for a reasoNABle approximation since $N/c$ is the effective simulation size and $c$ is small.
+Large simulation effort $N$ is required for a reasonable approximation since $N/c$ is the effective simulation size and $c$ is small.
 

### 2015-06-05 srisk7.tex
pdj changes

@@
 
-Our paper refines and extends the model of \cite{brownlees2015} in several interesting and important ways.
+Our paper refines and extends the model of \cite{brownlees2015} in several  ways.
 First, we reinterpret their SRISK measure as a put on the expected shortfall using stressed expectation.
@@
 The red horizontal line in each panel indicates the Basel limit:  any firm return less than the limit would constitute a Basel breach.
-In the left panel there is little confidence that the Basel limit will be reached since it requires a return on equity approaching 20\% -- with confidence less than xxx the Basel standard will be breached.
+In the left panel there is little confidence that the Basel limit will be reached since it requires a return on equity approaching 20\%.
 In the right panel there is no chance of a Basel breach under any of the projected return on equity view -- the bank is ``safe."

### 2016-10-09 jbes/JBES submission/Respones to referees.tex
Lots and lots of changes
Latest

\documentclass[11pt]{amsart}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}

\newcommand{\eps}{\epsilon}
\newcommand{\var}{{\rm var}}
\newcommand{\cov}{{\rm cov}}
\newcommand{\nid}{{\rm NID}}
\newcommand{\diag}{{\rm diag}}
\newcommand{\E}{{\mathrm E}}
\newcommand{\R}{{\mathrm R}}
\newcommand{\RD}{{\tilde{\mathrm R}}}
\newcommand{\Q}{{\mathrm Q}}
\newcommand{\U}{{\mathrm U}}
\newcommand{\Ex}{{\cal E}}
\newcommand{\cor}{\mathrm{cor}}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\e}{\mathrm{e}}
\newcommand{\de}{\mathrm{d}}
\newcommand{\p}{\mathrm{P}}
\newcommand{\Ln}{\mathrm{Ln}}
\newcommand{\sign}{\mathrm{sign}}

\newcommand{\Es}{\widetilde\E}

\newcommand{\ra}{\varrho}

\newcommand{\minn}{\mathrm{min}_n}
\newcommand{\maxn}{\mathrm{max}_n}

\newcommand{\cq}{\ ,\quad }
\newcommand{\qq}{\quad \Rightarrow \quad}
\newcommand{\oq}{\quad \Leftarrow \quad}
\newcommand{\eq}{\quad \Leftrightarrow \quad}

\newcommand{\br}{\ensuremath{\mathrm{BRISK}}}
\newcommand{\pr}{\ensuremath{\mathrm{PRISK}}}

\newcommand{\ppo}[1]{|{#1}|^+}

\newcommand{\ssection}[1]{%
  \section[#1]{\textbf{\uppercase{#1}}}}
\newcommand{\ssubsection}[1]{%
  \subsection[#1]{\normalfont\textbf{#1}}}

%\renewcommand{\labelenumi}{(\roman{enumi})}

\newcommand{\eref}[1]{(\ref{#1})}
\newcommand{\fref}[1]{Figure \ref{#1}}
\newcommand{\sref}[1]{\S\ref{#1}}
\newcommand{\tref}[1]{Table \ref{#1}}
\newcommand{\aref}[1]{\ref{#1}}

\newcommand{\bi}{\begin{itemize}}
\renewcommand{\i}{\item}
\newcommand{\ei}{\end{itemize}}

\newcommand{\es}{{\mathrm{ES}}}
\newcommand{\ses}{{\mathrm{SES}}}
\newcommand{\sr}{{\mathrm{SR}}}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Response to referees}
\author{The Author}
%\date{}                                           % Activate to display a given date or no date

\begin{document}
\maketitle
\section{Responses to the first referee}

Referee comments are reproduced in italics.  The order of the comments below are the same as those of the referee.

\begin{enumerate}
\item {\it The main contribution of this paper is to re-interpret SRISK as a put.}

We apologise  and accept our responsibility for misleading the referee into this mistaken conclusion.  SRISK is deconstructed, the parts  reconfigured, rebuilt and extended.    The implications of using $S^+$ (the payoff of a ``put") as opposed to $\{\E(S)\}^+$  appears critical and significant -- see the revised manuscript.  Using  $S^+$ emphasises the measurement of upper tail risk (see below) and leads to the distinction between baseline risk (BRISK) and psi risk (PRISK) as set out below.   The reconstruction has implications for risk aggregation, diversification and contagion.

\item  {\it Within this setting, the paper provides various, mostly theoretical definitions what can be done with this re--interpretation of SRISK. The literature behind those measures is actuarial ... and may not be familiar to the audience at large.}

Again we apologise for making the referee think the contributions are theoretical and  a reinterpretation of existing measures.  Our reconstructed measures  are implemented, applied  and analysed  in the empirical sections of the paper.

\item {\it ... to define SRISK in terms of a put, hardly seems to be a refinement.}

Please see above.  Again we accept full responsibility for leading the referee to this mistaken conclusion.

\item {\it `we take the stressed expectation of the put value.' First of all, this does not tell the regulator why this measure is important for him. Second, in a purely mathematical sense, the value of a put is a positive real number - a price. Taking a stressed expectation of such a number is meaningless. Do you mean: we take the stressed expectation of an expression which is alike the payoff of a put?}

 $\Es(S^+)$ focussed on the practically important  upper tail risk.   $\{\Es(S)\}^+$ potentially ``averages out" upper tail risk (of critical importance) with lower tail risk (of no direct interest to the regulator).  Using $\Es$ instead of $\E$ emphasises interest is under adverse scenarios.   $\Es$ generalises and includes the concept of conditional expectation given a crisis typically used  in the literature and mentioned by the referee.

We agree with the referee that a more precise statement is the  
the ``expectation of the put payoff value" rather than the ``expectation of the put."   Potentially misleading terminology has now been removed from the manuscript.

\item {\it please render the abstract comprehensible to an economic and finance audience and explain in intuitive words what you are doing and not by referring to possible unknown concepts.}

Have made the abstract more explicit and comprehensible.

\item {\it it would have been nice to have a comparison with say American firms.}

Ok agree with this.

\item {\it the paper makes the same counterfactual assumption as the literature that in case of a stress a bank has constant debt.}

Our assumption is as in \cite{brownlees2015} where it is argued as reasonable over a monthly horizon.   To change this would be to depart from the literature and make comparisons more intricate and difficult.

\item {\it is assumed that the prudential parameter 8\% is the same for all firms. Banks with riskier asset structure should have a different ? than banks with relatively safe investments. This should be incorporated too.}

This is a good point and is now emphasises  in the revised version.   Alternatively a final section makes explicit the connection the  Risk weighted asset  methodology.

\item {\it There are sentences which are hard to understand.}

Ok, agree with this

\item {\it We decompose SRISK into background stress and imposed system stress. ... However, since both components are not defined it is sort of hard to follow what is meant in the following discussion.}

Our presentation has  misled the referee into thinking ``both components not defined".     Baseline risk (previously called background risk) is explicitly defined as $\E(S^+)$.   Imposed system stress (now called psi--risk or PRISK) is explicitly defined as  $\Es(S^+)-\E(S^+)$
where $\Es$ is expectation under stress and explicitly defined with respect to a stress factor $\psi$.

\item {\it ... sharper focus on the incremental impact of further market conditions. ... This promise is not really fulfilled.}

Maybe this is correct

\item {\it ... what matters to the regulator and the taxpayers is the actual amount that the firm would need and not the risk neutral one. Also, since there is no duplication strategy, markets are not complete, it is not clear that even if one were to price a put in a finance sense that to go risk neutral is the right thing to do.}

This expands on the previous misunderstanding of put versus put value.   Note that the referee particularly refers to the ``actual amount that the firm would need"  ie.  $S^+$ (rather than $S$).   While the point is a tangential one, markets could be allowed to price $S^+$.   We agree that risk neutral valuation would require a complete market which is not at least immediately available in this context.  However the ``put" interpretation is tangential to our development and has now been downplayed.

\item {\it Use the same notations for capital shortfall (formula (1) etc, as
in Brownlees and Engle, 2010, 2015). This would really simplify reading the paper for someone with knowledge of the earlier literature.}

Have simplified notation as far as possible to make it align with that in the existing literature.

\end{enumerate}

\newpage
\section{Second referee}

 {\it The authors deal with an important and timely topic.  However there are  a number of concerns}
\begin{enumerate}
\item {\it ... not clear to me what is the value added of the paper. Yes, the generalisation of the framework provided by the authors makes a lot of sense. I like for instance the decomposition in section 7 of background and systemic stress. However, it is not clear to me what is the significant value added of the refinement carried out by the authors. I do not find this clearly explained in the manuscript.}

We are grateful for the author for pointing out the inadequacies in the previous presentation and have used his comments to make the contribution much more evident and transparent.   Please see the revised submission.  In particular we have stripped out all extraneous material, notation and in particular subscripting and have introduced an explicit section formalising stress testing.

\item  {\it authors could have validated the methodology put forward in this paper by comparing it empirically with other approaches out there (including SRISK and CoVaR).}

At this stage we have confined ourselves to developing, as rigorously as possible the theory and application and have contrasted the theory with that in the two other mentioned approaches.

\item  {\it ... the empirical application is quite limited in scope.}

\item {\it ...  There is no attempt to validate empirically the usefulness of the proposed approach.}

We apologise for having led the referee to this misunderstanding.   The aim of the empirical work in the paper is to validate the approach on a tight, albeit limited, dataset to illustrate the usefulness of the techniques.    We have used his comment and set about to improve the empirical validation.  Please see the revised manuscript.

\item {\it ...  there is no attempt to show that the approacj pushed forward in this work is better than standard SRISK methodology.}

In the revised manuscript we have more clearly delineated the pitfalls of SRISK:  namely the focus on $\{\Es(S)\}^+$ rather than 
$\Es(S^+)=\E(S^+)+\pr(S^+)$.  The former SRISK measure is defective, it is argued on the following grounds:
\begin{enumerate}
\item  The measure $\{\Es(S)\}^+$ does not effectively measure the tail risk associated with $S$ since it ``averages" out the tails.  Our measure uses $S^+$ which is responsive to (positive) tail risk.

It is worthwhile to examine the SRISK definition $\{\Es(S)\}^+$ and compare it to $\Es(S^+)$.  The former averages over positive and negative shortfalls treating either extreme equivalently.   So heightened volatility will not affect even though the risk of a damaging shortfall may be dramatically increased.    With $\Es(S^+)$ the focus is firmly on the damaging part of the distribution.   Next, when considering stressed expectation we have 
$$
\{\Es(S)\}^+ = \{\E(S) + \pr(S)\}^+
$$
In other words a high value suggests both $\E(S)$ and $\pr(S)$ are large.  
\item  The stressed expectation $\Es$ in SRISK is specialised.   In our presentation it is generally defined with respect to any stress $\psi$.
\item  The stressed expectation $\Es$ is made up of two components which have differing interpretation:  baseline risk unrelated to stress per se, and psi-risk (PRISK) defined solely in terms of $\psi$.  
\end{enumerate} 
\item {\it ... understand the authors want to focus on the case of Australia. However, I would be inclined to think that systemic risk measures are interesting for the pre-screening ?large? financial systems (say hundreds of financial institutions). It is unclear to me how systemic risk measures are useful for monitoring a system in which it is already know that there are very few core banks only.}

We agree with this comment.   However we were particularly concerned to initially implement and study the tools in the context of a more strictly defined setting.   We agree the next logical step is, given the demonstrated effectiveness of the tools, for more large scale bank and financial institution screening as in the richer data setting of the US or Europe. 
\item {\it This paper is not really about statistics/econometrics. In a way, an appropriately revised version of the paper could find a better fit in a finance journal.}
\item  {\it Too many sections. Methodological part and empirical parts are presented in scattered order.}

We agree and have radically cut down the number of sections.
\end{enumerate}
\newpage

\end{document}

### 2016-10-09 CIFR industry paper - FIRN.tex
Lots and lots of changes
Latest

\documentclass[authoryear]{elsarticle}

%\pagenumbering{gobble}

\usepackage{threeparttable}
\usepackage{caption}
\captionsetup[table]{skip=0pt}

\makeatletter
\def\ps@pprintTitle{%
\let\@oddhead\@empty
\let\@evenhead\@empty
\def\@oddfoot{}%
\let\@evenfoot\@oddfoot}
\makeatother

\setlength\arraycolsep{2pt}
\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}
\usepackage{graphicx}

\usepackage{amsfonts}
\usepackage{multirow}
\usepackage{comment}

%hello there
%\usepackage{chicago}
\bibliographystyle{chicago}

\newcommand{\eps}{\epsilon}
\newcommand{\var}{{\rm var}}
\newcommand{\cov}{{\rm cov}}
\newcommand{\nid}{{\rm NID}}
\newcommand{\diag}{{\rm diag}}
\newcommand{\E}{{\mathrm E}}
\newcommand{\R}{{\mathrm R}}
\newcommand{\RD}{{\tilde{\mathrm R}}}
\newcommand{\Q}{{\mathrm Q}}
\newcommand{\U}{{\mathrm U}}
\newcommand{\Ex}{{\cal E}}
\newcommand{\cor}{\mathrm{cor}}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\e}{\mathrm{e}}
\newcommand{\de}{\mathrm{d}}
\newcommand{\p}{\mathrm{P}}
\newcommand{\Ln}{\mathrm{Ln}}
\newcommand{\sign}{\mathrm{sign}}
\newcommand{\sref}[1]{Section \ref{#1}}

\newcommand{\ra}{\varrho}

\newcommand{\minn}{\mathrm{min}_n}
\newcommand{\maxn}{\mathrm{max}_n}

\newcommand{\cq}{\ ,\quad }
\newcommand{\qq}{\quad \Rightarrow \quad}
\newcommand{\oq}{\quad \Leftarrow \quad}
\newcommand{\eq}{\quad \Leftrightarrow \quad}

\newcommand{\be}[1]{\begin{equation}\label{#1}}
\newcommand{\ee}{\end{equation}}

\newcommand{\ppo}[1]{|{#1}|^+}

\newcommand{\ssection}[1]{%
  \section[#1]{\textbf{\uppercase{#1}}}}
\newcommand{\ssubsection}[1]{%
  \subsection[#1]{\normalfont\textbf{#1}}}

%\renewcommand{\labelenumi}{(\roman{enumi})}

\newcommand{\eref}[1]{(\ref{#1})}
\newcommand{\fref}[1]{Figure \ref{#1}}
\newcommand{\tref}[1]{Table \ref{#1}}
\newcommand{\aref}[1]{\ref{#1}}

\newcommand{\bi}{\begin{itemize}}
\renewcommand{\i}{\item}
\newcommand{\ei}{\end{itemize}}

\newcommand{\sr}{\ensuremath{\mathrm{SRISK}}}
\newcommand{\br}{\ensuremath{\mathrm{BRISK}}}
\newcommand{\pr}{\ensuremath{\mathrm{PRISK}}}

\newcommand{\Es}{\ensuremath{\widetilde\E}}

\newcommand{\es}{{\mathrm{ES}}}
\newcommand{\ses}{{\mathrm{SES}}}

\begin{document}

\begin{frontmatter}

\title{An early warning tool for measuring the build up of systemic risks in banks and financial systems}

\begin{abstract}
This paper develops, analyses and implements an early warning tool for  systemic risk in banks and financial entities. The tool is based on a refined approach to stress testing. Calculations performed on Australian bank data are shown to predict past distres. Risk is measured as  a function of expected capital shortfall in individual firms. A simple model of regulatory capital is assumed. Systemic risk is shown to be driven by the size and leverage of balance sheets and interdependence between firms.  Firm balance sheets are modelled using publicly available information and assumed to depend on market returns. Model refinements using more comprehensive information and practical implementation are also discussed.

\end{abstract}

\end{frontmatter}

\newpage

\section{Systemic risk and stress testing}\label{sreview}
%This section gives an overview of the industry view of systemic risk and stress testing

Systemic risk is the risk of a system-wide loss or failure, and is inherent in the financial industry due to firms with large, leveraged and interrelated balance sheets. The impact of systemic risk was felt
 during the 2008 global financial crisis (GFC) where the housing market downturn and Lehman Brothers failure triggered crisis in other financial firms and the global economy. The crisis was caused, amongst  other factors, by financial firms relying on one another and the state of the economy to sustain highly leveraged financial positions via the use of derivatives. The Lehman Brothers  failure directly or indirectly affected others. See \cite{kolb2010lessons} for a discussion of the 2008 global financial crisis.

Drivers of systemic risk are:
\begin{enumerate}

\i Financial dependence between firms
\i Dependence of individual firms  on common macroeconomic factors and market conditions
\i Proportionally large balance sheets of key  individual firms
\i High leverage with debt  many times the value of net assets

\end{enumerate}

Industry stress tests for banks conducted in 2010, 2012 and 2014 by the Australian Prudential Regulation Authority (APRA), and a recent exercise for life insurers, demonstrate the regulator's concern with the presence and extent of systemic risk in the financial industry. Stress testing examines the impact of a set of adverse assumptions or scenarios on the financial position of a firm. For the most recent banking stress test, interest rates and unemployment rates were assumed to increase over a prolonged period, resulting in a series of losses particularly from credit defaults.

Industry stress testing is an effective systemic risk measurement tool for two reasons. Firstly, balance sheets at face value do not apparently indicate the level of systemic risk. Two balance sheets may look similar but diverge significantly when a stress is applied, due to differences in business profile or the nature of assets and liabilities held. For example the loan portfolio of a bank may be diversified across Australia and overseas, whereas the same for another bank may be concentrated in a particular state or industry in Australia. A systemic stress is likely to have a far larger impact on the latter. Secondly, applying common adverse assumptions to all firms, rather than having firms select their own assumptions, leads to a realistic impact analysis of a market downturn.

Apart from industry stress testing, APRA imposes a set of prudential standards for financial firms to manage their solvency. Relevant standards relate to capital management: APS 110, GPS 110 and LPS 110 for banks, general insurers and life insurers, respectively, and risk management: CPS 220 for all financial firms. Specific requirements which are relevant to this paper are:
\bi

\i Using stress and scenario testing to identify and manage key risks. This is in addition to above industry stress tests.

\i Setting a risk appetite statement including a limit on the probability or extent of default, and monitoring the adherence to the limit.

\i Capital requirements which reflect the volatility of assets and liabilities held and their mismatch.

\ei

Financial markets are increasingly globalised with large firms having a presence in most major markets. Managing systemic risk globally has led to the identification and additional regulation of systemically important banks and insurers. These banks and insurers are identified using a similar set of  factors as those described above: the size of the balance sheet, extent of leverage, links with the financial market, and the impact of stressed financial conditions.

\section{Contributions of this paper}
%This section highlights contributions of the paper and introduces the 8 banks used

This paper proposes and develops an approach to assess the extent of systemic risk in the market as a whole and in individual firms.  The approach models  the impact of a stress on default risk and expected capital shortfall. Specific contributions are:
\bi
\i The notion of systemic risk is formalised as increases in expected capital shortfall under stress.

\i Stress testing is enhanced by considering all possible scenarios rather than one or more specific scenarios.

\i Baseline risk is present in the system even without stress and is again based on expected capital shortfall.

\i A forward looking tool is proposed to continuously monitor baseline and systemic risks in the entire market and firm contributions.
\ei
Systemic risk defined in this paper reaffirms and formalises key drivers listed in the previous section: size, leverage and interdependence between balance sheets of individual firms. Calculations are performed on past Australian bank data which includes the 2008 GFC. Results show heightened systemic risk in the lead up to, and during, the 2008 GFC. In addition the extent of systemic risk at present is significantly higher compared to levels 10 or 20 years ago, arguably due to not only persistent turbulence in global financial markets but also increased connectivity between firms.

Throughout this paper a one--factor model of regulatory capital requirements is assumed across all firms. This assumption removes complications of capital requirements in practice which vary between firms and across banks, general insurers and life insurers. These complications are not central to the development of this paper. Refining the model to reflect capital requirements in practice leads to straightforward modifications of results in this paper.

Calculations of systemic risk in this paper enhance the recent SRISK approach in \cite{brownlees2015} and are akin to default put options discussed in \citet{merton1977analytic}, \citet{doherty1986price}, \citet{cummins1988risk}, \citet{myers2001capital} and \citet{sherris2006solvency}. In addition the refined stress testing approach follows the concept of probability distortion \citep{wang2000class}, weighted average loss \citep{choo2009loss} and yields covariance based results similar to those in \cite{ruhm2003risk} and \cite{choo2010determining}.

To demonstrate the nature and usefulness of the proposed framework, the methodology is applied to eight Australian banks detailed in \tref{eightbanks} using publicly available daily financial data spanning 3 April 2000 through to 1 December 2014.  Stock prices, adjusted for dividends, are plotted in \fref{prices}.  The data is described in detail in \aref{data}.  Stock prices are multiplied by the number of shares to derive total equity. Total debt for each firm at each point of time are derived from annual accounting reports.

\begin{table}[htbp]
\label{banks}\caption{Major and minor Australian banks}\label{eightbanks}
\begin{center}
\begin{tabular}{l|l||l|l}
\hline
 \multicolumn{2}{c||}{Major}& \multicolumn{2}{c}{Minor}\\
 \hline
CBA & Commonwealth   & MQG  & Macquarie \\
ANZ  & Australia \& New Zealand  & BOQ  &  Queensland\\
NAB  & National Australia  & BEN & Bendigo and Adelaide \\
WBC  & Westpac & ABA & Auswide \\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{figure}[htbp]
\begin{center}
\includegraphics{figures/prices.pdf}
\caption{Stock  prices of four major (left panel) and four minor (right panel) Australian banks from early 2000 through to the end of 2014.  Price series normalised to start at 1.}
\label{prices}
\end{center}
\end{figure}

Remaining sections are structured as follows. Sections  \aref{s_capmodel} and \aref{s_expshort} outline a simple model of current and future capital shortfall based on a one factor model of regulatory capital. Section \aref{s_forward} describes how future expected capital shortfall can be monitored by modelling balance sheets based on available information. The model is applied to remaining developments of this paper. Sections \aref{s_st}, \aref{s_sfactor}, \aref{s_extend} and \aref{s_stmarket}  discuss the shortcomings of current stress testing approaches and put forward enhancements which form the definition of systemic risk. Section \aref{s_formal} formalises the risk framework proposed in this paper by separating baseline risk and systemic risk and monitoring firm contributions and market totals. Further illustrations using Australian bank data are provided in section \aref{s_app}. Section \aref{s_concl} concludes this paper by discussing ways to improve the risk modelling and the associated practical challenges.

\section{Regulatory capital and capital shortfall}\label{s_capmodel}
%This section introduces the simplistic model of capital shortfall

Capital shortfall of a firm is the gap between available capital and the regulatory required amount. Write $d$ and $w$ as the debt and equity of a firm at a particular point in time. Then assets are $d+w$. Suppose $0<k<1$ is the regulatory capital requirement as a proportion of assets, capturing market, credit, insurance, operational and other risks.   Then the capital shortfall is
\be{shortfall0}
 S\equiv k\times\mathrm{assets} - \mathrm{equity} = k (d+w)-w = k d\left(1-\frac{1-k}{kL}\right)\cq L\equiv \frac{d}{w} \ ,
\ee
where $L$ is the leverage.  In many cases for banks $k$  is approximately 8\%, sometimes called the ``Basel" requirement.

A negative capital shortfall implies  there is capital surplus.   Hence the effective shortfall is  the positive part of $S$, denoted $S^+$ and  $S^+=0$  unless equity $w$ is less than the prudential fraction $k$ of assets $d+w$.

In practice there  may be additional adjustments to the prudential fraction such as those relating to intangible assets and liability surpluses. Firms usually need to maintain an equity buffer above the regulatory capital requirement and hence the true capital shortfall is higher than in \eref{shortfall0}. These adjustments are ignored to keep the model simple and tractable.

The following features of capital shortfall in \eref{shortfall0} reflect practice:
\bi

\i Shortfall $S$ increases with the prudential fraction $k$, debt $d$, and leverage $L$.

\i If  $k=1$ then $S^+=S=d$.  Further $k=0$ implies $S^+=0$.

\i $S^+$ exceeds zero if and only if $L>(1-k)/k$: leverage exceeds a threshold computed from the prudential fraction $k$.

\i As  leverage $L$ becomes large,  both $S$ and $S^+$ approach $k d$. Thus $kd$ is approximately the amount of capital required for a very highly leveraged firm.

\ei

\section{Future capital shortfall}\label{s_expshort}
%This section extends the previous section to consider future capital shortfall and its expectation

Firms and regulators are interested in future capital shortfall such as the shortfall of a bank in one month's time.   A projected shortfall, couched in terms of  probabilities, may lead to regulatory action.  If $r$ is the log--return on equity over the next period and debt $d$ stays fixed then  future leverage is $d/(\e^r w)= \e^{-r}L$ where $L$ is the current leverage.  Then the future shortfall is
\begin{equation}\label{shortfall1}
S \equiv k d  (1-\e^{r-\ell})\cq \ell\equiv \ln L + \ln\frac{k}{1-k}   \  ,
\end{equation}
where $\ell$ is called the adjusted log--leverage.   If $r=0$ then \eref{shortfall1} reduces to current shortfall.
The assumption of constant debt $d$ is reasonable if the period is small such as a month, but can be relaxed with the availability of more comprehensive data such as detailed debt or liability profiles.

If $S$ is unknown it may be simulated based on an assumed model and appropriate scenarios.     Distributions of simulated values mimicking actual probability distributions are based on ``best estimate assumptions" which are derived from available data and judgement without deliberate bias. Stressed probability distributions  introduce deliberate conservatism or biases and are discussed later.
This paper simulates one month ahead shortfalls $S$ in \eref{shortfall1} using  a stochastic model for $r$ fitted using publicly available stock returns for Australian banks.   The aim is to provide a monthly monitoring tool for the real time assessment of risks and particularly systemic risks in each bank and the banking system as a whole.

With $S$  as in \eref{shortfall1} write $S^+$ as the positive part of $S$ equivalent to  $kd$ times a put with strike 1.   A return $r$ less than $\ell$ implies a positive shortfall.   The put value increases  with the adjusted log--leverage   $\ell$ and the fraction margin $k$.       Volatility in the return $r$ and negative return tail risk  increase the expected put value.

\section{Forward looking risk assesment}\label{s_forward}

Assessing future shortfall  $S$  gives a picture of the risk faced by the bank.  Regulators such as APRA are interested in real time monitoring of likely values of $S$ across  financial firms. Upward trends in $S$ or $\E(S)$ caused by heightened levels of either debt, leverage or return volatility  suggest  greater required oversight.

This section displays one month ahead simulated values of $S$ and market return  using a joint model based on daily bank and market returns.   The market return captures  a common driver of individual bank returns and individual bank shortfalls and permits the assessment of risk to individual banks of say a major overall market correction.    Aggregating shortfalls across banks  under such a scenario leads to an understanding of systemic risk.   The approach has recently been advocated in  \cite{brownlees2015} where dependencies in different firms  future rates of return  are modelled  using a daily GARCH--DCC time series model fitted using historical (relative to each month)  daily stock prices and market returns with  model parameters updated  as additional data become available.   The GARCH--DCC model  \citep{engle2002dynamic} captures shifts in return volatility over time, an important characteristic of stock returns. The GARCH--DCC model also captures the well known market phenomenon of changes in correlation between individual and overall market returns over time.

 \fref{figCBA}   displays two snapshot outputs from  6000  simulated one month forward projected shortfall $S$ for  CBA and the return in the general market, on  two dates: the start of January 2009 and the start of December 2014.  Thus the projection is the return over the next month based on available data at the start of the month. The simulated points do not involve look--ahead bias as the model at each time point is based on the available data to that point in time.

    The two panels  display very different volatility and slopes. In January 2009 both $S$ and market return distributions are highly volatile and correlated. The correlation remains strong in December 2014 but with less return volatility. These snapshots are used to compute baseline and systemic stresses discussed in subsequent sections.

Based on the available data at the two points in  time, policy makers and regulators faced entirely different projections.      The  horizontal origin line in each panel indicates the Basel limit:  an $S$ value greater than the limit leads to a Basel breach.   In the left panel there is a high likelihood that the Basel limit will be breached.  In the right panel there is no chance of a Basel breach -- the bank is ``safe" under all market scenarios.

 The black dots in each panel indicate the actual outcome after one month in both the market return and the bank shortfall \eref{shortfall0}.    In the left panel the outcome is a decline in   the market and  a shortfall $S>0$.    In the right panel there is a market downturn and a slight  increase in $S$ although $S$ remains negative.    Thus at the beginning of January  2009 CBA was projected to be far from compliance at the end of the  month while in December 2014 the one month projection suggests complete compliance.

\begin{figure}[htbp]
\begin{center}
\includegraphics{figures/figCBA.pdf}
\caption{Forecast bivariate distribution of future shortfall $S$ per unit $kd$  for CBA (vertical axis) and market rate of return (horizontal axis) at start of January 2009 (left panel)  and December 2014 (right panel). Note scales in both panels are the same, the relatively large volatility in the left panel, and the left skew in the  marginal distributions.  Black dots indicate actual  outcome at the end of the month.}\label{figCBA}
\end{center}
\end{figure}

There is no look--ahead bias in the calculations:  at any point estimates are computed using a model fitted to information available at that time.  For example the $S$ distribution at the  end of August 2013 is computed using debt and leverage levels at the end of July 2013 and the probability distribution of August returns fitted using past returns up to end July.  The GARCH--DCC model is only one possible implementation and other time series models may be used if they are shown to be more appropriate.

\section{Monitoring shortfall in real time}\label{brisk}

Measures of expected future shortfall or baseline risk include
$$
\E(S) \cq \{\E(S)\}^+ \cq \E(S^+)= \p(S>0)\E(S|S>0)\ .
$$
The first, $\E(S)$, can be positive or negative while the second and third are nonnegative.   The second measure is used in \cite{brownlees2015} to define a quantity called  SRISK.  The plus superscript denotes the ``positive part of."  The final measure $\E(S^+)$ focusses on the average of positive shortfalls and is the measure used in this study.   As indicated $\E(S^+)$ decomposes into the probability of a positive shortfall times the expected size of the shortfall given it is positive.   These two latter measures can individually be used as measures of the risk of shortfall.

This section displays the results from analyses as in the last section but now for all 8 banks listed \tref{eightbanks} and for the start of  each month,  beginning in 2003 and ending December 2014.   Simulated one month forward returns are used to calculate the normalised actual shortfalls
$
S^+/(kd)
$.
 As in \cite{brownlees2015}, $k=0.08$ while $d$ is the debt and for the given bank at the given time.  Using $S^+/(kd)$ rather than $S^+$  facilitates comparison across banks and  time.

Results are displayed in the two  panels of \fref{defaulttop} displaying baseline risk $\E(S^+)$ for the major and minor banks. The first suggestion of material expected shortfall arose with NAB  in early 2008 followed one month later by ANZ , and a further few months later by WBC  and CBA. Expected shortfall subsided shortly after 2009, however NAB 's position deteriorated again in 2011 lasting until 2013.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=12cm]{figures/defaulttop.pdf}
\caption{Baseline risk $\E(S_i^+)$  for   major (left panel) and  minor (right panel)  banks 2003--2014.}\label{defaulttop}
\end{center}
\end{figure}

The  panels in  \fref{defaulttop} display baseline risk: that is risk without assuming or conditioning on a stressful event.   Conditioning on such events leads to stress testing discussed in the next section.

\section{Stress testing based on single adverse event}\label{s_st}

Regulators focus on downside risk and focus on  capital shortfall $S$ or $S^+$ using conservative rather than best estimate assumptions. As discussed above, stress testing imposes adverse scenarios and is an important tool to assess systemic risk. The following  discusses standard stress testing and the next section shows a refined approach to stress testing applied to  shortfall $S$ of the  previous sections.

Common stress testing techniques, including those prescribed by APRA in its industry stress tests, focus on a single adverse scenario $\omega$ and its impact, that is the conditional expectation $\E(S|\omega)$. For example the 2014 industry stress test for banks consisted of two scenarios, one of which assumed that Australia GDP would contract by $4\%$ in 2015 and only return to positive growth in 2017. Adverse scenarios were also imposed on interest rates and unemployment during the same period.

Consider
$
\E(S| \omega)$
where $\omega$ is the event of  a market return less than say $-10\%$.   Thus the shortfall calculations are conditional on the basis of a substantial market correction.   In terms of \fref{figCBA} the conditioning considers all points to the left of $-10\%$ on the horizontal axis and computes the expected shortfall  or probability of shortfall  on the basis of these CBA returns.
Measures of stress caused by stress event $\omega$   include
$$
\E(S|\omega)-\E(S)\ ,
$$
that is, the  increase in the expected shortfall or proportionate increase in the probability of default.

There are two shortcomings when focus is placed on a single scenario:
\bi
\i All other scenarios are ignored. GDP growth, interest rates, market  returns, unemployment rates and other factors take on a continuous range of values. Hence assuming that market index returns are less than $-10\%$, for example, in stress testing and assessing the financial impact ignores the possibility of other adverse scenarios.

\i Focusing on a single scenario ignores the stochastic or probabilistic nature of actual outcomes. Additionally  when various scenarios are considered, there is no coherent framework to combine the scenarios to assess the overall stress impact on each firm. Hence stress test results are scattered, impede interpretation and may make for ambiguity.
\ei

\section{Stress testing based on more than one adverse event}\label{s_extend}

With more than one possible events $\omega$ covering the range of all possible scenarios, then\footnote{The sample space of possible scenarios is assumed discrete.   If not,  sums are replaced by integrals.  Also note that the development here and below can use either $S$ or $S^+$.}
\begin{equation}\label{stress1}
\E(S) =  \sum_\omega f(\omega) \E(S|\omega)\cq \sum_\omega f(\omega)=1\ ,
\end{equation}
where $f(\omega)$ is the probability associated with scenario $\omega$.
Hence expected capital shortfall combines conditional expectations under various scenarios using actual probabilities. Scenarios may represent simulations from a stochastic model.   Alternatively, scenarios relate to outcomes of market or macroeconomic factors during the upcoming period such as interest rates, credit spreads, market index returns, unemployment rates, house prices, inflation and economic growth. Subsequent sections of this paper assume a single factor driving the scenarios: market index returns.

Replacing the probabilities $f(\omega)$  in \eref{stress1} by distorted probabilities $\tilde f(\omega)$ leads to the distorted expectation
\begin{equation}\label{stress2}
\widetilde \E(S) =  \sum_\omega \tilde f(\omega) \E(S|\omega)\cq \sum_\omega \tilde f(\omega)=1\ .
\end{equation}
 Distorted  probabilities usually magnify the likelihood of adverse scenarios and diminish the likelihood of favourable scenarios such that  $\widetilde \E(S)>\E(S)$ -- the difference is formalised below. The standard stress testing approach focusses on a single scenario $\omega$, achieved by setting $\tilde f(\omega) =1$ yielding $\widetilde\E(S)=\E(S|\omega)$.

The computation of the stressed expected capital shortfall  \eref{stress2} is a common and practical modeling technique.  For example an economic scenario generator or ESG produces a large number of macroeconomic scenarios, and expected financial results are computed for each scenario and combined. The conditional expectation in \eref{stress1} allows for other random factors which drive financial results not captured in the scenarios. These random factors typically relate to firm specific volatility such as the amount of insurance claims for an insurer or loan defaults for a bank.

\section{Baseline and systemic stress}\label{s_sfactor}

One way to produce stressed probabilities is via a stress function $\psi(\omega)\ge 0$:
$$
\tilde f(\omega) = \psi(\omega) f(\omega)\cq \E(\psi) =\sum_\omega \psi(\omega)f(\omega) =  1\ .
$$
The stress function  $\psi(\omega)$ models stress from scenario $\omega$. If $\psi(\omega)>1$, scenario $\omega$ is deemed adverse and its probability exaggerated.  In terms of  stress function $\psi$ the stressed expectation is
\begin{equation}\label{stress3}
\widetilde \E(S) = \sum_\omega f(\omega) \psi(\omega) \E(S|\omega) = \E(\psi S) = \br+\pr\ .
\end{equation}
where
$$
\br(S)\equiv\E(S)\cq \pr(S) \equiv\cov(S,\psi)\ .
$$
   If $\psi$ models a systemic event, then the \pr\  is a systemic risk.

Baseline risk \br\ is the stress in the system aside from that imposed by stress $\psi(\omega)$.  Systemic stress or \pr\  is the stress imposed by $\psi(\omega)$ and in particular the adverse weighting  of various scenarios $\omega$.
More particularly baseline risk \br\  is the expected shortfall assuming the stochastic behaviour of the system is unchanged apart from changes indicated by current information. Systemic risk \pr\  measures the impact of a system--wide shock.  Such shocks are largely unpredictable. Unlike \br, computed from individual firm balance sheets, \pr\  is influenced by linkages between firm balance sheets, often caused by common dependence on macroeconomic factors such as market returns.

The stress factor $\psi$ is typically  tied to market or macroeconomic factors such as market returns, interest rates, unemployment rates and GDP growth, and is hence identical across firms. Systemic risk of a firm increases with the correlation between its capital shortfall and the stress factor.

Using the example in the previous section, the stress factor $\psi(\omega)=0$ for market returns $\omega$ above the lower $10\%$ threshold, and $\psi(\omega)=10$ for extreme returns $\omega$ below the threshold. Hence the bottom tail of market returns is stressed 10 times, and  other returns  ignored. Alternatively $\psi$ can be a monotonic decreasing  function in $\omega$. In this setup the worst possible market return is stressed most heavily, and the stress reduces as the market return becomes more favourable.  Unlike the standard stress testing approach, all scenarios of the market return are reflected as long as $\psi(\omega)>0$.

The stressed expectation in \eref{stress3} is closely related to the literature on distortion and weighted risk measurement. The stressed expectation $\E(\psi S)$ is consistent with weighted risks by \cite{furman2008weighted1}, \cite{choo2009loss} and \cite{choo2010determining}. \cite{choo2009loss} establishes equivalence, under specified conditions, between weighted risks and distortion risks \citep{wang2000class}. Distortion risks are expectations computed under distorted probability distributions, as is in \eref{stress2} where actual probabilities are replaced by hypothetical probabilities.

\section{Stress due to adverse overall market returns}\label{s_stmarket}

 Write $0\le \omega\le 1$ as the percentile rank of the market rate of return. For example $\omega=0.5$ denotes the median return for example, and $\omega=0$  the minimum return. Since $\omega$ is uniform between $0$ and $1$, and assuming a continuous range of returns
 $$
 \br\equiv\E(S) = \int_0^1 \E(S|\omega) \de \omega\;,
$$
The scenario $\omega=0.01$ with expected shortfall outcome $\E(S|\omega=0.01)$ is the expected shortfall given the stock market attaining the $1\%$ lower threshold or Value--at--Risk. Common phrases for this scenario include the ``worst return in 100 years" or a ``1--in--100 year event" although it should be pointed out that these phrases are incorrect since they refer to $0\le \omega\le 0.01$ or on average $\omega=0.005$, more adverse than $\omega=0.01$.

The scenario $\omega<0.01$ indicates a market return in the lower 1\% of possible returns. The stressed expectation in this case is the expected capital shortfall assuming market return falls below the $1\%$ lower threshold, commonly known as the Tail--Value--at--Risk or Conditional--Tail--Expectation \citep{mcneil2005qrm}.  In this case $\psi(\omega)=100$ for $\omega<0.01$ and zero otherwise leading to
$$
\br+\pr=\widetilde \E(S)  = 100\int_0^{0.01}\E(S|\omega) \de \omega
= \E(S|\omega<0.01) \;.
$$
In practice this stressed expectation is computed from a stochastic model by identifying simulations where the market return is in the bottom $1\%$. Capital shortfall is computed for the identified simulations and averaged to yield an estimate of $\widetilde \E(S)$. In contrast, standard stress tests only pick up a single scenario for the market return, or a collection of disparate scenarios.

A further example is to take $\psi(\omega)=n(1-\omega)^{n-1}$ where $n>0$.   In this case the worst percentile market returns are weighed most heavily with weights decreasing with percentile:
$$
\br+\pr=\widetilde \E(S) =  \int_0^1 \E(S|\omega)\de(1-\omega)^n \ .
$$
Note $(1-\omega)^n$ is the  distribution of the  worst percentile outcome in $n$ independent trials.  Hence $\widetilde\E(S)$ in this case corresponds to the expected shortfall if the market return is the worst in $n$ independent and identical copies of the current environment.

The above   shows the advantage of the refined stress testing approach over the standard approach. The standard approach assumes a single value for the market return which has an infinitesimal likelihood whereas the refined approach allows for a range of more plausible values. In addition Tail--Value--at--Risk has several well known advantages over Value--at--Risk as a risk measure and has been adopted in Swiss regulations and potentially used in updated Basel regulations.

\section{Systemic risk in groups of firms}\label{s_formal}

This section considers the the aggregate shortfall in a group or system of firms driven by a common stress factor $\psi$.   Write $S_i$ as the shortfall in firm $i$ with $S_i^+$ the positive part of $S_i$.    Aggregate shortfall is then $S^*\equiv\sum_iS^+_i$
\begin{equation}\label{new}
\br(S^*) = \sum_i\br(S^+_i)\cq \pr(S^*) = \sum_i\pr(S^+_i)\ .
\end{equation}
The final result follows from the fact that covariance is linear in both its arguments.  Similar results\footnote{Note that $S^*\ge (\sum_iS_i)^+=S^+$.  The  inequality holds since $S^*$ does not permit shortfalls in one firm to be offset by surpluses (negative shortfalls) in other firms.}  apply to
$S\equiv \sum_i S_i$.

Since $S^+$ is positive it is useful to consider percentage contributions to overall risk:
\begin{equation}\label{total2}
\left(\begin{array}{c}\%\ \mathrm{overall\ risk}\\ \mathrm{effect\ from}\ \psi\end{array}\right) = 100\ \frac{\pr(S^*)}{\br(S^*)}= \sum_i \frac{\br(S_i^+)}{\br(S^*)} \left(\begin{array}{c}\%\ \mathrm{risk}\\\mathrm{in }\ i \end{array}\right)\ .
\end{equation}
Thus overall \pr\  as a percentage of \br\   is  a weighted average of percentage \pr 's  in individual firms with weights   proportional to the amount of \br\  contained in firm $i$.  Firms with high baseline risk are potentially high contributions to overall systemic stress.    Baseline stress in a firm increases with the amount of debt.   However the proportional contribution of a firm is independent of the prudential fraction $k$ except to the extent that the latter effects the adjusted log--leverage.

Using a common $\psi$ identifies firms with large systemic risk.  Mergers and acquisitions reduces total capital shortfall. \br($S^*$)  and \pr($S^*$)\  prior to remedial action  ignore mergers and acquisitions as would be case with basing calculations on $S$.

\cite{brownlees2015} define SRISK as
\be{srisk}
\mathrm{SRISK} \equiv \sum_i\left\{\widetilde\E(S_i)\right\}^+=\sum_i\left\{\br(S_i)+\pr(S_i)\right\}^+\ .
\ee
with percentage contributions defined as
$$
\mathrm{SRISK}_i^\% = 100\times\frac{\{\widetilde\E(S_i)\}^+}{\mathrm{SRISK}}= 100\times \frac{\{\br(S_i)+\pr(S_i)\}^+}{\mathrm{SRISK}}
$$
With SRISK,  shortfalls are  offset with surpluses, if any, in other firms.
Further there is a mixture of \br\  and \pr\  with potential for mixed messages.

Separating  baseline and $\psi$--risks and monitoring  across firms, appropriate action can be taken either in relation to individual firms or the overall market. For an isolated firm with high baseline or systemic risks, remedial action such as reduced leverage or capital injection can be imposed on the firm. When systemic risk is high across all firms, such remedial actions are impractical and macroeconomic action is required, such as introducing regulations to stabilise the housing market.

\subsection{Baseline risk}

Baseline risk is inherent in the system. Capital shortfalls can occur even if the system is not under stress. It is informative to monitor:
\bi
\i Firm baseline risk $\br(S_i^+)$. A high value indicates the firm is either likely to suffer a capital shortfall in the future or it incurs a significant shortfall if one occurs. Remedial action is required to improve the balance sheet such as reducing debt or leverage and increasing capital.

\i Total baseline risk $\br(S^*)$ where $S^*=\sum_iS^+_i$. It is important to monitor total baseline risk closely since it is a forward looking indicator of a system failure. Increasing total baseline risk indicates a higher risk of widespread capital shortfall. Total baseline risk may be difficult to control once it crosses a threshold, e.g. capital injection is required across all firms.

\i Total diversified baseline risk $\br(S^+)$.   This measures baseline risk after allowance for possible mergers.

\i Contribution of a firm to total baseline risk, $\br(S^+_i)/\br(S^*)$ or $\br(S^+_i)/\br(S^+)$. This enables the regulator such as APRA to direct appropriate resources to firms with higher risk of capital shortfall.

\ei
Section \aref{s_forward} displays baseline risk calculations on Australian banks by using the GARCH--DCC to model future stock returns at different points in time based on available information at that time. Further results are shown below.

\subsection{Systemic risk}

The one month ahead systemic risk of a firm at a particular point of time is the covariance between the expected capital shortfall in one month and the stress factor $\psi$. The stress factor $\psi$ indicates the level of stress in the system or the severity of a macroeconomic scenario as described in \sref{s_sfactor}. Hence the systemic risk of a firm is driven by the dependence between its capital shortfall and the level of system or macroeconomic stress. A firm which has high leverage or debt levels, e.g. high baseline risk, may have high or low systemic risk:
\bi
\i High \pr\  applies if the firm has higher capital shortfall when the system is in distress. This may occur for example for a bank with loans having high loan-to-valuation ratios and is hence susceptible to increases in unemployment rates or reductions in residential property prices.

\i Low \pr\  applies, even if baseline risk is high, if firm shortfall is not tied to the system. For example the firm's business may be mostly sourced from overseas rather than local markets, and hence is unaffected when the local system is in distress.
\ei
Total systemic risk as shown above is the covariance between total capital shortfall and the stress factor. Hence there is large total systemic risk if capital shortfall across all firms are highly dependent on the stress factor.

\pr of form $i$ is made up of two parts
$$
\pr(S_i^+)=\widetilde \p(S_i>0) \widetilde \E(S_i|S_i>0) - \p(S_i>0)\E(S_i|S_i>0) \;,
$$
displaying it is a combination of impact of the increased probability and extent of shortfall with  stress and without stress.

Again it is important to monitor:
\bi
\i High $\pr(S_i^+)$ does not imply that the firm is expected to have a large capital shortfall. However the firm is susceptible to shortfall if a system shock does occur.

\i The total  $\pr(S^*)$ does not indicate imminent capital shortfall. However firms are becoming heavily dependent on one another and on the system and will be simultaneously in distress if a shock occurs.

\i Firm contributions to total systemic risk $\pr(S^*)$. This enables the regulator to identify systemically important firms.

\ei

\section{Monitoring risks in Australian banks}\label{s_app}

In this section we consider the sum of positive shortfalls $S^*=\sum_iS_i^+$ combined with $\psi(\omega)=n(1-\omega)^{n-1}$ where $0\le \omega\le 1$ is a market return equal to the $\omega$ percentile in the monthly market return distribution.   Then the stressed distribution of market returns is the worst  monthly market outcome in $n$ months.   The distribution of monthly market returns and hence worst monthly market returns is computed with the GARCH--DCC model based on daily firm and market return data up to the start of the given month.  The models takes account of changing volatilities and correlations and hence any distribution is dynamic, tailored to the data up to the given point of time.    High volatility implies high \br\ while high correlation implies high \pr.

\subsection{Risk position of banks and banking system on two dates}

\tref{twodates} contains real time stress calculations on the first trading day of  January 2009 and December 2014.  As before there is no look ahead bias -- calculations on each of the two dates use data available on the first day of the applicable month.   The first eight rows in the body of \tref{twodates} correspond to the eight banks used in this study.  The first  and second columns in the two halves of the table body contain the adjusted log--leverage  and debt  (as a percentage of total sustem debt) for each of the banks.

\begin{table}[ht]
\caption{One month ahead projections for banks}
\label{twodates}
\centering
\begin{threeparttable}
\small
\vspace{4mm}
\begin{tabular}{l|rrrr|rrrr}
\hline
&\multicolumn{4}{c|}{January 2009}&\multicolumn{4}{c}{December 2014}\\
  \hline
   & Aloglev& Debt & \br  & \pr  & Aloglev & Debt  &\br & \pr\\
 %  & $\ell$ & $d$ &$\E(S_i^+)$&$\Psi(S_i^+)$& $\ell$&$d$ & $\E(S_i^+)$ & $\Psi(S_i^+)$ \\
  \hline
CBA & 18.57 & 24.30 & 22.99 & 29.60 & -70.34 & 22.70 & 0.00 & 0.00 \\
  ANZ & 15.93 & 18.37 & 14.87 & 18.89 & -38.64 & 22.10 & 0.00 & 0.00 \\
  NAB & 31.97 & 25.50 & 39.98 & 19.41 & -12.45 & 25.61 & 50.52 & 67.13 \\
  WBC & -1.55 & 22.84 & 5.86 & 23.94 & -53.84 & 22.03 & 0.00 & 0.00 \\
  MQG & 41.22 & 5.75 & 11.02 & 5.46 & -46.10 & 4.33 & 0.17 & 0.12 \\
  BOQ & 63.30 & 1.32 & 3.55 & 0.99 & -17.05 & 1.33 & 0.80 & 1.34 \\
  BEN & 18.91 & 1.81 & 1.72 & 1.71 & -7.63 & 1.84 & 25.43 & 30.71 \\
  ABA & -8.12 & 0.10 & 0.00 & 0.00 & 9.22 & 0.07 & 23.07 & 0.71 \\
  \hline
  $S^*$ & 18.78 & 2.42 & 17.17 & 8.63 & -41.91 & 3.27 & 0.03 & 0.12 \\
  $S^+$ & 17.81 & 2.42 & 15.28 & 10.18 & -44.22 & 3.27 & 0.00 & 0.00 \\ \hline
\end{tabular}
\begin{tablenotes}
\item[]Main body of table uses shortfall measure  $S_i^+$. Aloglev is 100 times the adjusted log--leverage. \pr\  is with respect to expected worst monthly market return  in 12 months.  Main body of table displays percentage contributions of each firm to totals displayed in $S^*$ row.   The $S^*$ row displays 100 times debt weighted adjusted log--leverage, total debt in \$$10^{11}$, and $\br(S^*)$  and $\pr(S^*)$ per $0.08\times$debt.  $S^+$ row displays results with debt and equity pooled across banks.
\end{tablenotes}
\end{threeparttable}
\end{table}
\normalsize

January 2009 was a time of great stress for all eight banks.       Six of the eight banks were had positive capital shortfalls as indicated by the adjusted log--leverage column:   the two banks not in capital shortfall default were WBC and ABA.

 Percentage BASRISK and PSIRISK are displayed in the next 2 columns in each half of the table.    The baseline stress column indicates most of the baseline stress arises from NAB -- almost 40\% of the total.   The next most baseline stressed bank is CBA with WBC also a substantial contributor.   MQG contributes almost double to baseline stress compared to the proportion of total debt  it carries.  The other three small banks contribute relatively little to baseline stress with BOQ  almost 3 times expected on the basis of its debt.   \pr\   is highest for the CBA, higher than expected on the basis of its debt load and hence CBA was most susceptible to stress from additional general market equity devaluation.    All other banks appear to have \pr\ comparable to their size in terms of debt load with only NAB being less systemically important.    This should be compared to NAB's high baseline stress.

Continuing with January 2009, the final two rows indicate the total amount of stress in the system and its diversifiability.
The second last  row labelled ``$S^*$"  displays, in order, debt weighted adjusted log--leverage, total \br\  and total \pr.   The final row labelled ``$S^+$" displays the aggregate stress based on $S^+$, treating all eight banks as one entity.
On aggregate \br$(S^*)$  is about twice \pr$(S^*)$.   Thus there is more danger of increasing capital shortfall due to market volatility  as opposed to further stress from further substantial general market devaluation.  The final row indicates stresses are not diversifiable:    The marginally  smaller  ``diversified"  \pr\ is offset by an increase in \pr.

Stress readings  alter dramatically when moving to December 2014 -- there is virtually no stress in any bank and the small amount of  stress in the system is diversifiable.    Most of the  \br\ is carried by NAB with lesser contributions by BEN and ABA.    All the stress in the minor bank ABA is baseline stress as only NAB and NAB have substantial \pr\  contributions.   Again, however, it must be emphasised that there is minimal systemic stress in the system.  Notice total debt in the banking sector  jumps about 35\% between the two dates.

\subsection{\pr\ versus \br\  for individual banks}

\fref{sysstress} plots \pr\ versus \br\ for the eight Australian banks of \tref{eightbanks}.   Generally baseline stress is higher than systemic stress, although the mix differs between banks and the extent of stress. For example compared to the smaller Australian banks, bigger banks have a larger proportion of systemic stress relative to baseline stress. In addition MQG is more systemically risky amongst the smaller banks.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=12cm]{figures/sysstress.pdf}
\caption{\pr\  (y--axis) versus \br\  (x--axis)   for major banks (left panel) and  minor banks (right panel)  for 144 months during 2003--2014}
\label{sysstress}
\end{center}
\end{figure}

\subsection{Temporal \br\ in individual banks over time}\label{simulate1}

\fref{tbrisk} displays, the estimated $\br(S_i^+)$   for each major (left) and minor (right) Australian banks based on the projected one month ahead return distribution fitted using the GARCH--DCC model.   These \br\ results are discussed in \sref{brisk}.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=12cm]{figures/tbrisk.pdf}
\caption{$\br(S_i^*)$  for   major (left panel) and  minor (right panel)  banks 2003--2014.}\label{tbrisk}
\end{center}
\end{figure}

\subsection{Temporal \pr\ in individual banks }

The panels in \fref{tprisk} show \pr\ computed by assuming the worst market return in 12 identical months. The \pr\ for each bank generally exhibits similar patterns as \br\ displayed in \fref{tbrisk}.  However the scale of \pr\ is  lower indicating bank return volatility is a more significant issue than the consequences of a major market downturn.  However, importantly, there are differing patterns of \pr\ across banks which is an important for the regulator. For example ANZ had similar \pr\ stress as NAB around 2012 but lower \br. Hence although ANZ was not obviously in stress during 2012, it would be if a market downturn occurred. BEN and BOQ had high \br\ levels after 2008, but are overtaken by MQG in terms of \pr: MQG is more likely to suffer in a market downturn whereas BEN and BOQ are less likely to be impacted.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=12cm]{figures/tprisk.pdf}
\caption{$\pr(S_i^*)$  for   major (left panel) and  minor (right panel)  banks 2003--2014.}\label{tprisk}
\end{center}
\end{figure}

The above remarks are gleaned from the past behaviour of \pr\ over time.   In practice \pr\ and  \br\  will be monitored in real time providing up--to--date understanding of banks' risk positions as events unfold.

\subsection{Temporal \br\  in the banking system}\label{Baggregate}

BRISK for both $S^*$ and $S^+$ are plotted in \fref{muqsB}.  With the former quantity risk is not diversified across banks.   The right panel indicates that initial build up of  $\br(S^*)$ is not immediately followed up by a build up of $\br(S^+)$: that is initially most \br\ is diversifiable.   However once a critical point is reached (at about 0.75) there is an almost linear progression and every unit increase in $\br(S^*)$ is transmitted to a unit increase in $\br(S^+)$, that is there is no more diversification or capacity to absorb \br.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=12cm]{figures/muqsB.pdf}
\caption{$\br(S^*)$ and $\br(S^+)$ over time (left panel) and plotted against each other (right panel).}\label{muqsB}
\end{center}
\end{figure}

The capacity to absorb risk in the banking system relies on implicit merging and hence on a measure of shortfall such as $S^*$.    When two firms merge the leverage of the resulting firm is less than that of the more highly leveraged firm.   The merged firm is more able to withstand return on equity shocks  unless negative shocks are more prone for the merged firm.

Firms do not necessarily merge, even in dire financial circumstances.   Hence the mergers spoken of here are hypothetical.   From a regulators perspective, what would happen under a merger of all firms (or perhaps a group of firms) is nevertheless of interest.   A system as as a whole near Basel breach is more threatening that one where a few firms are near Basel breach but the system as a whole is strongly Basel compliant.

\subsection{Temporal \pr\  in the banking system}\label{Paggregate}

PRISK for both $S^*$ and $S^+$ are plotted in \fref{muqsP}.  The scales are the same as in \fref{muqsB} facilitating comparison.   Note firstly \pr\ is generally smaller: that is systemic stress as induced by a major market event is generally smaller than stress caused by increases in volatility.

Second, unlike baseline risk,   $\pr(S^+)$ can exceed $\pr(S^*)$ and in fact this occurs is quite typical in high stress environments.   Thus systemic risk in an aggregated system can be, and often is, higher than systemic risk in a disaggregated system suggesting interacting and reenforcing vulnerabilities.

Third, the manner in which $\pr(S^+)$ builds up as compared to $\pr(S^*)$ is different to the buildup in \br.   This is evident in the right panel of \fref{muqsP}.  Low levels of $\pr(S^*)$ are not reflected in $\pr(S^+)$, that is all risk is absorbable in the system.   However once a critical level of $\pr(S^*)$ is reached there is an ``explosive" effect on the system as measured with $\pr(S^+)$: each unit increase in the former leads to a significantly higher than unit response in the latter.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=12cm]{figures/muqsP.pdf}
\caption{$\pr(S^*)$ and $\pr(S^+)$ over time (left panel) and plotted against each other (right panel).}\label{muqsP}
\end{center}
\end{figure}

\section{Practical issues}\label{s_concl}

The following discusses key practical issues and challenges when calculating and monitoring baseline and systemic risks across firms. Performing the risk calculations requires a stochastic model which captures:
\begin{enumerate}
\i Future movements in firm balance sheets

\i Interdependence between firm balance sheets
\end{enumerate}
Modelling is a challenge given the complexity of firm balance sheets which are driven by a range of macroeconomic and firm specific factors. There are two approaches to the modelling: centralised or embedded in firm internal models. The centralised approach is discussed in this paper, using publicly available stock returns and making simplified assumptions on capital requirements, debt, and market returns being the driver of firm stock returns. The second approach of embedding the calculations in firm internal models is discussed below in this section.

The GARCH--DCC model proposed in this paper can be refined by identifying key items forming the balance sheet and their drivers apart from market returns. These drivers may include interest rates and potentially the entire yield curve, unemployment rates, GDP growth, and property prices (both residential and commercial). The impact of each driver differs by firm depending on the makeup of the balance sheet. For example a bank balance sheet where assets are mainly formed by residential loans will be more sensitive to residential property prices than another which is mainly formed by commercial loans. Analysing balance sheets and drivers in detail leads to refinements in modelling and baseline and systemic risk calculations.

Once a centralised model is built, data and calculations need to be continually refreshed to monitor baseline and systemic risks over time. This ensures that risk calculations are reflective of current levels of debt, leverage, volatility and correlation. The continual updating requires a tradeoff between model sophistication and the effort required to perform the calculations. A sophisticated model may produce accurate risk calculations at a certain point in time, but may require significant time and resources to refresh calculations on say a daily or even monthly basis. In this case a simpler model may be more suitable without significantly comprising the quality of the results.

It is likely that firms have sophisticated stochastic models of their balance sheets, and hence baseline and systemic risk calculations may be embedded in these models. For example banks which are accredited to use the Internal Ratings Based (IRB) approach and Advanced Measurement Approach (AMA) to calculate their regulatory capital requirements will have advanced stochastic models of their balance sheet over at least a one year. However given that the models are proprietary, a key challenge would be to access and integrate models across firms, and continually over time. Even if the models are available, they may be inconsistent (for example using different time intervals or macroeconomic drivers) which makes the integration challenging. The challenge increases when systemic risk is expanded to capture banking and insurance industries.

A more practical alternative is to rely on individual firms to perform calculations of their baseline and systemic risks, similar to how Australian banks were made to perform industry stress tests in 2014 and prior. Consistency in the calculations would be the main focus, and could be improved by for example supplying a common ESG (Economic Scenario Generator) to all firms although the practicality of doing so has to be assessed. In addition a frequent additional stress test exercise may be onerous for firms.

\newpage

\appendix
\renewcommand*{\thesection}{\Alph{section}}

\section{GARCH--DCC model}\label{garchdcc}

Denote the daily (log) return for firm $i$ at time $t$ as
\newcommand{\vareps}{\varepsilon}
\be{mean.model}
\delta_{it}=\mu_i+\sigma_{it}\eps_{it}\cq \eps_{it}\sim (0,1)\ .
\ee
The volatility $\sigma_{it}$ is modelled as
\be{vol}
\sigma_{i,t+1}^2 = \omega+ \sigma^2_{it}\{\beta+(\alpha+\gamma \eps^-_{it})\eps_{it}^2\}  \cq  \eps^-_{it}\equiv I(\eps_{it}<0)=I(\delta_{it}<\mu)\ ,
\ee
where $I$ denotes the indicator function.  Hence the response of $\sigma_{i,t+1}^2$ to $\eps_{it}^2$  is increased by $\gamma$   if
the rate of return is below the average $\mu_i$, compared to the response if $\delta_{it}>\mu_i$.  Equations \eref{mean.model} and \eref{vol} defined a simple threshold GARCH model:  called the TARCH(1,1).   In \eref{mean.model} the mean $\mu_i$ does not vary with time $t$ and in \eref{vol} it is assumed the terms  $\sigma_{it}^2$ and $\eps_{it}$ in the right hand side of \eref{vol} are sufficient to structure the dynamics of volatility and contemporaneous correlation.

The model defined by \eref{mean.model} and \eref{vol} is estimated  for each security $i$ jointly with  a similar model for  the market,  $i=m$.   Correlation between security $i$ and the market $m$ are implicitly modelled using  positive definite recursions   \citep{engle2002dynamic}
$$
(Q_{i,t+1}-S) = \alpha (\eta_{it}\eta_{it}'-S) + \beta (Q_{it}-S)\cq \eta_{it}\equiv(\eps_{it},\eps_{mt})' .
$$
The correlation defined by $Q_{it}$ is used as the correlation between $\eps_{it}$ and $\eps_{mt}$.

\section{Data sources}\label{data}

Data are sourced from DataStream using the company and datatype codes as set out in \tref{datastream}.

\begin{table}\caption{DataStream codes}\label{datastream}
\begin{center}
	\begin{tabular}{l|l}
	\hline
	\multicolumn{2}{l}{Company codes}\\
	\hline
A:ANZX & Australia and New Zealand Banking Group Limited\\
A:ABAX & Auswide Bank Limited\\
A:BOQX & Bank of Queensland Limited\\
A:BENX & Bendigo and Adelaide Bank Limited\\
A:CBAX & Commonwealth Bank of Australia\\
A:MQGX & Macquarie Bank Limited\\
A:NABX & National Australia Bank Limited\\
A:WBCX & Westpac Banking Corporation.\\
\hline
\multicolumn{2}{l}{Datatype codes}\\
\hline
	NOSH & Number of Shares\\
	P & Price\\
	WC02999 & Total Assets\\
	WC03501 & Shareholders Equity\\
	RZ & Total return index\\
\hline	
\end{tabular}
\end{center}
\end{table}

Firm equity $w$ is Number of Shares multiplied by Price. Firm debt $d$ is Total Assets minus Shareholders Equity. Stock returns are computed from the Total Return Index including paid dividends.

\newpage
\section{References}
\bibliography{piet2}

\end{document}

### 2016-10-09 CIFR industry paper.tex
Lots and lots of changes
Latest

--- 2016-10-09 CIFR industry paper - FIRN.tex
@@
 
+  \author{Piet de Jong\footnote{
+    The authors gratefully acknowledge the financial and other support from the Centre of International Financial Regulation (CIFR).}\hspace{.2cm}\\
+    Department of Applied Finance and Actuarial Studies, Macquarie University\\
+    and\\
+    Weihao Choo\\
+    Department of Applied Finance and Actuarial Studies, Macquarie University
+        and \\
+    Geoffrey Loudon\\
+    Department of Applied Finance and Actuarial Studies, Macquarie University\\}
+
 \begin{abstract}
@@
 \end{frontmatter}
-
-\newpage
 

### 2016-10-09 onepager.tex
Lots and lots of changes
Latest

\documentclass[authoryear]{elsarticle}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf,comment}
\usepackage{enumerate}
\usepackage{url} % not crucial - just used below for the URL 
\bibliographystyle{chicago}
\usepackage{threeparttable}

\newcommand{\logit}{\mathrm{logit}}
\newcommand{\I}{\mathrm{I}}
\newcommand{\E}{\mathrm{E}}
\newcommand{\p}{\mathrm{P}}
\newcommand{\e}{\mathrm{e}}
\renewcommand{\o}{\omega}
\newcommand{\vecm}{\mathrm{vec}}
\newcommand{\kp}{\otimes}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\cov}{\mathrm{cov}}
\newcommand{\eps}{\epsilon}
\newcommand{\ep}{\varepsilon}
\newcommand{\obdots}{\ddots}    % change this later
\newcommand{\Ex}{{\cal E}}
\newcommand{\Ax}{{\mathrm{A}}}
\newcommand{\Exd}{\Ex_d}
\newcommand{\Es}{\Ex}
\newcommand{\rat}{{\frac{c_{ij}}{c_{i,j-1}}}}
\newcommand{\rmu}{m}
\newcommand{\rsig}{  r}
\newcommand{\fd}{\mu}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\cor}{\mathrm{cor}}
\newcommand{\bx}[1]{\ensuremath{\overline{#1}|}}
\newcommand{\an}[1]{\ensuremath{a_{\bx{#1}}}}

\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}

\renewcommand{\i}{\item}
\newcommand{\sr}{\ensuremath{\mathrm{SRISK}}}
\newcommand{\br}{\ensuremath{\mathrm{BRISK}}}
\newcommand{\pr}{\ensuremath{\mathrm{PRISK}}}
\newcommand{\cs}{\ensuremath{\mathrm{CS}}}
\newcommand{\cri}{\ensuremath{\mathrm{Crisis}}}
\newcommand{\var}{\ensuremath{\mathrm{VaR}}}
\newcommand{\covar}{\ensuremath{\mathrm{CoVaR}}}
\newcommand{\med}{\ensuremath{\mathrm{m}}}
\newcommand{\de}{\mathrm{d}}
\renewcommand{\v}{\ensuremath{\mathrm{v}_q}}
\newcommand{\m}{\ensuremath{\mathrm{m}}}
\newcommand{\tvar}{\ensuremath{\mathrm{TVaR}}}
\renewcommand{\c}{\ensuremath{\mathrm{CoVaR_q}}}
\renewcommand{\v}{\ensuremath{\mathrm{VaR}_q}}

\newcommand{\eref}[1]{(\ref{#1})}
\newcommand{\fref}[1]{Figure \ref{#1}}
\newcommand{\sref}[1]{Section \ref{#1}}
\newcommand{\tref}[1]{Table \ref{#1}}
\newcommand{\aref}[1]{Appendix \ref{#1}}

\newcommand{\cq}{\ , \qquad}
\renewcommand{\P}{\mathrm{P}}
\newcommand{\Q}{\mathrm{Q}}

\newcommand{\Vx}{{\cal V}}
\newcommand{\be}[1]{\begin{equation}\label{#1}}
\newcommand{\ee}{\end{equation}}

\newcommand{\D}{\mathrm{D}}

\begin{document}

\section*{Monitoring systemic risk}\label{srisk}

 \cite{brownlees2015} define  systemic risk\footnote{In contrast to \cite{brownlees2015} we factor out the scale factor $kd$ making for a more transparent 0 to 1 scale for \sr.} for a group of firms in terms of the expected future capital requirement $S_i$ for each firm $i$ in the group:
\be{esrisk}
\sr =  \sum_i \pi_i\left\{\Es(S_i)\right\}^+ = \D[\{\Ex(S_i)\}^+]\cq \pi_i = \frac{d_i}{d}\cq d=\sum_id_i \ ,
\ee
where $S_i=1-\e^{r_i-\ell_i}$ is the shortfall  for firm $i$.
Here $\Es$ denotes expectation given a major general market downturn and $\D$ is debt weighted averaging.    Further \sr\ is expressed in units $kd$ and $0\le\sr\le 1$ with \sr\ near 1 indicating extreme financial distress for all firms. \sr\ is based on the expected capital requirement and firms with an expected capital surplus under stress are ignored.   The expression \eref{esrisk} slightly modifies the definition  of \cite{brownlees2015} by dividing their \sr\ expression by $kd$.

The systemic risk contribution of firm $i$  is  \citep{brownlees2015} 
\be{sriskperc}
\sr_i=\frac{\pi_i\{\Ex(S_i)\}^+}{\sr} \ .
 \ee
 Note $0\le \sr_i\le 1$ with larger values indicating firm $i$ is systemically important: it holds a high proportion $\pi_i$ of the total debt, and/or is likely to heavily breach, compared to other firms, the Basel capital requirement under the stress event implicit in the calculation of $\Ex$.  Expression \eref{sriskperc} depends on $k$ through each of the adjusted log--leverages $\ell_i$.

In this article we propose four modifications to \sr\ and $\sr_i$ defined in \eref{esrisk} and \eref{sriskperc}.   Each of these modifications is designed to improve stress monitoring.  The proposed  modifications to \sr\  are shown,  theoretically and empirically, to have more  sensitivity and specificity.   Sensitive, in the sense of more likely detect  firms likely to face financial distress.   Specific in the sense of   minimising false alarms.  The modifications are:
\begin{enumerate}
\item  Replacing $\{\Es(S_i)\} ^+$ in \eref{esrisk} and \eref{sriskperc} by $\Es(S_i^+)\ge\{\Es(S_i)\} ^+$.   The justification is that typically $\Es(S_i)=0$ and  hence \eref{esrisk} is not affected by firms that  have zero expected capital requirement even though in individual instances that capital requirement may be large.   Using $\Ex(S^+_i)$ instead of $\Ex(S_i)$ implies each firm counts with degree depending on the its proportionate contribution $\pi_i$ to total debt and the expected value of a put on its shortfall.   
\item Using more general   definitions of $\Es$ to encompass more flexible stress specifications.   For example modelling stress  as a 10\% market downturn, while pertinent and interesting, is obviously arbitrary.   This paper posits more flexible and robust specification of stressed expectation $\Ex$.   
\item  Baseline risk is defined as $0\le \E(S_i^+)\le 1$.  The  stress index  is the proportionate increase in baseline risk when stress $\psi$ is applied:
$$
s_i=\frac{\Ex(S_i^+)-\E(S_i^+)}{\E(S_i^+)}\ .
$$
Thus $1+s_i$ is a risk ratio, comparing the default put option price under stress and baseline conditions.
\item Total diversifiable baseline risk is $0\le\E(S^+)\le 1$ where, as before, $S=\D(S_i)$, total shortfall per unit $kd$ where $d$ is total debt.  The diversifiable stress index is 
$$
s=\frac{\Ex(S^+)-\E(S^+)}{\E(S^+)}\ .
$$

\item Total non-diversifiable baseline risk is $0\le\E\{\D(S_i^+)\}\le 1$.  The risk is non--diversifiable since shortfall $S_i>0$ in one firm cannot be offset by surplus in other firms.   Total non--diversifiabe  stress risk is
$$
s^*=\frac{\Ex\{\D(S_i^+)\}-\E\{\D(S_i^+)\}}{\E\{\D(S_i^+)\}} = \frac{\D\{s_i\E(S^+_i)\}}{\D\{\E(S^+_i)\}}\ ,
$$
a weighted average of firm specific stress risks $s_i$ using weights $\pi_i\E(S_i^+)$.   A firm figures highly in overall stress risk if its stress index is large, carries a significant portion of debt,  and its baseline risk is high.

\item  A measure of the absorbability of defaults in single firms is 
$$
 \alpha= \frac{s^*-s}{s}\ge 0\ .
$$
If $\alpha=0$ then $s^*= s$ and  shortfalls in individual firms translate  directly into a shortfall for the system as a whole.   Conversely a large value of $\alpha$ indicates stress in single firms can be absorbed elsewhere.   The reciprocal $1/\alpha$ is a measure of contagion.
\end{enumerate}

\section*{References}
\bibliography{piet2}
\end{document}

### 2016-10-09 presentation.tex
Lots and lots of changes
Latest

\documentclass{beamer}

\usepackage{threeparttable}

\newcommand{\eps}{\epsilon}
\newcommand{\var}{{\rm var}}
\newcommand{\cov}{{\rm cov}}
\newcommand{\nid}{{\rm NID}}
\newcommand{\diag}{{\rm diag}}
\newcommand{\E}{{\mathrm E}}
\newcommand{\R}{{\mathrm R}}
\newcommand{\RD}{{\tilde{\mathrm R}}}
\newcommand{\Q}{{\mathrm Q}}
\newcommand{\U}{{\mathrm U}}
\newcommand{\Ex}{{\cal E}}
\newcommand{\cor}{\mathrm{cor}}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\e}{\mathrm{e}}
\newcommand{\de}{\mathrm{d}}
\newcommand{\p}{\mathrm{P}}
\newcommand{\Ln}{\mathrm{Ln}}
\newcommand{\sign}{\mathrm{sign}}

\newcommand{\ra}{\varrho}

\newcommand{\minn}{\mathrm{min}_n}
\newcommand{\maxn}{\mathrm{max}_n}

\newcommand{\cq}{\ ,\quad }
\newcommand{\qq}{\quad \Rightarrow \quad}
\newcommand{\oq}{\quad \Leftarrow \quad}
\newcommand{\eq}{\quad \Leftrightarrow \quad}

\newcommand{\ppo}[1]{|{#1}|^+}

\newcommand{\ssection}[1]{%
  \section[#1]{\textbf{\uppercase{#1}}}}
\newcommand{\ssubsection}[1]{%
  \subsection[#1]{\normalfont\textbf{#1}}}

%\renewcommand{\labelenumi}{(\roman{enumi})}

\newcommand{\eref}[1]{(\ref{#1})}
\newcommand{\fref}[1]{Figure \ref{#1}}
\newcommand{\sref}[1]{\S\ref{#1}}
\newcommand{\tref}[1]{Table \ref{#1}}
\newcommand{\aref}[1]{\ref{#1}}

\newcommand{\bi}{\begin{itemize}}
\renewcommand{\i}{\item}
\newcommand{\ei}{\end{itemize}}

\newcommand{\es}{{\mathrm{ES}}}
\newcommand{\ses}{{\mathrm{SES}}}
\newcommand{\sr}{{\mathrm{SR}}}

\bibliographystyle{chicago}

% \usepackage{beamerthemesplit} // Activate for custom appearance

\title{Capital Shortfall in Banks and Stress testing}
\author{Piet de Jong, Geoff Loudon, Weihao Choo}
\date{\today}

\begin{document}

\frame{\titlepage}

\frame{\frametitle{Outline of presentation}
\bi
\i   Capital shortfall \framebox{Brownlees \& Engle (2015)}
\i   Future (1 month's time) capital shortfall \framebox{$S$}
\i   Example:  CBA return  \& market return
\i   Stress testing capital shortfall -- scenarios \framebox{$\omega$}
\i   Stress testing -- ``theory" --  stress function \framebox{$\psi(\omega)$}
\i   Proposed definition of "stress"  \framebox{$\psi_S$} ... $\psi$--risk in/on $S$
\i   Properties/features/estimating  \framebox{$\psi_S$}
\i   Baseline risk (BASRISK), $\psi$--risk (PSIRISK)
\i   Detailed look at 8 Australian banks 2003-2015 
\i   Formalisation of risk weighted assets methodology
\ei
}

\frame{\frametitle{What's new in this paper?}
\bi
\i  Build on techniques of Brownlees \& Engle (2015)
\bi
\i   Capital shortfall -- volatility lab
\i   GARCH-DCC methodology to model same
\i   Systemic stress measurement
\ei
\i  Development of  \framebox{statistical ``stress" methodology}
\bi
\i  Can be applied to any joint distributional framework
\i  Based on \framebox{stress function}
\i  Based on \framebox{stressed} probabilities and conditional expectation
\i  Distinguishes between \framebox{background} and \framebox{systemic} stress
\i  Appropriate quantitative definition of \framebox{systemic} stress
\ei
\i  Appropriate \framebox{aggregation} of stress and stress \framebox{contributions}
\i  Application to 8 Australian banks
\i  Comparison to asset risk weighting methodology
\i \framebox{Not done}:     
\bi
\i  Other Aust financial institution (insurance, bldg societies, etc)
\i EURO or US banks
\ei
\ei
}

\frame{\frametitle{Capital Shortfall -- Brownlees \& Engle (2015)}
$$
S= k (d+w)-w = k d\left(1-\frac{1-k}{kL}\right)
$$
\bi
\i  $d$ is debt, $w$ is equity, $d+w$  assets, $L\equiv \frac{d}{w}$ is the {\bf leverage}
\i  $k$ is the {\bf prudential fraction} -- often around 8\%, capturing market, credit, insurance, operational and other risks
\i  $S$ is amount ($\pm$)  to maintain {\bf solvency}.  $S<0$  indicates capital surplus
\i {\bf Definition of $S$ is  simplistic} ... 
\bi
\i  Maybe additional adjustments  relating to intangible assets and liability surpluses
\i Firms usually need to maintain an equity buffer above regulatory capital requirement and hence the true capital shortfall is higher
\ei
\i \framebox{$S=kd(1-\e^{-\ell})$} where $\ell=\ln\left(\frac{kL}{1-k}\right) = \mathrm{logit}(k) + \ln(L)$
\bi
\i   {\bf $\ell$ is the adjusted log--leverage}:  $\ell>0$  implies $S>0$
\ei
\ei
}

\frame{\frametitle{Australian Banks:  $w$ and $\ell$}
\begin{figure}[htbp]
\begin{center}
\includegraphics[width=7.5cm]{figures/prices2.pdf}
\caption{Daily stock  prices of four major (top left panel) and four minor (top right panel) Australian banks from early 2000 through to the end of 2014.  Price series normalised to start at 1. Bottom panels are adjusted log--leverages at start of every month from 2003 onwards.}
\label{prices}
\end{center}
\end{figure}
\bi
\i  Debt $d$ smooth step function
\i  In calculations below based on $k=8\%$  (Basel fraction)
\ei
}

\frame{\frametitle{Future capital shortfall}
  Interested in  capital shortfall in,  say, \framebox{1 month's time}
  $$
  S\equiv k d\left(1-\frac{1-k}{kL\e^{-r}}\right) = kd(1-\e^{r-\ell})
  $$
\bi
\i Assumes debt $d$ does \framebox{not} change over the month
\i  $r$ is the return on on equity:   $\e^rw$ equity in one month's time
\i $L$ is the current leverage:  $L\e^{-r}$ future leverage
\i $\ell$ is the (current) adjusted log--leverage.   If $r<\ell$ then $S>0$
\i  Interested in  $\E(S|\omega)$ under \framebox{adverse} scenarios $\omega$
\i  $\E(S|\omega)-\E(S)$ is the $\uparrow$ shortfall ``risk"  of  $\omega$
\bi
\i  What are  appropriate adverse scenarios $\omega$?
\i  How to model/calculate $\E(S|\omega)$? 
\ei
\ei
}

\frame{\frametitle{Example -- adverse scenario is market downturn}
\begin{figure}[htbp]
\begin{center}
\includegraphics[width=9cm]{figures/figCBA.pdf}
\caption{Forecast $(\omega,S)$ distribution where $\omega$ is one month forward market return and $S$ is CBA shortfall with $k=0.08$.  Distribution derived from $N=6000$ simulations based on GARCH--DCC model.  Axes in both panels are same scale.  Black dots indicate actual outcomes.}
\label{figCBA}
\end{center}
\end{figure}
\bi
\i  Generally $\uparrow$ market return  leads to $\downarrow S$
\i  Radically different risk of shortfall under market scenarios
\i  How to ``stress test"?
\ei
}

\frame{\frametitle{``What if" analysis:  Stress testing}
\bi 
\i {\bf Response}: $S$ -- e.g. capital shortfall in a bank
\i {\bf Scenario}: $\omega$  -- e.g. drop in housing prices
   \bi\i Scenario is {\bf systemic} since expected to effect many banks
       \i e.g. $\omega$ is 25\% reduction in  house prices
       \i $\omega$ is usually a  SINGLE scenario
    \ei
\i  {\bf Real world probability}: $f(\omega)$ known or unknown
\i {\bf  Baseline risk (BASRISK)}: $\E(S)$
\i  {\bf Stress function}: $\psi(\omega)=1/f(\omega)$, for given $\omega$, 0 otherwise
\i  {\bf Stressed probabilities}: $\tilde f(\omega) = \psi(\omega)f(\omega) = 1$, 0 otherwise
\i  {\bf Stressed risk}: $\widetilde\E(S) = \E(S|\omega)$
\i {\bf $\psi$--risk (PSIRISK) in $S$}: $\psi_S = \widetilde\E(S)-\E(S)$
\i  {\bf Modelling -- Computation}:   Spreadsheet to see effect on banks balance sheet and in particular on capital shortfall $S$.
\ei   
}

\frame{\frametitle{Stress testing:  proposed   ``framework/theory"}
\bi
\i   {\bf Response} random variable \framebox{$S$} 
\bi \i E.g. $S$ is the future capital shortfall of a bank or group of banks.  Or  indicator of a positive shortfall. \ei
\i {\bf Scenarios}  \framebox{$\omega$}. Mutually exclusive and exhaustive
\bi 
\i  best thought of as (generated by) one or more variables  ({\bf stressors}?)
\i  {\bf systemic} if they have impact on many response variables
\ei

\i {\bf Real world probabilities}:  \framebox{$f(\omega)$} 
\i  {\bf Baseline risk}: \framebox{$\E(S)\equiv\sum_\omega f(\omega) \E(S|\omega)$} 
\bi      \i If $\omega$  continuous then $f(\omega)$ is  a density, expectation an integral \ei
\i {\bf Stress function}: \framebox{$\psi(\omega)\ge 0$  with  $\E(\psi)=1$}
\bi
\i $\psi$ is  often subjective
\i $\psi$ can be regarded as a random variable on space of scenarios
\ei
\i {\bf Stressed probabilities}: {\small\framebox{$\tilde f(\omega)\equiv \psi(\omega)f(\omega)$}}
\bi \i $\psi(\omega)>1$ implies scenario $\omega$ is amplified  in importance \ei 
\i {\bf Stressed risk}:
\framebox{$ \widetilde \E(S) \equiv \E(\psi S)= \sum_\omega \tilde f(\omega)\E(S|\omega)$}   
\i {\bf $\psi$--risk} in $S$: \framebox{$\psi_S\equiv \widetilde\E(S)-\E(S)$}
\bi \i If $\psi(\omega)$ is constant then $\psi_S=0$ \ei
\ei
}

\frame{\frametitle{Example (1)}
  \bi
  \i  {\bf Response}:  $S$ -- capital shortfall in a bank
  \i  {\bf Scenario(s)}: $20\% $  housing market ``correction" 
  \bi
  \i Scenario is {\bf systemic} since expected to effect many banks
  \ei
  \i  {\bf Real world probabilities}: $f(-20\%)=?$
  \i  {\bf Stress function}: $\psi(-20\%)=1/f(-20\%)$, 0 otherwise
  \bi
  \i   completely emphasises -20\% outcome, \framebox{ignores all others}
  \i  $\E(\psi)=1$; direct calculation
  \ei 
  \i  {\bf Stressed probabilities}: $\tilde f(\omega) \equiv \psi(\omega)f(\omega) = \framebox{1 or 0}$
  \i {\bf Stressed risk}:   $\widetilde\E(S) \equiv \E(S|-20\%)$
  \i {\bf $\psi$--risk in $S$}: \framebox{$\psi_S \equiv \widetilde\E(S)-\E(S)$} ... ``elevated risk due to $\psi$"
  \i {\bf Computations}:   Spreadsheet or similar
  \i {\bf Criticisms}:   One scenario emphasised -- \framebox{all others ignored}
  \ei
}

\frame{\frametitle{Example (2) ... more realistic}
  \bi
  \i  {\bf Response}:  $S$, capital shortfall in a bank
  \i  {\bf Scenarios}: $0\le \omega\le 1 $   {\bf percentile} housing market downturn
  \bi
  \i Scenario is {\bf systemic} since expected to effect many banks
  \ei
  \i  {\bf Real world probabilities}: \framebox{$f(\omega)=1$}, the uniform density
  \i  {\bf Stress function}: \framebox{$\psi(\omega)=n(1-\omega)^{n-1}$}
  \bi
  \i   emphasises lower (bad) percentiles ; downplays others
  \i  $\E(\psi)=1$; direct calculation
  \ei 
  \i  {\bf Stressed probabilities}: $\tilde f(\omega) \equiv \psi(\omega)f(\omega) = \framebox{$n(1-\omega)^{n-1}$}$
  \bi
  \i  density of the {\bf worst percentile in $n$ independent trials}
  \ei 
  \i {\bf Stressed expectation}:   $\widetilde\E(S) \equiv \int_0^1\tilde f(\omega)\E(S|\omega)\de\omega=\E(S|\Omega)$
  \bi
  \i $\Omega$ is the event ``worst market outcome in $n$ months"
  \ei
  \i {\bf $\psi$--risk}: \framebox{$\psi_S \equiv \widetilde\E(S)-\E(S)$} ... ``elevated risk due to $\psi$"
  \ei
}

\frame{\frametitle{Example (3), (4), ...}
\bi
\i   Other response variables \framebox{$S$}
\i   Other scenario spaces/stressors \framebox{$\omega$}
\bi
\i   Oil prices fall ...,  Metal prices fall ...., Interest rates rise ... 
  terrorist attack ..., bank X collapses ..., Grexit ...
\i   Combinations (product spaces $\bigotimes$) of the above
\i   \framebox{percentile outcome} of a variable
\ei
\i   Real world probabilities \framebox{$f(\omega)$}
\bi \i Perhaps from a model 
\i Copulas useful if $\omega$ percentile and $\bigotimes$
\ei
\i   Stress function \framebox{$\psi(\omega)$}
\bi
\i Model $f(S,\omega)=f(\omega)f(S|\omega)$ and stress $f(\omega)$
\i If \framebox{$\omega$} percentile outcome  of a variable then $f(\omega)=1$ and then can perform \framebox{percentile} stressing
\ei
\ei
}

\frame{\frametitle{Understanding $\psi$--risk  (PSIRISK)}
$$
\widetilde\E(S) \equiv \sum_\omega \tilde f(\omega)\E(S|\omega) = \sum_\omega \psi(\omega)f(\omega)\E(S|\omega) 
$$$$
= \E(S\psi)=\E(S)\E(\psi) +\cov(S,\psi) =  \E(S) + \cov(S,\psi)
$$
\bi
\i \framebox{BASRISK$\equiv\E(S)$} ... baseline risk not allowing for $\psi$
\i \framebox{PSIRISK$\equiv\psi_S\equiv\cov(S,\psi)
 =\widetilde\E(S)-\E(S)$} ... extra risk
\bi
\i   $\psi_S$ large if $S$ and $\psi$ have large covariance
\i   $\cov$ is linear in $S$ and $\psi$ ... even if components  dependent
\i   $\cov(S,\psi)=\cov\{\E(S|\psi),\psi\}$
\ei
\i \framebox{PSIVOL=$\sigma_\psi\equiv\sqrt{\psi_\psi}$} ... $\psi$--volatility
\bi
\i $\psi(\omega)=1/f(\omega)$, 0 implies $\sigma_\psi=\e^{-\mathrm{logit}\{f(\omega)\}/2}$
\i unlikely scenario, $f(\omega)\approx 0$, implies huge PSIVOL
\ei
\i \framebox{$\E(S|\psi=x) \approx   \E(S) + \frac{\psi_S}{\sigma^2_\psi}(x-1)=\mathrm{BASRISK}+\frac{\mathrm{PSIRISK}}{\mathrm{PSIVOL}} z_x$}
\ei
}

\frame{\frametitle{Understanding PSIRISK (cont.)}
$$
\framebox{$-1\le\frac{\widetilde\E(S)-\E(S)}{\sigma_S\sigma_\psi}= \frac{\psi_S}{\sigma_S\sigma_\psi}
=\frac{\cov(S,\psi)}{\sqrt{\cov(S)\cov(\psi)}}\le 1$}
$$
\bi
\i {\bf Stress ``z--score"}: 
\framebox{$z\equiv \frac{\widetilde\E(S)-\E(S)}{\sigma_S}=\frac{\psi_S}{\sigma_S}=\sigma_\psi\cor(S,\psi)$}
\bi
\i ``connection" between $S$ and $\psi$  multiplied by $\psi$--vol
\i not affected by $S$ units of (linear) measurement
\i $|z|\le \sigma_\psi$
\i perhaps $z>2$ regarded as ``stressful" 
\ei
\i {\bf Standardised  $\psi$--risk}:
\framebox{$\psi_S^* \equiv \frac{\psi_S}{\sigma_\psi}=\frac{\widetilde\E(S)-\E(S)}{\sigma_\psi}=\sigma_S\cor(S,\psi)$}
\bi
\i  ``connection" between S and  $\psi$ multiplied by $S$--volatility
\i facilitates comparison across different stressors $\psi$
\i not affected by $\psi$-vol
\i $\E(S|\psi=x) \approx \E(S) +\psi_S^*\times\frac{x-1}{\sigma_\psi}$ so $\psi_S^*$ is std reg coef $S$ on $\psi$
\i $\frac{\E(S|\psi=x) - \E(S)}{\sigma_S} \approx \cor(S,\psi)\times \frac{x-1}{\sigma_\psi}$
\ei
\ei
}

\frame{\frametitle{BASRISK and PSIRISK computations}
\bi
\i Suppose   a model leading to $f(S,\omega)\equiv f(\omega)f(S|\omega)$
\bi
\i Repeat $N$ times:   $\omega\sim f(\omega)$ and $S(\omega)\sim f(S|\omega)$ then
\i  BASRISK= Baseline Risk = $\E(S)\approx \frac{1}{N}\sum_\omega S(\omega)$ 
\i PSIRISK$=\psi_S=\widetilde\E(S)-\E(S) \approx\frac{1}{N}\sum_\omega \{\psi(\omega)-1\}S(\omega)$
\ei
\i  Alternatively construct estimates of $\E(S)$ and $\E(S|\psi)$
\bi
\i   Perhaps via spreadsheet
\i  $\psi_S = \cov\{\E(S|\psi),\psi\}$
\ei
\i  If $\psi(\omega)$ is based on percentile of $\omega$ then
\bi
\i  $\psi(\omega) = \phi\left\{F(\omega)\right\}$ with $F(\omega)\approx\mathrm{rank(\omega)}/N$
\ei
\i With many stressors  $\omega$ is vector and $F(\omega)$ is a joint distn
\bi
\i  For perc stress $\psi(\omega)=\phi\{F(\omega)\}$ where $\phi$ is a copula density
\bi
\i  $\phi$  imposed ``danger" density
\i   eg What if worst outcome in $n$ years  in many stressors
\ei
\ei
\ei  
}

\frame{\frametitle{Percentile stressing}
\bi
\i $0\le\omega\le 1$ is the percentile of a variable: $f(\omega)=1$
\bi
\i E.g. housing market growth rate
\ei
\i Further suppose the stress function is
$$
\framebox{$\psi(\omega) = n(1-\omega)^{n-1} = \frac{\de\{1-(1-\omega)^n\}}{\de\omega}$}
$$
\i $\p\{\min(u_1,\ldots,u_n)\le\omega\}=1-\p(u_1>\omega)\cdots\p(u_n>\omega)$
\i $1-(1-\omega)^n$ is distn of min of $n$ independent uniforms
\i $\widetilde\E(S) \approx \frac{1}{N}\sum_\omega n(1-\omega)^{n-1}S(\omega)$
\bi 
\i $S(\omega)$ for $\omega\approx 0$ given large weight
\i $\widetilde\E(S)$ is the expectation given the worst
outcome in $n$ ``months"
\ei
\i Can generalize to eg $\psi(\omega)=c\e^{-\lambda\omega}$
\i $\psi(\omega)=\frac{I(\omega\le\alpha)}{\alpha}$ leads to $\widetilde\E(S)=\E(S|\omega<\alpha)$
\ei
}

\frame{\frametitle{Australian Banks equity $w$}
\begin{figure}[htbp]
\begin{center}
\includegraphics[width=10cm]{figures/prices.pdf}
\caption{Stock  prices of four major (left panel) and four minor (right panel) Australian banks from early 2000 through to the end of 2014.  Price series normalised to start at 1.}
\label{prices}
\end{center}
\end{figure}
}

\newcommand{\vareps}{\varepsilon}

\frame{\frametitle{Stress on Aust bank from market downturns}
\bi
\i  $S=dk(1-\e^{r-\ell})$ bank shortfall; $r$ is forward rate of return
\i  Stressor $\omega$ -- general stock market return
\i   \framebox{$f(S,\omega)$} from \framebox{$\delta_t\sim$ TARCH(1,1)-DCC}
\i  $\delta_t$ drives $r$ (monthly return) and $S$ (shortfall at end of month)
\bi
\i \framebox{$\delta_{t}=\mu+\sigma_{t}\eps_{t}$}  ...  $\eps_{t}\sim (0,1)$
\i \framebox{$ \sigma_{t+1}^2 = \omega+ \sigma^2_{t}\{\beta+(\alpha+\gamma \eps^-_{t})\eps_{t}^2\}$} ... volatility $\sigma_t$ is dynamic
\i $\eps^-_{t}\equiv I(\eps_{t}<0)=I(\delta_{t}<\mu)$
\ei 
\i  Similar model for daily \framebox{market} return
\i Correlation bank/market return from recursion -- \framebox{DCC}
$$
(Q_{t+1}-S) = \alpha (\eta_{t}\eta_{t}'-S) + \beta (Q_{t}-S)\cq \eta_{t}\equiv(\eps_{t},\eps_{mt})' .
$$
\i  Estimate unknown parameters -- quite a few -- use \framebox{R}
\bi
\i Model estimated to end of each month (2003 -- 2015)
\ei
\i  Project/simulate model forwards 1 month
\bi
\i  Use ``bootstrapped" $\eta_t$ in forward projection
\i  Use same ``bootstrapped" $\eps_{mt}$ for different joint models
\ei
\ei
}

\frame{\frametitle{CBA and market return}
\begin{figure}[htbp]
\begin{center}
\includegraphics[width=9cm]{figures/figCBA.pdf}
\caption{Forecast bivariate distribution of one month rates of return   for CBA and the market rate of return}
\label{figCBA}
\end{center}
\end{figure}
\bi
\i  Daily model is ``cranked" forward 1 month
\i  No ``look ahead" bias -- use only past data relative to $t$
\i  Do same (ie estimate/project) at start of every month
\i  Bootstrapped errors:   error distribution ``like past"
\ei
}

\frame{\frametitle{Australian Banks: risks over time}
\begin{figure}[htbp]
\begin{center}
\includegraphics[width=8cm]{figures/default.pdf}
\caption{Forecast one month ahead  $\p(S>0)$ (top panels), BASRISK $\E(S^+)/(kd)$ (middle panels) and PSIRISK $\psi_{S^+}/(kd)$ 
(bottom panels) for  four major (left panel) and four minor (right panel)  banks 2003--2014.  Note different scale on bottom two rows of panels. $\psi$--risk is worst market outcome in 12 months.}\label{default}
\end{center}
\end{figure}
}

\frame{\frametitle{SRISK -- systemic risk}
\bi
\i Brownlees \& Engle (2015) define:
$$
\mathrm{SRISK} \equiv \sum_i\{\widetilde\E(S_i)\}^+ \cq 
\mathrm{SRISK}_i\equiv\frac{\{\widetilde\E(S_i)\}^+}{\mathrm{SRISK}}
$$
\bi 
\i $S_i \equiv kd_i\left(1-\e^{r_i-\ell_i}\right)$;  ``positive part of" is $^+$
\i stress is ``general market downturn greater than 10\%" 
\i  Computed at start of each month, looking 1 month forward
\i   SRISK$_i$ is \framebox{systemic risk} in firm $i$ 
\ei
\i Criticisms/Extensions of SRISK:
\bi
\i  Why not $\sum_i\widetilde\E(S_i^+)$: properties, alternatives 
\i  $\widetilde\E$ restrictive:  generalised here with $\psi$
\i  $\widetilde\E = \E + \cov$:  only cov  contains ``systemic" risk
\ei 
\i  Our definition incorporates all 3 adjustments and clarifies risk:
$$
\mathrm{BASRISK}\equiv \sum_i\E(S_i^+)\cq \mathrm{PSIRISK}\equiv \sum_i\cov(S_i^+,\psi) 
$$
\ei
}

\frame{\frametitle{Aggregate BASRISK and PSIRISK}
$$
\mathrm{BASRISK}\equiv \sum_i\E(S_i^+)\cq\mathrm{PSIRISK}\equiv \sum_i\cov(S_i^+,\psi)
$$
\bi
\i  components in  sums are BASRISK$_i$ and PSIRISK$_i$
\i  Risks additive eg PSIRISK$=\cov(\sum_iS_i^+,\psi)$
\i  \%PSIRISK in firm $i$ is $100\times\frac{\mathrm{PSIRISK}_i}{\mathrm{PSIRISK}}$
\i  Write $S_*=\sum_iS_i$ as the ``pooled" shortfall (pool $d$ and $w$) 
$$
\mathrm{BASRISK}_*\equiv \E(S_*^+)\cq \mathrm{PSIRISK}_*\equiv \cov(S_*^+,\psi)
$$
\i  $\mathrm{BASRISK}-\mathrm{BASRISK}_*=\E\left\{(\sum_iS_i^+)-(\sum_iS_i)^+\right\}\ge 0$
\i  $\mathrm{PSIRISK}-\mathrm{PSIRISK}_*=\cov\left\{(\sum_iS_i^+)-(\sum_iS_i)^+,\psi\right\}$ ?

\ei
}

\frame{\frametitle{BASRISK and PSIRISK at two dates}
 \begin{table}[ht]
\centering
\begin{threeparttable}
\tiny
\begin{tabular}{l|rrrr|rrrr}
\hline
&\multicolumn{4}{c|}{January 2009}&\multicolumn{4}{c}{November 2014}\\
\hline
   & Aloglev& Debt & BASRISK & PSIRISK  & Aloglev & Debt  & BASRISK & PSIRISK\\  
  \hline
CBA & 18.57 & 24.30 & 22.99 & 29.60 & -70.34 & 22.70 & 0.00 & 0.00 \\ 
  ANZ & 15.93 & 18.37 & 14.87 & 18.89 & -38.64 & 22.10 & 0.00 & 0.00 \\ 
  NAB & 31.97 & 25.50 & 39.98 & 19.41 & -12.45 & 25.61 & 50.52 & 67.13 \\ 
  WBC & -1.55 & 22.84 & 5.86 & 23.94 & -53.84 & 22.03 & 0.00 & 0.00 \\ 
  MQG & 41.22 & 5.75 & 11.02 & 5.46 & -46.10 & 4.33 & 0.17 & 0.12 \\ 
  BOQ & 63.30 & 1.32 & 3.55 & 0.99 & -17.05 & 1.33 & 0.80 & 1.34 \\ 
  BEN & 18.91 & 1.81 & 1.72 & 1.71 & -7.63 & 1.84 & 25.43 & 30.71 \\ 
  ABA & -8.12 & 0.10 & 0.00 & 0.00 & 9.22 & 0.07 & 23.07 & 0.71 \\ 
  \hline
  Total & 18.78 &  & 17.17 & 8.63 & -41.91 &   & 0.03 & 0.12 \\ 
  * (pooled) & 17.81 & 2.42 & 15.28 & 10.18 & -44.22 & 3.27 & 0.00 & 0.00 \\ \hline
\end{tabular}
\begin{tablenotes}
\item[]Response is $S_i^+$, the positive part of capital shortfall. PSIRISK is with respect to expected worst monthly market return  in 12 months.  Main body of table displays percentage contributions of each firm to total debt, BASRISK and PSIRISK.   ``Total" row displays debt weighted average of adjusted log--leverage, BASRISK and PSIRISK are per $100k\times$debt.    Pooled  displays   results with debt and equity pooled across banks: pooled debt is in \$$10^{11}$.  Pooled   BASRISK and PSIRISK are per $100k\times$debt.  
\end{tablenotes}
\end{threeparttable}
\end{table}
\normalsize
\bi
\i  PSIRISK:   worst {\bf monthly} market return  in 12 months
\bi
\i given \framebox{then current} {\bf daily}  return distribution
\ei
\i  PSIRISK-PSIRISK$_*$ measures absorbability
\i  Jan 2009:   PSIABS$<0$ ... non absorbable $\psi$--risk
\ei 
}

\frame{\frametitle{BASRISK and PSIRISK  over time}
\bi
\i  System risk: worst market outcome in 12 months
\begin{figure}[htbp]
\begin{center}
\includegraphics[height=4cm]{figures/muqs.pdf}
\end{center}
\end{figure}
\i Top panels 
\bi 
\i  Left panel BASABS=BASRISK$-$BASRISK$_*\ge 0$ 
\i  Right panel PSIABS=PSIRISK$-$PSIRISK$_*\ngeqslant 0$
\i  PSIRISK can be ``contagious"
\ei
\i  Bottom panels:
\bi
\i  BASRISK (x--axis) versus  BASRISK$_*$  ... ditto for PSIRISK
\i  Contagion effects builds up ``later"
\ei   
\ei
}

\newcommand{\Ax}{{\cal A}}
\frame{\frametitle{Formalising risk weighted assets methodology}
Future shortfall in terms of assets $a\equiv d+w=\sum_ja_j$
$$
S\equiv  d-\alpha\Ax(\e^{r_j})\cq \alpha\equiv(1-k)a\cq \Ax(\e^{r_j})\equiv \sum_j\frac{a_j}{a}\e^{r_j}
$$
\bi
\i  $r_j$ is (uncertain) log--return on assets $a_j$
\i $\E(S)=d-\alpha\E\{\Ax(\e^{r_j})\}=d-\alpha\Ax\{\E(\e^{r_j})\}$
\i  Risk weighting methodology:  replace $\frac{a_j}{a}$ weights by $
\frac{a_j}{a\sigma_j}$
\bi
\i   How to determine the weights $\sigma_j$?
\ei
\i PSIRISK approach: replace $\E$ by $\widetilde\E$ using suitable $\psi$
\bi
\i $\psi_S=\widetilde\E(S)-\E(S)= -\alpha\cov\left\{\Ax(\e^{r_j}),\psi\right\}=-\alpha\Ax\{\cov(\e^{r_j},\psi)\}$
\i $\psi_S\approx -\alpha\Ax\{\cov(r_j),\psi\}$ since $\e^{r_j}\approx 1+r_j$
\i $\cov(r_j,\psi)\ll0$ implies  $a_j$ is  discounted
\ei
\i  Modelling
\bi
\i  Simulate from $f(r_j,\psi)=f(\psi)f(r_j|\psi)$ eg GARCH-DCC
$$
 \mathrm{BASRISK}\approx d-\alpha\Ax\{\E(r_j)\}\cq  \mathrm{PSIRISK}\approx -\alpha\Ax\left\{\cov(r_j,\psi)\right\}
$$
\i Alternatively use $f\{\Ax(r_j),\psi\}=f(\psi)f\{\Ax(r_j)|\psi\}$
\i if using eg $S^+$  then calculate $\psi_S$ via $\widetilde\E(S^+)-\E(S^+)$
\ei
\ei
}

\frame{\frametitle{Conclusions}
\bi
\i Have presented a consistent methodology for stress testing
\i Formalises intuitive approach to stress testing
\i Requires:
\bi
\i  An appropriate response subject to potential stress
\i  Scenario space
\i  Natural scenario probabilities
\i  Stress function defined on scenario space
\i A joint statistical model for the response and scenarios
\ei
\i Frameworks leads to natural definitions of
\bi
\i BASRISK -- baseline risk
\i PSIRISK -- risk due to assumed stress
\ei
\i BASRISK and PSIRISK aggregate additively
\i Concepts provide framework for defining risk diversifiability and contagion
\ei
}

\end{document}

### 2016-10-09 srisk10.tex
Lots and lots of changes
Latest

\documentclass[authoryear]{elsarticle}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf,comment}
\usepackage{enumerate}
\usepackage{url} % not crucial - just used below for the URL 
\bibliographystyle{chicago}
\usepackage{threeparttable}

\newcommand{\logit}{\mathrm{logit}}
\newcommand{\I}{\mathrm{I}}
\newcommand{\E}{\mathrm{E}}
\newcommand{\p}{\mathrm{P}}
\newcommand{\e}{\mathrm{e}}
\renewcommand{\o}{\omega}
\newcommand{\vecm}{\mathrm{vec}}
\newcommand{\kp}{\otimes}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\cov}{\mathrm{cov}}
\newcommand{\eps}{\epsilon}
\newcommand{\ep}{\varepsilon}
\newcommand{\obdots}{\ddots}    % change this later
\newcommand{\Ex}{{\cal E}}
\newcommand{\Ax}{{\mathrm{A}}}
\newcommand{\Exd}{\Ex_d}
\newcommand{\Es}{\Ex}
\newcommand{\rat}{{\frac{c_{ij}}{c_{i,j-1}}}}
\newcommand{\rmu}{m}
\newcommand{\rsig}{  r}
\newcommand{\fd}{\mu}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\cor}{\mathrm{cor}}
\newcommand{\bx}[1]{\ensuremath{\overline{#1}|}}
\newcommand{\an}[1]{\ensuremath{a_{\bx{#1}}}}

\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}

\renewcommand{\i}{\item}
\newcommand{\SR}{\ensuremath{\mathrm{SRISK}}}
\newcommand{\sr}{\ensuremath{\mathrm{srisk}}}
\newcommand{\br}{\ensuremath{\mathrm{base\ risk}}}
\newcommand{\st}{\ensuremath{\mathrm{strain}}}
\newcommand{\pr}{\ensuremath{\mathrm{strain}}}
\newcommand{\cs}{\ensuremath{\mathrm{CS}}}
\newcommand{\cri}{\ensuremath{\mathrm{Crisis}}}
\newcommand{\var}{\ensuremath{\mathrm{VaR}}}
\newcommand{\covar}{\ensuremath{\mathrm{CoVaR}}}
\newcommand{\med}{\ensuremath{\mathrm{m}}}
\newcommand{\de}{\mathrm{d}}
\renewcommand{\v}{\ensuremath{\mathrm{v}_q}}
\newcommand{\m}{\ensuremath{\mathrm{m}}}
\newcommand{\tvar}{\ensuremath{\mathrm{TVaR}}}
\renewcommand{\c}{\ensuremath{\mathrm{CoVaR_q}}}
\renewcommand{\v}{\ensuremath{\mathrm{VaR}_q}}

\newcommand{\eref}[1]{(\ref{#1})}
\newcommand{\fref}[1]{Figure \ref{#1}}
\newcommand{\sref}[1]{Section \ref{#1}}
\newcommand{\tref}[1]{Table \ref{#1}}
\newcommand{\aref}[1]{Appendix \ref{#1}}

\newcommand{\cq}{\ , \qquad}
\renewcommand{\P}{\mathrm{P}}
\newcommand{\Q}{\mathrm{Q}}

\newcommand{\Vx}{{\cal V}}

\newcommand{\be}[1]{\begin{equation}\label{#1}}
\newcommand{\ee}{\end{equation}}

\newcommand{\D}{\mathrm{D}}

\begin{document}

\title{An early warning system for monitoring  stress in the financial system}
%\author[acst]{Piet de Jong\corref{cor1}\footnote{The authors gratefully acknowledge CIFR, the Centre of International Financial Regulation for financial support and other assistance}}
%\ead{piet.dejong@mq.edu.au}
%\author[acst]{Geoffrey Loudon}
%\author[acst]{Weihao Choo}
%\address[acst]{Department of Applied Finance and Actuarial Studies Macquarie University, NSW 2109, Australia.}
%\cortext[cor1]{Corresponding author}

\begin{abstract}
SRISK methodology recently proposed in the literature is refined and extended using a formalised stress testing framework.  The framework distinguishes between two types of risk:  basis risk and stress risk.
basis risk is defined as

 Both expectations are  based on a time series model and  observations to date.   Stressed expectation differs from the ordinary expectation in the imposition of an additional hypothetical  stress, modelled using a stress function and scenarios.  Stress risk is the difference between stressed expectation and ordinary expectation.  Stress functions are chosen by the practitioner and  exaggerate the probability undesirable  outcomes.    Properties and characterisations of stress and stress related quantities are displayed and explored.  Systemic stress is defined in terms of stresses   impacting groups of firms or financial entities.    Application is made to the study of the stability of Australian banks using daily time series data.
\end{abstract}

\date{}
\maketitle
\noindent
{\it Keywords:}  Capital shortfall, basis risk, stress testing,  stressed expectation, stress diversification.

\newpage

\section{Introduction}\label{intro}
Monitoring stresses and systemic risk in the financial system is a key function of macro--prudential regulation. Central banks and other financial regulatory bodies such as the US Financial Stability Oversight Council, the European Systemic Risk Board and the Australian Prudential Regulation Authority (APRA) are concerned with developing and applying early warning quantitative  measures  to warn of potential episodes of heightened systemic risk.

Systemic risk has many dimensions. For example, in their influential review paper, \cite{Bisias2012} present a taxonomy of six categories of systemic risk comprising 31 quantitative risk measures. While attempts to gain consensus on a theoretical definition have proved elusive, several empirical measures of systemic risk have been developed and applied with  success.  An important example is the SRISK measure due to \cite{brownlees2015} -- an index that measures the expected capital shortfall of a financial institution conditional on a large and lengthy decline in equity markets. \cite{brownlees2015} show that their SRISK based measures are able to identify systemically important financial firms and are informative about the impact of financial crises on future macro-economic conditions.

This paper refines and extends the SRISK model of \cite{brownlees2015} in  key ways. First SRISK is formalised  as a put on the expected shortfall with the ordinary expectation defined as the basis risk (\br) associated with the put.   Using a stress function  the so--called stressed expectation is used to measure the impact of stress.   Stressed expectation can be similar to the \cite{brownlees2015} conditional expectation given  a severe market downturn.  However our generalised methodology  permits a more flexible definition of stress and a wider class of ``stressors" including stress defined in terms of  a number of extreme outcomes.  The difference between the stressed and ordinary expectation is defined as the stress risk associated, called \pr\ where P stand for psi,  the function $\psi$ modelling the stress.

\br\  and \pr\  capture different aspects of stress on a firm. \br\  is a function of existing volatility and leverage. As these factors increase, \br\  rises and this makes the firm more susceptible to \pr, regardless of the stress event itself.   Properties of \pr\  are explored.

\cite{brownlees2015} define stress by conditioning on an absolute cutoff of arbitrary size and length. With time dependent volatility or uncertainty, absolute cutoffs  are less meaningful and our development suggests  it is  useful to specify conditional behaviour in percentile terms relative to current market conditions. This yields a sharper focus on the incremental impact of further stress and permits a more incisive view of the  implications from SRISK numbers. These extensions provide additional insights into the sources and economic nature of for example systemic risk. The measures provide potentially new and improved ways of anticipating episodes of heightened systemic risk. Their practical use can be expected to help regulators monitor risk including systemic risk and contagion in timely fashion,   facilitating remedial action where necessary.

While our measures are designed for use in all financial systems, it is of particular interest to test them using the Australian setting for at least two reasons. First, the Australian financial system is dominated by only four banks. In Australia there are four major banks that hold 78\% of the total assets of all Authorised Deposit-taking Institutions in  Australia.\footnote{Based on balances at 31 December 2014 disclosed in APRA's Quarterly Authorised Deposit-taking Institution (ADI) Performance Report for March 2015.} It is therefore obvious that the four majors are systemically important and the remaining ADIs are not so unless stress in one of these minors somehow creates financial contagion to the majors, in an unforeseeable way. Second, the Australian banking system proved to be resilient through the recent global financial crisis (GFC), implying that systemic risk did not reach the extreme levels experienced by other countries where bank failures occurred. Both these features of the Australian system suggest that it may be difficult to find useful additional information about systemic risk by refining quantitative measures like SRISK. Since we are able to show that our measures are informative about systemic risk in Australia, we conjecture that they will provide additional insights elsewhere.

The nature and usefulness of our measures are demonstrated using publicly available daily financial data for the eight Australian banks detailed in \tref{eightbanks} spanning the period from  3 April 2000 through to 1 December 2014.  The data is described in detail in \aref{data}.  Prices, adjusted for dividends are plotted in \fref{prices}.  Prices are combined with number of shares to derive total equity. Total debt for each firm is also collected from annual accounting reports.

Remaining sections are structured as follows. Section \ref{litrev} briefly discusses related literature. Section \ref{capshort} defines current and future  capital shortfall similarly as \cite{brownlees2015} under a simple Basel II regulatory framework. The definition of systemic risk used by \cite{brownlees2015} is discussed, refined and improved in \sref{srisk}. Applications to Australian bank data are discussed in \sref{simulate} and \sref{simulate1}. Section \ref{aggregate}  discusses the aggregation of  stresses across firms with and without allowance for merging or diversification. Section \ref{monitoring} displays stress calculations as they would proceed in real time.   Section \ref{riskmethod} offers an alternative modelling approach, based on assets.  Section \ref{conclude} concludes.

\begin{table}[htbp]
\label{banks}\caption{Major and minor Australian banks}\label{eightbanks}
\begin{center}
\begin{tabular}{l|l|l|l}
\hline
 \multicolumn{2}{c|}{major}& \multicolumn{2}{c}{minor}\\
 \hline
CBA & Commonwealth Bank  & MQG & Macquarie \\
ANZ & Australia \& New Zealand  & BOQ & Bank of Queensland\\
NAB & National Australia  & BEN & Bendigo and Adelaide \\
WBC & Westpac & ABA& Auswide \\
\hline
\end{tabular}
\end{center}
\end{table}%

\begin{figure}[htbp]
\label{prices}
\begin{center}
 \begin{tabular}{cc}
      \resizebox{55mm}{!}{\includegraphics{figures/fig1a.pdf}} &
      \resizebox{55mm}{!}{\includegraphics{figures/fig1b.pdf}}\\
    \end{tabular}
\caption{Daily stock  prices of four major (left panel) and four minor (right panel) Australian banks 2000--2014.  Price series normalised to start at 1.}
\end{center}
\end{figure}

\section{Literature review}\label{litrev}
Many papers in the finance and economics literature are devoted to the development and application of a variety of quantitative measures of systemic risk or financial stress. \cite{Bisias2012} provide an instructive and qualitative survey of numerous measures in use. \cite{Giglio2015} supply empirical evidence on the ability of many of these measures, both individually and collectively, to provide early warning signals of deterioration in macro-economic conditions. In this section, we provide a selective overview of those measures most closely related to SRISK and its relevance for assessing systemic risk in the financial sector.

The genesis of SRISK lies in a series of papers including \cite{acharya2012aer}, \cite{acharya2012wp} and \cite{brownlees2010volatility}. In these papers, SRISK is defined as the expected capital shortfall of a financial firm, conditional on a crisis. A crisis is deemed to occur whenever a relevant market index suffers a significant decline over a chosen horizon. SRISK measures require an estimate of the long run marginal expected shortfall (LRMES) typically obtained by simulation methods.

\cite{brownlees2015}  develop empirical methodology to construct SRISK measures. SRISK depends on the firm's size, leverage and its LRMES. The LRMES is obtained by assuming a dynamic process for the joint distribution of firm and market returns. \cite{brownlees2015} use  the standard GARCH-DCC model of \cite{engle2002dynamic} with threshold ARCH volatilities on the basis that this represents a good trade-off between model complexity and prediction accuracy. The LRMES is computed as the Monte Carlo average of simulated multi-period returns,  conditional on the return being worse than the cut-off level chosen to identify a financial crisis. Using a sample of large US financial firms,  \cite{brownlees2015} show the practical usefulness of their measure in three ways: (i) SRISK rankings identify systemically risky US banks during the GFC; (ii) pre-crisis SRISK helps predict capital injections by the Fed Reserve; (iii) aggregate SRISK provides early warning of declines in industrial production and higher unemployment.

\cite{Engle2015} extend the model in \cite{brownlees2015} to incorporate global, country and industry effects. This extended model makes  use of the \citep{Engle2014dcb} dynamic conditional beta model. Their empirical methods are able to provide information about the relative systemic importance of industry type and country identity. For instance, they find  that systemic risk in Europe during the GFC was predominantly due to banks while France and the UK recorded the largest country-level SRISK numbers.

\cite{adrian2011covar} propose an alternative measure of systemic risk  emphasising the co--dependence of financial firms and the importance of risk spillovers within the financial sector. They introduce CoVaR$_i$ which computes the Value--at--Risk (VaR) of the entire financial system, conditional on institution $i$ being in distress. Distress is defined as the state where the institution is exactly at its VaR level. \cite{Girardi2013} improve CoVaR by conditioning on the institution being at most at its VaR. This generalisation is useful as it takes into account the severity of tail losses and facilitates back--testing of CoVaR.

\cite{acharya2012aer} relate SRISK and CoVaR and demonstrate that assuming the joint distribution of returns is conditionally normal, SRISK is a more complete measure. \cite{Benoit2013} show how several popular systemic risk measures including MES, CoVaR and SRISK are different transformations of market risk measures and derive those conditions under which they provide similar rankings of systemically important financial institutions.

Empirical estimates of SRISK  requires a model for the joint distribution of returns of individual firms and the market. Many of these papers use \cite{engle2002dynamic}'s GARCH--DCC model aiming to capture the time-varying dynamics of the return (co)variances in a feasible manner. While we also use this model in our empirical analysis, we emphasize that our approach can utilise any appropriate model for simulating the joint distribution of firm and market returns going forward.

\section{Capital requirements, leverage and future shortfall}\label{capshort}

If $d$ and $w$ are the debt and equity, respectively, of a  firm  and $k$ is the prudential requirement,  then  following \cite{brownlees2015}, the   capital requirement is
\be{capreq}
k (d+w)-w = k d\left(1-\frac{1-k}{kL}\right)=kd\left(1-\e^{-\ell}\right)
\ ,
\ee
where
\be{lev}
L=\frac{d}{w}\cq \ell=\ln\left(\frac{kL}{1-k}\right) = \logit(k) + \ln(L) \ .
\ee
The capital requirement \eref{capreq} is positive if $\ell>0$. Note $kd$ is the proportion of debt $d$ required as capital if equity $w=0$.  Each unit of  $w$ is counted $1-k$ towards required capital.     Alternatively $k$ is the proportion of assets $d+w$ excluded from capital calculations, and higher $k$ leads to higher capital shortfall.

A negative capital requirement -- that is a   surplus relative to requirements -- occurs  if $\ell<0$.   The default index $\ell$ is the rate of return $r$ that must be achieved in order for the firm to be on the just out of  default.   The default index $\ell$ depends on $k$, the prudential fraction.

\subsection{Basel default}
If $k=8\%$ and  \eref{capreq} is positive then the  firm or financial institution is said be in ``Basel default" or a ``Basel breach" has occurred.  The value\footnote{See for example \cite{brownlees2015}.} $k=8\%$ is the Basel fraction and  implies $\logit( k)=-2.44$ and
$
\ell = \ln(L) - 2.44
$.   A firm is said to be in Basel default if the default index $\ell>0$ and $\ell$ can be considered as an index of the degree to which a firm is in default.  Note  $\logit(k)$ enters $\ell$ as an additive constant and has  minor role in the subsequent technical development and can be varied to test for sensitivity to $k$.

The shorfall definition \eref{capreq} is simplistic and restrictive.   The definition and value $k=8\%$ is used here to conform to the previous literature and provide an easily accessible  platform to the key results of this paper,  without becoming entangled in precise and perhaps more realistic definitions of shortfall.   \sref{riskmethod} deals with a more realistic but more intricate definition.

\fref{Bloglev} displays default index $\ell$ with $ k=8\%$ for the four major and four minor Australian banks listed in \tref{banks} on the first trading day of each month from January 2003  through to December 2014.  Note most banks are Basel compliant up to about 2008, entering into Basel default from 2009 as a result of the GFC. Prolonged Basel defaults are experienced for some banks, notably NAB.

\begin{figure}[htbp]
\begin{center}
\includegraphics{figures/fig2.pdf}\caption{Basel default index  for four major (left panel) and four minor (right panel) Australian banks from the beginning of 2003 through to end of 2014.  All banks contravene the threshold (corresponding to the zero horizontal) around the start of 2009.}\label{Bloglev}
\end{center}
\end{figure}

\subsection{Future capital requirement and shortfall}

Financial institutions and regulators are concerned with future capital requirements, say in in a months time and in particular any potential shortfall.   Given the definition \eref{capreq}  the future capital requirement of the firm depends on the future return on equity $r$.   The future future equity is then  $w\e^{r}$ and assuming, as in \cite{brownlees2015} debt $d$ is constant, the  future capital requirement is, per unit $kd$ and analogous to \eref{capreq}, 
\be{fcapreq}
   S=1-\frac{1-k}{kL\e^{-r}} =1-\e^{r-\ell}\ .
\ee
The future return $r_i$ is unknown but its probability distribution may be relatively well understood and modelled.  Note $-\infty<S\le 1$ with $S=1$ indicating the future capital requirement is $kd$.

The positive part of \eref{fcapreq} is the future capital shortfall per unit $kd$
\be{bs}
S^+ = \left\{\begin{array}{lr} 0\ , & r\ge \ell\ ,\\ 1-\e^{r-\ell}\ , & r<\ell\ ,\end{array}\right.  
\ee
where $^+$ denotes the ``positive part of."  
Thus $S^+$ is  a put\footnote{Since $\E(S^+)=\E(S>0)\E(S|S>0)$ where   $\E(S^+)$ is the default probability  and $\E(S|S>0)$ is a measure of ``tail risk."   Both the default probability and tail risk are  defined relative to  $k$.  Since the expectation is ``normal" the probability and tail risk are both ``base" cases.} on the return $\e^{r-\ell}$ with strike 1 and $0\le S^+\le 1$.  From \eref{bs}, the  default index $\ell$ is the rate of return $r$ that must be achieved over the future period for the firm to just attain Basel solvency.   Default put options similar to \eref{bs} have been discussed in the insurance literature as critical to an evaluation of a firm:  see for
example \citet{merton1977analytic}, \citet{doherty1986price}, \citet{cummins1988risk}, \citet{myers2001capital} and \citet{sherris2006solvency}.

\subsection{Projecting future shortfall -- motivating example}
In subsequent sections  time series methods are used to project future capital requirements \eref{fcapreq}  and in particular future shortfall $S$ defined in \eref{bs} for different firms $i$, under basis conditions and under stressed scenarios.   These forecasts are used to determine the stress of both individual firms $i$ and the system as a whole.   To understand the basis of the approach \fref{simulation},   displays two snapshot outputs from projections generated as described  in \aref{garchdcc}:  6000  simulated one month ahead projected returns for  CBA and the wider market, on  two dates: the first trading day in January 2009 and the first trading day in December 2014.  The CBA returns are used to calculate the future shortfall per units $kd$ as in \eref{fcapreq}.  Both panels use the same horizontal and vertical scales.   Based on the available data at those two points in  time, policy makers and regulators faced entirely different projections.   The scatter of dots are the forward simulations.  Note there is no hindsight bias as the model at each time point is based on the available data to that point in time.     In the left panel $S>0$ and a positive capital shortfall is projected for most scenarios.    In the right panel $S=0$ and the banks are projected to have capital surpluses relative to requirements for any conceivable market scenarios.

 The black dots in each panel indicate the actual outcome after one month.    In the left panel the outcome is a decline in both  the market and CBA stock price.    In the right panel there is slight decline in the stock price, and a more substantial market downturn.    Thus at the beginning of January  2009 the one month forward projection for  CBA was far from compliance, while in December 2014 the one month forward projection is of complete compliance.

The two panels  display very different volatility and slopes. In January 2009 both CBA and the market return distributions are highly volatile and correlated. The correlation remains strong in December 2014 but with less return volatility.  Subsequent sections of this paper use time series of these  snapshots  to compute cross sectional and longitudinal basis and systemic stresses.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=12cm]{figures/figCBA.pdf}
\caption{Forecast bivariate distribution of $C$ the projected  one month ahead capital requirement for CBA per unit $kd$ versus the market rate of return at start of January 2009 (left panel)  and December 2014 (right panel). Note scales in both panels are the same, the relatively large volatility in the left panel, and the left skew in the  marginal distributions.  Black dots indicate actual  outcome at the end of each month.}\label{simulation}
\end{center}
\end{figure}

\section{Monitoring systemic risk}\label{srisk}

 \cite{brownlees2015} define  systemic risk\footnote{In contrast to \cite{brownlees2015} we factor out the scale factor $kd$ making for a more transparent 0 to 1 scale for \SR.} for a group of firms in terms of the expected future capital requirement $S_i$ for each firm $i$ in the group:
\be{esrisk}
\SR =  \sum_i \pi_i\left\{\Es(S_i)\right\}^+ = \D[\{\Ex(S_i)\}^+]\cq \pi_i = \frac{d_i}{d}\cq d=\sum_id_i \ ,
\ee
where $S_i$ is the shortfall \eref{fcapreq} for firm $i$.
Here $\Es$ denotes expectation given the systemic event of a major general market downturn and $\D$ is debt weighted averaging.    Further \SR\ is expressed in units $kd$ and $0\le\SR\le 1$ with \SR\ near 1 indicating extreme financial distress for all firms. \SR\ is based on the expected capital requirement and firms with an expected capital surplus under stress are ignored.   The expression \eref{esrisk} slightly modifies the definition  of \cite{brownlees2015} by dividing their \SR\ expression by $kd$.

The proportional contribution of firm $i$ to \SR \eref{esrisk}  is defined by   \citep{brownlees2015} as
\be{sriskperc}
\SR_i=\frac{\pi_i\{\Ex(S_i)\}^+}{\SR} \ .
 \ee
 Note $0\le \SR_i\le 1$ with larger values indicating firm $i$ is systemically important: it holds a high proportion $\pi_i$ of the total debt, and/or is likely to heavily breach the Basel capital requirement.  Expression \eref{sriskperc} depends on $k$ through each of the default indexs $\ell_i$.

In this article we propose four modifications to \SR\ and $\SR_i$ defined in \eref{esrisk} and \eref{sriskperc}.   These modifications are designed to improve stress monitoring.  The  modifications  are shown,  theoretically and empirically, to have more  sensitivity and specificity.   Sensitive, in the sense of more likely detect  firms likely to face financial distress.   Specific in the sense of   minimising false alarms.  The modifications are:
\begin{enumerate}
\item  Replacing $\{\Es(S_i)\} ^+$ in \eref{esrisk} and \eref{sriskperc} by $\Es(S_i^+)\ge\{\Es(S_i)\} ^+$. The justification is that typically $\Es(S_i)=0$ and  hence \eref{esrisk} is not affected by firms that  have zero expected capital requirement even though in individual instances that capital requirement may be large.   Using $\Ex(S^+_i)$ instead of $\Ex(S_i)$ implies each firm counts with degree depending on the its proportionate contribution $\pi_i$ to total debt and the expected value of a put on its shortfall.  Thus the analogue of \SR\  in \eref{srisk} is 
\be{srisk2}
\sr=\Ex\{\D(S_i^+)\} = \D\{\Ex(S_i^+)\} = \sum_i\pi_i(\sr_i)\ ,
\ee
where $0\le \sr_i\le 1$ and $\pi_i(\sr_i)$ is the proportion of \sr\ originating in firm $i$.

\item Using more general   definitions of $\Es$ to encompass more flexible stress specifications.   Modelling stress  as  10\% market general market downturn or more, while interesting, is obviously arbitrary.   This paper posits more flexible and robust specification of stressed expectation $\Ex$.   This is discussed in \sref{formal}.

\item The srisk defined in \eref{srisk2} is broken up into two components
\be{breakup}
\sr=\D\{\E(S_i^+)\}+\D[\{\Ex(S_i^+)\}-\E(S_i^+)\}]\ . 
\ee
called the base risk and strain, respectively.     Hence \sr\ is a debt weighted average of base risks and strains.       A firm counts highly in \sr\  if it carries a significant portion of total debt,  has high base risk and  high strain.

\item Pooled base risk is defined as  $0\le\E(S^+)\le 1$ where $S=\D(S_i)$.  Similarly pooled strain is  
$\Ex(S^+)-\E(S^+)$.

\item Non--pooled shortfall is defined as $S^*=\sum_iS_i^+$ with non--pooled base risk $\E(S^*)$ and strain $\Ex(S^*)-\E(S^*)$.

\item Similar to before, $\Ex(S_i^+)=\Ex(S_i^+>0)\Ex(S_i|S_i>0)$.   The two factors on the right are called the stressed default probability and stressed tail risk, respectively.    The measures
$$
\Ex(S_i^+>0)-\E(S_i^+>0)\cq \Ex(S_i|S_i>0)-\E(S_i|S_i>0)
$$
are the default probability and tail risk strain, respectively.

\item    System  base resilience  is measured with the positive number 
\be{resil}
 \ln \frac{\E(S^*)}{\E(S^+)} = \ln\frac{\E(S^*>0)}{\E(S^+>0)} + \ln\frac{\E(S^*|S^*>0)}{\E(S^+|S^+>0)}\ .
\ee
A large value indicates shortfall in individual firms can be absorbed in the system.   A value near zero indicates there is no capacity for the system to absorb shortfall in individual firms.  Using $\Ex$ instead of $\E$ in \eref{resil} yields the resilience under stress.

\end{enumerate}

\section{A formal framework for systemic risk measurement}\label{formal}
The  proposed improved framework considers future capital shortfall $S$ as defined in \eref{fcapreq}  for a a single firm or group of firms.   Then the framework for measuring stress may focus on $S$, the positive part  $S^+$ as defined in \eref{bs}, or a more general function of $S$.   For concreteness suppose the focus is on $S^+$.

The improved framework consists of:
\bi
\i  A collection of scenarios generically labelled $\omega$ where  $\omega$ discrete or continuous.  Scenarios may be both benign or serious in terms of their potential impact on shortfall $S$.   Scenarios $\omega$ are systemic if they have potential impact on many firms.

\i The ``natural" probability of scenario $\omega$ is $p(\omega)$.   If $\omega$ is continuous then $p(\omega)$ is interpreted as a probability density.

\i  Basis strain is defined as the ordinary expectation
$$
 \E(S^+)=\sum_\omega p(\omega) \E(S^+|\omega)\cq 0\le\E(S^+)\le 1\ .
$$
For continuous $\omega$,  the sum is interpreted as an integral.

\i  A stress function $\psi(\omega)\ge 0$ defined on the  scenarios $\omega$ with  $\E(\psi)=1$.  The stress function serves to amplify or downplay the importance of different scenarios.   On average the amplification is 1.   The stress function serves to ``bias" outcomes towards ``stressful" scenarios, that is scenarios likely to drive up shortfall.

\i The \sr\ of a firm is the expected shortfall under the stressed probabilities $\psi(\omega)p(\omega)$:
\be{formula}
\Es(S^+) = \E\{\psi\E(S^+|\psi)\}=\E(\psi S^+)=\E(S^+)+\cov(S^+,\psi)\ ,
\ee
where the last equality follows since $\E(\psi)=1$.   Note $0\le\Ex(S^+)\le 1$.     
The import of $\psi(\omega)$ is to change the natural probabilities $p(\omega)$ to ``stressed" probabilities $\psi(\omega)p(\omega)$.

 \i The strain is defined as the additional expectation due to stress 
 $$
\Es(S^+)-\E(S^+)\cq \mathrm{srisk} = (\mathrm{base\ risk})+\mathrm{strain}\ \ .
 $$

 \i Note that 
 $$
 \ln\frac{\Ex(S^+)}{\E(S^+)} = \ln \frac{\Ex(S>0)}{\E(S>0)} +\ln\frac{\Ex(S|S>0)}{\E(S|S>0)}\ .
 $$
 That is, the approximate percentage change in risk due to stress is the the percentage change in the default probability plus the percentage change in the tail risk.
  \ei

\subsection{Practical stress functions}
The simplest example is where $\psi(\omega)=0$ except for a single  scenario $\omega$ where it is equal to $1/p(\omega)$.   In this case all probability is transferred to the single scenario $\omega$ and $\Es(S)=\E(S|\omega)$.  
This conditional expectation is often modelled and computed with a spreadsheet.

The stress function used in  \cite{brownlees2015} is where $\omega$ is the market return and $\psi(\omega)=0$ unless $\omega\le 0.1$ in which case $\psi(\omega) = c$ where $c$ is 	 such that the area under $\psi$ is 1.   In other words scenarios are different market returns with stress being zero unless market return is  a drop of 10\% or more.   This stress function is quite blunt:   stress is either on or off and if on there is no reckoning as to the degree of stress.

A richer example is where $\omega$ is the percentile of a variable such as the overall market return, measured relative to the current  market return distribution.   Then $p(\omega)$ is the uniform density on the unit interval.   If 
$$
\psi(\omega)=n\{1-(1-\omega)^{n-1}\}\ ,
$$
then $\psi$ is the density of the worst percentile outcome in $n$ independent trials.   In this case \pr\  corresponds to the increase in risk when the general market has its worst outcome in $n$ independent trials given the current return distribution.  This stress function  is used to study stress in Australian banks in \sref{simulate1}.  If $n=1$ then $\psi(\omega)=1$, there is no stress, and $\Es(S)=\E(S)$ and \pr=0.

Another example, close to that implemented in \cite{brownlees2015} is where $\omega$ is a percentile with $\psi(\omega)=1/c$ for $\omega<c$ and 0 otherwise.   In this case  $\Es(S)=\E(S|\psi<c)$ and \pr\  is the difference between the   tail and ordinary expectation.
More general stressed expectations of the form of \eref{formula} are discussed in \cite{furman2008weighted1} and \cite{choo2010determining}.

\subsection{Strain potential}

A  measure of potential for a stress function $\psi$ to induce strain is its volatility denoted $\sigma_\psi$. If $\psi$ is constant then $\sigma_\psi=0$.   If $\psi(\omega)$ picks out a single scenario $\omega$ then 
$$
\sigma_\psi= \e^{-\logit\{p(\omega)\}/2}\ ,
$$
which is large if the scenario probability $p(\omega)$ is small.

Standardised strain is: 
$$
\beta_\psi= \frac{\mathrm{strain}}{\sigma_\psi}=\sigma_{S^+} \times\cor(S^+,\psi)\ .
$$
measuring the departure of $\Es(S)$ from $\E(S)$ in units of $\psi$ volatility. Here $\cor$ denotes correlation. The measure $\beta_\psi$ facilitates the comparison of strain on $S$ across different stressors and has the interpretation of a regression coefficient:
$$
\E(S^+|\psi=x) \approx (\br) +\left(\frac{\st}{\sigma_\psi}\right)\left(\frac{x-1}{\sigma_\psi}\right)\ .
$$
Thus $\beta_\psi$ measures, in minimum mean square error sense, the change in strain as stress increases by one standardised unit.

 Strain can also be measured  in units of $S$ volatility:
$$
\frac{\Es(S^+)-\E(S^+)}{\sigma_{S^+}}=\sigma_\psi\cor(S^+,\psi)\ .
$$
This measure gauges the extremity of strain.

\subsection{Computing basis strain and stress strain via simulation}
Given $N$ simulations $\omega\sim p(\omega)$ and $S(\omega)\sim p(S|\omega)$  then  $S(\omega)\sim p(S)$ and  
$$
 \frac{1}{N}\sum_\omega S^+(\omega)\rightarrow \E(S^+) \cq \frac{1}{N}\sum_\omega \psi(\omega)S^+(\omega)\rightarrow \Ex(S^+) \ ,
$$
as the simulation effort $N$ increases.

If $\psi$ is based  on percentile outcomes   then the simulated $\omega$ are ranked and $\psi(\omega)$ is computed from the empirical rank of $\omega$.  If $\omega$ has many components corresponding to percentiles of different variables then $\psi(\omega)$ is a copula density chosen to induce appropriate  tail dependence.

 As in \cite{brownlees2015},  $\omega$ in the next section is the projected  market return while $S(\omega)$ or more particularly $S_i(\omega)$  is the shortfall for firm $i$ based on its projected rate of return $r_i$ given the market return $\omega$.   The joint distribution of $\omega$ and $r_i$ is simulated  from  fitted bivariate time series models.  The market return is used as the stressor with the stress function $\psi$ modelling  stress scenarios.

The time series models used are stochastic volatility models based on the GARCH--DCC framework of \cite{engle2002dynamic} summarised in \aref{garchdcc}. The GARCH-DCC model captures prolonged periods of high volatility and correlation in firm and market returns, typical in financial markets. The GARCH--DCC framework is one possible implementation.   For example future return scenarios may be constructed in a more ad--hoc manner e.g. judiciously constructed scenarios by regulators or policymakers.   The  framework set out in \sref{srisk} can be based on  any  generated  future  scenarios.

\fref{simulation} displays simulations from a joint distribution generated from the GARCH--DCC model estimated from daily returns.  The left panel utilises  one month forward simulated returns at the start of January 2008.   The market returns are on the x--axis while the shortfall $S$ corresponding to associated CBA return are on the y--axis.  Low market returns are likely to lead to sharply higher CBA shortfall, as compared to the right panel showing the same as at December 2014.   This is suggested by the slope of the scatter plots:  the left slope appears steeper than the right. This implies higher systemic stress in December 2008. In addition $S$ volatilities are much higher in the left panel compared to the right, indicating higher basis stress in December 2008. Also note that with a stressor function $\psi$ defined in terms of market return percentiles, the magnitude of a market downturn at a fixed percentile threshold is more significant in the left panel.

\section{Australian bank stress forecasts}\label{simulate1}

\fref{fig4} displays, in the top panels, the estimated basis risk for each major (left) and minor (right) Australian banks based on the projected one month ahead return distribution fitted using the GARCH--DCC model.  Note the return distributions are constructed from data only available at that time and hence are not affected by look--ahead bias.  The first inclinations of increasing basis risk occurs with NAB in early 2008 followed one month later by ANZ, and  a further few months later by WBC and CBA. basis risk subsided shortly after 2009, however basis risk for NAB rose again in 2011 and this sustained till 2013.  In general smaller banks are subject to higher basis risk after normalising for debt levels.

Bottom panels in \fref{default} show \pr\ computed by assuming the worst market return in 12 identical months. \pr\ for each bank generally exhibits similar patterns as \br. However, importantly, some banks have differing patterns which is an important observation for the regulator since \pr\ indicates sensitivity to market-wide downturns. For example ANZ had similar \pr\ stress as NAB around 2012 but lower \br. Hence although ANZ was not obviously in stress during 2012, it would be if a market downturn occurred. Bendigo and BOQ had high \br\ levels after 2008, but are overtaken by Macquarie in terms of \pr: Macquarie is more likely to suffer in a market downturn whereas Bendigo and BOQ are less likely to be impacted.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=12cm]{figures/fig4.pdf}
\caption{Basis strain  (top panels) and stress strain (bottom panels) based on one month ahead  forecasts $S_i^+$ for   major (left panel) and  minor (right panel)  Australian banks 2003--2014.  Stress is based on worst monthly market outcome in 1 year.  Note different y--scale on top and bottom panels.}\label{fig4}
\end{center}
\end{figure}

\fref{fig5} gives a picture of the relative magnitudes of \br\ and \pr\ in each of the eight banks.   For the major banks NAB stand out as, having \br\ more dominant than \pr\ and generally having heightened levels of \br.   ANZ appears to have relatively higher levels of \pr.    For the minors, MQG has persistently higher levels of \pr\ with BOQ and BEN comparable ratios and ABA having virtually no \pr\ compared to \br\ at any level of the latter.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=12cm]{figures/fig5.pdf}
\caption{Historical relationship between stress strain and basis strain    for major   and  minor banks.}
\label{fig5}
\end{center}
\end{figure}

\section{Monitoring aggregate  stress and contagion}\label{aggregate}

This section uses two measures of future aggregate shortfall for a group of firms based on two different methods of aggregating default risk across firms:
$$
S^+ = \{\D(S_i)\}^+\le \D(S_i^+) =S^*\ .
$$
Here $S^+$ is referred to as the ``pooled" or ``diversified" shortfall with shortfall in one firm able to be offset by surplus elsewhere.  The shortfall $S^*$ is ``non--diversified" with shortfall in each firm $i$ adding up.

With $\Ex(S^+)$ heightened risk only arises if there is an ``on average"  shortfall.   Thus SRISK is relatively insensitive to tail events.  The second aggregation of risk displayed in \tref{dsrisk} uses $S^*$, the  sum of positive shortfalls across firms.  With $S^*$, shortfall within a firm is not offset by averaging  nor with surpluses in other firms. The measure is thus more sensitive to tail risk.

The second aggregation of risk displayed in \tref{dsrisk} uses $S^*$, the  sum of positive shortfalls across firms.  With $S^*$, shortfall within a firm is not offset by averaging  nor with surpluses in other firms. The measure is thus more sensitive to tail risk.

Our measures of basis and stress contagion are 
\be{cont}
\frac{\E(S^+)}{\E(S^*)}\cq  \frac{\Ex(S^+)}{\Ex(S^*)}- \frac{\E(S^+)}{\E(S^*)}
\ee
 both of which lies between 0 and 1.   A value near one indicates little of the risk in the group of firms, due to basis events or stress is absorbable and hence defaults are not diversifiable.   A value near 0 indicates virtually all of the risk in the system can ``diversified away."

 \tref{dsrisk} displays and compares and contrasts the different definitions of risk. The last line of \tref{dsrisk} reproduces the \SR\  measure of \cite{brownlees2015}. Note $\Es(S)$ combines both basis stress, due to high volatility or leverage, and the imposed hypothetical stress. To understand the nature of stress it is important to understand the mix of these two different stresses.

\begin{table}[htbp]
\caption{Different strains}\label{dsrisk}
\begin{center}
\begin{tabular}{l|c|c|c}
\hline
& basis & strain & srisk\\
\hline
pooled &$\E(S^+)$ &$ \Ex(S^+)-\E(S^+)$ & $\Ex(S^+)$\\
non--pooled & $\E(S^*)$& $\Ex(S^*)-\E(S^*)$&$\Ex(S^*)$\\
\hline
resilience & $\ln\frac{\E(S^*)}{\E(S^+)}$& $\ln\frac{\Ex(S^*)}{\Ex(S^+)}-\ln\frac{\E(S^*)}{\E(S^+)}$&$\ln\frac{\Ex(S^*)}{\Ex(S^+)}$ \\
\hline
\SR & \multicolumn{2}{c}{$\D[\{\Ex(S_i)\}^+]$}\\
\hline
\end{tabular}
\end{center}
\label{default}
\end{table}%

System resilience aims to answer the question of whether the system as a whole can absorb shocks.   The capacity to absorb relies on implicit merging and hence on a measure of shortfall such as $S^+$.    When two firms merge the leverage of the resulting firm is less than that of the more highly leveraged firm.   The merged firm is more able to withstand return on equity shocks  unless negative shocks are more prone for the merged firm.   Similarly when many firms merge  puts $S^+$ for the conglomerate become less valuable.

Firms do not necessarily merge, even in dire financial circumstances.   Hence the mergers spoken of here are hypothetical.   From a regulators perspective, what would happen under a merger of all firms (or perhaps a group of firms) is nevertheless of interest.   A system as as a whole near Basel breach is more threatening that one where a few firms are near Basel breach but the system as a whole is strongly Basel compliant.

\section{Monitoring individual banks contribution to stress}

The proportionate contributions of bank $i$ to base risk, strain and \sr\ are 
\be{contrib}
\frac{\pi_i\E(S_i^+)}{\D\{\E(S_i^+)\}}\cq \frac{\pi_i\{\Ex(S_i^+)-\E(S_i^+)\}}{\D\{\Ex(S_i^+)-\E(S_i^+)\}}\cq \frac{\pi_i\Ex(S_i^+)}{\D\{\Ex(S_i^+)\}}\ ,
\ee
respectively.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=12cm]{figures/fig6.pdf}
\caption{Projected one month  Australian banks risks through the financial crisis years 2008 through to the end of 2010.  Top panels are basis risk and stress risk.  Bottom left panel computes  basis and stress risk using pooling and no--pooling, and compares the same to \SR.   Bottom right panel displays contagion risk as defined in equation \eref{cont}.}
\label{fig6}
\end{center}
\end{figure}

\subsection{Aggregate stress in the Australian banking sector}\label{monitoring}
 \tref{jan2009} contains real time stress calculations on the first trading day of  January 2009.  As before there is no look ahead bias -- calculations on each of the two dates use data available on the first day of the applicable month.   The first eight rows in in the body of \tref{jan2009} correspond to the eight banks used in this study.  The first  and second columns in the two halves of the table body contain the default index  and debt  (as a percentage of total system debt) for each of the banks.

The absorbance capacity is a measure of the system to absorb base risk, strain or srisk through merger.   If, for example, $\E(S^+)$ is much smaller than $\E(S^*)$ then a large portion of base risk can be ``diversified away" by merging firms.   This suggest the measures
$$
1-\frac{\E(S^+)}{\E(S^*)}\approx\ln\frac{\E(S^*)}{\E(S^+)}\cq \frac{\Ex(S^*)-\E(S^*)}{\Ex(S^+)-\E(S^+)}\cq \frac{\Ex(S^*)}{\Ex(S^+)} \ .
$$
The first and last measures lie between 0 and 1 with values near 0 
 near 0 indicating there is no pooling buffer. \tref{jan2009} displays the calculations for January 2009.

\begin{table}[ht]
 \caption{Analysis of bank  risk:  January 2009}\label{jan2009}
\centering
\begin{tabular}{l|rr|rrr}
 \hline
 & default & debt & \multicolumn{3}{c}{\% of non--pooled}  \\ 
 \cline{4-6}
bank & index  & \% & base risk & strain & $\mathrm{srisk}$\\
\hline
CBA & 18.57 & 24.30 & 22.99 & 29.60 & 25.20 \\ 
  ANZ & 15.93 & 18.37 & 14.87 & 18.89 & 16.21 \\ 
  NAB & 31.97 & 25.50 & 39.98 & 19.41 & 33.10 \\ 
  WBC & -1.55 & 22.84 & 5.86 & 23.94 & 11.91 \\ 
  MQG & 41.22 & 5.75 & 11.02 & 5.46 & 9.16 \\ 
  BOQ & 63.30 & 1.32 & 3.55 & 0.99 & 2.70 \\ 
  BEN & 18.91 & 1.81 & 1.72 & 1.71 & 1.72 \\ 
  ABA & -8.12 & 0.10 & 0.00 & 0.00 & 0.00 \\ 
  \hline
  \multicolumn{3}{r|}{non--pooled}  & 17.17 & 8.63 & 25.80 \\ 
  \multicolumn{3}{r|}{pooled} & 15.28 & 10.18 & 25.46 \\ 
  \multicolumn{3}{r|}{resilience} & 11.66 & -16.48 & 1.34 \\ 
   \hline
\end{tabular}
\end{table}

January 2009 was a time of great strain for all eight banks.       Six of the eight banks were in Basel default with positive capital shortfalls as indicated by the default index column:   the two banks not in Basel default were WBC and ABA.

 Percentage base risk, strain and srisk    are displayed in the next 3 columns.    Most of the base risk arises from NAB -- almost 40\% of the total.   The next most base risk arises from  is CBA.   MQG  contributes almost double to base risk compared to the proportion of total debt  it carries.  The other three small banks contribute relatively little to base risk with BOQ  almost 3 times expected on the basis of its debt.

Strain  is highest for the CBA, higher than expected on the basis of its debt load and hence CBA was most susceptible to stress from additional general market equity devaluation.    All other banks appear have strain comparable to their size in terms of debt load with only NAB having proportionally less strain.    This should be compared to NAB's high base risk.

The final two rows of \tref{jan2009} indicate the total amount of stress in the system and it's diversifiability.    
The second last  row labelled ``Total"  displays, in order, debt weighted default index, total \br\  and total \pr.  On aggregate Total \br\  is about twice \pr.   Thus there is more danger of increasing capital shortfall due to market volatility  as opposed to further stress from further substantial general market devaluation.  The final row indicates stresses are not diversifiable:    The marginally  smaller  ``diversified"  basis stress is offset by an increase in \pr.

Stress readings  change dramatically when moving to December 2014 -- there is virtually no stress in any bank and the small amount of  stress in the system is diversifiable.    Most  \br\ is carried by NAB with lesser contributions by BEN and ABA.    All the stress in the minor bank ABA is basis stress as only NAB and NAB have substantial \pr\  contributions.   Again, however, it must be emphasised that there is minimal systemic stress in the system.  Notice total debt in the banking sector  jumps about 35\% between the two dates.

The two  panels of \fref{fig6} track  \br\ and \pr\ for the banking sector as a whole through time.   There is virtually no risk in the system till late 2007 and the early warnings show a buildup in \br\ in $S^*$ compared to $S^+$.   Thus initially all \br\ is diversifiable suggesting \br\ is building up in a few banks.   This pattern of diversifiability in \br\ is generally maintained except at the peak of the crisis at the beginning of 2009 and in late 2011.  This pattern of \br\ buildup is evident in the bottom panel displaying all \br\ is, for small levels of risk initially absorbable -- that is present in $S^*$ but not present in $S^+$.

The top right panel in \fref{fig6} displays the time series behaviour of \pr.  Generally \pr\ is less than \br.   Further, in situations of elevated risk,  \pr\ in $S^+$ exceeds that in $S^*$ indicating systemic stress from a general market downturn is greater in the system as a whole than its constituent parts.   Again, however, as displayed in the bottom right panel, \pr\ initially builds up in $S^*$, and only later manifests itself in $S^+$.  However the buildup is rapid so that with significant \pr\ the level in $S^+$ exceeds that in $S^*$.

\section{Risk weighted asset methodology}\label{riskmethod}

The current stress framework can be used in conjunction with   the  risk weighting asset (RWA) methodology often used in determining capital shortfall.   RWA in effect assesses future stressed assets,   as opposed to, with SRISK,  future equity.   The same stress methodology can be used to stress assets.

Given debt $d$ and equity $w$ for a firm,  assets are
$$
d+w=\sum_ja_j\ ,
$$
where $a_j$ denotes the value of assets in asset class $j$.   Future shortfall is, equivalent to \eref{fcapreq},  
\be{shortfall2}
S=  d-(1-k)\sum_ja_j\e^{r_j}\ ,
\ee
where $r_j$ is the (uncertain) log--return on assets $a_j$.  With the risk weighting methodology the weights $a_j$  are replaced by $a_j/\sigma_j$ where $\sigma_j\ge 1$ is a ``risk" weight with large  weights assigned to  assets  with large perceived ``riskiness."

Suppose $S$, $d$ and $r$ are the vectors of shortfalls, debts  and returns, respectively for the firms, and matrix $A$ has rows corresponding to the asset values of different firms.  Then the vector of firm shortfalls is
$$
S = d-(1-k)A\e^{r}\ ,
$$ 
where  exponentiation is componentwise.   Writing $S^+$ as the vector of positive shortfalls then, as in \sref{aggregate}, two aggregate measures of expected shortfall are $S^*= \sum_iS_i^+$ and $S^+=(\sum_iS_i)^+$ where $S_i$ is component $i$ of vector $S$.

Estimation of \br\ and \pr\ can proceed via simulation:
$$
\omega\sim p(\omega)\cq r(\omega)\sim p(r|\omega)
$$
where $r(\omega)$ is  the simulated vector of returns for the asset classes given scenario $\omega$.   The vector of shortfalls corresponding to $\omega$ is then $S(\omega)=d-(1-k) A\e^{r(\omega)}$  where $A$ is the matrix with row $i$ corresponding to the current asset values for firm $i$ and $\e^{r(\omega)}$ denotes componentwise exponentiation.   Then the vectors of \br\ and \pr, with components corresponding to the different firms $i$ are estimated as  
\be{srisk4}
\br\approx \frac{1}{N}\sum_\omega S^+(\omega)\cq
 \pr\approx \frac{1}{N}\sum_\omega  \{\psi(\omega)-1\}S^+(\omega)\ ,
\ee
with similar results for $S^*=\sum_iS_i^+$ and $(\sum_iS_i)^+$.

Stressful scenarios can be implicitly constructed via the following percentile method.   Suppose $r\sim p(r)$ are simulations from the joint distribution of future asset returns.   Returns for each asset class are  ranked yielding simulated percentile vectors $\omega$.   Denote $S(\omega)$ as the vector of shortfalls computed as before from returns $r$ corresponding to $\omega$.   Then use these $S(\omega)$  in the expressions \eref{srisk4} with
$$
\psi(\omega) = nc(\omega)\prod_j \{1-(1-\omega_j)^{n-1}\}\ ,
$$
where $c(\omega)$ is a copula density designed to exaggerate the juxtaposition of  adverse percentile occurrences: such as exaggerated lower tail dependence.   If $c(\omega)= 1$  there is no exaggeration  and the copula associated with the $r(\omega)$ is the copula induced by $p(r)$.  If $n=1$ there is no sculpting of the marginal distributions.

\section{Conclusion}\label{conclude}

This paper presents a consistent methodology for stress testing and the measurement of  risk using the concept of stressed expectations.   Stressed expectation  formalises stress testing widely used in practice.  Stresses are introduced using a stress function and systemic stress uses a stress function based on system wide variables.   Methods and concepts are applied to publicly available time series of Australian bank data to monitor stress in Australian banks over time.   The methods identity banks in distress and those with high contribution to systemic stress.

\bigskip
\begin{center}
{\large\bf SUPPLEMENTARY MATERIAL}
\end{center}

\appendix
\renewcommand*{\thesection}{\Alph{section}}

\section{GARCH--DCC model}\label{garchdcc}

Denote the daily (log) return for firm $i$ at time $t$ as
\newcommand{\vareps}{\varepsilon}
\be{mean.model}
\delta_{it}=\mu_i+\sigma_{it}\eps_{it}\cq \eps_{it}\sim (0,1)\ .
\ee
The volatility $\sigma_{it}$ is modelled as
\be{vol}
\sigma_{i,t+1}^2 = \omega+ \sigma^2_{it}\{\beta+(\alpha+\gamma \eps^-_{it})\eps_{it}^2\}  \cq  \eps^-_{it}= I(\eps_{it}<0)=I(\delta_{it}<\mu)\ ,
\ee
where $I$ denotes the indicator function.  Hence the response of $\sigma_{i,t+1}^2$ to $\eps_{it}^2$  is increased by $\gamma$   if
the rate of return is below the average $\mu_i$, compared to the response if $\delta_{it}>\mu_i$.  Equations \eref{mean.model} and \eref{vol} defined a simple threshold GARCH model:  called the TARCH(1,1).   In \eref{mean.model} the mean $\mu_i$ does not vary with time $t$ and in \eref{vol} it is assumed the terms  $\sigma_{it}^2$ and $\eps_{it}$ in the right hand side of \eref{vol} are sufficient to structure the dynamics of volatility and contemporaneous correlation.

The model defined by \eref{mean.model} and \eref{vol} is estimated  for each security $i$ jointly with  a similar model for  the market,  $i=m$.   Correlation between security $i$ and the market $m$ are implicitly modelled using  positive definite recursions   \citep{engle2002dynamic}
$$
(Q_{i,t+1}-S) = \alpha (\eta_{it}\eta_{it}'-S) + \beta (Q_{it}-S)\cq \eta_{it}=(\eps_{it},\eps_{mt})' .
$$
The correlation defined by $Q_{it}$ is used as the correlation between $\eps_{it}$ and $\eps_{mt}$.

\section{Data sources}\label{data}

Data are sourced from DataStream using the company and datatype codes as set out in \tref{datastream}.

\begin{table}\caption{DataStream codes}\label{datastream}
\begin{center}
	\begin{tabular}{l|l}
	\hline
	\multicolumn{2}{l}{Company codes}\\
	\hline
A:ANZX & Australia and New Zealand Banking Group Limited\\
A:ABAX & Auswide Bank Limited\\
A:BOQX & Bank of Queensland Limited\\
A:BENX & Bendigo and Adelaide Bank Limited\\
A:CBAX & Commonwealth Bank of Australia\\
A:MQGX & Macquarie Bank Limited\\
A:NABX & National Australia Bank Limited\\
A:WBCX & Westpac Banking Corporation.\\
\hline
\multicolumn{2}{l}{Datatype codes}\\
\hline
	NOSH & Number of Shares\\
	P & Price\\
	WC02999 & Total Assets\\
	WC03501 & Shareholders Equity\\
	RZ & Total return index\\
\hline	
\end{tabular}
\end{center}
\end{table}

Firm equity $w$ is Number of Shares multiplied by Price. Firm debt $d$ is Total Assets minus Shareholders Equity. Stock returns are computed from the Total Return Index including paid dividends.

\section{Computations}

All model fits in this paper are performed using the R language \citep{R-Development-Core-Team:2008aa} and in particular the rmgarch package described by \cite{ghalanos2012rmgarch}.  All other calculations including simulations are implemented in the J language \citep{iverson2003j}.

In the forward simulated forward projections the  innovations are chosen randomly from past innovations.   These past innovations are chosen consistently:  at a particular $t$ either all or none of $\eps_{it}$ are chosen.

\section*{References}
\bibliography{piet2}
\end{document}

### 2016-10-09 srisk7.tex
Lots and lots of changes
Latest

@@
 \bibliographystyle{chicago}
+\usepackage{threeparttable}
 
@@
 
-\begin{table}[htdp]
+\begin{table}[htbp]
 \label{banks}\caption{Major and minor Australian banks}\label{eightbanks}
@@
  \begin{table}[ht]
-\caption{One month ahead bank stress calculations$^\dag$}\label{twodates}
+\caption{Projected one month ahead  stress for banks}\label{twodates}
 \centering
+\begin{threeparttable}
 \small
 \vspace{4mm}
-\begin{tabular}{l|rrrrr|rrrrr}
+\begin{tabular}{l|rrrr|rrrr}
 \hline
-&\multicolumn{5}{c|}{January 2009}&\multicolumn{5}{c}{November 2014}\\
+&\multicolumn{4}{c|}{January 2009}&\multicolumn{4}{c}{November 2014}\\
   \hline
-bank & B-log& debt &\multicolumn{2}{c}{stress}&  B-def   & B-log& debt   & \multicolumn{2}{c}{stress}& B-def \\
-  \cline{4-5}\cline{9-10}
-       &  lev& prop    & back & syst & prob & lev& prop  & back & syst & prob \\
-  \cline{2-11} 
-         & $\ell_{it} $ & $\pi_{it}$ & $\mu^*_{it}$  & $s^*_{it}$ & $q_{it}$  
-         & $\ell_{it} $ & $\pi_{it}$ & $\mu^*_{it}$  & $s^*_{it}$ & $q_{it}$  
-        \\
+   & Aloglev& Debt & BASRISK & PSIRISK  & Aloglev & Debt  & BASRISK & PSIRISK\\  
   \hline
-CBA & 18.57 & 24.30 & 22.99 & 29.60 & 91.43 & -70.34 & 22.70 & 0.00 & 0.00 & 0.00 \\ 
-  ANZ & 15.93 & 18.37 & 14.87 & 18.89 & 92.82 & -38.64 & 22.10 & 0.00 & 0.00 & 0.00 \\ 
-  NAB & 31.97 & 25.50 & 39.98 & 19.41 & 99.97 & -12.45 & 25.61 & 50.52 & 67.13 & 1.23 \\ 
-  WBC & -1.55 & 22.84 & 5.86 & 23.94 & 40.42 & -53.84 & 22.03 & 0.00 & 0.00 & 0.00 \\ 
-  MQG & 41.22 & 5.75 & 11.02 & 5.46 & 99.92 & -46.10 & 4.33 & 0.17 & 0.12 & 0.03 \\ 
-  BOQ & 63.30 & 1.32 & 3.55 & 0.99 & 99.95 & -17.05 & 1.33 & 0.80 & 1.34 & 0.33 \\ 
-  BEN & 18.91 & 1.81 & 1.72 & 1.71 & 90.53 & -7.63 & 1.84 & 25.43 & 30.71 & 8.47 \\ 
-  ABA& -8.12 & 0.10 & 0.00 & 0.00 & 9.97 & 9.22 & 0.07 & 23.07 & 0.71 & 89.63 \\ 
+CBA & 18.57 & 24.30 & 22.99 & 29.60 & -70.34 & 22.70 & 0.00 & 0.00 \\ 
+  ANZ & 15.93 & 18.37 & 14.87 & 18.89 & -38.64 & 22.10 & 0.00 & 0.00 \\ 
+  NAB & 31.97 & 25.50 & 39.98 & 19.41 & -12.45 & 25.61 & 50.52 & 67.13 \\ 
+  WBC & -1.55 & 22.84 & 5.86 & 23.94 & -53.84 & 22.03 & 0.00 & 0.00 \\ 
+  MQG & 41.22 & 5.75 & 11.02 & 5.46 & -46.10 & 4.33 & 0.17 & 0.12 \\ 
+  BOQ & 63.30 & 1.32 & 3.55 & 0.99 & -17.05 & 1.33 & 0.80 & 1.34 \\ 
+  BEN & 18.91 & 1.81 & 1.72 & 1.71 & -7.63 & 1.84 & 25.43 & 30.71 \\ 
+  ABA & -8.12 & 0.10 & 0.00 & 0.00 & 9.22 & 0.07 & 23.07 & 0.71 \\ 
   \hline
-  $\Ex_d$ & 18.78 &  & 17.17 & 8.63 & 82.72 & -41.91 &  & 0.03 & 0.12 & 0.54 \\ 
-  $\Sigma$ & 17.81 & $^\dag$2.42 & 15.28 & 10.18 & 96.72 & -44.22 & $^\dag$3.27 & 0.00 & 0.00 & 0.00 \\ 
-\hline
+  Total & 18.78 & 2.42 & 17.17 & 8.63 & -41.91 & 3.27 & 0.03 & 0.12 \\ 
+  Pooled & 17.81 & 2.42 & 15.28 & 10.18 & -44.22 & 3.27 & 0.00 & 0.00 \\ \hline
 \end{tabular}
-
-$^\dag$All numbers multiplied by 100 except total debt (in \$bln).
+\begin{tablenotes}
+\item[]Response is positive part of capital shortfall.
+PSIRISK is with respect to expected worst monthly market return  in 12 months.
+Main body of table displays percentage contributions of each firm to total BASRISK and PSIRISK.
+Total row displays debt weighted adjusted log--leverage, total debt in \$$10^{11}$ and BASRISK and PSIRISK per $0.08\times$debt.
+Pooled row displays results with debt and equity pooled across banks.
+\end{tablenotes}
+\end{threeparttable}
 \end{table}

### 2016-10-09 srisk8.tex
Lots and lots of changes
Latest

--- 2016-10-09 srisk10.tex
@@
-\documentclass[authoryear]{elsarticle}
+\documentclass[12pt]{article}
 \usepackage{amsmath}
@@
 \usepackage{enumerate}
+\usepackage{natbib}
 \usepackage{url} % not crucial - just used below for the URL 
@@
 \usepackage{threeparttable}
+
+%\pdfminorversion=4
+% NOTE: To produce blinded version, replace "0" with "1" below.
+\newcommand{\blind}{0}
+
+% DON'T change margins - should be 1 inch all around.
+\addtolength{\oddsidemargin}{-.5in}%
+\addtolength{\evensidemargin}{-.5in}%
+\addtolength{\textwidth}{1in}%
+\addtolength{\textheight}{1.3in}%
+\addtolength{\topmargin}{-.8in}%
 
@@
 \newcommand{\Exd}{\Ex_d}
-\newcommand{\Es}{\Ex}
+\newcommand{\Es}{\widetilde\E}
 \newcommand{\rat}{{\frac{c_{ij}}{c_{i,j-1}}}}
@@
 \renewcommand{\i}{\item}
-\newcommand{\SR}{\ensuremath{\mathrm{SRISK}}}
-\newcommand{\sr}{\ensuremath{\mathrm{srisk}}}
-\newcommand{\br}{\ensuremath{\mathrm{base\ risk}}}
-\newcommand{\st}{\ensuremath{\mathrm{strain}}}
-\newcommand{\pr}{\ensuremath{\mathrm{strain}}}
+\newcommand{\sr}{\ensuremath{\mathrm{SRISK}}}
+\newcommand{\br}{\ensuremath{\mathrm{BRISK}}}
+\newcommand{\pr}{\ensuremath{\mathrm{PRISK}}}
 \newcommand{\cs}{\ensuremath{\mathrm{CS}}}
@@
 \newcommand{\Vx}{{\cal V}}
-
 \newcommand{\be}[1]{\begin{equation}\label{#1}}
@@
 
-\newcommand{\D}{\mathrm{D}}
-
 \begin{document}
 
-\title{An early warning system for monitoring  stress in the financial system}
-%\author[acst]{Piet de Jong\corref{cor1}\footnote{The authors gratefully acknowledge CIFR, the Centre of International Financial Regulation for financial support and other assistance}}
-%\ead{piet.dejong@mq.edu.au}
-%\author[acst]{Geoffrey Loudon}
-%\author[acst]{Weihao Choo}
-%\address[acst]{Department of Applied Finance and Actuarial Studies Macquarie University, NSW 2109, Australia.}
-%\cortext[cor1]{Corresponding author}
+%\bibliographystyle{natbib}
 
+\def\spacingset#1{\renewcommand{\baselinestretch}%
+{#1}\small\normalsize} \spacingset{1}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\if0\blind
+{
+  \title{\bf Monitoring  risk in the financial system using time series methods}
+  \author{Piet de Jong\thanks{
+    The authors gratefully acknowledge CIFR, the Centre of International Financial Regulation for financial support and other assistance.}\hspace{.2cm}\\
+    Department of Applied Finance and Actuarial Studies, Macquarie University\\
+    and \\
+    Geoffrey Loudon\\
+    Department of Applied Finance and Actuarial Studies, Macquarie University\\
+    and\\
+    Weihao Choo\\
+    Department of Applied Finance and Actuarial Studies, Macquarie University}
+  \maketitle
+} \fi
+
+\if1\blind
+{
+  \bigskip
+  \bigskip
+  \bigskip
+  \begin{center}
+    {\LARGE\bf Measuring baseline and systemic risk using financial time series}
+\end{center}
+  \medskip
+} \fi
+
+\bigskip
 \begin{abstract}
-SRISK methodology recently proposed in the literature is refined and extended using a formalised stress testing framework.
-The framework distinguishes between two types of risk:  basis risk and stress risk.
-basis risk is defined as
-
- Both expectations are  based on a time series model and  observations to date.
-Stressed expectation differs from the ordinary expectation in the imposition of an additional hypothetical  stress, modelled using a stress function and scenarios.
-Stress risk is the difference between stressed expectation and ordinary expectation.
-Stress functions are chosen by the practitioner and  exaggerate the probability undesirable  outcomes.
+SRISK methodology recently proposed in the literature is refined and extended.
+The refinement is to define  systemic risk using a formalised stress testing framework including a stress function.
+Baseline risk and the stress risk  are in terms of the  ordinary and stressed expectation.
+Stressed expectation is expectation computed  under a hypothetical  stress, modelled with the stress function and scenarios.
+Systemic stress is defined in terms of a stress function and systemic scenarios impacting on a number of firms or financial entities.
+Stress functions are chosen by the practitioner and typically exaggerate undesirable extreme outcomes.
 Properties and characterisations of stress and stress related quantities are displayed and explored.
-Systemic stress is defined in terms of stresses   impacting groups of firms or financial entities.
 Application is made to the study of the stability of Australian banks using daily time series data.
@@
 
-\date{}
-\maketitle
-\noindent
-{\it Keywords:}  Capital shortfall, basis risk, stress testing,  stressed expectation, stress diversification.
+\noindent%
+{\it Keywords:}  Capital shortfall, baseline risk, stress testing,  stressed expectation, stress diversification.
+\vfill
 
 \newpage
+\spacingset{1.45} % DON'T change the spacing!
 
@@
 Central banks and other financial regulatory bodies such as the US Financial Stability Oversight Council, the European Systemic Risk Board and the Australian Prudential Regulation Authority (APRA) are concerned with developing and applying early warning quantitative  measures  to warn of potential episodes of heightened systemic risk.
-
 Systemic risk has many dimensions.
@@
 This paper refines and extends the SRISK model of \cite{brownlees2015} in  key ways.
-First SRISK is formalised  as a put on the expected shortfall with the ordinary expectation defined as the basis risk (\br) associated with the put.
-Using a stress function  the so--called stressed expectation is used to measure the impact of stress.
+First, their SRISK measure is refined  as a put on the expected shortfall.
+Second, the ordinary expectation of is defined as the baseline risk (\br) associated with the put.
+Using a stress function  the so--called stressed expectation is used to characterise the expectation given a stress.
 Stressed expectation can be similar to the \cite{brownlees2015} conditional expectation given  a severe market downturn.
-However our generalised methodology  permits a more flexible definition of stress and a wider class of ``stressors" including stress defined in terms of  a number of extreme outcomes.
-The difference between the stressed and ordinary expectation is defined as the stress risk associated, called \pr\ where P stand for psi,  the function $\psi$ modelling the stress.
+However our generalised methodology  permits a far more flexible definition of stress and a wider class of ``stressors" including stress defined in terms of  a number of extreme outcomes.
+The difference between the stressed and ordinary expectation is defined as the risk associated with the stress, called \pr\ where PSI refers the function modelling the stress.
 
@@
 \cite{brownlees2015} define stress by conditioning on an absolute cutoff of arbitrary size and length.
-With time dependent volatility or uncertainty, absolute cutoffs  are less meaningful and our development suggests  it is  useful to specify conditional behaviour in percentile terms relative to current market conditions.
+Our development suggests  it is also helpful to specify conditional behaviour in percentile terms relative to current market conditions.
 This yields a sharper focus on the incremental impact of further stress and permits a more incisive view of the  implications from SRISK numbers.
@@
 
-The nature and usefulness of our measures are demonstrated using publicly available daily financial data for the eight Australian banks detailed in \tref{eightbanks} spanning the period from  3 April 2000 through to 1 December 2014.
+To demonstrate the nature and usefulness of our measures, we use publicly available daily financial data for the eight Australian banks detailed in \tref{eightbanks} spanning the period from  3 April 2000 through to 1 December 2014.
 The data is described in detail in \aref{data}.
@@
 Section \ref{litrev} briefly discusses related literature.
-Section \ref{capshort} defines current and future  capital shortfall similarly as \cite{brownlees2015} under a simple Basel II regulatory framework.
-The definition of systemic risk used by \cite{brownlees2015} is discussed, refined and improved in \sref{srisk}.
+Section \ref{capshort} and \ref{futshort} define current and future  capital shortfall similarly as \cite{brownlees2015} under a simple Basel II regulatory framework.
+The definition of systemic risk used by \cite{brownlees2015} is discussed in \sref{srisk}, and is refined and extended in \sref{improve}.
 Applications to Australian bank data are discussed in \sref{simulate} and \sref{simulate1}.
@@
 \begin{center}
- \begin{tabular}{cc}
-      \resizebox{55mm}{!}{\includegraphics{figures/fig1a.pdf}} &
-      \resizebox{55mm}{!}{\includegraphics{figures/fig1b.pdf}}\\
-    \end{tabular}
+\includegraphics[width=16cm]{figures/prices.pdf}
 \caption{Daily stock  prices of four major (left panel) and four minor (right panel) Australian banks 2000--2014.  Price series normalised to start at 1.}
@@
 
-\cite{brownlees2015}  develop empirical methodology to construct SRISK measures.
+\cite{brownlees2015} further develop the empirical methodology to construct SRISK measures.
 SRISK depends on the firm's size, leverage and its LRMES.
@@
 \cite{Engle2015} extend the model in \cite{brownlees2015} to incorporate global, country and industry effects.
-This extended model makes  use of the \citep{Engle2014dcb} dynamic conditional beta model.
+This extended model makes  use of \cite{Engle2014dcb}'s dynamic conditional beta model.
 Their empirical methods are able to provide information about the relative systemic importance of industry type and country identity.
@@
 
-\cite{adrian2011covar} propose an alternative measure of systemic risk  emphasising the co--dependence of financial firms and the importance of risk spillovers within the financial sector.
-They introduce CoVaR$_i$ which computes the Value--at--Risk (VaR) of the entire financial system, conditional on institution $i$ being in distress.
+\cite{adrian2011covar} propose an alternative measure of systemic risk that emphasises the co-dependence of financial firms and the importance of risk spillovers within the financial sector.
+They introduce CoVaR$_i$ which computes the Value-at-Risk (VaR) of the entire financial system, conditional on institution $i$ being in distress.
 Distress is defined as the state where the institution is exactly at its VaR level.
 \cite{Girardi2013} improve CoVaR by conditioning on the institution being at most at its VaR.
-This generalisation is useful as it takes into account the severity of tail losses and facilitates back--testing of CoVaR.
+This generalisation is useful as it takes into account the severity of tail losses and facilitates back-testing of CoVaR.
 
@@
 Empirical estimates of SRISK  requires a model for the joint distribution of returns of individual firms and the market.
-Many of these papers use \cite{engle2002dynamic}'s GARCH--DCC model aiming to capture the time-varying dynamics of the return (co)variances in a feasible manner.
+Many of these papers use \cite{engle2002dynamic}'s GARCH-DCC model aiming to capture the time-varying dynamics of the return (co)variances in a feasible manner.
 While we also use this model in our empirical analysis, we emphasize that our approach can utilise any appropriate model for simulating the joint distribution of firm and market returns going forward.
 
-\section{Capital requirements, leverage and future shortfall}\label{capshort}
+\section{Capital shortfall and leverage}\label{capshort}
 
-If $d$ and $w$ are the debt and equity, respectively, of a  firm  and $k$ is the prudential requirement,  then  following \cite{brownlees2015}, the   capital requirement is
-\be{capreq}
+If $d$ and $w$ are the debt and equity, respectively, of a particular  firm at a particular point of time, and $k$ is the prudential requirement,  then  as defined \cite{brownlees2015}, the  capital shortfall at that time is
+\be{shortfall}
 k (d+w)-w = k d\left(1-\frac{1-k}{kL}\right)=kd\left(1-\e^{-\ell}\right)
@@
 where
-\be{lev}
-L=\frac{d}{w}\cq \ell=\ln\left(\frac{kL}{1-k}\right) = \logit(k) + \ln(L) \ .
-\ee
-The capital requirement \eref{capreq} is positive if $\ell>0$.
-Note $kd$ is the proportion of debt $d$ required as capital if equity $w=0$.
-Each unit of  $w$ is counted $1-k$ towards required capital.
-Alternatively $k$ is the proportion of assets $d+w$ excluded from capital calculations, and higher $k$ leads to higher capital shortfall.
+$$
+L\equiv\frac{d}{w}\cq \ell\equiv\ln\left(\frac{kL}{1-k}\right) = \logit(k) + \ln(L) \ .
+$$
+The quantity $\ell$ is called the adjusted log--leverage of firm  and $\ell>0$ implies, for the given $k$, capital shortfall is positive.
+The parameter $k$ is the proportion of assets $d+w$ excluded from capital calculations, and higher $ k$ leads to higher capital shortfall.
 
-A negative capital requirement -- that is a   surplus relative to requirements -- occurs  if $\ell<0$.
-The default index $\ell$ is the rate of return $r$ that must be achieved in order for the firm to be on the just out of  default.
-The default index $\ell$ depends on $k$, the prudential fraction.
+The $\logit(k)$ enters $\ell$ as an additive constant and has  minor role in the technical development and can be varied to test for senstivity etc.
+Assume\footnote{See for example \cite{brownlees2015}.} $k=0.08$ as under Basel II implying $\logit( k)=-2.44$ and the adjusted log--leverage $\ell$ is the actual log--leverage minus 2.44.
+At this $k$, if $S>0$ there is positive capital shortfall and  the firm or financial institution is said be in ``Basel default" or a ``Basel breach" has occurred.
+If $S<0$ there is capital surplus and  the firm is said to be ``Basel compliant."
 
-\subsection{Basel default}
-If $k=8\%$ and  \eref{capreq} is positive then the  firm or financial institution is said be in ``Basel default" or a ``Basel breach" has occurred.
-The value\footnote{See for example \cite{brownlees2015}.} $k=8\%$ is the Basel fraction and  implies $\logit( k)=-2.44$ and
-$
-\ell = \ln(L) - 2.44
-$.
-A firm is said to be in Basel default if the default index $\ell>0$ and $\ell$ can be considered as an index of the degree to which a firm is in default.
-Note  $\logit(k)$ enters $\ell$ as an additive constant and has  minor role in the subsequent technical development and can be varied to test for sensitivity to $k$.
+The definition of capital shortfall in \eref{shortfall} is restrictive if not simplistic.
+It is used here to conform to the previous literature and provide an easily accessible  platform to the key results of this paper,  without becoming entangled in precise and perhaps more realistic definitions of shortfall.
+Indeed \sref{riskmethod} deals with a more realistic and intricate definition.
 
-The shorfall definition \eref{capreq} is simplistic and restrictive.
-The definition and value $k=8\%$ is used here to conform to the previous literature and provide an easily accessible  platform to the key results of this paper,  without becoming entangled in precise and perhaps more realistic definitions of shortfall.
-\sref{riskmethod} deals with a more realistic but more intricate definition.
-
-\fref{Bloglev} displays default index $\ell$ with $ k=8\%$ for the four major and four minor Australian banks listed in \tref{banks} on the first trading day of each month from January 2003  through to December 2014.
-Note most banks are Basel compliant up to about 2008, entering into Basel default from 2009 as a result of the GFC.
-Prolonged Basel defaults are experienced for some banks, notably NAB.
+\fref{Bloglev} displays adjusted log--leverages $\ell$ with $ k=0.08$ for the four major and four minor Australian banks listed in \tref{banks} on the first trading day of each month from January 2003  through to December 2014.
+Note most banks are Basel compliant up to about 2008, entering into Basel breaches from 2009 as a result of the GFC.
+Prolonged Basel breaches are experienced for particular banks, notably NAB.
 
@@
 \begin{center}
-\includegraphics{figures/fig2.pdf}\caption{Basel default index  for four major (left panel) and four minor (right panel) Australian banks from the beginning of 2003 through to end of 2014.
+\includegraphics[width=16cm]{figures/bloglev.pdf}
+\caption{Adjusted log--leverages for four major (left panel) and four minor (right panel) Australian banks from the beginning of 2003 through to end of 2014.
 All banks contravene the threshold (corresponding to the zero horizontal) around the start of 2009.}\label{Bloglev}
@@
 
-\subsection{Future capital requirement and shortfall}
+\section{Future capital shortfall}\label{futshort}
 
-Financial institutions and regulators are concerned with future capital requirements, say in in a months time and in particular any potential shortfall.
-Given the definition \eref{capreq}  the future capital requirement of the firm depends on the future return on equity $r$.
-The future future equity is then  $w\e^{r}$ and assuming, as in \cite{brownlees2015} debt $d$ is constant, the  future capital requirement is, per unit $kd$ and analogous to \eref{capreq},
-\be{fcapreq}
-   S=1-\frac{1-k}{kL\e^{-r}} =1-\e^{r-\ell}\ .
+Financial institutions and regulators are concerned with future shortfall.
+Future shortfall depends on the future return on equity.
+If $r$ is the future return on equity over say a month then the  equity in one month's time is $w\e^r$ and future shortfall is
+\be{fshortfall}
+  S\equiv k d\left(1-\frac{1-k}{kL\e^{-r}}\right) = kd(1-\e^{r-\ell})\ .
 \ee
-The future return $r_i$ is unknown but its probability distribution may be relatively well understood and modelled.  Note $-\infty<S\le 1$ with $S=1$ indicating the future capital requirement is $kd$.
+This assumes debt $d$ stays constant over the month.   The future return $r$ is unknown but its probability distribution may be modelled and relatively well understood.
 
-The positive part of \eref{fcapreq} is the future capital shortfall per unit $kd$
+The actual capital shortfall is $S^+$, the positive part of $S$:
 \be{bs}
-S^+ = \left\{\begin{array}{lr} 0\ , & r\ge \ell\ ,\\ 1-\e^{r-\ell}\ , & r<\ell\ ,\end{array}\right.  
+S^+ = kd (1-\e^{r-\ell})^+\ .
 \ee
-where $^+$ denotes the ``positive part of."  
-Thus $S^+$ is  a put\footnote{Since $\E(S^+)=\E(S>0)\E(S|S>0)$ where   $\E(S^+)$ is the default probability  and $\E(S|S>0)$ is a measure of ``tail risk."   Both the default probability and tail risk are  defined relative to  $k$.
-Since the expectation is ``normal" the probability and tail risk are both ``base" cases.} on the return $\e^{r-\ell}$ with strike 1 and $0\le S^+\le 1$.
-From \eref{bs}, the  default index $\ell$ is the rate of return $r$ that must be achieved over the future period for the firm to just attain Basel solvency.
+Thus $S^+$ is $kd$ times a put on the return $\e^{r-\ell}$ with strike 1.
+There is a future shortfall if $r<\ell$.
 Default put options similar to \eref{bs} have been discussed in the insurance literature as critical to an evaluation of a firm:  see for
@@
 
-\subsection{Projecting future shortfall -- motivating example}
-In subsequent sections  time series methods are used to project future capital requirements \eref{fcapreq}  and in particular future shortfall $S$ defined in \eref{bs} for different firms $i$, under basis conditions and under stressed scenarios.
-These forecasts are used to determine the stress of both individual firms $i$ and the system as a whole.
-To understand the basis of the approach \fref{simulation},   displays two snapshot outputs from projections generated as described  in \aref{garchdcc}:  6000  simulated one month ahead projected returns for  CBA and the wider market, on  two dates: the first trading day in January 2009 and the first trading day in December 2014.
-The CBA returns are used to calculate the future shortfall per units $kd$ as in \eref{fcapreq}.
+To illustrate the setup, \fref{simulation}   displays two snapshot outputs from projections generated as described  in \aref{garchdcc}:  6000  simulated one month ahead projected returns for  CBA and the wider market, on  two dates: the first trading day in January 2009 and the first trading day in December 2014.
+The CBA returns are used to calculate the future shortfall per units $kd$ as in \eref{fshortfall}.
 Both panels use the same horizontal and vertical scales.
-Based on the available data at those two points in  time, policy makers and regulators faced entirely different projections.
+Thus based on the available data at those two points in  time, policy makers and regulators faced entirely different projections based on the same time series model.
 The scatter of dots are the forward simulations.
 Note there is no hindsight bias as the model at each time point is based on the available data to that point in time.
-In the left panel $S>0$ and a positive capital shortfall is projected for most scenarios.
-In the right panel $S=0$ and the banks are projected to have capital surpluses relative to requirements for any conceivable market scenarios.
+In the left panel $S>0$ for most scenarios.
+In the right panel $S<0$ for any conceivable market scenario.
 
@@
 In the right panel there is slight decline in the stock price, and a more substantial market downturn.
-Thus at the beginning of January  2009 the one month forward projection for  CBA was far from compliance, while in December 2014 the one month forward projection is of complete compliance.
+Thus at the beginning of January  2009 CBA was projected to be far from compliance in a month while in December 2014 the one month projection is of complete compliance.
 
  The two panels  display very different volatility and slopes.
-In January 2009 both CBA and the market return distributions are highly volatile and correlated.
+In January 2009 both CBA and market return distributions are highly volatile and correlated.
 The correlation remains strong in December 2014 but with less return volatility.
-Subsequent sections of this paper use time series of these  snapshots  to compute cross sectional and longitudinal basis and systemic stresses.
+These snapshots are used to compute baseline and systemic stresses shown in subsequent sections.
 
@@
 \begin{center}
-\includegraphics[width=12cm]{figures/figCBA.pdf}
-\caption{Forecast bivariate distribution of $C$ the projected  one month ahead capital requirement for CBA per unit $kd$ versus the market rate of return at start of January 2009 (left panel)  and December 2014 (right panel).
+\includegraphics[width=16cm]{figures/figCBA.pdf}
+\caption{Forecast bivariate distribution of future shortfall $S$ per unit $kd$  for CBA (vertical axis) and market rate of return (horizontal axis) at start of January 2009 (left panel)  and December 2014 (right panel).
 Note scales in both panels are the same, the relatively large volatility in the left panel, and the left skew in the  marginal distributions.
-Black dots indicate actual  outcome at the end of each month.}\label{simulation}
+Black dots indicate actual  outcome at the end of the month.}\label{simulation}
 \end{center}
@@
 
-\section{Monitoring systemic risk}\label{srisk}
+\section{Systemic risk SRISK}\label{srisk}
 
- \cite{brownlees2015} define  systemic risk\footnote{In contrast to \cite{brownlees2015} we factor out the scale factor $kd$ making for a more transparent 0 to 1 scale for \SR.} for a group of firms in terms of the expected future capital requirement $S_i$ for each firm $i$ in the group:
+ \cite{brownlees2015} defines  systemic risk for a group of firms  at a particular point of time as
 \be{esrisk}
-\SR =  \sum_i \pi_i\left\{\Es(S_i)\right\}^+ = \D[\{\Ex(S_i)\}^+]\cq \pi_i = \frac{d_i}{d}\cq d=\sum_id_i \ ,
+\sr\equiv \sum_i \left\{\Es(S_i)\right\}^+ \ ,
 \ee
-where $S_i$ is the shortfall \eref{fcapreq} for firm $i$.
-Here $\Es$ denotes expectation given the systemic event of a major general market downturn and $\D$ is debt weighted averaging.
-Further \SR\ is expressed in units $kd$ and $0\le\SR\le 1$ with \SR\ near 1 indicating extreme financial distress for all firms.
-\SR\ is based on the expected capital requirement and firms with an expected capital surplus under stress are ignored.
-The expression \eref{esrisk} slightly modifies the definition  of \cite{brownlees2015} by dividing their \SR\ expression by $kd$.
+where $S_i$ refers to the future shortfall in firm $i$.
+Further  $\Es$ denotes expectation given a major general market downturn.
+Hence the expected capital shortfall (allowing surplus offset) is computed from \eref{fshortfall} assuming a market downturn and added across all firms.
+Firms with an expected capital surplus under stress are ignored.
 
-The proportional contribution of firm $i$ to \SR \eref{esrisk}  is defined by   \citep{brownlees2015} as
+The systemic risk of firm $i$ at a particular point of time is defined by \cite{brownlees2015} as the proportionate contribution \eref{esrisk}:
 \be{sriskperc}
-\SR_i=\frac{\pi_i\{\Ex(S_i)\}^+}{\SR} \ .
+\sr_i\equiv\frac{\{\widetilde\E(S_i)\}^+}{\sr}\ .
  \ee
- Note $0\le \SR_i\le 1$ with larger values indicating firm $i$ is systemically important: it holds a high proportion $\pi_i$ of the total debt, and/or is likely to heavily breach the Basel capital requirement.
-Expression \eref{sriskperc} depends on $k$ through each of the default indexs $\ell_i$.
+Large $\mathrm{SRISK}_{i}$ indicates firm $i$ is systemically important: it holds a high proportion of the total debt, and it is likely to heavily breach the Basel capital requirement compared to remaining other firms.
+Expression \eref{sriskperc} depends on $k$ through each of the adjusted log--leverages $\ell_i$.
+Given a general market downturn, the values $\{\Es(S_i)\}^+$  in \eref{sriskperc} are known:  there is no uncertainty except for possible  uncertainty in estimating the stressed conditional  expected value.
 
-In this article we propose four modifications to \SR\ and $\SR_i$ defined in \eref{esrisk} and \eref{sriskperc}.
-These modifications are designed to improve stress monitoring.
-The  modifications  are shown,  theoretically and empirically, to have more  sensitivity and specificity.
-Sensitive, in the sense of more likely detect  firms likely to face financial distress.
-Specific in the sense of   minimising false alarms.
-The modifications are:
-\begin{enumerate}
-\item  Replacing $\{\Es(S_i)\} ^+$ in \eref{esrisk} and \eref{sriskperc} by $\Es(S_i^+)\ge\{\Es(S_i)\} ^+$.
-The justification is that typically $\Es(S_i)=0$ and  hence \eref{esrisk} is not affected by firms that  have zero expected capital requirement even though in individual instances that capital requirement may be large.
-Using $\Ex(S^+_i)$ instead of $\Ex(S_i)$ implies each firm counts with degree depending on the its proportionate contribution $\pi_i$ to total debt and the expected value of a put on its shortfall.
-Thus the analogue of \SR\  in \eref{srisk} is
-\be{srisk2}
-\sr=\Ex\{\D(S_i^+)\} = \D\{\Ex(S_i^+)\} = \sum_i\pi_i(\sr_i)\ ,
+The above general setup  is subject to criticisms and improvements.
+First, SRISK in \eref{sriskperc} can be modified to be based on $S_i^+$ the positive part of shortfall rather than the positive part of expected shortfall.
+In many cases $\Es(S_i)=0$  and insensitive to actual shortfalls.
+Second, the definition of $\Es$ is restrictive: a market downturn defined by a market downturn greater than 10\%.
+Such a specific absolute downturn is unnecessarily arbitrary.
+For example the downturn is more easily achieved  in a highly volatile environment and hence the stress response takes on different meanings depending on context.
+Third as shown below the stressed expectation $\Es$ is composed of two parts, so--called baseline risk and change in expectation risk caused by the actual stress event.
+
+\section{Improved systemic risk measurement}\label{improve}
+
+This section describes a general framework for  systemic risk measurement.
+The framework builds on and aims to improve on the techniques built into f \sr\ and $\sr_i$ in \eref{esrisk} and \eref{sriskperc}.
+The framework assumes a response variable such as capital shortfall $S$ or $S^+$ for a firm or group of firm subjected to stress.
+The  framework   puts ``stress testing" on a formal footing.
+
+For notational convenience assume the response of interest is $S$ although this can be replaced with $S^+$ or some other function of $S$.  The framework is built up from the following parts:
+\bi
+\i  A stress function $\psi(\omega)\ge 0$ defined on scenarios $\omega$.
+Scenarios $\omega$ can be discrete or continuous.
+Further $\E(\psi)=1$ where expectation is across all scenarios.
+Scenarios $\omega$ are systemic if they have potential impact on many firms.
+\i  Baseline risk is defined as the ordinary expectation
+$$
+\br\equiv \E(S)\equiv\sum_\omega f(\omega) \E(S|\omega)\ ,
+$$
+where $f(\omega)$ denotes the ``real world" probabilities of different scenarios.    If the space of scenarios is continuous then $f(\omega)$ is a density and the  sum an integral.
+\i Stressed expectation  is defined in terms of the stress function as
+\be{formula}
+\Es(S) \equiv \sum_\omega \psi(\omega) f(\omega)\E(S|\omega)=\E\{\psi\E(S|\psi)\}=\E(\psi S)=\E(S)+\cov(S,\psi)\ ,
 \ee
-where $0\le \sr_i\le 1$ and $\pi_i(\sr_i)$ is the proportion of \sr\ originating in firm $i$.
-
-\item Using more general   definitions of $\Es$ to encompass more flexible stress specifications.
-Modelling stress  as  10\% market general market downturn or more, while interesting, is obviously arbitrary.
-This paper posits more flexible and robust specification of stressed expectation $\Ex$.
-This is discussed in \sref{formal}.
-
-\item The srisk defined in \eref{srisk2} is broken up into two components
-\be{breakup}
-\sr=\D\{\E(S_i^+)\}+\D[\{\Ex(S_i^+)\}-\E(S_i^+)\}]\ . 
-\ee
-called the base risk and strain, respectively.
-Hence \sr\ is a debt weighted average of base risks and strains.
-A firm counts highly in \sr\  if it carries a significant portion of total debt,  has high base risk and  high strain.
-
-\item Pooled base risk is defined as  $0\le\E(S^+)\le 1$ where $S=\D(S_i)$.  Similarly pooled strain is  
-$\Ex(S^+)-\E(S^+)$.
-
-\item Non--pooled shortfall is defined as $S^*=\sum_iS_i^+$ with non--pooled base risk $\E(S^*)$ and strain $\Ex(S^*)-\E(S^*)$.
-
-\item Similar to before, $\Ex(S_i^+)=\Ex(S_i^+>0)\Ex(S_i|S_i>0)$.   The two factors on the right are called the stressed default probability and stressed tail risk, respectively.    The measures
+where the last equality follows since $\E(\psi)=1$.
+The import of $\psi(\omega)$ is to change the natural probabilities $f(\omega)$ to ``stressed" probabilities $\tilde f(\omega)\equiv \psi(\omega)f(\omega)$.
+Note $\sum_\omega \tilde f(\omega)=\E(\psi)=1$.
+ \i $\psi$--risk is defined as the difference between baseline risk and stressed risk
  $$
-\Ex(S_i^+>0)-\E(S_i^+>0)\cq \Ex(S_i|S_i>0)-\E(S_i|S_i>0)
+ \pr \equiv \Es(S)-\E(S) = \cov(S,\psi)\cq \Es(S)=\br+\pr\ .
  $$
-are the default probability and tail risk strain, respectively.
-
-\item    System  base resilience  is measured with the positive number 
-\be{resil}
- \ln \frac{\E(S^*)}{\E(S^+)} = \ln\frac{\E(S^*>0)}{\E(S^+>0)} + \ln\frac{\E(S^*|S^*>0)}{\E(S^+|S^+>0)}\ .
-\ee
-A large value indicates shortfall in individual firms can be absorbed in the system.
-A value near zero indicates there is no capacity for the system to absorb shortfall in individual firms.
-Using $\Ex$ instead of $\E$ in \eref{resil} yields the resilience under stress.
-
-\end{enumerate}
-
-\section{A formal framework for systemic risk measurement}\label{formal}
-The  proposed improved framework considers future capital shortfall $S$ as defined in \eref{fcapreq}  for a a single firm or group of firms.
-Then the framework for measuring stress may focus on $S$, the positive part  $S^+$ as defined in \eref{bs}, or a more general function of $S$.
-For concreteness suppose the focus is on $S^+$.
-
-The improved framework consists of:
-\bi
-\i  A collection of scenarios generically labelled $\omega$ where  $\omega$ discrete or continuous.
-Scenarios may be both benign or serious in terms of their potential impact on shortfall $S$.
-Scenarios $\omega$ are systemic if they have potential impact on many firms.
-
-\i The ``natural" probability of scenario $\omega$ is $p(\omega)$.   If $\omega$ is continuous then $p(\omega)$ is interpreted as a probability density.
-
-\i  Basis strain is defined as the ordinary expectation
-$$
- \E(S^+)=\sum_\omega p(\omega) \E(S^+|\omega)\cq 0\le\E(S^+)\le 1\ .
-$$
-For continuous $\omega$,  the sum is interpreted as an integral.
-
-\i  A stress function $\psi(\omega)\ge 0$ defined on the  scenarios $\omega$ with  $\E(\psi)=1$.
-The stress function serves to amplify or downplay the importance of different scenarios.
-On average the amplification is 1.
-The stress function serves to ``bias" outcomes towards ``stressful" scenarios, that is scenarios likely to drive up shortfall.
-
-\i The \sr\ of a firm is the expected shortfall under the stressed probabilities $\psi(\omega)p(\omega)$:
-\be{formula}
-\Es(S^+) = \E\{\psi\E(S^+|\psi)\}=\E(\psi S^+)=\E(S^+)+\cov(S^+,\psi)\ ,
-\ee
-where the last equality follows since $\E(\psi)=1$.   Note $0\le\Ex(S^+)\le 1$.     
-The import of $\psi(\omega)$ is to change the natural probabilities $p(\omega)$ to ``stressed" probabilities $\psi(\omega)p(\omega)$.
-
- \i The strain is defined as the additional expectation due to stress 
- $$
-\Es(S^+)-\E(S^+)\cq \mathrm{srisk} = (\mathrm{base\ risk})+\mathrm{strain}\ \ .
- $$
-
- \i Note that 
- $$
- \ln\frac{\Ex(S^+)}{\E(S^+)} = \ln \frac{\Ex(S>0)}{\E(S>0)} +\ln\frac{\Ex(S|S>0)}{\E(S|S>0)}\ .
- $$
- That is, the approximate percentage change in risk due to stress is the the percentage change in the default probability plus the percentage change in the tail risk.
 \ei
 
-\subsection{Practical stress functions}
-The simplest example is where $\psi(\omega)=0$ except for a single  scenario $\omega$ where it is equal to $1/p(\omega)$.
+ A simple example is where $\psi(\omega)=0$ except for a single  scenario $\omega$ where it is equal to $1/f(\omega)$.
 In this case all probability is transferred to the single scenario $\omega$ and $\Es(S)=\E(S|\omega)$.
-This conditional expectation is often modelled and computed with a spreadsheet.
+The conditional expectation is often computed with a spreadsheet.
 
-The stress function used in  \cite{brownlees2015} is where $\omega$ is the market return and $\psi(\omega)=0$ unless $\omega\le 0.1$ in which case $\psi(\omega) = c$ where $c$ is 	 such that the area under $\psi$ is 1.
-In other words scenarios are different market returns with stress being zero unless market return is  a drop of 10\% or more.
-This stress function is quite blunt:   stress is either on or off and if on there is no reckoning as to the degree of stress.
-
-A richer example is where $\omega$ is the percentile of a variable such as the overall market return, measured relative to the current  market return distribution.
-Then $p(\omega)$ is the uniform density on the unit interval.
+A richer example is where $\omega$ is the percentile of a variable such as the overall market return, measured relative to the currently applicable market return distribution.
+Then $f(\omega)$ is the uniform density on the unit interval.
 If
@@
 then $\psi$ is the density of the worst percentile outcome in $n$ independent trials.
-In this case \pr\  corresponds to the increase in risk when the general market has its worst outcome in $n$ independent trials given the current return distribution.
+This stress function implies \pr\  corresponds to the increase in risk when the general market has its worst outcome in $n$ independent trials.
 This stress function  is used to study stress in Australian banks in \sref{simulate1}.
@@
 Another example, close to that implemented in \cite{brownlees2015} is where $\omega$ is a percentile with $\psi(\omega)=1/c$ for $\omega<c$ and 0 otherwise.
-In this case  $\Es(S)=\E(S|\psi<c)$ and \pr\  is the difference between the   tail and ordinary expectation.
+In this case  $\Es(S)=\E(S|\psi<c)$ and \pr\  is the difference between the  conditional tail and ordinary expectation.
 More general stressed expectations of the form of \eref{formula} are discussed in \cite{furman2008weighted1} and \cite{choo2010determining}.
 
-\subsection{Strain potential}
+Both \br\ and \pr\ are linear and aggregate over firms.  For example
+$$
+\pr\left(\sum_iS_i\right) = \sum_i\pr\left(S_i\right)\ .
+$$
+Linearity is obvious for \br\ and for \pr\  follows from the linearity of covariance.
 
-A  measure of potential for a stress function $\psi$ to induce strain is its volatility denoted $\sigma_\psi$.
-If $\psi$ is constant then $\sigma_\psi=0$.
-If $\psi(\omega)$ picks out a single scenario $\omega$ then
+A useful measure of the ``danger" associated with a stressor is the volatility of $\psi$ denoted $\sigma_\psi=\sqrt{\pr(\psi)}$.
+For example if $\psi(\omega)$ picks out a single scenario $\omega$ then
 $$
-\sigma_\psi= \e^{-\logit\{p(\omega)\}/2}\ ,
+\sigma_\psi= \e^{-\logit\{f(\omega)\}/2}\ ,
 $$
-which is large if the scenario probability $p(\omega)$ is small.
-
-Standardised strain is: 
+which is large if the scenario probability $f(\omega)$ is small.  This suggest standardising \pr:
 $$
-\beta_\psi= \frac{\mathrm{strain}}{\sigma_\psi}=\sigma_{S^+} \times\cor(S^+,\psi)\ .
+\beta_\psi\equiv\frac{\pr}{\sigma_\psi} = \frac{\Es(S)-\E(S)}{\sigma_\psi}=\sigma_S\cor(S,\psi)\ .
 $$
@@
 Here $\cor$ denotes correlation.
-The measure $\beta_\psi$ facilitates the comparison of strain on $S$ across different stressors and has the interpretation of a regression coefficient:
+Standardised \pr\ $\beta_\psi$ facilitates the comparison of stress on $S$ across different stressors and, as the notation suggests, has the interpretation of a regression coefficient:
 $$
-\E(S^+|\psi=x) \approx (\br) +\left(\frac{\st}{\sigma_\psi}\right)\left(\frac{x-1}{\sigma_\psi}\right)\ .
+\E(S|\psi=x) \approx \E(S)+\beta_\psi \left(\frac{x-1}{\sigma_\psi}\right)\ .
 $$
-Thus $\beta_\psi$ measures, in minimum mean square error sense, the change in strain as stress increases by one standardised unit.
+Thus $\beta_\psi$ measures, in minimum mean square error sense, the change in the expectation of $S$ as stress increases by one standardised unit.
 
- Strain can also be measured  in units of $S$ volatility:
+  Stress can also be measured  in units of $S$ volatility:
 $$
-\frac{\Es(S^+)-\E(S^+)}{\sigma_{S^+}}=\sigma_\psi\cor(S^+,\psi)\ .
+\frac{\pr}{\sigma_S}=\frac{\Es(S)-\E(S)}{\sigma_S}=\sigma_\psi\cor(S,\psi)\ .
 $$
-This measure gauges the extremity of strain.
+This measure gauges the extremity of shortfall.
 
-\subsection{Computing basis strain and stress strain via simulation}
-Given $N$ simulations $\omega\sim p(\omega)$ and $S(\omega)\sim p(S|\omega)$  then  $S(\omega)\sim p(S)$ and  
+In many financial contexts expected shortfalls  may increase  due to increased volatility.   This is captured with \br.  \pr\ focusses on the  stress effects induced with $\psi$.
+
+\br\ and \pr\ are easily computed  in a simulation environment given a joint model $f(S,\psi)=f(\psi)f(S|\psi)$ for $S$ and the scenarios $\omega$.
+If $N$ of simulations $\omega\sim f(\omega)$ and $S(\omega)\sim f(S|\omega)$ are generated and then
 $$
- \frac{1}{N}\sum_\omega S^+(\omega)\rightarrow \E(S^+) \cq \frac{1}{N}\sum_\omega \psi(\omega)S^+(\omega)\rightarrow \Ex(S^+) \ ,
+\br \approx \frac{1}{N}\sum_\omega S(\omega)\cq \pr\approx \frac{1}{N}\sum_\omega \{\psi(\omega)-1\}S(\omega)
 $$
-as the simulation effort $N$ increases.
+If $\psi$ is based  on percentile outcomes   then the simulated $\omega$ are ranked and $\psi(\omega)$ based on the rank of $\omega$.
+If $\omega$ has many components corresponding to percentiles of different variables then $\psi(\omega)$ is a copula density with appropriate induced tail dependence.
 
-If $\psi$ is based  on percentile outcomes   then the simulated $\omega$ are ranked and $\psi(\omega)$ is computed from the empirical rank of $\omega$.
-If $\omega$ has many components corresponding to percentiles of different variables then $\psi(\omega)$ is a copula density chosen to induce appropriate  tail dependence.
+\section{Forward shortfall and  return simulations}\label{simulate}
 
- As in \cite{brownlees2015},  $\omega$ in the next section is the projected  market return while $S(\omega)$ or more particularly $S_i(\omega)$  is the shortfall for firm $i$ based on its projected rate of return $r_i$ given the market return $\omega$.
-The joint distribution of $\omega$ and $r_i$ is simulated  from  fitted bivariate time series models.
-The market return is used as the stressor with the stress function $\psi$ modelling  stress scenarios.
+The estimation of \br\  and \pr\   requires simulated future capital shortfalls.
+As in \cite{brownlees2015}, projections in this paper are constructed  using time series models of forward rates of return  for each bank $i$ and the market rate of return.
+The market return is used as the stressor with different choices of the stress function $\psi$ modelling different stress scenarios.
 
-The time series models used are stochastic volatility models based on the GARCH--DCC framework of \cite{engle2002dynamic} summarised in \aref{garchdcc}.
+The time series models used are stochastic volatility models based on the GARCH--DCC model of \cite{engle2002dynamic} summarised in \aref{garchdcc}.
 The GARCH-DCC model captures prolonged periods of high volatility and correlation in firm and market returns, typical in financial markets.
@@
 judiciously constructed scenarios by regulators or policymakers.
-The  framework set out in \sref{srisk} can be based on  any  generated  future  scenarios.
+The  framework set out in \sref{improve} can be based on  any  generated  future  scenarios.
 
@@
 This implies higher systemic stress in December 2008.
-In addition $S$ volatilities are much higher in the left panel compared to the right, indicating higher basis stress in December 2008.
+In addition $S$ volatilities are much higher in the left panel compared to the right, indicating higher baseline stress in December 2008.
 Also note that with a stressor function $\psi$ defined in terms of market return percentiles, the magnitude of a market downturn at a fixed percentile threshold is more significant in the left panel.
 
-\section{Australian bank stress forecasts}\label{simulate1}
+\section{One month ahead forecast risk in individual banks}\label{simulate1}
 
-\fref{fig4} displays, in the top panels, the estimated basis risk for each major (left) and minor (right) Australian banks based on the projected one month ahead return distribution fitted using the GARCH--DCC model.
+\fref{default} displays, in the top panels, the estimated \br\  corresponding to $S^+$ for each major (left) and minor (right) Australian banks based on the projected one month ahead return distribution fitted using the GARCH--DCC model.
 Note the return distributions are constructed from data only available at that time and hence are not affected by look--ahead bias.
-The first inclinations of increasing basis risk occurs with NAB in early 2008 followed one month later by ANZ, and  a further few months later by WBC and CBA.
-basis risk subsided shortly after 2009, however basis risk for NAB rose again in 2011 and this sustained till 2013.
-In general smaller banks are subject to higher basis risk after normalising for debt levels.
+The first inclinations of increasing \br\ with NAB in early 2008 followed one month later by ANZ, and  a further few months later by WBC and CBA.
+\br\ subsided shortly after 2009, however \br\  for NAB rose again in 2011 and this sustained till 2013.
+In general smaller banks are subject to higher \br\  after normalising for debt levels.
 
@@
 \begin{center}
-\includegraphics[width=12cm]{figures/fig4.pdf}
-\caption{Basis strain  (top panels) and stress strain (bottom panels) based on one month ahead  forecasts $S_i^+$ for   major (left panel) and  minor (right panel)  Australian banks 2003--2014.
-Stress is based on worst monthly market outcome in 1 year.
-Note different y--scale on top and bottom panels.}\label{fig4}
+\includegraphics[width=16cm]{figures/default.pdf}
+\caption{Forecast one month ahead  \br\ (top panels) and \pr\ (bottom panels) based on $S^+$ for   major (left panel) and  minor (right panel)  banks 2003--2014.
+Note different y--scale on top and bottom panels.}\label{default}
 \end{center}
@@
 
-\fref{fig5} gives a picture of the relative magnitudes of \br\ and \pr\ in each of the eight banks.
-For the major banks NAB stand out as, having \br\ more dominant than \pr\ and generally having heightened levels of \br.
-ANZ appears to have relatively higher levels of \pr.
-For the minors, MQG has persistently higher levels of \pr\ with BOQ and BEN comparable ratios and ABA having virtually no \pr\ compared to \br\ at any level of the latter.
+\section{Aggregate market stress}\label{aggregate}
 
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=12cm]{figures/fig5.pdf}
-\caption{Historical relationship between stress strain and basis strain    for major   and  minor banks.}
-\label{fig5}
-\end{center}
-\end{figure}
+\cite{brownlees2015} defines systemic risk in terms of $\Es(S)$.
+However a stressed expectation may be high simply on account of  higher than normal volatility or leverage.
+Hence \cite{brownlees2015} combines both baseline stress, due to high volatility or leverage, and the imposed system stress.
+However it is important to understand the mix of the two different stresses.
 
-\section{Monitoring aggregate  stress and contagion}\label{aggregate}
-
-This section uses two measures of future aggregate shortfall for a group of firms based on two different methods of aggregating default risk across firms:
-$$
-S^+ = \{\D(S_i)\}^+\le \D(S_i^+) =S^*\ .
-$$
-Here $S^+$ is referred to as the ``pooled" or ``diversified" shortfall with shortfall in one firm able to be offset by surplus elsewhere.
-The shortfall $S^*$ is ``non--diversified" with shortfall in each firm $i$ adding up.
-
-With $\Ex(S^+)$ heightened risk only arises if there is an ``on average"  shortfall.
-Thus SRISK is relatively insensitive to tail events.
-The second aggregation of risk displayed in \tref{dsrisk} uses $S^*$, the  sum of positive shortfalls across firms.
-With $S^*$, shortfall within a firm is not offset by averaging  nor with surpluses in other firms.
-The measure is thus more sensitive to tail risk.
-
-The second aggregation of risk displayed in \tref{dsrisk} uses $S^*$, the  sum of positive shortfalls across firms.
-With $S^*$, shortfall within a firm is not offset by averaging  nor with surpluses in other firms.
-The measure is thus more sensitive to tail risk.
-
-Our measures of basis and stress contagion are 
-\be{cont}
-\frac{\E(S^+)}{\E(S^*)}\cq  \frac{\Ex(S^+)}{\Ex(S^*)}- \frac{\E(S^+)}{\E(S^*)}
-\ee
- both of which lies between 0 and 1.
-A value near one indicates little of the risk in the group of firms, due to basis events or stress is absorbable and hence defaults are not diversifiable.
-A value near 0 indicates virtually all of the risk in the system can ``diversified away."
-
- \tref{dsrisk} displays and compares and contrasts the different definitions of risk.
-The last line of \tref{dsrisk} reproduces the \SR\  measure of \cite{brownlees2015}.
-Note $\Es(S)$ combines both basis stress, due to high volatility or leverage, and the imposed hypothetical stress.
-To understand the nature of stress it is important to understand the mix of these two different stresses.
+Two practical alternatives to SRISK for aggregating risk in financial institutions are set out \tref{aggstress}.  
+The first row of the table reproduces the defintion of SRISK in \eref{srisk} and decomposes the same into \br\ and \pr.
+It is apparent that \sr\  measures a mix of \br\ and \pr.
+Further risks only arise if there is an ``on average"  shortfall and the measure is relatively insensitive to tail events .
 
 \begin{table}[htbp]
-\caption{Different strains}\label{dsrisk}
+\caption{Measures of aggregate stress}\label{aggstress}
+\small
 \begin{center}
-\begin{tabular}{l|c|c|c}
+\begin{tabular}{l|l}
 \hline
-& basis & strain & srisk\\
+Measure&Expression\\
 \hline
-pooled &$\E(S^+)$ &$ \Ex(S^+)-\E(S^+)$ & $\Ex(S^+)$\\
-non--pooled & $\E(S^*)$& $\Ex(S^*)-\E(S^*)$&$\Ex(S^*)$\\
-\hline
-resilience & $\ln\frac{\E(S^*)}{\E(S^+)}$& $\ln\frac{\Ex(S^*)}{\Ex(S^+)}-\ln\frac{\E(S^*)}{\E(S^+)}$&$\ln\frac{\Ex(S^*)}{\Ex(S^+)}$ \\
-\hline
-\SR & \multicolumn{2}{c}{$\D[\{\Ex(S_i)\}^+]$}\\
+SRISK \citep{brownlees2015} & $\sum_i\{\Es(S_i)\}^+=\sum_i\{\br(S_i)+\pr(S_i)\}^+$ \\
+No shortfall diversification: $S^*\equiv\sum_iS_i^+$  &$\sum_i\Es(S_i^+)=\br(S^*) +\pr(S^*)$ \\
+Shortfall diversification:
+$ S\equiv \sum_iS_i$&$\Es\{(\sum_iS_i)^+\}=\br(S^+) +\pr(S^+)$\\
 \hline
@@
 \end{center}
-\label{default}
+\normalsize
 \end{table}%
+
+The second aggregation of risk displayed in \tref{aggstress} uses $S^*$, the aggregate sum of positive shortfalls.
+With $S^*$ shortfall in one firm are not offset by  surpluses elsewhere and the measure is sensitive to tail risk.
+If subscript $\%$ denotes percentage contribution to the corresponding total then a direct calculation shows the total risk $\br+\pr$ in $S_i^+$ as a percentage of the total risk in  $S^*\equiv \sum_iS^+_i\ge S^+$ is
+\be{percc}
+ \pr_\%(S^+_i)+\frac{\br(S^*)}{\br(S^*)+\pr(S^*)}\left\{\br_\%(S^+_i)-\pr_\%(S^+_i)\right\}\ ,
+\ee
+ where the percentage subscripts indicate percentages of the corresponding totals.
+Thus total risk is dominated by \br\ if the latter is large compared to \pr\ as apparent in the time series analyses in \sref{simulate1}.
+
+ The final  row measure of \tref{aggstress}  allows for pooling of  shortfall across firms.  Since $S^*\ge S^+$ and both \br\  and \pr\ are additive 
+ $$
+ \sum_i\br(S_i^+)=\br(S^*)\ge\br(S^+)\ ,
+ $$$$
+ \sum_i\pr(S_i^+)=\pr(S^*) = \pr(S^+)+\pr(S^*-S^+)\ .
+ $$
+The difference $S^*-S^+$ is the ``diversifiable" shortfall and $\pr(S^*-S^+)$ measures the covariance between the diversifiable shortfall and  stress $\psi$.
 
@@
 
-\section{Monitoring individual banks contribution to stress}
-
-The proportionate contributions of bank $i$ to base risk, strain and \sr\ are 
-\be{contrib}
-\frac{\pi_i\E(S_i^+)}{\D\{\E(S_i^+)\}}\cq \frac{\pi_i\{\Ex(S_i^+)-\E(S_i^+)\}}{\D\{\Ex(S_i^+)-\E(S_i^+)\}}\cq \frac{\pi_i\Ex(S_i^+)}{\D\{\Ex(S_i^+)\}}\ ,
-\ee
-respectively.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=12cm]{figures/fig6.pdf}
-\caption{Projected one month  Australian banks risks through the financial crisis years 2008 through to the end of 2010.
-Top panels are basis risk and stress risk.
-Bottom left panel computes  basis and stress risk using pooling and no--pooling, and compares the same to \SR.
-Bottom right panel displays contagion risk as defined in equation \eref{cont}.}
-\label{fig6}
-\end{center}
-\end{figure}
-
-\subsection{Aggregate stress in the Australian banking sector}\label{monitoring}
- \tref{jan2009} contains real time stress calculations on the first trading day of  January 2009.
+\section{Monthly monitoring  of financial stress}\label{monitoring}
+ \tref{twodates} contains real time stress calculations on the first trading day of  January 2009 and December 2014.
 As before there is no look ahead bias -- calculations on each of the two dates use data available on the first day of the applicable month.
-The first eight rows in in the body of \tref{jan2009} correspond to the eight banks used in this study.
-The first  and second columns in the two halves of the table body contain the default index  and debt  (as a percentage of total system debt) for each of the banks.
-
-The absorbance capacity is a measure of the system to absorb base risk, strain or srisk through merger.
-If, for example, $\E(S^+)$ is much smaller than $\E(S^*)$ then a large portion of base risk can be ``diversified away" by merging firms.
-This suggest the measures
-$$
-1-\frac{\E(S^+)}{\E(S^*)}\approx\ln\frac{\E(S^*)}{\E(S^+)}\cq \frac{\Ex(S^*)-\E(S^*)}{\Ex(S^+)-\E(S^+)}\cq \frac{\Ex(S^*)}{\Ex(S^+)} \ .
-$$
-The first and last measures lie between 0 and 1 with values near 0 
- near 0 indicating there is no pooling buffer. \tref{jan2009} displays the calculations for January 2009.
+The first eight rows in in the body of \tref{twodates} correspond to the eight banks used in this study.
+The first  and second columns in the two halves of the table body contain the
+ Adjusted log--leverage  and debt  (as a percentage of total sustem debt) for each of the banks.
 
 \begin{table}[ht]
- \caption{Analysis of bank  risk:  January 2009}\label{jan2009}
+\caption{Projected one month ahead  stress for banks}
+\label{twodates}
 \centering
-\begin{tabular}{l|rr|rrr}
+\begin{threeparttable}
+\small
+\vspace{4mm}
+\begin{tabular}{l|rrrr|rrrr}
 \hline
- & default & debt & \multicolumn{3}{c}{\% of non--pooled}  \\ 
- \cline{4-6}
-bank & index  & \% & base risk & strain & $\mathrm{srisk}$\\
+&\multicolumn{4}{c|}{January 2009}&\multicolumn{4}{c}{December 2014}\\
   \hline
-CBA & 18.57 & 24.30 & 22.99 & 29.60 & 25.20 \\ 
-  ANZ & 15.93 & 18.37 & 14.87 & 18.89 & 16.21 \\ 
-  NAB & 31.97 & 25.50 & 39.98 & 19.41 & 33.10 \\ 
-  WBC & -1.55 & 22.84 & 5.86 & 23.94 & 11.91 \\ 
-  MQG & 41.22 & 5.75 & 11.02 & 5.46 & 9.16 \\ 
-  BOQ & 63.30 & 1.32 & 3.55 & 0.99 & 2.70 \\ 
-  BEN & 18.91 & 1.81 & 1.72 & 1.71 & 1.72 \\ 
-  ABA & -8.12 & 0.10 & 0.00 & 0.00 & 0.00 \\ 
+   & Aloglev& Debt & \br  & \pr  & Aloglev & Debt  &\br & \pr\\  
+ %  & $\ell$ & $d$ &$\E(S_i^+)$&$\Psi(S_i^+)$& $\ell$&$d$ & $\E(S_i^+)$ & $\Psi(S_i^+)$ \\
   \hline
-  \multicolumn{3}{r|}{non--pooled}  & 17.17 & 8.63 & 25.80 \\ 
-  \multicolumn{3}{r|}{pooled} & 15.28 & 10.18 & 25.46 \\ 
-  \multicolumn{3}{r|}{resilience} & 11.66 & -16.48 & 1.34 \\ 
+CBA & 18.57 & 24.30 & 22.99 & 29.60 & -70.34 & 22.70 & 0.00 & 0.00 \\ 
+  ANZ & 15.93 & 18.37 & 14.87 & 18.89 & -38.64 & 22.10 & 0.00 & 0.00 \\ 
+  NAB & 31.97 & 25.50 & 39.98 & 19.41 & -12.45 & 25.61 & 50.52 & 67.13 \\ 
+  WBC & -1.55 & 22.84 & 5.86 & 23.94 & -53.84 & 22.03 & 0.00 & 0.00 \\ 
+  MQG & 41.22 & 5.75 & 11.02 & 5.46 & -46.10 & 4.33 & 0.17 & 0.12 \\ 
+  BOQ & 63.30 & 1.32 & 3.55 & 0.99 & -17.05 & 1.33 & 0.80 & 1.34 \\ 
+  BEN & 18.91 & 1.81 & 1.72 & 1.71 & -7.63 & 1.84 & 25.43 & 30.71 \\ 
+  ABA & -8.12 & 0.10 & 0.00 & 0.00 & 9.22 & 0.07 & 23.07 & 0.71 \\ 
   \hline
+  Total $S^*$ & 18.78 & 2.42 & 17.17 & 8.63 & -41.91 & 3.27 & 0.03 & 0.12 \\ 
+  Pooled $S^+$ & 17.81 & 2.42 & 15.28 & 10.18 & -44.22 & 3.27 & 0.00 & 0.00 \\ \hline
 \end{tabular}
+\begin{tablenotes}
+\item[]The main body of table uses shortfall measure  is $S_i^+$.
+Aloglev is 100 times the adjusted log--leverage.
+\pr\  is with respect to expected worst monthly market return  in 12 months.
+Main body of table displays percentage contributions of each firm to totals displayed in ``Total" row.
+Total row displays 100 times debt weighted adjusted log--leverage, total debt in \$$10^{11}$, and \br\  and \pr\  per $0.08\times$debt and based on $S^*$.
+Pooled row displays results with debt and equity pooled across banks and results based on $S^+$.
+\end{tablenotes}
+\end{threeparttable}
 \end{table}
+\normalsize
 
-January 2009 was a time of great strain for all eight banks.
-Six of the eight banks were in Basel default with positive capital shortfalls as indicated by the default index column:   the two banks not in Basel default were WBC and ABA.
+January 2009 was a time of great stress for all eight banks.
+Six of the eight banks were in Basel default with positive capital shortfalls as indicated by the adjusted log--leverage column:   the two banks not in Basel default were WBC and ABA.
 
- Percentage base risk, strain and srisk    are displayed in the next 3 columns.
-Most of the base risk arises from NAB -- almost 40\% of the total.
-The next most base risk arises from  is CBA.
-MQG  contributes almost double to base risk compared to the proportion of total debt  it carries.
-The other three small banks contribute relatively little to base risk with BOQ  almost 3 times expected on the basis of its debt.
+ Percentage \br\  and \pr\  are displayed in the next 2 columns in each half of the table.
+The baseline stress column indicates most of the baseline stress arises from NAB -- almost 40\% of the total.
+The next most baseline stressed bank is CBA with WBC also a substantial contributor.
+The MQG bank contributes almost double to baseline stress compared to the proportion of total debt  it carries.
+The other three small banks contribute relatively little to baseline stress with BOQ  almost 3 times expected on the basis of its debt.
+\pr\   is highest for the CBA, higher than expected on the basis of its debt load and hence CBA was most susceptible to stress from additional general market equity devaluation.
+All other banks appear have \pr\ comparable to their size in terms of debt load with only NAB being less systemically important.
+This should be compared to NAB's high baseline stress.
 
-Strain  is highest for the CBA, higher than expected on the basis of its debt load and hence CBA was most susceptible to stress from additional general market equity devaluation.
-All other banks appear have strain comparable to their size in terms of debt load with only NAB having proportionally less strain.
-This should be compared to NAB's high base risk.
-
-The final two rows of \tref{jan2009} indicate the total amount of stress in the system and it's diversifiability.    
-The second last  row labelled ``Total"  displays, in order, debt weighted default index, total \br\  and total \pr.
+Continuing with January 2009, the final two rows indicate the total amount of stress in the system and it's diversifiability.    
+The second last  row labelled ``Total"  displays, in order, debt weighted adjusted log--leverage, total \br\  and total \pr.
 On aggregate Total \br\  is about twice \pr.
 Thus there is more danger of increasing capital shortfall due to market volatility  as opposed to further stress from further substantial general market devaluation.
-The final row indicates stresses are not diversifiable:    The marginally  smaller  ``diversified"  basis stress is offset by an increase in \pr.
+The final row indicates stresses are not diversifiable:    The marginally  smaller  ``diversified"  baseline stress is offset by an increase in \pr.
 
@@
 Most  \br\ is carried by NAB with lesser contributions by BEN and ABA.
-All the stress in the minor bank ABA is basis stress as only NAB and NAB have substantial \pr\  contributions.
+All the stress in the minor bank ABA is baseline stress as only NAB and NAB have substantial \pr\  contributions.
 Again, however, it must be emphasised that there is minimal systemic stress in the system.
@@
 
-The two  panels of \fref{fig6} track  \br\ and \pr\ for the banking sector as a whole through time.
+The two top panels of \fref{muqs} track  \br\ and \pr\ for the banking sector as a whole through time.
 There is virtually no risk in the system till late 2007 and the early warnings show a buildup in \br\ in $S^*$ compared to $S^+$.
@@
 
-The top right panel in \fref{fig6} displays the time series behaviour of \pr.
+The top right panels in \fref{muqs} display the time series behaviour of \pr.
 Generally \pr\ is less than \br.
-Further, in situations of elevated risk,  \pr\ in $S^+$ exceeds that in $S^*$ indicating systemic stress from a general market downturn is greater in the system as a whole than its constituent parts.
+Further, in situations of elevated risk,  \pr\ in $S^+$ exceeds that in $S^*f$ indicating systemic stress from a general market downturn is greater in the system as a whole than its constituent parts.
 Again, however, as displayed in the bottom right panel, \pr\ initially builds up in $S^*$, and only later manifests itself in $S^+$.
@@
 
+\fref{sysstress} gives a picture of the relative magnitudes of \br\ and \pr\ in each of the eight banks.
+For the major banks NAB stands out as, having \br\ more dominant than \pr\ and generally having heightened levels of \br.
+ANZ appears to have relatively higher levels of \pr.
+For the minors, MQG has persistently higher levels of \pr\ with BOQ and BEN comparable ratios and ABA having virtually no \pr\ compares to \br\ at any level of the latter.
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=16cm]{figures/muqs.pdf}
+\caption{Risk based on $S^*$ and $S^+$.
+Results for \br\ and \pr\ in left and right panels, respectively.
+The top panels track results   from the beginning of 2003 through to the end of 2014.
+Bottom panels  plot  two measures in the corresponding top panel against each other: On the left \br($S^+$) on y--axis versus \br($S^*$) on x--axis, and similarly for  \pr\ in the bottom right panel.}\label{muqs}
+\end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=16cm]{figures/sysstress.pdf}
+\caption{\pr\  (y--axis) versus \br\  (x--axis)   for major banks (left panel) and  minor banks (right panel)  for 144 months 2003--2014}
+\label{sysstress}
+\end{center}
+\end{figure}
+
 \section{Risk weighted asset methodology}\label{riskmethod}
 
-The current stress framework can be used in conjunction with   the  risk weighting asset (RWA) methodology often used in determining capital shortfall.
+This section displays the application of the current stress framework to  the  risk weighting asset (RWA) methodology often used in determining capital shortfall.
 RWA in effect assesses future stressed assets,   as opposed to, with SRISK,  future equity.
@@
 
-Given debt $d$ and equity $w$ for a firm,  assets are
+Given debt $d$ and equity $w$ for a firm at a particular point of time,  assets are
 $$
-d+w=\sum_ja_j\ ,
+a\equiv d+w=\sum_ja_j\ ,
 $$
-where $a_j$ denotes the value of assets in asset class $j$.   Future shortfall is, equivalent to \eref{fcapreq},  
+where $a_j$ denotes the value of assets in asset class $j$.   In terms of current assets $a$, future shortfall is, equivalent to \eref{fshortfall},  
 \be{shortfall2}
-S=  d-(1-k)\sum_ja_j\e^{r_j}\ ,
+S\equiv  d-\alpha\Ax(\e^{r_j})\cq \alpha\equiv(1-k)a\cq \Ax(\e^{r_j})\equiv \sum_j\frac{a_j}{a}\e^{r_j}\ .
 \ee
-where $r_j$ is the (uncertain) log--return on assets $a_j$.
-With the risk weighting methodology the weights $a_j$  are replaced by $a_j/\sigma_j$ where $\sigma_j\ge 1$ is a ``risk" weight with large  weights assigned to  assets  with large perceived ``riskiness."
+Here $r_j$ is the (uncertain) log--return on assets $a_j$ and $\Ax$ denotes weighted averaging using weights $a_j$, the current value of assets in class $j$.
 
-Suppose $S$, $d$ and $r$ are the vectors of shortfalls, debts  and returns, respectively for the firms, and matrix $A$ has rows corresponding to the asset values of different firms.
-Then the vector of firm shortfalls is
+The expected shortfall is 
+\be{rw1}
+\E(S)=d-\alpha\E\{\Ax(\e^{r_j})\}=d-\alpha\Ax\{\E(\e^{r_j})\}\ .
+\ee
+With the risk weighting methodology the weights $a_j/a$ in $\Ax$ are replaced by $a_j/(a\sigma_j)$ where $\sigma_j>0$ is a ``risk" weight.
+Large risk weights $\sigma_j$ are assigned to  assets classes $j$ deemed risky:  assets are downweighed according to  perceived ``riskiness."
+
+The methodology set out in previous sections can be used to formalise the selection of weights $\sigma_j$.
+In particular $\Es$ based on an appropriate risk function $\psi$ replaces $\E$ in \eref{rw1} and leads to \br\ and \pr.
+In particular
 $$
-S = d-(1-k)A\e^{r}\ ,
+\pr(S_i)= -\alpha\times\pr\{\Ax_i(\e^{r_j}\}= -\alpha\times\Ax_i\{\pr(\e^{r_j})\}\ ,
 $$
-where  exponentiation is componentwise.
-Writing $S^+$ as the vector of positive shortfalls then, as in \sref{aggregate}, two aggregate measures of expected shortfall are $S^*= \sum_iS_i^+$ and $S^+=(\sum_iS_i)^+$ where $S_i$ is component $i$ of vector $S$.
+with a similar result for \br.  Here $S_i$ is the shortfall for firm $i$ and $\Ax_i$ utilises the asset weights of firm $i$.
 
-Estimation of \br\ and \pr\ can proceed via simulation:
-$$
-\omega\sim p(\omega)\cq r(\omega)\sim p(r|\omega)
-$$
-where $r(\omega)$ is  the simulated vector of returns for the asset classes given scenario $\omega$.
-The vector of shortfalls corresponding to $\omega$ is then $S(\omega)=d-(1-k) A\e^{r(\omega)}$  where $A$ is the matrix with row $i$ corresponding to the current asset values for firm $i$ and $\e^{r(\omega)}$ denotes componentwise exponentiation.
-Then the vectors of \br\ and \pr, with components corresponding to the different firms $i$ are estimated as
-\be{srisk4}
-\br\approx \frac{1}{N}\sum_\omega S^+(\omega)\cq
- \pr\approx \frac{1}{N}\sum_\omega  \{\psi(\omega)-1\}S^+(\omega)\ ,
-\ee
-with similar results for $S^*=\sum_iS_i^+$ and $(\sum_iS_i)^+$.
-
-Stressful scenarios can be implicitly constructed via the following percentile method.
-Suppose $r\sim p(r)$ are simulations from the joint distribution of future asset returns.
-Returns for each asset class are  ranked yielding simulated percentile vectors $\omega$.
-Denote $S(\omega)$ as the vector of shortfalls computed as before from returns $r$ corresponding to $\omega$.
-Then use these $S(\omega)$  in the expressions \eref{srisk4} with
-$$
-\psi(\omega) = nc(\omega)\prod_j \{1-(1-\omega_j)^{n-1}\}\ ,
-$$
-where $c(\omega)$ is a copula density designed to exaggerate the juxtaposition of  adverse percentile occurrences: such as exaggerated lower tail dependence.
-If $c(\omega)= 1$  there is no exaggeration  and the copula associated with the $r(\omega)$ is the copula induced by $p(r)$.
-If $n=1$ there is no sculpting of the marginal distributions.
+If $\pr(\e^{r_j})\approx\pr(r_j)$ is negative and asset  $j$ is important then \pr$(S_i)$ is large.
+Hence risky assets increase the \pr\ associated with the firm and implicitly increases the imputed shortfall.
+Note $\pr(\e^{r_j})$ is independent of $i$:  different firms combine these via firm specific asset weighting $\Ax_i$.
+Thus a model is constructed for each asset class $j$ rather than, as in the previous sections,  each equity $i$.
+Returns $r_j$ and stresses $\psi$ are jointly simulated from a joint density $f(r_j,\psi)=f(\psi)f(r_j|\psi)$ and simulated returns are used to compute the shortfall \eref{shortfall2} and, in turn \br\ and \pr.
 
@@
 \be{vol}
-\sigma_{i,t+1}^2 = \omega+ \sigma^2_{it}\{\beta+(\alpha+\gamma \eps^-_{it})\eps_{it}^2\}  \cq  \eps^-_{it}= I(\eps_{it}<0)=I(\delta_{it}<\mu)\ ,
+\sigma_{i,t+1}^2 = \omega+ \sigma^2_{it}\{\beta+(\alpha+\gamma \eps^-_{it})\eps_{it}^2\}  \cq  \eps^-_{it}\equiv I(\eps_{it}<0)=I(\delta_{it}<\mu)\ ,
 \ee
@@
 $$
-(Q_{i,t+1}-S) = \alpha (\eta_{it}\eta_{it}'-S) + \beta (Q_{it}-S)\cq \eta_{it}=(\eps_{it},\eps_{mt})' .
+(Q_{i,t+1}-S) = \alpha (\eta_{it}\eta_{it}'-S) + \beta (Q_{it}-S)\cq \eta_{it}\equiv(\eps_{it},\eps_{mt})' .
 $$
@@
 
-\section*{References}
 \bibliography{piet2}

### 2016-10-09 srisk9 copy.tex
Lots and lots of changes
Latest

--- 2016-10-09 srisk8.tex
@@
-\documentclass[12pt]{article}
+\documentclass[authoryear]{elsarticle}
 \usepackage{amsmath}
@@
 \usepackage{enumerate}
-\usepackage{natbib}
 \usepackage{url} % not crucial - just used below for the URL 
@@
 \usepackage{threeparttable}
-
-%\pdfminorversion=4
-% NOTE: To produce blinded version, replace "0" with "1" below.
-\newcommand{\blind}{0}
-
-% DON'T change margins - should be 1 inch all around.
-\addtolength{\oddsidemargin}{-.5in}%
-\addtolength{\evensidemargin}{-.5in}%
-\addtolength{\textwidth}{1in}%
-\addtolength{\textheight}{1.3in}%
-\addtolength{\topmargin}{-.8in}%
 
@@
 \newcommand{\Exd}{\Ex_d}
-\newcommand{\Es}{\widetilde\E}
+\newcommand{\Es}{\Ex}
 \newcommand{\rat}{{\frac{c_{ij}}{c_{i,j-1}}}}
@@
 
-%\bibliographystyle{natbib}
+\title{An early warning system for monitoring  stress in the financial system}
+%\author[acst]{Piet de Jong\corref{cor1}\footnote{The authors gratefully acknowledge CIFR, the Centre of International Financial Regulation for financial support and other assistance}}
+%\ead{piet.dejong@mq.edu.au}
+%\author[acst]{Geoffrey Loudon}
+%\author[acst]{Weihao Choo}
+%\address[acst]{Department of Applied Finance and Actuarial Studies Macquarie University, NSW 2109, Australia.}
+%\cortext[cor1]{Corresponding author}
 
-\def\spacingset#1{\renewcommand{\baselinestretch}%
-{#1}\small\normalsize} \spacingset{1}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\if0\blind
-{
-  \title{\bf Monitoring  risk in the financial system using time series methods}
-  \author{Piet de Jong\thanks{
-    The authors gratefully acknowledge CIFR, the Centre of International Financial Regulation for financial support and other assistance.}\hspace{.2cm}\\
-    Department of Applied Finance and Actuarial Studies, Macquarie University\\
-    and \\
-    Geoffrey Loudon\\
-    Department of Applied Finance and Actuarial Studies, Macquarie University\\
-    and\\
-    Weihao Choo\\
-    Department of Applied Finance and Actuarial Studies, Macquarie University}
-  \maketitle
-} \fi
-
-\if1\blind
-{
-  \bigskip
-  \bigskip
-  \bigskip
-  \begin{center}
-    {\LARGE\bf Measuring baseline and systemic risk using financial time series}
-\end{center}
-  \medskip
-} \fi
-
-\bigskip
 \begin{abstract}
-SRISK methodology recently proposed in the literature is refined and extended.
-The refinement is to define  systemic risk using a formalised stress testing framework including a stress function.
-Baseline risk and the stress risk  are in terms of the  ordinary and stressed expectation.
-Stressed expectation is expectation computed  under a hypothetical  stress, modelled with the stress function and scenarios.
-Systemic stress is defined in terms of a stress function and systemic scenarios impacting on a number of firms or financial entities.
-Stress functions are chosen by the practitioner and typically exaggerate undesirable extreme outcomes.
+SRISK methodology recently proposed in the literature is refined and extended using a formalised stress testing framework and exploiting time series methods.
+Baseline risk and the stress risk  are in terms of time series based ordinary and stressed expectation.
+Stressed expectation is expectation computed  under a hypothetical  stress, modelled with a stress function and scenarios.
+Systemic stress is defined in terms of stresses   impacting groups of firms or financial entities.
+Stress functions are chosen by the practitioner and  exaggerate the probability undesirable  outcomes.
 Properties and characterisations of stress and stress related quantities are displayed and explored.
@@
 
-\noindent%
+\date{}
+\maketitle
+\noindent
 {\it Keywords:}  Capital shortfall, baseline risk, stress testing,  stressed expectation, stress diversification.
-\vfill
 
 \newpage
-\spacingset{1.45} % DON'T change the spacing!
 
@@
 Central banks and other financial regulatory bodies such as the US Financial Stability Oversight Council, the European Systemic Risk Board and the Australian Prudential Regulation Authority (APRA) are concerned with developing and applying early warning quantitative  measures  to warn of potential episodes of heightened systemic risk.
+
 Systemic risk has many dimensions.
@@
 This paper refines and extends the SRISK model of \cite{brownlees2015} in  key ways.
-First, their SRISK measure is refined  as a put on the expected shortfall.
-Second, the ordinary expectation of is defined as the baseline risk (\br) associated with the put.
-Using a stress function  the so--called stressed expectation is used to characterise the expectation given a stress.
+First SRISK is formalised  as a put on the expected shortfall with the ordinary expectation defined as the baseline risk (\br) associated with the put.
+Using a stress function  the so--called stressed expectation is used to measure the impact of stress.
 Stressed expectation can be similar to the \cite{brownlees2015} conditional expectation given  a severe market downturn.
-However our generalised methodology  permits a far more flexible definition of stress and a wider class of ``stressors" including stress defined in terms of  a number of extreme outcomes.
-The difference between the stressed and ordinary expectation is defined as the risk associated with the stress, called \pr\ where PSI refers the function modelling the stress.
+However our generalised methodology  permits a more flexible definition of stress and a wider class of ``stressors" including stress defined in terms of  a number of extreme outcomes.
+The difference between the stressed and ordinary expectation is defined as the stress risk associated, called \pr\ where P stand for psi,  the function $\psi$ modelling the stress.
 
@@
 \cite{brownlees2015} define stress by conditioning on an absolute cutoff of arbitrary size and length.
-Our development suggests  it is also helpful to specify conditional behaviour in percentile terms relative to current market conditions.
+With time dependent volatility or uncertainty, absolute cutoffs  are less meaningful and our development suggests  it is  useful to specify conditional behaviour in percentile terms relative to current market conditions.
 This yields a sharper focus on the incremental impact of further stress and permits a more incisive view of the  implications from SRISK numbers.
@@
 
-To demonstrate the nature and usefulness of our measures, we use publicly available daily financial data for the eight Australian banks detailed in \tref{eightbanks} spanning the period from  3 April 2000 through to 1 December 2014.
+The nature and usefulness of our measures are demonstrated using publicly available daily financial data for the eight Australian banks detailed in \tref{eightbanks} spanning the period from  3 April 2000 through to 1 December 2014.
 The data is described in detail in \aref{data}.
@@
 Section \ref{litrev} briefly discusses related literature.
-Section \ref{capshort} and \ref{futshort} define current and future  capital shortfall similarly as \cite{brownlees2015} under a simple Basel II regulatory framework.
-The definition of systemic risk used by \cite{brownlees2015} is discussed in \sref{srisk}, and is refined and extended in \sref{improve}.
+Section \ref{capshort} defines current and future  capital shortfall similarly as \cite{brownlees2015} under a simple Basel II regulatory framework.
+The definition of systemic risk used by \cite{brownlees2015} is discussed, refined and improved in \sref{srisk}.
 Applications to Australian bank data are discussed in \sref{simulate} and \sref{simulate1}.
@@
 \begin{center}
-\includegraphics[width=16cm]{figures/prices.pdf}
+ \begin{tabular}{cc}
+      \resizebox{55mm}{!}{\includegraphics{figures/fig1a.pdf}} &
+      \resizebox{55mm}{!}{\includegraphics{figures/fig1b.pdf}}\\
+    \end{tabular}
 \caption{Daily stock  prices of four major (left panel) and four minor (right panel) Australian banks 2000--2014.  Price series normalised to start at 1.}
@@
 
-\cite{brownlees2015} further develop the empirical methodology to construct SRISK measures.
+\cite{brownlees2015}  develop empirical methodology to construct SRISK measures.
 SRISK depends on the firm's size, leverage and its LRMES.
@@
 \cite{Engle2015} extend the model in \cite{brownlees2015} to incorporate global, country and industry effects.
-This extended model makes  use of \cite{Engle2014dcb}'s dynamic conditional beta model.
+This extended model makes  use of the \citep{Engle2014dcb} dynamic conditional beta model.
 Their empirical methods are able to provide information about the relative systemic importance of industry type and country identity.
@@
 
-\cite{adrian2011covar} propose an alternative measure of systemic risk that emphasises the co-dependence of financial firms and the importance of risk spillovers within the financial sector.
-They introduce CoVaR$_i$ which computes the Value-at-Risk (VaR) of the entire financial system, conditional on institution $i$ being in distress.
+\cite{adrian2011covar} propose an alternative measure of systemic risk  emphasising the co--dependence of financial firms and the importance of risk spillovers within the financial sector.
+They introduce CoVaR$_i$ which computes the Value--at--Risk (VaR) of the entire financial system, conditional on institution $i$ being in distress.
 Distress is defined as the state where the institution is exactly at its VaR level.
 \cite{Girardi2013} improve CoVaR by conditioning on the institution being at most at its VaR.
-This generalisation is useful as it takes into account the severity of tail losses and facilitates back-testing of CoVaR.
+This generalisation is useful as it takes into account the severity of tail losses and facilitates back--testing of CoVaR.
 
@@
 Empirical estimates of SRISK  requires a model for the joint distribution of returns of individual firms and the market.
-Many of these papers use \cite{engle2002dynamic}'s GARCH-DCC model aiming to capture the time-varying dynamics of the return (co)variances in a feasible manner.
+Many of these papers use \cite{engle2002dynamic}'s GARCH--DCC model aiming to capture the time-varying dynamics of the return (co)variances in a feasible manner.
 While we also use this model in our empirical analysis, we emphasize that our approach can utilise any appropriate model for simulating the joint distribution of firm and market returns going forward.
 
-\section{Capital shortfall and leverage}\label{capshort}
+\section{Capital shortfall, leverage and future shortfall}\label{capshort}
 
@@
 It is used here to conform to the previous literature and provide an easily accessible  platform to the key results of this paper,  without becoming entangled in precise and perhaps more realistic definitions of shortfall.
-Indeed \sref{riskmethod} deals with a more realistic and intricate definition.
+\sref{riskmethod} deals with a more realistic and intricate definition.
 
@@
 \begin{center}
-\includegraphics[width=16cm]{figures/bloglev.pdf}
+ \begin{tabular}{cc}
+      \resizebox{55mm}{!}{\includegraphics{figures/fig2a.pdf}} &
+      \resizebox{55mm}{!}{\includegraphics{figures/fig2b.pdf}}\\
+    \end{tabular}
 \caption{Adjusted log--leverages for four major (left panel) and four minor (right panel) Australian banks from the beginning of 2003 through to end of 2014.
@@
 \end{figure}
-
-\section{Future capital shortfall}\label{futshort}
 
@@
 
-The actual capital shortfall is $S^+$, the positive part of $S$:
+The  future capital shortfall is $S^+$, the positive part of $S$:
 \be{bs}
-S^+ = kd (1-\e^{r-\ell})^+\ .
+S^+ = kd (1-\e^{r-\ell})^+=\left\{\begin{array}{lr} 0\ , & r\ge \ell\ ,\\ kd (1-\e^{r-\ell})\ , & r<\ell\ .\end{array}\right.
 \ee
 Thus $S^+$ is $kd$ times a put on the return $\e^{r-\ell}$ with strike 1.
-There is a future shortfall if $r<\ell$.
 Default put options similar to \eref{bs} have been discussed in the insurance literature as critical to an evaluation of a firm:  see for
@@
 
-To illustrate the setup, \fref{simulation}   displays two snapshot outputs from projections generated as described  in \aref{garchdcc}:  6000  simulated one month ahead projected returns for  CBA and the wider market, on  two dates: the first trading day in January 2009 and the first trading day in December 2014.
+To appreciate the behaviour of $S$ and $S^+$, \fref{simulation}   displays two snapshot outputs from projections generated as described  in \aref{garchdcc}:  6000  simulated one month ahead projected returns for  CBA and the wider market, on  two dates: the first trading day in January 2009 and the first trading day in December 2014.
 The CBA returns are used to calculate the future shortfall per units $kd$ as in \eref{fshortfall}.
 Both panels use the same horizontal and vertical scales.
-Thus based on the available data at those two points in  time, policy makers and regulators faced entirely different projections based on the same time series model.
+Based on the available data at those two points in  time, policy makers and regulators faced entirely different projections.
 The scatter of dots are the forward simulations.
@@
 In the right panel there is slight decline in the stock price, and a more substantial market downturn.
-Thus at the beginning of January  2009 CBA was projected to be far from compliance in a month while in December 2014 the one month projection is of complete compliance.
+Thus at the beginning of January  2009 the one month forward projection for  CBA was far from compliance, while in December 2014 the one month forward projection is of complete compliance.
 
 The two panels  display very different volatility and slopes.
-In January 2009 both CBA and market return distributions are highly volatile and correlated.
+In January 2009 both CBA and the market return distributions are highly volatile and correlated.
 The correlation remains strong in December 2014 but with less return volatility.
-These snapshots are used to compute baseline and systemic stresses shown in subsequent sections.
+Subsequent sections of this paper use time series of these  snapshots  to compute cross sectional and longitudinal baseline and systemic stresses.
 
@@
 \begin{center}
-\includegraphics[width=16cm]{figures/figCBA.pdf}
+\includegraphics[width=12cm]{figures/figCBA.pdf}
 \caption{Forecast bivariate distribution of future shortfall $S$ per unit $kd$  for CBA (vertical axis) and market rate of return (horizontal axis) at start of January 2009 (left panel)  and December 2014 (right panel).
 Note scales in both panels are the same, the relatively large volatility in the left panel, and the left skew in the  marginal distributions.
-Black dots indicate actual  outcome at the end of the month.}\label{simulation}
+Black dots indicate actual  outcome at the end of each month.}\label{simulation}
 \end{center}
@@
 
-\section{Systemic risk SRISK}\label{srisk}
+\section{Improving SRISK for systemic risk monitoring}\label{srisk}
 
@@
 where $S_i$ refers to the future shortfall in firm $i$.
-Further  $\Es$ denotes expectation given a major general market downturn.
+Here, as before, $^+$ indicates the ``positive part"   and  $\Es$ denotes expectation given a major general market downturn.
 Hence the expected capital shortfall (allowing surplus offset) is computed from \eref{fshortfall} assuming a market downturn and added across all firms.
@@
 
-The systemic risk of firm $i$ at a particular point of time is defined by \cite{brownlees2015} as the proportionate contribution \eref{esrisk}:
+The systemic risk of firm $i$ at a particular point of time is  \citep{brownlees2015} the proportional contribution to \eref{esrisk}
 \be{sriskperc}
-\sr_i\equiv\frac{\{\widetilde\E(S_i)\}^+}{\sr}\ .
+\sr_i\equiv\frac{\{\Ex(S_i)\}^+}{\sr}\ .
  \ee
@@
 
-The above general setup  is subject to criticisms and improvements.
-First, SRISK in \eref{sriskperc} can be modified to be based on $S_i^+$ the positive part of shortfall rather than the positive part of expected shortfall.
-In many cases $\Es(S_i)=0$  and insensitive to actual shortfalls.
-Second, the definition of $\Es$ is restrictive: a market downturn defined by a market downturn greater than 10\%.
-Such a specific absolute downturn is unnecessarily arbitrary.
-For example the downturn is more easily achieved  in a highly volatile environment and hence the stress response takes on different meanings depending on context.
-Third as shown below the stressed expectation $\Es$ is composed of two parts, so--called baseline risk and change in expectation risk caused by the actual stress event.
+A more sensitive measure results when \eref{sriskperc} is based on $\Es(S_i^+)$ rather than $\{\Es(S_i)\}^+$.
+In many cases $\Es(S_i)=0$  and hence insensitive to actual shortfalls.
+Further, the definition of $\Es$ is readily generalised to encompass more flexible stress specifications.
+For example ``cutoff"  market downturns such as 10\%  are more easily achieved  in a highly volatile environment implying the stress response takes on different meanings depending on volatility.
+Finally, as shown below, the stressed expectation $\Es$ is composed of two parts, so--called baseline risk and change in expectation risk caused by the actual stress event.
 
-\section{Improved systemic risk measurement}\label{improve}
+\subsection{Improved systemic risk measurement framework}
+The  proposed improved framework assumes a response variable such as capital shortfall $S$ or $S^+$ for a firm or group of firm subjected to stress.
+For notational convenience assume the response of interest is $S$ although this can be replaced with $S^+$ or  other function of $S$.
+The improved framework is built up from the following parts:
+\bi
+\i  There exist a collection of scenarios labelled $\omega$ where  $\omega$ discrete or continuous.
+Scenarios $\omega$ are systemic if they have potential impact on many firms.
+The ``natural" probability of scenario $\omega$ is $f(\omega)$.
+If $\omega$ is continuous then $f(\omega)$ is interpreted as a probability density.
 
-This section describes a general framework for  systemic risk measurement.
-The framework builds on and aims to improve on the techniques built into f \sr\ and $\sr_i$ in \eref{esrisk} and \eref{sriskperc}.
-The framework assumes a response variable such as capital shortfall $S$ or $S^+$ for a firm or group of firm subjected to stress.
-The  framework   puts ``stress testing" on a formal footing.
+\i  A stress function $\psi(\omega)\ge 0$ is defined on the  scenarios $\omega$ with  $\E(\psi)=1$.
 
-For notational convenience assume the response of interest is $S$ although this can be replaced with $S^+$ or some other function of $S$.  The framework is built up from the following parts:
-\bi
-\i  A stress function $\psi(\omega)\ge 0$ defined on scenarios $\omega$.
-Scenarios $\omega$ can be discrete or continuous.
-Further $\E(\psi)=1$ where expectation is across all scenarios.
-Scenarios $\omega$ are systemic if they have potential impact on many firms.
 \i  Baseline risk is defined as the ordinary expectation
@@
 $$
-where $f(\omega)$ denotes the ``real world" probabilities of different scenarios.    If the space of scenarios is continuous then $f(\omega)$ is a density and the  sum an integral.
-\i Stressed expectation  is defined in terms of the stress function as
+  If $\omega$ continuous then the sum is interpreted as an integral.
+
+\i Stressed expectation  is
 \be{formula}
@@
 where the last equality follows since $\E(\psi)=1$.
-The import of $\psi(\omega)$ is to change the natural probabilities $f(\omega)$ to ``stressed" probabilities $\tilde f(\omega)\equiv \psi(\omega)f(\omega)$.
-Note $\sum_\omega \tilde f(\omega)=\E(\psi)=1$.
- \i $\psi$--risk is defined as the difference between baseline risk and stressed risk
+The import of $\psi(\omega)$ is to change the natural probabilities $f(\omega)$ to ``stressed" probabilities $\psi(\omega)f(\omega)$.
+Note $\sum_\omega\psi(\omega) f(\omega)=\E(\psi)=1$.
+ \i $\psi$--risk is defined as the difference between stressed risk and baseline risk
  $$
@@
 
- A simple example is where $\psi(\omega)=0$ except for a single  scenario $\omega$ where it is equal to $1/f(\omega)$.
+\subsection{Practical stress functions}
+The simplest example is where $\psi(\omega)=0$ except for a single  scenario $\omega$ where it is equal to $1/f(\omega)$.
 In this case all probability is transferred to the single scenario $\omega$ and $\Es(S)=\E(S|\omega)$.
@@
 
-A richer example is where $\omega$ is the percentile of a variable such as the overall market return, measured relative to the currently applicable market return distribution.
+A richer example is where $\omega$ is the percentile of a variable such as the overall market return, measured relative to the current  market return distribution.
 Then $f(\omega)$ is the uniform density on the unit interval.
@@
 then $\psi$ is the density of the worst percentile outcome in $n$ independent trials.
-This stress function implies \pr\  corresponds to the increase in risk when the general market has its worst outcome in $n$ independent trials.
+In this case \pr\  corresponds to the increase in risk when the general market has its worst outcome in $n$ independent trials given the current return distribution.
 This stress function  is used to study stress in Australian banks in \sref{simulate1}.
@@
 Another example, close to that implemented in \cite{brownlees2015} is where $\omega$ is a percentile with $\psi(\omega)=1/c$ for $\omega<c$ and 0 otherwise.
-In this case  $\Es(S)=\E(S|\psi<c)$ and \pr\  is the difference between the  conditional tail and ordinary expectation.
+In this case  $\Es(S)=\E(S|\psi<c)$ and \pr\  is the difference between the   tail and ordinary expectation.
 More general stressed expectations of the form of \eref{formula} are discussed in \cite{furman2008weighted1} and \cite{choo2010determining}.
 
-Both \br\ and \pr\ are linear and aggregate over firms.  For example
+\subsection{BRISK and PRISK properties and associated measures}
+
+Both \br\ and \pr\ are linear and aggregate over firms:
 $$
-\pr\left(\sum_iS_i\right) = \sum_i\pr\left(S_i\right)\ .
+\br\left(\sum_iS_i\right) = \sum_i\br\left(S_i\right)\cq\pr\left(\sum_iS_i\right) = \sum_i\pr\left(S_i\right)\ .
 $$
-Linearity is obvious for \br\ and for \pr\  follows from the linearity of covariance.
+Linearity is obvious for \br\ and linearity for \pr\  follows from the linearity of covariance.
 
@@
 
-In many financial contexts expected shortfalls  may increase  due to increased volatility.   This is captured with \br.  \pr\ focusses on the  stress effects induced with $\psi$.
-
-\br\ and \pr\ are easily computed  in a simulation environment given a joint model $f(S,\psi)=f(\psi)f(S|\psi)$ for $S$ and the scenarios $\omega$.
-If $N$ of simulations $\omega\sim f(\omega)$ and $S(\omega)\sim f(S|\omega)$ are generated and then
+\br\ and \pr\ are readily computed  via simulation given a joint model $f(S,\omega)=f(\omega)f(S|\omega)$ for $S$ and the scenarios $\omega$.
+Given $N$ simulations $\omega\sim f(\omega)$ and $S(\omega)\sim f(S|\omega)$  then
 $$
-\br \approx \frac{1}{N}\sum_\omega S(\omega)\cq \pr\approx \frac{1}{N}\sum_\omega \{\psi(\omega)-1\}S(\omega)
+\br \approx \frac{1}{N}\sum_\omega S(\omega)\cq \pr\approx \frac{1}{N}\sum_\omega \{\psi(\omega)-1\}S(\omega)\ .
 $$
-If $\psi$ is based  on percentile outcomes   then the simulated $\omega$ are ranked and $\psi(\omega)$ based on the rank of $\omega$.
+If $\psi$ is based  on percentile outcomes   then the simulated $\omega$ are ranked and $\psi(\omega)$ is based on the rank of $\omega$.
 If $\omega$ has many components corresponding to percentiles of different variables then $\psi(\omega)$ is a copula density with appropriate induced tail dependence.
 
-\section{Forward shortfall and  return simulations}\label{simulate}
+\subsection{Forward return and shortfall simulations}\label{simulate}
 
@@
 judiciously constructed scenarios by regulators or policymakers.
-The  framework set out in \sref{improve} can be based on  any  generated  future  scenarios.
+The  framework set out in \sref{srisk} can be based on  any  generated  future  scenarios.
 
@@
 
-\section{One month ahead forecast risk in individual banks}\label{simulate1}
+\section{Australian bank stress forecasts}\label{simulate1}
 
@@
 \begin{center}
-\includegraphics[width=16cm]{figures/default.pdf}
-\caption{Forecast one month ahead  \br\ (top panels) and \pr\ (bottom panels) based on $S^+$ for   major (left panel) and  minor (right panel)  banks 2003--2014.
+\includegraphics[width=12cm]{figures/default.pdf}
+\caption{\br\ (top panels) and \pr\ (bottom panels) based on one month ahead  forecasts of $S^+$ for   major (left panel) and  minor (right panel)  Australian banks 2003--2014.
+PRISK is based on worst monthly market outcome in 1 year.
 Note different y--scale on top and bottom panels.}\label{default}
@@
 
-\section{Aggregate market stress}\label{aggregate}
+\fref{sysstress} gives a picture of the relative magnitudes of \br\ and \pr\ in each of the eight banks.
+For the major banks NAB stand out as, having \br\ more dominant than \pr\ and generally having heightened levels of \br.
+ANZ appears to have relatively higher levels of \pr.
+For the minors, MQG has persistently higher levels of \pr\ with BOQ and BEN comparable ratios and ABA having virtually no \pr\ compared to \br\ at any level of the latter.
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=12cm]{figures/sysstress.pdf}
+\caption{\pr\  (y--axis) versus \br\  (x--axis)   for major  (left panel) and  minor banks (right panel)  for 144 months 2003--2014}
+\label{sysstress}
+\end{center}
+\end{figure}
+
+\section{Monitoring aggregate  stress}\label{aggregate}
 
 \cite{brownlees2015} defines systemic risk in terms of $\Es(S)$.
-However a stressed expectation may be high simply on account of  higher than normal volatility or leverage.
-Hence \cite{brownlees2015} combines both baseline stress, due to high volatility or leverage, and the imposed system stress.
-However it is important to understand the mix of the two different stresses.
+However $\Es(S)$ combines both baseline stress, due to high volatility or leverage, and the imposed system stress.
+To understand the nature of stress it is important to understand the mix of these two different stresses.
+
+\subsection{Alternative aggregate stress measures}
 
 Two practical alternatives to SRISK for aggregating risk in financial institutions are set out \tref{aggstress}.  
-The first row of the table reproduces the defintion of SRISK in \eref{srisk} and decomposes the same into \br\ and \pr.
+The first row of the table reproduces the definition of SRISK in \eref{srisk} and decomposes \eref{srisk} into \br\ and \pr.
 It is apparent that \sr\  measures a mix of \br\ and \pr.
-Further risks only arise if there is an ``on average"  shortfall and the measure is relatively insensitive to tail events .
+Further heightened risk only arises if there is an ``on average"  shortfall.
+Thus SRISK is relatively insensitive to tail events .
 
@@
 
-The second aggregation of risk displayed in \tref{aggstress} uses $S^*$, the aggregate sum of positive shortfalls.
-With $S^*$ shortfall in one firm are not offset by  surpluses elsewhere and the measure is sensitive to tail risk.
-If subscript $\%$ denotes percentage contribution to the corresponding total then a direct calculation shows the total risk $\br+\pr$ in $S_i^+$ as a percentage of the total risk in  $S^*\equiv \sum_iS^+_i\ge S^+$ is
+The second aggregation of risk displayed in \tref{aggstress} uses $S^*$, the  sum of positive shortfalls across firms.
+With $S^*$, shortfall within a firm is not offset by averaging  nor with surpluses in other firms.
+The measure is thus more sensitive to tail risk.
+A direct calculation shows
 \be{percc}
- \pr_\%(S^+_i)+\frac{\br(S^*)}{\br(S^*)+\pr(S^*)}\left\{\br_\%(S^+_i)-\pr_\%(S^+_i)\right\}\ ,
+\frac{\Es(S_i^+)}{\Es(S^*)} =  \frac{\pr(S^+_i)}{\pr(S^*)}+\frac{\E(S^*)}{\Es(S^*)}\left\{\br_\%(S^+_i)-\pr_\%(S^+_i)\right\}\ .
 \ee
- where the percentage subscripts indicate percentages of the corresponding totals.
-Thus total risk is dominated by \br\ if the latter is large compared to \pr\ as apparent in the time series analyses in \sref{simulate1}.
+The analyses in \sref{simulate1} suggest \br\ tends to dominate \pr.   Thus total risk tends to be dominated by \br.
 
@@
 
-\section{Monthly monitoring  of financial stress}\label{monitoring}
+\subsection{Aggregate stress in the Australian banking sector}\label{monitoring}
  \tref{twodates} contains real time stress calculations on the first trading day of  January 2009 and December 2014.
@@
 \begin{table}[ht]
-\caption{Projected one month ahead  stress for banks}
+\caption{One month ahead bank stress projections}
 \label{twodates}
@@
 \begin{tablenotes}
-\item[]The main body of table uses shortfall measure  is $S_i^+$.
+\item[]The main body of table uses shortfall measure $S_i^+$.
 Aloglev is 100 times the adjusted log--leverage.
@@
 
-The two top panels of \fref{muqs} track  \br\ and \pr\ for the banking sector as a whole through time.
+The two  panels of \fref{fig6} track  \br\ and \pr\ for the banking sector as a whole through time.
 There is virtually no risk in the system till late 2007 and the early warnings show a buildup in \br\ in $S^*$ compared to $S^+$.
@@
 
-The top right panels in \fref{muqs} display the time series behaviour of \pr.
+The top right panel in \fref{fig6} displays the time series behaviour of \pr.
 Generally \pr\ is less than \br.
-Further, in situations of elevated risk,  \pr\ in $S^+$ exceeds that in $S^*f$ indicating systemic stress from a general market downturn is greater in the system as a whole than its constituent parts.
+Further, in situations of elevated risk,  \pr\ in $S^+$ exceeds that in $S^*$ indicating systemic stress from a general market downturn is greater in the system as a whole than its constituent parts.
 Again, however, as displayed in the bottom right panel, \pr\ initially builds up in $S^*$, and only later manifests itself in $S^+$.
@@
 
-\fref{sysstress} gives a picture of the relative magnitudes of \br\ and \pr\ in each of the eight banks.
-For the major banks NAB stands out as, having \br\ more dominant than \pr\ and generally having heightened levels of \br.
-ANZ appears to have relatively higher levels of \pr.
-For the minors, MQG has persistently higher levels of \pr\ with BOQ and BEN comparable ratios and ABA having virtually no \pr\ compares to \br\ at any level of the latter.
-
 \begin{figure}[htbp]
 \begin{center}
-\includegraphics[width=16cm]{figures/muqs.pdf}
-\caption{Risk based on $S^*$ and $S^+$.
-Results for \br\ and \pr\ in left and right panels, respectively.
-The top panels track results   from the beginning of 2003 through to the end of 2014.
-Bottom panels  plot  two measures in the corresponding top panel against each other: On the left \br($S^+$) on y--axis versus \br($S^*$) on x--axis, and similarly for  \pr\ in the bottom right panel.}\label{muqs}
+ \begin{tabular}{cc}
+      \resizebox{55mm}{!}{\includegraphics{figures/fig6a.pdf}} &
+      \resizebox{55mm}{!}{\includegraphics{figures/fig6b.pdf}}\\
+    \end{tabular}
+\caption{One month ahead system BRISK and PRISK based on predicted $S^*$ and $S^+$   from the beginning of 2003 through to end of 2014.}\label{fig6}
 \end{center}
@@
 
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=16cm]{figures/sysstress.pdf}
-\caption{\pr\  (y--axis) versus \br\  (x--axis)   for major banks (left panel) and  minor banks (right panel)  for 144 months 2003--2014}
-\label{sysstress}
-\end{center}
-\end{figure}
+%  Bottom panels  plot  two measures in the corresponding top 
+% panel against each other: On the left \br($S^+$) on y--axis versus % \br($S^*$) on x--axis, and similarly for  \pr\ in the bottom right 
+% panel.
 
@@
 $$
-a\equiv d+w=\sum_ja_j\ ,
+d+w=\sum_ja_j\ ,
 $$
-where $a_j$ denotes the value of assets in asset class $j$.   In terms of current assets $a$, future shortfall is, equivalent to \eref{fshortfall},  
+where $a_j$ denotes the value of assets in asset class $j$.   Future shortfall is, equivalent to \eref{fshortfall},  
 \be{shortfall2}
-S\equiv  d-\alpha\Ax(\e^{r_j})\cq \alpha\equiv(1-k)a\cq \Ax(\e^{r_j})\equiv \sum_j\frac{a_j}{a}\e^{r_j}\ .
+S\equiv  d-(1-k)\sum_ja_j\e^{r_j}\ ,
 \ee
-Here $r_j$ is the (uncertain) log--return on assets $a_j$ and $\Ax$ denotes weighted averaging using weights $a_j$, the current value of assets in class $j$.
+where $r_j$ is the (uncertain) log--return on assets $a_j$.
+With the risk weighting methodology the weights $a_j$  are replaced by $a_j/\sigma_j$ where $\sigma_j\ge 1$ is a ``risk" weight with large  weights assigned to  assets  with large perceived ``riskiness."
 
-The expected shortfall is 
-\be{rw1}
-\E(S)=d-\alpha\E\{\Ax(\e^{r_j})\}=d-\alpha\Ax\{\E(\e^{r_j})\}\ .
+Suppose $S$, $d$ and $r$ are the vectors of shortfalls, debts  and returns, respectively for the firms, and matrix $A$ has rows corresponding to the asset values of different firms.
+Then the vector of firm shortfalls is
+$$
+S = d-(1-k)A\e^{r}\ ,
+$$ 
+where  exponentiation is componentwise.
+Writing $S^+$ as the vector of positive shortfalls then, as in \sref{aggregate}, two aggregate measures of expected shortfall are $S^*\equiv \sum_iS_i^+$ and $(\sum_iS_i)^+$ where $S_i$ is component $i$ of vector $S$.
+
+Estimation of \br\ and \pr\ can proceed via simulation:
+$$
+\omega\sim f(\omega)\cq r(\omega)\sim f(r|\omega)
+$$
+where $r(\omega)$ is  the simulated vector of returns for the asset classes given scenario $\omega$.
+The vector of shortfalls corresponding to $\omega$ is then $S(\omega)=d-(1-k) A\e^{r(\omega)}$  where $A$ is the matrix with row $i$ corresponding to the current asset values for firm $i$ and $\e^{r(\omega)}$ denotes componentwise exponentiation.
+Then the vectors of \br\ and \pr, with components corresponding to the different firms $i$ are estimated as
+\be{srisk4}
+\br(S^+)\approx \frac{1}{N}\sum_\omega S^+(\omega)\cq
+ \pr(S^+)\approx \frac{1}{N}\sum_\omega  \{\psi(\omega)-1\}S^+(\omega)\ ,
 \ee
-With the risk weighting methodology the weights $a_j/a$ in $\Ax$ are replaced by $a_j/(a\sigma_j)$ where $\sigma_j>0$ is a ``risk" weight.
-Large risk weights $\sigma_j$ are assigned to  assets classes $j$ deemed risky:  assets are downweighed according to  perceived ``riskiness."
+with similar results for $S^*=\sum_iS_i^+$ and $(\sum_iS_i)^+$.
 
-The methodology set out in previous sections can be used to formalise the selection of weights $\sigma_j$.
-In particular $\Es$ based on an appropriate risk function $\psi$ replaces $\E$ in \eref{rw1} and leads to \br\ and \pr.
-In particular
+Stressful scenarios can be implicitly constructed via the following percentile method.
+Suppose $r\sim f(r)$ are simulations from the joint distribution of future asset returns.
+Returns for each asset class are  ranked yielding simulated percentile vectors $\omega$.
+Denote $S(\omega)$ as the vector of shortfalls computed as before from returns $r$ corresponding to $\omega$.
+Then use these $S(\omega)$  in the expressions \eref{srisk4} with
 $$
-\pr(S_i)= -\alpha\times\pr\{\Ax_i(\e^{r_j}\}= -\alpha\times\Ax_i\{\pr(\e^{r_j})\}\ ,
+\psi(\omega) = nc(\omega)\prod_j \{1-(1-\omega_j)^{n-1}\}\ ,
 $$
-with a similar result for \br.  Here $S_i$ is the shortfall for firm $i$ and $\Ax_i$ utilises the asset weights of firm $i$.
-
-If $\pr(\e^{r_j})\approx\pr(r_j)$ is negative and asset  $j$ is important then \pr$(S_i)$ is large.
-Hence risky assets increase the \pr\ associated with the firm and implicitly increases the imputed shortfall.
-Note $\pr(\e^{r_j})$ is independent of $i$:  different firms combine these via firm specific asset weighting $\Ax_i$.
-Thus a model is constructed for each asset class $j$ rather than, as in the previous sections,  each equity $i$.
-Returns $r_j$ and stresses $\psi$ are jointly simulated from a joint density $f(r_j,\psi)=f(\psi)f(r_j|\psi)$ and simulated returns are used to compute the shortfall \eref{shortfall2} and, in turn \br\ and \pr.
+where $c(\omega)$ is a copula density designed to exaggerate the juxtaposition of  adverse percentile occurrences: such as exaggerated lower tail dependence.
+If $c(\omega)\equiv 1$  there is no exaggeration  and the copula associated with the $r(\omega)$ is the copula induced by $f(r)$.
+If $n=1$ there is no sculpting of the marginal distributions.
 

### 2016-10-09 srisk9.tex
Lots and lots of changes
Latest

--- 2016-10-09 srisk9 copy.tex
@@
 \begin{abstract}
-SRISK methodology recently proposed in the literature is refined and extended using a formalised stress testing framework and exploiting time series methods.
-Baseline risk and the stress risk  are in terms of time series based ordinary and stressed expectation.
+SRISK methodology recently proposed in the literature is refined and extended using a formalised stress testing framework.
+The framework defines two types of risk:  baseline risk and the stress risk, corresponding to ordinary and ``stressed" expectation, respectively, given a time series model and past observations.
 Stressed expectation is expectation computed  under a hypothetical  stress, modelled with a stress function and scenarios.
-Systemic stress is defined in terms of stresses   impacting groups of firms or financial entities.
 Stress functions are chosen by the practitioner and  exaggerate the probability undesirable  outcomes.
 Properties and characterisations of stress and stress related quantities are displayed and explored.
+Systemic stress is defined in terms of stresses   impacting groups of firms or financial entities.
 Application is made to the study of the stability of Australian banks using daily time series data.
